### 2015-03-02 cutsystems.tex
Initial commit.

\documentclass[english,letter paper,12pt,leqno]{article}
\usepackage{stmaryrd}
\usepackage{amsmath, amscd, amssymb, mathrsfs, accents, amsfonts,amsthm}
\usepackage[all]{xy}
\usepackage{tikz}
\def\nicedashedcolourscheme{\shadedraw[top color=blue!22, bottom color=blue!22, draw=gray, dashed]}
\def\nicecolourscheme{\shadedraw[top color=blue!22, bottom color=blue!22, draw=white]}
\def\nicepalecolourscheme{\shadedraw[top color=blue!12, bottom color=blue!12, draw=white]}
\def\nicenocolourscheme{\shadedraw[top color=gray!2, bottom color=gray!25, draw=white]}
\def\nicereallynocolourscheme{\shadedraw[top color=white!2, bottom color=white!25, draw=white]}
\definecolor{Myblue}{rgb}{0,0,0.6}
\usepackage[a4paper,colorlinks,citecolor=Myblue,linkcolor=Myblue,urlcolor=Myblue,pdfpagemode=None]{hyperref}

\SelectTips{cm}{}

\setlength{\evensidemargin}{0.1in}
\setlength{\oddsidemargin}{0.1in}
\setlength{\textwidth}{6.3in}
\setlength{\topmargin}{0.0in}
\setlength{\textheight}{8.5in}
\setlength{\headheight}{0in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\newtheoremstyle{example}{\topsep}{\topsep}
	{}
	{}
	{\bfseries}
	{.}
	{2pt}
	{\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}

	\theoremstyle{example}
	\newtheorem{definition}[theorem]{Definition}
	\newtheorem{example}[theorem]{Example}
	\newtheorem{remark}[theorem]{Remark}

\numberwithin{equation}{section}

% Operators
\def\eval{\operatorname{ev}}
\def\res{\operatorname{Res}}
\def\Coker{\operatorname{Coker}}
\def\Ker{\operatorname{Ker}}
\def\im{\operatorname{Im}}
\def\can{\operatorname{can}}
\def\K{\mathbf{K}}
\def\D{\mathbf{D}}
\def\N{\mathbf{N}}
\def\LG{\mathcal{LG}}
\def\Ab{\operatorname{Ab}}
\def\Hom{\operatorname{Hom}}
\def\modd{\operatorname{mod}}
\def\Modd{\operatorname{Mod}}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\tot}{Tot}
\DeclareMathOperator{\ch}{ch}
\DeclareMathOperator{\str}{str}
\DeclareMathOperator{\hmf}{hmf}
\DeclareMathOperator{\HMF}{HMF}
\DeclareMathOperator{\hf}{HF}
\DeclareMathOperator{\At}{At}
\DeclareMathOperator{\Cat}{Cat}
\DeclareMathOperator{\Spec}{Spec}

\begin{document}

% Commands
\def\Res{\res\!}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\Ress}[1]{\res_{#1}\!}
\newcommand{\cat}[1]{\mathcal{#1}}
\newcommand{\lto}{\longrightarrow}
\newcommand{\xlto}[1]{\stackrel{#1}\lto}
\newcommand{\mf}[1]{\mathfrak{#1}}
\newcommand{\md}[1]{\mathscr{#1}}
\def\l{\,|\,}
\def\sgn{\textup{sgn}}

\title{Computing with cut systems}
\author{Daniel Murfet}

\maketitle

\begin{abstract}
A cut system has objects, $1$-morphisms and $2$-morphisms, similar to a bicategory. In contrast to the composition of $1$-morphisms in a bicategory, the cut operation on $1$-morphims in a cut system produces representations of Clifford algebras in supercategories rather than bare objects. The motivating example of a cut system refines the bicategory of Landau-Ginzburg models, in which the objects are hypersurface singularities and the $1$-morphisms are matrix factorisations.
\end{abstract}

\section{Introduction}

In this paper we develop a new semantics of composition using a bicategorical formalism that we call \emph{cut systems}, inspired by Gentzen's cut-elimination \cite{gentzen} and Girard's geometry of interaction \cite{girard_towards}. The formalism is used to ``make computable'' a bicategory of isolated hypersurface singularities and matrix factorisations that has been studied in the context of topological field theory \cite{McNameethesis, cr0909.4381}. This means that the operations making up the data of the bicategory are given algorithmically, and can be implemented on a computer. One of the main applications, to be given in a sequel \cite{cutsystems2}, is to construct a model of a fragment of Girard's linear logic \cite{girard_llogic}. Roughly speaking, this provides mathematical semantics for a programming language in which data types are interpreted as hypersurface singularities, and programs are interpreted as homotopy equivalence classes of matrix factorisations.

What is a semantics of composition? Consider that in a category or bicategory $\cat{A}$, for every triple of objects $a,b,c$ and morphisms
\[
\xymatrix@C+2pc{
a \ar[r]^-{\Phi} & b \ar[r]^-{\Psi} & c
}
\]
there is an assignment to $(\Psi, \Phi)$ of a composition $\Psi \circ \Phi$. A \emph{semantics of composition} for $\cat{A}$ is a mathematical construct providing some kind of inner structure for this ``assignment'' which is coherent as $a,b,c,\Phi,\Psi$ vary. The main examples of this kind of semantics are in computer science and mathematical logic.

For example, suppose that $\cat{A}$ is the category of sets and that we have functions
\[
\xymatrix@C+2pc{
\mathbb{N} \ar[r]^-{\Phi} & \mathbb{N} \ar[r]^-{\Psi} & \mathbb{N}
}
\]
where $\Phi$ and $\Psi$ are ``finitely described'' in the sense that they are computed by algorithms $X$ and $Y$, respectively. To be explicit, let us take $X,Y$ to be terms in the $\lambda$-calculus \cite{selinger}. If $[-]$ denotes assignment to an algorithm of the function it describes, then $\Phi = [X], \Psi = [Y]$ and $\Psi \circ \Phi = [Y \l X]$ where $Y \l X$ is the result of feeding the output of the algorithm $X$ as an input to the algorithm $Y$. In the logic literature this concatenation is known as a \emph{cut}.\footnote{We note that the notation $Y \l X$ for the cut is not standard, so don't blame the logicians for it.} To encounter the desired semantics we need the additional observation that the cut $Y \l X$ is not in normal form (whatever this means) but it may be reduced to normal form by a rewriting process on terms in the $\lambda$-calculus called $\beta$-reduction. This does not change the associated function: the normal form of $Y \l X$ also computes $\Psi \circ \Phi$.

A semantics of composition for the category of computable functions is then given by the process which begins with the pair $(Y,X)$ of finite descriptions of $\Psi,\Phi$, forms the cut $Y \l X$, and then computes a normal form giving a finite description of $\Psi \circ \Phi$.

\medskip

This seems very far from geometry, but we can informally recast a problem of algebraic geometry in a similar light. Suppose $A,B,C$ are smooth projective algebraic varieties and that we are given triangulated functors between derived categories of coherent sheaves
\[
\xymatrix{
\mathbf{D}^b(A) \ar[r]^-{\Phi} & \mathbf{D}^b(B) \ar[r]^-{\Psi} & \mathbf{D}^b(C)
}\,.
\]
Suppose that $\Phi,\Psi$ are finitely described, in the sense that they are both integral functors associated to kernels: $\Phi$ is convolution with a complex of coherent sheaves $X$ on $A \times B$, and $\Psi$ is convolution with a complex $Y$ on $B \times C$. If for example $A,B,C$ are the $\operatorname{Proj}$ of graded algebras, $X$ and $Y$ can be described by lists of matrices of homogeneous polynomials. An obvious question is: what is the finite description of the functor $\Psi \circ \Phi$?

It is easy to see that $\Psi \circ \Phi$ is convolution with the kernel $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$, which is a complex of quasi-coherent sheaves on $A \times C$ with coherent cohomology, but this is not described by a finite amount of data. Finding a finite description of $\Psi \circ \Phi$ is precisely the problem of determing the complex of coherent sheaves which is isomorphic, in $\mathbf{D}^b(A \times C)$, to $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$. We refer to such a complex of coherent sheaves as a \emph{finite model} of $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$.

Consider the case where $A = C = \operatorname{Spec}(\mathbb{C})$, so $X,Y$ are complexes of coherent sheaves on $B$ and $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X \cong \mathbb{R}\! \operatorname{Hom}_{\cat{O}_B}(Y^{\vee}, X)$ is a complex of infinite-dimensional vector spaces with finite-dimensional cohomology. An example of a finite model is an isomorphism in the derived category of all $\mathbb{C}$-vector spaces of this complex with its cohomology
\begin{equation}\label{eq:computing_hom_derived}
Y \otimes^{\mathbb{L}}_{\cat{O}_B} X \cong \bigoplus_{n \in \mathbb{Z}} \Ext^n(Y^{\vee},X)[-n]\,.
\end{equation}
One finite description of $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$, and transitively of $\Psi \circ \Phi$, is therefore a list of numbers: the dimensions of the vector spaces on the right hand side of \eqref{eq:computing_hom_derived}. Determining these numbers is difficult, to put it mildly: a fundamental problem in algebraic geometry is to understand how these numbers depend on the input data $X$ and $Y$.

By a (perhaps naive) analogy with computable functions, one might wonder if in the general case there exists an object $Y \l X$ in some triangulated category together with a reduction process that would help find a finite description for $\Psi \circ \Phi$. This is the question of whether or not there is a semantics of composition in the bicategory of smooth projective varieties and Fourier-Mukai kernels \cite{ct1007.2679}. Unfortunately, we do not know such a theory!

However, it turns out that there \emph{is} a satisfactory semantics of this kind when instead of smooth projective varieties we consider isolated hypersurface singularities $W,V,U$ and triangulated functors between homotopy categories of matrix factorisations \cite{yoshino98}
\begin{equation}\label{eq:pair_functors_hmf}
\xymatrix{
\hmf(W) \ar[r]^-{\Phi} & \hmf(V) \ar[r]^-{\Psi} & \hmf(U)
}\,.
\end{equation}
To explain further, we need to introduce the language of cut systems.

\medskip

A \emph{cut system} $\cat{A}$ over a $\mathbb{Q}$-algebra $k$ has a class of objects and for each pair $a,b$ of objects a $k$-linear supercategory $\cat{A}(a,b)$. Informally, one should think of this as a category of finite models. There is an operation on $\cat{A}$, the \emph{cut}, which assigns to $X \in \cat{A}(a,b)$ and $Y \in \cat{A}(b,c)$ a representation $Y \l X$ in $\cat{A}(a,c)$ of a Clifford algebra which depends on the intermediate object $b$. The object $Y \l X$ and the endomorphisms giving the Clifford action are required to be effectively computable, say by explicit formulas, from the input data $X,Y$. In the example of a cut system developed in this paper, Clifford algebras arise as endomorphism algebras of exterior algebras, which in turn arise as the underlying graded modules of Koszul complexes. Associated to the cut system $\cat{A}$ is a bicategory $\cat{A}^\bullet$ in which the composition is derived from the cut operation, and so is also effectively computable.

A \emph{cut model} of a bicategory $\cat{B}$ is a cut system $\cat{A}$ with the same objects as $\cat{B}$, together with an equivalence $I: \cat{B} \lto \cat{A}^\bullet$. There are fully faithful functors $I: \cat{B}(a,b) \lto \cat{A}(a,b)$ which we think of as assigning finite models to the $1$-morphisms of $\cat{B}$, and an isomorphism of Clifford representations for every composable pair of $1$-morphisms $X,Y$ in $\cat{B}$, where $S$ denotes the spinor representation:
\begin{equation}\label{eq:intro_cut_semantics}
I(Y) \l I(X) \cong S \otimes_k I( Y \circ X )\,.
\end{equation}
The cut model provides $\cat{B}$ with a semantics of composition: given finite models $I(X), I(Y)$ of $X,Y$ there is a process beginning with the cut $I(Y) \l I(X)$ which extracts the subobject $I(Y \circ X)$ using the Clifford action. The result $I( Y \circ X )$ of this computation is the desired finite model of the composition $Y \circ X$ in $\cat{B}$.
\medskip

The formalism is adapted to, and motivated by, an example: the bicategory of Landau-Ginzburg models $\LG$. Let us return to the diagram \eqref{eq:pair_functors_hmf} as our starting point. There is an analogue of integral functors in this setting, so that it makes sense to talk about $\Phi$ and $\Psi$ as being respectively given by convolution with kernels $X,Y$. If $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$ define isolated hypersurface singularities then $X$ is a finite rank matrix factorisation of $V - W$ over $k[x,z]$, and similarly for $Y$.

Again, the question is: what is the finite description of $\Psi \circ \Phi$? It is naturally given by convolution with a matrix factorisation $Y \otimes X$ which is not finitely generated: finding a finite description of $\Psi \circ \Phi$ therefore amounts to finding a finite model for $Y \otimes X$. To fit this into the formalism of cut systems, we use the  bicategory $\LG$ in which the objects are isolated hypersurface singularities\footnote{Roughly speaking. See Section \ref{section:superbicatLG}.} and $1$-morphisms $W \lto V$ are matrix factorisations of $V - W$. In this bicategory, the finite descriptions of the functors in \eqref{eq:pair_functors_hmf} give rise to a composable pair of $1$-morphisms
\begin{equation}\label{eq:cut_lg}
\xymatrix@C+2pc{
W \ar[r]^-{X} & V \ar[r]^-{Y} & U
}\,.
\end{equation}
whose composition in $\LG$ is the tensor product $Y \otimes X$.

The main results of this paper are the construction of a cut sytem $\cat{L}$ and cut model $I: \LG \lto \cat{L}^\bullet$. In the situation of \eqref{eq:cut_lg} $X$ and $Y$ are their own finite model (so $I(X) = X$ and $I(Y) = Y$) and a finite model of the composite $Y \otimes X$ in $\cat{B}$ may be computed from the cut $Y \l X$ in $\cat{L}$, which is an explicitly given finite rank matrix factorisation of $U - W$ together with a Clifford action described in terms of derivatives of the differentials of $X,Y$ and certain invariants called Atiyah classes.

One consequence is that $\LG$ is equivalent to the bicategory $\cat{L}^\bullet$, which is \emph{computable} in the sense that its operations may be embodied in software. To some extent this software already exists: a component of what we are here calling the cut system $\cat{L}$ (developed earlier in joint work with Dyckerhoff \cite{dm1102.2957}\footnote{For a more detailed discussion of the relation of this work with the present paper, see Remark \ref{remark:relation_to_toby_paper}.}) has already been implemented in the computer algebra package Singular in joint work with Carqueville \cite{khovhompaper}, and used to compute tables of Khovanov-Rozansky knot homologies. The code was also used in the discovery of the generalised orbifolding relations among ADE singularities by Carqueville, Ros Camacho and Runkel \cite{ade}.

\medskip
In conclusion, the purpose of this paper is to develop the theory of cut systems as a mathematical foundation for the application to be given in \cite{cutsystems2}. Let us briefly summarise the contents of that work: one can show that the superbicategory $\cat{L}^\bullet$ is monoidal, has adjoints and is pivotal. This makes it a natural target for models of Girard's linear logic, which is a generalisation of the $\lambda$-calculus in which the terms may be viewed as algorithms that have a refined syntax of resource usage compared to the $\lambda$-calculus. The model of linear logic to be given in \cite{cutsystems2} interprets algorithms $x,y$ as $1$-morphisms $[x],[y]$ in $\cat{L}^\bullet$.

This interpretation has two novelties: first of all, the target $\cat{L}^\bullet$ has a semantics of composition that may be compared to cut-elimination in linear logic (the analogue of $\beta$-reduction in the $\lambda$-calculus) as in Girard's geometry of interaction \cite{girard_towards}. This connection is what motivates the terminology of ``cut systems'' in the present paper. The second novelty is that, compared to the usual mathematical semantics of programming languages where algorithms are interpreted as functions between sets, our interpretation is bicategorical: in particular, equations $[x] \circ [y] \cong [y] \circ [x]$ or $[x]^2 \cong [x]$ on programs are represented by data that is part of the semantics.

%. For a precise definition see Section \ref{??}}. To such a $W$ we associate a category of algebraic objects called matrix factorisations. A matrix factorisation of $W(x)$ is a matrix of polynomials $D$ satisfying $D^2 = W \cdot I_n$, where $I_n$ is the identity matrix.

%For $W = x y^2 + y^3$ an example is
%\[
%D_1 = \begin{pmatrix} 0 & x - i y \\ x + iy & 0 \end{pmatrix} %, \qquad D_2 = \begin{pmatrix} 0 & y - x \\ (y - e^{2 \pi i /3} x)(y - e^{4 \pi i /3} x ) & 0 \end{pmatrix}
%\]
%A \emph{morphism} of matrix factorisations $\Phi: D_1 \lto D_2$ is a matrix of polynomials $\Phi$ satisfying the relation $\Phi D_1 = D_2 \Phi$. Together the matrix factorisations of $W$ and the morphisms between them form the category of matrix factorisations of $W$.

%In the second part of the paper we explain how the multiplicative fragment of linear logic can be interpreted in the bicategory of Landau-Ginzburg models, with formulas mapped to isolated hypersurface singularities and proofs mapped to matrix factorisations. The multiplicative fragment is not very expressive, so our focus in the present paper is not on embedding sophisticated programs into $\cat{LG}$. Rather, we explain how cut systems give a dynamic model of cut-elimination following Girard's geometry of interaction. The basic construction of a cut system involves homological perturbation, and by interpreting this as a fixed point construction we will show that the result of normalization can be expressed in a power series expansion similar to Girard's famous execution formula.

\medskip

The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory. In Section \ref{section:cut_systems} we define cut systems and the superbicategory associated to a cut system, then we construct the cut model of $\LG$ in Section \ref{section:lg_cut_system}.

\medskip

\emph{Acknowledgements.} Thanks to Nils Carqueville and Ingo Runkel for helpful comments on the draft. Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.

\section{Background}\label{section:background}

Throughout $k$ is a commutative $\mathbb{Q}$-algebra. By default categories and functors are $k$-linear.

\subsection{Supercategories}

A superbicategory has for every $1$-morphism $F$ an associated $1$-morphism $\Psi F$ with $\Psi^2 \cong 1$, and in this sense the categories of $1$-morphisms are $\mathbb{Z}_2$-graded. The bicategory of Landau-Ginzburg models is an example of a superbicategory. Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role in the definition of cut systems, superbicategories are the natural language. Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.

\begin{definition} A \emph{supercategory} is a category $\cat{C}$ together with a functor $\Psi: \cat{C} \lto \cat{C}$ and a natural isomorphism $\xi: \Psi^2 \lto 1_{\cat{C}}$ satisfying the condition
\[
\xi * 1_{\Psi} = 1_{\Psi} * \xi
\]
as natural transformations $\Psi^3 \lto \Psi$. A \emph{superfunctor} $(F, \gamma)$ from a supercategory $(\cat{C}, \Psi_{\cat{C}})$ to a supercategory $(\cat{D}, \Psi_{\cat{D}})$ is a functor $F: \cat{C} \lto \cat{D}$ together with a natural isomorphism $\gamma: F \Psi_{\cat{C}} \lto \Psi_{\cat{D}} F$ satisfying
\[
1_F * \xi = (\xi * 1_F ) ( 1_{\Psi} * \gamma ) ( \gamma * 1_{\Psi} )\,.
\]
A \emph{supernatural transformation} $\varphi: F \lto G$ between superfunctors $(F,\gamma_F), (G,\gamma_G)$ is a natural transformation making the following diagram commute:
\[
\xymatrix{
F \Psi \ar[r]^-{\varphi \Psi}\ar[d]_-{\gamma_F} & G \Psi \ar[d]^-{\gamma_G}\\
\Psi F \ar[r]_-{\Psi \varphi} & \Psi G
}\,.
\] 
\end{definition}

\begin{example}\label{example:Aassup} If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra there is a supercategory $\cat{A}$ with set of objects $|\cat{A}| = \mathbb{Z}_2$ and morphisms $\cat{A}(0,0) = \cat{A}(1,1) = A_0, \cat{A}(0,1) = \cat{A}(1,0) = A_1$ with the obvious composition and addition rules. The functor $\Psi$ is defined on objects by $\Psi(i) = i+1$ and on morphisms by the identity, while $\xi = 1$.
\end{example}

Let $\cat{C}$ be a supercategory. For objects $X,Y \in \cat{C}$ we define the $\mathbb{Z}_2$-graded $k$-module
\[
\cat{C}^*(X,Y) = \prod_{i \in \mathbb{Z}_2} \cat{C}(X, \Psi^i Y)\,.
\]
There is for any triple $X,Y,Z$ of objects a morphism of graded modules
\[
\cat{C}^*(Y,Z) \otimes_k \cat{C}^*(X, Y) \lto \cat{C}^*(X,Z)
\]
given for instance by $\varphi \otimes \psi \mapsto \xi \Psi( \varphi ) \psi$ when $\varphi, \psi$ are both of degree one. This makes $\cat{C}$ into a category enriched over the monoidal category of $\mathbb{Z}_2$-graded $k$-modules.

There are isomorphisms of graded modules $\cat{C}^*(X, \Psi Y) \cong \Psi \cat{C}^*(X, Y) \cong \cat{C}^*(\Psi X, Y)$ where $\Psi V = V [1]$ denotes the grading shift on a $\mathbb{Z}_2$-graded $k$-module. For $\mathbb{Z}_2$-graded $k$-modules $V,W$ we write $\Hom^0_k(V, W)$ for the module of degree zero maps and $\Hom_k^*(V, W)$ for the $\mathbb{Z}_2$-graded module of homogeneous maps. If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $A^{\operatorname{op}}$ denotes the same underlying graded module with multiplication $f * g = (-1)^{|f||g|} gf$.

\begin{definition} Let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra and $\cat{C}$ a supercategory. A \emph{left $A$-module in $\cat{C}$} is an object $X \in \cat{C}$ together with a morphism of $\mathbb{Z}_2$-graded algebras $A \lto \cat{C}^*(X,X)$. A \emph{morphism} of left $A$-modules is a morphism in $\cat{C}$ which commutes with the $A$-action in the obvious sense. The category of left $A$-modules in $\cat{C}$ is denoted $\cat{C}_A$. Right modules are defined similarly, using $A^{\operatorname{op}}$.
\end{definition}

\begin{remark}\label{remark:supercat_idempcomp} Viewing $A$ as a supercategory $\cat{A}$ as in Example \ref{example:Aassup}, there is an equivalence between the category of $A$-modules in $\cat{C}$ and the category of superfunctors $\cat{A} \lto \cat{C}$ and supernatural transformations.
\end{remark}

\begin{remark}\label{remark:idempotent_completion} The \emph{idempotent completion} $\cat{C}^\omega$ of a category $\cat{C}$ has as objects pairs $(X,e)$ consisting of an object $X \in \cat{C}$ and an idempotent endomorphism $e: X \lto X$. In $\cat{C}^\omega$ a morphism $\phi: (X,e) \lto (Y,e)$ is a morphism $\phi: X \lto Y$ satisfying $\phi e = \phi$ and $e \phi = \phi$. The identity on $(X,e)$ is $e$. There is a fully faithful functor $\iota: \cat{C} \lto \cat{C}^{\omega}, \iota(X) = (X,1_X)$ which is an equivalence if $\cat{C}$ is idempotent complete (i.e. all idempotents split in $\cat{C}$).

If $\cat{C}$ is a supercategory then there is a functor $\Psi^\omega: \cat{C}^\omega \lto \cat{C}^\omega$ defined on objects by $\Psi(X,e) = (\Psi X, \Psi e)$ and a natural isomorphism $\xi: \Psi^\omega \circ \Psi^\omega \lto 1_{\cat{C}^\omega}$ defined by $\xi_{(X,e)} = e \xi_X$. The tuple $(\cat{C}^\omega, \Psi^\omega, \xi^\omega)$ is a supercategory.
\end{remark}

For background on bicategories see \cite{bor94} and the references in \cite{lgdual}. We follow the notation of \cite{lgdual}, so that lower case letters $a,b, \ldots$ denote objects of a bicategory, while upper case letters $X,Y, \ldots$ and greek letters $\alpha, \beta, \ldots$ respectively denote $1$-morphisms and $2$-morphisms. Units are denoted $\Delta$, associators are $\alpha$, and unitors are $\lambda, \rho$. The composition of $Y,X$ is denoted $YX$ or $Y \circ X$.

\begin{definition} A \emph{superbicategory} is a bicategory $\cat{B}$ together with the data:
\begin{itemize}
\item For each object $a$ a $1$-morphism $\Psi_a: a \lto a$ and a $2$-isomorphism $\xi_a: \Psi^2_a \lto \Delta_a$.
\item For each $1$-morphism $X: a \lto b$ a natural $2$-isomorphism $\gamma_X: X \Psi_a \lto \Psi_b X$.
\end{itemize}
This data is required to satisfy the following axioms:
\begin{itemize}
\item For each composable pair $X,Y$ of $1$-morphisms the diagram
\[
\xymatrix@C+2pc@R+1pc{
(YX) \Psi \ar[rrr]^-{\gamma_{YX}} \ar[d]_-{\alpha} & & & \Psi ( YX )\\
Y ( X \Psi ) \ar[r]_-{1_Y * \gamma_X} & Y( \Psi X ) \ar[r]_-{\alpha^{-1}} & ( Y \Psi ) X \ar[r]_-{\gamma_Y * 1_X} & (\Psi Y ) X \ar[u]_-{\alpha}
}
\]
commutes.
\item For every object $a$, $\xi_a * 1_\Psi = 1_\Psi * \xi_a$.
\item For every $1$-morphism $X : a \lto b$, $1_X * \xi_a = ( \xi_b * 1_X ) ( 1_\Psi * \gamma_X ) (\gamma_X * 1_\Psi )$.
\end{itemize}
\end{definition}

\begin{example} Supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
\end{example}

A superbicategory can be constructed out of a bicategory $\cat{B}$ in which the categories $\cat{B}(a,b)$ are all equipped with the structure of supercategories; see Appendix \ref{section:constructing_superbicategories}.

\begin{example}\label{example:bicategory_m} There is a bicategory of $\mathbb{Z}_2$-graded $k$-algebras where $1$-morphisms are $\mathbb{Z}_2$-graded bimodules and $2$-morphisms are degree zero bimodule maps. Given a $B$-$A$-module $M$ the shift $M[1]$ has the grading $M[1]_i = M_{i+1}$ and the left and right action given by
\[
b \cdot m = (-1)^{|b|} bm, \qquad m \cdot a = (-1)^{|a|} m a\,.
\]
This is a functor $\Psi = (-)[1]$ on the category of $B$-$A$-bimodules and with $\xi = 1$ this defines the structure of a supercategory on this category of bimodules. The usual isomorphisms of bimodules $\tau$
\begin{align}
N[1] \otimes M &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto n \otimes m \label{eq:shift_iso_a}\\
N \otimes M[1] &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto (-1)^{|n|} n \otimes m\label{eq:shift_iso_b}
\end{align}
satisfy the conditions in Appendix \ref{section:constructing_superbicategories} and therefore give the bicategory of $\mathbb{Z}_2$-graded algebras and bimodules the structure of a superbicategory.
\end{example}

\begin{definition} Given two superbicategories $\cat{B}, \cat{C}$ a \emph{lax superfunctor} $\Phi: \cat{B} \lto \cat{C}$ is a lax functor together with, for each object $a$ in $\cat{B}$, a $2$-morphism
\[
\kappa_a: \Psi_{\Phi a} \lto \Phi( \Psi_a )
\]
satisfying two coherence conditions:
\begin{itemize}
\item[(a)] for all $a$, commutativity of
\[
\xymatrix@C+2pc{
\Psi_{\Phi a} \Psi_{\Phi a} \ar[dd]_-{\xi}\ar[r]^-{\kappa * \kappa} & \Phi( \Psi_a ) \Phi( \Psi_a ) \ar[d]\\
& \Phi( \Psi_a \Psi_a ) \ar[d]^-{\Phi(\xi)}\\
\Delta_{\Phi a} \ar[r] & \Phi( \Delta_a )
}
\]
\item[(b)] for each $1$-morphism $X: a \lto b$ in $\cat{B}$, commutativity of
\[
\xymatrix@C+2pc{
\Phi(X) \Psi_{\Phi a} \ar[d]_-{\gamma} \ar[r]^-{1 * \kappa} & \Phi(X) \Phi(\Psi_a) \ar[r] & \Phi( X \Psi_a ) \ar[d]^-{\Phi(\gamma)}\\
\Psi_{\Phi b} \Phi(X) \ar[r]_-{\kappa * 1} & \Phi(\Psi_b) \Phi(X) \ar[r] & \Phi( \Psi_b X)
}
\]
\end{itemize}
A \emph{strong superfunctor} is a lax superfunctor with $\kappa_a$ an isomorphism for every object $a$.
\end{definition}

\subsection{The superbicategory of Landau-Ginzburg models}\label{section:superbicatLG}

A polynomial $W \in k[x_1,\ldots,x_n]$ is a \emph{potential} if it satisfies the three conditions set out in \cite[Section 2.2]{lgdual}, the two most important being that the partial derivatives $\partial_{x_1} W, \ldots, \partial_{x_n} W$ form a quasi-regular sequence in $k[x]$ and that the quotient $J_W = k[x]/(\partial_{x_1} W, \ldots, \partial_{x_n} W)$ is a finitely generated free $k$-module. Typical examples are the ADE singularities \cite[I \S 2.4]{greuel} of which the simplest are the $A_N$-singularities $W_{A_N} = x_1^{N+1} + x_2^2 + \cdots + x_n^2$ .

A \emph{matrix factorisation} of $W$ over $k[x]$ is a $\mathbb{Z}_2$-graded free $k[x]$-module $X = X^0 \oplus X^1$ together with an odd operator (the differential) $d_X: X \lto X$ satisfying $d_X^2 = W \cdot 1_X$. A matrix factorisation $(X,d_X)$ is \emph{finite rank} if the underlying free module is finitely generated. In this case we may, after choosing a homogeneous basis, write
\[
d_X = \begin{pmatrix} 0 & d_X^1 \\ d_X^0 & 0 \end{pmatrix}
\]
for matrices of polynomials $d_X^0, d_X^1$. Morphisms of matrix factorisations are degree zero $k[x]$-linear maps which commute with the differentials. There is a homotopy relation on morphisms, and the \emph{homotopy category} $\HMF(k[x],W)$ of matrix factorisations has as objects matrix factorisations and as morphisms the equivalence classes of morphisms of matrix factorisations up to homotopy. By $\hmf(k[x],W)$ we denote the full subcategory of finite rank matrix factorisations. For background we refer to \cite{yoshino98}.

By $\hmf(k[x],W)^{\oplus}$ we denote the full subcategory of $\HMF(k[x],W)$ consisting of matrix factorisations which are direct summands (in the homotopy category) of finite rank matrix factorisations. Since $\HMF(k[x],W)$ is idempotent complete, there is an equivalence (see Remark \ref{remark:idempotent_completion} for the notation)
\[
\hmf(k[x],W)^\omega \lto \hmf(k[x],W)^{\oplus}
\]
sending a pair $(X,e)$ to an infinite rank matrix factorisation splitting the idempotent $e$.

If $(X,d_X)$ is a matrix factorisation then so is $(X[1], -d_X)$, and this defines a functor $\Psi = (-)[1]$ on the homotopy category of matrix factorisations. Together with the identity $\xi: \Psi^2 \lto 1$ this makes $\HMF(k[x],W)$ and $\hmf(k[x],W)$ into supercategories.

The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$. Given potentials $W \in k[x]$ and $V \in k[z]$ the supercategory $\cat{LG}(W,V)$ is
\[
\cat{LG}(W,V) = \hmf(k[x,z], V - W)^{\oplus}\,.
\]
Given a third potential $U \in k[y]$ the composition law is a functor
\[
\LG(W,V) \otimes_k \LG(V, U) \lto \LG(W, U)
\]
which sends a pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ to the tensor product
\begin{equation}\label{eq:tensor_comp}
Y \otimes X = ( Y \otimes_{k[z]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
\end{equation}
This statement requires some care: $k[x,y,z]$ is an infinite rank free module over $k[x,z]$ and so $Y \otimes X$ is an infinite rank matrix factorisation of $U - W$ over $k[x,z]$. However one can prove that $Y \otimes X$ is a direct summand of a finite rank matrix factorisation \cite{dm1102.2957} and therefore a valid object in $\LG(W,U)$.

Let $W \in k[x_1,\ldots,x_n]$ be a potential and $W(x')$ the same polynomial but in a second set of variables $x_1',\ldots,x_n'$. Using formal symbols $\Theta_i$ of odd degree, we define the $k[x,x']$-module
\[
\Delta_W = \bigwedge \big( \bigoplus_{i=1}^n k[x,x'] \cdot \Theta_i \big)\,.
\]
Equipped with a certain differential (see \cite{lgdual}) this is a matrix factorisation of $W(x) - W(x')$ and defines the unit in $\cat{LG}(W,W)$ for composition of $1$-morphisms. For the associator and unitor maps $\rho: X \otimes \Delta_W \lto X$ and $\lambda: \Delta_V \otimes X \lto X$ we also refer to \emph{ibid.}

\begin{lemma} $\LG$ is a superbicategory.
\end{lemma}
\begin{proof}
The categories $\LG(W,V)$ are all naturally supercategories, and the same isomorphisms as in \eqref{eq:shift_iso_a}, \eqref{eq:shift_iso_b} define the necessary natural isomorphisms $\tau$ to equip $\LG$ with the structure of a superbicategory with $\Psi_W = \Delta_W[1]$, using Appendix \ref{section:constructing_superbicategories}.
\end{proof}

The superbicategory structure on $\LG$ is used implicitly in \cite[Section 7]{lgdual}.

\subsection{Clifford algebras}\label{section:clifford_algs}

In a cut system the composition rule produces objects which are representations of Clifford algebras. We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}. For $n \ge 0$ the Clifford algebra $A_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $a_1,\ldots,a_n$ and $a_1^\dagger, \ldots, a_n^\dagger$ subject to the following relations
\[
[a_i, a_j] = 0, \qquad [a_i^\dagger, a_j^\dagger] = 0, \qquad [a_i, a_j^\dagger] = \delta_{ij}\,.
\]
for all $1 \le i, j \le n$. In this paper all our commutators are graded, $[a,b] = ab - (-1)^{|a||b|} ba$. We set $A_0 = k$. The algebras $A_n$ are Morita trivial in the sense that they are isomorphic to the endomorphism algebras of finite rank free $\mathbb{Z}_2$-graded $k$-modules.

Indeed, if $F_n = k \theta_1 \oplus \cdots \oplus k \theta_n$ with $|\theta_i| = 1$ for all $i$, then

\begin{lemma} With $S_n = \bigwedge F_n$ the map $A_n \lto \End_k(S_n)$ defined by
\[
a_i \mapsto \theta_i \wedge (-), \qquad a_i^\dagger \mapsto \theta_i^*\, \lrcorner\, (-)
\]
is an isomorphism of $\mathbb{Z}_2$-graded $k$-algebras, where $\lrcorner$ denotes contraction.
\end{lemma}

In particular this means that every $\mathbb{Z}_2$-graded $A_n$-module is isomorphic to $S_n \otimes_k V$ for some $\mathbb{Z}_2$-graded $k$-module $V$. From the isomorphism of $k$-modules
\[
S_m \otimes_k S_n = \bigwedge F_m \otimes_k \bigwedge F_n \cong \bigwedge F_{m+n} = S_{m+n}
\]
we deduce an isomorphism of algebras
\begin{equation}\label{eq:algebra_A_additive}
A_m \otimes_k A_n \cong A_{m+n}\,.
\end{equation}
Given $m, n \ge 0$ we introduce notation for the $A_m$-$A_n$-bimodule
\begin{equation}
S_{m,n} = S_m \otimes_k S_n^*
\end{equation}
where $S_n^* = \Hom_k(S_n, k)$. There is an isomorphism of $A_l$-$A_n$-bimodules
\begin{equation}\label{eq:isosbimodule}
S_{l,m} \otimes_{A_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{A_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
\end{equation}
In the case $k = \mathbb{C}$, $S_n$ is often referred to as the \emph{spinor representation} \cite[p.14]{friedrich}.

\begin{remark} Recall that given a finite rank free $k$-module $V$ and a symmetric bilinear form $B: V \otimes_k V \lto k$ the associated Clifford algebra $\operatorname{Cl}(V, B)$ is the associative $k$-algebra generated by the elements of $V$ subject to the relations
\[
vw + wv = B(v,w) \cdot 1\,.
\]
This is a $\mathbb{Z}_2$-graded $k$-algebra when we assign $|v| = 1$ for all $v \in V$ and $|1| = 0$. If we take $V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then $A_n$ is the Clifford algebra of the pair $(V,B)$.
\end{remark}

\subsection{The Clifford thickening}

Let $\cat{C}$ be a small idempotent complete supercategory. We construct a new supercategory $\cat{C}^\bullet$ called the \emph{Clifford thickening} in which the objects are pairs $(X,n)$ of an integer $n \ge 0$ and a left $A_n$-module $X$ in $\cat{C}$.

We will need the operation of tensoring objects of $\cat{C}$ with $k$-modules. This is standard material, which is recalled in Appendix \ref{section:tensorproduct_supcat}. The upshot is that if $A$ is a Morita trivial $\mathbb{Z}_2$-graded $k$-algebra and if $X \in \cat{C}$ is a left $A$-module, while $V$ is a $\mathbb{Z}_2$-graded right $A$-module (in the usual sense, i.e. in the category of $k$-modules) then there is an object $V \otimes_A X$ in $\cat{C}$ which is functorial in both $V$ and $X$. Morever if $V$ is a $B$-$A$-bimodule then $V \otimes_A X$ is naturally a left $B$-module, and so on. If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{C}_A$ denotes the supercategory of $A$-modules in $\cat{C}$ with $A$-linear maps.

Similarly to Example \ref{example:bicategory_m} there is a superbicategory $\cat{M}$ of Morita trivial $\mathbb{Z}_2$-graded $k$-algebras: $1$-morphisms are $\mathbb{Z}_2$-graded bimodules which are finitely generated and projective over $k$ and $2$-morphisms are degree zero bimodule maps.

\begin{proposition} The assignment of the supercategory $\cat{C}_A$ to an algebra $A$ and of the superfunctor $\Phi_V = V \otimes_A (-)$ to a $B$-$A$-bimodule $V$ determines a strong superfunctor
\[
\Phi^{\cat{C}}: \cat{M} \lto \Cat^{\operatorname{sup}}_k
\]
to the superbicategory of small supercategories and superfunctors.
\end{proposition}
\begin{proof}
The isomorphism $\Phi_W \circ \Phi_V \cong \Phi_{W \otimes V}$ is given by Lemma \ref{lemma:assoctensor}, and apart from that the only checking that needs to be done are straightforward coherence diagrams.
\end{proof}

Next we construct a strong functor into $\cat{M}$ which picks out the Clifford algebras.

\begin{definition}
Let $\mathbb{N}$ denote the category of integers $n \ge 0$ with a unique morphism $\phi_{m,n}: n \lto m$ for each pair $m,n$. %This category is monoidal with $m \otimes n = m + n$.
\end{definition}

We view $\mathbb{N}$ as a bicategory with only identity $2$-morphisms.

\begin{lemma} There is a strong functor $\mathbb{N} \lto \cat{M}$ defined by
\begin{gather*}
n \mapsto A_n = \End_k( S_n ),\\
\phi_{m,n} \mapsto S_{m,n} = S_m \otimes_k S_n^*\,.
\end{gather*}
\end{lemma}

The composite of these strong functors is a strong functor
\begin{equation}\label{eq:strongfunctorgroth}
\xymatrix@C+1pc{
\mathbb{N} \ar[r] & \cat{M} \ar[r]^-{\Phi^{\cat{C}}} & \Cat^{\operatorname{sup}}_k
}
\end{equation}
sending $n$ to the category of left $A_n$-modules in $\cat{C}$ and $\phi_{m,n}$ to the functor $S_{m,n} \otimes_{A_n} -$. There is a close connection between strong functors into the bicategory of small categories, and what are called cofibered categories, given by the Grothendieck construction \cite{vistoli}.

\begin{definition} The \emph{Clifford thickening} $\cat{C}^\bullet$ of the supercategory $\cat{C}$ is the category which results from the Grothendieck construction applied to the strong functor \eqref{eq:strongfunctorgroth}.
\end{definition}

More concretely $\cat{C}^\bullet$ is the category with objects all pairs $(X,n)$ of an integer $n \ge 0$ and an object $X \in \cat{C}$ with a left $A_n$-action. A morphism $\alpha: (X,n) \lto (Y,m)$ is a morphism of $A_m$-modules $\alpha: S_{m,n} \otimes_{A_n} X \lto Y$. Composition of a pair of morphisms
\begin{equation}\label{eq:comp_chain0}
\xymatrix{
(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
}
\end{equation}
is given by the morphism of $A_l$-modules
\begin{equation}\label{eq:comp_chain1}
\xymatrix@C+1pc{
S_{l, n} \otimes_{A_n} X \ar[r]^-{\cong} & (S_{l,m} \otimes_{A_m} S_{m,n}) \otimes_{A_n} X \ar[d]^-{\cong}\\
& S_{l,m} \otimes_{A_m} ( S_{m,n} \otimes_{A_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{A_m} Y \ar[r]^-{\beta} & Z\,.
}
\end{equation}
There is a canonical functor $p: \cat{C}^\bullet \lto \mathbb{N}$ defined by $p(X,n) = n$, which defines a cofibered category over $\mathbb{N}$ by the definition of the Grothendieck construction.

\begin{lemma} $\cat{C}^\bullet$ is a supercategory and the functor $\iota: \cat{C} \lto \cat{C}^\bullet$ defined by $\iota(X) = (X,0)$ is an equivalence of supercategories.
\end{lemma}
\begin{proof}
The supercategory structure is given by the functor $\Psi: \cat{C}^\bullet \lto \cat{C}^\bullet$ where $\Psi(X,n) = ( \Psi X, n )$ and $\Psi X$ has the $A_n$-action given by Definition \ref{defn:psimodule}.

The functor $\iota$ is fully faithful. To see that it is essentially surjective, let $(X,n) \in \cat{C}^\bullet$ be given. We show that $(X,n)$ is isomorphic to $(\widetilde{X},0)$ where $\widetilde{X} = S_n^* \otimes_{A_n} X$. This follows from the fact that the isomorphism
\[
S_n \otimes_k \widetilde{X} = S_n \otimes_k S_n^* \otimes_{A_n} X \cong X
\]
defines an isomorphism $(\widetilde{X}, 0) \lto (X,n)$ in $\cat{C}^\bullet$.
\end{proof}

\begin{definition}\label{defn:idempotent_e} For $n \ge 0$ let $e_n \in A_n$ denote the element
\[
e_n = a_1^\dagger \cdots a_n^\dagger a_n \cdots a_1\,.
\]
This is the idempotent corresponding to the summand $k \cdot 1$ of $S_n$.
\end{definition}

\begin{remark}\label{remark:tensor_and_idempotent} It may seem odd to labour to construct a category $\cat{C}^\bullet$ equivalent to $\cat{C}$. The point is that while $(X,n)$ and $(\widetilde{X}, 0)$ are isomorphic in $\cat{C}^\bullet$, they still represent quantitatively different states of knowledge. If $\widetilde{X}$ is known then $X$ may be easily constructed by taking direct sums, but if $X$ is known then forming the tensor product $\widetilde{X}$ is equivalent to splitting the idempotent $e_n: X \lto X$ and this requires work.
% If $X$ is an $A_n$-module in $\cat{C}$, then the defining property of $\widetilde{X} = S_n^* \otimes_{A_n} X$ is that there is a morphism $\eta: X \lto \widetilde{X}$ satisfying $\eta \circ a_i = 0$ for all $1 \le i \le n$ and which is universal with this property. That is, given any morphism $\delta:X  \lto Y$ with this property there is a unique morphism $\kappa: \widetilde{X} \lto Y$ such that $\kappa \circ \eta = \delta$. A morphism $\delta: X \lto Y$ satisfies $\delta \circ a_i = 0$ for $1 \le i \le n$ if and only if $\delta \circ ( 1 - e_n ) = 0$.

For each $n$ the fiber of the functor $p: \cat{C}^\bullet \lto \mathbb{N}$ over $n$ is $\cat{C}_{A_n}$. We may depict the cofibered category $p$ as follows:
\begin{equation}\label{eq:cofibered_diagram}
\xymatrix@C+3pc@R+1pc{
\cat{C} \ar@{.}[d] \ar@<1ex>[rrr]^-{E} & & & \cat{C}_{A_n} \ar@{.}[d] \ar@<1ex>[lll]^-{F}\\
0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & n \ar@{.>}@<0.8ex>[l]
}\,.
\end{equation}
The transport between the fibers is given by the equivalences
\[
E(-) = S_{n} \otimes_k (-), \qquad F(-) = S^*_{n} \otimes_{A_n} (-)\,.
\]
While these functors are adjoint, and therefore uniquely determine one another, we have explained that there is a fundamental asymmetry between them from the point of view of computation: knowledge of an object of $\cat{C}^\bullet$ over $n$ represents a state of higher uncertainty than knowledge of an object over $m < n$, given that in the end both objects ``only'' contain the information of the corresponding object $\widetilde{X}$ over zero, but more work is necessary to extract this information from an object of $\cat{C}_{A_n}$ than from an object of $\cat{C}_{A_m}$.
\end{remark}

\begin{remark}\label{remark:tensor_in_steps} Given $(X,n) \in \cat{C}^\bullet$, one way to compute the tensor product
\[
S_{n+1,n} \otimes_{A_n} X = (S_{n+1} \otimes_k S_n^*) \otimes_{A_n} X \cong S_{n+1} \otimes_k ( S_n^* \otimes_{A_n} X )
\]
is to compute $S_n^* \otimes_{A_n} X$ and then take direct sums. Alternatively,
\begin{align*}
S_{n+1,n} \otimes_{A_n} X &= S_{n+1} \otimes_k S_n^* \otimes_{A_n} X\\
&\cong S_1 \otimes_k S_n \otimes_k S_n^* \otimes_{A_n} X \\
&\cong S_1 \otimes_k A_n \otimes_{A_n} X \\
&\cong S_1 \otimes_k X\,.
\end{align*}
That is, if we equip $S_1 \otimes_k X = X \oplus \Psi X$ with an $A_{n+1} \cong A_1 \otimes A_n$ action by making $A_n$ act on $X$ and $A_1$ act on $S_1$, this computes the tensor product. In a similar way, $S_{n-1,n} \otimes_{A_n} X$ is computed by splitting the idempotent $a_1^\dagger a_1$ on $X$, so that the functor $F$ of \eqref{eq:cofibered_diagram} may be computed in $n$ steps by splitting $a_1^\dagger a_1$, then $a_2^\dagger a_2$, and so on.
\end{remark}
%TODO note: $S_{m,n} \otimes_{A_n}$ is an equivalence so all fibers are isomorphic to $\cat{C}$.

\begin{remark} An alternative description of morphisms in $\cat{C}^\bullet$ follows from Lemma \ref{lemma:morphisms_two_forms}. This result tells us that given an $A_n$-module $X$ and $A_m$-module $Y$ in $\cat{C}$ there is a bijection between morphisms of $A_m$-modules $\alpha: S_{m,n} \otimes_{A_n} X \lto Y$ and morphisms
\[
\alpha_0: X \lto Y \text{ satisfying } \alpha_0 \circ a_i = 0 \text{ for } 1 \le i \le n \text{ and } a_i^\dagger \circ \alpha_0 = 0 \text{ for } 1 \le i \le m\,.
\]
The bijection is defined by sending $\alpha$ to the composite ($\iota$ is defined by $\iota(1) = 1 \otimes 1^*$)
\[
\xymatrix@C+2pc{
X \cong A_n \otimes_{A_n} X \ar[r]^-{\iota \otimes 1} & S_{m,n} \otimes_{A_n} X \ar[r]^-{\alpha} & Y
}\,
\]
Given a chain of composable morphisms as in \eqref{eq:comp_chain0} there are corresponding morphisms $\alpha_0: X \lto Y$ and $\beta_0: Y \lto Z$ and it can be checked that the morphism corresponding under the bijection of Lemma \ref{lemma:morphisms_two_forms} to the composite $\beta \circ \alpha$ given in \eqref{eq:comp_chain1} is
\[
(\beta \circ \alpha)_0 = \beta_0 \circ \alpha_0\,.
\]
\end{remark}

\section{Cut systems}\label{section:cut_systems}

We begin with the definition of cut functors.

\begin{definition} Given supercategories $\cat{C}_1,\cat{C}_2,\cat{C}_3$ a \emph{superfunctor} $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3$ is a functor together with natural isomorphisms
\begin{align*}
\tau &: T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T,\\
\tau &: T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
\end{align*}
making the following diagrams commute:
\begin{equation}\label{eq:psicomp1}
\xymatrix@R+1pc@C+1pc{
T( 1 \otimes \Psi^2 ) \ar[r]^-{\tau}\ar[d]_-{T(1 \otimes \xi)} & \Psi T( 1 \otimes \Psi ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
T \ar[rr]_-{1_T} & & T
}
\end{equation}
\begin{equation}\label{eq:psicomp2}
\xymatrix@R+1pc@C+1pc{
T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\psi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
T \ar[rr]_-{1_T} & & T
}
\end{equation}
\begin{equation}\label{eq:psicomp3}
\xymatrix@R+1pc@C+1pc{
T( \Psi \otimes \Psi ) \ar[r]^-{\tau}\ar[d]_-{-\tau} & \Psi T( 1 \otimes \Psi ) \ar[d]^-{\tau}\\
\Psi T( \Psi \otimes 1 ) \ar[r]_-{\tau} & \Psi^2 T
}
\end{equation}

\end{definition}

\begin{definition}\label{defn:cutfunctor1} A \emph{cut functor of degree $t$} on a triple $\cat{C}_1, \cat{C}_2,\cat{C}_3$ of idempotent complete small supercategories is a superfunctor $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3^\bullet$ such that
\[
\xymatrix{
\cat{C}_1 \times \cat{C}_2 \ar[r]^-{T} & \cat{C}_3^\bullet \ar[r]^-{p} & \mathbb{N}
}
\]
sends every object to the integer $t \in \mathbb{N}$.
\end{definition}

With the above notation:

\begin{proposition}\label{prop:extend_cut_functor} Given a cut functor $T$ of degree $t$ on $\cat{C}_1, \cat{C}_2,\cat{C}_3$ there is a canonical superfunctor $\widetilde{T}: \cat{C}_1^\bullet \otimes_k \cat{C}_2^\bullet \lto \cat{C}_3^\bullet$ with the property that the diagram
\[
\xymatrix{
\cat{C}_1 \times \cat{C}_2 \ar[dr]_-{\iota \times \iota} \ar[rr]^-{T} & & \cat{C}_3^\bullet\\
& \cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[ur]_-{\widetilde{T}}
}
\]
commutes, and for every pair of objects $X \in \cat{C}_1^\bullet$ and $Y \in \cat{C}_2^\bullet$
\[
p \widetilde{T}( X, Y ) = p( X ) + p( Y ) + t\,.
\]
We refer to $\widetilde{T}$ as the \emph{extension} of $T$.
%and
%\[
%\xymatrix@C+2pc{
%\cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[d]_-{p \times p}\ar[rr]^-{\widetilde{T}} & & \cat{C}_3^\bullet \ar[dd]^-{p}\\
%\mathbb{N} \times \mathbb{N} \ar[d]_-{\cong}\\
%\mathbb{N} \times \{ * \} \times \mathbb{N} \ar[r]_-{1 \times t \times 1} & \mathbb{N} \times \mathbb{N} \times \mathbb{N} \ar[r]_-{\otimes} & \mathbb{N}
%}
%\]
%commute. 
\end{proposition}
\begin{proof}
The proof is given in Appendix \ref{app:proof_cut_extension}.
\end{proof}

We will use \emph{effectively computable} as a synonym for the precise notion of a \emph{computable} function \cite{enderton}, since ``computable'' often has a more colloquial meaning in our context.

% This is the definition from cutsys10
\begin{definition} A \emph{cut system} $\cat{A}$ is determined by the following data:
\begin{itemize}
\item A class $|\cat{A}|$ of objects and for each object $a$ an integer $\pi(a) \ge 0$.
\item For each pair $a,b$ of objects a small idempotent complete supercategory $\cat{A}(a,b)$. 
\item For each triple $a,b,c$ of objects a cut functor of degree $\pi(b)$
\[
T: \cat{A}(a,b) \otimes_k \cat{A}(b,c) \lto \cat{A}(a,c)^{\bullet}\,.
\]
The image of a pair $X \otimes Y$ under the canonical extension
\[
\widetilde{T}: \cat{A}(a,b)^\bullet \otimes_k \cat{A}(b,c)^\bullet \lto \cat{A}(a,c)^\bullet
\]
is denoted $Y \l X$ and is called the \emph{cut of $Y$ and $X$ along $b$}.
\item For each object $a$, an object $\Delta_a \in \cat{A}(a,a)$.
\item For objects $a,b,c,d$ a natural isomorphism $\alpha$ as shown below:
\[
\xymatrix@C+2pc{
\cat{A}(a,b) \times \cat{A}(b,c) \times \cat{A}(c,d) \ar[d]_-{T \times 1} \ar[r]^-{1 \times T} & \cat{A}(a,b) \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\alpha}\\
\cat{A}(a,c)^\bullet \times \cat{A}(c,d) \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
}
\]
That is, for $X \in \cat{A}(a,b), Y \in \cat{A}(b,c), Z \in \cat{A}(c,d)$ an isomorphism
\[
\alpha_{Z,Y,X}: ( Z \l Y ) \l X \lto Z \l ( Y \l X )
\]
of $A_{\pi(b)} \otimes_k A_{\pi(c)}$-modules in $\cat{A}(a,d)$, natural in all three variables.
\item For objects $a,b$ natural isomorphisms $\mu, \eta$ as shown below:
\[
\xymatrix@C+2pc{
1 \times \cat{A}(a,b) \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b) \ar@{=>}@<4ex>[l]_-{\eta} \ar@{=>}@<-4ex>[r]^-{\mu} \ar[d]^-{\iota} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b) \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
\cat{A}(a,a) \times \cat{A}(a,b) \ar[r]_-{T} & \cat{A}(A,B)^\bullet & \cat{A}(a,b) \times \cat{A}(b,b) \ar[l]^-{T}
}
\]
where $1$ is the category with one object and one morphism and $\iota_{\Delta}$ is the functor sending this object to $\Delta$. That is, for each $X \in \cat{A}(a,b)$ a pair of isomorphisms
\begin{equation}\label{eq:defn_cutsys_lambda}
\mu: X \lto \Delta_b \l X, \quad \eta: X \lto X \l \Delta_a
\end{equation}
in $\cat{A}(a,b)^\bullet$ natural in $X$.
\end{itemize}
This data is subject to the following coherence conditions:
\begin{itemize}
\item[(1)] For objects $a,b,c,d,e$ and $X \in \cat{A}(a,b),Y \in \cat{A}(b,c),Z \in \cat{A}(c,d),Q \in \cat{A}(d,e)$, commutativity of the diagram
\begin{equation}
\xymatrix@C+2pc{
((Q \l Z) \l Y ) \l X \ar[d]_-{\alpha_{Q \l Z, Y, X}}\ar[r]^-{\alpha_{Q,Z,Y} \l 1} & (Q \l (Z \l Y)) \l X \ar[r]^-{\alpha_{Q, Z \l Y, X}} & Q \l ( ( Z \l Y ) \l X ) \ar[d]^-{1 \l \alpha_{Z,Y,X}}\\
(Q \l Z) \l (Y \l X) \ar[rr]_-{\alpha_{Q, Z, Y \l X}} & & Q \l ( Z \l ( Y \l X ) )
}
\end{equation}
Note that when we write $\alpha_{Q, Z \l Y, X}$ we refer only the underlying object of $Z \l Y$.
\item[(2)] For objects $a,b$ and $X \in \cat{A}(a,b), Y \in \cat{A}(b,c)$ commutativity of the diagram
\begin{equation}\label{eq:unitor_constraint_cut}
\xymatrix{
(Y \l \Delta_b ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
& Y \l X \ar[ul]^-{\eta \l 1_X} \ar[ur]_-{1_Y \l \mu}
}
\end{equation}
\item[(3)] commutativity of \eqref{eq:psiunitor1},\eqref{eq:psiunitor2} for every $X$ and \eqref{eq:psithirdlastdia}, \eqref{eq:psimiddledia}, \eqref{eq:psilastdia} for every composable triple $X,Y,Z$.
\end{itemize}
Finally, the data is subject to three computability conditions:
\begin{itemize}
\item[(1)] For each pair of objects $a,b$ the category $\cat{A}(a,b)$ is effectively computable, in the sense that the morphisms and objects are described by finite data and the composition rule is computable.
\item[(2)] For each triple $a,b,c$ of objects the associated cut functor is effectively computable. In particular, for $1$-morphisms $Y$ and $X$ the object $Y \l X$ and its Clifford action are effectively computable from $X$ and $Y$.
\item[(3)] The associators and unitors are effectively computable from their arguments.
\end{itemize}
\end{definition}

\begin{remark} To give natural isomorphisms \eqref{eq:defn_cutsys_lambda} in $\cat{A}(a,b)^\bullet$ is equivalent to giving natural isomorphisms in $\cat{A}(a,b)$
\begin{equation}\label{eq:unitor_tilde_pre}
\mu: S_{\pi(b)} \otimes_k X \lto \Delta_b \l X, \quad \eta: S_{\pi(a)} \otimes_k X \lto X \l \Delta_a
\end{equation}
which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.

By Lemma \ref{lemma:morphism_out_1} such morphisms correspond bijectively to morphisms in $\cat{A}(a,b)$
\begin{equation}\label{eq:unitor_tilde}
\mu_0: X \lto \Delta_b \l X, \quad \eta_0: X \lto X \l \Delta_a
\end{equation}
satisfying respectively $a_i^\dagger \circ \mu_0 = 0$ for $1 \le i \le m$ and $a_i^\dagger \circ \eta_0 = 0$ for $1 \le i \le n$. The reason to introduce these maps is that commutativity of \eqref{eq:unitor_constraint_cut} can be more conveniently expressed in terms of the maps in \eqref{eq:unitor_tilde}, see Lemma \ref{lemma:unitor_check_help} below.
\end{remark}

Let $\cat{A}$ be a cut system. There is a superbicategory $\cat{A}^\bullet$ with objects the class of objects of $\cat{A}$ and with $1$- and $2$-morphisms defined by $\cat{A}^\bullet(a,b) = \cat{A}(a,b)^\bullet$. The units of $\cat{A}^\bullet$ are the objects $\Delta_a$ in the cut system, and the composition in the bicategory is given by the canonical extensions $\widetilde{T}$. To complete the definition of a superbicategory it only remains to give the associators and unitors, and the super-structure.

\begin{lemma} Given objects $a,b,c,d$ the natural isomorphism $\alpha$ canonically extends to a natural isomorphism $\widetilde{\alpha}$ as in the diagram
\[
\xymatrix@C+2pc{
\cat{A}(a,b)^\bullet \times \cat{A}(b,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[d]_-{\widetilde{T} \times 1} \ar[r]^-{1 \times \widetilde{T}} & \cat{A}(a,b)^\bullet \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\widetilde{\alpha}}\\
\cat{A}(a,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
}
\]
\end{lemma}
\begin{proof}
Suppose $(X,n) \in \cat{A}(a,b)^\bullet, (Y,m) \in \cat{A}(b,c)^\bullet$ and $(Z,t) \in \cat{A}(c,d)^\bullet$ are given. The underlying object of $((Z,t) \l (Y, m)) \l (X,n)$ is $(Z \l Y) \l X$, and it is clear that $\alpha_{Z,Y,X}$ is $A_t \otimes A_m \otimes A_n$-linear and therefore defines an isomorphism in $\cat{A}(a,d)^\bullet$
\[
\alpha_{Z,Y,X}: ((Z,t) \l (Y, m)) \l (X,n) \lto (Z,t) \l ((Y, m) \l (X,n))\,.
\]
Naturality is straightforward.
\end{proof}

\begin{lemma} Given objects $a,b$ the natural isomorphisms $\eta, \mu$ canonically extend to natural isomorphisms $\widetilde{\eta}, \widetilde{\mu}$ as in the diagram
\[
\xymatrix@C+2pc{
1 \times \cat{A}(a,b)^\bullet \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b)^\bullet \ar@{=>}@<4ex>[l]_-{\widetilde{\eta}} \ar@{=>}@<-4ex>[r]^-{\widetilde{\mu}} \ar[d]^-{1} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b)^\bullet \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
\cat{A}(a,a)^\bullet \times \cat{A}(a,b)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(A,B)^\bullet & \cat{A}(a,b)^\bullet \times \cat{A}(b,b)^\bullet \ar[l]^-{\widetilde{T}}
}
\]
 \end{lemma}
\begin{proof}
Let $(X,n) \in \cat{A}(a,b)^\bullet$. Forgetting the $A_n$-action on $X$, we have isomorphisms $\eta$ and $\mu$ as in \eqref{eq:unitor_tilde_pre}, which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear. Since these isomorphisms are natural, they are automatically $A_n$-linear. Verifying that these isomorphisms are natural with respect to the larger class of morphisms in $\cat{A}(a,b)^\bullet$ is straightforward.
\end{proof}

The supercategory structure is given as part of the cut system, so we have:

% The above definition of a cut system is from cutsys10. This is by p.11 there something which gives rise to a cut system in the sense of cutsys6, which is proved there to define a superbicategory.
\begin{proposition} Given a cut system $\cat{A}$, $\cat{A}^\bullet$ is a superbicategory.
\end{proposition}
\begin{proof}
This follows from Lemma \ref{lemma:constructingsuper}, with associator $\widetilde{\alpha}$ and unitors $\lambda =\widetilde{\mu}^{-1}, \rho = \widetilde{\eta}^{-1}$. The coherence follows from the coherence axioms of the cut system.
\end{proof}

We often confuse a cut system $\cat{A}$ with the associated superbicategory. For example, we refer to objects $X$ of $\cat{A}(a,b)^\bullet$ as a $1$-morphisms. To distinguish objects of the original category $\cat{A}(a,b)$ we refer to these objects as \emph{normal} or \emph{cut-free} $1$-morphisms. We keep the notation $Y \l X$ for the composition rule in $\cat{A}^\bullet$.

The following lemma is useful in verifying the unitor constraint.

\begin{lemma}\label{lemma:unitor_check_help} The commutativity of \eqref{eq:unitor_constraint_cut} is equivalent to commutativity of
\begin{equation}\label{eq:unitor_check_help1}
\xymatrix@C+1pc{
(Y \l \Delta_b) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
Y \l X \ar[u]^-{\eta_0 \l 1} & Y \l X \ar[l]^-{e_{\pi(b)}} \ar[r]_-{e_{\pi(b)}} & Y \l X \ar[u]_-{1 \l \mu_0}
}
\end{equation}
where $e_{\pi(b)}$ is the idempotent of Definition \ref{defn:idempotent_e}.
\end{lemma}
\begin{proof}
Let $m = \pi(b)$. Then $(Y \l \Delta_b) \l X$ has two $A_m$ actions, one from $Y \l \Delta_b$ which we denote by $A_{m_1}$, and the other from the cut with $X$ which we denote by $A_{m_2}$. By definition of the canonical extension $\widetilde{T}$ in Appendix \ref{app:proof_cut_extension}, $\eta \l 1$ is the $A_{m_1+m_2}$-linear morphism
\[
\eta: S_{m_1 + m_2, m_2} \otimes_{A_{m_2}} ( Y \l X ) \lto (Y \l \Delta_b ) \l X
\]
which corresponds under Lemma \ref{lemma:morphisms_two_forms} to
\[
\xymatrix@C+1pc{
Y \l X \ar[r]^-{e_m} & Y \l X \ar[r]^-{\eta_0 \l 1} & (Y \l \Delta_b) \l X
}\,.
\]
Applying the same logic to $\mu$ completes the proof.
\end{proof}

In a cut system the unitors $\mu, \eta$ go in the opposite direction to what one would expect from the conventions of bicategories. This is because it is more natural to describe morphisms out of a cut-free $1$-morphism and into a $1$-morphism carrying a nontrivial Clifford representation, than in the other direction.

\subsection{Cut models}\label{section:cut_models}

\begin{definition} A \emph{cut model} for a superbicategory $\cat{B}$ is a cut system $\cat{A}$ with the same underlying class of objects as $\cat{B}$ and a strong superfunctor $I: \cat{B} \lto \cat{A}^\bullet$ with the property that for every pair of objects $a,b$ the functor
\[
I_{a,b}: \cat{B}(a,b) \lto \cat{A}(a,b)^\bullet
\]
factors as
\[
\xymatrix{
\cat{B}(a,b) \ar[rr]^-{I_{a,b}} \ar[dr]_-{J_{a,b}} & & \cat{A}(a,b)^\bullet\\
& \cat{A}(a,b) \ar[ur]_-{\iota}
}
\]
where $J_{a,b}$ is an equivalence of supercategories. We often identify $X$ with $I(X)$.
\end{definition}

A cut model is an effectively computable model for composition of $1$-morphisms in~$\cat{B}$. Given $X: a \lto b$ and $Y: b \lto c$, let us suppose that the composition $Y \circ X$ in $\cat{B}$ is not defined algorithmically: perhaps this object is only identified up to unique isomorphism by a universal property. In contrast, the cut $Y \l X$ is computable from $X$ and $Y$, and the strong superfunctor $I$ provides an isomorphism in $\cat{A}(a,c)^\bullet$
\begin{equation}
Y \l X \cong Y \circ X\,.
\end{equation}
Here $Y \circ X$ is embedded into $\cat{A}^\bullet$ as a cut-free $1$-morphism and the cut $Y \l X$ by definition comes with an $A_{\pi(b)}$-module structure. That is, there is an isomorphism of $A_{\pi(b)}$-modules
\begin{equation}\label{eq:cutvsoriginal}
Y \l X \cong S_{\pi(b)} \otimes_k (Y \circ X )
\end{equation}
or what is the same, an isomorphism of objects in $\cat{A}(a,b)$
\begin{equation}\label{eq:cutvsoriginal2}
S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X ) \cong Y \circ X \,.
\end{equation}
The general philosophy is that a cut model decomposes composition in $\cat{B}$ into two stages: 
\begin{itemize}
\item first form the cut $Y \l X$, and then
\item tensor $Y \l X$ with $S^*_{\pi(b)}$ to compute $Y \circ X$. 
\end{itemize}
The idea is that the desired composition $Y \circ X$ lies inside $Y \l X$ in a way that is ``known'' in the sense that it is encoded by the Clifford action, but which is only \emph{realised} or \emph{constructed} after a computation is done. Forming the tensor product $S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ starting with the concretely known object $Y \l X$ can be further decomposed into a $\pi(b)$-step process of ``atomic'' computations, using the diagram of Remark \ref{remark:tensor_and_idempotent}
\begin{equation}\label{eq:computation_fiber_diagram}
\xymatrix@C+1pc@R+1pc{
Z_0 \cong Y \circ X \ar@{.}[d] & Z_1 \ar@{.}[d] & & Z_{\pi(b)-1} \ar@{.}[d] & Z_{\pi(b)} = Y \l X \ar@{.}[d]\\
0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b)-1  \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b) \ar@{.>}@<0.8ex>[l]
}\,.
\end{equation}
% remark:tensor_in_steps.
The intermediate objects are $Z_i = S_{i, \pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ for $i < \pi(b)$. Each of these objects $Z_i$ is obtained from $Z_{i+1}$ by splitting an idempotent of the form $a^\dagger a$.

Suppose we are in the situation where $Y \circ X$ is identified by a universal property but an explicit object realising this universal property is not given as part of $\cat{B}$. Then the result of the $\pi(b)$-step computation depicted above is an explicit object $Z_0$ of $\cat{A}(a,c) \cong \cat{B}(a,c)$ with this universal property. Thus the cut system gives a process for constructing representing objects for the uniquely defined isomorphism class $Y \circ X$ of $\cat{B}(a,c)$.

Conceptually, the number of steps in \eqref{eq:computation_fiber_diagram} represents the computational cost of a cut across the object $b$. For any cut across this object, $\pi(b)$-steps are necessary to convert the ``uncertainty'' represented by $Y \l X$ with its $A_{\pi(b)}$-action to the certainty of an object of $\cat{A}(a,c)$ (in the sense of Remark \ref{remark:tensor_and_idempotent}). In the example of the next section, the cost $\pi(W)$ of cutting across a hypersurface singularity $W$ is determined by its dimension.

\section{The Landau-Ginzburg cut system}\label{section:lg_cut_system}

In this section we introduce the cut system $\cat{L}$, beginning with a sketch of the major pieces and then proceeding to the technical details. The objects of the cut system are the same as the objects of the bicategory $\LG$, that is, pairs $(x, W)$ consisting of a set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x]$. Such an object is often written as $W$ or $W(x)$. The integer $\pi(x,W) = n$ is the number of variables.

Given objects $(x,W)$ and $(z,V)$ the supercategory $\cat{L}(W, V)$ is
\[
\cat{L}(W,V) = \hmf( k[x,z], V - W )^{\omega}\,,
\]
where $(-)^\omega$ denotes the idempotent completion; see Remark \ref{remark:idempotent_completion}. The objects of $\cat{L}(W,V)$ are therefore pairs $(X,e)$ consisting of a matrix factorisation $X$ of $V - W$ and an idempotent $e: X \lto X$.

Next we sketch the definition of the cut functors for $\cat{L}$. Let $W \in k[x_1,\ldots,x_n], V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ be potentials. The cut functor
\begin{gather*}
\cat{L}(W, V) \otimes_k \cat{L}(V, U) \lto \cat{L}(W, U)^\bullet\,\\
X \otimes Y \mapsto Y \l X
\end{gather*}
of degree $m$ is defined on matrix factorisations $X$ of $V - W$ and $Y$ of $U - V$ as follows. The object $Y \l X$ is a finite rank matrix factorisation of $W - U$ equipped with an action of the Clifford algebra $A_m$. The underlying matrix factorisation is
\[
Y \l X = Y \otimes_{k[z]} J_V \otimes_{k[z]} X
\]
where
\[
J_V = k[z] / ( \partial_{z_1} V, \ldots, \partial_{z_m} V )\,.
\]
With the differential $d_Y \otimes 1 + 1 \otimes d_X$, $Y \l X$ is a finite rank matrix factorisation of $U - W$ over $k[x,y]$ by virtue of the fact that $J_V$ is a finite rank free $k$-module. As an explicit matrix of polynomials in $k[x,y]$ the differential on $Y \l X$ can be obtained from the differentials on $X$ and $Y$ (which involve $k[z,x]$ and $k[y,z]$ respectively) by replacing occurrences of $z$ by a certain square matrix of scalars; see the proof of Theorem \ref{theorem:l_cut_system} for more details.

It remains to define the action of the generators $a_i$ and $a_i^\dagger$ of $A_m$ on $Y \l X$. We give the formulas below; later we will prove that these operators satisfy Clifford relations and that, with this action, $X \otimes Y \mapsto Y \l X$ is a cut functor.

The key ingredients of the Clifford action are the Atiyah classes of $Y \otimes X$, which are defined by first taking the technical step of extending scalars
\begin{equation}\label{eq:completed_tensor_product}
Y \,\check{\otimes}\, X = Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X
\end{equation}
and putting a connection on this module. We write $t = (t_1,\ldots,t_m)$ for the quasi-regular sequence of partial derivatives $t_i = \partial_{z_i} V$ and recall that there is by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
\begin{equation}\label{eq:connection_nabla}
\nabla: k\llbracket z \rrbracket \lto k\llbracket z \rrbracket \otimes_{k[t]} \Omega^1_{k[t]/k}
\end{equation}
the components of which are $k$-linear operators denoted $\partial_{t_i}: k\llbracket z \rrbracket \lto k\llbracket z \rrbracket$. A simple example of such a connection is given in Section \ref{example:computing_homs}. The operators $\partial_{t_i}$ extend to $k[x,y]$-linear operators on the free module $Y \, \check{\otimes}\, X$ and the $i$th Atiyah class is the operator
\[
\At_i = [d_{Y \otimes X}, \partial_{t_i}]\,.
\]
on $Y \,\check{\otimes}\, X$. This operator is the $i$th Atiyah class of $Y \,\check{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}. A reference for Atiyah classes is \cite{buchweitz_flenner}.

The Atiyah class is $k[t]$-linear and passes to a $k$-linear operator on the quotient $Y \l X$ of $Y \,\check{\otimes}\, X$. We need another operator on this matrix factorisation, for $1 \le j \le m$
\begin{equation}\label{eq:lambda_defn}
\lambda_j = 1 \otimes \partial_{z_j}(d_X)\,.
\end{equation}
With this notation, the action of the generators $a_i, a_i^\dagger$ of $A_m$ on $Y \l X$ is defined by
\begin{equation}\label{eq:intro_clifford_act1}
a_i^\dagger = \At_i
\end{equation}
and
\begin{equation}\label{eq:intro_clifford_act2}
a_i = - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \At_{q_1} \cdots \At_{q_l}
\end{equation}
where $1 \le q_i \le m$ for $1 \le i \le l$. For explicit examples of these operators, see Section \ref{example:computing_homs}.

The remaining components of the cut system $\cat{L}$ are the units $\Delta_W \in \cat{L}(W,W)$, which are the same as those for $\LG$ given in Section \ref{section:superbicatLG}, and the associators and unitors. To define the associator, let $W, V, U, Q$ be potentials with $V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ and suppose we are given a triple of composable $1$-morphisms
\begin{equation}\label{eq:composable_triple}
\xymatrix{
(q, Q) & (y, U) \ar[l]_-{Z} & (z,V) \ar[l]_-{Y} & (x,W) \ar[l]_-{X}
}\,.
\end{equation}
The isomorphism of matrix factorisations
\begin{gather*}
\alpha: Z \l (Y \l X) = Z \otimes J_U \otimes ( Y \otimes J_V \otimes X ) \lto (Z \otimes J_U \otimes Y) \otimes J_V \otimes X = (Z \l Y) \l X,\\
z \otimes (y \otimes x) \mapsto (z \otimes y) \otimes x
\end{gather*}
turns out to be $A_m \otimes A_p$-linear, and defines the associator for $\cat{L}$.

The unitors can also be described by explicit formulas. Given $X \in \cat{L}(W,V)$ as above with homogeneous basis $e_i$ as a $\mathbb{Z}_2$-graded $k[x,z]$-module, we define morphisms of matrix factorisations
\begin{gather}
\mu_0: X \lto \Delta_V \l X \,, \\
\mu_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j \Theta_{i_1} \ldots \Theta_{i_l} \left\{ \partial^{z,z'}_{[i_l]}(d_X) \cdots \partial^{z,z'}_{[i_1]}(d_X) \right\}_{ji} \otimes e_j\label{eq:explicit_mu0}
\end{gather}
and
\begin{gather}
\eta_0: X \lto X \l \Delta_W \,,\\
\eta_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j (-1)^{\binom{l}{2} + l|e_i|} e_j \otimes \left\{ \partial^{x,x'}_{[i_1]}(d_X) \cdots \partial^{x,x'}_{[i_l]}(d_X) \right\}_{ji} \Theta_{i_1} \ldots \Theta_{i_l}
\end{gather}
To make sense of these formulas, note that $\Delta_V$ is a matrix factorisation of $V(z) - V(z')$ over $k[z,z']$ and $\Delta_W$ is a matrix factorisation of $W(x) - W(x')$ over $k[x,x']$, while the divided difference operators are defined by
\[
{}^{t_i}(-): k[x,x'] \lto k[x,x']\,, \qquad f \mapsto f|_{x_i \mapsto x'_i}
\]
and
\[
\partial^{x,x'}_{[i]}: k[x,x'] \lto k[x,x']\,, \qquad f \mapsto \frac{{}^{t_1 \ldots t_{i-1}} f - {}^{t_1 \ldots t_i} f}{x_i - x'_i}
\]
and in the same way for $z,z'$. For a concrete example of these formulas see \cite{lgdual_survey}. The actual unitors are the morphisms $X \lto \Delta_V \l X$ and $X \lto X \l \Delta_W$ in $\cat{L}(W,V)^\bullet$ corresponding to $\mu_0$ and $\eta_0$ under the bijection of Lemma \ref{lemma:morphism_out_1}. It is not meant to be clear \emph{a priori} that these formulas even define morphisms, let alone that they satisfy the axioms for unitors; all these checks will be performed below.
\\

The major theorem, to be proved over the course of this section:

\begin{theorem}\label{theorem:l_cut_system} $\cat{L}$ is a cut system.
\end{theorem}

\subsection{The details}

We present the cut $Y \l X$ with its Clifford action as arising from the following problem: how do we find a finite model of the matrix factorisation $Y \otimes X$ over $k[x,y]$? This problem was addressed in joint work with Dyckerhoff \cite{dm1102.2957} and we rely heavily on these results; the main new ingredient here is the construction of Appendix \ref{section:cliffordactkos}.

The solution is given in the language of homological perturbation, which is recalled in Appendix \ref{section:homolog_fix}, with a reformulation in terms of splitting homotopies due to Barnes and Lambe \cite{barneslambe}. From the point of view of perturbation it is natural to look for a decomposition $d_{Y \otimes X} = d + \delta$ where a finite representative of $(Y \otimes X, d)$. Then the perturbation lemma can be used to parlay this into a finite model for the object of interest $(Y \otimes X, d + \delta)$.

There seems to be no obvious way to do this, but there is a simple way out: we replace $Y \otimes X$ by a sum of copies
\begin{equation}\label{eq:larger_object}
(Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
\end{equation}
in such a way that this larger object \emph{does} fit into the pattern of the perturbation lemma. More precisely, \eqref{eq:larger_object} will be the tensor product of $Y \otimes X$ with a $\mathbb{Z}_2$-graded $k$-module and we find in \eqref{eq:iso_larger_object} an isomorphic object for which a finite model may be found by perturbing a finite model for one ``piece'' of the differential. Then we need only remember the data of how to extract $Y \otimes X$ from inside this larger object: this data is the Clifford action.
\medskip

% As long as the $t_i$ belong to the maximal ideal
Let us now proceed to the details. We keep the above notation, so $k[z] = k[z_1,\ldots,z_m]$. The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ (where $t_i = \partial_{z_i} V$) has as its underlying graded module the exterior algebra on the $\theta_i$ of degree $-1$. If $F = k\theta_1 \oplus \cdots \oplus k\theta_m$ then
\begin{equation}\label{defn:koszul}
K = \bigwedge F \otimes_k k[z], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
\end{equation}
As explained in Appendix \ref{section:cliffordactkos} since each $t_i$ acts null-homotopically on $Y \otimes X$ there is an isomorphism of linear factorisations (writing $S_m = \bigwedge F$ as per our usual convention)
\begin{equation}\label{eq:iso_larger_object}
\xymatrix@C+3pc{ K \otimes Y \otimes X \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k (Y \otimes X)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
\end{equation}
where the differential on the left is $d_{Y \otimes X} + d_K$, on the right the differential is $d_{Y \otimes X}$, and $\delta = \sum_i \lambda_i \theta_i^*$ where $\lambda_i$ is a choice of null-homotopy for the action of $t_i$.

From the identity $d^2_Y = V - W$ we deduce that
\[
\partial_{z_i}(d_Y) d_Y + d_Y \partial_{z_i}(d_Y) = \partial_{z_i} V
\]
so that we may choose $\lambda_j$ to be the operator \eqref{eq:lambda_defn}. Note that the right hand side of \eqref{eq:iso_larger_object} is a direct sum of (shifted) copies of $Y \otimes X$; this is the object we intended in \eqref{eq:larger_object}. The Clifford algebra $A_m$ naturally acts on this matrix factorisation via closed linear operators.

The next step is to find a finite model of $K \otimes Y \otimes X$ using the perturbation lemma, by writing the differential as $d_K + d_{Y \otimes X}$ and finding a finite model of $(K \otimes Y \otimes X, d_K)$. We begin by giving a finite model for the Koszul complex $(K, d_K)$ using connections.
\medskip

The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $k\llbracket z \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra. By identifying $d t_i$ with $\theta_i$ we may identify this tensor product with $K$ itself, so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $K$.  It is straightforward to check that $[d_K, \nabla]$ is invertible on the graded submodule $K_{\le -1}$ of nonzero degree terms, and we define
\[
H = [d_K, \nabla]^{-1} \nabla\,.
\]

\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $K$.
\end{proposition}
\begin{proof}
See \cite[Section 8.1]{dm1102.2957}.
\end{proof}

The associated strong deformation retract of $\mathbb{Z}$-graded $k$-complexes is
\begin{equation}\label{eq:originalHdef}
\xymatrix@C+2pc{
(J_V,0) \ar@<-1ex>[r]_{\sigma} & (K, d_K), \ar@<-1ex>[l]_{\pi}
} \quad H
\end{equation}
where $\pi: K \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $k\llbracket z \rrbracket \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $k\llbracket z \rrbracket$ uniquely determined by $\nabla$. The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of the Koszul complex $K$.

Recall that the tensor product $Y \,\check{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,y]\llbracket z \rrbracket$. Let us write $\ell = k[x,y]$ so that the connection $\nabla$ extends to a standard $\ell$-linear flat connection on $R$. A choice of homogeneous basis for $X$ and $Y$ allows us to write $Y \otimes X \cong k[x,y,z] \otimes_k V$ for some $\mathbb{Z}_2$-graded free $k$-module $V$, so
\begin{equation}\label{eq:lambdaiso2}
K \otimes_{k\llbracket z \rrbracket}( Y \,\check{\otimes}\, X ) \cong K \otimes_{k\llbracket z \rrbracket} (R \otimes_k V) \cong K \otimes_k k[x,y] \otimes_k V
\end{equation}
In this way the $k$-linear splitting homotopy $H$ on $K$ induces an $\ell$-linear operator $H \otimes 1$ on $K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X$, which we again denote by $H$.

\begin{lemma} $H$ is an $\ell$-linear splitting homotopy on the complex $(K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, d_K)$.
\end{lemma}

The associated strong deformation retract is
\[
\xymatrix@C+2pc{
(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
} \quad H
\]
The map $\pi$ is $R$-linear induced by the map $\pi: K \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}. This is the desired finite model of $K \otimes Y \otimes X$ equipped with only the differential $d_K$.

We now view $d_{Y \otimes X}$ as a perturbation. The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$. Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
\[
\phi_\infty = \sum_{m \ge 0} (-1)^m (H d_{Y \otimes X})^m H
\]
is an $\ell$-linear splitting homotopy achieving the desired aim.

Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $\ell$-linear splitting homotopy on $K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X$ and the associated $\ell$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
\begin{equation}\label{eq:finite_model_defo}
\xymatrix@C+4pc{
Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, \ar@<-1ex>[l]_-{\pi}
} \quad \phi_\infty
\end{equation}
where the differential on the left is $d_{Y \otimes X}$ and on the right it is $d_K + d_{Y \otimes X}$. 
%$A = d_{Y \otimes X}( 1 + H d_{Y \otimes X} )^{-1}$ and $\sigma_\infty = \sigma - H A \sigma$. We need only justify why in \eqref{eq:perturbedsdr} we have $d_\infty = d_{Y \otimes X}$ and $f_\infty = \pi$. But this follows from $H \sigma = 0$ and $\pi H = 0$. 
%\begin{equation}
%\xymatrix@C+4pc{
%Y \l X \ar@<-1ex>[r]_-{\exp(-\delta) \sigma_\infty} & S_m \otimes_k ( Y \,\check{\otimes}\, X )\ar@<-1ex>[l]_-{\pi \exp(\delta)}
%}\,.
%\end{equation}
%of linear factorisations of $U - W$ over $k[x,y]$.

\begin{proposition}\label{prop:final_homotopy_equiv_cut} There is a homotopy equivalence of matrix factorisations over $k[x,y]$
\begin{equation}\label{eq:final_finite_model}
\xymatrix@C+4pc{
Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
}
\end{equation}
where $\Phi = \pi \exp(-\delta) \epsilon$ and $\Phi^{-1} = \epsilon^{-1} \exp(\delta) \sigma_\infty$ and $\epsilon: Y \otimes X \lto Y \,\check{\otimes}\, X$ is canonical.
\end{proposition}
\begin{proof}
Together \eqref{eq:iso_larger_object} and \eqref{eq:finite_model_defo} give a homotopy equivalence
\begin{equation}\label{eq:final_finite_model2}
\xymatrix@C+4pc{
Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & K \otimes Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
}\,.
\end{equation}
By \cite[Remark 7.7]{dm1102.2957} $\epsilon$ is a homotopy equivalence over $k[x,y]$, completing the proof.
\end{proof}

This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $S_m \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object. It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $S_m \otimes_k( Y \otimes X )$.

This equivalence induces an $A_m$ action on $Y \l X$ via the action on $S_m$.

\begin{definition} We introduce closed odd $k[x,y]$-linear operators on $Y \l X$ by
\begin{equation}\label{eq:new_operators}
(a_i^\dagger)_{Y,X} = \Phi \circ a_i^\dagger \circ \Phi^{-1}, \qquad (a_i)_{Y,X} = \Phi \circ a_i \circ \Phi^{-1}\,.
\end{equation}
\end{definition}

\begin{proposition}\label{prop:clifford_action} The operators $(a_i)_{Y,X}, (a_i^{\dagger})_{Y,X}$ of \eqref{eq:new_operators} agree with those in \eqref{eq:intro_clifford_act1}, \eqref{eq:intro_clifford_act2}.
\end{proposition}
\begin{proof}
Let us define intermediate operators on $K \otimes Y \otimes X$
\[
\psi_i^\dagger = \exp(-\delta) a_i^\dagger \exp(\delta), \qquad \psi_i = \exp(-\delta) a_i \exp(\delta).
\]
By Appendix \ref{section:cliffordactkos}, $\psi_i^\dagger = \theta^*_i$ and
\[
\psi_i = \theta_i - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_l}^*\,.
\]
Next we recall that, with $t_i = \partial_{z_i} V$, we have by \cite[Section 10]{dm1102.2957}
\begin{equation}\label{eq:atiyah_formula_sigma}
\sigma_\infty = \sum_{l \ge 0} \sum_{q_1,\ldots,q_l} (-1)^{\binom{l+1}{2}} \frac{1}{l!} [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}] \theta_{q_1} \cdots \theta_{q_l} + (t \text{ terms})\,.
\end{equation}
That is, $\sigma_\infty$ is given modulo the submodule $(t_1,\ldots,t_m) K \otimes Y \otimes X$ by the formula above. Hence we compute
\begin{align*}
(a_i^\dagger)_{Y,X} &= \pi \psi_i^\dagger \sigma_\infty = \pi \theta_i^* \sigma_\infty\\
&= \sum_{l \ge 0} \sum_{q_1,\ldots,q_l} (-1)^{\binom{l+1}{2}} \frac{1}{l!} [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}] \pi \theta_i^* \theta_{q_1} \cdots \theta_{q_l}\\
&= \sum_q [d_{Y \otimes X}, \partial_{t_q}] \pi \theta_i^* \theta_q\\
&= [d_{Y \otimes X}, \partial_{t_i}] = \At_i\,.
\end{align*}
To simplify the notation in the following, we define ($i$ is fixed) for a tuple $\bold{q} = (q_1,\ldots,q_l)$
\begin{gather*}
\tau_{\bold{q}} = [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, \ldots [ \lambda_{q_1}, \lambda_i ] \cdots ]\,,\\
\At_{\bold{q}} = [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}]\,.
\end{gather*}
With this notation we compute
\begin{align*}
(a_i)_{Y,X} &= \pi \psi_i \sigma_\infty\\
&= - \lambda_i - \pi \sum_{l \ge 1, k \ge 0} \sum_{q_1,\ldots,q_l} \sum_{w_1,\ldots,w_k} \frac{1}{(l+1)! k!} (-1)^{kl+\binom{k+1}{2}} \tau_{\bold{q}}  \At_{\bold{w}} \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{w_1} \cdots \theta_{w_k}\,.
\end{align*}
But $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $l = k$ and to $\bold{q}$ a permutation of $\bold{w}$. Since
\[
\theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{q_{\sigma(1)}} \cdots \theta_{q_{\sigma(l)}} = (-1)^{|\sigma|} (-1)^{\binom{l}{2}}
\]
we have, using the fact that the Atiyah classes anti-commute,
\begin{align*}
(a_i)_{Y,X} &= - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \sum_{\sigma \in S_l} (-1)^{|\sigma|} \frac{1}{l! (l+1)!} \tau_{\bold{q}} \At_{\sigma(\bold{q})}\\
&= - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} \tau_{\bold{q}} \At_{\bold{q}}
\end{align*}
which completes the proof.
\end{proof}

%The upshot is that if we equip $Y \l X$ with the Clifford action $\{ a_i, a_i^\dagger \}_i$ defined at the beginning of this section then the homotopy equivalence of Proposition \ref{prop:final_homotopy_equiv_cut} is $A_m$-linear.

\begin{remark} There is a question of whether or not the $A_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries). But Atiyah classes are independent, up to homotopy, of the choice of connection, and it is easy to see that the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis. Hence the action is indeed canonical.
\end{remark}

\begin{proposition} The above construction defines a cut functor of degree $m$
\begin{gather*}
\cat{L}(W, V) \otimes_k \cat{L}(V,U) \lto \cat{L}(W, U)^\bullet\\
X \otimes Y \mapsto (Y \l X, \{ a_i, a_i^\dagger \}_i )
\end{gather*}
sending a morphism $\phi \otimes \psi$ to $\psi \l \phi = \psi \otimes 1 \otimes \phi$.
\end{proposition}
\begin{proof}
We check that the construction is functorial, the compatibility with the supercategory structure is straightforward and we omit it. We only check functoriality in $X$, as the check for $Y$ is the same. So let $\phi: X \lto X'$ be a morphism of matrix factorisations. Let $a_i, a_i^\dagger$ denote the actions on both $X$ and $X'$, so that we need to check
\[
(1\l\phi) a_i = a_i (1 \l \phi), \qquad (1\l\phi) a_i^\dagger = a_i^\dagger (1 \l \phi)\,.
\]
It is enough to prove that $(1 \l \phi) \At_i = \At_i (1 \l \phi)$ and $(1 \l \phi) \lambda_i = \lambda_i (1 \l \phi)$ up to homotopy. The former follows from naturality of the Atiyah class (the arguments in either \cite[Lemma 3.3]{buchweitz_flenner} or \cite[Lemma 3.6]{dm1102.2957} also apply in the current context to show the desired naturality). For the latter we use Lemma \ref{lemma:naturalityoflambda} below.
\end{proof}

\begin{remark}\label{remark:iso_quotient_map} If $\iota: k \lto S_m$ denotes the map $\iota(1) = 1$ then by Lemma \ref{lemma:morphism_out_1} the composite
\[
\xymatrix@C+2pc{
Y \otimes X \cong k \otimes_k ( Y \otimes X ) \ar[r]^-{\iota \otimes 1} & S_m \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
}
\]
is simply the quotient map $\varrho: Y \otimes X \lto Y \l X$.
\end{remark}

\begin{lemma}\label{lemma:naturalityoflambda} Let $R$ be a $k$-algebra, $W \in R$. Let $\partial$ be a $k$-linear derivation on $R$ and $\phi: X \lto X'$ a morphism of finite rank matrix factorisations over $R$ with chosen homogeneous bases. Then the diagram
\[
\xymatrix{
X \ar[d]_{\partial(d_X)} \ar[r]^\phi & X' \ar[d]^{\partial(d_{X'})}\\
X \ar[r]_{\phi} & X'
}
\]
commutes up to homotopy.
\end{lemma}
\begin{proof}
From $d_{X'} \phi = \phi d_X$ we deduce
\[
\partial( d_{X'} ) \phi + d_{X'} \partial( \phi ) = \partial( \phi ) d_X + \phi \partial( d_X )
\]
and hence
\[
\partial( d_{X'} ) \phi - \phi \partial( d_X ) = \partial(\phi) d_X - d_{X'} \partial(\phi)
\]
as claimed.
\end{proof}

To complete the construction of the cut system we need to finish defining the associator and unitors (a task begun at the outset of the section) and to prove that the coherence conditions hold. Regarding the associator, we only need to check that $\alpha$ commutes with the Clifford actions. In the context of \eqref{eq:composable_triple},

\begin{lemma} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $A_m \otimes A_p$-linear.
\end{lemma}
\begin{proof}
We prove the $A_p$-linearity of $\alpha$, the proof for $A_m$ is similar. The algebra $A_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$. The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of 
\[
M = Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
\]
relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$. Specifically, the generator $a_i^{\dagger}$ of $A_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$. But this operator can be identified with an Atiyah class of the linear factorisation
\begin{equation}\label{eq:assoc_proof_M}
Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X \big)
\end{equation}
relative to the ring morphism
\begin{equation}\label{eq:assoc_proof_M2}
k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
\end{equation}
By the same argument the action of $A_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} Y \big) \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}. It is therefore clear that the associator $\alpha$ identifies these two actions.
\end{proof}

Earlier the unitors were described by explicit formulas. Here we begin more abstractly: let $X \in \cat{L}(W,V)$ be a matrix factorisation with $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$. Since $\Delta_V$ is the unit in $\LG$ there is a homotopy equivalence $\lambda: \Delta_V \otimes_{k[z]} X \lto X$ and so by Proposition \ref{prop:final_homotopy_equiv_cut} there are homotopy equivalences
\begin{equation}
\xymatrix@C+3pc{
\Delta_V \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( \Delta_V \otimes X )\ar@<-1ex>[l]_-{\Phi} \ar@<-1ex>[r]_-{1 \otimes \lambda} & S_m \otimes_k X \ar@<-1ex>[l]_-{1 \otimes \lambda^{-1}} 
}\,.
\end{equation}
By construction these isomorphisms are $A_m$-linear, and the map from right to left is an isomorphism $\mu: X \lto \Delta_V \l X$ in $\cat{L}(W,V)^\bullet$ corresponding under Lemma \ref{lemma:morphism_out_1} to
\[
\mu_0 = \xymatrix@C+1pc{
X \ar[r]^-{\lambda^{-1}} & \Delta_V \otimes_{k[z]} X \ar[r]^-{\varrho} & \Delta_V \l X
}\,.
\]
where $\varrho$ is the quotient map. Given the explicit formula for $\lambda^{-1}$ from \cite[Section 4.1]{lgdual}, this map $\mu_0$ has the explicit formula given earlier in \eqref{eq:explicit_mu0}. Since $\mu_0$ is natural in $X$, this also proves that $\mu$ is a natural isomorphism. The details for $\eta$ are similar, so the unitors are now defined.

\begin{remark}\label{remark:inflation} Let $V \in k[z_1,\ldots,z_m]$ be a potential and choose a $k$-basis for $J_V$. Then multiplication by $z_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[z_i]$ over $k$.

Given $X$ and $Y$ the cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $z_i$ by the scalar matrix $[z_i]$. This ``inflation'' produces a matrix of polynomials over $k[x,y]$. 
\end{remark}

\begin{proof}[Proof of Theorem \ref{theorem:l_cut_system}] We first check the coherence axioms. The first and third are trivial. To prove (2) we need by Lemma \ref{lemma:unitor_check_help} only check commutativity of \eqref{eq:unitor_check_help1} in the usual situation of $X: W \lto V$ and $Y: V \lto U$.

This amounts to checking commutativity of
\begin{equation}\label{eq:coherence3_1}
\xymatrix{
(Y \l \Delta_V ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_V \l X )\\
(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes J_V \otimes X \ar[l]^-{e_m} \ar[r]_-{e_m} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
}\,.
\end{equation}
By definition $e_m$ factors as
\[
\xymatrix{
Y \l X \ar[r]^-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X ) \ar[r] & Y \otimes X \ar[r] & S_m \otimes_k (Y \otimes X) \ar[r]^-{\Phi} & Y \l X
}
\]
so commutativity of \eqref{eq:coherence3_1} follows from commutativity of
\[
\xymatrix@C-0.5pc{
(Y \l \Delta_V ) \l X \ar[rrr]^-{\alpha} & & & Y \l ( \Delta_V \l X )\\
(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & (Y \otimes \Delta_V ) \otimes X \ar[l]_-{\varrho} \ar[r]^-{\alpha} & Y \otimes (\Delta_V \otimes X) \ar[r]^-{\varrho} & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes X \ar[u]^-{\rho^{-1} \otimes 1} \ar@{=}[r] \ar[l]^-{\varrho} & Y \otimes X \ar[u]_-{1 \otimes \lambda^{-1}} \ar[r]_-{\varrho} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
}\,.
\]
The innermost square of this diagram is the coherence constraint for the unitors in $\LG$.

Finally, we check the computability conditions. The associator and unitors are derived explicitly from $d_X$ and $d_Y$, so (3) is clear, and (2) is addressed by Remark \ref{remark:inflation} and the explicit formulas for the Clifford action. For (1), the objects and morphisms of $\cat{L}(W,V)$ are described by finite matrices of polynomials, and the composition rule is given by multiplication of matrices. There is one subtlety: morphisms are matrices of polynomials \emph{identified up to homotopy}.

To argue that $\cat{L}(W,V)$ is effectively computable we need to show that it is possible to determine algorithmically whether two morphisms are homotopic. This is important even at the level of objects: an object is a pair $(X,e)$ where $e^2 = e$ holds up to homotopy. Without an effective homotopy relation, there would be no algorithmic way to even distinguish between objects and non-objects. The necessary check is in Section \ref{example:computing_homs}.
\end{proof}

\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}. To see the connection, recall the idempotent $e_m \in A_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$. The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is 
\[
e_m' = a_1 \cdots a_m a_m^\dagger \cdots a_1^\dagger\,.
\]
Using \eqref{eq:intro_clifford_act1} and \eqref{eq:intro_clifford_act2} we can write down the explicit form of this idempotent acting on $Y \l X$. On this object each of the $a_i$'s acts simply as $- \lambda_i$ because all of the $a_j^\dagger$'s appear to the right. Hence on $Y \l X$
\begin{align*}
e_m' &= (-1)^{\binom{m}{2}} a_1 \cdots a_m a_1^\dagger \cdots a_m^\dagger \\
&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
\end{align*}
which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.

In \emph{ibid.} we constructed finite models of convolutions $Y \circ X$ one pair $(Y,X)$ at time. To make this assignment of finite models coherently for all $1$-morphisms in $\LG$ simultaneously it is natural to identify the Clifford actions which underlie the idempotents, as we do here.
\end{remark}

\subsection{The cut model of $\LG$}

Let $\cat{L}$ be the cut system described above, and let $\cat{L}^\bullet$ denote the associated superbicategory. With $\LG$ the superbicategory of Section \ref{section:superbicatLG} we construct a cut model $I: \LG \lto \cat{L}^\bullet$. On objects $I$ is the identity. For potentials $V,W$ we need to define a functor
\begin{equation}\label{eq:cut_model_equiv}
I_{V,W}: \LG(W,V) \lto \cat{L}^\bullet(W,V)\,.
\end{equation}
Recall that with $\cat{C} = \hmf(k[x,z], V - W)$,
\[
\cat{L}^\bullet(W,V) = \cat{C}^{\omega \bullet}\,, \quad \LG(W,V) = \cat{C}^{\oplus}\,.
\]
An object of $\cat{C}^{\omega \bullet}$ is a tuple $((X,e), n)$ consisting of an integer $n \ge 0$ and an $A_n$-module $(X,e)$ in $\cat{C}^\omega$, while an object of $\cat{C}^{\oplus}$ is a (possibly infinite) matrix factorisation of $V - W$ which is a direct summand of a finite rank one.

On the full subcategory of finite rank matrix factorisation of $V - W$, $I_{V,W}$ is the identity and this functor extends uniquely (up to natural equivalence) to $\LG(W,V)$. To be more explicit about it: for each $X \in \LG(W,V)$ we \emph{choose} a finite rank matrix factorisation $\bar{X}$ together with an idempotent $e$ and morphisms $f_X, g_X$ as in the diagram
\[
\xymatrix@C+2pc{
\bar{X} \ar@(ul,dl)_-{e} \ar@<1ex>[r]^-{f_X} & X \ar@<1ex>[l]^-{g_X}
}
\]
satisfying $g_X f_X = e$ and $f_X g_X = 1_X$. Then the full definition of $I$ is given by
\[
I( X ) = ((\bar{X}, e), 0)\,, \qquad I( \phi ) = g_Y \phi f_X\,.
\]
To complete the definition of a strong functor $I$ it remains to give a natural $2$-isomorphism
\begin{equation}\label{eq:strong_functor_varphi}
\varphi: I(Y \otimes X) \lto I(Y) \l I(X)
\end{equation}
for every pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ in $\LG$.

We give the definition of $\varphi$ where $X,Y$ are finite rank matrix factorisations; the general case follows. Recall the $A_m$-linear isomorphism of Proposition \ref{prop:final_homotopy_equiv_cut}
\begin{equation}\label{eq:cutmodelequiv}
\xymatrix@C+4pc{
Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
}\,.
\end{equation}
% TODO issue with completion
This is essentially the desired natural isomorphism $\varphi$, and it is only necessary to package it a little more carefully. Let $e = e_m \in A_m$ denote the idempotent from Definition \ref{defn:idempotent_e}. If we define $\nu: S_m \lto k$ to be the projection onto $k \cdot 1$ then there is a diagram
\[
\xymatrix@C+4pc{
Y \l X \ar@<1ex>[r]^-{\nu \Phi^{-1}} & Y \otimes X \ar@<1ex>[l]^-{\varrho}
}
\]
expressing $Y \otimes X$ as the splitting of the idempotent $e$ on $Y \l X$. Here $\varrho: Y \otimes X \lto Y \l X$ is the quotient map. The usphot is that as objects of $\cat{L}(W,V)^{\omega \bullet}$
\[
I(Y \otimes X) = ((Y\l X, e), 0), \qquad I(Y) \l I(X) = ( (Y \l X, 1), m )\,.
\]
Morphisms $\varphi$ as in \eqref{eq:strong_functor_varphi} are in bijection with morphisms
\[
\varphi_0: (Y \l X, e) \lto (Y\l X, 1)
\]
in $\hmf(k[x,z], U - W)^{\omega}$ satisfying $\theta_i^* \circ \varphi_0 = 0$ for $1 \le i \le m$. The endomorphism $\varphi_0 = e_m$ of $Y \l X$ fits the bill. In the category of infinite rank matrix factorisations, $\varphi_0$ is just the morphism $\varrho$. It follows that $\varphi$ is a natural isomorphism, since it corresponds to $\Phi$.

\begin{theorem} The data $(I, \varphi)$ defines a cut model $\LG \lto \cat{L}^\bullet$.
\end{theorem}
\begin{proof}
Once we have shown that $(I, \varphi)$ is a strong functor it is clearly ``super'', and by construction it defines a cut model. There are two coherence conditions: the first is commutativity of the following diagram, in the context of a composable triple as in \eqref{eq:composable_triple}:
\begin{equation}\label{eq:dia_coherence1}
\xymatrix@C+2pc{
(I(Z) \l I(Y) ) \l I(X) \ar[r]^-{\alpha} \ar[d]_-{\varphi \l 1} & I(Z) \l ( I(Y) \l I(X) ) \ar[d]^-{1 \l \varphi} \\
I(Z \otimes Y) \l I(X) \ar[d]_-{\varphi} &  I(Z) \l I(Y \otimes X)\ar[d]^-{\varphi}\\
I( (Z \otimes Y) \otimes X ) \ar[r]_-{I(\alpha)} & I(Z \otimes (Y \otimes X))
}
\end{equation}
The key to checking this lies in understanding what $I( Z \otimes (Y \otimes X) )$ is. But as we have argued above, $Y \otimes X$ is a summand of $Y \l X$ with idempotent $e_m$ while $Z \otimes ( Y \l X )$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p$. This implies that $Z \otimes (Y \otimes X)$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p e_m = e_m e_p = e_{m+p}$, so
\[
I( (Z \otimes Y) \otimes X ) = ( Z \l (Y \l X), e_{m+p} ), \quad I( Z \otimes (Y \otimes X) ) = ( (Z \l Y) \l X, e_{m+p} )\,.
\]
Then commutativity of \eqref{eq:dia_coherence1} reduces to commutativity in $\hmf(Q - W)^{\omega}$ of
\[
\xymatrix@C+2pc{
( (Z \l Y ) \l X, 1 ) \ar[r]^-{\alpha} & ( Z \l (Y \l X ), 1)\\
( (Z \l Y) \l X, e_p \l 1) \ar[u]^-{e_p \l 1} & ( Z \l (Y \l X), 1 \l e_m) \ar[u]_-{e_m}\\
( (Z \l Y) \l X, e_{m+p} ) \ar[u]^-{e_{m+p}} \ar[r]_-{e_{m+p}} & ( Z \l (Y \l X), e_{m+p} ) \ar[u]_-{e_{m+p}}
}
\]
which is clear.

The remaining coherence conditions are commutativity, for $X: W \lto V$, of
\begin{equation}\label{eq:dia_coherence2}
\xymatrix{
I(X) \ar[dr]_-{\eta} & & I( X \otimes \Delta_W ) \ar[ll]_-{I(\rho)} \\
& I(X) \l \Delta_W \ar[ur]_-{\varphi}
}
\end{equation}
and a similar diagram for $\lambda$. By definition $I(\rho)$ is the inverse of
\[
\xymatrix{
X \ar[r]^-{\eta^{-1}} & X \otimes \Delta_W \ar[r]^{\varrho} & X \l \Delta_W
}
\]
so checking commutativity of \eqref{eq:dia_coherence2} can be done using Lemma \ref{lemma:morphism_out_1}, and similarly for the diagram involving $\mu$.
\end{proof}

\subsection{Example: the Hom complex}\label{example:computing_homs}

Using the cut model $\cat{L}$ we can study the complex $\Hom_R(X,Y)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[z_1,\ldots,z_m]$. In particular, we will explain how the homotopy relation on morphisms of matrix factorisations is effectively computable.

The pair $(k,0)$ is an object in $\LG$ and we may view $Y$ and the dual matrix factorisation $X^{\vee}$ of $-V$ as a pair of $1$-morphisms
\begin{equation}\label{eq:compute_hom_composition}
\xymatrix@C+2pc{
0 \ar[r]^-{Y} & V \ar[r]^-{X^{\vee}} & 0
}\,.
\end{equation}
The composite is a $1$-morphism $0 \lto 0$, that is, $\mathbb{Z}_2$-graded complex of $k$-modules. This is the Hom complex of $R$-linear homogeneous maps $X \lto Y$,
\[
X^{\vee} \otimes_R Y \cong \Hom_R(X, Y)
\]
with the differential $\phi \mapsto d_Y \circ \phi - (-1)^{|\phi|} \phi \circ d_X$. The cut model provides a two-step process to compute the result of the composition in \eqref{eq:compute_hom_composition}. First form the cut
\[
X^{\vee} \l Y = X^{\vee} \otimes_R J_V \otimes_R Y = \Hom_{J_V}( \bar{X}, \bar{Y} )
\]
where $\bar{X} = X \otimes_R J_V, \bar{Y} = Y \otimes_R J_V$. This is a complex of finite-rank $\mathbb{Z}_2$-graded free $k$-modules, and there is an $A_m$-linear homotopy equivalence
\[
\Phi: S_m \otimes_k \Hom_R(X,Y) \lto \Hom_{J_V}( \bar{X}, \bar{Y} )\,.
\]
Set $H = \Hom_{J_V}( \bar{X}, \bar{Y} )$ and define
\[
B = \im( d^1_H: H^1 \lto H^0 )\,.
\]
As a matrix of scalars $d^1_H$ may be computed from the differentials $d_X, d_Y$ by inflation, as described in Remark \ref{remark:inflation}. Let $\psi: X \lto Y$ be a morphism of matrix factorisations. Then $\psi$ is null-homotopic if and only if $\psi' = \Phi(\psi) \in \Hom_{J_V}( \bar{X}, \bar{Y} )$ is a coboundary. As a matrix, $\psi'$ is obtained from $\psi$ by inflation. This reduces the problem of determing whether or not $\psi$ is null-homotopic to the subspace membership problem for the pair $(B, \psi')$. If $k$ is a field this may be computed by a row-reduction, and otherwise using Gr\"obner bases.

\begin{example} Suppose $V = z^N$ in $k[z]$ for $N \ge 2$. Take matrix factorisations $X,Y$ with the same underlying free $R = k[z]$-module $X = Y = R \oplus R \theta$ and differentials
\[
d_X = z^i \theta + z^{N-i} \theta^* = \begin{pmatrix} 0 & z^{N-i} \\ z^i & 0 \end{pmatrix}, \qquad d_Y = z^j \theta + z^{N-j} \theta^* = \begin{pmatrix} 0 & z^{N-j}\\ z^j & 0 \end{pmatrix}
\]
where $1 \le i,j \le N/2$. Using the basis $\Hom_R(X,Y) = R \theta \theta^* \oplus R \theta^* \theta \oplus R\theta \oplus R \theta^*$,
\begin{equation}\label{eq:differential_hom}
d_{\Hom} = \begin{pmatrix} 0 & 0 & z^{N-i} & z^j \\ 
0 & 0 & z^{N-j} & z^i \\
-z^i & z^j & 0 & 0 \\
z^{N-j} & -z^{N-i} & 0 & 0 \end{pmatrix}\,.
\end{equation}
Let us now compute the cut $X^{\vee} \l Y$ with its Clifford action. With
\[
J_V = k[z]/z^{N-1} = k \cdot 1 \oplus k \cdot z \oplus \cdots k \cdot z^{N-2}
\]
the matrix of multiplication by $z$ on $J_V$ is $[z] = \begin{pmatrix} 0 & 0\\ I_{N-2} & 0 \end{pmatrix}$. The differential on
\[
X^{\vee} \l Y = \Hom_{J_V}( \bar{X}, \bar{Y} ) = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
\]
is then obtained from \eqref{eq:differential_hom} by replacing every $z$ by the matrix $[z]$.

The Clifford algebra $A_1$ acts by two generators $a, a^\dagger$. To determine their matrices, note that with $t = z^{N-1}$, $k[z]$ is a free $k[t]$-module with basis $1, \ldots, z^{N-2}$. Given a polynomial $f(z)$ we may uniquely write it as $f(z) = \sum_{l = 0}^{N-2} f_l \cdot z^l$ with $f_l \in k[t]$. There is a connection $\nabla: k[z] \lto k[z] \otimes_{k[t]} \Omega^1_{k[t]/k}$ whose associated $k$-linear operator $\partial_t$ is
\[
\partial_t: k[z] \lto k[z], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) z^l \,.
\]
Notice that for $0 \le q \le N - 1$, $\partial_t(z^q) = \delta_{q (N-1)} \cdot 1$.

The Atiyah class is the $k[t]$-linear operator $\At = [d_{\Hom}, \partial_t]$ on $\Hom_R(X,Y)$. We may compute it for example on generators by
\[
\At( \theta \theta^* ) = \partial_t d_{\Hom}( \theta \theta^* ) = - \partial_t( z^i ) \theta + \partial_t( z^{N-j} ) \theta^* = - \delta_{i (N-1)} \theta + \delta_{(N-j)(N-1)} \theta^*\,.
\]
The Atiyah class passes to a $k$-linear operator $a^\dagger$ on $X^{\vee} \l Y$ with matrix ($I$ denotes $I_{N-1}$)
\begin{equation}\label{eq:aityah_class_hom_example}
a^\dagger = \begin{pmatrix} 0 & 0 & \delta_{i1} \cdot I & \delta_{j(N-1)} \cdot I \\ 
0 & 0 & \delta_{j1} \cdot I & \delta_{i(N-1)} \cdot I \\
- \delta_{i(N-1)} \cdot I & \delta_{j(N-1)} \cdot I & 0 & 0 \\
\delta_{j1} \cdot I & - \delta_{i1} \cdot I & 0 & 0 \end{pmatrix}\,.
\end{equation}
Similarly one can determine that the matrix of $\lambda$ on $X^{\vee} \l Y$ is
\[
\lambda = \begin{pmatrix} 0 & 0 & 0 & \frac{j}{N} [z^{j-1}] \\
0 & 0 & \frac{N-j}{N} [z^{N-j-1}] & 0\\
0 & \frac{j}{N} [z^{j-1}] & 0 & 0\\
\frac{N-j}{N} [z^{N-j-1}] & 0 & 0 & 0\end{pmatrix}\,.
\]
By definition $a = - \lambda - \lambda^2 a^\dagger$ so this completes the description of the cut $( X^{\vee} \l Y, \{ a, a^\dagger \} )$. Splittng the idempotent $a^\dagger a$ on the $\mathbb{Z}_2$-graded complex $X^{\vee} \l Y$ of finite rank free $k$-modules yields a finite model for $\Hom_R(X,Y)$.
\end{example}

\appendix

\section{Homological perturbation and fixed points}\label{section:homolog_fix}

A fundamental role in this paper is played by the homological perturbation lemma. While this result is usually stated for complexes the standard results generalise immediately to linear factorisations, and in this section we collect these standard results. But we begin by recalling the motivating problem for which the perturbation lemma is the solution.

Let $Q$ be a complex of infinite rank free abelian groups. Suppose that the cohomology is finitely generated, so that $Q$ contains in some sense only a ``finite'' amount of information. One can ask for a description which makes this finiteness manifest: the obvious answer is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.

A \emph{deformation retract} of complexes is a pair of morphisms
\begin{equation}\label{eq:example_defo_retract}
\xymatrix@C+2pc{
C \ar@<-1ex>[r]_\nabla & Q, \ar@<-1ex>[l]_f
} \quad \phi
\end{equation}
and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $f \nabla = 1_C, \nabla f = 1_Q - [d_Q, \phi]$ so that $f, \nabla$ are mutually inverse homotopy equivalences. A deformation retract is \emph{strong} if it satisfies some additional conditions, listed below. The point is that if $C$ is finitely generated, then \eqref{eq:example_defo_retract} gives the desired finite representative in the homotopy equivalence class of $Q$.

\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-modules
\[
\xymatrix@C+2pc@R+1pc{
0 \ar[d] \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar[d]^-{x}\\
k \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar@/_3pc/@{.>}[u]_-{\phi}
}
\]
in which the first column is the complex $C$ which has $k$ concentrated in degree zero, and the second column $Q$ is the Koszul complex on $x$. The map $f: k[x] \lto k$ sends every polynomial to its constant term, while $\nabla: k \lto k[x]$ is the inclusion of the constants. The operator $\phi$ is defined by $\phi( x^n ) = x^{n-1}$ and $\phi(1) = 0$. Together these maps are a deformation retract giving $k$ as the ``finite model'' of $Q$.
\end{example}

Suppose now that a deformation retract computing a finite representative for $Q$ cannot be found immediately, but that we know how to decompose the differential as $d_Q = d + \tau$ in such a way that there is a finite representative for the complex $(Q,d)$. The perturbation lemma allows us, with some conditions, to ``mix in'' the operator $\tau$ to obtain a finite model for the original complex $Q$.
\\

Let $R$ be a commutative ring and $W \in R$. Everything we say applies, in the case where $W = 0$, to both $\mathbb{Z}_2$-graded and $\mathbb{Z}$-graded complexes.  For our purposes the reformulation of the perturbation lemma in terms of fixed points by Barnes and Lambe is more natural, so we emphasise the ``splitting homotopies'' of \cite{barneslambe}.

\begin{definition} A \emph{splitting homotopy} on a linear factorisation $(A,d)$ of $W$ is a degree $-1$ operator $\phi$ on $A$ satisfying
\begin{itemize}
\item[(i)] $\phi^2 = 0$,
\item[(ii)] $\phi d \phi = \phi$.
\end{itemize}
A \emph{morphism} $(A,d, \phi) \lto (A,d',\phi')$ of splitting homotopies is a morphism $\alpha: A \lto A'$ of linear factorisations satisfying $\phi' \alpha = \alpha \phi$.
\end{definition}

The condition (ii) says that $\phi$ is a \emph{fixed point} of the operator $F(x) = x d x$.

\begin{definition} A \emph{strong deformation retract} of linear factorisations of $W$ is a pair of morphisms of linear factorisations
\begin{equation}\label{eq:defn_sdr}
\xymatrix@C+2pc{
(M,d) \ar@<-1ex>[r]_\nabla & (A,d), \ar@<-1ex>[l]_f
} \quad \phi
\end{equation}
together with a degree $-1$ operator $\phi: A \lto A$ satisfying
\begin{itemize}
\item[(i)] $f \nabla = 1_M$,
\item[(ii)] $\nabla f = 1_A - [d, \phi]$,
\item[(iii)] $\phi^2 = 0$,
\item[(iv)] $\phi \nabla = 0$,
\item[(v)] $f \phi = 0$.
\end{itemize}
A \emph{morphism} of strong deformation retracts is a commutative diagram
\[
\xymatrix@C+2pc{
(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\nabla & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_f\\
(M',d') \ar@<-1ex>[r]_{\nabla'} & (A',d') \ar@<-1ex>[l]_{f'}
}
\]
that is, a pair of morphisms $\alpha, \beta$ such that $\beta \nabla = \nabla' \alpha$, $\alpha f = f' \beta$ and $\phi' \beta = \beta \phi$.
\end{definition}

We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}. Namely, a strong deformation retract in the above sense is the same as a special deformation retract in the sense of \emph{ibid.} with $h = - \phi$.

\begin{lemma}\label{lemma:equivocate} There is an equivalence between the category of splitting homotopies $\cat{C}_1$ and the category of  strong deformation retracts $\cat{C}_2$.
\end{lemma}
\begin{proof}
We briefly recall the construction from \cite[p.883]{barneslambe}, which is not stated in terms of categories but is obviously functorial. Given a strong deformation retract \eqref{eq:defn_sdr} the data $(A, \phi)$ is a splitting homotopy. In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $\pi = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(\phi)$ with the associated projection $f$ and inclusion $\nabla$. Then this is a strong deformation retract, together with the original $\phi$.
\end{proof}

%Taking splitting homotopies as the primary object has the advantage of hiding some of the incidental complexity in the perturbation lemma.
Here is the problem that the formalism is designed to solve: suppose $(A,d)$ is a linear factorisation of $W$ and that $\tau$ is a degree $+1$ operator on $A$ such that $(A, d + \tau)$ is a linear factorisation of $V$ (possibly different to $W$). This $\tau$ is called the \emph{perturbation}.

\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(\pi) \cong \im(\pi')$ as graded $R$-modules, where $\pi = 1_A - [d, \phi]$ and $\pi' = 1_A - [d + \tau, \phi']$. 
\end{definition}

That is, with $\xi = d + \tau$ the problem is to find a fixed point of the operator
\[
F(x) = x \xi x
\]
among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(\pi)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
\[
\phi_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \phi = \phi - \phi \tau \phi + \phi \tau \phi \tau \phi - \cdots
\]
is a solution of this fixed point problem:

\begin{theorem}[Perturbation lemma]\label{theorem:pertlemma} Suppose $\phi \tau$ has finite order. Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi)$ and satisfies the isomorphism condition in the transference problem.
\end{theorem}
\begin{proof}
The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations.
\end{proof}

The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}. The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
\begin{equation}\label{eq:perturbedsdr}
\xymatrix@C+2pc{
(M,d_\infty) \ar@<-1ex>[r]_{\nabla_\infty} & (A, \xi), \ar@<-1ex>[l]_{f_\infty}
} \quad \phi_\infty
\end{equation}
where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
\begin{align*}
\nabla_\infty &= \nabla - \phi A \nabla,\\
f_\infty &= f - f A \phi,\\
d_\infty &= d + f A \nabla\,.
\end{align*}
As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
\[
\im(1 - [\xi, \phi_\infty]) \cong \im(\pi) = M
\]
be identified with $M$, and the induced maps are the $\nabla_\infty, f_\infty, d_\infty$ given above. It is also possible to give a direct proof as in \cite{crainic}. To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one just studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation. The standard way of generating fixed points, say by iterating $F$ infinitely many times on $\phi$, produces the same answer provided one takes the limit of the coefficients in $\mathbb{Q}$ with respect to the $2$-adic valuation; see \cite[p.885]{barneslambe}.

\section{Tensor products in supercategories}\label{section:tensorproduct_supcat}

Let $\cat{C}$ be an idempotent complete supercategory.

\begin{definition} Let $V$ be a $\mathbb{Z}_2$-graded $k$-module and $X$ an object of $\cat{C}$. An object of $\cat{C}$ representing the functor $\Hom^0_k( V, \cat{C}^*(X, -))$ is denoted $V \otimes_k X$ if it exists. That is to say, the tensor product consists of an object $V \otimes_k X$ and a natural isomorphism
\[
\rho_Y: \cat{C}( V \otimes_k X, Y ) \lto \Hom^0_k( V, \cat{C}^*(X,Y) )\,.
\]
Such a pair is unique up to unique isomorphism, if it exists.
\end{definition}

\begin{remark} 
From $\rho$ we also obtain an isomorphism of $\mathbb{Z}_2$-graded $k$-modules
\[
\cat{C}^*( V \otimes_k X, Y ) \cong \Hom_k^*( V, \cat{C}^*(X,Y) )\,.
\]
The tensor product $V \otimes_k X$ is made functorial in $V$ and $X$ in such a way that $\rho$ is natural in all its variables.
\end{remark}

\begin{example} If $V = k^{\oplus n} \oplus k[1]^{\oplus m}$ is finite and free then
\[
V \otimes_k X = X^{\oplus n} \oplus \Psi X ^{\oplus m}
\]
is a representing object, with the obvious isomorphism $\rho$.
\end{example}

\begin{lemma} If $\cat{C}$ is idempotent complete and $V$ is a finitely generated projective $\mathbb{Z}_2$-graded $k$-module, then $V \otimes_k X$ exists for any object $X$.
\end{lemma}
\begin{proof}
Let $V'$ be a finite free $k$-module with $f: V' \lto V, g: V \lto V'$ satisfying $fg = 1$. This determines an idempotent $1 \otimes e$ on $V' \otimes_k X$, which splits by hypothesis in $\cat{C}$. The object splitting this idempotent has the right property to be $V \otimes_k X$.
\end{proof}
% via morphisms $F,G$ with
%\[
%\xymatrix@C+1pc{
%Q \ar@<0.8ex>[r]^-{G} & V' \otimes_k X \ar@<0.8ex>[l]^-{F} 
%} \qquad FG = 1, GF = 1 \otimes e
%\]
%for some object $Q$. We have
%\begin{align*}
%\cat{C}( Q, Y ) &\cong \{ f: V' \otimes_k X \lto Y \l f(1 \otimes e) = 1 \otimes e \}\\
%&\cong \{ \hat{f} \in \Hom_k( V', \cat{C}^*(X,Y)) \l \hat{f} e = e \}\\
%&\cong \Hom_k( V, \cat{C}^*(X,Y))\,.
%\end{align*}
%and hence $V \otimes_k X = Q$ exists.
%\end{proof}

More generally, let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra.

\begin{definition} Given a right $\mathbb{Z}_2$-graded $A$-module $V$ and an object $X$ of $\cat{C}$, we denote by $V \otimes_A X$ the object representing the functor $\Hom^0_A( V, \cat{C}^*(X,-))$ if it exists. That is, the tensor product is an object $V \otimes_A X$ together with a natural isomorphism
\begin{equation}\label{eq:isodefatensor}
\rho_Y: \cat{C}(V \otimes_A X, Y) \lto \Hom^0_A( V, \cat{C}^*(X,Y))\,.
\end{equation}
As before, the tensor product is functorial in both $V$ and $X$.
\end{definition}

Henceforth we concentrate our attention on $\mathbb{Z}_2$-graded $k$-algebras $A$ which are \emph{Morita trivial} in the sense that they are isomorphic to an algebra of the form $\End_k(P)$ for a finite rank free $\mathbb{Z}_2$-graded $k$-module $P$.

\begin{lemma} If $A \cong \End_k(P)$ then for any $A$-module $X$ in $\cat{C}$ there is an object $\widetilde{X}$ and an isomorphism of $A$-modules $X \cong P \otimes_k \widetilde{X}$.
\end{lemma}
\begin{proof}
The natural idempotents in $A$ act as idempotents on $X$, which split.
\end{proof}

\begin{lemma} If $A \cong \End_k(P)$ and $V$ is a $\mathbb{Z}_2$-graded right $A$-module which is finitely generated and projective as a $k$-module, then $V \otimes_A X$ exists for any $A$-module $X$.
\end{lemma}
\begin{proof}
Write $P^* = \Hom_k(P,k)$ so that $V \cong \widetilde{V} \otimes_k P^*$ as right $A$-modules for some $\mathbb{Z}_2$-graded $k$-module $\widetilde{V}$. Since $V$ is finitely generated projective over $k$, so is $\widetilde{V}$. By the previous lemma, $X \cong P \otimes_k \widetilde{X}$ for some object $\widetilde{X}$, so we might expect that
\[
V \otimes_A X \cong (\widetilde{V} \otimes_k P^*) \otimes_A (P \otimes_k \widetilde{X}) \cong \widetilde{V} \otimes_k \widetilde{X}
\]
Working backwards: $\widetilde{V} \otimes_k \widetilde{X}$ exists and has the right universal property since
\begin{align*}
\cat{C}(\widetilde{V} \otimes_k \widetilde{X}, Y) &\cong \Hom_k( V \otimes_A P, \cat{C}^*(\widetilde{X}, Y))\\
&\cong \Hom_A( V, P^* \otimes_k \cat{C}^*(\widetilde{X}, Y))\\
&\cong \Hom_A( V, \cat{C}^*( X, Y ) )
\end{align*}
as claimed.
\end{proof}

From now on $A,B,C$ are Morita trivial $k$-algebras. Recall $\cat{C}_A$ denotes the category of left $A$-modules in $\cat{C}$.

\begin{definition}\label{defn:psimodule} Given a left $A$-module $X$ in $\cat{C}$, the object $\Psi X$ is a left $A$-module, where $a \in A_0$ acts by $\Psi(a)$ and $a \in A_1$ acts by
\[
\xymatrix{
\Psi (X) \ar[r]^-{\Psi(a)} & \Psi \Psi (X) \ar[r]^-{-1} & \Psi \Psi (X)
}\,.
\]
This determines a functor $\Psi: \cat{C}_A \lto \cat{C}_A$.
\end{definition}

\begin{lemma} $(\cat{C}_A, \Psi)$ is a supercategory.
\end{lemma}
\begin{proof}
The natural isomorphism $\xi_X: \Psi \Psi (X) \lto X$ is given by the identity in $\cat{C}$.
\end{proof}

Let $V$ be a $B$-$A$-bimodule which is finitely generated and projective over $k$. If $X$ is a left $A$-module in $\cat{C}$ then $V \otimes_A X$ is made into a left $B$-module in $\cat{C}$ uniquely such that \eqref{eq:isodefatensor} is a natural isomorphism of $B$-modules. Hence the tensor product gives a functor
\[
\Phi_V = V \otimes_A (-): \cat{C}_A \lto \cat{C}_B\,.
\]
Given a $B$-$A$-bimodule $V$ and an object $X$ for which $V \otimes_A X$ exists, there are natural isomorphisms of $B$-modules
\[
\Psi V \otimes_A X \cong \Psi(V \otimes_A X) \cong V \otimes_A \Psi X
\]
induced from the isomorphisms
\[
\Hom_A( \Psi V, \cat{C}^*(X, -)) \cong \Hom_A( V, \Psi \cat{C}^*(X, -) ) \cong \Hom_A( V, \cat{C}^*(\Psi X, -))\,.
\]
It follows that $\Phi_V$ is a superfunctor.

\begin{lemma}\label{lemma:assoctensor} Let $W$ be a $C$-$B$-bimodule and $V$ a $B$-$A$-bimodule. Then there is a natural isomorphism of $C$-modules
\[
(W \otimes_B V) \otimes_A X \cong W \otimes_B ( V \otimes_A X )
\]
\end{lemma}
\begin{proof}
This follows from the isomorphism
\begin{align*}
\Hom_A(W, \cat{C}^*(V \otimes_A X, -)) &\cong \Hom_A( W, \Hom_A^*(V, \cat{C}^*(X, -)))\\
&\cong \Hom_A(W \otimes_A V, \cat{C}^*(X, -))\,.
\end{align*}
\end{proof}

Now we specialise to the Clifford algebras $A_n$ and their modules.

\begin{lemma}\label{lemma:simplehom} Let $X$ be a $\mathbb{Z}_2$-graded left $A_n$-module. There is a $k$-linear isomorphism
\[
\Hom_{A_n}^0( S_n, X ) \cong \{ x \in X^0 \l a_i^\dagger \cdot x = 0 \text{ for all } 1 \le i \le n \}
\]
defined by $f \mapsto f(1)$. If $X$ is a right $A_n$-module there is a $k$-linear isomorphism
\[
\Hom^0_{A_n}( (S_n)^*, X ) \cong \{ x \in X^0 \l x \cdot a_i = 0 \text{ for all } 1 \le i \le n \}
\]
defined by $f \mapsto f(1^*)$.
\end{lemma}

\begin{lemma}\label{lemma:morphism_out_1} For an $A_n$-module $Y$ there is a $k$-linear isomorphism
\[
\cat{C}_{A_n}( S_n \otimes_k X, Y ) \cong \{ \delta: X \lto Y \l a_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
\]
defined by sending $\alpha: S_n \otimes_k X \lto Y$ to the composite
\[
\xymatrix@C+2pc{
X \cong k \otimes_k X \ar[r]^-{\iota \otimes 1} & S_n \otimes_k X \ar[r]^-{\alpha} & Y
}
\]
where $\iota: k \lto S_n$ is defined by $\iota(1) = 1$.
\end{lemma}
\begin{proof}
This follows from Lemma \ref{lemma:simplehom} and the isomorphism
\[
\cat{C}_{A_n}(S_n \otimes_k X, Y ) \cong \Hom_{A_n}( S_n, \cat{C}^*(X,Y) )\,.
\]
\end{proof}

More generally

\begin{lemma}\label{lemma:morphisms_two_forms} Let $X \in C_{A_p}$ and $Y \in \cat{C}_{A_q}$. There is a $k$-linear isomorphism
\begin{align*}
\cat{C}_{A_q}( S_{q,p} \otimes_{A_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ a_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ a_i^\dagger \circ \delta &= 0 \text{ for } 1 \le i \le q \}
\end{align*}
defined by sending $\alpha: S_{q,p} \otimes_{A_p} X \lto Y$ to the composite
\[
\xymatrix@C+2pc{
X \cong A_p \otimes_{A_p} X \ar[r]^-{\iota \otimes 1} & S_{q,p} \otimes_{A_p} X \ar[r]^-{\alpha} & Y
}
\]
where $\iota: A_p \lto S_{q,p}$ is defined by $\iota(1) = 1 \otimes 1^*$.
\end{lemma}
\begin{proof}
Using the previous lemma and Lemma \ref{lemma:simplehom},
\begin{align*}
\cat{C}_{A_q}( S_{q,p} \otimes_{A_p} X, Y ) &\cong \Hom^0_{A_p-A_q}( S_{q} \otimes_k S_p^* , \cat{C}^*(X,Y))\\
&\cong \Hom^0_{A_q}( S_q, \Hom^*_{A_p}( S_p^*, \cat{C}^*(X,Y) ))\\
&\cong \{ \delta \in \Hom^0_{A_q}( S_p^*, \cat{C}^*(X,Y) ) \l a_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
&\cong \{ \delta: X \lto Y \l \delta \circ a_i = 0 \text{ for } 1 \le i \le p \text{ and } a_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}
\end{align*}
as claimed.
\end{proof}

\section{Extending cut functors}\label{app:proof_cut_extension}

The purpose of this appendix is to give the proof of Proposition \ref{prop:extend_cut_functor}. First, note that

\begin{lemma}\label{lemma:altcomppersp} Let $\cat{C}$ be a small idempotent complete supercategory and take morphisms
\[
\xymatrix{
(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
}\\
\]
in $\cat{C}^\bullet$. Under \eqref{eq:isodefatensor} these correspond to bimodule maps
\[
\widetilde{\alpha}: S_{m,n} \lto \cat{C}^*(X,Y)\,, \qquad \widetilde{\beta}: S_{l,m} \lto \cat{C}^*(Y,Z)\,.
\]
The composite $\beta \circ \alpha: S_{l,n} \otimes_{A_n} X \lto Z$ in $\cat{C}^\bullet$ corresponds to the composite
\[
\xymatrix{
S_{l,n} \cong S_{l,m} \otimes_{A_m} S_{m,n} \ar[r]^-{\widetilde{\beta} \otimes \widetilde{\alpha}} & \cat{C}^*(Y,Z) \otimes_{A_m} \cat{C}^*(X,Y) \ar[r]^-{\circ} & \cat{C}^*(X,Z)
}\,.
\]
\end{lemma}
\begin{proof}
Follows by evaluation on $1 \otimes 1^* \in S_{l,n}$.
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:extend_cut_functor}]
Given $(X,n) \in \cat{C}_1^\bullet$ and $(Y,m) \in \cat{C}_2^\bullet$ we have $T(X,Y) = (Z,t)$ for some object $Z$ of $\cat{C}_3$. Given $a \in A_n$, say of odd degree, there is a morphism of $A_t$-modules $Z \lto \Psi Z$ given by
\[
\xymatrix@C+2pc{
T(X,Y) \ar[r]^-{T(a \otimes 1)} & T(\Psi X, Y ) \ar[r]^-{\tau} & \Psi T(X,Y)
}
\]
and this defines an algebra morphism $A_n \lto \cat{C}_3^*(Z,Z)$. Doing the same for $A_m$ defines a morphism $A_{m+t+n} \cong A_m \otimes A_t \otimes A_n \lto \cat{C}_3^*(Z,Z)$ and an object $(Z, m + t +n) \in \cat{C}_3^\bullet$. We define $\widetilde{T}$ on objects by
\begin{equation}\label{eq:ttilde}
\widetilde{T}( (X,n), (Y,m) ) = (Z, m + t + n)\,.
\end{equation}
Next we define $\widetilde{T}$ on morphisms. Given $\alpha: (X_1,n_1) \lto (X_2,n_2)$ in $\cat{C}_1^\bullet$ and $T(X_i,Y) = (Z_i,t)$ for $i = 1,2$ we must construct a morphism
\[
\widetilde{T}(\alpha,1): (Z_1, m+t+n_1) \lto (Z_2, m+t+n_2)\,.
\]
Since $\alpha$ corresponds to an $A_{n_1}$-linear map $\widetilde{\alpha}: V \lto \cat{C}_1^*(X_1,X_2)$ we can compose with $T$ to get an $A_{n_2}$-$A_{n_1}$-bilinear map $\eta := T(1,Y) \circ \widetilde{\alpha}: V \lto \cat{C}_3^*(Z_1,Z_2)$. This extends to a morphism of $A_{n_2+c}$-$A_{n_1+c}$-bimodules
\[
V \otimes_k A_c \lto \cat{C}_3^*(Z_1,Z_2), \qquad v \otimes a \mapsto \eta(v) a\,.
\]
There is a canonical isomorphism of $A_{n+2+c}$-$A_{n_1+c}$-bimodules
\begin{align*}
S_{n_2+c,n_1+c} \cong S_{n_2+c} \otimes_k S_{n_1+c}^* \cong (S_{n_2} \otimes_k S_c) \otimes_k (S_c^* \otimes_k S_{n_1}^*) \cong V \otimes_k (S_c \otimes_k S_c^*) \cong V \otimes_k A_c
\end{align*}
so we have constructed $S_{n_2+c,n_1+c} \lto \cat{C}_3^*(Z_1,Z_2)$ which corresponds to a morphism of $A_{n_2+c}$-modules $S_{n_2+c, n_1+c} \otimes_{A_{n_1+c}} Z_1 \lto Z_2$ which we define to be $\widetilde{T}(\alpha,1)$. Functoriality of this construction follows from Lemma \ref{lemma:altcomppersp}. The functoriality in the other variable follows similarly. By construction $\widetilde{T}$ makes both of the required diagrams commute.
\end{proof}

\section{Constructing superbicategories}\label{section:constructing_superbicategories}

This appendix collects the data needed for constructing a superbicategory $\cat{B}$ from a collection of supercategories $\cat{B}(a,b)$. Given a bicategory $\cat{B}$ and for each pair of objects $a,b$ the structure of a supercategory on $\cat{B}(a,b)$, we denote composition by
\[
T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
\]
We assume this is a superfunctor, i.e. that \eqref{eq:psicomp1}-\eqref{eq:psicomp3} commute. Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$. We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.

Suppose that for all objects $a,b,c$ we are given natural isomorphisms
\begin{align*}
T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T, \qquad T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
\end{align*}
both of which will be denoted $\tau$. We define for an object $a$ the $1$-morphism $\Psi_a = \Psi( \Delta_a )$ and the $2$-isomorphism $\xi_a$ to be the following composite (using the structure maps of $\cat{B}$ and isomorphisms $\tau$)
\[
\xi_a: \Psi_a \l \Psi_a = \Psi( \Delta_a ) \l \Psi( \Delta_a ) \cong \Psi( \Delta_a \l \Psi(\Delta_a ) ) \cong \Psi^2( \Delta_a \l \Delta_a ) \cong \Delta_a \l \Delta_a \cong \Delta_a\,.
\]
Similarly given a $1$-morphism $X: a \lto b$ we have a $2$-isomorphism $\gamma_X$
\[
\gamma_X: X \l \Psi_a = X \l \Psi( \Delta_a ) \cong \Psi( X \l \Delta_a ) \cong \Psi(X) \cong \Psi( \Delta_b \l X ) \cong \Psi( \Lambda_b ) \l X = \Psi_b \l X\,.
\]
Given a $1$-morphism $X: a \lto b$ in $\cat{B}$ there are diagrams
\begin{gather}
\xymatrix@R+1pc@C+1pc{
\Delta_b \l \Psi (X) \ar[dr]_-{\lambda_{\Psi a}} \ar[rr]^-{\tau} & & \Psi( \Delta_b \l X ) \ar[dl]^-{\Psi( \lambda )}\\
& \Psi(X)
} \label{eq:psiunitor1}\\
\xymatrix@R+1pc@C+1pc{
\Psi(X) \l \Delta_a \ar[rr]^-{\tau}\ar[dr]_-{\rho} & & \Psi( X \l \Delta_a ) \ar[dl]^-{\Psi(\rho)}\\
& \Psi(X)
} \label{eq:psiunitor2}
\end{gather}
whose commutativity expresses compatibility of the functors $\Psi$ with the units, while for a composable triple $X,Y,Z$ the commutativity of the diagrams
\begin{gather}
\xymatrix{
(Z \l Y) \l \Psi(X) \ar[dd]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( Y \l \Psi(X)) \ar[d]^-{\tau}\\
 & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
} \label{eq:psithirdlastdia}\\
\xymatrix{
(Z \l \Psi(Y)) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( \Psi(Y) \l X) \ar[d]^-{\tau}\\
\Psi( Z \l Y ) \l X \ar[d]_-{\tau} & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
} \label{eq:psimiddledia}\\
\xymatrix{
(\Psi(Z) \l Y) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & \Psi(Z) \l ( Y \l X ) \ar[dd]^-{\tau}\\
\Psi(Z \l Y) \l X \ar[d]_-{\tau} & & \\
\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
}\label{eq:psilastdia}
\end{gather}
expresses compatibility of $\Psi$ with the associator of $\cat{B}$.

\begin{lemma}\label{lemma:constructingsuper}
Given a bicategory $\cat{B}$ with the structure of a supercategory on $\cat{B}(a,b)$ for all pairs $a,b$, and natural isomorphisms $\tau$, suppose that \eqref{eq:psiunitor1}-\eqref{eq:psilastdia} commute. Then with $\Psi, \xi$ and $\gamma$ defined as above, $\cat{B}$ is a superbicategory.
\end{lemma}
\begin{proof}
The proof is an easy but somewhat lengthy exercise, which we omit.
\end{proof}

\section{Clifford actions and Koszul complexes}\label{section:cliffordactkos}
% spkos series

Let $R$ be a $\mathbb{Q}$-algebra and $(X,d)$ a linear factorisation of some $W \in R$. Let $t_1,\ldots,t_n$ be a sequence of elements of $R$ acting null-homotopically on $X$ and choose degree $-1$ operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$.

Letting $\theta_i$ be a formal variable of degree $-1$, we define the Koszul complex $(K,d_K)$ with underlying graded module the exterior algebra $K$ on the $\theta_i$, as in \eqref{defn:koszul}. The tensor product $K \otimes X = (K \otimes X, d + d_K)$ is another linear factorisation of $W$ and on the underlying graded module $K \otimes X$ we have operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$. We can define additional operators in terms of these by $\psi_k^* = \theta_k^*$ and
\begin{equation}
\psi_k = \theta_k - \sum_{m \ge 0} \sum_{q_1,\ldots,q_m} \frac{1}{(m+1)!} [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_k ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
\end{equation}
The appendix is taken up with the proof of:

\begin{theorem}\label{theorem:psik} The operators $\psi_k, \psi_k^*$ on $K \otimes X$ are closed and satisfy the Clifford relations
\begin{equation}\label{eq:clifford_reln_psi}
[ \psi_i, \psi_j ] = 0, \quad [ \psi_i^{*}, \psi_j^{*} ] = 0, \quad [ \psi_i, \psi_j^{*} ] = \delta_{ij}\,.
\end{equation}
\end{theorem}

We introduce the notation
\begin{align*}
\delta &= \sum_{i=1}^n \lambda_i \theta_i^*,\\
\exp(-\delta) &= \sum_{m \ge 0} (-1)^m \frac{1}{m!} \delta^m\,.
\end{align*}

\begin{proposition}\label{prop:equivalencekoszul} There are mutually inverse isomorphisms of linear factorisations
\[
\xymatrix@C+3pc{ (K \otimes X, d + d_K) \ar@<1ex>[r]^-{ \exp(\delta) } & (K \otimes X, d) \ar@<1ex>[l]^-{ \exp(-\delta) } }\,.
\]
\end{proposition}

Before we give the proof, we need the key observation that $[d, \delta] = \sum_i [d, \lambda_i] \theta_i^* = d_K$. More generally

\begin{lemma}\label{lemma:pert1} $[d, \delta^m] = m \delta^{m-1} d_K$ for $m \ge 1$.
\end{lemma}
\begin{proof}
\[
[ d, \delta^m ] = \sum_{i=0}^{m-1} \delta^i [d, \delta] \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i d_K \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i \delta^{m-i-1} d_K = m \delta^{m-1} d_K
\]
\end{proof}

\begin{lemma}\label{lemma:pert2} $[ d, \exp(-\delta) ] = - \exp(-\delta) d_K$ and $[ d, \exp(\delta) ] = \exp(\delta) d_K$.
\end{lemma}
\begin{proof}
We prove the first identity using Lemma \ref{lemma:pert1}, the second is the same:
\begin{align*}
[d, \exp(-\delta)] &= \sum_{m \ge 1} \frac{(-1)^m}{m!} [ d, \delta^m ]\\
&= \sum_{m \ge 1} \frac{(-1)^m}{m!} m \delta^{m-1} d_K\\
&= - \sum_{m \ge 0} \frac{(-1)^m}{m!} \delta^m d_K\\
&= - \exp(-\delta) d_K
\end{align*}
\end{proof}

\begin{proof}[Proof of Proposition \ref{prop:equivalencekoszul}]
It suffices to show $\exp(-\delta)$ is a morphism of linear factorisations. But using Lemma \ref{lemma:pert2}
\[
(d + d_K) \exp(-\delta) - \exp(-\delta) d = [d, \exp(-\delta)] + d_K \exp(-\delta) = 0
\]
and similarly for the other equation.
\end{proof}

The operators $\theta_i, \theta_i^*$ generate a Clifford action on the exterior algebra $K$ and therefore act via closed operators on $K \otimes X$. The $\psi_k, \psi_k^*$ are defined to be the translation of this Clifford structure to the $K \otimes X$ using the Proposition, i.e.
\begin{align}
\psi_k &= \exp(-\delta) \theta_k \exp(\delta), \label{eq:defn_psik1}\\
\psi_k^{*} &= \exp(-\delta) \theta_k^* \exp(\delta)\,. \label{eq:defn_psik2}
\end{align}

It remains to show that these operators have the form described prior to the statement of the theorem.

\begin{lemma} $\psi_k^{*} = \theta_k^*$ for $1 \le k \le n$.
\end{lemma}
\begin{proof}
Since $\delta$ commutes with $\theta_k^*$, $\exp(-\delta) \theta_k^* = \theta_k^* \exp(-\delta)$.
\end{proof}

However the operator $\theta_k$ is not closed, indeed $[ \theta_i, d + d_K ] = t_i$, and so giving a closed formula for $\psi_k^*$ is more involved. In the development below we fix an index $k$. To compute $\psi_k$ the strategy is to commute $\theta_k$ past $\exp(-\delta)$. To this end we must first compute $[\theta_k, \delta^m]$ and then $[\theta_k, \exp(-\delta)]$. The calculation begins
\begin{equation}\label{eq:catfish}
[ \theta_k, \delta^m ] = \sum_{p=0}^{m-1} \delta^p [ \theta_k, \delta ] \delta^{m-p-1} = - \sum_{p=0}^{m-1} \delta^p [ \delta, \theta_k ] \delta^{m-p-1}\,.
\end{equation}
We need to understand how to commute $\delta^p$ past the $[ \delta, \theta_k ]$. The following notation will be used for any elements of $a,b$ of a graded ring and $m \ge 1$
\[
[b, a]^{(m)} = [b, [b, [b, \cdots [b, a] \dots ]
\]
where there are $m$ occurrences of $b$. By convention $[b,a]^{(0)} = a$.

\begin{lemma} $b^m [b, a] = \sum_{i+j=m} \binom{m}{i} [b,a]^{(i+1)} b^j$ for $m \ge 1$.
\end{lemma}
\begin{proof}
By induction, with the case $m = 1$ being clear. Using the inductive hypothesis
\[
b^{m+1} [b, a] = \sum_{i+j=m} \binom{m}{i} b [b,a]^{(i+1)} b^j = \sum_{i+j=m} \binom{m}{i} \Big[ [b,a]^{(i+2)} b^j + [b,a]^{(i+1)} b^{j+1} \Big]\,.
\]
The powers of $b$ range from $0$ to $m+1$ and the coefficient of $b^j$ for $1 \le j \le m$ is
\[
\binom{m}{m-j} [b,a]^{(m-j+2)} + \binom{m}{m-j+1} [b,a]^{(m-j+2)} = \binom{m+1}{m+1-j} [b,a]^{(m-j+2)}\,.
\]
The coefficient of $b^0$ is $[b,a]^{(m+2)}$ and the coefficient of $b^{m+1}$ is $[b,a]^{(1)}$, so we are done.
\end{proof}

From the previous lemma we deduce that
\begin{equation}\label{eq:calc1}
\delta^p [ \delta, \theta_k ] = \sum_{i+j=p} \binom{p}{i} [ \delta, \theta_k ]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [ \delta, \lambda_k ]^{(i)} \delta^j\,.
\end{equation}
The next thing to compute is $[ \delta, \lambda_k ]^{(i)}$ for any $i$. For a tuple $\bold{q} = (q_1,\ldots,q_m)$ of integers between $1$ and $n$ we write (remembering that $k$ is fixed)
\begin{gather*}
\tau_{\bold{q}} = [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \lambda_k ] \cdots ]\\
\theta_{\bold{q}}^* = \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
\end{gather*}

\begin{lemma} For $m \ge 0$
\[
[ \delta, \lambda_k ]^{(m)} = (-1)^m \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m}\,.
\]
\end{lemma}
\begin{proof}
By the inductive hypothesis
\begin{align*}
[\delta, \lambda_k]^{(m+1)} &= [ \delta, [ \delta, \lambda_k ]^{(m)} ]\\
&= (-1)^m \sum_{\bold{q}} [ \delta, \tau_{\bold{q}} \theta_{\bold{q}}^* ]\\
&= (-1)^m \sum_{\bold{q}, q_{m+1}} [ \lambda_{q_{m+1}} \theta_{q_{m+1}}^*, \tau_{\bold{q}} \theta_{\bold{q}}^* ]\\
&= (-1)^m \sum_{\bold{q}, q_{m+1}} \big( \lambda_{q_{m+1}} \theta_{q_{m+1}}^* \tau_{\bold{q}} \theta_{\bold{q}}^* + \tau_{\bold{q}} \theta_{\bold{q}}^* \lambda_{q_{m+1}} \theta_{q_{m+1}}^* \big)\\
&= (-1)^m \sum_{\bold{q}, q_{m+1}} \big( -\lambda_{q_{m+1}} \tau_{\bold{q}}  \theta_{\bold{q}}^* \theta_{q_{m+1}}^* + (-1)^m \tau_{\bold{q}} \lambda_{q_{m+1}} \theta_{\bold{q}}^* \theta_{q_{m+1}}^* \big)\\
&= (-1)^{m+1} \sum_{\bold{q}, q_{m+1}} [ \lambda_{q_{m+1}}, \tau_{\bold{q}} ] \theta_{\bold{q}}^* \theta_{q_{m+1}}^*
\end{align*}
as claimed.
\end{proof}

Continuing the computation of \eqref{eq:calc1} we have
\begin{equation}
\label{eq:calc2}
\delta^p [\delta, \theta_k ] = \sum_{i+j=p} \binom{p}{i} (-1)^i \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^j\,.
\end{equation}

\begin{lemma}\label{lemma:commutator_wha} For $m \ge 1$
\[
[ \theta_k, \delta^m ] = \sum_{i=0}^{m-1} (-1)^{i+1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^{m-i-1}
\]
\end{lemma}
\begin{proof} 
Beginning from \eqref{eq:catfish}
\begin{align*}
[ \theta_k, \delta^m ] &= - \sum_{p=0}^{m-1} \delta^p [ \delta, \theta_k ] \delta^{m-p-1}\\
&= - \sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} (-1)^i \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^j \delta^{m-p-1}
\end{align*}
\end{proof}

\begin{lemma}\label{lemma:combin} For integers $a, b \ge 0$
\begin{equation}\label{eq:combin}
\frac{b!}{(a+b+1)!} \sum_{a \le m \le a + b} \binom{m}{a} = \frac{1}{(a+1)!}
\end{equation}
\end{lemma}
\begin{proof}
Denoting the left hand side of \eqref{eq:combin} by $\Omega_{a,b}$ the proof is an induction on $b$, i.e. by computing $\Omega_{a,b+1}$ in terms of $\Omega_{a,b}$.
\end{proof}

\begin{lemma}
\[
[\theta_k, \exp(-\delta)] = \sum_{m \ge 0} \frac{1}{(m+1)!} \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m} \exp(-\delta)\,.
\]
\end{lemma}
\begin{proof}
Using Lemma \ref{lemma:combin} and Lemma \ref{lemma:commutator_wha}
\begin{align*}
[\theta_k, \exp(-\delta)] &= \sum_{m \ge 0} \frac{(-1)^m}{m!} [\theta_k, \delta^m]\\
&= \sum_{m \ge 0} \sum_{i=0}^{m-1} (-1)^{i+m+1} \frac{1}{m!} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^{m-i-1}\\
&= \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{(t+1+i)!} \sum_{i \le p \le t + i} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^t\\
&= \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{t!} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^t\\
&= \sum_{m \ge 0} \frac{1}{(m+1)!} \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m} \exp(-\delta)\,.
\end{align*}
\end{proof}

\begin{proof}[Proof of Theorem \ref{theorem:psik}] 
\begin{align*}
\psi_k &= \exp(-\delta) \theta_k \exp(\delta)\\
&= \theta_k \exp(-\delta) \exp(\delta) + [ \exp(-\delta), \theta_k ] \exp(\delta)\\
&= \theta_k - [ \theta_k, \exp(-\delta) ] \exp(\delta)\\
&= \theta_k - \sum_{i \ge 0} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \exp(-\delta) \exp(\delta)\\
&= \theta_k - \sum_{i \ge 0} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} 
\end{align*}
which completes the proof.
\end{proof}

\bibliographystyle{amsalpha}
\providecommand{\bysame}{\leavevmode\hbox to3em{\hrulefill}\thinspace}
\providecommand{\href}[2]{#2}
\begin{thebibliography}{BHLS03}

% reference for \lambda-calculus
% reference for cut
% geometry of interaction

\bibitem{barneslambe}
D.~W.~Barnes and L.~A.~Lambe, \emph{A fixed point approach to homological perturbation theory}, Proc. Amer.
  Math. Soc. \textbf{112} Number 3 (1991), 881--892.

\bibitem{bor94}
F.~Borceux, \textsl{Handbook of categorical algebra $1$}, volume $50$ of \textsl{Encyclopedia of Mathematics and its Applications}, Cambridge University Press, Cambridge, 1994.

\bibitem{buchweitz_flenner}
R.-O.~Buchweitz and H.~Flenner, \textsl{A semiregularity map for modules and applications to deformations}, Compositio Math. \textbf{137} (2003), 135--210.

\bibitem{ct1007.2679}
A.~{C\u ald\u araru} and S.~Willerton, \textsl{The Mukai pairing, I: a categorical approach},
New York Journal of Mathematics \textbf{16} (2010), 61--98, 
  \href{http://arxiv.org/abs/0707.2052}{[arXiv:0707.2052]}.

\bibitem{khovhompaper}
N.~Carqueville and D.~Murfet, \textsl{Computing {K}hovanov-{R}ozansky homology and defect fusion}, Algebraic \& Geometric Topology \textbf{14} (2014), 489--537, \href{http://arxiv.org/abs/1108.1081}{[arXiv:1108.1081]}.

\bibitem{lgdual}
N.~Carqueville and D.~Murfet, \textsl{Adjunctions and defects in {L}andau-{G}inzburg models}, \href{http://arxiv.org/abs/1208.1481}{[arXiv:1208.1481]}.

\bibitem{lgdual_survey}
N.~Carqueville and D.~Murfet, \textsl{A toolkit for defect computations in Landau-Ginzburg models}, \href{http://arxiv.org/abs/1303.1389}{[arXiv:1303.1389]}, contribution to the String-Math 2012 proceedings.

\bibitem{ade}
N.~Carqueville, A.~Ros Camacho and I.~Runkel, \textsl{Orbifold equivalent potentials}, \href{http://arxiv.org/abs/1311.3354}{[arXiv:1311.3354]}.

\bibitem{cr0909.4381}
N.~Carqueville and I.~Runkel, \textsl{On the monoidal structure of matrix bi-factorisations}, J. Phys.
  A: Math. Theor. \textbf{43} (2010), 275401,
  \href{http://arxiv.org/abs/0909.4381}{[arXiv:0909.4381]}.

\bibitem{crainic}
M.~Crainic, \emph{On the perturbation lemma, and deformations}, \href{http://arxiv.org/abs/math/0403266}{[arXiv:0403266]}

\bibitem{d0904.4713}
T.~Dyckerhoff, \textsl{Compact generators in categories of matrix factorizations},
  Duke Math. J. \textbf{159} (2011), 223--274,
  \href{http://arxiv.org/abs/0904.4713}{[arXiv:0904.4713]}.

\bibitem{dm1102.2957}
T.~Dyckerhoff and D.~Murfet, \textsl{Pushing forward matrix factorisations}, Duke Math. J. \textbf{162} (2013), 1249--1311, \href{http://arxiv.org/abs/1102.2957}{[arXiv:1102.2957]}.

\bibitem{ellis_lauda}
A.~Ellis and A.~Lauda, \textsl{An odd categorification of $U_q(\mathfrak{sl}_2)$}, \href{http://arxiv.org/abs/1307.7816}{[arXiv:1307.7816]}.

\bibitem{enderton}
H.~B.~Enderton, \textsl{Elements of recursion theory}, Handbook of Mathematical Logic, North-Holland (1977) 527--566.

\bibitem{friedrich}
T.~Friedrich, \textsl{{D}irac operations in {R}iemannian geometry}, Graduate studies in mathematics \textbf{25}, AMS (1997).

\bibitem{gentzen}
G.~Gentzen, \textsl{The Collected Papers of Gerhard Gentzen}, (Ed. M. E. Szabo), Amsterdam, Netherlands: North-Holland, 1969.

\bibitem{girard_llogic}
J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.

\bibitem{girard_towards}
J.-Y.~Girard, \textsl{Towards a geometry of interaction}, In J.~W.~Gray and A.~Scedrov, editors, Categories in Computer Science and Logic, volume 92 of Contemporary Mathematics, 69--108, AMS (1989).

\bibitem{greuel}
G.-M.~Greuel, C.~Lossen and E.~Shustin, \textsl{Introduction to singularities and deformations}, Springer (2007).

\bibitem{kang}
S.-J.~Kang, M.~Kashiwara and S.-J.~Oh, \textsl{Supercategorification of quantum Kac-Moody algebras}, Adv. Math \textbf{242} (2013) 116--162, \href{http://arxiv.org/abs/1206.5933}{[arXiv:1206.5933]}.

\bibitem{kang2}
S.-J.~Kang, M.~Kashiwara and S.-J.~Oh, \textsl{Supercategorification of quantum Kac-Moody algebras II}, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.

\bibitem{Calinetal}
C.~I. Lazaroiu and D.~McNamee, unpublished.

\bibitem{McNameethesis}
D.~McNamee, \textsl{On the mathematical structure of topological defects in
  {L}andau-{G}inzburg models}, MSc Thesis, Trinity College Dublin, 2009.

\bibitem{cutsystems2}
D.~Murfet, \textsl{Computing with cut systems II: linear logic}, in progress.

\bibitem{selinger}
P.~Selinger, \textsl{Lecture notes on the {L}ambda calculus}, \href{http://arxiv.org/abs/0804.3434}{[arXiv:0804.3434]}.

\bibitem{vistoli}
A.~Vistoli, \textsl{Notes on {G}rothendieck topologies, fibered categories and descent theory}, \href{http://arxiv.org/abs/math/0412512}{[arXiv:0412512]}.

\bibitem{yoshino98}
Y.~Yoshino, \textsl{Tensor products of matrix factorizations}, Nagoya Math. J.
  \textbf{152} (1998), 39--56.

\end{thebibliography}

\end{document}

### 2015-03-02 cutsystems_cuts.tex
Initial commit.

%There is a bicategory $\cat{V}$ of smooth projective algebraic varieties over $\mathbb{C}$ \cite{??}, where the $1$-morphisms between varieties $\md{x}: A \lto B$ are Fourier-Mukai kernels, that is, complexes of coherent sheaves $\md{X}$ on the product $A \times B$.

%For example, let $B = Proj(A)$ for some graded algebra $A = k[x_1,\ldots,x_n]/I$, and let $\md{X}, \md{Y}$ be complexes of vector bundles on $B$. In the bicategory $\cat{V}$ there are $1$-morphisms
%\[
%\xymatrix@C+2pc{
%\operatorname{pt} \ar[r]^-{\md{X}} & B \ar[r]^-{\md{Y}^{\vee}} & \operatorname{pt}
%}
%]
%where $\operatorname{pt} = \Spec(\mathbb{C})$. The composite in $\cat{V}$ is the complex
%\begin{equation}\label{eq:infinite_tensor_scheme}
%y^{\vee} \otimes^{\mathbb{L}} x = \md{Y}^{\vee} \otimes^{\mathbb{L}} \md{X} \cong 
%\end{equation}
%which is infinite-dimensional but has finite-dimensional cohomology.

%Suppose that $\md{X}, \md{Y}$ are finitely described, for example that $X, Y$ are complexes of finitely generated graded free $A$-modules and $\md{X}, \md{Y}$ the associated complexes of sheaves, which are therefore described in terms of finite lists of matrices of homogeneous polynomials.

\subsection{Splitting homotopies from connections}

We now develop the splitting homotopy of Example \ref{example:koszulsplit} in its most general form, in terms of Koszul complexes and connections. The splittings homotopies in this paper will all be derived as perturbations of these ``connection type'' examples. The material in the next two sections is from \cite{??}, we quote it here for the reader's convenience.

Let $k$ be a $\mathbb{Q}$-algebra and $R$ a $k$-algebra, $t_1,\ldots, t_n$ a quasi-regular sequence in $R$ such that $\bar{R} = R/(t_1,\ldots,t_n)$ is a finitely generated free $k$-module and $R$ admits a flat $k$-linear connection which is standard in the sense of \cite{??}
\[
\nabla: R \lto R \otimes_{k[t]} \Omega^1_{k[t]/k}
\]
and has the property that $\Ker(\nabla) + (t_1,\ldots,t_n) R = R$. With $\theta_i$ a formal variable of degree $-1$ the Koszul complex $K = K(t_1,\ldots,t_n)$ (see Definition \ref{defn:koszul}) has as its underlying graded module the exterior algebra on the $\theta_i$.

The connection $\nabla$ extends canonically to an operator on $R \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra. By identifying $d t_i$ with the generator $\theta_i$ of $K$ we may identify this tensor product with $K$ itself, so that $\nabla$ becomes a degree $-1$ $k$-linear operator on $K$. It is straightforward to check that the operator $[d_K, \nabla]$ is invertible on the graded submodule $K_{\le -1}$ of nonzero degree terms, and we define
\[
H = [d_K, \nabla]^{-1} \nabla\,.
\]

\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $K$.
\end{proposition}
\begin{proof}
See \cite[Section 8.1]{papertoby}.
\end{proof}

The associated strong deformation retract of $\mathbb{Z}$-graded $k$-complexes is
\begin{equation}\label{eq:originalHdef}
\xymatrix@C+2pc{
(\bar{R},0) \ar@<-1ex>[r]_{\sigma} & (\Lambda, d_K), \ar@<-1ex>[l]_{\pi}
} \quad H
\end{equation}
where $\pi: K \lto \bar{R}$ is the canonical $R$-linear quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $R \lto \bar{R}$, and $\sigma$ is a $k$-linear embedding of $\bar{R}$ into $R$ uniquely determined by the choice of connection.

\begin{remark} There is some flexibility to beginning with a connection rather than assuming that $R$ is a free $k[t]$-module, but this complication is not essential: the above is a very slight generalization of the simplest example, where $R = k[t]$ itself, $\nabla$ is the K\"ahler differential, and for a homogeneous polynomial $f \in k[t]$ and homogeneous tensor $\omega$
\[
[d_K, \nabla]^{-1}(f \omega) = \frac{1}{|f| + |\omega|} f \omega 
\]
and hence
\[
H( f \omega ) =  \frac{1}{|f| + |\omega|} \sum_i \partial_{t_i} (f) \theta_i \wedge \omega\,.
\]
In this case $\sigma$ is just the embedding of $k$ as the constant polynomials in $k[t]$.
\end{remark}

\subsection{Splitting homotopies on matrix factorisations}

With the notation of the previous section let $(X,d_X)$ be a finite rank matrix factorisation over $R$ of some $W \in k$. That is, $X$ is a finite rank free $R$-module and $d_X$ is $R$-linear, and the potential $W$ is in the image of the structure map $k \lto R$. The aim is to present $X \otimes K$ as being $k$-homotopy equivalent to a finite rank matrix factorisation over $k$, using a splitting homotopy on $X \otimes K = (X \otimes \Lambda, d_X + d_K)$ obtained via the perturbation lemma from a splitting homotopy on $(X \otimes \Lambda, d_K)$, viewing $d_X$ as a perturbation on the latter.

Choosing a homogeneous $R$-basis allows us to write $X \cong V \otimes_k R$ for some $\mathbb{Z}_2$-graded free $k$-module $V$, in which case
\begin{equation}\label{eq:lambdaiso2}
X \otimes \Lambda \cong (V \otimes_k R) \otimes_R \Lambda \cong V \otimes_k \Lambda
\end{equation}
In this way, using the basis, the $k$-linear splitting homotopy $H$ on $K = (\Lambda, d_K)$ gives rise to a $k$-linear operator $1 \otimes H$ on $X \otimes \Lambda$, which we again denote by $H$.

\begin{lemma} $H$ is a $k$-linear splitting homotopy on the complex $(X \otimes \Lambda, d_K)$.
\end{lemma}

The associated strong deformation retract is
\[
\xymatrix@C+2pc{
(\bar{X},0) \ar@<-1ex>[r]_-{\sigma} & (X \otimes \Lambda, d_K), \ar@<-1ex>[l]_-{\pi}
} \quad H
\]
where $\bar{X} = X / (t_1,\ldots,t_n)X = X \otimes_R \bar{R}$, $\pi$ is $R$-linear induced by the map $\pi: K \lto \bar{R}$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.

We now view $\tau = d_X$ as a perturbation of $(X \otimes \Lambda, d_K)$. Naturally $(d_K + \tau)^2 = W$, so that the potential is changed by this perturbation. The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $X \otimes K = (X \otimes \Lambda, d_K + d_X)$ in such a way that the underlying graded module is $\bar{X}$. Since $H d_X$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
\[
\phi_\infty = \sum_{m \ge 0} (-1)^m (H d_X)^m H
\]
is a $k$-linear splitting homotopy achieving the desired aim.

The next result is \cite[Proposition 7.1]{??}.

\begin{corollary} $\phi_\infty$ is a $k$-linear splitting homotopy on $X \otimes K$ and the associated $k$-linear strong deformation retract of linear factorisations of $W$ is of the form
\begin{equation}
\xymatrix@C+2pc{
(\bar{X},d_X) \ar@<-1ex>[r]_-{\sigma_\infty} & (X \otimes \Lambda, d_X + d_K), \ar@<-1ex>[l]_-{\pi}
} \quad \phi_\infty
\end{equation}
where $A = d_X( 1 + H d_X )^{-1}$ and $\sigma_\infty = \sigma - H A \sigma$.
\end{corollary} 
\begin{proof}
We need only justify why in \eqref{eq:perturbedsdr} we have $d_\infty = d_X$ and $f_\infty = \pi$. But this follows from $H \sigma = 0$ and $\pi H = 0$.
\end{proof}

### 2015-08-29 cutsystems-new.tex
New version of cut systems paper.

--- 2015-03-02 cutsystems.tex
@@
+% TODO
+% - fix the equivalence of L with LG
+% - add stuff to the example
+
 \documentclass[english,letter paper,12pt,leqno]{article}
@@
 \usepackage[all]{xy}
+\usepackage{dsfont}
 \usepackage{tikz}
@@
 \newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{setup}[theorem]{Setup}
 
@@
 	\newtheorem{remark}[theorem]{Remark}
+	\newtheorem{strat}[theorem]{Strategy}
 
@@
 \def\Modd{\operatorname{Mod}}
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\nN{\mathds{N}}
+\def\nZ{\mathds{Z}}
+\def\nQ{\mathds{Q}}
+\def\nR{\mathds{R}}
+\def\nC{\mathds{C}}
 \DeclareMathOperator{\Ext}{Ext}
@@
 
-\title{Computing with cut systems}
+\title{Computing with cut systems +}
 \author{Daniel Murfet}
@@
 
+\tableofcontents
+
 \section{Introduction}
 
-In this paper we develop a new semantics of composition using a bicategorical formalism that we call \emph{cut systems}, inspired by Gentzen's cut-elimination \cite{gentzen} and Girard's geometry of interaction \cite{girard_towards}.
-The formalism is used to ``make computable'' a bicategory of isolated hypersurface singularities and matrix factorisations that has been studied in the context of topological field theory \cite{McNameethesis, cr0909.4381}.
-This means that the operations making up the data of the bicategory are given algorithmically, and can be implemented on a computer.
-One of the main applications, to be given in a sequel \cite{cutsystems2}, is to construct a model of a fragment of Girard's linear logic \cite{girard_llogic}.
-Roughly speaking, this provides mathematical semantics for a programming language in which data types are interpreted as hypersurface singularities, and programs are interpreted as homotopy equivalence classes of matrix factorisations.
-
-What is a semantics of composition? Consider that in a category or bicategory $\cat{A}$, for every triple of objects $a,b,c$ and morphisms
-\[
-\xymatrix@C+2pc{
-a \ar[r]^-{\Phi} & b \ar[r]^-{\Psi} & c
-}
-\]
-there is an assignment to $(\Psi, \Phi)$ of a composition $\Psi \circ \Phi$.
-A \emph{semantics of composition} for $\cat{A}$ is a mathematical construct providing some kind of inner structure for this ``assignment'' which is coherent as $a,b,c,\Phi,\Psi$ vary.
-The main examples of this kind of semantics are in computer science and mathematical logic.
-
-For example, suppose that $\cat{A}$ is the category of sets and that we have functions
-\[
-\xymatrix@C+2pc{
-\mathbb{N} \ar[r]^-{\Phi} & \mathbb{N} \ar[r]^-{\Psi} & \mathbb{N}
-}
-\]
-where $\Phi$ and $\Psi$ are ``finitely described'' in the sense that they are computed by algorithms $X$ and $Y$, respectively.
-To be explicit, let us take $X,Y$ to be terms in the $\lambda$-calculus \cite{selinger}.
-If $[-]$ denotes assignment to an algorithm of the function it describes, then $\Phi = [X], \Psi = [Y]$ and $\Psi \circ \Phi = [Y \l X]$ where $Y \l X$ is the result of feeding the output of the algorithm $X$ as an input to the algorithm $Y$.
-In the logic literature this concatenation is known as a \emph{cut}.\footnote{We note that the notation $Y \l X$ for the cut is not standard, so don't blame the logicians for it.} To encounter the desired semantics we need the additional observation that the cut $Y \l X$ is not in normal form (whatever this means) but it may be reduced to normal form by a rewriting process on terms in the $\lambda$-calculus called $\beta$-reduction.
-This does not change the associated function: the normal form of $Y \l X$ also computes $\Psi \circ \Phi$.
-
-A semantics of composition for the category of computable functions is then given by the process which begins with the pair $(Y,X)$ of finite descriptions of $\Psi,\Phi$, forms the cut $Y \l X$, and then computes a normal form giving a finite description of $\Psi \circ \Phi$.
-
-\medskip
-
-This seems very far from geometry, but we can informally recast a problem of algebraic geometry in a similar light.
-Suppose $A,B,C$ are smooth projective algebraic varieties and that we are given triangulated functors between derived categories of coherent sheaves
-\[
-\xymatrix{
-\mathbf{D}^b(A) \ar[r]^-{\Phi} & \mathbf{D}^b(B) \ar[r]^-{\Psi} & \mathbf{D}^b(C)
-}\,.
-\]
-Suppose that $\Phi,\Psi$ are finitely described, in the sense that they are both integral functors associated to kernels: $\Phi$ is convolution with a complex of coherent sheaves $X$ on $A \times B$, and $\Psi$ is convolution with a complex $Y$ on $B \times C$.
-If for example $A,B,C$ are the $\operatorname{Proj}$ of graded algebras, $X$ and $Y$ can be described by lists of matrices of homogeneous polynomials.
-An obvious question is: what is the finite description of the functor $\Psi \circ \Phi$?
-
-It is easy to see that $\Psi \circ \Phi$ is convolution with the kernel $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$, which is a complex of quasi-coherent sheaves on $A \times C$ with coherent cohomology, but this is not described by a finite amount of data.
-Finding a finite description of $\Psi \circ \Phi$ is precisely the problem of determing the complex of coherent sheaves which is isomorphic, in $\mathbf{D}^b(A \times C)$, to $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$.
-We refer to such a complex of coherent sheaves as a \emph{finite model} of $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$.
-
-Consider the case where $A = C = \operatorname{Spec}(\mathbb{C})$, so $X,Y$ are complexes of coherent sheaves on $B$ and $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X \cong \mathbb{R}\!
-\operatorname{Hom}_{\cat{O}_B}(Y^{\vee}, X)$ is a complex of infinite-dimensional vector spaces with finite-dimensional cohomology.
-An example of a finite model is an isomorphism in the derived category of all $\mathbb{C}$-vector spaces of this complex with its cohomology
-\begin{equation}\label{eq:computing_hom_derived}
-Y \otimes^{\mathbb{L}}_{\cat{O}_B} X \cong \bigoplus_{n \in \mathbb{Z}} \Ext^n(Y^{\vee},X)[-n]\,.
-\end{equation}
-One finite description of $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$, and transitively of $\Psi \circ \Phi$, is therefore a list of numbers: the dimensions of the vector spaces on the right hand side of \eqref{eq:computing_hom_derived}.
-Determining these numbers is difficult, to put it mildly: a fundamental problem in algebraic geometry is to understand how these numbers depend on the input data $X$ and $Y$.
-
-By a (perhaps naive) analogy with computable functions, one might wonder if in the general case there exists an object $Y \l X$ in some triangulated category together with a reduction process that would help find a finite description for $\Psi \circ \Phi$.
-This is the question of whether or not there is a semantics of composition in the bicategory of smooth projective varieties and Fourier-Mukai kernels \cite{ct1007.2679}.
-Unfortunately, we do not know such a theory!
-
-However, it turns out that there \emph{is} a satisfactory semantics of this kind when instead of smooth projective varieties we consider isolated hypersurface singularities $W,V,U$ and triangulated functors between homotopy categories of matrix factorisations \cite{yoshino98}
-\begin{equation}\label{eq:pair_functors_hmf}
-\xymatrix{
-\hmf(W) \ar[r]^-{\Phi} & \hmf(V) \ar[r]^-{\Psi} & \hmf(U)
-}\,.
-\end{equation}
-To explain further, we need to introduce the language of cut systems.
-
-\medskip
-
-A \emph{cut system} $\cat{A}$ over a $\mathbb{Q}$-algebra $k$ has a class of objects and for each pair $a,b$ of objects a $k$-linear supercategory $\cat{A}(a,b)$.
-Informally, one should think of this as a category of finite models.
-There is an operation on $\cat{A}$, the \emph{cut}, which assigns to $X \in \cat{A}(a,b)$ and $Y \in \cat{A}(b,c)$ a representation $Y \l X$ in $\cat{A}(a,c)$ of a Clifford algebra which depends on the intermediate object $b$.
-The object $Y \l X$ and the endomorphisms giving the Clifford action are required to be effectively computable, say by explicit formulas, from the input data $X,Y$.
-In the example of a cut system developed in this paper, Clifford algebras arise as endomorphism algebras of exterior algebras, which in turn arise as the underlying graded modules of Koszul complexes.
-Associated to the cut system $\cat{A}$ is a bicategory $\cat{A}^\bullet$ in which the composition is derived from the cut operation, and so is also effectively computable.
-
-A \emph{cut model} of a bicategory $\cat{B}$ is a cut system $\cat{A}$ with the same objects as $\cat{B}$, together with an equivalence $I: \cat{B} \lto \cat{A}^\bullet$.
-There are fully faithful functors $I: \cat{B}(a,b) \lto \cat{A}(a,b)$ which we think of as assigning finite models to the $1$-morphisms of $\cat{B}$, and an isomorphism of Clifford representations for every composable pair of $1$-morphisms $X,Y$ in $\cat{B}$, where $S$ denotes the spinor representation:
-\begin{equation}\label{eq:intro_cut_semantics}
-I(Y) \l I(X) \cong S \otimes_k I( Y \circ X )\,.
-\end{equation}
-The cut model provides $\cat{B}$ with a semantics of composition: given finite models $I(X), I(Y)$ of $X,Y$ there is a process beginning with the cut $I(Y) \l I(X)$ which extracts the subobject $I(Y \circ X)$ using the Clifford action.
-The result $I( Y \circ X )$ of this computation is the desired finite model of the composition $Y \circ X$ in $\cat{B}$.
-\medskip
-
-The formalism is adapted to, and motivated by, an example: the bicategory of Landau-Ginzburg models $\LG$.
-Let us return to the diagram \eqref{eq:pair_functors_hmf} as our starting point.
-There is an analogue of integral functors in this setting, so that it makes sense to talk about $\Phi$ and $\Psi$ as being respectively given by convolution with kernels $X,Y$.
-If $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$ define isolated hypersurface singularities then $X$ is a finite rank matrix factorisation of $V - W$ over $k[x,z]$, and similarly for $Y$.
-
-Again, the question is: what is the finite description of $\Psi \circ \Phi$?
-It is naturally given by convolution with a matrix factorisation $Y \otimes X$ which is not finitely generated: finding a finite description of $\Psi \circ \Phi$ therefore amounts to finding a finite model for $Y \otimes X$.
-To fit this into the formalism of cut systems, we use the  bicategory $\LG$ in which the objects are isolated hypersurface singularities\footnote{Roughly speaking.
-See Section \ref{section:superbicatLG}.} and $1$-morphisms $W \lto V$ are matrix factorisations of $V - W$.
-In this bicategory, the finite descriptions of the functors in \eqref{eq:pair_functors_hmf} give rise to a composable pair of $1$-morphisms
-\begin{equation}\label{eq:cut_lg}
-\xymatrix@C+2pc{
-W \ar[r]^-{X} & V \ar[r]^-{Y} & U
-}\,.
-\end{equation}
-whose composition in $\LG$ is the tensor product $Y \otimes X$.
-
-The main results of this paper are the construction of a cut sytem $\cat{L}$ and cut model $I: \LG \lto \cat{L}^\bullet$.
-In the situation of \eqref{eq:cut_lg} $X$ and $Y$ are their own finite model (so $I(X) = X$ and $I(Y) = Y$) and a finite model of the composite $Y \otimes X$ in $\cat{B}$ may be computed from the cut $Y \l X$ in $\cat{L}$, which is an explicitly given finite rank matrix factorisation of $U - W$ together with a Clifford action described in terms of derivatives of the differentials of $X,Y$ and certain invariants called Atiyah classes.
-
-One consequence is that $\LG$ is equivalent to the bicategory $\cat{L}^\bullet$, which is \emph{computable} in the sense that its operations may be embodied in software.
+The bicategory of Landau-Ginzburg models $\LG$ has polynomials $W(x)$ called \textsl{potentials} as its objects, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
+This bicategory has been studied extensively in connection with topological field theory \cite{??} and knot invariants \cite{??}.
+The most important and nontrivial structure in this bicategory is the functor
+\be\label{eq:intro_functor_comp}
+\LG(V,U) \otimes_{\nC} \LG(W, V) \lto \LG(W,U)
+\ee
+which composes $1$-morphisms for potentials $W(x),V(y),U(z)$.
+Continuing the approach developed with Dyckerhoff in \cite{??}, the aim of this paper is to explicitly describe this functor.
+Any increase in our understanding of the operation of composition in $\LG$ has implications for the subjects where this bicategory makes an appearance, but our primary application is to the semantics of linear logic constructed in \cite{??}.
+
+\begin{itemize}
+\item We define another bicategory without units $\cat{L}$
+\item We prove $\cat{L}$ is equivalent to $\LG$
+\item We show how to model $\cat{L}$ in schemes (next paper)
+\end{itemize}
+
+First of all, let us be more precise about the kind of explicit description we are looking for.
+Observe that once we have chosen a homogeneous basis, a matrix factorisation of $W(x) - V(y)$ is just a matrix of polynomials
+\[
+D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (W(x) - V(y)) \cdot I_{2r}\,.
+\]
+If we fix the rank $r$ and bound the degrees of the monomials appearing in $D$ by some integer $k$, it is easy to parametrise such matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$.
+Then the set of objects of $\LG(W,V)$ can be described as a disjoint union of inductive limits of these schemes
+\[
+\operatorname{ob} \LG(W,V) = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)\,.
+\]
+The kind of explicit description we are looking for is a lifting of the function \eqref{eq:intro_functor_comp} on the level of objects to a morphism of schemes
+\be\label{eq:composition_as_schememap}
+\mathscr{M}_{r',k'}(V,U) \times \mathscr{M}_{r,k}(W,V) \lto \mathscr{M}_{f(r,r'),g(k,k')}(W, U)\,.
+\ee
+Unfortunately this appears difficult, if not impossible, as stated.
+In this article we explain how the replacement of $\LG(W,U)$ by an equivalent category $\cat{L}(W,U)$, called the \textsl{Clifford thickening}, allows for such a lifting of \eqref{eq:intro_functor_comp} to a morphism of schemes.
+
+% One consequence is that $\LG$ is equivalent to the bicategory $\cat{L}^\bullet$, which is \emph{computable} in the sense that its operations may be embodied in software.
 To some extent this software already exists: a component of what we are here calling the cut system $\cat{L}$ (developed earlier in joint work with Dyckerhoff \cite{dm1102.2957}\footnote{For a more detailed discussion of the relation of this work with the present paper, see Remark \ref{remark:relation_to_toby_paper}.}) has already been implemented in the computer algebra package Singular in joint work with Carqueville \cite{khovhompaper}, and used to compute tables of Khovanov-Rozansky knot homologies.
 The code was also used in the discovery of the generalised orbifolding relations among ADE singularities by Carqueville, Ros Camacho and Runkel \cite{ade}.
-
-\medskip
-In conclusion, the purpose of this paper is to develop the theory of cut systems as a mathematical foundation for the application to be given in \cite{cutsystems2}.
-Let us briefly summarise the contents of that work: one can show that the superbicategory $\cat{L}^\bullet$ is monoidal, has adjoints and is pivotal.
-This makes it a natural target for models of Girard's linear logic, which is a generalisation of the $\lambda$-calculus in which the terms may be viewed as algorithms that have a refined syntax of resource usage compared to the $\lambda$-calculus.
-The model of linear logic to be given in \cite{cutsystems2} interprets algorithms $x,y$ as $1$-morphisms $[x],[y]$ in $\cat{L}^\bullet$.
-
-This interpretation has two novelties: first of all, the target $\cat{L}^\bullet$ has a semantics of composition that may be compared to cut-elimination in linear logic (the analogue of $\beta$-reduction in the $\lambda$-calculus) as in Girard's geometry of interaction \cite{girard_towards}.
-This connection is what motivates the terminology of ``cut systems'' in the present paper.
-The second novelty is that, compared to the usual mathematical semantics of programming languages where algorithms are interpreted as functions between sets, our interpretation is bicategorical: in particular, equations $[x] \circ [y] \cong [y] \circ [x]$ or $[x]^2 \cong [x]$ on programs are represented by data that is part of the semantics.
-
-%.
-For a precise definition see Section \ref{??}}.
-To such a $W$ we associate a category of algebraic objects called matrix factorisations.
-A matrix factorisation of $W(x)$ is a matrix of polynomials $D$ satisfying $D^2 = W \cdot I_n$, where $I_n$ is the identity matrix.
-
-%For $W = x y^2 + y^3$ an example is
-%\[
-%D_1 = \begin{pmatrix} 0 & x - i y \\ x + iy & 0 \end{pmatrix} %, \qquad D_2 = \begin{pmatrix} 0 & y - x \\ (y - e^{2 \pi i /3} x)(y - e^{4 \pi i /3} x ) & 0 \end{pmatrix}
-%\]
-%A \emph{morphism} of matrix factorisations $\Phi: D_1 \lto D_2$ is a matrix of polynomials $\Phi$ satisfying the relation $\Phi D_1 = D_2 \Phi$.
-Together the matrix factorisations of $W$ and the morphisms between them form the category of matrix factorisations of $W$.
-
-%In the second part of the paper we explain how the multiplicative fragment of linear logic can be interpreted in the bicategory of Landau-Ginzburg models, with formulas mapped to isolated hypersurface singularities and proofs mapped to matrix factorisations.
-The multiplicative fragment is not very expressive, so our focus in the present paper is not on embedding sophisticated programs into $\cat{LG}$.
-Rather, we explain how cut systems give a dynamic model of cut-elimination following Girard's geometry of interaction.
-The basic construction of a cut system involves homological perturbation, and by interpreting this as a fixed point construction we will show that the result of normalization can be expressed in a power series expansion similar to Girard's famous execution formula.
-
 \medskip
@@
 Since $\HMF(k[x],W)$ is idempotent complete, there is an equivalence (see Remark \ref{remark:idempotent_completion} for the notation)
-\[
+\be\label{eq:omegavsoplus}
 \hmf(k[x],W)^\omega \lto \hmf(k[x],W)^{\oplus}
-\]
+\ee
 sending a pair $(X,e)$ to an infinite rank matrix factorisation splitting the idempotent $e$.
@@
 The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$.
-Given potentials $W \in k[x]$ and $V \in k[z]$ the supercategory $\cat{LG}(W,V)$ is
-\[
-\cat{LG}(W,V) = \hmf(k[x,z], V - W)^{\oplus}\,.
-\]
-Given a third potential $U \in k[y]$ the composition law is a functor
+Given potentials $W \in k[x]$ and $V \in k[y]$ the supercategory $\cat{LG}(W,V)$ is
+\[
+\cat{LG}(W,V) = \hmf(k[x,y], V - W)^{\oplus}\,.
+\]
+Given a third potential $U \in k[z]$ the composition law is a functor
 \[
@@
 \begin{equation}\label{eq:tensor_comp}
-Y \otimes X = ( Y \otimes_{k[z]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
+Y \otimes X = ( Y \otimes_{k[y]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
 \end{equation}
@@
 
+\subsection{Partial derivatives as homotopies}\label{section:partial}
+
+Let $R = k[x_1,\ldots,x_n]$ be a polynomial ring and $X$ a finite rank matrix factorisation of $W$ over $R$.
+Let us fix a homogeneous basis for $X$ so that we may identify $d_X$ with a matrix, and differentiate this matrix entry-wise to obtain the matrix $\lambda_i = \partial_{x_i}(d_X)$.
+
+\begin{lemma} The odd $R$-linear operator $\lambda_i$ on $X$ is independent, up to homotopy, of the choice of basis.
+\end{lemma}
+
+\begin{lemma} As operators on $X$ we have $[ d_X, \lambda_i ] = \partial_{x_i} W \cdot 1_X$.
+\end{lemma}
+\begin{proof}
+Applying the Leibniz rule to the equation $d_X d_X = W$ we obtain
+\be\label{eq:partials_are_homotopies}
+d_X \partial_{x_i}(d_X) + \partial_{x_i}(d_X) d_X = \partial_{x_i} W
+\ee
+as claimed.
+\end{proof}
+
+It follows that any element in the Jacobi ideal $( \partial_{x_1}W , \ldots, \partial_{x_n} W )$ acts null-homotopically on any morphism in the homotopy category $\hmf(R,W)$.
+Moreover these homotopies $\lambda_i$ are central, in the following sense:
+
+\begin{lemma}\label{lemma:naturalityoflambda} Let $\phi: X \lto X'$ be a morphism of matrix factorisations and write $\lambda_i = \partial_{x_i}(d_X)$ and $\lambda'_i = \partial_{x_i}(d_{X'})$.
+Then there is a homotopy $\phi \lambda_i \simeq \lambda'_i \phi$.
+\end{lemma}
+\begin{proof}
+From $d_{X'} \phi = \phi d_X$ we deduce
+\[
+\partial_{x_i}( d_{X'} ) \phi + d_{X'} \partial_{x_i}( \phi ) = \partial_{x_i}( \phi ) d_X + \phi \partial_{x_i}( d_X )
+\]
+and hence
+\[
+\partial_{x_i}( d_{X'} ) \phi - \phi \partial_{x_i}( d_X ) = \partial_{x_i}(\phi) d_X - d_{X'} \partial_{x_i}(\phi)
+\]
+as claimed.
+\end{proof}
+
+\begin{lemma}\label{lemma:commutator_of_lambdas} There is a homotopy $[ \lambda_i, \lambda_j ] \simeq \partial_{x_i x_j}(W) \cdot 1_X$.
+\end{lemma}
+\begin{proof}
+Differentiating \eqref{eq:partials_are_homotopies} with respect to $j$ leaves
+\[
+\partial_{x_j}(d_X) \partial_{x_i}(d_X) + d_X \partial_{x_jx_i}(d_X) + \partial_{x_jx_i}(d_X) d_X + \partial_{x_i}(d_X) \partial_{x_j}(d_X) = \partial_{x_ix_j}W
+\]
+from which we read off
+\[
+\lambda_i \lambda_j + \lambda_j \lambda_i = \partial_{x_ix_j}W + [d, -\partial_{x_jx_i}(d_X)]\,.
+\]
+\end{proof}
+
 \subsection{Clifford algebras}\label{section:clifford_algs}
@@
 We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}.
-For $n \ge 0$ the Clifford algebra $A_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $a_1,\ldots,a_n$ and $a_1^\dagger, \ldots, a_n^\dagger$ subject to the following relations
-\[
-[a_i, a_j] = 0, \qquad [a_i^\dagger, a_j^\dagger] = 0, \qquad [a_i, a_j^\dagger] = \delta_{ij}\,.
-\]
+For $n \ge 0$ the Clifford algebra $C_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $\gamma_1,\ldots,\gamma_n$ and $\gamma_1^\dagger, \ldots, \gamma_n^\dagger$ subject to the following relations
+\be\label{eq:clifford_relations}
+[\gamma_i, \gamma_j] = 0, \qquad [\gamma_i^\dagger, \gamma_j^\dagger] = 0, \qquad [\gamma_i, \gamma_j^\dagger] = \delta_{ij}\,.
+\ee
 for all $1 \le i, j \le n$.
 In this paper all our commutators are graded, $[a,b] = ab - (-1)^{|a||b|} ba$.
-We set $A_0 = k$.
-The algebras $A_n$ are Morita trivial in the sense that they are isomorphic to the endomorphism algebras of finite rank free $\mathbb{Z}_2$-graded $k$-modules.
-
-Indeed, if $F_n = k \theta_1 \oplus \cdots \oplus k \theta_n$ with $|\theta_i| = 1$ for all $i$, then
-
-\begin{lemma} With $S_n = \bigwedge F_n$ the map $A_n \lto \End_k(S_n)$ defined by
-\[
-a_i \mapsto \theta_i \wedge (-), \qquad a_i^\dagger \mapsto \theta_i^*\, \lrcorner\, (-)
-\]
-is an isomorphism of $\mathbb{Z}_2$-graded $k$-algebras, where $\lrcorner$ denotes contraction.
-\end{lemma}
-
-In particular this means that every $\mathbb{Z}_2$-graded $A_n$-module is isomorphic to $S_n \otimes_k V$ for some $\mathbb{Z}_2$-graded $k$-module $V$. From the isomorphism of $k$-modules
-\[
-S_m \otimes_k S_n = \bigwedge F_m \otimes_k \bigwedge F_n \cong \bigwedge F_{m+n} = S_{m+n}
-\]
-we deduce an isomorphism of algebras
+We set $C_0 = k$.
+These Clifford algebras have essentially only one nontrivial representation, sometimes called the \emph{spinor representation} \cite[p.14]{friedrich}.
+To define this representation we use the $\nZ_2$-graded $k$-module
+\[
+F_n = k \theta_1 \oplus \cdots \oplus k \theta_n
+\]
+where the $\theta_i$ are formal variables of odd degree, and set
+\be
+S_n = \bigwedge F_n = \bigwedge\big( k \theta_1 \oplus \cdots \oplus k \theta_n \big)\,.
+\ee
+
+\begin{definition}\label{defn:contraction} Left multiplication in the exterior algebra defines an odd operator
+\begin{gather*}
+\theta_i \wedge (-): S_n \lto S_n\,,\\
+\theta_{j_1} \cdots \theta_{j_r} \mapsto \theta_i \theta_{j_1} \cdots \theta_{j_r}\,.
+\end{gather*}
+Contraction from the left defines an odd operator
+\begin{gather*}
+\theta_i^*\, \lrcorner\, (-): S_n \lto S_n\,,\\
+\theta_{j_1} \cdots \theta_{j_r} \mapsto \sum_{l=1}^r (-1)^{(l-1)} \delta_{i,j_l} \theta_{j_1} \cdots \widehat{ \theta_{j_l} } \cdots \theta_{j_r}\,.
+\end{gather*}
+\end{definition}
+
+Usually we write simply $\theta_i$ for the operator $\theta_i \wedge (-)$ and $\theta_i^*$ for the operator $\theta_i^*\, \lrcorner\, (-)$.
+The spinor representation is defined by the next lemma, which also shows that the algebras $C_n$ are Morita trivial in the sense that they are isomorphic to the endomorphism algebras of a finite rank free $\mathbb{Z}_2$-graded $k$-module.
+
+\begin{lemma}\label{defn:spinorrep} The map $C_n \lto \End_k(S_n)$ defined by
+\[
+\gamma_i \mapsto \theta_i \wedge (-), \qquad \gamma_i^\dagger \mapsto \theta_i^*\, \lrcorner\, (-)
+\]
+is an isomorphism of $\mathbb{Z}_2$-graded $k$-algebras.
+\end{lemma}
+
+In particular this means that every $\mathbb{Z}_2$-graded $C_n$-module is isomorphic to $S_n \otimes_k V$ for some $\mathbb{Z}_2$-graded $k$-module $V$. Using the isomorphism of $k$-modules
+\[
+F_m \oplus F_n \cong F_{m+n}
+\]
+which maps the ordered basis $\theta_1,\ldots,\theta_m$ of $F_m$ to the first $m$ basis elements of $F_{m+n}$ in their given order, and the ordered basis of $F_n$ to the last $n$ basis elements, we define
+\[
+S_m \otimes_k S_n = \bigwedge F_m \otimes_k \bigwedge F_n \cong \bigwedge F_{m+n} = S_{m+n}\,.
+\]
+From this we deduce an isomorphism of algebras
 \begin{equation}\label{eq:algebra_A_additive}
-A_m \otimes_k A_n \cong A_{m+n}\,.
-\end{equation}
-Given $m, n \ge 0$ we introduce notation for the $A_m$-$A_n$-bimodule
+C_m \otimes_k C_n \cong C_{m+n}\,.
+\end{equation}
+Given $m, n \ge 0$ we introduce notation for the $C_m$-$C_n$-bimodule
 \begin{equation}
-S_{m,n} = S_m \otimes_k S_n^*
-\end{equation}
-where $S_n^* = \Hom_k(S_n, k)$. There is an isomorphism of $A_l$-$A_n$-bimodules
+S_{m,n} = S_m \otimes_k S_n^* = \Hom_k(S_n,S_m)
+\end{equation}
+where $S_n^* = \Hom_k(S_n, k)$. There is an isomorphism of $C_l$-$C_n$-bimodules
 \begin{equation}\label{eq:isosbimodule}
-S_{l,m} \otimes_{A_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{A_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
-\end{equation}
-In the case $k = \mathbb{C}$, $S_n$ is often referred to as the \emph{spinor representation} \cite[p.14]{friedrich}.
+S_{l,m} \otimes_{A_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{C_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
+\end{equation}
+
+\begin{definition}\label{defn:idempotent_e} For $n \ge 0$ let $e_n \in C_n$ denote the element
+\[
+e_n = \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1\,.
+\]
+This is the idempotent corresponding to the summand $k \cdot 1$ of $S_n$.
+\end{definition}
+
+\begin{definition}\label{defn:idempotent_gen} More generally, given $m, n \ge 0$ consider the $k$-linear map
+\[
+\xymatrix{
+S_n \ar[r] & k \cdot 1 \ar[r]^{\operatorname{inc}} & S_m
+}
+\]
+given by the projection to $k \cdot 1$ followed by the inclusion into $S_m$. This defines an element
+\[
+\iota_{m,n} \in \Hom_k(S_n, S_m) = S_m \otimes_k S_n^*\,.
+\]
+Then obviously $\iota_{n,n} = e_n$.
+\end{definition}
 
@@
 This is a $\mathbb{Z}_2$-graded $k$-algebra when we assign $|v| = 1$ for all $v \in V$ and $|1| = 0$.
-If we take $V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then $A_n$ is the Clifford algebra of the pair $(V,B)$.
+If we take $V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then $C_n$ is the Clifford algebra of the pair $(V,B)$.
 \end{remark}
 
-\subsection{The Clifford thickening}
-
-Let $\cat{C}$ be a small idempotent complete supercategory.
-We construct a new supercategory $\cat{C}^\bullet$ called the \emph{Clifford thickening} in which the objects are pairs $(X,n)$ of an integer $n \ge 0$ and a left $A_n$-module $X$ in $\cat{C}$.
-
-We will need the operation of tensoring objects of $\cat{C}$ with $k$-modules.
-This is standard material, which is recalled in Appendix \ref{section:tensorproduct_supcat}.
-The upshot is that if $A$ is a Morita trivial $\mathbb{Z}_2$-graded $k$-algebra and if $X \in \cat{C}$ is a left $A$-module, while $V$ is a $\mathbb{Z}_2$-graded right $A$-module (in the usual sense, i.e.
-in the category of $k$-modules) then there is an object $V \otimes_A X$ in $\cat{C}$ which is functorial in both $V$ and $X$.
+\section{The Clifford thickening}
+
+Let $\cat{T}$ be a small idempotent complete supercategory.
+We construct a new supercategory $\cat{T}^\bullet$ called the \emph{Clifford thickening} in which the objects are pairs $(X,n)$ of an integer $n \ge 0$ and a left $C_n$-module $X$ in $\cat{T}$.
+Recall that if $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{T}_A$ denotes the supercategory of $A$-modules in $\cat{T}$ with $A$-linear maps.
+
+%The upshot is that if $A$ is a Morita trivial $\mathbb{Z}_2$-graded $k$-algebra and if $X \in \cat{T}$ is a left $A$-module, while $V$ is a $\mathbb{Z}_2$-graded right $A$-module (in the usual sense, i.e.
+in the category of $k$-modules) then there is an object $V \otimes_A X$ in $\cat{T}$ which is functorial in both $V$ and $X$.
 Morever if $V$ is a $B$-$A$-bimodule then $V \otimes_A X$ is naturally a left $B$-module, and so on.
-If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{C}_A$ denotes the supercategory of $A$-modules in $\cat{C}$ with $A$-linear maps.
 
 Similarly to Example \ref{example:bicategory_m} there is a superbicategory $\cat{M}$ of Morita trivial $\mathbb{Z}_2$-graded $k$-algebras: $1$-morphisms are $\mathbb{Z}_2$-graded bimodules which are finitely generated and projective over $k$ and $2$-morphisms are degree zero bimodule maps.
-
-\begin{proposition} The assignment of the supercategory $\cat{C}_A$ to an algebra $A$ and of the superfunctor $\Phi_V = V \otimes_A (-)$ to a $B$-$A$-bimodule $V$ determines a strong superfunctor
-\[
-\Phi^{\cat{C}}: \cat{M} \lto \Cat^{\operatorname{sup}}_k
+We will need the operation of tensoring objects of $\cat{T}$ with $k$-modules, which is recalled in Appendix \ref{section:tensorproduct_supcat}.
+
+\begin{proposition} The assignment of the supercategory $\cat{T}_A$ to an algebra $A$ and of the superfunctor $\Phi_V = V \otimes_A (-)$ to a $B$-$A$-bimodule $V$ determines a strong superfunctor
+\[
+\Phi^{\cat{T}}: \cat{M} \lto \Cat^{\operatorname{sup}}_k
 \]
@@
 \begin{gather*}
-n \mapsto A_n = \End_k( S_n ),\\
+n \mapsto C_n = \End_k( S_n ),\\
 \phi_{m,n} \mapsto S_{m,n} = S_m \otimes_k S_n^*\,.
@@
 \xymatrix@C+1pc{
-\mathbb{N} \ar[r] & \cat{M} \ar[r]^-{\Phi^{\cat{C}}} & \Cat^{\operatorname{sup}}_k
+\mathbb{N} \ar[r] & \cat{M} \ar[r]^-{\Phi^{\cat{T}}} & \Cat^{\operatorname{sup}}_k
 }
 \end{equation}
-sending $n$ to the category of left $A_n$-modules in $\cat{C}$ and $\phi_{m,n}$ to the functor $S_{m,n} \otimes_{A_n} -$.
+sending $n$ to the category of left $C_n$-modules in $\cat{T}$ and $\phi_{m,n}$ to the functor $S_{m,n} \otimes_{C_n} -$.
 There is a close connection between strong functors into the bicategory of small categories, and what are called cofibered categories, given by the Grothendieck construction \cite{vistoli}.
 
-\begin{definition} The \emph{Clifford thickening} $\cat{C}^\bullet$ of the supercategory $\cat{C}$ is the category which results from the Grothendieck construction applied to the strong functor \eqref{eq:strongfunctorgroth}.
+\begin{definition} The \emph{Clifford thickening} $\cat{T}^\bullet$ of the supercategory $\cat{T}$ is the category which results from the Grothendieck construction applied to the strong functor \eqref{eq:strongfunctorgroth}.
 \end{definition}
 
-More concretely $\cat{C}^\bullet$ is the category with objects all pairs $(X,n)$ of an integer $n \ge 0$ and an object $X \in \cat{C}$ with a left $A_n$-action.
-A morphism $\alpha: (X,n) \lto (Y,m)$ is a morphism of $A_m$-modules $\alpha: S_{m,n} \otimes_{A_n} X \lto Y$.
+More concretely $\cat{T}^\bullet$ is the category with objects all pairs $(X,n)$ of an integer $n \ge 0$ and an object $X \in \cat{T}$ together with a left $C_n$-action.
+A morphism $\alpha: (X,n) \lto (Y,m)$ is a morphism of $C_m$-modules $\alpha: S_{m,n} \otimes_{C_n} X \lto Y$.
 Composition of a pair of morphisms
@@
 \end{equation}
-is given by the morphism of $A_l$-modules
+is given by the morphism of $C_l$-modules
 \begin{equation}\label{eq:comp_chain1}
 \xymatrix@C+1pc{
-S_{l, n} \otimes_{A_n} X \ar[r]^-{\cong} & (S_{l,m} \otimes_{A_m} S_{m,n}) \otimes_{A_n} X \ar[d]^-{\cong}\\
-& S_{l,m} \otimes_{A_m} ( S_{m,n} \otimes_{A_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{A_m} Y \ar[r]^-{\beta} & Z\,.
+S_{l, n} \otimes_{C_n} X \ar[r]^-{\cong} & (S_{l,m} \otimes_{C_m} S_{m,n}) \otimes_{C_n} X \ar[d]^-{\cong}\\
+& S_{l,m} \otimes_{A_m} ( S_{m,n} \otimes_{C_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{C_m} Y \ar[r]^-{\beta} & Z\,.
 }
 \end{equation}
-There is a canonical functor $p: \cat{C}^\bullet \lto \mathbb{N}$ defined by $p(X,n) = n$, which defines a cofibered category over $\mathbb{N}$ by the definition of the Grothendieck construction.
-
-\begin{lemma} $\cat{C}^\bullet$ is a supercategory and the functor $\iota: \cat{C} \lto \cat{C}^\bullet$ defined by $\iota(X) = (X,0)$ is an equivalence of supercategories.
-\end{lemma}
-\begin{proof}
-The supercategory structure is given by the functor $\Psi: \cat{C}^\bullet \lto \cat{C}^\bullet$ where $\Psi(X,n) = ( \Psi X, n )$ and $\Psi X$ has the $A_n$-action given by Definition \ref{defn:psimodule}.
-
-The functor $\iota$ is fully faithful.
-To see that it is essentially surjective, let $(X,n) \in \cat{C}^\bullet$ be given.
-We show that $(X,n)$ is isomorphic to $(\widetilde{X},0)$ where $\widetilde{X} = S_n^* \otimes_{A_n} X$.
-This follows from the fact that the isomorphism
-\[
-S_n \otimes_k \widetilde{X} = S_n \otimes_k S_n^* \otimes_{A_n} X \cong X
-\]
-defines an isomorphism $(\widetilde{X}, 0) \lto (X,n)$ in $\cat{C}^\bullet$.
-\end{proof}
-
-\begin{definition}\label{defn:idempotent_e} For $n \ge 0$ let $e_n \in A_n$ denote the element
-\[
-e_n = a_1^\dagger \cdots a_n^\dagger a_n \cdots a_1\,.
-\]
-This is the idempotent corresponding to the summand $k \cdot 1$ of $S_n$.
+There is a canonical functor $p: \cat{T}^\bullet \lto \mathbb{N}$ defined by $p(X,n) = n$, which defines a cofibered category over $\mathbb{N}$ by the definition of the Grothendieck construction.
+This definition has the benefit of being derived from a general construction, but there is an alternative description of morphisms which is less cumbersome:
+
+\begin{definition} Let $\cat{T}^{\star}$ be the category with the same objects as $\cat{T}^\bullet$ and
+\begin{align*}
+\cat{T}^{\star}( (X,n), (Y,m) ) &= \Big\{ \alpha \in \cat{T}(X,Y) \l \alpha \gamma_i = 0 \text{ for } 1 \le i \le n \text{ and }\\
+&\qquad \qquad\qquad \qquad \;\; \gamma_i^\dagger \alpha = 0 \text{ for } 1 \le i \le m \Big\}\,.
+\end{align*}
+Composition is as in $\cat{T}$, but the identity on $(X,n)$ in $\cat{T}^\star$ is the morphism
+\[
+1^*_{(X,n)} = e_n
+\]
+where $e_n$ is the action on $X$ of the canonical idempotent from Definition \ref{defn:idempotent_e}.
 \end{definition}
 
-\begin{remark}\label{remark:tensor_and_idempotent} It may seem odd to labour to construct a category $\cat{C}^\bullet$ equivalent to $\cat{C}$.
+\begin{lemma}\label{lemma:equivcliffordthick} $\cat{T}^{\star}$ is a category and there is an equivalence of categories
+\[
+\Theta: \cat{T}^\bullet \lto \cat{T}^{\star}
+\]
+\end{lemma}
+\begin{proof}
+To prove that $\cat{T}^{\star}$ is a category it only needs to be checked that $1^*_{(X,n)}$ really acts as an identity. Let $\alpha: X \lto Y$ be a morphism in $\cat{T}^{\star}$ and consider
+\begin{align*}
+\alpha e_n &= \alpha \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1\\
+&= \alpha \left( \gamma_1^\dagger \cdots \gamma_{n-1}^\dagger \gamma_{n-1} \cdots \gamma_1 - \gamma_1^\dagger \cdots \gamma_n \gamma_n^\dagger \cdots \gamma_1 \right)\\
+&= \alpha \gamma_1^\dagger \cdots \gamma_{n-1}^\dagger \gamma_{n-1} \cdots \gamma_1
+\end{align*}
+since in the second summand within the brackets, there is nothing to stop $\gamma_n$ from commuting to the left and annihilating with $\alpha$.
+Proceeding inductively, we see that $\alpha e_n = \alpha$.
+The proof that $e_n \alpha = \alpha$ is similar.
+
+The functor $\Theta$ is defined to be the identity on objects, and given $\beta: (X,n) \lto (Y,m)$ in $\cat{T}^{\bullet}$ which is a morphism $\beta: S_{m,n} \otimes_{C_n} X \lto Y$ in $\cat{T}$ we define
+\begin{gather*}
+\Theta(\beta): X \lto Y\,,\\
+\Theta(\beta)( x ) = \beta( \iota_{m,n} \otimes x )
+\end{gather*}
+where $\iota_{m,n}$ is as in Definition \ref{defn:idempotent_gen}.
+We relegate the proof that this functor gives a bijection on morphism sets to Lemma \ref{lemma:morphisms_two_forms}.
+Functoriality is easily checked, and $\Theta(1_X) = e_n$ since by definition $\iota_{n,n} = e_n$.
+\end{proof}
+
+Every $C_n$-module $X$ in $\cat{T}$ is of the form $S_n \otimes_k V$ for some object $V$. It will be important later to know exactly how to extract the object $V$ from $X$ by splitting an idempotent.
+
+\begin{lemma}\label{lemma:whackamole} Let $X$ be a $C_n$-module in $\cat{T}$. The idempotent $e_n: X \lto X$ splits, say 
+\[
+\xymatrix@C+2pc{
+X \ar@<1ex>[r]^-{f_0} & V \ar@<1ex>[l]^-{g_0}
+}
+\]
+with $f_0 g_0 = 1_V$ and $g_0 f_0 = e_n$ and in $\cat{T}^\bullet$ there are mutually inverse isomorphisms
+\[
+\xymatrix@C+2pc{
+(X, n) \ar@<1ex>[r]^-{f} & (V,0) \ar@<1ex>[l]^-{g}\,.
+}
+\]
+induced by $f_0,g_0$. In particular
+\be
+S_n^* \otimes_{C_n} X \cong V\,, \qquad S_n \otimes_k V \cong X\,.
+\ee
+\end{lemma}
+\begin{proof}
+The map $f_0$ is a morphism $(X,n) \lto (V,0)$ in $\cat{T}^{\star}$ since
+\[
+f_0 \gamma_i = f_0 e_n \gamma_i = f_0 \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1 \gamma_i = 0\,.
+\]
+Similarly $g_0$ defines a morphism $(V,0) \lto (X,n)$.
+Let $f,g$ be the morphisms in $\cat{T}^\bullet$ corresponding to $f_0,g_0$ under the equivalence of Lemma \ref{lemma:equivcliffordthick}.
+To prove that $fg = 1_{(X,n)}$ and $gf = 1_{(V,0)}$ in $\cat{T}^{\bullet}$ it suffices to prove that $f_0 g_0 = 1^*_{(X,n)} = e_n$ and $g_0 f_0 = 1^*_{(V,0)}$ in $\cat{T}^{\star}$.
+But this is true by definition.
+\end{proof}
+
+\begin{lemma}\label{lemma:embedcliffordthick} $\cat{T}^\bullet$ is a supercategory and the functor $\iota: \cat{T} \lto \cat{T}^\bullet$ defined by $\iota(X) = (X,0)$ is an equivalence of supercategories.
+\end{lemma}
+\begin{proof}
+The supercategory structure is given by the functor $\Psi: \cat{T}^\bullet \lto \cat{T}^\bullet$ where $\Psi(X,n) = ( \Psi X, n )$ and $\Psi X$ has the $C_n$-action given by Definition \ref{defn:psimodule}.
+The functor $\iota$ is fully faithful and it follows from Lemma \ref{lemma:whackamole} that it is essentially surjective.
+\end{proof}
+
+%\begin{remark}\label{remark:tensor_and_idempotent} It may seem odd to labour to construct a category $\cat{C}^\bullet$ equivalent to $\cat{C}$.
 The point is that while $(X,n)$ and $(\widetilde{X}, 0)$ are isomorphic in $\cat{C}^\bullet$, they still represent quantitatively different states of knowledge.
@@
 
-For each $n$ the fiber of the functor $p: \cat{C}^\bullet \lto \mathbb{N}$ over $n$ is $\cat{C}_{A_n}$. We may depict the cofibered category $p$ as follows:
-\begin{equation}\label{eq:cofibered_diagram}
-\xymatrix@C+3pc@R+1pc{
-\cat{C} \ar@{.}[d] \ar@<1ex>[rrr]^-{E} & & & \cat{C}_{A_n} \ar@{.}[d] \ar@<1ex>[lll]^-{F}\\
-0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & n \ar@{.>}@<0.8ex>[l]
-}\,.
-\end{equation}
-The transport between the fibers is given by the equivalences
-\[
-E(-) = S_{n} \otimes_k (-), \qquad F(-) = S^*_{n} \otimes_{A_n} (-)\,.
-\]
-While these functors are adjoint, and therefore uniquely determine one another, we have explained that there is a fundamental asymmetry between them from the point of view of computation: knowledge of an object of $\cat{C}^\bullet$ over $n$ represents a state of higher uncertainty than knowledge of an object over $m < n$, given that in the end both objects ``only'' contain the information of the corresponding object $\widetilde{X}$ over zero, but more work is necessary to extract this information from an object of $\cat{C}_{A_n}$ than from an object of $\cat{C}_{A_m}$.
-\end{remark}
-
-\begin{remark}\label{remark:tensor_in_steps} Given $(X,n) \in \cat{C}^\bullet$, one way to compute the tensor product
-\[
-S_{n+1,n} \otimes_{A_n} X = (S_{n+1} \otimes_k S_n^*) \otimes_{A_n} X \cong S_{n+1} \otimes_k ( S_n^* \otimes_{A_n} X )
-\]
-is to compute $S_n^* \otimes_{A_n} X$ and then take direct sums. Alternatively,
-\begin{align*}
-S_{n+1,n} \otimes_{A_n} X &= S_{n+1} \otimes_k S_n^* \otimes_{A_n} X\\
-&\cong S_1 \otimes_k S_n \otimes_k S_n^* \otimes_{A_n} X \\
-&\cong S_1 \otimes_k A_n \otimes_{A_n} X \\
-&\cong S_1 \otimes_k X\,.
-\end{align*}
-That is, if we equip $S_1 \otimes_k X = X \oplus \Psi X$ with an $A_{n+1} \cong A_1 \otimes A_n$ action by making $A_n$ act on $X$ and $A_1$ act on $S_1$, this computes the tensor product.
+%For each $n$ the fiber of the functor $p: \cat{C}^\bullet \lto \mathbb{N}$ over $n$ is $\cat{C}_{A_n}$. We may depict the cofibered category $p$ as follows:
+%\begin{equation}\label{eq:cofibered_diagram}
+%\xymatrix@C+3pc@R+1pc{
+%\cat{C} \ar@{.}[d] \ar@<1ex>[rrr]^-{E} & & & \cat{C}_{A_n} \ar@{.}[d] \ar@<1ex>[lll]^-{F}\\
+%0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & n \ar@{.>}@<0.8ex>[l]
+%}\,.
+%\end{equation}
+%The transport between the fibers is given by the equivalences
+%\[
+%E(-) = S_{n} \otimes_k (-), \qquad F(-) = S^*_{n} \otimes_{A_n} (-)\,.
+%\]
+%While these functors are adjoint, and therefore uniquely determine one another, we have explained that there is a fundamental asymmetry between them from the point of view of computation: knowledge of an object of $\cat{C}^\bullet$ over $n$ represents a state of higher uncertainty than knowledge of an object over $m < n$, given that in the end both objects ``only'' contain the information of the corresponding object $\widetilde{X}$ over zero, but more work is necessary to extract this information from an object of $\cat{C}_{A_n}$ than from an object of $\cat{C}_{A_m}$.
+%\end{remark}
+
+%\begin{remark}\label{remark:tensor_in_steps} Given $(X,n) \in \cat{T}^\bullet$, one way to compute the tensor product
+%\[
+%S_{n+1,n} \otimes_{A_n} X = (S_{n+1} \otimes_k S_n^*) \otimes_{A_n} X \cong S_{n+1} \otimes_k ( S_n^* \otimes_{A_n} X )
+%\]
+%is to compute $S_n^* \otimes_{A_n} X$ and then take direct sums. Alternatively,
+%\begin{align*}
+%S_{n+1,n} \otimes_{A_n} X &= S_{n+1} \otimes_k S_n^* \otimes_{A_n} X\\
+%&\cong S_1 \otimes_k S_n \otimes_k S_n^* \otimes_{A_n} X \\
+%&\cong S_1 \otimes_k A_n \otimes_{A_n} X \\
+%&\cong S_1 \otimes_k X\,.
+%\end{align*}
+%That is, if we equip $S_1 \otimes_k X = X \oplus \Psi X$ with an $A_{n+1} \cong A_1 \otimes A_n$ action by making $A_n$ act on $X$ and $A_1$ act on $S_1$, this computes the tensor product.
 In a similar way, $S_{n-1,n} \otimes_{A_n} X$ is computed by splitting the idempotent $a_1^\dagger a_1$ on $X$, so that the functor $F$ of \eqref{eq:cofibered_diagram} may be computed in $n$ steps by splitting $a_1^\dagger a_1$, then $a_2^\dagger a_2$, and so on.
-\end{remark}
+%\end{remark}
 %TODO note: $S_{m,n} \otimes_{A_n}$ is an equivalence so all fibers are isomorphic to $\cat{C}$.
 
-\begin{remark} An alternative description of morphisms in $\cat{C}^\bullet$ follows from Lemma \ref{lemma:morphisms_two_forms}.
-This result tells us that given an $A_n$-module $X$ and $A_m$-module $Y$ in $\cat{C}$ there is a bijection between morphisms of $A_m$-modules $\alpha: S_{m,n} \otimes_{A_n} X \lto Y$ and morphisms
-\[
-\alpha_0: X \lto Y \text{ satisfying } \alpha_0 \circ a_i = 0 \text{ for } 1 \le i \le n \text{ and } a_i^\dagger \circ \alpha_0 = 0 \text{ for } 1 \le i \le m\,.
-\]
-The bijection is defined by sending $\alpha$ to the composite ($\iota$ is defined by $\iota(1) = 1 \otimes 1^*$)
-\[
-\xymatrix@C+2pc{
-X \cong A_n \otimes_{A_n} X \ar[r]^-{\iota \otimes 1} & S_{m,n} \otimes_{A_n} X \ar[r]^-{\alpha} & Y
-}\,
-\]
-Given a chain of composable morphisms as in \eqref{eq:comp_chain0} there are corresponding morphisms $\alpha_0: X \lto Y$ and $\beta_0: Y \lto Z$ and it can be checked that the morphism corresponding under the bijection of Lemma \ref{lemma:morphisms_two_forms} to the composite $\beta \circ \alpha$ given in \eqref{eq:comp_chain1} is
-\[
-(\beta \circ \alpha)_0 = \beta_0 \circ \alpha_0\,.
-\]
-\end{remark}
-
-\section{Cut systems}\label{section:cut_systems}
-
-We begin with the definition of cut functors.
-
-\begin{definition} Given supercategories $\cat{C}_1,\cat{C}_2,\cat{C}_3$ a \emph{superfunctor} $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3$ is a functor together with natural isomorphisms
-\begin{align*}
-\tau &: T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T,\\
-\tau &: T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
-\end{align*}
-making the following diagrams commute:
-\begin{equation}\label{eq:psicomp1}
-\xymatrix@R+1pc@C+1pc{
-T( 1 \otimes \Psi^2 ) \ar[r]^-{\tau}\ar[d]_-{T(1 \otimes \xi)} & \Psi T( 1 \otimes \Psi ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
-T \ar[rr]_-{1_T} & & T
-}
-\end{equation}
-\begin{equation}\label{eq:psicomp2}
-\xymatrix@R+1pc@C+1pc{
-T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\psi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
-T \ar[rr]_-{1_T} & & T
-}
-\end{equation}
-\begin{equation}\label{eq:psicomp3}
-\xymatrix@R+1pc@C+1pc{
-T( \Psi \otimes \Psi ) \ar[r]^-{\tau}\ar[d]_-{-\tau} & \Psi T( 1 \otimes \Psi ) \ar[d]^-{\tau}\\
-\Psi T( \Psi \otimes 1 ) \ar[r]_-{\tau} & \Psi^2 T
-}
-\end{equation}
-
-\end{definition}
-
-\begin{definition}\label{defn:cutfunctor1} A \emph{cut functor of degree $t$} on a triple $\cat{C}_1, \cat{C}_2,\cat{C}_3$ of idempotent complete small supercategories is a superfunctor $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3^\bullet$ such that
-\[
-\xymatrix{
-\cat{C}_1 \times \cat{C}_2 \ar[r]^-{T} & \cat{C}_3^\bullet \ar[r]^-{p} & \mathbb{N}
-}
-\]
-sends every object to the integer $t \in \mathbb{N}$.
-\end{definition}
-
-With the above notation:
-
-\begin{proposition}\label{prop:extend_cut_functor} Given a cut functor $T$ of degree $t$ on $\cat{C}_1, \cat{C}_2,\cat{C}_3$ there is a canonical superfunctor $\widetilde{T}: \cat{C}_1^\bullet \otimes_k \cat{C}_2^\bullet \lto \cat{C}_3^\bullet$ with the property that the diagram
-\[
-\xymatrix{
-\cat{C}_1 \times \cat{C}_2 \ar[dr]_-{\iota \times \iota} \ar[rr]^-{T} & & \cat{C}_3^\bullet\\
-& \cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[ur]_-{\widetilde{T}}
-}
-\]
-commutes, and for every pair of objects $X \in \cat{C}_1^\bullet$ and $Y \in \cat{C}_2^\bullet$
-\[
-p \widetilde{T}( X, Y ) = p( X ) + p( Y ) + t\,.
-\]
-We refer to $\widetilde{T}$ as the \emph{extension} of $T$.
-%and
-%\[
-%\xymatrix@C+2pc{
-%\cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[d]_-{p \times p}\ar[rr]^-{\widetilde{T}} & & \cat{C}_3^\bullet \ar[dd]^-{p}\\
-%\mathbb{N} \times \mathbb{N} \ar[d]_-{\cong}\\
-%\mathbb{N} \times \{ * \} \times \mathbb{N} \ar[r]_-{1 \times t \times 1} & \mathbb{N} \times \mathbb{N} \times \mathbb{N} \ar[r]_-{\otimes} & \mathbb{N}
-%}
-%\]
-%commute. 
-\end{proposition}
-\begin{proof}
-The proof is given in Appendix \ref{app:proof_cut_extension}.
-\end{proof}
-
-We will use \emph{effectively computable} as a synonym for the precise notion of a \emph{computable} function \cite{enderton}, since ``computable'' often has a more colloquial meaning in our context.
-
-% This is the definition from cutsys10
-\begin{definition} A \emph{cut system} $\cat{A}$ is determined by the following data:
-\begin{itemize}
-\item A class $|\cat{A}|$ of objects and for each object $a$ an integer $\pi(a) \ge 0$.
-\item For each pair $a,b$ of objects a small idempotent complete supercategory $\cat{A}(a,b)$. 
-\item For each triple $a,b,c$ of objects a cut functor of degree $\pi(b)$
-\[
-T: \cat{A}(a,b) \otimes_k \cat{A}(b,c) \lto \cat{A}(a,c)^{\bullet}\,.
-\]
-The image of a pair $X \otimes Y$ under the canonical extension
-\[
-\widetilde{T}: \cat{A}(a,b)^\bullet \otimes_k \cat{A}(b,c)^\bullet \lto \cat{A}(a,c)^\bullet
-\]
-is denoted $Y \l X$ and is called the \emph{cut of $Y$ and $X$ along $b$}.
-\item For each object $a$, an object $\Delta_a \in \cat{A}(a,a)$.
-\item For objects $a,b,c,d$ a natural isomorphism $\alpha$ as shown below:
-\[
-\xymatrix@C+2pc{
-\cat{A}(a,b) \times \cat{A}(b,c) \times \cat{A}(c,d) \ar[d]_-{T \times 1} \ar[r]^-{1 \times T} & \cat{A}(a,b) \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\alpha}\\
-\cat{A}(a,c)^\bullet \times \cat{A}(c,d) \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
-}
-\]
-That is, for $X \in \cat{A}(a,b), Y \in \cat{A}(b,c), Z \in \cat{A}(c,d)$ an isomorphism
-\[
-\alpha_{Z,Y,X}: ( Z \l Y ) \l X \lto Z \l ( Y \l X )
-\]
-of $A_{\pi(b)} \otimes_k A_{\pi(c)}$-modules in $\cat{A}(a,d)$, natural in all three variables.
-\item For objects $a,b$ natural isomorphisms $\mu, \eta$ as shown below:
-\[
-\xymatrix@C+2pc{
-1 \times \cat{A}(a,b) \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b) \ar@{=>}@<4ex>[l]_-{\eta} \ar@{=>}@<-4ex>[r]^-{\mu} \ar[d]^-{\iota} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b) \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
-\cat{A}(a,a) \times \cat{A}(a,b) \ar[r]_-{T} & \cat{A}(A,B)^\bullet & \cat{A}(a,b) \times \cat{A}(b,b) \ar[l]^-{T}
-}
-\]
-where $1$ is the category with one object and one morphism and $\iota_{\Delta}$ is the functor sending this object to $\Delta$. That is, for each $X \in \cat{A}(a,b)$ a pair of isomorphisms
-\begin{equation}\label{eq:defn_cutsys_lambda}
-\mu: X \lto \Delta_b \l X, \quad \eta: X \lto X \l \Delta_a
-\end{equation}
-in $\cat{A}(a,b)^\bullet$ natural in $X$.
-\end{itemize}
-This data is subject to the following coherence conditions:
-\begin{itemize}
-\item[(1)] For objects $a,b,c,d,e$ and $X \in \cat{A}(a,b),Y \in \cat{A}(b,c),Z \in \cat{A}(c,d),Q \in \cat{A}(d,e)$, commutativity of the diagram
-\begin{equation}
-\xymatrix@C+2pc{
-((Q \l Z) \l Y ) \l X \ar[d]_-{\alpha_{Q \l Z, Y, X}}\ar[r]^-{\alpha_{Q,Z,Y} \l 1} & (Q \l (Z \l Y)) \l X \ar[r]^-{\alpha_{Q, Z \l Y, X}} & Q \l ( ( Z \l Y ) \l X ) \ar[d]^-{1 \l \alpha_{Z,Y,X}}\\
-(Q \l Z) \l (Y \l X) \ar[rr]_-{\alpha_{Q, Z, Y \l X}} & & Q \l ( Z \l ( Y \l X ) )
-}
-\end{equation}
-Note that when we write $\alpha_{Q, Z \l Y, X}$ we refer only the underlying object of $Z \l Y$.
-\item[(2)] For objects $a,b$ and $X \in \cat{A}(a,b), Y \in \cat{A}(b,c)$ commutativity of the diagram
-\begin{equation}\label{eq:unitor_constraint_cut}
-\xymatrix{
-(Y \l \Delta_b ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
-& Y \l X \ar[ul]^-{\eta \l 1_X} \ar[ur]_-{1_Y \l \mu}
-}
-\end{equation}
-\item[(3)] commutativity of \eqref{eq:psiunitor1},\eqref{eq:psiunitor2} for every $X$ and \eqref{eq:psithirdlastdia}, \eqref{eq:psimiddledia}, \eqref{eq:psilastdia} for every composable triple $X,Y,Z$.
-\end{itemize}
-Finally, the data is subject to three computability conditions:
-\begin{itemize}
-\item[(1)] For each pair of objects $a,b$ the category $\cat{A}(a,b)$ is effectively computable, in the sense that the morphisms and objects are described by finite data and the composition rule is computable.
-\item[(2)] For each triple $a,b,c$ of objects the associated cut functor is effectively computable.
-In particular, for $1$-morphisms $Y$ and $X$ the object $Y \l X$ and its Clifford action are effectively computable from $X$ and $Y$.
-\item[(3)] The associators and unitors are effectively computable from their arguments.
-\end{itemize}
-\end{definition}
-
-\begin{remark} To give natural isomorphisms \eqref{eq:defn_cutsys_lambda} in $\cat{A}(a,b)^\bullet$ is equivalent to giving natural isomorphisms in $\cat{A}(a,b)$
-\begin{equation}\label{eq:unitor_tilde_pre}
-\mu: S_{\pi(b)} \otimes_k X \lto \Delta_b \l X, \quad \eta: S_{\pi(a)} \otimes_k X \lto X \l \Delta_a
-\end{equation}
-which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.
-
-By Lemma \ref{lemma:morphism_out_1} such morphisms correspond bijectively to morphisms in $\cat{A}(a,b)$
-\begin{equation}\label{eq:unitor_tilde}
-\mu_0: X \lto \Delta_b \l X, \quad \eta_0: X \lto X \l \Delta_a
-\end{equation}
-satisfying respectively $a_i^\dagger \circ \mu_0 = 0$ for $1 \le i \le m$ and $a_i^\dagger \circ \eta_0 = 0$ for $1 \le i \le n$.
-The reason to introduce these maps is that commutativity of \eqref{eq:unitor_constraint_cut} can be more conveniently expressed in terms of the maps in \eqref{eq:unitor_tilde}, see Lemma \ref{lemma:unitor_check_help} below.
-\end{remark}
-
-Let $\cat{A}$ be a cut system.
-There is a superbicategory $\cat{A}^\bullet$ with objects the class of objects of $\cat{A}$ and with $1$- and $2$-morphisms defined by $\cat{A}^\bullet(a,b) = \cat{A}(a,b)^\bullet$.
-The units of $\cat{A}^\bullet$ are the objects $\Delta_a$ in the cut system, and the composition in the bicategory is given by the canonical extensions $\widetilde{T}$.
-To complete the definition of a superbicategory it only remains to give the associators and unitors, and the super-structure.
-
-\begin{lemma} Given objects $a,b,c,d$ the natural isomorphism $\alpha$ canonically extends to a natural isomorphism $\widetilde{\alpha}$ as in the diagram
-\[
-\xymatrix@C+2pc{
-\cat{A}(a,b)^\bullet \times \cat{A}(b,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[d]_-{\widetilde{T} \times 1} \ar[r]^-{1 \times \widetilde{T}} & \cat{A}(a,b)^\bullet \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\widetilde{\alpha}}\\
-\cat{A}(a,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
-}
-\]
-\end{lemma}
-\begin{proof}
-Suppose $(X,n) \in \cat{A}(a,b)^\bullet, (Y,m) \in \cat{A}(b,c)^\bullet$ and $(Z,t) \in \cat{A}(c,d)^\bullet$ are given.
-The underlying object of $((Z,t) \l (Y, m)) \l (X,n)$ is $(Z \l Y) \l X$, and it is clear that $\alpha_{Z,Y,X}$ is $A_t \otimes A_m \otimes A_n$-linear and therefore defines an isomorphism in $\cat{A}(a,d)^\bullet$
-\[
-\alpha_{Z,Y,X}: ((Z,t) \l (Y, m)) \l (X,n) \lto (Z,t) \l ((Y, m) \l (X,n))\,.
-\]
-Naturality is straightforward.
-\end{proof}
-
-\begin{lemma} Given objects $a,b$ the natural isomorphisms $\eta, \mu$ canonically extend to natural isomorphisms $\widetilde{\eta}, \widetilde{\mu}$ as in the diagram
-\[
-\xymatrix@C+2pc{
-1 \times \cat{A}(a,b)^\bullet \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b)^\bullet \ar@{=>}@<4ex>[l]_-{\widetilde{\eta}} \ar@{=>}@<-4ex>[r]^-{\widetilde{\mu}} \ar[d]^-{1} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b)^\bullet \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
-\cat{A}(a,a)^\bullet \times \cat{A}(a,b)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(A,B)^\bullet & \cat{A}(a,b)^\bullet \times \cat{A}(b,b)^\bullet \ar[l]^-{\widetilde{T}}
-}
-\]
- \end{lemma}
-\begin{proof}
-Let $(X,n) \in \cat{A}(a,b)^\bullet$.
-Forgetting the $A_n$-action on $X$, we have isomorphisms $\eta$ and $\mu$ as in \eqref{eq:unitor_tilde_pre}, which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.
-Since these isomorphisms are natural, they are automatically $A_n$-linear.
-Verifying that these isomorphisms are natural with respect to the larger class of morphisms in $\cat{A}(a,b)^\bullet$ is straightforward.
-\end{proof}
-
-The supercategory structure is given as part of the cut system, so we have:
-
-% The above definition of a cut system is from cutsys10. This is by p.11 there something which gives rise to a cut system in the sense of cutsys6, which is proved there to define a superbicategory.
-\begin{proposition} Given a cut system $\cat{A}$, $\cat{A}^\bullet$ is a superbicategory.
-\end{proposition}
-\begin{proof}
-This follows from Lemma \ref{lemma:constructingsuper}, with associator $\widetilde{\alpha}$ and unitors $\lambda =\widetilde{\mu}^{-1}, \rho = \widetilde{\eta}^{-1}$.
-The coherence follows from the coherence axioms of the cut system.
-\end{proof}
-
-We often confuse a cut system $\cat{A}$ with the associated superbicategory.
-For example, we refer to objects $X$ of $\cat{A}(a,b)^\bullet$ as a $1$-morphisms.
-To distinguish objects of the original category $\cat{A}(a,b)$ we refer to these objects as \emph{normal} or \emph{cut-free} $1$-morphisms.
-We keep the notation $Y \l X$ for the composition rule in $\cat{A}^\bullet$.
-
-The following lemma is useful in verifying the unitor constraint.
-
-\begin{lemma}\label{lemma:unitor_check_help} The commutativity of \eqref{eq:unitor_constraint_cut} is equivalent to commutativity of
-\begin{equation}\label{eq:unitor_check_help1}
-\xymatrix@C+1pc{
-(Y \l \Delta_b) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
-Y \l X \ar[u]^-{\eta_0 \l 1} & Y \l X \ar[l]^-{e_{\pi(b)}} \ar[r]_-{e_{\pi(b)}} & Y \l X \ar[u]_-{1 \l \mu_0}
-}
-\end{equation}
-where $e_{\pi(b)}$ is the idempotent of Definition \ref{defn:idempotent_e}.
-\end{lemma}
-\begin{proof}
-Let $m = \pi(b)$.
-Then $(Y \l \Delta_b) \l X$ has two $A_m$ actions, one from $Y \l \Delta_b$ which we denote by $A_{m_1}$, and the other from the cut with $X$ which we denote by $A_{m_2}$.
-By definition of the canonical extension $\widetilde{T}$ in Appendix \ref{app:proof_cut_extension}, $\eta \l 1$ is the $A_{m_1+m_2}$-linear morphism
-\[
-\eta: S_{m_1 + m_2, m_2} \otimes_{A_{m_2}} ( Y \l X ) \lto (Y \l \Delta_b ) \l X
-\]
-which corresponds under Lemma \ref{lemma:morphisms_two_forms} to
-\[
-\xymatrix@C+1pc{
-Y \l X \ar[r]^-{e_m} & Y \l X \ar[r]^-{\eta_0 \l 1} & (Y \l \Delta_b) \l X
-}\,.
-\]
-Applying the same logic to $\mu$ completes the proof.
-\end{proof}
-
-In a cut system the unitors $\mu, \eta$ go in the opposite direction to what one would expect from the conventions of bicategories.
-This is because it is more natural to describe morphisms out of a cut-free $1$-morphism and into a $1$-morphism carrying a nontrivial Clifford representation, than in the other direction.
-
-\subsection{Cut models}\label{section:cut_models}
-
-\begin{definition} A \emph{cut model} for a superbicategory $\cat{B}$ is a cut system $\cat{A}$ with the same underlying class of objects as $\cat{B}$ and a strong superfunctor $I: \cat{B} \lto \cat{A}^\bullet$ with the property that for every pair of objects $a,b$ the functor
-\[
-I_{a,b}: \cat{B}(a,b) \lto \cat{A}(a,b)^\bullet
-\]
-factors as
-\[
-\xymatrix{
-\cat{B}(a,b) \ar[rr]^-{I_{a,b}} \ar[dr]_-{J_{a,b}} & & \cat{A}(a,b)^\bullet\\
-& \cat{A}(a,b) \ar[ur]_-{\iota}
-}
-\]
-where $J_{a,b}$ is an equivalence of supercategories. We often identify $X$ with $I(X)$.
-\end{definition}
-
-A cut model is an effectively computable model for composition of $1$-morphisms in~$\cat{B}$.
-Given $X: a \lto b$ and $Y: b \lto c$, let us suppose that the composition $Y \circ X$ in $\cat{B}$ is not defined algorithmically: perhaps this object is only identified up to unique isomorphism by a universal property.
-In contrast, the cut $Y \l X$ is computable from $X$ and $Y$, and the strong superfunctor $I$ provides an isomorphism in $\cat{A}(a,c)^\bullet$
-\begin{equation}
-Y \l X \cong Y \circ X\,.
-\end{equation}
-Here $Y \circ X$ is embedded into $\cat{A}^\bullet$ as a cut-free $1$-morphism and the cut $Y \l X$ by definition comes with an $A_{\pi(b)}$-module structure.
-That is, there is an isomorphism of $A_{\pi(b)}$-modules
-\begin{equation}\label{eq:cutvsoriginal}
-Y \l X \cong S_{\pi(b)} \otimes_k (Y \circ X )
-\end{equation}
-or what is the same, an isomorphism of objects in $\cat{A}(a,b)$
-\begin{equation}\label{eq:cutvsoriginal2}
-S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X ) \cong Y \circ X \,.
-\end{equation}
-The general philosophy is that a cut model decomposes composition in $\cat{B}$ into two stages: 
-\begin{itemize}
-\item first form the cut $Y \l X$, and then
-\item tensor $Y \l X$ with $S^*_{\pi(b)}$ to compute $Y \circ X$. 
-\end{itemize}
-The idea is that the desired composition $Y \circ X$ lies inside $Y \l X$ in a way that is ``known'' in the sense that it is encoded by the Clifford action, but which is only \emph{realised} or \emph{constructed} after a computation is done.
-Forming the tensor product $S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ starting with the concretely known object $Y \l X$ can be further decomposed into a $\pi(b)$-step process of ``atomic'' computations, using the diagram of Remark \ref{remark:tensor_and_idempotent}
-\begin{equation}\label{eq:computation_fiber_diagram}
-\xymatrix@C+1pc@R+1pc{
-Z_0 \cong Y \circ X \ar@{.}[d] & Z_1 \ar@{.}[d] & & Z_{\pi(b)-1} \ar@{.}[d] & Z_{\pi(b)} = Y \l X \ar@{.}[d]\\
-0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b)-1  \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b) \ar@{.>}@<0.8ex>[l]
-}\,.
-\end{equation}
-% remark:tensor_in_steps.
-The intermediate objects are $Z_i = S_{i, \pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ for $i < \pi(b)$.
-Each of these objects $Z_i$ is obtained from $Z_{i+1}$ by splitting an idempotent of the form $a^\dagger a$.
-
-Suppose we are in the situation where $Y \circ X$ is identified by a universal property but an explicit object realising this universal property is not given as part of $\cat{B}$.
-Then the result of the $\pi(b)$-step computation depicted above is an explicit object $Z_0$ of $\cat{A}(a,c) \cong \cat{B}(a,c)$ with this universal property.
-Thus the cut system gives a process for constructing representing objects for the uniquely defined isomorphism class $Y \circ X$ of $\cat{B}(a,c)$.
-
-Conceptually, the number of steps in \eqref{eq:computation_fiber_diagram} represents the computational cost of a cut across the object $b$.
-For any cut across this object, $\pi(b)$-steps are necessary to convert the ``uncertainty'' represented by $Y \l X$ with its $A_{\pi(b)}$-action to the certainty of an object of $\cat{A}(a,c)$ (in the sense of Remark \ref{remark:tensor_and_idempotent}).
-In the example of the next section, the cost $\pi(W)$ of cutting across a hypersurface singularity $W$ is determined by its dimension.
-
-\section{The Landau-Ginzburg cut system}\label{section:lg_cut_system}
-
-In this section we introduce the cut system $\cat{L}$, beginning with a sketch of the major pieces and then proceeding to the technical details.
+\section{The superbicategory $\cat{L}$}\label{section:lg_cut_system}
+
+%In this section we introduce the cut system $\cat{L}$, beginning with a sketch of the major pieces and then proceeding to the technical details.
 The objects of the cut system are the same as the objects of the bicategory $\LG$, that is, pairs $(x, W)$ consisting of a set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x]$.
@@
 
-Given objects $(x,W)$ and $(z,V)$ the supercategory $\cat{L}(W, V)$ is
-\[
-\cat{L}(W,V) = \hmf( k[x,z], V - W )^{\omega}\,,
-\]
-where $(-)^\omega$ denotes the idempotent completion; see Remark \ref{remark:idempotent_completion}.
-The objects of $\cat{L}(W,V)$ are therefore pairs $(X,e)$ consisting of a matrix factorisation $X$ of $V - W$ and an idempotent $e: X \lto X$.
-
-Next we sketch the definition of the cut functors for $\cat{L}$. Let $W \in k[x_1,\ldots,x_n], V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ be potentials. The cut functor
+In this section we define a bicategory without units which we call the \textsl{cut system} model of $\LG$.
+Later in Section \ref{??} we will prove that this bicategory is equivalent to $\LG$, although this will not be apparent at first.
+Given objects $(x,W)$ and $(y,V)$ of $\LG$ we define
+\be\label{eq:defnluv}
+\cat{L}(W,V) = \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,
+\ee
+where $(-)^\omega$ denotes the idempotent completion and $(-)^{\bullet}$ the Clifford thickening. The first aim of this section is to define, for any object $(z,U)$ of $\LG$, a functor
 \begin{gather*}
-\cat{L}(W, V) \otimes_k \cat{L}(V, U) \lto \cat{L}(W, U)^\bullet\,\\
-X \otimes Y \mapsto Y \l X
+\cat{L}(V,U) \otimes_k \cat{L}(W,V) \lto \cat{L}(W, U)\,\\
+(Y,X) \mapsto Y \l X
 \end{gather*}
-of degree $m$ is defined on matrix factorisations $X$ of $V - W$ and $Y$ of $U - V$ as follows.
-The object $Y \l X$ is a finite rank matrix factorisation of $W - U$ equipped with an action of the Clifford algebra $A_m$.
-The underlying matrix factorisation is
-\[
-Y \l X = Y \otimes_{k[z]} J_V \otimes_{k[z]} X
-\]
+which we call the \textsl{cut functor}. The cut operation is defined on matrix factorisations $X$ of $V - W$ and $Y$ of $U - V$ as follows, assuming $y = (y_1,\ldots,y_m)$ and writing
+\be\label{eq:defnjacobian}
+J_V = k[y] / ( \partial_{y_1} V, \ldots, \partial_{y_m} V )\,.
+\ee
+
+\begin{lemma} The $\nZ_2$-graded $k[x,z]$-module
+\[
+Y \l X = Y \otimes_{k[y]} J_V \otimes_{k[y]} X
+\]
+with the differential $d_Y \otimes 1 + 1 \otimes d_X$ is a finite rank matrix factorisation of $U - W$.
+\end{lemma}
+\begin{proof}
+Since $V$ is a potential $J_V$ is a finite rank free $k$-module, and it follows that $Y \l X$ is a finite rank free $k[x,z]$-module.
+
+\end{proof}
+%If $\{ e_i \}_{i \in I}$ and $\{ f_j \}_{j \in J}$ are homogeneous bases of $Y, X$ over $k[z,y]$ and $k[y,x]$ respectively, and if $\{ v_k \}_{k \in K}$ is a $k$-basis for $J_V$ (which we give degree zero) then $\{ e_i \otimes v_k \otimes f_j \}_{i,j,k}$ is a $k[x,z]$-basis for $Y \l X$.
+
+\begin{definition} Given morphisms of matrix factorisations $\phi: X \lto X'$ and $\psi: Y \lto Y'$ we define the morphism of matrix factorisations
+\[
+\psi \l \phi: Y \l X \lto Y' \l X'
+\]
+to be induced on the quotient by $\psi \otimes \phi: Y \otimes X \lto Y' \otimes X'$. This is clearly functorial in the sense that for morphisms $\phi': X' \lto X''$ and $\psi': Y' \lto Y''$ we have
+\begin{align}
+( \psi' \l \phi' ) \circ ( \psi \l \phi ) = ( \psi' \psi ) \l ( \phi' \phi )\,,
+\end{align}
+and $1_Y \l 1_X = 1_{Y \l X}$.
+\end{definition}
+
+\begin{remark}
+As an explicit matrix of polynomials in $k[x,y]$ the differential on $Y \l X$ can be obtained from the differentials on $X$ and $Y$ (which involve $k[z,x]$ and $k[y,z]$ respectively) by replacing occurrences of $z$ by a certain square matrix of scalars; see the proof of Theorem \ref{theorem:l_cut_system} for more details.
+\end{remark}
+
+The next step is to equip $Y \l X$ with a Clifford action, which will be defined using the partial derivatives $\partial_{y_i}(d_X)$ and Atiyah classes.
+The Atiyah classes are defined by first taking the technical step of extending scalars
+\begin{equation}\label{eq:completed_tensor_product}
+Y \,\check{\otimes}\, X = Y \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} X
+\end{equation}
+and putting a connection on this module.
+We write $t = (t_1,\ldots,t_m)$ for the quasi-regular sequence of partial derivatives $t_i = \partial_{y_i} V$ and recall that there is by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
+\begin{equation}\label{eq:connection_nabla}
+\nabla: k\llbracket y \rrbracket \lto k\llbracket y \rrbracket \otimes_{k[t]} \Omega^1_{k[t]/k}
+\end{equation}
+the components of which are $k$-linear operators $\partial_{t_i}: k\llbracket y \rrbracket \lto k\llbracket y \rrbracket$.
+A simple example of such a connection is given in Section \ref{example:computing_homs}.
+Using a chosen homogeneous basis $\{ e_i \otimes f_j \}_{i,j}$ for $Y \otimes X$ we may extend the operators $\partial_{t_i}$ extend to $k[x,z]$-linear operators
+\begin{gather*}
+\partial_{t_i}: Y \, \check{\otimes}\, X \lto Y \, \check{\otimes}\, X\\
+e_i \otimes h(y) \otimes f_j \mapsto e_i \otimes \partial_{t_i}( h(y) ) \otimes f_j\,.
+\end{gather*}
+
+\begin{lemma} The operator $[ d_{Y \otimes X}, \partial_{t_i} ]$ is $k[t]$-linear and therefore passes to a $k[x,z]$-linear operator on the quotient $Y \l X = \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
+\end{lemma}
+
+\begin{definition} The $i$th Atiyah class is this odd $k[x,z]$-linear operator
+\[
+\At^{Y,X}_i = [d_{Y \otimes X}, \partial_{t_i}]: Y \l X \lto Y \l X \,.
+\]
+Usually we just write this operator as $\At_i$ where it will not cause confusion.
+\end{definition}
+
+This operator is the $i$th Atiyah class of $Y \,\check{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}.
+A reference for Atiyah classes is \cite{buchweitz_flenner}, but we will prove the necessary properties here for the reader's convenience.
+
+\begin{lemma}\label{lemma:atiyahclosed} The operator $\At_i$ on $Y \l X$ is closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are homotopies
+\be\label{eq:atiyahclosednatural}
+\At^{Y',X'}_i \circ \,( \psi \l \phi ) \simeq ( \psi \l \phi ) \circ \At^{Y,X}_i\,.
+\ee
+That is, the Atiyah classes are \emph{natural}.
+\end{lemma}
+\begin{proof}
+The Atiyah class is closed since
+\[
+[d, \At_i] = [d, [d, \partial_{t_i}]] = 0\,.
+\]
+If $\kappa: Y \otimes X \lto Y' \otimes X'$ is any $k[x,y,z]$-linear even closed operator, 
+\[
+[ \kappa, [ d, \partial_{t_i} ] ] + [ \partial_{t_i}, [\kappa, d]] + [ d, [ \partial_{t_i}, \kappa] ] = 0
+\]
+from which we deduce that $[\partial_{t_i}, \kappa]$ is a homotopy establishing \eqref{eq:atiyahclosednatural}.
+\end{proof}
+
+The other ingredient in defining the Clifford action are the partial derivatives $\partial_{y_i}(d_X)$, as discussed in Section \ref{section:partial}.
+On $Y \otimes X$ we have the odd operator $\partial_{y_i}(d_X) = 1 \otimes \partial_{y_i}(d_X)$ which is a homotopy for the action of $\partial_{y_i}(V - W) = \partial_{y_i}(V)$.
+Hence when we pass to the quotient, $\partial_{y_i}(d_X)$ is a closed odd operator on $Y \l X$.
+
+\begin{definition}\label{defn:cliffordaction_cut} On $Y \l X$ we define odd $k[x,z]$-linear closed operators
+\begin{equation}\label{eq:intro_clifford_act1}
+\gamma_i^\dagger = \At_i\,, \qquad \gamma_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
+\end{equation}
+\end{definition}
+
+\begin{theorem} Given matrix factorisations $Y,X$ as above, the data
+\be
+Y \l X = \left( Y \otimes_{k[y]} J_V \otimes_{k[y]} X, \{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m \right)
+\ee
+defines a representation of $C_m$ in the homotopy category of matrix factorisations, that is, the $\gamma_i, \gamma_i^\dagger$ satisfy the Clifford relations \eqref{eq:clifford_relations}
+up to homotopy.
+\end{theorem}
+\begin{proof}
+This will follow from the considerations of Section \ref{??} but we feel it is worthwhile to give a direct proof, both to demonstrate how straightforward it is and in order to have written down explicit homotopies for the various relations.
+
+By the graded Jacobi identity
+\begin{align*}
+[\At_i, \At_j] &= [\At_i, [d, \partial_{t_j}]]\\
+&= - [\partial_{t_j}, [\At_i, d]] - [d, [\partial_{t_j}, \At_i]]\\
+&= [d, -[\partial_{t_j}, \At_i]]\,.
+\end{align*}
+Hence $[\gamma_i^\dagger, \gamma_j^\dagger] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
+\begin{align*}
+[\partial_{y_i}(d_X), \At_j] &= [\partial_{y_i}(d_X), [d, \partial_{t_j}]]\\
+&= -[\partial_{t_j}, [\partial_{y_i}(d_X), d]] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
+&= -[\partial_{t_j}, t_i] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
+&= -\delta_{ij} + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\,.
+\end{align*}
+Again we set $g_{ij} = [\partial_{t_j}, \partial_{y_i}(d_X)]$ for later use. We compute that
+\begin{align*}
+[ \gamma_i, \gamma^\dagger_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
+&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [ \At_q, \At_j]\\
+&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [d, h_{qj}]\\
+&= \delta_{ij} + \big[d, -g_{ij} - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) h_{qj}\big]\,.
+\end{align*}
+Finally, using Lemma \ref{lemma:commutator_of_lambdas}
+\begin{align*}
+[ \gamma_i, \gamma_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
+&= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
+&\quad + \frac{1}{2}\sum_q \partial_{y_q y_i}(V) \big[ \At_q, \partial_{y_j}(d_X) \big]\\
+&\quad + \frac{1}{4}\sum_{p,q} \partial_{y_py_i}(V) \partial_{y_qy_j}(V) \big[ \At_p, \At_q \big]\\
+&= \partial_{y_iy_j}(V) + [d, - \partial_{y_jy_i}(d_X)]\\
+&\qquad + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \left( -\delta_{iq} + [d, [ \partial_{t_q}, \partial_{y_i}(d_X)]] \right)\\
+&\qquad + \frac{1}{2} \sum_q \partial_{y_qy_i}(V) \left( -\delta_{jq} + [d, [\partial_{t_q}, \partial_{y_j}(d_X)]] \right)\\
+&\qquad + \frac{1}{4}\sum_{p,q} \partial_{y_py_i}(V) \partial_{y_qy_j}(V) [d, -[\partial_{t_q}, \At_p]]\\
+&= [d, c_{ij}]
+\end{align*}
 where
-\[
-J_V = k[z] / ( \partial_{z_1} V, \ldots, \partial_{z_m} V )\,.
-\]
-With the differential $d_Y \otimes 1 + 1 \otimes d_X$, $Y \l X$ is a finite rank matrix factorisation of $U - W$ over $k[x,y]$ by virtue of the fact that $J_V$ is a finite rank free $k$-module.
-As an explicit matrix of polynomials in $k[x,y]$ the differential on $Y \l X$ can be obtained from the differentials on $X$ and $Y$ (which involve $k[z,x]$ and $k[y,z]$ respectively) by replacing occurrences of $z$ by a certain square matrix of scalars; see the proof of Theorem \ref{theorem:l_cut_system} for more details.
-
-It remains to define the action of the generators $a_i$ and $a_i^\dagger$ of $A_m$ on $Y \l X$.
-We give the formulas below; later we will prove that these operators satisfy Clifford relations and that, with this action, $X \otimes Y \mapsto Y \l X$ is a cut functor.
-
-The key ingredients of the Clifford action are the Atiyah classes of $Y \otimes X$, which are defined by first taking the technical step of extending scalars
-\begin{equation}\label{eq:completed_tensor_product}
-Y \,\check{\otimes}\, X = Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X
-\end{equation}
-and putting a connection on this module.
-We write $t = (t_1,\ldots,t_m)$ for the quasi-regular sequence of partial derivatives $t_i = \partial_{z_i} V$ and recall that there is by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
-\begin{equation}\label{eq:connection_nabla}
-\nabla: k\llbracket z \rrbracket \lto k\llbracket z \rrbracket \otimes_{k[t]} \Omega^1_{k[t]/k}
-\end{equation}
-the components of which are $k$-linear operators denoted $\partial_{t_i}: k\llbracket z \rrbracket \lto k\llbracket z \rrbracket$.
-A simple example of such a connection is given in Section \ref{example:computing_homs}.
-The operators $\partial_{t_i}$ extend to $k[x,y]$-linear operators on the free module $Y \, \check{\otimes}\, X$ and the $i$th Atiyah class is the operator
-\[
-\At_i = [d_{Y \otimes X}, \partial_{t_i}]\,.
-\]
-on $Y \,\check{\otimes}\, X$.
-This operator is the $i$th Atiyah class of $Y \,\check{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}.
-A reference for Atiyah classes is \cite{buchweitz_flenner}.
-
-The Atiyah class is $k[t]$-linear and passes to a $k$-linear operator on the quotient $Y \l X$ of $Y \,\check{\otimes}\, X$. We need another operator on this matrix factorisation, for $1 \le j \le m$
-\begin{equation}\label{eq:lambda_defn}
-\lambda_j = 1 \otimes \partial_{z_j}(d_X)\,.
-\end{equation}
-With this notation, the action of the generators $a_i, a_i^\dagger$ of $A_m$ on $Y \l X$ is defined by
-\begin{equation}\label{eq:intro_clifford_act1}
-a_i^\dagger = \At_i
-\end{equation}
-and
-\begin{equation}\label{eq:intro_clifford_act2}
-a_i = - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \At_{q_1} \cdots \At_{q_l}
-\end{equation}
-where $1 \le q_i \le m$ for $1 \le i \le l$. For explicit examples of these operators, see Section \ref{example:computing_homs}.
-
-The remaining components of the cut system $\cat{L}$ are the units $\Delta_W \in \cat{L}(W,W)$, which are the same as those for $\LG$ given in Section \ref{section:superbicatLG}, and the associators and unitors.
-To define the associator, let $W, V, U, Q$ be potentials with $V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ and suppose we are given a triple of composable $1$-morphisms
+\begin{align*}
+c_{ij} &= - \partial_{y_jy_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_qy_j}(V)  [\partial_{t_q}, \partial_{y_i}(d_X)]\\
+&\qquad + \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [\partial_{t_q}, \partial_{y_j}(d_X)]\\
+&\qquad - \frac{1}{4} \sum_{p,q}  \partial_{y_py_i}(V) \partial_{y_qy_j}(V)  [\partial_{t_q}, \At_p]\,.
+\end{align*}
+\end{proof}
+
+\begin{lemma}\label{prop:morphismsarecliffordreps} Given morphisms $\phi: X \lto X', \psi: Y \lto Y'$, the morphism of matrix factorisations $\psi \l \phi$ is a morphism of $C_m$-representations in the homotopy category.
+\end{lemma}
+\begin{proof}
+This follows easily from the fact that Atiyah classes are natural (Lemma \ref{lemma:atiyahclosed}) and the homotopies $\partial_{y_i}(d_X)$ are central (Lemma \ref{lemma:naturalityoflambda}).
+\end{proof}
+
+\begin{proposition}\label{prop:cutisafunctor} The cut operation defines a functor
+\be\label{eq:cutisafunctor}
+\cat{L}(V,U) \otimes_k \cat{L}(W,V) \lto \cat{L}(W, U)
+\ee
+\end{proposition}
+\begin{proof}
+What we have done so far in this section defines a functor
+\[
+\hmf( k[y,z], U - V ) \otimes \hmf( k[x,y], V - W ) \lto \hmf( k[x,z], U - W )^{\omega \bullet}
+\]
+and since the latter category is idempotent complete, this lifts to a functor
+\[
+\hmf( k[y,z], U - V )^{\omega} \otimes \hmf( k[x,y], V - W )^{\omega} \lto \hmf( k[x,z], U - W )^{\omega \bullet}\,.
+\]
+Explicitly, this functor is given for $(Y,e_Y) \in \cat{L}(V,U)$ and $(X,e_X) \in \cat{L}(W,V)$ by
+\[
+(Y, e_Y) \l (X, e_X) = (Y \l X, e_Y \l e_X)\,.
+\]
+Now suppose we have representations $( Y, \{ \rho_j, \rho_j^\dagger \}_{j=1}^r )$ of $C_r$ in $\cat{L}(V,U)$ and $( X, \{ \tau_l, \tau^\dagger_l \}_{l=1}^s )$ of $C_s$ in $\cat{L}(W,V)$.
+Here $Y,X$ may come equipped with idempotents but these are easily handled so we ignore them in what follows.
+Since the cut operation is functorial, we have representations of $C_r$ and $C_s$ on $Y \l X$ given by
+\[
+\big\{ \rho_j \l 1_X, \rho_j^\dagger \l 1_X \big\}_{j=1}^r\,, \qquad \big\{ 1_Y \l \tau_l, 1_Y \l \tau_l^\dagger \big\}_{l=1}^s\,.
+\]
+The operators from the action of $C_r$ anticommute with the operators from the action of $C_s$ because they act on different components of a tensor product.
+Moreover, both actions anticommute with the new $C_m$ action $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ coming from the cut, by Lemma \ref{prop:morphismsarecliffordreps}.
+Thus $Y \l X$ is equipped with the structure of a $C_r \otimes C_m \otimes C_s \cong C_{r+m+s}$-representation.
+\end{proof}
+
+In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.
+
+\begin{definition} A \textsl{(super)bicategory without units} has all the data and satisfies all the conditions of a (super)bicategory, with the exception of the existence of unit $1$-morphisms, unitors, and their coherence diagram.
+\end{definition}
+
+\begin{definition} The superbicategory without units $\cat{L}$ has
+\begin{itemize}
+\item \textbf{Objects:} same as $\LG$, that is, potentials $(k[x], W)$.
+\item \textbf{$1$- and $2$-morphisms:} defined by \eqref{eq:defnluv}.
+\item \textbf{Composition:} defined by the cut operation \eqref{eq:cutisafunctor}.
+\item \textbf{Associators:} given a triple of composable $1$-morphisms
 \begin{equation}\label{eq:composable_triple}
-\xymatrix{
+\xymatrix@C+2pc{
 (q, Q) & (y, U) \ar[l]_-{Z} & (z,V) \ar[l]_-{Y} & (x,W) \ar[l]_-{X}
@@
 \end{equation}
-The isomorphism of matrix factorisations
+with $V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ the isomorphism
 \begin{gather*}
-\alpha: Z \l (Y \l X) = Z \otimes J_U \otimes ( Y \otimes J_V \otimes X ) \lto (Z \otimes J_U \otimes Y) \otimes J_V \otimes X = (Z \l Y) \l X,\\
+\alpha: Z \l (Y \l X) \lto (Z \l Y) \l X,\\
 z \otimes (y \otimes x) \mapsto (z \otimes y) \otimes x
 \end{gather*}
-turns out to be $A_m \otimes A_p$-linear, and defines the associator for $\cat{L}$.
-
-The unitors can also be described by explicit formulas.
-Given $X \in \cat{L}(W,V)$ as above with homogeneous basis $e_i$ as a $\mathbb{Z}_2$-graded $k[x,z]$-module, we define morphisms of matrix factorisations
+is $C_m \otimes C_p$-linear (see Lemma \ref{lemma:associator} below) and is the associator for $\cat{L}$.
+\end{itemize}
+\end{definition}
+
+\begin{lemma}\label{lemma:associator} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $C_m \otimes C_p$-linear.
+\end{lemma}
+\begin{proof}
+We prove the $C_p$-linearity of $\alpha$, the proof for $C_m$ is similar.
+The algebra $C_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$.
+The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of
+\[
+M = Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
+\]
+relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
+Specifically, the generator $C_i^{\dagger}$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
+But this operator can be identified with an Atiyah class of the linear factorisation
+\begin{equation}\label{eq:assoc_proof_M}
+Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X \big)
+\end{equation}
+relative to the ring morphism
+\begin{equation}\label{eq:assoc_proof_M2}
+k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
+\end{equation}
+By the same argument the action of $C_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} Y \big) \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}.
+It is therefore clear that the associator $\alpha$ identifies these two actions.
+\end{proof}
+
+\begin{theorem} Thus defined $\cat{L}$ is a superbicategory without units.
+\end{theorem}
+\begin{proof}
+The only thing to check is the coherence of the associator, which is trivial.
+\end{proof}
+
+\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}.
+To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$.
+The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is
+\[
+e_m' = a_1 \cdots a_m a_m^\dagger \cdots a_1^\dagger\,.
+\]
+Using \eqref{eq:intro_clifford_act1} and \eqref{eq:intro_clifford_act2} we can write down the explicit form of this idempotent acting on $Y \l X$.
+On this object each of the $a_i$'s acts simply as $- \lambda_i$ because all of the $a_j^\dagger$'s appear to the right.
+Hence on $Y \l X$
+\begin{align*}
+e_m' &= (-1)^{\binom{m}{2}} a_1 \cdots a_m a_1^\dagger \cdots a_m^\dagger \\
+&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
+\end{align*}
+which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.
+
+In \emph{ibid.} we constructed finite models of convolutions $Y \circ X$ one pair $(Y,X)$ at time.
+To make this assignment of finite models coherently for all $1$-morphisms in $\LG$ simultaneously it is natural to identify the Clifford actions which underlie the idempotents, as we do here.
+\end{remark}
+
+\begin{remark} There is a question of whether or not the $A_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
+But Atiyah classes are independent, up to homotopy, of the choice of connection, and it is easy to see that the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis.
+Hence the action is indeed canonical.
+\end{remark}
+
+\begin{remark}\label{remark:inflation} Let $V \in k[z_1,\ldots,z_m]$ be a potential and choose a $k$-basis for $J_V$.
+Then multiplication by $z_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[z_i]$ over $k$.
+
+Given $X$ and $Y$ the cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $z_i$ by the scalar matrix $[z_i]$.
+This ``inflation'' produces a matrix of polynomials over $k[x,y]$.
+\end{remark}
+
+\section{The equivalence of $\cat{L}$ and $\LG$}
+
+We prove that the cut functor defined in Section \ref{section:lg_cut_system} models composition in $\LG$ by providing an equivalence of this bicategory with $\cat{L}$.
+This is done by presenting the cut $Y \l X$ with its Clifford action as the solution of the problem of finding a finite model for the matrix factorisation $Y \otimes X$ over $k[x,z]$.
+
+As was mentioned in Section \ref{section:superbicatLG}, $Y \otimes X$ is a matrix factorisation of infinite rank over $k[x,z]$.
+The obvious notion of a ``finite model'' would be a finite rank matrix factorisation to which $Y \otimes X$ is homotopy equivalent, but providing such a finite model generically seems impossible.
+We propose a different notion of finite model based on Clifford representations, and solve the problem in this setting.
+The solution we give here builds on earlier progress on this problem with Dyckerhoff \cite{dm1102.2957}.
+
+\begin{setup}\label{setupforfusion} The situation is as follows:
+\begin{itemize}
+\item $(x,W), (y, V), (z,U)$ are objects of $\LG$ with $k[y] = k[y_1,\ldots,y_m]$.
+\item $Y$ is a finite rank matrix factorisation of $U - V$ over $k[y,z]$.
+\item $X$ is a finite rank matrix factorisation of $V - W$ over $k[x,y]$.
+\end{itemize}
+\end{setup}
+
+The strategy is to consider the direct sum of (shifted) copies
+\begin{equation}\label{eq:larger_object}
+V \otimes_k ( Y \otimes X ) = (Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
+\end{equation}
+where $V$ is the exterior algebra
+\[
+V = \bigwedge( k[1]^{\oplus m} )\,.
+\]
+We find a finite model of this larger object, and in addition record a method of extracting the subobject $Y \otimes X$.
+Some necessary background is presented in Section \ref{section:homolog_fix} and Section \ref{section:cliffordactkos}, and finally the full construction is presented in Section \ref{section:theequivalence}.
+The overall strategy is:
+
+\begin{strat}\label{strategy} We show there is a differential $d_K$ ($K$ stands for Koszul) such that
+\begin{itemize}
+\item[1)] The complex $( V \otimes_k ( Y \otimes X ), d_K )$ has a finite model: there is a homotopy equivalence
+\be
+(Y \l X, 0) \cong \big( V \otimes_k ( Y \otimes X ), d_K \big)
+\ee
+ over $k[x,z]$ where $Y \l X$ is the graded module from Section \ref{section:lg_cut_system}.
+\item[2)] The perturbation lemma (Section \ref{section:homolog_fix}) promotes this to a homotopy equivalence
+\be\label{eq:woofeif}
+(Y \l X, d_{Y \otimes X}) \cong \big( V \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big)
+\ee
+by mixing in the differential $d_{Y \otimes X}$ on both sides.
+\item[3)] Using Section \ref{section:cliffordactkos} we show there is a homotopy equivalence
+\be\label{eq:woofeif2}
+\big( V \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big) \cong \big( V \otimes_k ( Y \otimes X ), d_{Y \otimes X}\big)\,.
+\ee
+\item[4)] Combining \eqref{eq:woofeif} and \eqref{eq:woofeif2} we have the desired finite model
+\be\label{eq:iso_of_clifford_modelfinite}
+(Y \l X, d_{Y \otimes X}) \cong ( V \otimes_k ( Y \otimes X ), d_{Y \otimes X})\,.
+\ee
+There is a canonical action of the Clifford algebra $C_m$ on $V$ and thus on the right hand side, which ``remembers'' how to extract $Y \otimes X$ from this larger object.
+Transferring this action yields the operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ on $Y \l X$ from Section \ref{section:lg_cut_system}.
+\end{itemize}
+\end{strat}
+
+In conclusion, there is an isomorphism of Clifford representations \eqref{eq:iso_of_clifford_modelfinite} in the homotopy category of finite rank matrix factorisations of $U - W$ over $k[x,z]$, and this is our solution to the problem of finding a finite model of $Y \otimes X$.
+Once we have established all of this, proving that $\cat{L}$ and $\LG$ are equivalent bicategories will be immediate.
+
+\subsection{Homological perturbation and fixed points}\label{section:homolog_fix}
+
+A fundamental role in this paper is played by the homological perturbation lemma.
+While this result is usually stated for complexes the standard results generalise immediately to linear factorisations, and in this section we collect these standard results.
+But we begin by recalling the motivating problem for which the perturbation lemma is the solution.
+
+Let $Q$ be a complex of infinite rank free abelian groups.
+Suppose that the cohomology is finitely generated, so that $Q$ contains in some sense only a ``finite'' amount of information.
+One can ask for a description which makes this finiteness manifest: the obvious answer is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.
+
+A \emph{deformation retract} of complexes is a pair of morphisms
+\begin{equation}\label{eq:example_defo_retract}
+\xymatrix@C+2pc{
+C \ar@<-1ex>[r]_\nabla & Q, \ar@<-1ex>[l]_f
+} \quad \phi
+\end{equation}
+and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $f \nabla = 1_C, \nabla f = 1_Q - [d_Q, \phi]$ so that $f, \nabla$ are mutually inverse homotopy equivalences.
+A deformation retract is \emph{strong} if it satisfies some additional conditions, listed below.
+The point is that if $C$ is finitely generated, then \eqref{eq:example_defo_retract} gives the desired finite representative in the homotopy equivalence class of $Q$.
+
+\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-modules
+\[
+\xymatrix@C+2pc@R+1pc{
+0 \ar[d] \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar[d]^-{x}\\
+k \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar@/_3pc/@{.>}[u]_-{\phi}
+}
+\]
+in which the first column is the complex $C$ which has $k$ concentrated in degree zero, and the second column $Q$ is the Koszul complex on $x$.
+The map $f: k[x] \lto k$ sends every polynomial to its constant term, while $\nabla: k \lto k[x]$ is the inclusion of the constants.
+The operator $\phi$ is defined by $\phi( x^n ) = x^{n-1}$ and $\phi(1) = 0$.
+Together these maps are a deformation retract giving $k$ as the ``finite model'' of $Q$.
+\end{example}
+
+Suppose now that a deformation retract computing a finite representative for $Q$ cannot be found immediately, but that we know how to decompose the differential as $d_Q = d + \tau$ in such a way that there is a finite representative for the complex $(Q,d)$.
+The perturbation lemma allows us, with some conditions, to ``mix in'' the operator $\tau$ to obtain a finite model for the original complex $Q$.
+\\
+
+Let $R$ be a commutative ring and $W \in R$.
+Everything we say applies, in the case where $W = 0$, to both $\mathbb{Z}_2$-graded and $\mathbb{Z}$-graded complexes.
+For our purposes the reformulation of the perturbation lemma in terms of fixed points by Barnes and Lambe is more natural, so we emphasise the ``splitting homotopies'' of \cite{barneslambe}.
+
+\begin{definition} A \emph{splitting homotopy} on a linear factorisation $(A,d)$ of $W$ is a degree $-1$ operator $\phi$ on $A$ satisfying
+\begin{itemize}
+\item[(i)] $\phi^2 = 0$,
+\item[(ii)] $\phi d \phi = \phi$.
+\end{itemize}
+A \emph{morphism} $(A,d, \phi) \lto (A,d',\phi')$ of splitting homotopies is a morphism $\alpha: A \lto A'$ of linear factorisations satisfying $\phi' \alpha = \alpha \phi$.
+\end{definition}
+
+The condition (ii) says that $\phi$ is a \emph{fixed point} of the operator $F(x) = x d x$.
+
+\begin{definition} A \emph{strong deformation retract} of linear factorisations of $W$ is a pair of morphisms of linear factorisations
+\begin{equation}\label{eq:defn_sdr}
+\xymatrix@C+2pc{
+(M,d) \ar@<-1ex>[r]_\nabla & (A,d), \ar@<-1ex>[l]_f
+} \quad \phi
+\end{equation}
+together with a degree $-1$ operator $\phi: A \lto A$ satisfying
+\begin{itemize}
+\item[(i)] $f \nabla = 1_M$,
+\item[(ii)] $\nabla f = 1_A - [d, \phi]$,
+\item[(iii)] $\phi^2 = 0$,
+\item[(iv)] $\phi \nabla = 0$,
+\item[(v)] $f \phi = 0$.
+\end{itemize}
+A \emph{morphism} of strong deformation retracts is a commutative diagram
+\[
+\xymatrix@C+2pc{
+(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\nabla & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_f\\
+(M',d') \ar@<-1ex>[r]_{\nabla'} & (A',d') \ar@<-1ex>[l]_{f'}
+}
+\]
+that is, a pair of morphisms $\alpha, \beta$ such that $\beta \nabla = \nabla' \alpha$, $\alpha f = f' \beta$ and $\phi' \beta = \beta \phi$.
+\end{definition}
+
+We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}.
+Namely, a strong deformation retract in the above sense is the same as a special deformation retract in the sense of \emph{ibid.} with $h = - \phi$.
+
+\begin{lemma}\label{lemma:equivocate} There is an equivalence between the category of splitting homotopies $\cat{C}_1$ and the category of  strong deformation retracts $\cat{C}_2$.
+\end{lemma}
+\begin{proof}
+We briefly recall the construction from \cite[p.883]{barneslambe}, which is not stated in terms of categories but is obviously functorial.
+Given a strong deformation retract \eqref{eq:defn_sdr} the data $(A, \phi)$ is a splitting homotopy.
+In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $\pi = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(\phi)$ with the associated projection $f$ and inclusion $\nabla$.
+Then this is a strong deformation retract, together with the original $\phi$.
+\end{proof}
+
+%Taking splitting homotopies as the primary object has the advantage of hiding some of the incidental complexity in the perturbation lemma.
+Here is the problem that the formalism is designed to solve: suppose $(A,d)$ is a linear factorisation of $W$ and that $\tau$ is a degree $+1$ operator on $A$ such that $(A, d + \tau)$ is a linear factorisation of $V$ (possibly different to $W$).
+This $\tau$ is called the \emph{perturbation}.
+
+\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(\pi) \cong \im(\pi')$ as graded $R$-modules, where $\pi = 1_A - [d, \phi]$ and $\pi' = 1_A - [d + \tau, \phi']$.
+\end{definition}
+
+That is, with $\xi = d + \tau$ the problem is to find a fixed point of the operator
+\[
+F(x) = x \xi x
+\]
+among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(\pi)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
+\[
+\phi_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \phi = \phi - \phi \tau \phi + \phi \tau \phi \tau \phi - \cdots
+\]
+is a solution of this fixed point problem:
+
+\begin{theorem}[Perturbation lemma]\label{theorem:pertlemma} Suppose $\phi \tau$ has finite order.
+Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi)$ and satisfies the isomorphism condition in the transference problem.
+\end{theorem}
+\begin{proof}
+The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations (see comments in blah).
+\end{proof}
+
+The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}.
+The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
+\begin{equation}\label{eq:perturbedsdr}
+\xymatrix@C+2pc{
+(M,d_\infty) \ar@<-1ex>[r]_{\nabla_\infty} & (A, \xi), \ar@<-1ex>[l]_{f_\infty}
+} \quad \phi_\infty
+\end{equation}
+where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
+\begin{align*}
+\nabla_\infty &= \nabla - \phi A \nabla,\\
+f_\infty &= f - f A \phi,\\
+d_\infty &= d + f A \nabla\,.
+\end{align*}
+As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
+\[
+\im(1 - [\xi, \phi_\infty]) \cong \im(\pi) = M
+\]
+be identified with $M$, and the induced maps are the $\nabla_\infty, f_\infty, d_\infty$ given above.
+It is also possible to give a direct proof as in \cite{crainic}.
+To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one just studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.
+
+\subsection{Clifford actions and Koszul complexes}\label{section:cliffordactkos}
+% spkos series
+
+Let $(X,d)$ be a complex of $R$-modules on which $t_1,\ldots,t_n \in R$ act null-homotopically.
+Tensoring $X$ with the Koszul complex $K(t_i)$ yields the same complex as taking the cone of $t_i \cdot 1_X = 0: X \lto X$, and therefore we have a homotopy equivalence
+\be
+K(t_i) \otimes_R X \cong \operatorname{cone}( t_i \cdot 1_X ) \cong X \oplus X[1] \cong ( k \oplus k[1] ) \otimes_k X\,.
+\ee
+Iterating this operation we obtain a homotopy equivalence with $K = K(t_1,\ldots,t_n)$,
+\be\label{eq:cliffordactkos_1}
+K \otimes_R X \cong \bigwedge( k[1]^{\oplus n} ) \otimes_k X
+\ee
+where the left hand side is a complex with differential $d_K + d$ and the right hand side has only the differential $d$. On the right hand side we have an obvious action of
+\be
+C_n = \End_k\left( \bigwedge( k[1]^{\oplus n} ) \right)
+\ee
+and the purpose of this section is to compute the corresponding action of $C_n$ via closed odd endomorphisms of the complex $K \otimes_R X$. In fact we will do this more generally:
+
+\begin{setup} Let $R$ be a $k$-algebra and write $\otimes$ for $\otimes_R$.
+Let $(X,d)$ be a linear factorisation of $W \in R$ and $t_1,\ldots,t_n$ a sequence of elements of $R$ acting null-homotopically on $X$.
+We choose odd $R$-linear operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$ for $1 \le i \le n$.
+\end{setup}
+
+\begin{remark} All equalities in this section mean equalities of linear maps. If we mean homotopy, we will explicitly write $\simeq$.
+\end{remark}
+
+We introduce formal variables $\theta_1,\ldots,\theta_n$ of odd degree and set
+\[
+V = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
+\]
+On this $\nZ$-graded $k$-module there are canonical odd $k$-linear operators $\theta_i, \theta_i^*$ defined as in Definition \ref{defn:contraction}.
+The Koszul complex $K$ of the sequence $t_1,\ldots,t_n$ is defined by
+\begin{equation}\label{defn:koszul}
+K = V \otimes_k R, \qquad d_K = \sum_{i=1}^n t_i \theta_i^*\,.
+\end{equation} 
+The tensor products $K \otimes X = (K \otimes X, d + d_K)$ and $V \otimes_k X = ( V \otimes_k X, d )$ are both linear factorisation of $W$ with isomorphic underlying graded modules.
+On this underlying graded module $K \otimes X \cong V \otimes_k X$ we have the odd $R$-linear operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$ and we introduce the following even $R$-linear operators
+\begin{align*}
+\delta &= \sum_{i=1}^n \lambda_i \theta_i^*,\\
+\exp(-\delta) &= \sum_{m \ge 0} (-1)^m \frac{1}{m!} \delta^m\,.
+\end{align*}
+Observe that $\delta$ is nilpotent so the exponential makes sense.
+
+\begin{proposition}\label{prop:equivalencekoszul} There are mutually inverse isomorphisms of linear factorisations
+\be\label{eq:equivalencekoszul}
+\xymatrix@C+5pc{ K \otimes X\; \ar@<1ex>[r]^-{ \exp(\delta) } & \;V \otimes_k X \ar@<1ex>[l]^-{ \exp(-\delta) } }
+\ee
+where the left hand side has differential $d + d_K$ and the right hand side has $d$.
+\end{proposition}
+
+We break the proof into a series of lemmas:
+
+\begin{lemma}\label{lemma:pert1} $[d, \delta^m] = m \delta^{m-1} d_K$ for $m \ge 1$.
+\end{lemma}
+\begin{proof}
+The case of $m = 1$ is clear
+\[
+[d, \delta] = \sum_i [d, \lambda_i] \theta_i^* = d_K\,.
+\]
+For $m > 1$ we use the case $m = 1$ to show that
+\[
+[ d, \delta^m ] = \sum_{i=0}^{m-1} \delta^i [d, \delta] \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i d_K \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i \delta^{m-i-1} d_K = m \delta^{m-1} d_K\,.
+\]
+\end{proof}
+
+\begin{lemma}\label{lemma:pert2} $[ d, \exp(-\delta) ] = - \exp(-\delta) d_K$ and $[ d, \exp(\delta) ] = \exp(\delta) d_K$.
+\end{lemma}
+\begin{proof}
+We prove the first identity using Lemma \ref{lemma:pert1}, the second is the same:
+\begin{align*}
+[d, \exp(-\delta)] &= \sum_{m \ge 1} \frac{(-1)^m}{m!} [ d, \delta^m ]\\
+&= \sum_{m \ge 1} \frac{(-1)^m}{m!} m \delta^{m-1} d_K\\
+&= - \sum_{m \ge 0} \frac{(-1)^m}{m!} \delta^m d_K\\
+&= - \exp(-\delta) d_K
+\end{align*}
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:equivalencekoszul}]
+It suffices to show $\exp(-\delta)$ is a morphism of linear factorisations. But using Lemma \ref{lemma:pert2}
+\[
+(d + d_K) \exp(-\delta) - \exp(-\delta) d = [d, \exp(-\delta)] + d_K \exp(-\delta) = 0
+\]
+and similarly for the other equation.
+\end{proof}
+
+\begin{definition}\label{defn:transfer_contract} Let $\gamma$ be a homogeneous $R$-linear operator on $V \otimes_k X$.
+We define the \textsl{transfer} $\cat{T}(\gamma)$ to be the homogeneous $R$-linear operator on $K \otimes X$ induced by $\gamma$ using the equivalence \eqref{eq:equivalencekoszul}, that is,
+\be
+\cat{T}(\gamma) = \exp(-\delta) \gamma \exp(\delta)\,.
+\ee
+\end{definition}
+
+\begin{remark} We do not necessarily require that $\gamma$ be closed, but since
+\be
+[\cat{T}(\gamma), d_K + d] = \cat{T}( [\gamma, d] )
+\ee
+if $\gamma$ is a closed operator then so is $\cat{T}(\gamma)$. 
+\end{remark}
+
+Of particular interest are the transfers of the generators $\theta_i, \theta_i^*$ of the Clifford action. The transfer of the contraction operator $\theta_i^*$ is easy:
+
+\begin{lemma} $\cat{T}(\theta_i^*) = \theta_i^*$.
+\end{lemma}
+\begin{proof}
+Since $\theta_i^*$ commutes with $\delta$.
+\end{proof}
+
+However the calculation of $\cat{T}(\theta_i)$ is much more involved.
+To compute $\cat{T}(\gamma)$ the strategy is to try and commute $\gamma$ past $\exp(-\delta)$ and see what happens.
+To this end we must first compute $[\gamma, \delta^m]$.
+We begin the calculations with some general statements about graded commutators.
+
+To this end let $A$ be a $\nZ$-graded $\nQ$-algebra and $a,b,c$ homogeneous elements.
+
+\begin{lemma} We have
+\begin{align}
+[ab,c] &= a[b,c] + (-1)^{|b||c|} [a,c]b\,,\\
+[a,bc] &= [a,b]c + (-1)^{|a||b|} b[a,c]\,. \label{eq:commutator_with_product}
+\end{align}
+\end{lemma}
+
+We adopt the following notation for iterated commutators
+
+\begin{definition} The iterated commutator $[a,b]^{(m)}$ is defined by $[a,b]^{(0)} = b$ and
+\[
+[a,b]^{(m+1)} = [a, [a,b]^{(m)}]\,.
+\]
+Observe that $[a,b]^{(m)}$ is a linear function of $b$, but not $a$.
+\end{definition}
+
+\begin{lemma}\label{lemma:woop3} For $m \ge 1$ we have
+\[
+[a,b^m] = \sum_{i=0}^{m-1} (-1)^{i|a||b|} b^i [a,b] b^{m-i-1}\,.
+\]
+\end{lemma}
+\begin{proof}
+Easy proof by induction using \eqref{eq:commutator_with_product}.
+\end{proof}
+
+\begin{lemma}\label{lemma:woop4} For $m \ge 1$ we have
+\be
+a^m [a, b] = \sum_{\substack{0 \le i,j \le m \\ i+j=m}} \binom{m}{i} [a,b]^{(i+1)} a^j\,.
+\ee
+\end{lemma}
+\begin{proof}
+By induction, with the case $m = 1$ being clear. Using the inductive hypothesis
+\[
+a^{m+1} [a, b] = \sum_{i+j=m} \binom{m}{i} a [a,b]^{(i+1)} a^j = \sum_{i+j=m} \binom{m}{i} \Big[ [a,b]^{(i+2)} a^j + [a,b]^{(i+1)} a^{j+1} \Big]\,.
+\]
+The powers of $a$ range from $0$ to $m+1$ and the coefficient of $a^j$ for $1 \le j \le m$ is
+\[
+\binom{m}{m-j} [a,b]^{(m-j+2)} + \binom{m}{m-j+1} [a,b]^{(m-j+2)} = \binom{m+1}{m+1-j} [a,b]^{(m-j+2)}\,.
+\]
+The coefficient of $a^0$ is $[a,b]^{(m+2)}$ and the coefficient of $a^{m+1}$ is $[a,b]^{(1)}$, so we are done.
+\end{proof}
+
+\begin{lemma}\label{lemma_iteratedcomm} Let odd elements $a_i, b_i \in A$ be given for $1 \le i \le n$ such that $[a_i, b_j] = 0$ for all $1 \le i,j \le n$ and define
+\[
+D = \sum_{i=1}^n a_i b_i\,.
+\]
+Suppose $[b_i,c] = 0$ for $1 \le i \le n$. Then for $m \ge 0$
+\be\label{eq:lemma_iteratedcomm}
+[D, c]^{(m)} = (-1)^{m|c|} \sum_{1 \le q_1,\ldots,q_m \le n} [a_{q_m}, [a_{q_{m-1}}, \ldots, [ a_{q_1}, c] \cdots ]] b_{q_1} \cdots b_{q_m}\,.
+\ee
+\end{lemma}
+\begin{proof}
+For convenience we introduce, for any tuple of indices $\bold{q} = (q_1,\ldots,q_m)$ of integers $1 \le q_i \le n$, the notation
 \begin{gather}
-\mu_0: X \lto \Delta_V \l X \,, \\
-\mu_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j \Theta_{i_1} \ldots \Theta_{i_l} \left\{ \partial^{z,z'}_{[i_l]}(d_X) \cdots \partial^{z,z'}_{[i_1]}(d_X) \right\}_{ji} \otimes e_j\label{eq:explicit_mu0}
+\tau_{\bold{q}} = [ a_{q_m}, [ a_{q_{m-1}}, \ldots [ a_{q_1}, c ] \cdots ] \label{defn:tau}\\
+b_{\bold{q}} = b_{q_1} \cdots b_{q_m} \label{defn:bq}\,.
 \end{gather}
-and
-\begin{gather}
-\eta_0: X \lto X \l \Delta_W \,,\\
-\eta_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j (-1)^{\binom{l}{2} + l|e_i|} e_j \otimes \left\{ \partial^{x,x'}_{[i_1]}(d_X) \cdots \partial^{x,x'}_{[i_l]}(d_X) \right\}_{ji} \Theta_{i_1} \ldots \Theta_{i_l}
-\end{gather}
-To make sense of these formulas, note that $\Delta_V$ is a matrix factorisation of $V(z) - V(z')$ over $k[z,z']$ and $\Delta_W$ is a matrix factorisation of $W(x) - W(x')$ over $k[x,x']$, while the divided difference operators are defined by
-\[
-{}^{t_i}(-): k[x,x'] \lto k[x,x']\,, \qquad f \mapsto f|_{x_i \mapsto x'_i}
-\]
-and
-\[
-\partial^{x,x'}_{[i]}: k[x,x'] \lto k[x,x']\,, \qquad f \mapsto \frac{{}^{t_1 \ldots t_{i-1}} f - {}^{t_1 \ldots t_i} f}{x_i - x'_i}
-\]
-and in the same way for $z,z'$.
-For a concrete example of these formulas see \cite{lgdual_survey}.
-The actual unitors are the morphisms $X \lto \Delta_V \l X$ and $X \lto X \l \Delta_W$ in $\cat{L}(W,V)^\bullet$ corresponding to $\mu_0$ and $\eta_0$ under the bijection of Lemma \ref{lemma:morphism_out_1}.
-It is not meant to be clear \emph{a priori} that these formulas even define morphisms, let alone that they satisfy the axioms for unitors; all these checks will be performed below.
-\\
-
-The major theorem, to be proved over the course of this section:
-
-\begin{theorem}\label{theorem:l_cut_system} $\cat{L}$ is a cut system.
+For $m = 0$ the right hand side of \eqref{eq:lemma_iteratedcomm} is $c$ by convention, so the statement is trivial. We compute using the inductive hypothesis that
+\begin{align*}
+[D, c]^{(m+1)} &= [ D, [D, c]^{(m)} ]\\
+&= \big[D, (-1)^{m|c|} \sum_{\bold{q}} \tau_{\bold{q}} b_{\bold{q}}\big]\\
+&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i [ a_i b_i , \tau_{\bold{q}} b_{\bold{q}}]\\
+&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i \left( a_i b_i \tau_{\bold{q}} b_{\bold{q}} - \tau_{\bold{q}} b_{\bold{q}} a_i b_i \right)\\
+&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i \left( (-1)^{|c|} a_i \tau_{\bold{q}} b_{\bold{q}} b_i - (-1)^m \tau_{\bold{q}} a_i b_{\bold{q}} b_i \right)\\
+&= (-1)^{(m+1)|c|} \sum_{\bold{q}, i} [ a_i, \tau_{\bold{q}} ] b_{\bold{q}} b_i
+\end{align*}
+which completes the proof.
+\end{proof}
+
+Eventually we are going to substitute $a_i = \lambda_i, b_i = \theta_i^*$ so that $D = \delta$, and we will take further $c = \gamma$.
+In this notation, the aim of all of this is to compute the commutators $[c, D^m]$ and then $[c, \exp(-D)]$.
+Since most of the calculation can be done in $A$, so we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.
+
+\begin{lemma}\label{lemma:commutator_wha} For $m \ge 1$
+\[
+[ c, D^m ] = \sum_{i=0}^{m-1} (-1)^{(i+1)|c| + 1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}\,.
+\]
+\end{lemma}
+\begin{proof} 
+By Lemma \ref{lemma:woop3} we have
+\begin{equation}\label{eq:catfish}
+[ c, D^m ] = \sum_{p=0}^{m-1} D^p [ c, D ] D^{m-p-1} = -\sum_{p=0}^{m-1} D^p [ c, D ] D^{m-p-1}\,.
+\end{equation}
+Then using Lemma \ref{lemma:woop4} this becomes
+\be
+-\sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} [D, c]^{(i+1)} D^{m-p-1+j}
+\ee
+which by Lemma \ref{lemma_iteratedcomm} equals
+\be
+\sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} (-1)^{(i+1)|c| + 1} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}
+\ee
+which is what we needed to show.
+\end{proof}
+
+Putting this all together:
+
+\begin{proposition}\label{prop:ccommutesexpD} Let $A$ be a $\nZ_2$-graded $\nQ$-algebra and
+\begin{itemize}
+\item Let $a_i, b_i \in A$ be odd elements with $[a_i,b_j] = 0$ for $1 \le i,j \le n$.
+\item Assume that $D = \sum_{i=1}^n a_i b_i$ has finite order, that is, $D^r = 0$ for some $r > 0$.
+\item Let $c \in A$ be an odd element, with $[b_i, c] = 0$ for $1 \le i \le n$.
+\end{itemize}
+Then
+\be\label{eq:ccommutesexpD}
+[c, \exp(-D)] = - \sum_{m \ge 1} \frac{1}{m!} \sum_{q_1,\ldots,q_m} [ a_{q_m}, [ a_{q_{m-1}}, \ldots [ a_{q_1}, c ] \cdots ] b_{q_1} \cdots b_{q_m} \exp(-D)\,.
+\ee
+\end{proposition}
+\begin{proof}
+Using Lemma \ref{lemma:commutator_wha}
+\begin{align*}
+[c, \exp(-D)] &= \sum_{m \ge 0} \frac{(-1)^m}{m!} [c, D^m]\\
+&= \sum_{m \ge 0} \frac{(-1)^{m+i}}{m!} \sum_{i=0}^{m-1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}\,.
+\end{align*}
+Rewriting this sum in terms of the variable $t = m - i - 1$ yields
+\[
+- \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^{t}}{(t+i+1)!} \sum_{i \le p \le t+i}  \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{t}\,.
+\]
+Using Lemma \ref{lemma:combin} below this may be rewritten as
+\[
+- \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{t!} \frac{1}{(i+1)!} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{t}
+\]
+which clearly agrees with \eqref{eq:ccommutesexpD}.
+\end{proof}
+
+\begin{lemma}\label{lemma:combin} For integers $a, b \ge 0$
+\begin{equation}\label{eq:combin}
+\frac{b!}{(a+b+1)!} \sum_{a \le m \le a + b} \binom{m}{a} = \frac{1}{(a+1)!}
+\end{equation}
+\end{lemma}
+\begin{proof}
+Denoting the left hand side of \eqref{eq:combin} by $\Omega_{a,b}$ the proof is an induction on $b$, i.e. by computing $\Omega_{a,b+1}$ in terms of $\Omega_{a,b}$.
+\end{proof}
+
+Now let us return to the original problem, of calculating the transfer $\cat{T}(\gamma)$ from Definition \ref{defn:transfer_contract}. We will only need this in the following special case:
+
+\begin{corollary}\label{corollary_transfergamma} Let $\gamma$ be an odd $R$-linear operator on $X$. Then
+\be\label{eq:transfer_gamma}
+\cat{T}(\gamma) = \gamma + \sum_{m \ge 1} \sum_{q_1,\ldots,q_m}  \frac{1}{m!} [\lambda_{q_m}, [\lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \gamma] \cdots ]] \theta^*_{q_1} \ldots \theta^*_{q_m}
+\ee
+is the tranferred operator on $K \otimes X$, where the $q_j$'s range over $1, \ldots, n$.
+\end{corollary}
+\begin{proof}
+This is immediate from Proposition \ref{prop:ccommutesexpD}, substituting $a_i = \lambda_i, b_i = \theta_i^*,c = \gamma$, since
+\[
+\exp(-D) c \exp(D) = c - [c, \exp(-D)] \exp(D)\,.
+\]
+\end{proof}
+
+%\cat{T}(\gamma) = \gamma + \sum_{m \ge 1} \sum_{\bold{q} = (q_1,\ldots,q_m)}  \sum_{\sigma \in \mf{S}_m} \frac{(-1)^{|\sigma|}}{(m!)^2} \tau_{\bold{q}}(\gamma) \At_{\sigma(\bold{q})}
+%\ee
+%where for $\bold{q} = (q_1,\ldots,q_m)$
+%\begin{align*}
+%\tau_{\bold{q}}(\gamma) &= [\lambda_{q_m}, [\lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \gamma] \cdots ]]\,,\\
+%\At_{\sigma(\bold{q})} &= \At_{q_{\sigma(1)}} \cdots \At_{q_{\sigma(m)}}\,.
+
+\begin{remark} Observe that since the $\theta_i^*$ square to zero, only sequences of distinct indices $q_1,\ldots,q_m$ contribute in the sum \eqref{eq:transfer_gamma}. The low order terms are
+\be
+\cat{T}(\gamma) = \gamma + \sum_q [\lambda_q, \gamma] \theta^*_q + \frac{1}{2} \sum_{p,q} [\lambda_p, [\lambda_q, \gamma]] \theta_q^*\theta_p^* + \cdots
+\ee
+\end{remark}
+
+Finally, we compute the transfer of the operator $\theta_i$ on $\bigwedge( \oplus_j k \theta_j ) \otimes_k X$:
+
+\begin{theorem}\label{theorem:psik} We have
+\begin{equation}\label{eq:psik}
+\cat{T}(\theta_i) = \theta_i - \sum_{m \ge 0} \sum_{q_1,\ldots,q_m} \frac{1}{(m+1)!} [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
+\end{equation}
 \end{theorem}
-
-\subsection{The details}
-
-We present the cut $Y \l X$ with its Clifford action as arising from the following problem: how do we find a finite model of the matrix factorisation $Y \otimes X$ over $k[x,y]$?
-This problem was addressed in joint work with Dyckerhoff \cite{dm1102.2957} and we rely heavily on these results; the main new ingredient here is the construction of Appendix \ref{section:cliffordactkos}.
-
-The solution is given in the language of homological perturbation, which is recalled in Appendix \ref{section:homolog_fix}, with a reformulation in terms of splitting homotopies due to Barnes and Lambe \cite{barneslambe}.
-From the point of view of perturbation it is natural to look for a decomposition $d_{Y \otimes X} = d + \delta$ where a finite representative of $(Y \otimes X, d)$.
-Then the perturbation lemma can be used to parlay this into a finite model for the object of interest $(Y \otimes X, d + \delta)$.
-
-There seems to be no obvious way to do this, but there is a simple way out: we replace $Y \otimes X$ by a sum of copies
-\begin{equation}\label{eq:larger_object}
-(Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
-\end{equation}
-in such a way that this larger object \emph{does} fit into the pattern of the perturbation lemma.
-More precisely, \eqref{eq:larger_object} will be the tensor product of $Y \otimes X$ with a $\mathbb{Z}_2$-graded $k$-module and we find in \eqref{eq:iso_larger_object} an isomorphic object for which a finite model may be found by perturbing a finite model for one ``piece'' of the differential.
-Then we need only remember the data of how to extract $Y \otimes X$ from inside this larger object: this data is the Clifford action.
-\medskip
+\begin{proof}
+Observe that Corollary \ref{corollary_transfergamma} and the preceeding developments do not apply directly to $\theta_i$, because $[ \theta_j^*, \theta_i ] = \delta_{ij}$ whereas we have required the commutator $[b_j,c] = 0$ to vanish in the above.
+However, we do have
+\[
+[ \delta, \theta_i ] = \sum_j [ \lambda_j \theta_j^*, \theta_i ] = \sum_j \lambda_j \delta_{ij} = \lambda_i\,.
+\]
+And we can adjust the calculations above as follows. Firstly, using Lemma \ref{lemma:woop4} we obtain
+\[
+\delta^p [\delta, \theta_i] = \sum_{i+j=p} \binom{p}{i} [\delta, \theta_i]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [\delta, \lambda_i]^{(i)} \delta^j
+\]
+Tracking this through the rest of the calculation, as above, yields \eqref{eq:psik}.
+\end{proof}
+
+\begin{remark} The low order terms of \eqref{eq:psik} are
+\be
+\cat{T}(\theta_i) = \theta_i - \lambda_i - \frac{1}{2} \sum_q [\lambda_q, \lambda_i] \theta^*_q + \cdots
+\ee
+\end{remark}
+
+It is immediate that
+
+\begin{theorem} The closed odd operators $\cat{T}(\theta_i)$ and $\cat{T}(\theta_i^*) = \theta_i^*$ on the linear factorisation $(K \otimes X, d_K + d)$ form a representation of the Clifford algebra $C_n$.
+\end{theorem}
+
+By construction, Proposition \ref{prop:equivalencekoszul} is now promoted to an isomorphism of representations of $C_n$, with $\cat{T}(\theta_i), \cat{T}(\theta_i^*)$ acting on $K \otimes X$ and the $\theta_i, \theta_i^*$ acting on $\bigwedge( \oplus_i k\theta_i ) \otimes_k X$.
+
+\begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_n$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_n$.
+An explicit isomorphism can be written down using the techniques developed in this Section, see Appendix \ref{section:variation_of_homotopy}.
+\end{remark}
+
+\begin{remark}\label{remark:cancellations_transfer} Suppose for each pair $1 \le i,j \le n$ that up to homotopy
+\be
+[\lambda_i, \lambda_j] \simeq f_{ij} \cdot 1_X
+\ee
+for elements $f_{ij} \in R$.
+Then the formula for $\cat{T}(\theta_i)$ simplifies substantially: for any indices $i,j,k$ we have $[\lambda_i, [\lambda_j, \lambda_k]] \simeq [\lambda_i, f_{jk}] = 0$ so that \eqref{eq:psik} becomes
+\be
+\cat{T}(\theta_i) \simeq \theta_i - \lambda_i - \frac{1}{2} \sum_q f_{qi} \theta^*_q\,.
+\ee
+%The simplification for a general odd operator $\gamma$ is more modest. By the Jacobi identity
+%\[
+%[\lambda_i, [\lambda_j,\gamma]] + [\gamma, [\lambda_i, \lambda_j]] + [\lambda_j, [\gamma, \lambda_i]] = 0\,.
+%\]
+%Since $[\gamma, [\lambda_i, \lambda_j]] = [\gamma, f_{ij}] = 0$, this yields
+%\[
+%[\lambda_i, [\lambda_j, \gamma]] = -[\lambda_j, [\lambda_i, \gamma]]\,.
+%\]
+%Thus
+%\begin{align*}
+%\sum_{i,j} [\lambda_i, [\lambda_j, \gamma]] \theta_j^* \theta_i^* &= \sum_{i < j}\left( [\lambda_i, [\lambda_j, \gamma]] \theta_j^* \theta_i^* + [\lambda_j, [\lambda_i, \gamma]] \theta_i^*\theta_j^* \right)\\
+%&= \sum_{i < j} 2 [\lambda_i, [\lambda_j, \gamma]] \theta_j^*\theta_i^*\,.
+%\end{align*}
+%In this way any truly interesting cancellations are prevented by the operators $\theta_i^*$.
+\end{remark}
+
+\subsection{The finite model}\label{section:theequivalence}
 
 % As long as the $t_i$ belong to the maximal ideal
-Let us now proceed to the details.
-We keep the above notation, so $k[z] = k[z_1,\ldots,z_m]$.
-The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ (where $t_i = \partial_{z_i} V$) has as its underlying graded module the exterior algebra on the $\theta_i$ of degree $-1$.
-If $F = k\theta_1 \oplus \cdots \oplus k\theta_m$ then
+We proceed to rediscover $Y \l X$ with its Clifford action as a finite model of $Y \otimes X$.
+Using this we prove in the next section that $\cat{L}$ and $\LG$ are equivalent bicategories.
+The notation is as in Setup \ref{setupforfusion}.
+We introduce formal variables $\theta_i$ of odd degree and set
+\[
+V = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
+\]
+The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ (where $t_i = \partial_{y_i} V$) is defined by
 \begin{equation}\label{defn:koszul}
-K = \bigwedge F \otimes_k k[z], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
-\end{equation}
-As explained in Appendix \ref{section:cliffordactkos} since each $t_i$ acts null-homotopically on $Y \otimes X$ there is an isomorphism of linear factorisations (writing $S_m = \bigwedge F$ as per our usual convention)
-\begin{equation}\label{eq:iso_larger_object}
-\xymatrix@C+3pc{ K \otimes Y \otimes X \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k (Y \otimes X)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
-\end{equation}
-where the differential on the left is $d_{Y \otimes X} + d_K$, on the right the differential is $d_{Y \otimes X}$, and $\delta = \sum_i \lambda_i \theta_i^*$ where $\lambda_i$ is a choice of null-homotopy for the action of $t_i$.
-
-From the identity $d^2_Y = V - W$ we deduce that
-\[
-\partial_{z_i}(d_Y) d_Y + d_Y \partial_{z_i}(d_Y) = \partial_{z_i} V
-\]
-so that we may choose $\lambda_j$ to be the operator \eqref{eq:lambda_defn}.
-Note that the right hand side of \eqref{eq:iso_larger_object} is a direct sum of (shifted) copies of $Y \otimes X$; this is the object we intended in \eqref{eq:larger_object}.
-The Clifford algebra $A_m$ naturally acts on this matrix factorisation via closed linear operators.
-
-The next step is to find a finite model of $K \otimes Y \otimes X$ using the perturbation lemma, by writing the differential as $d_K + d_{Y \otimes X}$ and finding a finite model of $(K \otimes Y \otimes X, d_K)$.
-We begin by giving a finite model for the Koszul complex $(K, d_K)$ using connections.
-\medskip
-
-The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $k\llbracket z \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra.
-By identifying $d t_i$ with $\theta_i$ we may identify this tensor product with $K$ itself, so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $K$.
-It is straightforward to check that $[d_K, \nabla]$ is invertible on the graded submodule $K_{\le -1}$ of nonzero degree terms, and we define
+K = V \otimes_k k[y], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
+\end{equation}
+According to Strategy \ref{strategy} the first step is to find a finite model of
+\[
+( K \otimes_{k[y]} ( Y \otimes X ), d_K ) = ( V \otimes_k ( Y \otimes X ), d_K )\,.
+\]
+\textbf{First step.} A finite model for $(K, d_K)$ is obtained using connections.
+The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $k\llbracket y \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra.
+By identifying $d t_i$ with $\theta_i$ we may make the identification
+\[
+\check{K} := K \otimes_{k[y]} k\llbracket y \rrbracket \cong k\llbracket y \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}
+\]
+so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $\check{K}$.
+It is straightforward to check that $[d_K, \nabla]$ is invertible on the graded submodule $\check{K}_{\le -1}$ of nonzero degree terms, and we define
 \[
@@
 
-\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $K$.
+\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $(\check{K},d_K)$.
 \end{proposition}
@@
 \xymatrix@C+2pc{
-(J_V,0) \ar@<-1ex>[r]_{\sigma} & (K, d_K), \ar@<-1ex>[l]_{\pi}
+(J_V,0) \ar@<-1ex>[r]_{\sigma} & (\check{K}, d_K), \ar@<-1ex>[l]_{\pi}
 } \quad H
 \end{equation}
-where $\pi: K \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $k\llbracket z \rrbracket \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $k\llbracket z \rrbracket$ uniquely determined by $\nabla$.
-The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of the Koszul complex $K$.
-
-Recall that the tensor product $Y \,\check{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,y]\llbracket z \rrbracket$.
-Let us write $\ell = k[x,y]$ so that the connection $\nabla$ extends to a standard $\ell$-linear flat connection on $R$.
-A choice of homogeneous basis for $X$ and $Y$ allows us to write $Y \otimes X \cong k[x,y,z] \otimes_k V$ for some $\mathbb{Z}_2$-graded free $k$-module $V$, so
+where $J_V$ is the Jacobi algebra from \eqref{eq:defnjacobian}, $\pi: \check{K} \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $k\llbracket y \rrbracket \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $k\llbracket y \rrbracket$ uniquely determined by $\nabla$.
+The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of the Koszul complex $\check{K}$.
+
+Recall that the tensor product $Y \,\check{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,z]\llbracket y \rrbracket$.
+The connection $\nabla$ extends to a standard $k[x,z]$-linear flat connection on $R$.
+A choice of homogeneous basis for $X$ and $Y$ allows us to write $Y \otimes X \cong k[x,y,z] \otimes_k Q$ for some $\mathbb{Z}_2$-graded free $k$-module $Q$, so
 \begin{equation}\label{eq:lambdaiso2}
-K \otimes_{k\llbracket z \rrbracket}( Y \,\check{\otimes}\, X ) \cong K \otimes_{k\llbracket z \rrbracket} (R \otimes_k V) \cong K \otimes_k k[x,y] \otimes_k V
-\end{equation}
-In this way the $k$-linear splitting homotopy $H$ on $K$ induces an $\ell$-linear operator $H \otimes 1$ on $K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X$, which we again denote by $H$.
-
-\begin{lemma} $H$ is an $\ell$-linear splitting homotopy on the complex $(K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, d_K)$.
+\check{K} \otimes_{k\llbracket y \rrbracket}( Y \,\check{\otimes}\, X ) \cong \check{K} \otimes_{k\llbracket y \rrbracket} (R \otimes_k Q) \cong \check{K} \otimes_k k[x,z] \otimes_k Q
+\end{equation}
+In this way the $k$-linear splitting homotopy $H$ on $\check{K}$ induces an $k[x,z]$-linear operator $H \otimes 1$ on $\check{K} \otimes_{k\llbracket y \rrbracket}( Y \,\check{\otimes}\, X)$, which we again denote by $H$.
+It is immediate that
+
+\begin{lemma} $H$ is a $k[x,z]$-linear splitting homotopy on $(\check{K} \otimes_{k\llbracket y \rrbracket} ( Y \,\check{\otimes}\, X ), d_K)$.
 \end{lemma}
@@
 \xymatrix@C+2pc{
-(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
+(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
 } \quad H
 \]
-The map $\pi$ is $R$-linear induced by the map $\pi: K \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.
+The map $\pi$ is $R$-linear induced by the map $\pi: \check{K} \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.
 This is the desired finite model of $K \otimes Y \otimes X$ equipped with only the differential $d_K$.
 
-We now view $d_{Y \otimes X}$ as a perturbation.
-The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
+\vspace{0.3cm}
+
+\textbf{Second step.} We now view $d_{Y \otimes X}$ as a perturbation.
+The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
 Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
@@
 \]
-is an $\ell$-linear splitting homotopy achieving the desired aim.
-
-Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $\ell$-linear splitting homotopy on $K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X$ and the associated $\ell$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
+is $k[x,z]$-linear splitting homotopy achieving the desired aim.
+
+Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $k[x,z]$-linear splitting homotopy on $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ and the associated $k[x,z]$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
 \begin{equation}\label{eq:finite_model_defo}
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, \ar@<-1ex>[l]_-{\pi}
-} \quad \phi_\infty
-\end{equation}
-where the differential on the left is $d_{Y \otimes X}$ and on the right it is $d_K + d_{Y \otimes X}$. 
+\big( Y \l X, d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{\sigma_\infty} & \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X, d_K + d_{Y \otimes X} \big)\,, \ar@<-1ex>[l]_-{\pi}
+} \quad \phi_\infty\,.
+\end{equation}
 %$A = d_{Y \otimes X}( 1 + H d_{Y \otimes X} )^{-1}$ and $\sigma_\infty = \sigma - H A \sigma$.
@@
 
-\begin{proposition}\label{prop:final_homotopy_equiv_cut} There is a homotopy equivalence of matrix factorisations over $k[x,y]$
+\textbf{Third step.} Since each $t_i$ acts null-homotopically on $Y \otimes X$ there is by Section \ref{section:cliffordactkos} an isomorphism of linear factorisations
+\begin{equation}\label{eq:iso_larger_object}
+\xymatrix@C+3pc{ \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \otimes X, d_K + d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{ \exp(\delta) } & \big( V \otimes_k Y \,\check{\otimes}\, X, d_{Y \otimes X} \big)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
+\end{equation}
+where $\delta = \sum_i \lambda_i \theta_i^*$ for a choice $\lambda_i$ of null-homotopy for the action of $t_i$.
+From the identity $d^2_X = V - W$ we deduce that $\partial_{y_i}(d_X) d_X + d_X \partial_{y_i}(d_X) = \partial_{y_i} V = t_i$ so that we may, and do, choose $\lambda_i = \partial_{y_i}(d_X)$, see Section \ref{section:partial}.
+
+\vspace{0.3cm}
+
+\textbf{Fourth step.} Combining \eqref{eq:finite_model_defo} and \eqref{eq:iso_larger_object} we have a homotopy equivalence of matrix factorisations over $k[x,z]$
+\begin{equation}\label{eq:final_finite_model2}
+\xymatrix@C+4pc{
+Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & V \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
+}\,.
+\end{equation}
+By \cite[Remark 7.7]{dm1102.2957} the canonical map $\epsilon: Y \otimes X \lto Y \,\check{\otimes}\, X$ is a homotopy equivalence over $k[x,z]$ so finally we have
+
+\begin{theorem}\label{theorem:htpy_equivalence_main} There is a homotopy equivalence of matrix factorisations over $k[x,z]$
 \begin{equation}\label{eq:final_finite_model}
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & V \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
 }
 \end{equation}
-where $\Phi = \pi \exp(-\delta) \epsilon$ and $\Phi^{-1} = \epsilon^{-1} \exp(\delta) \sigma_\infty$ and $\epsilon: Y \otimes X \lto Y \,\check{\otimes}\, X$ is canonical.
+where $\Phi = \pi \exp(-\delta) \epsilon$ and $\Phi^{-1} = \epsilon^{-1} \exp(\delta) \sigma_\infty$.
+\end{theorem}
+
+The canonical action of $C_m$ on the spinor representation $V$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $V \otimes_k ( Y \otimes X )$.
+In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$, and it remains to show that these two actions are compatible.
+
+\begin{proposition}\label{prop:clifford_action} The map $\Phi$ is an isomorphism of $C_m$- representations in the homotopy category. That is, there are homotopies
+\[
+\gamma_i \Phi \simeq \Phi \theta_i \,, \qquad \gamma_i^\dagger \Phi \simeq \Phi \theta_i^*\,.
+\]
 \end{proposition}
 \begin{proof}
-Together \eqref{eq:iso_larger_object} and \eqref{eq:finite_model_defo} give a homotopy equivalence
-\begin{equation}\label{eq:final_finite_model2}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & K \otimes Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
-}\,.
-\end{equation}
-By \cite[Remark 7.7]{dm1102.2957} $\epsilon$ is a homotopy equivalence over $k[x,y]$, completing the proof.
-\end{proof}
-
-This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $S_m \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object.
-It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $S_m \otimes_k( Y \otimes X )$.
-
-This equivalence induces an $A_m$ action on $Y \l X$ via the action on $S_m$.
-
-\begin{definition} We introduce closed odd $k[x,y]$-linear operators on $Y \l X$ by
-\begin{equation}\label{eq:new_operators}
-(a_i^\dagger)_{Y,X} = \Phi \circ a_i^\dagger \circ \Phi^{-1}, \qquad (a_i)_{Y,X} = \Phi \circ a_i \circ \Phi^{-1}\,.
-\end{equation}
-\end{definition}
-
-\begin{proposition}\label{prop:clifford_action} The operators $(a_i)_{Y,X}, (a_i^{\dagger})_{Y,X}$ of \eqref{eq:new_operators} agree with those in \eqref{eq:intro_clifford_act1}, \eqref{eq:intro_clifford_act2}.
-\end{proposition}
-\begin{proof}
-Let us define intermediate operators on $K \otimes Y \otimes X$
-\[
-\psi_i^\dagger = \exp(-\delta) a_i^\dagger \exp(\delta), \qquad \psi_i = \exp(-\delta) a_i \exp(\delta).
-\]
-By Appendix \ref{section:cliffordactkos}, $\psi_i^\dagger = \theta^*_i$ and
-\[
-\psi_i = \theta_i - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_l}^*\,.
-\]
-Next we recall that, with $t_i = \partial_{z_i} V$, we have by \cite[Section 10]{dm1102.2957}
+We prove that $\gamma_i \simeq \Phi \theta_i \Phi^{-1}$ and $\gamma_i^\dagger \simeq \Phi \theta_i^* \Phi^{-1}$.
+With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $V \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
+\[
+\cat{T}(\theta_i) = \exp(-\delta) \theta_i \exp(\delta)\,, \qquad \cat{T}(\theta_i^*) = \exp(-\delta) \theta_i^* \exp(\delta)\,.
+\]
+Then we use Lemma \ref{lemma:commutator_of_lambdas}, according to which there are homotopies
+\[
+[ \lambda_j, \lambda_k ] = [ \partial_{y_j}(d_X), \partial_{y_k}(d_X) ] \simeq \partial_{y_jy_k}(V)\,.
+\]
+Therefore by Theorem \ref{theorem:psik} and Remark \ref{remark:cancellations_transfer} we have $\cat{T}(\theta_i^*) = \theta_i^*$ and a homotopy
+\be\label{eq:comp338h}
+\cat{T}(\theta_i) \simeq \theta_i - \lambda_i - \frac{1}{2}\sum_q \partial_{y_q y_i}(V) \theta_q^*\,.
+\ee
+It remains to compute the further transfer of these operators to $Y \l X$. The key point is proven in Lemma \ref{lemma:transfercreations} below, where we show that there is a homotopy
+\be\label{eq:transfercr}
+\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty \simeq \At_{q_1} \cdots \At_{q_l}
+\ee
+for any indices $q_1,\ldots,q_l$. Hence
+\[
+\Phi \theta_i^* \Phi^{-1} \simeq \pi \cat{T}(\theta_i^*) \sigma_\infty = \pi \theta_i^* \sigma_\infty \simeq \At_i = \gamma_i^\dagger\,.
+\]
+Since $\pi$ projects onto $\theta$-degree zero,
+\begin{align*}
+\Phi \theta_i \Phi^{-1} &\simeq \pi \cat{T}(\theta_i) \sigma_\infty\\
+&\simeq - \pi \lambda_i \sigma_\infty - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) \pi \theta_q^* \sigma_\infty\\
+&\simeq - \lambda_i - \frac{1}{2}\sum_q \partial_{y_qy_i}(V) \At_q\\
+&= \gamma_i
+\end{align*}
+which completes the proof.
+\end{proof}
+
+\begin{lemma}\label{lemma:transfercreations} In the context of the diagram \eqref{eq:final_finite_model2} there is a $k[x,z]$-linear homotopy
+\[
+\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty \simeq \At_{q_1} \cdots \At_{q_l}
+\]
+for any sequence of indices $1 \le q_1,\ldots,q_l \le m$.
+\end{lemma}
+\begin{proof}
+Recall that, with $t_i = \partial_{z_i} V$, we have by \cite[Section 10]{dm1102.2957}
 \begin{equation}\label{eq:atiyah_formula_sigma}
-\sigma_\infty = \sum_{l \ge 0} \sum_{q_1,\ldots,q_l} (-1)^{\binom{l+1}{2}} \frac{1}{l!} [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}] \theta_{q_1} \cdots \theta_{q_l} + (t \text{ terms})\,.
-\end{equation}
-That is, $\sigma_\infty$ is given modulo the submodule $(t_1,\ldots,t_m) K \otimes Y \otimes X$ by the formula above. Hence we compute
+\sigma_\infty = \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2}} \frac{1}{s!} [ d_{Y \otimes X}, \partial_{t_{p_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{p_s}}] \theta_{p_1} \cdots \theta_{p_s} + (t \text{ terms})\,.
+\end{equation}
+That is, $\sigma_\infty$ is given modulo the submodule $(t_1,\ldots,t_m) K \otimes Y \otimes X$ by the formula above. Since $\pi$ vanishes on this submodule,
 \begin{align*}
-(a_i^\dagger)_{Y,X} &= \pi \psi_i^\dagger \sigma_\infty = \pi \theta_i^* \sigma_\infty\\
-&= \sum_{l \ge 0} \sum_{q_1,\ldots,q_l} (-1)^{\binom{l+1}{2}} \frac{1}{l!} [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}] \pi \theta_i^* \theta_{q_1} \cdots \theta_{q_l}\\
-&= \sum_q [d_{Y \otimes X}, \partial_{t_q}] \pi \theta_i^* \theta_q\\
-&= [d_{Y \otimes X}, \partial_{t_i}] = \At_i\,.
+\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty &= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2}} \frac{1}{s!} [ d_{Y \otimes X}, \partial_{t_{p_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{p_s}}] \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}\\
+&= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s}{2}} \frac{1}{s!} \At_{p_1} \cdots \At_{p_s} \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}
 \end{align*}
-To simplify the notation in the following, we define ($i$ is fixed) for a tuple $\bold{q} = (q_1,\ldots,q_l)$
-\begin{gather*}
-\tau_{\bold{q}} = [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, \ldots [ \lambda_{q_1}, \lambda_i ] \cdots ]\,,\\
-\At_{\bold{q}} = [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}]\,.
-\end{gather*}
-With this notation we compute
-\begin{align*}
-(a_i)_{Y,X} &= \pi \psi_i \sigma_\infty\\
-&= - \lambda_i - \pi \sum_{l \ge 1, k \ge 0} \sum_{q_1,\ldots,q_l} \sum_{w_1,\ldots,w_k} \frac{1}{(l+1)!
-k!} (-1)^{kl+\binom{k+1}{2}} \tau_{\bold{q}}  \At_{\bold{w}} \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{w_1} \cdots \theta_{w_k}\,.
-\end{align*}
-But $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $l = k$ and to $\bold{q}$ a permutation of $\bold{w}$. Since
+since $[ d_{Y \otimes X}, \partial_{t_{p_i}}] = - \At_{p_i}$.
+Now $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $s = l$ and to $\bold{p}$ a permutation of $\bold{q}$.
+Since
 \[
@@
 \begin{align*}
-(a_i)_{Y,X} &= - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \sum_{\sigma \in S_l} (-1)^{|\sigma|} \frac{1}{l! (l+1)!} \tau_{\bold{q}} \At_{\sigma(\bold{q})}\\
-&= - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} \tau_{\bold{q}} \At_{\bold{q}}
+\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty &= \sum_{\sigma \in \mathfrak{S}_l} (-1)^{|\sigma|} \frac{1}{l!} \At_{q_{\sigma(1)}} \cdots \At_{q_{\sigma(l)}}\\
+&\simeq \At_{q_1} \cdots \At_{q_l}
 \end{align*}
@@
 
-%The upshot is that if we equip $Y \l X$ with the Clifford action $\{ a_i, a_i^\dagger \}_i$ defined at the beginning of this section then the homotopy equivalence of Proposition \ref{prop:final_homotopy_equiv_cut} is $A_m$-linear.
-
-\begin{remark} There is a question of whether or not the $A_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
-But Atiyah classes are independent, up to homotopy, of the choice of connection, and it is easy to see that the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis.
-Hence the action is indeed canonical.
+Finally, we will need naturality of Theorem \ref{theorem:htpy_equivalence_main}.
+
+\begin{proposition}\label{prop:naturality_main_thm} If $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations the diagram
+\begin{equation}\label{eq:final_finite_naturality}
+\xymatrix@C+4pc@R+1pc{
+Y \l X \ar[d]_-{\psi \l \phi} & V \otimes_k ( Y \otimes X )\ar[l]_-{\Phi} \ar[d]^-{\psi \otimes \phi}\\
+Y' \l X' & V \otimes_k ( Y' \otimes X' )\ar[l]^-{\Phi}
+}
+\end{equation}
+commutes up to $k[x,z]$-linear homotopy.
+\end{proposition}
+\begin{proof}
+Given the formula $\Phi = \pi \exp(-\delta) \epsilon$ it is clearly enough to show that $\psi \l \phi$ commutes up to homotopy with $\delta$, and for this it is enough to show that there is a homotopy
+\[
+\partial_{y_i}(d_{X'}) \phi \simeq \phi \partial_{y_i}(d_X)
+\]
+for each $i$. But this is the content of Lemma \ref{lemma:naturalityoflambda}.
+\end{proof}
+
+This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $V \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object.
+It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $V \otimes_k( Y \otimes X )$.
+
+\begin{remark} The isomorphism of $C_m$-representations in the homotopy category
+\[
+\Phi: V \otimes_k (Y \otimes X) \lto Y \l X
+\]
+is straightforward to compute.
+Firstly, since $\Phi = \pi \exp(-\delta) \varepsilon$ and the operator $\delta = \sum_i \lambda_i \theta_i^*$ annihilates the identity of the exterior algebra $1 \in V$, the composite
+\be
+\xymatrix@C+2pc{
+( k \cdot 1 ) \otimes_k ( Y \otimes X ) \ar[r]^-{\operatorname{inc}} & V \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
+}
+\ee
+is just the quotient map $Y \otimes X \lto Y \l X$, which we write as $\nu \mapsto \bar{\nu}$. Using
+\[
+\exp(-\delta) = 1 - \sum_i \lambda_i \theta_i^* - \frac{1}{2}\sum_{i,j} \lambda_i \lambda_j \theta_i^* \theta_j^* + \cdots
+\]
+we have for example
+\begin{align*}
+\Phi( \theta_1 \theta_2 \otimes \nu ) &= - \frac{1}{2} \sum_{i,j} \pi \lambda_i \lambda_j  \theta_i^* \theta_j^*( \theta_1 \theta_2 \otimes \nu )\\
+&= \frac{1}{2}\left( \lambda_1 \lambda_2 -\lambda_2 \lambda_1 \right)( \bar{\nu} )\,.
+\end{align*}
 \end{remark}
 
-\begin{proposition} The above construction defines a cut functor of degree $m$
-\begin{gather*}
-\cat{L}(W, V) \otimes_k \cat{L}(V,U) \lto \cat{L}(W, U)^\bullet\\
-X \otimes Y \mapsto (Y \l X, \{ a_i, a_i^\dagger \}_i )
-\end{gather*}
-sending a morphism $\phi \otimes \psi$ to $\psi \l \phi = \psi \otimes 1 \otimes \phi$.
-\end{proposition}
-\begin{proof}
-We check that the construction is functorial, the compatibility with the supercategory structure is straightforward and we omit it.
-We only check functoriality in $X$, as the check for $Y$ is the same.
-So let $\phi: X \lto X'$ be a morphism of matrix factorisations.
-Let $a_i, a_i^\dagger$ denote the actions on both $X$ and $X'$, so that we need to check
-\[
-(1\l\phi) a_i = a_i (1 \l \phi), \qquad (1\l\phi) a_i^\dagger = a_i^\dagger (1 \l \phi)\,.
-\]
-It is enough to prove that $(1 \l \phi) \At_i = \At_i (1 \l \phi)$ and $(1 \l \phi) \lambda_i = \lambda_i (1 \l \phi)$ up to homotopy.
-The former follows from naturality of the Atiyah class (the arguments in either \cite[Lemma 3.3]{buchweitz_flenner} or \cite[Lemma 3.6]{dm1102.2957} also apply in the current context to show the desired naturality).
-For the latter we use Lemma \ref{lemma:naturalityoflambda} below.
-\end{proof}
-
-\begin{remark}\label{remark:iso_quotient_map} If $\iota: k \lto S_m$ denotes the map $\iota(1) = 1$ then by Lemma \ref{lemma:morphism_out_1} the composite
+\subsection{The equivalence of $\cat{L}$ and $\LG$}\label{section:equivalenceforreal}
+
+The bicategories $\LG$ and $\cat{L}$ have the same objects. Their morphism categories are 
+\begin{align*}
+\cat{L}(W,V) &= \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,\\
+\LG(W,V) &= \hmf( k[x,y], V - W )^{\oplus}
+\end{align*}
+with the notation from Section \ref{section:superbicatLG}. These are equivalent supercategories, via the following chain of equivalences
+\be
+\xymatrix@C-1pc{
+& \ar[dl]_-{\iota}\hmf( k[x,y], V - W )^{\omega}\ar[dr]^-{F}\\
+\Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet} &  & \hmf( k[x,y], V - W )^{\oplus}\ar@{.>}[ll]^-{\cat{Z}_{W,V}}
+}
+\ee
+where $\iota$ is the equivalence of a supercategory with its Clifford thickening, $F$ is the functor given earlier in \eqref{eq:omegavsoplus} and we define $\cat{Z}_{W,V} = \iota \circ F^{-1}$ to make the diagram commute.
+
+The latter functor $F$ is defined by choosing\footnote{One can avoid invoking the axiom of choice here by defining the splitting using homotopy colimits, see \cite{??}}, for each object $(X,e)$ a (possibly infinite rank) matrix factorisation $F(X,e)$ which splits the idempotent $e$.
+That is, such that there are morphisms in the homotopy category
 \[
 \xymatrix@C+2pc{
-Y \otimes X \cong k \otimes_k ( Y \otimes X ) \ar[r]^-{\iota \otimes 1} & S_m \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
+X \ar@<1ex>[r]^-{f} & F(X,e) \ar@<1ex>[l]^-{g}
 }
 \]
-is simply the quotient map $\varrho: Y \otimes X \lto Y \l X$.
-\end{remark}
-
-\begin{lemma}\label{lemma:naturalityoflambda} Let $R$ be a $k$-algebra, $W \in R$.
-Let $\partial$ be a $k$-linear derivation on $R$ and $\phi: X \lto X'$ a morphism of finite rank matrix factorisations over $R$ with chosen homogeneous bases.
-Then the diagram
-\[
-\xymatrix{
-X \ar[d]_{\partial(d_X)} \ar[r]^\phi & X' \ar[d]^{\partial(d_{X'})}\\
-X \ar[r]_{\phi} & X'
+with $f g = 1$ and $gf = e$.
+The inverse is defined by choosing, for each infinite rank matrix factorisation $T$ which is a summand in the homotopy category of something finite rank, an actual finite rank $X$ and morphisms $f,g$ with $fg = 1_T$, and defining
+\[
+F^{-1}(T) = (X,gf)\,.
+\]
+We may arrange these choices so that if $T$ is \emph{already} finite rank then $F^{-1}(T) = (T, 1_T)$.
+
+\begin{theorem} $\cat{Z}: \LG \lto \cat{L}$ is an equivalence of superbicategories without units.
+\end{theorem}
+\begin{proof}
+The only real content here is to produce a $2$-isomorphism
+\be\label{eq:superfuncvarphi}
+\varphi_{Y,X}: \cat{Z}_{V,U}(Y) \l \cat{Z}_{W,V}(X) \lto \cat{Z}_{W,U}( Y \otimes X )
+\ee
+in the usual situation of Setup \ref{setupforfusion}, which is natural in both $Y$ and $X$. Once we have done this the rest follows by functoriality.
+
+Since $Y,X$ in this case are already finite rank $\cat{Z}(Y) = Y$ and $\cat{Z}(X) = X$.
+The calculation of $\cat{Z}( Y \otimes X )$ is more interesting, because $Y \otimes X$ is infinite rank over $k[x,z]$.
+However we know from Proposition \ref{prop:clifford_action} that there is an isomorphism in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $k[x,z]$
+\begin{equation}\label{eq:final_finite_modelagain}
+\xymatrix@C+4pc{
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & V \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
 }
-\]
-commutes up to homotopy.
-\end{lemma}
-\begin{proof}
-From $d_{X'} \phi = \phi d_X$ we deduce
-\[
-\partial( d_{X'} ) \phi + d_{X'} \partial( \phi ) = \partial( \phi ) d_X + \phi \partial( d_X )
-\]
-and hence
-\[
-\partial( d_{X'} ) \phi - \phi \partial( d_X ) = \partial(\phi) d_X - d_{X'} \partial(\phi)
-\]
-as claimed.
-\end{proof}
-
-To complete the construction of the cut system we need to finish defining the associator and unitors (a task begun at the outset of the section) and to prove that the coherence conditions hold.
-Regarding the associator, we only need to check that $\alpha$ commutes with the Clifford actions.
-In the context of \eqref{eq:composable_triple},
-
-\begin{lemma} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $A_m \otimes A_p$-linear.
-\end{lemma}
-\begin{proof}
-We prove the $A_p$-linearity of $\alpha$, the proof for $A_m$ is similar.
-The algebra $A_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$.
-The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of
-\[
-M = Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
-\]
-relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
-Specifically, the generator $a_i^{\dagger}$ of $A_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
-But this operator can be identified with an Atiyah class of the linear factorisation
-\begin{equation}\label{eq:assoc_proof_M}
-Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X \big)
-\end{equation}
-relative to the ring morphism
-\begin{equation}\label{eq:assoc_proof_M2}
-k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
-\end{equation}
-By the same argument the action of $A_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} Y \big) \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}.
-It is therefore clear that the associator $\alpha$ identifies these two actions.
-\end{proof}
-
-Earlier the unitors were described by explicit formulas.
-Here we begin more abstractly: let $X \in \cat{L}(W,V)$ be a matrix factorisation with $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$.
-Since $\Delta_V$ is the unit in $\LG$ there is a homotopy equivalence $\lambda: \Delta_V \otimes_{k[z]} X \lto X$ and so by Proposition \ref{prop:final_homotopy_equiv_cut} there are homotopy equivalences
-\begin{equation}
-\xymatrix@C+3pc{
-\Delta_V \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( \Delta_V \otimes X )\ar@<-1ex>[l]_-{\Phi} \ar@<-1ex>[r]_-{1 \otimes \lambda} & S_m \otimes_k X \ar@<-1ex>[l]_-{1 \otimes \lambda^{-1}} 
-}\,.
-\end{equation}
-By construction these isomorphisms are $A_m$-linear, and the map from right to left is an isomorphism $\mu: X \lto \Delta_V \l X$ in $\cat{L}(W,V)^\bullet$ corresponding under Lemma \ref{lemma:morphism_out_1} to
-\[
-\mu_0 = \xymatrix@C+1pc{
-X \ar[r]^-{\lambda^{-1}} & \Delta_V \otimes_{k[z]} X \ar[r]^-{\varrho} & \Delta_V \l X
-}\,.
-\]
-where $\varrho$ is the quotient map.
-Given the explicit formula for $\lambda^{-1}$ from \cite[Section 4.1]{lgdual}, this map $\mu_0$ has the explicit formula given earlier in \eqref{eq:explicit_mu0}.
-Since $\mu_0$ is natural in $X$, this also proves that $\mu$ is a natural isomorphism.
-The details for $\eta$ are similar, so the unitors are now defined.
-
-\begin{remark}\label{remark:inflation} Let $V \in k[z_1,\ldots,z_m]$ be a potential and choose a $k$-basis for $J_V$.
-Then multiplication by $z_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[z_i]$ over $k$.
-
-Given $X$ and $Y$ the cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $z_i$ by the scalar matrix $[z_i]$.
-This ``inflation'' produces a matrix of polynomials over $k[x,y]$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem \ref{theorem:l_cut_system}] We first check the coherence axioms.
-The first and third are trivial.
-To prove (2) we need by Lemma \ref{lemma:unitor_check_help} only check commutativity of \eqref{eq:unitor_check_help1} in the usual situation of $X: W \lto V$ and $Y: V \lto U$.
-
-This amounts to checking commutativity of
-\begin{equation}\label{eq:coherence3_1}
-\xymatrix{
-(Y \l \Delta_V ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_V \l X )\\
-(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
-Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes J_V \otimes X \ar[l]^-{e_m} \ar[r]_-{e_m} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
-}\,.
-\end{equation}
-By definition $e_m$ factors as
-\[
-\xymatrix{
-Y \l X \ar[r]^-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X ) \ar[r] & Y \otimes X \ar[r] & S_m \otimes_k (Y \otimes X) \ar[r]^-{\Phi} & Y \l X
+\end{equation}
+where $Y \l X$ is finite rank. Recall from Definition \ref{defn:idempotent_e} that the idempotent
+\[
+e_m = \gamma_1^\dagger \cdots \gamma_m^\dagger \gamma_m \cdots \gamma_1 \in C_m
+\]
+represents projection onto $k \cdot 1$ in $V$.
+Since \eqref{eq:final_finite_modelagain} is an isomorphism of $C_m$-representations the idempotent $e_m$ acting on $Y \l X$ must split to the same thing as the idempotent $e_m$ acting on the right hand side, which obviously splits to $Y \otimes X$.
+Put differently, there is a diagram in the homotopy category
+\[
+\xymatrix@C+2pc{
+Y \l X \ar@<1ex>[r]^-{f} & Y \otimes X \ar@<1ex>[l]^-{g}
 }
 \]
-so commutativity of \eqref{eq:coherence3_1} follows from commutativity of
-\[
-\xymatrix@C-0.5pc{
-(Y \l \Delta_V ) \l X \ar[rrr]^-{\alpha} & & & Y \l ( \Delta_V \l X )\\
-(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & (Y \otimes \Delta_V ) \otimes X \ar[l]_-{\varrho} \ar[r]^-{\alpha} & Y \otimes (\Delta_V \otimes X) \ar[r]^-{\varrho} & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
-Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes X \ar[u]^-{\rho^{-1} \otimes 1} \ar@{=}[r] \ar[l]^-{\varrho} & Y \otimes X \ar[u]_-{1 \otimes \lambda^{-1}} \ar[r]_-{\varrho} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
-}\,.
-\]
-The innermost square of this diagram is the coherence constraint for the unitors in $\LG$.
-
-Finally, we check the computability conditions.
-The associator and unitors are derived explicitly from $d_X$ and $d_Y$, so (3) is clear, and (2) is addressed by Remark \ref{remark:inflation} and the explicit formulas for the Clifford action.
-For (1), the objects and morphisms of $\cat{L}(W,V)$ are described by finite matrices of polynomials, and the composition rule is given by multiplication of matrices.
-There is one subtlety: morphisms are matrices of polynomials \emph{identified up to homotopy}.
-
-To argue that $\cat{L}(W,V)$ is effectively computable we need to show that it is possible to determine algorithmically whether two morphisms are homotopic.
-This is important even at the level of objects: an object is a pair $(X,e)$ where $e^2 = e$ holds up to homotopy.
-Without an effective homotopy relation, there would be no algorithmic way to even distinguish between objects and non-objects.
-The necessary check is in Section \ref{example:computing_homs}.
-\end{proof}
-
-\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}.
-To see the connection, recall the idempotent $e_m \in A_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$.
-The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is
-\[
-e_m' = a_1 \cdots a_m a_m^\dagger \cdots a_1^\dagger\,.
-\]
-Using \eqref{eq:intro_clifford_act1} and \eqref{eq:intro_clifford_act2} we can write down the explicit form of this idempotent acting on $Y \l X$.
-On this object each of the $a_i$'s acts simply as $- \lambda_i$ because all of the $a_j^\dagger$'s appear to the right.
-Hence on $Y \l X$
-\begin{align*}
-e_m' &= (-1)^{\binom{m}{2}} a_1 \cdots a_m a_1^\dagger \cdots a_m^\dagger \\
-&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
-\end{align*}
-which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.
-
-In \emph{ibid.} we constructed finite models of convolutions $Y \circ X$ one pair $(Y,X)$ at time.
-To make this assignment of finite models coherently for all $1$-morphisms in $\LG$ simultaneously it is natural to identify the Clifford actions which underlie the idempotents, as we do here.
-\end{remark}
-
-\subsection{The cut model of $\LG$}
-
-Let $\cat{L}$ be the cut system described above, and let $\cat{L}^\bullet$ denote the associated superbicategory.
-With $\LG$ the superbicategory of Section \ref{section:superbicatLG} we construct a cut model $I: \LG \lto \cat{L}^\bullet$.
-On objects $I$ is the identity.
-For potentials $V,W$ we need to define a functor
-\begin{equation}\label{eq:cut_model_equiv}
-I_{V,W}: \LG(W,V) \lto \cat{L}^\bullet(W,V)\,.
-\end{equation}
-Recall that with $\cat{C} = \hmf(k[x,z], V - W)$,
-\[
-\cat{L}^\bullet(W,V) = \cat{C}^{\omega \bullet}\,, \quad \LG(W,V) = \cat{C}^{\oplus}\,.
-\]
-An object of $\cat{C}^{\omega \bullet}$ is a tuple $((X,e), n)$ consisting of an integer $n \ge 0$ and an $A_n$-module $(X,e)$ in $\cat{C}^\omega$, while an object of $\cat{C}^{\oplus}$ is a (possibly infinite) matrix factorisation of $V - W$ which is a direct summand of a finite rank one.
-
-On the full subcategory of finite rank matrix factorisation of $V - W$, $I_{V,W}$ is the identity and this functor extends uniquely (up to natural equivalence) to $\LG(W,V)$.
-To be more explicit about it: for each $X \in \LG(W,V)$ we \emph{choose} a finite rank matrix factorisation $\bar{X}$ together with an idempotent $e$ and morphisms $f_X, g_X$ as in the diagram
-\[
-\xymatrix@C+2pc{
-\bar{X} \ar@(ul,dl)_-{e} \ar@<1ex>[r]^-{f_X} & X \ar@<1ex>[l]^-{g_X}
-}
-\]
-satisfying $g_X f_X = e$ and $f_X g_X = 1_X$. Then the full definition of $I$ is given by
-\[
-I( X ) = ((\bar{X}, e), 0)\,, \qquad I( \phi ) = g_Y \phi f_X\,.
-\]
-To complete the definition of a strong functor $I$ it remains to give a natural $2$-isomorphism
-\begin{equation}\label{eq:strong_functor_varphi}
-\varphi: I(Y \otimes X) \lto I(Y) \l I(X)
-\end{equation}
-for every pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ in $\LG$.
-
-We give the definition of $\varphi$ where $X,Y$ are finite rank matrix factorisations; the general case follows. Recall the $A_m$-linear isomorphism of Proposition \ref{prop:final_homotopy_equiv_cut}
-\begin{equation}\label{eq:cutmodelequiv}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
-}\,.
-\end{equation}
-% TODO issue with completion
-This is essentially the desired natural isomorphism $\varphi$, and it is only necessary to package it a little more carefully.
-Let $e = e_m \in A_m$ denote the idempotent from Definition \ref{defn:idempotent_e}.
-If we define $\nu: S_m \lto k$ to be the projection onto $k \cdot 1$ then there is a diagram
-\[
-\xymatrix@C+4pc{
-Y \l X \ar@<1ex>[r]^-{\nu \Phi^{-1}} & Y \otimes X \ar@<1ex>[l]^-{\varrho}
-}
-\]
-expressing $Y \otimes X$ as the splitting of the idempotent $e$ on $Y \l X$.
-Here $\varrho: Y \otimes X \lto Y \l X$ is the quotient map.
-The usphot is that as objects of $\cat{L}(W,V)^{\omega \bullet}$
-\[
-I(Y \otimes X) = ((Y\l X, e), 0), \qquad I(Y) \l I(X) = ( (Y \l X, 1), m )\,.
-\]
-Morphisms $\varphi$ as in \eqref{eq:strong_functor_varphi} are in bijection with morphisms
-\[
-\varphi_0: (Y \l X, e) \lto (Y\l X, 1)
-\]
-in $\hmf(k[x,z], U - W)^{\omega}$ satisfying $\theta_i^* \circ \varphi_0 = 0$ for $1 \le i \le m$.
-The endomorphism $\varphi_0 = e_m$ of $Y \l X$ fits the bill.
-In the category of infinite rank matrix factorisations, $\varphi_0$ is just the morphism $\varrho$.
-It follows that $\varphi$ is a natural isomorphism, since it corresponds to $\Phi$.
-
-\begin{theorem} The data $(I, \varphi)$ defines a cut model $\LG \lto \cat{L}^\bullet$.
-\end{theorem}
-\begin{proof}
-Once we have shown that $(I, \varphi)$ is a strong functor it is clearly ``super'', and by construction it defines a cut model.
-There are two coherence conditions: the first is commutativity of the following diagram, in the context of a composable triple as in \eqref{eq:composable_triple}:
-\begin{equation}\label{eq:dia_coherence1}
-\xymatrix@C+2pc{
-(I(Z) \l I(Y) ) \l I(X) \ar[r]^-{\alpha} \ar[d]_-{\varphi \l 1} & I(Z) \l ( I(Y) \l I(X) ) \ar[d]^-{1 \l \varphi} \\
-I(Z \otimes Y) \l I(X) \ar[d]_-{\varphi} &  I(Z) \l I(Y \otimes X)\ar[d]^-{\varphi}\\
-I( (Z \otimes Y) \otimes X ) \ar[r]_-{I(\alpha)} & I(Z \otimes (Y \otimes X))
-}
-\end{equation}
-The key to checking this lies in understanding what $I( Z \otimes (Y \otimes X) )$ is.
-But as we have argued above, $Y \otimes X$ is a summand of $Y \l X$ with idempotent $e_m$ while $Z \otimes ( Y \l X )$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p$.
-This implies that $Z \otimes (Y \otimes X)$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p e_m = e_m e_p = e_{m+p}$, so
-\[
-I( (Z \otimes Y) \otimes X ) = ( Z \l (Y \l X), e_{m+p} ), \quad I( Z \otimes (Y \otimes X) ) = ( (Z \l Y) \l X, e_{m+p} )\,.
-\]
-Then commutativity of \eqref{eq:dia_coherence1} reduces to commutativity in $\hmf(Q - W)^{\omega}$ of
-\[
-\xymatrix@C+2pc{
-( (Z \l Y ) \l X, 1 ) \ar[r]^-{\alpha} & ( Z \l (Y \l X ), 1)\\
-( (Z \l Y) \l X, e_p \l 1) \ar[u]^-{e_p \l 1} & ( Z \l (Y \l X), 1 \l e_m) \ar[u]_-{e_m}\\
-( (Z \l Y) \l X, e_{m+p} ) \ar[u]^-{e_{m+p}} \ar[r]_-{e_{m+p}} & ( Z \l (Y \l X), e_{m+p} ) \ar[u]_-{e_{m+p}}
-}
-\]
-which is clear.
-
-The remaining coherence conditions are commutativity, for $X: W \lto V$, of
-\begin{equation}\label{eq:dia_coherence2}
-\xymatrix{
-I(X) \ar[dr]_-{\eta} & & I( X \otimes \Delta_W ) \ar[ll]_-{I(\rho)} \\
-& I(X) \l \Delta_W \ar[ur]_-{\varphi}
-}
-\end{equation}
-and a similar diagram for $\lambda$. By definition $I(\rho)$ is the inverse of
-\[
-\xymatrix{
-X \ar[r]^-{\eta^{-1}} & X \otimes \Delta_W \ar[r]^{\varrho} & X \l \Delta_W
-}
-\]
-so checking commutativity of \eqref{eq:dia_coherence2} can be done using Lemma \ref{lemma:morphism_out_1}, and similarly for the diagram involving $\mu$.
+where $g$ is the quotient map, and $f g = 1_{Y \otimes X}$ while $g f = e_m$.\footnote{$f$ is $\Phi^{-1}$ followed by projection onto $\theta$-degree zero.
+Not a very friendly map.} Then we may take as our definition
+\[
+\cat{Z}( Y \otimes X ) = (Y \l X, e_m)\,.
+\]
+So the problem is to define a $2$-isomorphism \eqref{eq:superfuncvarphi}, that is,
+\[
+\varphi_{Y,X}: (Y \l X, 1, \{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m) \lto (Y \l X, e_m)
+\]
+in the Clifford thickening of the idempotent completion of $\hmf(k[x,z],U - W)$, where the left hand side is equipped with the idempotent $1$ and the action $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ of $C_m$ while the right hand side has no Clifford action and idempotent $e_m$.
+
+But by Lemma \ref{lemma:whackamole} the identity map $\varphi_{Y,X} = 1_{Y \l X}$ is such an isomorphism, because the object $(Y \l X, e_m)$ of the idempotent completion by definition splits the idempotent $e_m$ on $Y \l X$.
+Naturality of \eqref{eq:superfuncvarphi} in $Y,X$ is a consequence of the naturality of \eqref{eq:final_finite_modelagain}, see Proposition \ref{prop:naturality_main_thm}.
 \end{proof}
@@
 
+TODO: remark on difference between $\partial(d_Y)$ and $\partial(d_X)$
+
 \appendix
-
-\section{Homological perturbation and fixed points}\label{section:homolog_fix}
-
-A fundamental role in this paper is played by the homological perturbation lemma.
-While this result is usually stated for complexes the standard results generalise immediately to linear factorisations, and in this section we collect these standard results.
-But we begin by recalling the motivating problem for which the perturbation lemma is the solution.
-
-Let $Q$ be a complex of infinite rank free abelian groups.
-Suppose that the cohomology is finitely generated, so that $Q$ contains in some sense only a ``finite'' amount of information.
-One can ask for a description which makes this finiteness manifest: the obvious answer is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.
-
-A \emph{deformation retract} of complexes is a pair of morphisms
-\begin{equation}\label{eq:example_defo_retract}
-\xymatrix@C+2pc{
-C \ar@<-1ex>[r]_\nabla & Q, \ar@<-1ex>[l]_f
-} \quad \phi
-\end{equation}
-and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $f \nabla = 1_C, \nabla f = 1_Q - [d_Q, \phi]$ so that $f, \nabla$ are mutually inverse homotopy equivalences.
-A deformation retract is \emph{strong} if it satisfies some additional conditions, listed below.
-The point is that if $C$ is finitely generated, then \eqref{eq:example_defo_retract} gives the desired finite representative in the homotopy equivalence class of $Q$.
-
-\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-modules
-\[
-\xymatrix@C+2pc@R+1pc{
-0 \ar[d] \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar[d]^-{x}\\
-k \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar@/_3pc/@{.>}[u]_-{\phi}
-}
-\]
-in which the first column is the complex $C$ which has $k$ concentrated in degree zero, and the second column $Q$ is the Koszul complex on $x$.
-The map $f: k[x] \lto k$ sends every polynomial to its constant term, while $\nabla: k \lto k[x]$ is the inclusion of the constants.
-The operator $\phi$ is defined by $\phi( x^n ) = x^{n-1}$ and $\phi(1) = 0$.
-Together these maps are a deformation retract giving $k$ as the ``finite model'' of $Q$.
-\end{example}
-
-Suppose now that a deformation retract computing a finite representative for $Q$ cannot be found immediately, but that we know how to decompose the differential as $d_Q = d + \tau$ in such a way that there is a finite representative for the complex $(Q,d)$.
-The perturbation lemma allows us, with some conditions, to ``mix in'' the operator $\tau$ to obtain a finite model for the original complex $Q$.
-\\
-
-Let $R$ be a commutative ring and $W \in R$.
-Everything we say applies, in the case where $W = 0$, to both $\mathbb{Z}_2$-graded and $\mathbb{Z}$-graded complexes.
-For our purposes the reformulation of the perturbation lemma in terms of fixed points by Barnes and Lambe is more natural, so we emphasise the ``splitting homotopies'' of \cite{barneslambe}.
-
-\begin{definition} A \emph{splitting homotopy} on a linear factorisation $(A,d)$ of $W$ is a degree $-1$ operator $\phi$ on $A$ satisfying
-\begin{itemize}
-\item[(i)] $\phi^2 = 0$,
-\item[(ii)] $\phi d \phi = \phi$.
-\end{itemize}
-A \emph{morphism} $(A,d, \phi) \lto (A,d',\phi')$ of splitting homotopies is a morphism $\alpha: A \lto A'$ of linear factorisations satisfying $\phi' \alpha = \alpha \phi$.
-\end{definition}
-
-The condition (ii) says that $\phi$ is a \emph{fixed point} of the operator $F(x) = x d x$.
-
-\begin{definition} A \emph{strong deformation retract} of linear factorisations of $W$ is a pair of morphisms of linear factorisations
-\begin{equation}\label{eq:defn_sdr}
-\xymatrix@C+2pc{
-(M,d) \ar@<-1ex>[r]_\nabla & (A,d), \ar@<-1ex>[l]_f
-} \quad \phi
-\end{equation}
-together with a degree $-1$ operator $\phi: A \lto A$ satisfying
-\begin{itemize}
-\item[(i)] $f \nabla = 1_M$,
-\item[(ii)] $\nabla f = 1_A - [d, \phi]$,
-\item[(iii)] $\phi^2 = 0$,
-\item[(iv)] $\phi \nabla = 0$,
-\item[(v)] $f \phi = 0$.
-\end{itemize}
-A \emph{morphism} of strong deformation retracts is a commutative diagram
-\[
-\xymatrix@C+2pc{
-(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\nabla & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_f\\
-(M',d') \ar@<-1ex>[r]_{\nabla'} & (A',d') \ar@<-1ex>[l]_{f'}
-}
-\]
-that is, a pair of morphisms $\alpha, \beta$ such that $\beta \nabla = \nabla' \alpha$, $\alpha f = f' \beta$ and $\phi' \beta = \beta \phi$.
-\end{definition}
-
-We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}.
-Namely, a strong deformation retract in the above sense is the same as a special deformation retract in the sense of \emph{ibid.} with $h = - \phi$.
-
-\begin{lemma}\label{lemma:equivocate} There is an equivalence between the category of splitting homotopies $\cat{C}_1$ and the category of  strong deformation retracts $\cat{C}_2$.
-\end{lemma}
-\begin{proof}
-We briefly recall the construction from \cite[p.883]{barneslambe}, which is not stated in terms of categories but is obviously functorial.
-Given a strong deformation retract \eqref{eq:defn_sdr} the data $(A, \phi)$ is a splitting homotopy.
-In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $\pi = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(\phi)$ with the associated projection $f$ and inclusion $\nabla$.
-Then this is a strong deformation retract, together with the original $\phi$.
-\end{proof}
-
-%Taking splitting homotopies as the primary object has the advantage of hiding some of the incidental complexity in the perturbation lemma.
-Here is the problem that the formalism is designed to solve: suppose $(A,d)$ is a linear factorisation of $W$ and that $\tau$ is a degree $+1$ operator on $A$ such that $(A, d + \tau)$ is a linear factorisation of $V$ (possibly different to $W$).
-This $\tau$ is called the \emph{perturbation}.
-
-\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(\pi) \cong \im(\pi')$ as graded $R$-modules, where $\pi = 1_A - [d, \phi]$ and $\pi' = 1_A - [d + \tau, \phi']$.
-\end{definition}
-
-That is, with $\xi = d + \tau$ the problem is to find a fixed point of the operator
-\[
-F(x) = x \xi x
-\]
-among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(\pi)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
-\[
-\phi_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \phi = \phi - \phi \tau \phi + \phi \tau \phi \tau \phi - \cdots
-\]
-is a solution of this fixed point problem:
-
-\begin{theorem}[Perturbation lemma]\label{theorem:pertlemma} Suppose $\phi \tau$ has finite order.
-Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi)$ and satisfies the isomorphism condition in the transference problem.
-\end{theorem}
-\begin{proof}
-The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations.
-\end{proof}
-
-The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}.
-The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
-\begin{equation}\label{eq:perturbedsdr}
-\xymatrix@C+2pc{
-(M,d_\infty) \ar@<-1ex>[r]_{\nabla_\infty} & (A, \xi), \ar@<-1ex>[l]_{f_\infty}
-} \quad \phi_\infty
-\end{equation}
-where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
-\begin{align*}
-\nabla_\infty &= \nabla - \phi A \nabla,\\
-f_\infty &= f - f A \phi,\\
-d_\infty &= d + f A \nabla\,.
-\end{align*}
-As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
-\[
-\im(1 - [\xi, \phi_\infty]) \cong \im(\pi) = M
-\]
-be identified with $M$, and the induced maps are the $\nabla_\infty, f_\infty, d_\infty$ given above.
-It is also possible to give a direct proof as in \cite{crainic}.
-To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one just studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation.
-The standard way of generating fixed points, say by iterating $F$ infinitely many times on $\phi$, produces the same answer provided one takes the limit of the coefficients in $\mathbb{Q}$ with respect to the $2$-adic valuation; see \cite[p.885]{barneslambe}.
 
@@
 
-Now we specialise to the Clifford algebras $A_n$ and their modules.
-
-\begin{lemma}\label{lemma:simplehom} Let $X$ be a $\mathbb{Z}_2$-graded left $A_n$-module. There is a $k$-linear isomorphism
-\[
-\Hom_{A_n}^0( S_n, X ) \cong \{ x \in X^0 \l a_i^\dagger \cdot x = 0 \text{ for all } 1 \le i \le n \}
-\]
-defined by $f \mapsto f(1)$. If $X$ is a right $A_n$-module there is a $k$-linear isomorphism
-\[
-\Hom^0_{A_n}( (S_n)^*, X ) \cong \{ x \in X^0 \l x \cdot a_i = 0 \text{ for all } 1 \le i \le n \}
+Now we specialise to the Clifford algebras $C_n$ and their modules.
+
+\begin{lemma}\label{lemma:simplehom} Let $X$ be a $\mathbb{Z}_2$-graded left $C_n$-module. There is a $k$-linear isomorphism
+\[
+\Hom_{C_n}^0( S_n, X ) \cong \big\{ x \in X^0 \l \gamma_i^\dagger \cdot x = 0 \text{ for all } 1 \le i \le n \big\}
+\]
+defined by $f \mapsto f(1)$. If $X$ is a right $C_n$-module there is a $k$-linear isomorphism
+\[
+\Hom^0_{C_n}( (S_n)^*, X ) \cong \big\{ x \in X^0 \l x \cdot \gamma_i = 0 \text{ for all } 1 \le i \le n \big\}
 \]
@@
 
-\begin{lemma}\label{lemma:morphism_out_1} For an $A_n$-module $Y$ there is a $k$-linear isomorphism
-\[
-\cat{C}_{A_n}( S_n \otimes_k X, Y ) \cong \{ \delta: X \lto Y \l a_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
+\begin{lemma}\label{lemma:morphism_out_1} For an $C_n$-module $Y$ there is a $k$-linear isomorphism
+\[
+\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta: X \lto Y \l \gamma_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
 \]
@@
 \[
-\cat{C}_{A_n}(S_n \otimes_k X, Y ) \cong \Hom_{A_n}( S_n, \cat{C}^*(X,Y) )\,.
+\cat{C}_{C_n}(S_n \otimes_k X, Y ) \cong \Hom_{C_n}( S_n, \cat{C}^*(X,Y) )\,.
 \]
@@
 
-\begin{lemma}\label{lemma:morphisms_two_forms} Let $X \in C_{A_p}$ and $Y \in \cat{C}_{A_q}$. There is a $k$-linear isomorphism
+\begin{lemma}\label{lemma:morphisms_two_forms} Let $X \in C_{C_p}$ and $Y \in \cat{C}_{C_q}$. There is a $k$-linear isomorphism
 \begin{align*}
-\cat{C}_{A_q}( S_{q,p} \otimes_{A_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ a_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ a_i^\dagger \circ \delta &= 0 \text{ for } 1 \le i \le q \}
+\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ \gamma_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ \gamma_i^\dagger \circ \delta &= 0 \text{ for } 1 \le i \le q \}
 \end{align*}
-defined by sending $\alpha: S_{q,p} \otimes_{A_p} X \lto Y$ to the composite
+defined by sending $\alpha: S_{q,p} \otimes_{C_p} X \lto Y$ to the composite
 \[
 \xymatrix@C+2pc{
-X \cong A_p \otimes_{A_p} X \ar[r]^-{\iota \otimes 1} & S_{q,p} \otimes_{A_p} X \ar[r]^-{\alpha} & Y
+X \cong C_p \otimes_{C_p} X \ar[r]^-{\iota \otimes 1} & S_{q,p} \otimes_{C_p} X \ar[r]^-{\alpha} & Y
 }
 \]
-where $\iota: A_p \lto S_{q,p}$ is defined by $\iota(1) = 1 \otimes 1^*$.
+where $\iota: C_p \lto S_{q,p}$ is defined by $\iota(1) = 1 \otimes 1^*$.
 \end{lemma}
@@
 \begin{align*}
-\cat{C}_{A_q}( S_{q,p} \otimes_{A_p} X, Y ) &\cong \Hom^0_{A_p-A_q}( S_{q} \otimes_k S_p^* , \cat{C}^*(X,Y))\\
-&\cong \Hom^0_{A_q}( S_q, \Hom^*_{A_p}( S_p^*, \cat{C}^*(X,Y) ))\\
-&\cong \{ \delta \in \Hom^0_{A_q}( S_p^*, \cat{C}^*(X,Y) ) \l a_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
-&\cong \{ \delta: X \lto Y \l \delta \circ a_i = 0 \text{ for } 1 \le i \le p \text{ and } a_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}
+\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) &\cong \Hom^0_{C_p-C_q-\operatorname{bimod}}( S_{q} \otimes_k S_p^* , \cat{C}^*(X,Y))\\
+&\cong \Hom^0_{C_q}( S_q, \Hom^*_{C_p}( S_p^*, \cat{C}^*(X,Y) ))\\
+&\cong \{ \delta \in \Hom^0_{C_q}( S_p^*, \cat{C}^*(X,Y) ) \l \gamma_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
+&\cong \{ \delta: X \lto Y \l \delta \circ \gamma_i = 0 \text{ for } 1 \le i \le p \text{ and } \gamma_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}
 \end{align*}
 as claimed.
-\end{proof}
-
-\section{Extending cut functors}\label{app:proof_cut_extension}
-
-The purpose of this appendix is to give the proof of Proposition \ref{prop:extend_cut_functor}. First, note that
-
-\begin{lemma}\label{lemma:altcomppersp} Let $\cat{C}$ be a small idempotent complete supercategory and take morphisms
-\[
-\xymatrix{
-(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
-}\\
-\]
-in $\cat{C}^\bullet$. Under \eqref{eq:isodefatensor} these correspond to bimodule maps
-\[
-\widetilde{\alpha}: S_{m,n} \lto \cat{C}^*(X,Y)\,, \qquad \widetilde{\beta}: S_{l,m} \lto \cat{C}^*(Y,Z)\,.
-\]
-The composite $\beta \circ \alpha: S_{l,n} \otimes_{A_n} X \lto Z$ in $\cat{C}^\bullet$ corresponds to the composite
-\[
-\xymatrix{
-S_{l,n} \cong S_{l,m} \otimes_{A_m} S_{m,n} \ar[r]^-{\widetilde{\beta} \otimes \widetilde{\alpha}} & \cat{C}^*(Y,Z) \otimes_{A_m} \cat{C}^*(X,Y) \ar[r]^-{\circ} & \cat{C}^*(X,Z)
-}\,.
-\]
-\end{lemma}
-\begin{proof}
-Follows by evaluation on $1 \otimes 1^* \in S_{l,n}$.
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop:extend_cut_functor}]
-Given $(X,n) \in \cat{C}_1^\bullet$ and $(Y,m) \in \cat{C}_2^\bullet$ we have $T(X,Y) = (Z,t)$ for some object $Z$ of $\cat{C}_3$.
-Given $a \in A_n$, say of odd degree, there is a morphism of $A_t$-modules $Z \lto \Psi Z$ given by
-\[
-\xymatrix@C+2pc{
-T(X,Y) \ar[r]^-{T(a \otimes 1)} & T(\Psi X, Y ) \ar[r]^-{\tau} & \Psi T(X,Y)
-}
-\]
-and this defines an algebra morphism $A_n \lto \cat{C}_3^*(Z,Z)$.
-Doing the same for $A_m$ defines a morphism $A_{m+t+n} \cong A_m \otimes A_t \otimes A_n \lto \cat{C}_3^*(Z,Z)$ and an object $(Z, m + t +n) \in \cat{C}_3^\bullet$.
-We define $\widetilde{T}$ on objects by
-\begin{equation}\label{eq:ttilde}
-\widetilde{T}( (X,n), (Y,m) ) = (Z, m + t + n)\,.
-\end{equation}
-Next we define $\widetilde{T}$ on morphisms. Given $\alpha: (X_1,n_1) \lto (X_2,n_2)$ in $\cat{C}_1^\bullet$ and $T(X_i,Y) = (Z_i,t)$ for $i = 1,2$ we must construct a morphism
-\[
-\widetilde{T}(\alpha,1): (Z_1, m+t+n_1) \lto (Z_2, m+t+n_2)\,.
-\]
-Since $\alpha$ corresponds to an $A_{n_1}$-linear map $\widetilde{\alpha}: V \lto \cat{C}_1^*(X_1,X_2)$ we can compose with $T$ to get an $A_{n_2}$-$A_{n_1}$-bilinear map $\eta := T(1,Y) \circ \widetilde{\alpha}: V \lto \cat{C}_3^*(Z_1,Z_2)$.
-This extends to a morphism of $A_{n_2+c}$-$A_{n_1+c}$-bimodules
-\[
-V \otimes_k A_c \lto \cat{C}_3^*(Z_1,Z_2), \qquad v \otimes a \mapsto \eta(v) a\,.
-\]
-There is a canonical isomorphism of $A_{n+2+c}$-$A_{n_1+c}$-bimodules
-\begin{align*}
-S_{n_2+c,n_1+c} \cong S_{n_2+c} \otimes_k S_{n_1+c}^* \cong (S_{n_2} \otimes_k S_c) \otimes_k (S_c^* \otimes_k S_{n_1}^*) \cong V \otimes_k (S_c \otimes_k S_c^*) \cong V \otimes_k A_c
-\end{align*}
-so we have constructed $S_{n_2+c,n_1+c} \lto \cat{C}_3^*(Z_1,Z_2)$ which corresponds to a morphism of $A_{n_2+c}$-modules $S_{n_2+c, n_1+c} \otimes_{A_{n_1+c}} Z_1 \lto Z_2$ which we define to be $\widetilde{T}(\alpha,1)$.
-Functoriality of this construction follows from Lemma \ref{lemma:altcomppersp}.
-The functoriality in the other variable follows similarly.
-By construction $\widetilde{T}$ makes both of the required diagrams commute.
 \end{proof}
@@
 
-\section{Clifford actions and Koszul complexes}\label{section:cliffordactkos}
-% spkos series
-
-Let $R$ be a $\mathbb{Q}$-algebra and $(X,d)$ a linear factorisation of some $W \in R$.
-Let $t_1,\ldots,t_n$ be a sequence of elements of $R$ acting null-homotopically on $X$ and choose degree $-1$ operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$.
-
-Letting $\theta_i$ be a formal variable of degree $-1$, we define the Koszul complex $(K,d_K)$ with underlying graded module the exterior algebra $K$ on the $\theta_i$, as in \eqref{defn:koszul}.
-The tensor product $K \otimes X = (K \otimes X, d + d_K)$ is another linear factorisation of $W$ and on the underlying graded module $K \otimes X$ we have operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$.
-We can define additional operators in terms of these by $\psi_k^* = \theta_k^*$ and
-\begin{equation}
-\psi_k = \theta_k - \sum_{m \ge 0} \sum_{q_1,\ldots,q_m} \frac{1}{(m+1)!} [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_k ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
-\end{equation}
-The appendix is taken up with the proof of:
-
-\begin{theorem}\label{theorem:psik} The operators $\psi_k, \psi_k^*$ on $K \otimes X$ are closed and satisfy the Clifford relations
-\begin{equation}\label{eq:clifford_reln_psi}
-[ \psi_i, \psi_j ] = 0, \quad [ \psi_i^{*}, \psi_j^{*} ] = 0, \quad [ \psi_i, \psi_j^{*} ] = \delta_{ij}\,.
-\end{equation}
-\end{theorem}
-
-We introduce the notation
-\begin{align*}
-\delta &= \sum_{i=1}^n \lambda_i \theta_i^*,\\
-\exp(-\delta) &= \sum_{m \ge 0} (-1)^m \frac{1}{m!} \delta^m\,.
-\end{align*}
-
-\begin{proposition}\label{prop:equivalencekoszul} There are mutually inverse isomorphisms of linear factorisations
-\[
-\xymatrix@C+3pc{ (K \otimes X, d + d_K) \ar@<1ex>[r]^-{ \exp(\delta) } & (K \otimes X, d) \ar@<1ex>[l]^-{ \exp(-\delta) } }\,.
-\]
-\end{proposition}
-
-Before we give the proof, we need the key observation that $[d, \delta] = \sum_i [d, \lambda_i] \theta_i^* = d_K$. More generally
-
-\begin{lemma}\label{lemma:pert1} $[d, \delta^m] = m \delta^{m-1} d_K$ for $m \ge 1$.
-\end{lemma}
-\begin{proof}
-\[
-[ d, \delta^m ] = \sum_{i=0}^{m-1} \delta^i [d, \delta] \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i d_K \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i \delta^{m-i-1} d_K = m \delta^{m-1} d_K
-\]
-\end{proof}
-
-\begin{lemma}\label{lemma:pert2} $[ d, \exp(-\delta) ] = - \exp(-\delta) d_K$ and $[ d, \exp(\delta) ] = \exp(\delta) d_K$.
-\end{lemma}
-\begin{proof}
-We prove the first identity using Lemma \ref{lemma:pert1}, the second is the same:
-\begin{align*}
-[d, \exp(-\delta)] &= \sum_{m \ge 1} \frac{(-1)^m}{m!} [ d, \delta^m ]\\
-&= \sum_{m \ge 1} \frac{(-1)^m}{m!} m \delta^{m-1} d_K\\
-&= - \sum_{m \ge 0} \frac{(-1)^m}{m!} \delta^m d_K\\
-&= - \exp(-\delta) d_K
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop:equivalencekoszul}]
-It suffices to show $\exp(-\delta)$ is a morphism of linear factorisations. But using Lemma \ref{lemma:pert2}
-\[
-(d + d_K) \exp(-\delta) - \exp(-\delta) d = [d, \exp(-\delta)] + d_K \exp(-\delta) = 0
-\]
-and similarly for the other equation.
-\end{proof}
-
-The operators $\theta_i, \theta_i^*$ generate a Clifford action on the exterior algebra $K$ and therefore act via closed operators on $K \otimes X$.
-The $\psi_k, \psi_k^*$ are defined to be the translation of this Clifford structure to the $K \otimes X$ using the Proposition, i.e.
-\begin{align}
-\psi_k &= \exp(-\delta) \theta_k \exp(\delta), \label{eq:defn_psik1}\\
-\psi_k^{*} &= \exp(-\delta) \theta_k^* \exp(\delta)\,. \label{eq:defn_psik2}
-\end{align}
-
-It remains to show that these operators have the form described prior to the statement of the theorem.
-
-\begin{lemma} $\psi_k^{*} = \theta_k^*$ for $1 \le k \le n$.
-\end{lemma}
-\begin{proof}
-Since $\delta$ commutes with $\theta_k^*$, $\exp(-\delta) \theta_k^* = \theta_k^* \exp(-\delta)$.
-\end{proof}
-
-However the operator $\theta_k$ is not closed, indeed $[ \theta_i, d + d_K ] = t_i$, and so giving a closed formula for $\psi_k^*$ is more involved.
-In the development below we fix an index $k$.
-To compute $\psi_k$ the strategy is to commute $\theta_k$ past $\exp(-\delta)$.
-To this end we must first compute $[\theta_k, \delta^m]$ and then $[\theta_k, \exp(-\delta)]$.
-The calculation begins
-\begin{equation}\label{eq:catfish}
-[ \theta_k, \delta^m ] = \sum_{p=0}^{m-1} \delta^p [ \theta_k, \delta ] \delta^{m-p-1} = - \sum_{p=0}^{m-1} \delta^p [ \delta, \theta_k ] \delta^{m-p-1}\,.
-\end{equation}
-We need to understand how to commute $\delta^p$ past the $[ \delta, \theta_k ]$. The following notation will be used for any elements of $a,b$ of a graded ring and $m \ge 1$
-\[
-[b, a]^{(m)} = [b, [b, [b, \cdots [b, a] \dots ]
-\]
-where there are $m$ occurrences of $b$. By convention $[b,a]^{(0)} = a$.
-
-\begin{lemma} $b^m [b, a] = \sum_{i+j=m} \binom{m}{i} [b,a]^{(i+1)} b^j$ for $m \ge 1$.
-\end{lemma}
-\begin{proof}
-By induction, with the case $m = 1$ being clear. Using the inductive hypothesis
-\[
-b^{m+1} [b, a] = \sum_{i+j=m} \binom{m}{i} b [b,a]^{(i+1)} b^j = \sum_{i+j=m} \binom{m}{i} \Big[ [b,a]^{(i+2)} b^j + [b,a]^{(i+1)} b^{j+1} \Big]\,.
-\]
-The powers of $b$ range from $0$ to $m+1$ and the coefficient of $b^j$ for $1 \le j \le m$ is
-\[
-\binom{m}{m-j} [b,a]^{(m-j+2)} + \binom{m}{m-j+1} [b,a]^{(m-j+2)} = \binom{m+1}{m+1-j} [b,a]^{(m-j+2)}\,.
-\]
-The coefficient of $b^0$ is $[b,a]^{(m+2)}$ and the coefficient of $b^{m+1}$ is $[b,a]^{(1)}$, so we are done.
-\end{proof}
-
-From the previous lemma we deduce that
-\begin{equation}\label{eq:calc1}
-\delta^p [ \delta, \theta_k ] = \sum_{i+j=p} \binom{p}{i} [ \delta, \theta_k ]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [ \delta, \lambda_k ]^{(i)} \delta^j\,.
-\end{equation}
-The next thing to compute is $[ \delta, \lambda_k ]^{(i)}$ for any $i$. For a tuple $\bold{q} = (q_1,\ldots,q_m)$ of integers between $1$ and $n$ we write (remembering that $k$ is fixed)
-\begin{gather*}
-\tau_{\bold{q}} = [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \lambda_k ] \cdots ]\\
-\theta_{\bold{q}}^* = \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
-\end{gather*}
-
-\begin{lemma} For $m \ge 0$
-\[
-[ \delta, \lambda_k ]^{(m)} = (-1)^m \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m}\,.
-\]
-\end{lemma}
-\begin{proof}
-By the inductive hypothesis
-\begin{align*}
-[\delta, \lambda_k]^{(m+1)} &= [ \delta, [ \delta, \lambda_k ]^{(m)} ]\\
-&= (-1)^m \sum_{\bold{q}} [ \delta, \tau_{\bold{q}} \theta_{\bold{q}}^* ]\\
-&= (-1)^m \sum_{\bold{q}, q_{m+1}} [ \lambda_{q_{m+1}} \theta_{q_{m+1}}^*, \tau_{\bold{q}} \theta_{\bold{q}}^* ]\\
-&= (-1)^m \sum_{\bold{q}, q_{m+1}} \big( \lambda_{q_{m+1}} \theta_{q_{m+1}}^* \tau_{\bold{q}} \theta_{\bold{q}}^* + \tau_{\bold{q}} \theta_{\bold{q}}^* \lambda_{q_{m+1}} \theta_{q_{m+1}}^* \big)\\
-&= (-1)^m \sum_{\bold{q}, q_{m+1}} \big( -\lambda_{q_{m+1}} \tau_{\bold{q}}  \theta_{\bold{q}}^* \theta_{q_{m+1}}^* + (-1)^m \tau_{\bold{q}} \lambda_{q_{m+1}} \theta_{\bold{q}}^* \theta_{q_{m+1}}^* \big)\\
-&= (-1)^{m+1} \sum_{\bold{q}, q_{m+1}} [ \lambda_{q_{m+1}}, \tau_{\bold{q}} ] \theta_{\bold{q}}^* \theta_{q_{m+1}}^*
-\end{align*}
-as claimed.
-\end{proof}
-
-Continuing the computation of \eqref{eq:calc1} we have
-\begin{equation}
-\label{eq:calc2}
-\delta^p [\delta, \theta_k ] = \sum_{i+j=p} \binom{p}{i} (-1)^i \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^j\,.
-\end{equation}
-
-\begin{lemma}\label{lemma:commutator_wha} For $m \ge 1$
-\[
-[ \theta_k, \delta^m ] = \sum_{i=0}^{m-1} (-1)^{i+1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^{m-i-1}
-\]
-\end{lemma}
-\begin{proof} 
-Beginning from \eqref{eq:catfish}
-\begin{align*}
-[ \theta_k, \delta^m ] &= - \sum_{p=0}^{m-1} \delta^p [ \delta, \theta_k ] \delta^{m-p-1}\\
-&= - \sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} (-1)^i \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^j \delta^{m-p-1}
-\end{align*}
-\end{proof}
-
-\begin{lemma}\label{lemma:combin} For integers $a, b \ge 0$
-\begin{equation}\label{eq:combin}
-\frac{b!}{(a+b+1)!} \sum_{a \le m \le a + b} \binom{m}{a} = \frac{1}{(a+1)!}
-\end{equation}
-\end{lemma}
-\begin{proof}
-Denoting the left hand side of \eqref{eq:combin} by $\Omega_{a,b}$ the proof is an induction on $b$, i.e. by computing $\Omega_{a,b+1}$ in terms of $\Omega_{a,b}$.
-\end{proof}
-
-\begin{lemma}
-\[
-[\theta_k, \exp(-\delta)] = \sum_{m \ge 0} \frac{1}{(m+1)!} \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m} \exp(-\delta)\,.
-\]
-\end{lemma}
-\begin{proof}
-Using Lemma \ref{lemma:combin} and Lemma \ref{lemma:commutator_wha}
-\begin{align*}
-[\theta_k, \exp(-\delta)] &= \sum_{m \ge 0} \frac{(-1)^m}{m!} [\theta_k, \delta^m]\\
-&= \sum_{m \ge 0} \sum_{i=0}^{m-1} (-1)^{i+m+1} \frac{1}{m!} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^{m-i-1}\\
-&= \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{(t+1+i)!} \sum_{i \le p \le t + i} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^t\\
-&= \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{t!} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^t\\
-&= \sum_{m \ge 0} \frac{1}{(m+1)!} \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m} \exp(-\delta)\,.
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{theorem:psik}] 
-\begin{align*}
-\psi_k &= \exp(-\delta) \theta_k \exp(\delta)\\
-&= \theta_k \exp(-\delta) \exp(\delta) + [ \exp(-\delta), \theta_k ] \exp(\delta)\\
-&= \theta_k - [ \theta_k, \exp(-\delta) ] \exp(\delta)\\
-&= \theta_k - \sum_{i \ge 0} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \exp(-\delta) \exp(\delta)\\
-&= \theta_k - \sum_{i \ge 0} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} 
-\end{align*}
-which completes the proof.
-\end{proof}
-
 \bibliographystyle{amsalpha}
@@
 
-\bibitem{enderton}
-H.~B.~Enderton, \textsl{Elements of recursion theory}, Handbook of Mathematical Logic, North-Holland (1977) 527--566.
-
 \bibitem{friedrich}
@@
 
-\bibitem{gentzen}
-G.~Gentzen, \textsl{The Collected Papers of Gerhard Gentzen}, (Ed. M. E. Szabo), Amsterdam, Netherlands: North-Holland, 1969.
-
 \bibitem{girard_llogic}
@@
 
-\bibitem{girard_towards}
-J.-Y.~Girard, \textsl{Towards a geometry of interaction}, In J.~W.~Gray and A.~Scedrov, editors, Categories in Computer Science and Logic, volume 92 of Contemporary Mathematics, 69--108, AMS (1989).
-
 \bibitem{greuel}
@@
 S.-J.~Kang, M.~Kashiwara and S.-J.~Oh, \textsl{Supercategorification of quantum Kac-Moody algebras II}, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.
-
-\bibitem{Calinetal}
-C.~I. Lazaroiu and D.~McNamee, unpublished.
 

### 2015-08-29 cutsystems2_blah.tex
New version of cut systems paper.

--- 2015-08-29 cutsystems-new.tex
@@
-% TODO
-% - fix the equivalence of L with LG
-% - add stuff to the example
-
 \documentclass[english,letter paper,12pt,leqno]{article}
@@
 \usepackage[all]{xy}
-\usepackage{dsfont}
 \usepackage{tikz}
-\def\nicedashedcolourscheme{\shadedraw[top color=blue!22, bottom color=blue!22, draw=gray, dashed]}
-\def\nicecolourscheme{\shadedraw[top color=blue!22, bottom color=blue!22, draw=white]}
-\def\nicepalecolourscheme{\shadedraw[top color=blue!12, bottom color=blue!12, draw=white]}
-\def\nicenocolourscheme{\shadedraw[top color=gray!2, bottom color=gray!25, draw=white]}
-\def\nicereallynocolourscheme{\shadedraw[top color=white!2, bottom color=white!25, draw=white]}
-\definecolor{Myblue}{rgb}{0,0,0.6}
-\usepackage[a4paper,colorlinks,citecolor=Myblue,linkcolor=Myblue,urlcolor=Myblue,pdfpagemode=None]{hyperref}
 
@@
 \newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{setup}[theorem]{Setup}
 
@@
 	\theoremstyle{example}
-	\newtheorem{definition}[theorem]{Definition}
-	\newtheorem{example}[theorem]{Example}
-	\newtheorem{remark}[theorem]{Remark}
-	\newtheorem{strat}[theorem]{Strategy}
+	\newtheorem{definition}[equation]{Definition}
+	\newtheorem{example}[equation]{Example}
+	\newtheorem{remark}[equation]{Remark}
 
@@
 \def\Ker{\operatorname{Ker}}
-\def\im{\operatorname{Im}}
+\def\im{\operatorname{im}}
 \def\can{\operatorname{can}}
@@
 \def\Modd{\operatorname{Mod}}
-\def\be{\begin{equation}}
-\def\ee{\end{equation}}
-\def\nN{\mathds{N}}
-\def\nZ{\mathds{Z}}
-\def\nQ{\mathds{Q}}
-\def\nR{\mathds{R}}
-\def\nC{\mathds{C}}
 \DeclareMathOperator{\Ext}{Ext}
@@
 \DeclareMathOperator{\Cat}{Cat}
-\DeclareMathOperator{\Spec}{Spec}
 
@@
 \def\Res{\res\!}
-\newcommand{\ud}{\mathrm{d}}
-\newcommand{\Ress}[1]{\res_{#1}\!}
 \newcommand{\cat}[1]{\mathcal{#1}}
@@
 
-\title{Computing with cut systems +}
+\title{Cut systems and bicategories II}
 \author{Daniel Murfet}
@@
 
-\begin{abstract}
-A cut system has objects, $1$-morphisms and $2$-morphisms, similar to a bicategory.
-In contrast to the composition of $1$-morphisms in a bicategory, the cut operation on $1$-morphims in a cut system produces representations of Clifford algebras in supercategories rather than bare objects.
-The motivating example of a cut system refines the bicategory of Landau-Ginzburg models, in which the objects are hypersurface singularities and the $1$-morphisms are matrix factorisations.
-\end{abstract}
-
-\tableofcontents
-
 \section{Introduction}
 
-The bicategory of Landau-Ginzburg models $\LG$ has polynomials $W(x)$ called \textsl{potentials} as its objects, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
-This bicategory has been studied extensively in connection with topological field theory \cite{??} and knot invariants \cite{??}.
-The most important and nontrivial structure in this bicategory is the functor
-\be\label{eq:intro_functor_comp}
-\LG(V,U) \otimes_{\nC} \LG(W, V) \lto \LG(W,U)
-\ee
-which composes $1$-morphisms for potentials $W(x),V(y),U(z)$.
-Continuing the approach developed with Dyckerhoff in \cite{??}, the aim of this paper is to explicitly describe this functor.
-Any increase in our understanding of the operation of composition in $\LG$ has implications for the subjects where this bicategory makes an appearance, but our primary application is to the semantics of linear logic constructed in \cite{??}.
+\begin{itemize}
+\item The interpretation of MALL (multiplicative additive linear logic)
+\item Higher computation
+\item Implementation in Singular
+\end{itemize}
+
+TODO: finite fields, exponentials, link between additives and probabilistic semantics
+
+\section{The interpretation of linear logic}
+
+In the sequel:
 
 \begin{itemize}
-\item We define another bicategory without units $\cat{L}$
-\item We prove $\cat{L}$ is equivalent to $\LG$
-\item We show how to model $\cat{L}$ in schemes (next paper)
+\item What is linear logic
+\item Geometry of interaction
+\item Interpretations of linear logic in monoidal categories
+\item $\LG$ is a monoidal bicategory
+\item What is a monoidal cut system?
+\item The interpretation
+\item Do some kind of argument on equality of boolean circuits using algebra?
+i.e.
+normalize a boolean circuit with two stages.
+Of course everything is boring if we just use identity defects, so also use the crossing.
 \end{itemize}
 
-First of all, let us be more precise about the kind of explicit description we are looking for.
-Observe that once we have chosen a homogeneous basis, a matrix factorisation of $W(x) - V(y)$ is just a matrix of polynomials
-\[
-D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (W(x) - V(y)) \cdot I_{2r}\,.
-\]
-If we fix the rank $r$ and bound the degrees of the monomials appearing in $D$ by some integer $k$, it is easy to parametrise such matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$.
-Then the set of objects of $\LG(W,V)$ can be described as a disjoint union of inductive limits of these schemes
-\[
-\operatorname{ob} \LG(W,V) = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)\,.
-\]
-The kind of explicit description we are looking for is a lifting of the function \eqref{eq:intro_functor_comp} on the level of objects to a morphism of schemes
-\be\label{eq:composition_as_schememap}
-\mathscr{M}_{r',k'}(V,U) \times \mathscr{M}_{r,k}(W,V) \lto \mathscr{M}_{f(r,r'),g(k,k')}(W, U)\,.
-\ee
-Unfortunately this appears difficult, if not impossible, as stated.
-In this article we explain how the replacement of $\LG(W,U)$ by an equivalent category $\cat{L}(W,U)$, called the \textsl{Clifford thickening}, allows for such a lifting of \eqref{eq:intro_functor_comp} to a morphism of schemes.
+\section{Higher computation}
 
-% One consequence is that $\LG$ is equivalent to the bicategory $\cat{L}^\bullet$, which is \emph{computable} in the sense that its operations may be embodied in software.
-To some extent this software already exists: a component of what we are here calling the cut system $\cat{L}$ (developed earlier in joint work with Dyckerhoff \cite{dm1102.2957}\footnote{For a more detailed discussion of the relation of this work with the present paper, see Remark \ref{remark:relation_to_toby_paper}.}) has already been implemented in the computer algebra package Singular in joint work with Carqueville \cite{khovhompaper}, and used to compute tables of Khovanov-Rozansky knot homologies.
-The code was also used in the discovery of the generalised orbifolding relations among ADE singularities by Carqueville, Ros Camacho and Runkel \cite{ade}.
-\medskip
+Observables, proof-of-work, structured input data (modules over monads) and induced output structure via $2$-morphisms, proof-of-idempotence, proof-of-commutativity, cones and crossings, observational equivalence via Chern characters.
 
-The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
-In Section \ref{section:cut_systems} we define cut systems and the superbicategory associated to a cut system, then we construct the cut model of $\LG$ in Section \ref{section:lg_cut_system}.
+\section{The implementation in Singular}
 
-\medskip
+Introduction: computation is integration.
+Argue that the true mathematical semantics of symbols are cohomology classes (example of basis for the cohomology of torus).
+Computation has two stages: in the first stage one produces new cohomology classes from old ones via convolution (e.g.
+concatenating $\lambda$-terms) and in the second stage one finds out how to write the new cycles as linear combinations of the normal forms (e.g.
+normalisation).
+In terms of Hodge theory finding harmonic representatives consists of projecting onto certain subspaces, i.e.
+\emph{integrals} against the chosen basis.
+We deal with a categorified notion of cocycle, the second stage is now represented by finding finite rank representatives in symbolic form (in the case of loops at $0$ splitting idempotents is analogous to picking out the subspace of harmonic forms in a larger space of cocycles).
 
-\emph{Acknowledgements.} Thanks to Nils Carqueville and Ingo Runkel for helpful comments on the draft.
-Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.
-
-\section{Background}\label{section:background}
-
-Throughout $k$ is a commutative $\mathbb{Q}$-algebra. By default categories and functors are $k$-linear.
-
-\subsection{Supercategories}
-
-A superbicategory has for every $1$-morphism $F$ an associated $1$-morphism $\Psi F$ with $\Psi^2 \cong 1$, and in this sense the categories of $1$-morphisms are $\mathbb{Z}_2$-graded.
-The bicategory of Landau-Ginzburg models is an example of a superbicategory.
-Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role in the definition of cut systems, superbicategories are the natural language.
-Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.
-
-\begin{definition} A \emph{supercategory} is a category $\cat{C}$ together with a functor $\Psi: \cat{C} \lto \cat{C}$ and a natural isomorphism $\xi: \Psi^2 \lto 1_{\cat{C}}$ satisfying the condition
-\[
-\xi * 1_{\Psi} = 1_{\Psi} * \xi
-\]
-as natural transformations $\Psi^3 \lto \Psi$.
-A \emph{superfunctor} $(F, \gamma)$ from a supercategory $(\cat{C}, \Psi_{\cat{C}})$ to a supercategory $(\cat{D}, \Psi_{\cat{D}})$ is a functor $F: \cat{C} \lto \cat{D}$ together with a natural isomorphism $\gamma: F \Psi_{\cat{C}} \lto \Psi_{\cat{D}} F$ satisfying
-\[
-1_F * \xi = (\xi * 1_F ) ( 1_{\Psi} * \gamma ) ( \gamma * 1_{\Psi} )\,.
-\]
-A \emph{supernatural transformation} $\varphi: F \lto G$ between superfunctors $(F,\gamma_F), (G,\gamma_G)$ is a natural transformation making the following diagram commute:
-\[
-\xymatrix{
-F \Psi \ar[r]^-{\varphi \Psi}\ar[d]_-{\gamma_F} & G \Psi \ar[d]^-{\gamma_G}\\
-\Psi F \ar[r]_-{\Psi \varphi} & \Psi G
-}\,.
-\] 
-\end{definition}
-
-\begin{example}\label{example:Aassup} If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra there is a supercategory $\cat{A}$ with set of objects $|\cat{A}| = \mathbb{Z}_2$ and morphisms $\cat{A}(0,0) = \cat{A}(1,1) = A_0, \cat{A}(0,1) = \cat{A}(1,0) = A_1$ with the obvious composition and addition rules.
-The functor $\Psi$ is defined on objects by $\Psi(i) = i+1$ and on morphisms by the identity, while $\xi = 1$.
-\end{example}
-
-Let $\cat{C}$ be a supercategory. For objects $X,Y \in \cat{C}$ we define the $\mathbb{Z}_2$-graded $k$-module
-\[
-\cat{C}^*(X,Y) = \prod_{i \in \mathbb{Z}_2} \cat{C}(X, \Psi^i Y)\,.
-\]
-There is for any triple $X,Y,Z$ of objects a morphism of graded modules
-\[
-\cat{C}^*(Y,Z) \otimes_k \cat{C}^*(X, Y) \lto \cat{C}^*(X,Z)
-\]
-given for instance by $\varphi \otimes \psi \mapsto \xi \Psi( \varphi ) \psi$ when $\varphi, \psi$ are both of degree one.
-This makes $\cat{C}$ into a category enriched over the monoidal category of $\mathbb{Z}_2$-graded $k$-modules.
-
-There are isomorphisms of graded modules $\cat{C}^*(X, \Psi Y) \cong \Psi \cat{C}^*(X, Y) \cong \cat{C}^*(\Psi X, Y)$ where $\Psi V = V [1]$ denotes the grading shift on a $\mathbb{Z}_2$-graded $k$-module.
-For $\mathbb{Z}_2$-graded $k$-modules $V,W$ we write $\Hom^0_k(V, W)$ for the module of degree zero maps and $\Hom_k^*(V, W)$ for the $\mathbb{Z}_2$-graded module of homogeneous maps.
-If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $A^{\operatorname{op}}$ denotes the same underlying graded module with multiplication $f * g = (-1)^{|f||g|} gf$.
-
-\begin{definition} Let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra and $\cat{C}$ a supercategory.
-A \emph{left $A$-module in $\cat{C}$} is an object $X \in \cat{C}$ together with a morphism of $\mathbb{Z}_2$-graded algebras $A \lto \cat{C}^*(X,X)$.
-A \emph{morphism} of left $A$-modules is a morphism in $\cat{C}$ which commutes with the $A$-action in the obvious sense.
-The category of left $A$-modules in $\cat{C}$ is denoted $\cat{C}_A$.
-Right modules are defined similarly, using $A^{\operatorname{op}}$.
-\end{definition}
-
-\begin{remark}\label{remark:supercat_idempcomp} Viewing $A$ as a supercategory $\cat{A}$ as in Example \ref{example:Aassup}, there is an equivalence between the category of $A$-modules in $\cat{C}$ and the category of superfunctors $\cat{A} \lto \cat{C}$ and supernatural transformations.
-\end{remark}
-
-\begin{remark}\label{remark:idempotent_completion} The \emph{idempotent completion} $\cat{C}^\omega$ of a category $\cat{C}$ has as objects pairs $(X,e)$ consisting of an object $X \in \cat{C}$ and an idempotent endomorphism $e: X \lto X$.
-In $\cat{C}^\omega$ a morphism $\phi: (X,e) \lto (Y,e)$ is a morphism $\phi: X \lto Y$ satisfying $\phi e = \phi$ and $e \phi = \phi$.
-The identity on $(X,e)$ is $e$.
-There is a fully faithful functor $\iota: \cat{C} \lto \cat{C}^{\omega}, \iota(X) = (X,1_X)$ which is an equivalence if $\cat{C}$ is idempotent complete (i.e.
-all idempotents split in $\cat{C}$).
-
-If $\cat{C}$ is a supercategory then there is a functor $\Psi^\omega: \cat{C}^\omega \lto \cat{C}^\omega$ defined on objects by $\Psi(X,e) = (\Psi X, \Psi e)$ and a natural isomorphism $\xi: \Psi^\omega \circ \Psi^\omega \lto 1_{\cat{C}^\omega}$ defined by $\xi_{(X,e)} = e \xi_X$.
-The tuple $(\cat{C}^\omega, \Psi^\omega, \xi^\omega)$ is a supercategory.
-\end{remark}
-
-For background on bicategories see \cite{bor94} and the references in \cite{lgdual}.
-We follow the notation of \cite{lgdual}, so that lower case letters $a,b, \ldots$ denote objects of a bicategory, while upper case letters $X,Y, \ldots$ and greek letters $\alpha, \beta, \ldots$ respectively denote $1$-morphisms and $2$-morphisms.
-Units are denoted $\Delta$, associators are $\alpha$, and unitors are $\lambda, \rho$.
-The composition of $Y,X$ is denoted $YX$ or $Y \circ X$.
-
-\begin{definition} A \emph{superbicategory} is a bicategory $\cat{B}$ together with the data:
 \begin{itemize}
-\item For each object $a$ a $1$-morphism $\Psi_a: a \lto a$ and a $2$-isomorphism $\xi_a: \Psi^2_a \lto \Delta_a$.
-\item For each $1$-morphism $X: a \lto b$ a natural $2$-isomorphism $\gamma_X: X \Psi_a \lto \Psi_b X$.
+\item History of computer science as in Sergeraert.
+\item Computation with cocycles on the torus $T$ and kernels on $T \times T$.
+\item We want to then refer to effective homology, but this requires a transition... take the point of view that Hodge theory is really a deformation retract?
 \end{itemize}
-This data is required to satisfy the following axioms:
-\begin{itemize}
-\item For each composable pair $X,Y$ of $1$-morphisms the diagram
-\[
-\xymatrix@C+2pc@R+1pc{
-(YX) \Psi \ar[rrr]^-{\gamma_{YX}} \ar[d]_-{\alpha} & & & \Psi ( YX )\\
-Y ( X \Psi ) \ar[r]_-{1_Y * \gamma_X} & Y( \Psi X ) \ar[r]_-{\alpha^{-1}} & ( Y \Psi ) X \ar[r]_-{\gamma_Y * 1_X} & (\Psi Y ) X \ar[u]_-{\alpha}
-}
-\]
-commutes.
-\item For every object $a$, $\xi_a * 1_\Psi = 1_\Psi * \xi_a$.
-\item For every $1$-morphism $X : a \lto b$, $1_X * \xi_a = ( \xi_b * 1_X ) ( 1_\Psi * \gamma_X ) (\gamma_X * 1_\Psi )$.
-\end{itemize}
-\end{definition}
-
-\begin{example} Supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
-\end{example}
-
-A superbicategory can be constructed out of a bicategory $\cat{B}$ in which the categories $\cat{B}(a,b)$ are all equipped with the structure of supercategories; see Appendix \ref{section:constructing_superbicategories}.
-
-\begin{example}\label{example:bicategory_m} There is a bicategory of $\mathbb{Z}_2$-graded $k$-algebras where $1$-morphisms are $\mathbb{Z}_2$-graded bimodules and $2$-morphisms are degree zero bimodule maps.
-Given a $B$-$A$-module $M$ the shift $M[1]$ has the grading $M[1]_i = M_{i+1}$ and the left and right action given by
-\[
-b \cdot m = (-1)^{|b|} bm, \qquad m \cdot a = (-1)^{|a|} m a\,.
-\]
-This is a functor $\Psi = (-)[1]$ on the category of $B$-$A$-bimodules and with $\xi = 1$ this defines the structure of a supercategory on this category of bimodules.
-The usual isomorphisms of bimodules $\tau$
-\begin{align}
-N[1] \otimes M &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto n \otimes m \label{eq:shift_iso_a}\\
-N \otimes M[1] &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto (-1)^{|n|} n \otimes m\label{eq:shift_iso_b}
-\end{align}
-satisfy the conditions in Appendix \ref{section:constructing_superbicategories} and therefore give the bicategory of $\mathbb{Z}_2$-graded algebras and bimodules the structure of a superbicategory.
-\end{example}
-
-\begin{definition} Given two superbicategories $\cat{B}, \cat{C}$ a \emph{lax superfunctor} $\Phi: \cat{B} \lto \cat{C}$ is a lax functor together with, for each object $a$ in $\cat{B}$, a $2$-morphism
-\[
-\kappa_a: \Psi_{\Phi a} \lto \Phi( \Psi_a )
-\]
-satisfying two coherence conditions:
-\begin{itemize}
-\item[(a)] for all $a$, commutativity of
-\[
-\xymatrix@C+2pc{
-\Psi_{\Phi a} \Psi_{\Phi a} \ar[dd]_-{\xi}\ar[r]^-{\kappa * \kappa} & \Phi( \Psi_a ) \Phi( \Psi_a ) \ar[d]\\
-& \Phi( \Psi_a \Psi_a ) \ar[d]^-{\Phi(\xi)}\\
-\Delta_{\Phi a} \ar[r] & \Phi( \Delta_a )
-}
-\]
-\item[(b)] for each $1$-morphism $X: a \lto b$ in $\cat{B}$, commutativity of
-\[
-\xymatrix@C+2pc{
-\Phi(X) \Psi_{\Phi a} \ar[d]_-{\gamma} \ar[r]^-{1 * \kappa} & \Phi(X) \Phi(\Psi_a) \ar[r] & \Phi( X \Psi_a ) \ar[d]^-{\Phi(\gamma)}\\
-\Psi_{\Phi b} \Phi(X) \ar[r]_-{\kappa * 1} & \Phi(\Psi_b) \Phi(X) \ar[r] & \Phi( \Psi_b X)
-}
-\]
-\end{itemize}
-A \emph{strong superfunctor} is a lax superfunctor with $\kappa_a$ an isomorphism for every object $a$.
-\end{definition}
-
-\subsection{The superbicategory of Landau-Ginzburg models}\label{section:superbicatLG}
-
-A polynomial $W \in k[x_1,\ldots,x_n]$ is a \emph{potential} if it satisfies the three conditions set out in \cite[Section 2.2]{lgdual}, the two most important being that the partial derivatives $\partial_{x_1} W, \ldots, \partial_{x_n} W$ form a quasi-regular sequence in $k[x]$ and that the quotient $J_W = k[x]/(\partial_{x_1} W, \ldots, \partial_{x_n} W)$ is a finitely generated free $k$-module.
-Typical examples are the ADE singularities \cite[I \S 2.4]{greuel} of which the simplest are the $A_N$-singularities $W_{A_N} = x_1^{N+1} + x_2^2 + \cdots + x_n^2$ .
-
-A \emph{matrix factorisation} of $W$ over $k[x]$ is a $\mathbb{Z}_2$-graded free $k[x]$-module $X = X^0 \oplus X^1$ together with an odd operator (the differential) $d_X: X \lto X$ satisfying $d_X^2 = W \cdot 1_X$.
-A matrix factorisation $(X,d_X)$ is \emph{finite rank} if the underlying free module is finitely generated.
-In this case we may, after choosing a homogeneous basis, write
-\[
-d_X = \begin{pmatrix} 0 & d_X^1 \\ d_X^0 & 0 \end{pmatrix}
-\]
-for matrices of polynomials $d_X^0, d_X^1$.
-Morphisms of matrix factorisations are degree zero $k[x]$-linear maps which commute with the differentials.
-There is a homotopy relation on morphisms, and the \emph{homotopy category} $\HMF(k[x],W)$ of matrix factorisations has as objects matrix factorisations and as morphisms the equivalence classes of morphisms of matrix factorisations up to homotopy.
-By $\hmf(k[x],W)$ we denote the full subcategory of finite rank matrix factorisations.
-For background we refer to \cite{yoshino98}.
-
-By $\hmf(k[x],W)^{\oplus}$ we denote the full subcategory of $\HMF(k[x],W)$ consisting of matrix factorisations which are direct summands (in the homotopy category) of finite rank matrix factorisations.
-Since $\HMF(k[x],W)$ is idempotent complete, there is an equivalence (see Remark \ref{remark:idempotent_completion} for the notation)
-\be\label{eq:omegavsoplus}
-\hmf(k[x],W)^\omega \lto \hmf(k[x],W)^{\oplus}
-\ee
-sending a pair $(X,e)$ to an infinite rank matrix factorisation splitting the idempotent $e$.
-
-If $(X,d_X)$ is a matrix factorisation then so is $(X[1], -d_X)$, and this defines a functor $\Psi = (-)[1]$ on the homotopy category of matrix factorisations.
-Together with the identity $\xi: \Psi^2 \lto 1$ this makes $\HMF(k[x],W)$ and $\hmf(k[x],W)$ into supercategories.
-
-The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$.
-Given potentials $W \in k[x]$ and $V \in k[y]$ the supercategory $\cat{LG}(W,V)$ is
-\[
-\cat{LG}(W,V) = \hmf(k[x,y], V - W)^{\oplus}\,.
-\]
-Given a third potential $U \in k[z]$ the composition law is a functor
-\[
-\LG(W,V) \otimes_k \LG(V, U) \lto \LG(W, U)
-\]
-which sends a pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ to the tensor product
-\begin{equation}\label{eq:tensor_comp}
-Y \otimes X = ( Y \otimes_{k[y]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
-\end{equation}
-This statement requires some care: $k[x,y,z]$ is an infinite rank free module over $k[x,z]$ and so $Y \otimes X$ is an infinite rank matrix factorisation of $U - W$ over $k[x,z]$.
-However one can prove that $Y \otimes X$ is a direct summand of a finite rank matrix factorisation \cite{dm1102.2957} and therefore a valid object in $\LG(W,U)$.
-
-Let $W \in k[x_1,\ldots,x_n]$ be a potential and $W(x')$ the same polynomial but in a second set of variables $x_1',\ldots,x_n'$.
-Using formal symbols $\Theta_i$ of odd degree, we define the $k[x,x']$-module
-\[
-\Delta_W = \bigwedge \big( \bigoplus_{i=1}^n k[x,x'] \cdot \Theta_i \big)\,.
-\]
-Equipped with a certain differential (see \cite{lgdual}) this is a matrix factorisation of $W(x) - W(x')$ and defines the unit in $\cat{LG}(W,W)$ for composition of $1$-morphisms.
-For the associator and unitor maps $\rho: X \otimes \Delta_W \lto X$ and $\lambda: \Delta_V \otimes X \lto X$ we also refer to \emph{ibid.}
-
-\begin{lemma} $\LG$ is a superbicategory.
-\end{lemma}
-\begin{proof}
-The categories $\LG(W,V)$ are all naturally supercategories, and the same isomorphisms as in \eqref{eq:shift_iso_a}, \eqref{eq:shift_iso_b} define the necessary natural isomorphisms $\tau$ to equip $\LG$ with the structure of a superbicategory with $\Psi_W = \Delta_W[1]$, using Appendix \ref{section:constructing_superbicategories}.
-\end{proof}
-
-The superbicategory structure on $\LG$ is used implicitly in \cite[Section 7]{lgdual}.
-
-\subsection{Partial derivatives as homotopies}\label{section:partial}
-
-Let $R = k[x_1,\ldots,x_n]$ be a polynomial ring and $X$ a finite rank matrix factorisation of $W$ over $R$.
-Let us fix a homogeneous basis for $X$ so that we may identify $d_X$ with a matrix, and differentiate this matrix entry-wise to obtain the matrix $\lambda_i = \partial_{x_i}(d_X)$.
-
-\begin{lemma} The odd $R$-linear operator $\lambda_i$ on $X$ is independent, up to homotopy, of the choice of basis.
-\end{lemma}
-
-\begin{lemma} As operators on $X$ we have $[ d_X, \lambda_i ] = \partial_{x_i} W \cdot 1_X$.
-\end{lemma}
-\begin{proof}
-Applying the Leibniz rule to the equation $d_X d_X = W$ we obtain
-\be\label{eq:partials_are_homotopies}
-d_X \partial_{x_i}(d_X) + \partial_{x_i}(d_X) d_X = \partial_{x_i} W
-\ee
-as claimed.
-\end{proof}
-
-It follows that any element in the Jacobi ideal $( \partial_{x_1}W , \ldots, \partial_{x_n} W )$ acts null-homotopically on any morphism in the homotopy category $\hmf(R,W)$.
-Moreover these homotopies $\lambda_i$ are central, in the following sense:
-
-\begin{lemma}\label{lemma:naturalityoflambda} Let $\phi: X \lto X'$ be a morphism of matrix factorisations and write $\lambda_i = \partial_{x_i}(d_X)$ and $\lambda'_i = \partial_{x_i}(d_{X'})$.
-Then there is a homotopy $\phi \lambda_i \simeq \lambda'_i \phi$.
-\end{lemma}
-\begin{proof}
-From $d_{X'} \phi = \phi d_X$ we deduce
-\[
-\partial_{x_i}( d_{X'} ) \phi + d_{X'} \partial_{x_i}( \phi ) = \partial_{x_i}( \phi ) d_X + \phi \partial_{x_i}( d_X )
-\]
-and hence
-\[
-\partial_{x_i}( d_{X'} ) \phi - \phi \partial_{x_i}( d_X ) = \partial_{x_i}(\phi) d_X - d_{X'} \partial_{x_i}(\phi)
-\]
-as claimed.
-\end{proof}
-
-\begin{lemma}\label{lemma:commutator_of_lambdas} There is a homotopy $[ \lambda_i, \lambda_j ] \simeq \partial_{x_i x_j}(W) \cdot 1_X$.
-\end{lemma}
-\begin{proof}
-Differentiating \eqref{eq:partials_are_homotopies} with respect to $j$ leaves
-\[
-\partial_{x_j}(d_X) \partial_{x_i}(d_X) + d_X \partial_{x_jx_i}(d_X) + \partial_{x_jx_i}(d_X) d_X + \partial_{x_i}(d_X) \partial_{x_j}(d_X) = \partial_{x_ix_j}W
-\]
-from which we read off
-\[
-\lambda_i \lambda_j + \lambda_j \lambda_i = \partial_{x_ix_j}W + [d, -\partial_{x_jx_i}(d_X)]\,.
-\]
-\end{proof}
-
-\subsection{Clifford algebras}\label{section:clifford_algs}
-
-In a cut system the composition rule produces objects which are representations of Clifford algebras.
-We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}.
-For $n \ge 0$ the Clifford algebra $C_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $\gamma_1,\ldots,\gamma_n$ and $\gamma_1^\dagger, \ldots, \gamma_n^\dagger$ subject to the following relations
-\be\label{eq:clifford_relations}
-[\gamma_i, \gamma_j] = 0, \qquad [\gamma_i^\dagger, \gamma_j^\dagger] = 0, \qquad [\gamma_i, \gamma_j^\dagger] = \delta_{ij}\,.
-\ee
-for all $1 \le i, j \le n$.
-In this paper all our commutators are graded, $[a,b] = ab - (-1)^{|a||b|} ba$.
-We set $C_0 = k$.
-These Clifford algebras have essentially only one nontrivial representation, sometimes called the \emph{spinor representation} \cite[p.14]{friedrich}.
-To define this representation we use the $\nZ_2$-graded $k$-module
-\[
-F_n = k \theta_1 \oplus \cdots \oplus k \theta_n
-\]
-where the $\theta_i$ are formal variables of odd degree, and set
-\be
-S_n = \bigwedge F_n = \bigwedge\big( k \theta_1 \oplus \cdots \oplus k \theta_n \big)\,.
-\ee
-
-\begin{definition}\label{defn:contraction} Left multiplication in the exterior algebra defines an odd operator
-\begin{gather*}
-\theta_i \wedge (-): S_n \lto S_n\,,\\
-\theta_{j_1} \cdots \theta_{j_r} \mapsto \theta_i \theta_{j_1} \cdots \theta_{j_r}\,.
-\end{gather*}
-Contraction from the left defines an odd operator
-\begin{gather*}
-\theta_i^*\, \lrcorner\, (-): S_n \lto S_n\,,\\
-\theta_{j_1} \cdots \theta_{j_r} \mapsto \sum_{l=1}^r (-1)^{(l-1)} \delta_{i,j_l} \theta_{j_1} \cdots \widehat{ \theta_{j_l} } \cdots \theta_{j_r}\,.
-\end{gather*}
-\end{definition}
-
-Usually we write simply $\theta_i$ for the operator $\theta_i \wedge (-)$ and $\theta_i^*$ for the operator $\theta_i^*\, \lrcorner\, (-)$.
-The spinor representation is defined by the next lemma, which also shows that the algebras $C_n$ are Morita trivial in the sense that they are isomorphic to the endomorphism algebras of a finite rank free $\mathbb{Z}_2$-graded $k$-module.
-
-\begin{lemma}\label{defn:spinorrep} The map $C_n \lto \End_k(S_n)$ defined by
-\[
-\gamma_i \mapsto \theta_i \wedge (-), \qquad \gamma_i^\dagger \mapsto \theta_i^*\, \lrcorner\, (-)
-\]
-is an isomorphism of $\mathbb{Z}_2$-graded $k$-algebras.
-\end{lemma}
-
-In particular this means that every $\mathbb{Z}_2$-graded $C_n$-module is isomorphic to $S_n \otimes_k V$ for some $\mathbb{Z}_2$-graded $k$-module $V$. Using the isomorphism of $k$-modules
-\[
-F_m \oplus F_n \cong F_{m+n}
-\]
-which maps the ordered basis $\theta_1,\ldots,\theta_m$ of $F_m$ to the first $m$ basis elements of $F_{m+n}$ in their given order, and the ordered basis of $F_n$ to the last $n$ basis elements, we define
-\[
-S_m \otimes_k S_n = \bigwedge F_m \otimes_k \bigwedge F_n \cong \bigwedge F_{m+n} = S_{m+n}\,.
-\]
-From this we deduce an isomorphism of algebras
-\begin{equation}\label{eq:algebra_A_additive}
-C_m \otimes_k C_n \cong C_{m+n}\,.
-\end{equation}
-Given $m, n \ge 0$ we introduce notation for the $C_m$-$C_n$-bimodule
-\begin{equation}
-S_{m,n} = S_m \otimes_k S_n^* = \Hom_k(S_n,S_m)
-\end{equation}
-where $S_n^* = \Hom_k(S_n, k)$. There is an isomorphism of $C_l$-$C_n$-bimodules
-\begin{equation}\label{eq:isosbimodule}
-S_{l,m} \otimes_{A_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{C_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
-\end{equation}
-
-\begin{definition}\label{defn:idempotent_e} For $n \ge 0$ let $e_n \in C_n$ denote the element
-\[
-e_n = \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1\,.
-\]
-This is the idempotent corresponding to the summand $k \cdot 1$ of $S_n$.
-\end{definition}
-
-\begin{definition}\label{defn:idempotent_gen} More generally, given $m, n \ge 0$ consider the $k$-linear map
-\[
-\xymatrix{
-S_n \ar[r] & k \cdot 1 \ar[r]^{\operatorname{inc}} & S_m
-}
-\]
-given by the projection to $k \cdot 1$ followed by the inclusion into $S_m$. This defines an element
-\[
-\iota_{m,n} \in \Hom_k(S_n, S_m) = S_m \otimes_k S_n^*\,.
-\]
-Then obviously $\iota_{n,n} = e_n$.
-\end{definition}
-
-\begin{remark} Recall that given a finite rank free $k$-module $V$ and a symmetric bilinear form $B: V \otimes_k V \lto k$ the associated Clifford algebra $\operatorname{Cl}(V, B)$ is the associative $k$-algebra generated by the elements of $V$ subject to the relations
-\[
-vw + wv = B(v,w) \cdot 1\,.
-\]
-This is a $\mathbb{Z}_2$-graded $k$-algebra when we assign $|v| = 1$ for all $v \in V$ and $|1| = 0$.
-If we take $V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then $C_n$ is the Clifford algebra of the pair $(V,B)$.
-\end{remark}
-
-\section{The Clifford thickening}
-
-Let $\cat{T}$ be a small idempotent complete supercategory.
-We construct a new supercategory $\cat{T}^\bullet$ called the \emph{Clifford thickening} in which the objects are pairs $(X,n)$ of an integer $n \ge 0$ and a left $C_n$-module $X$ in $\cat{T}$.
-Recall that if $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{T}_A$ denotes the supercategory of $A$-modules in $\cat{T}$ with $A$-linear maps.
-
-%The upshot is that if $A$ is a Morita trivial $\mathbb{Z}_2$-graded $k$-algebra and if $X \in \cat{T}$ is a left $A$-module, while $V$ is a $\mathbb{Z}_2$-graded right $A$-module (in the usual sense, i.e.
-in the category of $k$-modules) then there is an object $V \otimes_A X$ in $\cat{T}$ which is functorial in both $V$ and $X$.
-Morever if $V$ is a $B$-$A$-bimodule then $V \otimes_A X$ is naturally a left $B$-module, and so on.
-
-Similarly to Example \ref{example:bicategory_m} there is a superbicategory $\cat{M}$ of Morita trivial $\mathbb{Z}_2$-graded $k$-algebras: $1$-morphisms are $\mathbb{Z}_2$-graded bimodules which are finitely generated and projective over $k$ and $2$-morphisms are degree zero bimodule maps.
-We will need the operation of tensoring objects of $\cat{T}$ with $k$-modules, which is recalled in Appendix \ref{section:tensorproduct_supcat}.
-
-\begin{proposition} The assignment of the supercategory $\cat{T}_A$ to an algebra $A$ and of the superfunctor $\Phi_V = V \otimes_A (-)$ to a $B$-$A$-bimodule $V$ determines a strong superfunctor
-\[
-\Phi^{\cat{T}}: \cat{M} \lto \Cat^{\operatorname{sup}}_k
-\]
-to the superbicategory of small supercategories and superfunctors.
-\end{proposition}
-\begin{proof}
-The isomorphism $\Phi_W \circ \Phi_V \cong \Phi_{W \otimes V}$ is given by Lemma \ref{lemma:assoctensor}, and apart from that the only checking that needs to be done are straightforward coherence diagrams.
-\end{proof}
-
-Next we construct a strong functor into $\cat{M}$ which picks out the Clifford algebras.
-
-\begin{definition}
-Let $\mathbb{N}$ denote the category of integers $n \ge 0$ with a unique morphism $\phi_{m,n}: n \lto m$ for each pair $m,n$. %This category is monoidal with $m \otimes n = m + n$.
-\end{definition}
-
-We view $\mathbb{N}$ as a bicategory with only identity $2$-morphisms.
-
-\begin{lemma} There is a strong functor $\mathbb{N} \lto \cat{M}$ defined by
-\begin{gather*}
-n \mapsto C_n = \End_k( S_n ),\\
-\phi_{m,n} \mapsto S_{m,n} = S_m \otimes_k S_n^*\,.
-\end{gather*}
-\end{lemma}
-
-The composite of these strong functors is a strong functor
-\begin{equation}\label{eq:strongfunctorgroth}
-\xymatrix@C+1pc{
-\mathbb{N} \ar[r] & \cat{M} \ar[r]^-{\Phi^{\cat{T}}} & \Cat^{\operatorname{sup}}_k
-}
-\end{equation}
-sending $n$ to the category of left $C_n$-modules in $\cat{T}$ and $\phi_{m,n}$ to the functor $S_{m,n} \otimes_{C_n} -$.
-There is a close connection between strong functors into the bicategory of small categories, and what are called cofibered categories, given by the Grothendieck construction \cite{vistoli}.
-
-\begin{definition} The \emph{Clifford thickening} $\cat{T}^\bullet$ of the supercategory $\cat{T}$ is the category which results from the Grothendieck construction applied to the strong functor \eqref{eq:strongfunctorgroth}.
-\end{definition}
-
-More concretely $\cat{T}^\bullet$ is the category with objects all pairs $(X,n)$ of an integer $n \ge 0$ and an object $X \in \cat{T}$ together with a left $C_n$-action.
-A morphism $\alpha: (X,n) \lto (Y,m)$ is a morphism of $C_m$-modules $\alpha: S_{m,n} \otimes_{C_n} X \lto Y$.
-Composition of a pair of morphisms
-\begin{equation}\label{eq:comp_chain0}
-\xymatrix{
-(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
-}
-\end{equation}
-is given by the morphism of $C_l$-modules
-\begin{equation}\label{eq:comp_chain1}
-\xymatrix@C+1pc{
-S_{l, n} \otimes_{C_n} X \ar[r]^-{\cong} & (S_{l,m} \otimes_{C_m} S_{m,n}) \otimes_{C_n} X \ar[d]^-{\cong}\\
-& S_{l,m} \otimes_{A_m} ( S_{m,n} \otimes_{C_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{C_m} Y \ar[r]^-{\beta} & Z\,.
-}
-\end{equation}
-There is a canonical functor $p: \cat{T}^\bullet \lto \mathbb{N}$ defined by $p(X,n) = n$, which defines a cofibered category over $\mathbb{N}$ by the definition of the Grothendieck construction.
-This definition has the benefit of being derived from a general construction, but there is an alternative description of morphisms which is less cumbersome:
-
-\begin{definition} Let $\cat{T}^{\star}$ be the category with the same objects as $\cat{T}^\bullet$ and
-\begin{align*}
-\cat{T}^{\star}( (X,n), (Y,m) ) &= \Big\{ \alpha \in \cat{T}(X,Y) \l \alpha \gamma_i = 0 \text{ for } 1 \le i \le n \text{ and }\\
-&\qquad \qquad\qquad \qquad \;\; \gamma_i^\dagger \alpha = 0 \text{ for } 1 \le i \le m \Big\}\,.
-\end{align*}
-Composition is as in $\cat{T}$, but the identity on $(X,n)$ in $\cat{T}^\star$ is the morphism
-\[
-1^*_{(X,n)} = e_n
-\]
-where $e_n$ is the action on $X$ of the canonical idempotent from Definition \ref{defn:idempotent_e}.
-\end{definition}
-
-\begin{lemma}\label{lemma:equivcliffordthick} $\cat{T}^{\star}$ is a category and there is an equivalence of categories
-\[
-\Theta: \cat{T}^\bullet \lto \cat{T}^{\star}
-\]
-\end{lemma}
-\begin{proof}
-To prove that $\cat{T}^{\star}$ is a category it only needs to be checked that $1^*_{(X,n)}$ really acts as an identity. Let $\alpha: X \lto Y$ be a morphism in $\cat{T}^{\star}$ and consider
-\begin{align*}
-\alpha e_n &= \alpha \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1\\
-&= \alpha \left( \gamma_1^\dagger \cdots \gamma_{n-1}^\dagger \gamma_{n-1} \cdots \gamma_1 - \gamma_1^\dagger \cdots \gamma_n \gamma_n^\dagger \cdots \gamma_1 \right)\\
-&= \alpha \gamma_1^\dagger \cdots \gamma_{n-1}^\dagger \gamma_{n-1} \cdots \gamma_1
-\end{align*}
-since in the second summand within the brackets, there is nothing to stop $\gamma_n$ from commuting to the left and annihilating with $\alpha$.
-Proceeding inductively, we see that $\alpha e_n = \alpha$.
-The proof that $e_n \alpha = \alpha$ is similar.
-
-The functor $\Theta$ is defined to be the identity on objects, and given $\beta: (X,n) \lto (Y,m)$ in $\cat{T}^{\bullet}$ which is a morphism $\beta: S_{m,n} \otimes_{C_n} X \lto Y$ in $\cat{T}$ we define
-\begin{gather*}
-\Theta(\beta): X \lto Y\,,\\
-\Theta(\beta)( x ) = \beta( \iota_{m,n} \otimes x )
-\end{gather*}
-where $\iota_{m,n}$ is as in Definition \ref{defn:idempotent_gen}.
-We relegate the proof that this functor gives a bijection on morphism sets to Lemma \ref{lemma:morphisms_two_forms}.
-Functoriality is easily checked, and $\Theta(1_X) = e_n$ since by definition $\iota_{n,n} = e_n$.
-\end{proof}
-
-Every $C_n$-module $X$ in $\cat{T}$ is of the form $S_n \otimes_k V$ for some object $V$. It will be important later to know exactly how to extract the object $V$ from $X$ by splitting an idempotent.
-
-\begin{lemma}\label{lemma:whackamole} Let $X$ be a $C_n$-module in $\cat{T}$. The idempotent $e_n: X \lto X$ splits, say 
-\[
-\xymatrix@C+2pc{
-X \ar@<1ex>[r]^-{f_0} & V \ar@<1ex>[l]^-{g_0}
-}
-\]
-with $f_0 g_0 = 1_V$ and $g_0 f_0 = e_n$ and in $\cat{T}^\bullet$ there are mutually inverse isomorphisms
-\[
-\xymatrix@C+2pc{
-(X, n) \ar@<1ex>[r]^-{f} & (V,0) \ar@<1ex>[l]^-{g}\,.
-}
-\]
-induced by $f_0,g_0$. In particular
-\be
-S_n^* \otimes_{C_n} X \cong V\,, \qquad S_n \otimes_k V \cong X\,.
-\ee
-\end{lemma}
-\begin{proof}
-The map $f_0$ is a morphism $(X,n) \lto (V,0)$ in $\cat{T}^{\star}$ since
-\[
-f_0 \gamma_i = f_0 e_n \gamma_i = f_0 \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1 \gamma_i = 0\,.
-\]
-Similarly $g_0$ defines a morphism $(V,0) \lto (X,n)$.
-Let $f,g$ be the morphisms in $\cat{T}^\bullet$ corresponding to $f_0,g_0$ under the equivalence of Lemma \ref{lemma:equivcliffordthick}.
-To prove that $fg = 1_{(X,n)}$ and $gf = 1_{(V,0)}$ in $\cat{T}^{\bullet}$ it suffices to prove that $f_0 g_0 = 1^*_{(X,n)} = e_n$ and $g_0 f_0 = 1^*_{(V,0)}$ in $\cat{T}^{\star}$.
-But this is true by definition.
-\end{proof}
-
-\begin{lemma}\label{lemma:embedcliffordthick} $\cat{T}^\bullet$ is a supercategory and the functor $\iota: \cat{T} \lto \cat{T}^\bullet$ defined by $\iota(X) = (X,0)$ is an equivalence of supercategories.
-\end{lemma}
-\begin{proof}
-The supercategory structure is given by the functor $\Psi: \cat{T}^\bullet \lto \cat{T}^\bullet$ where $\Psi(X,n) = ( \Psi X, n )$ and $\Psi X$ has the $C_n$-action given by Definition \ref{defn:psimodule}.
-The functor $\iota$ is fully faithful and it follows from Lemma \ref{lemma:whackamole} that it is essentially surjective.
-\end{proof}
-
-%\begin{remark}\label{remark:tensor_and_idempotent} It may seem odd to labour to construct a category $\cat{C}^\bullet$ equivalent to $\cat{C}$.
-The point is that while $(X,n)$ and $(\widetilde{X}, 0)$ are isomorphic in $\cat{C}^\bullet$, they still represent quantitatively different states of knowledge.
-If $\widetilde{X}$ is known then $X$ may be easily constructed by taking direct sums, but if $X$ is known then forming the tensor product $\widetilde{X}$ is equivalent to splitting the idempotent $e_n: X \lto X$ and this requires work.
-% If $X$ is an $A_n$-module in $\cat{C}$, then the defining property of $\widetilde{X} = S_n^* \otimes_{A_n} X$ is that there is a morphism $\eta: X \lto \widetilde{X}$ satisfying $\eta \circ a_i = 0$ for all $1 \le i \le n$ and which is universal with this property.
-That is, given any morphism $\delta:X  \lto Y$ with this property there is a unique morphism $\kappa: \widetilde{X} \lto Y$ such that $\kappa \circ \eta = \delta$.
-A morphism $\delta: X \lto Y$ satisfies $\delta \circ a_i = 0$ for $1 \le i \le n$ if and only if $\delta \circ ( 1 - e_n ) = 0$.
-
-%For each $n$ the fiber of the functor $p: \cat{C}^\bullet \lto \mathbb{N}$ over $n$ is $\cat{C}_{A_n}$. We may depict the cofibered category $p$ as follows:
-%\begin{equation}\label{eq:cofibered_diagram}
-%\xymatrix@C+3pc@R+1pc{
-%\cat{C} \ar@{.}[d] \ar@<1ex>[rrr]^-{E} & & & \cat{C}_{A_n} \ar@{.}[d] \ar@<1ex>[lll]^-{F}\\
-%0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & n \ar@{.>}@<0.8ex>[l]
-%}\,.
-%\end{equation}
-%The transport between the fibers is given by the equivalences
-%\[
-%E(-) = S_{n} \otimes_k (-), \qquad F(-) = S^*_{n} \otimes_{A_n} (-)\,.
-%\]
-%While these functors are adjoint, and therefore uniquely determine one another, we have explained that there is a fundamental asymmetry between them from the point of view of computation: knowledge of an object of $\cat{C}^\bullet$ over $n$ represents a state of higher uncertainty than knowledge of an object over $m < n$, given that in the end both objects ``only'' contain the information of the corresponding object $\widetilde{X}$ over zero, but more work is necessary to extract this information from an object of $\cat{C}_{A_n}$ than from an object of $\cat{C}_{A_m}$.
-%\end{remark}
-
-%\begin{remark}\label{remark:tensor_in_steps} Given $(X,n) \in \cat{T}^\bullet$, one way to compute the tensor product
-%\[
-%S_{n+1,n} \otimes_{A_n} X = (S_{n+1} \otimes_k S_n^*) \otimes_{A_n} X \cong S_{n+1} \otimes_k ( S_n^* \otimes_{A_n} X )
-%\]
-%is to compute $S_n^* \otimes_{A_n} X$ and then take direct sums. Alternatively,
-%\begin{align*}
-%S_{n+1,n} \otimes_{A_n} X &= S_{n+1} \otimes_k S_n^* \otimes_{A_n} X\\
-%&\cong S_1 \otimes_k S_n \otimes_k S_n^* \otimes_{A_n} X \\
-%&\cong S_1 \otimes_k A_n \otimes_{A_n} X \\
-%&\cong S_1 \otimes_k X\,.
-%\end{align*}
-%That is, if we equip $S_1 \otimes_k X = X \oplus \Psi X$ with an $A_{n+1} \cong A_1 \otimes A_n$ action by making $A_n$ act on $X$ and $A_1$ act on $S_1$, this computes the tensor product.
-In a similar way, $S_{n-1,n} \otimes_{A_n} X$ is computed by splitting the idempotent $a_1^\dagger a_1$ on $X$, so that the functor $F$ of \eqref{eq:cofibered_diagram} may be computed in $n$ steps by splitting $a_1^\dagger a_1$, then $a_2^\dagger a_2$, and so on.
-%\end{remark}
-%TODO note: $S_{m,n} \otimes_{A_n}$ is an equivalence so all fibers are isomorphic to $\cat{C}$.
-
-\section{The superbicategory $\cat{L}$}\label{section:lg_cut_system}
-
-%In this section we introduce the cut system $\cat{L}$, beginning with a sketch of the major pieces and then proceeding to the technical details.
-The objects of the cut system are the same as the objects of the bicategory $\LG$, that is, pairs $(x, W)$ consisting of a set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x]$.
-Such an object is often written as $W$ or $W(x)$.
-The integer $\pi(x,W) = n$ is the number of variables.
-
-In this section we define a bicategory without units which we call the \textsl{cut system} model of $\LG$.
-Later in Section \ref{??} we will prove that this bicategory is equivalent to $\LG$, although this will not be apparent at first.
-Given objects $(x,W)$ and $(y,V)$ of $\LG$ we define
-\be\label{eq:defnluv}
-\cat{L}(W,V) = \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,
-\ee
-where $(-)^\omega$ denotes the idempotent completion and $(-)^{\bullet}$ the Clifford thickening. The first aim of this section is to define, for any object $(z,U)$ of $\LG$, a functor
-\begin{gather*}
-\cat{L}(V,U) \otimes_k \cat{L}(W,V) \lto \cat{L}(W, U)\,\\
-(Y,X) \mapsto Y \l X
-\end{gather*}
-which we call the \textsl{cut functor}. The cut operation is defined on matrix factorisations $X$ of $V - W$ and $Y$ of $U - V$ as follows, assuming $y = (y_1,\ldots,y_m)$ and writing
-\be\label{eq:defnjacobian}
-J_V = k[y] / ( \partial_{y_1} V, \ldots, \partial_{y_m} V )\,.
-\ee
-
-\begin{lemma} The $\nZ_2$-graded $k[x,z]$-module
-\[
-Y \l X = Y \otimes_{k[y]} J_V \otimes_{k[y]} X
-\]
-with the differential $d_Y \otimes 1 + 1 \otimes d_X$ is a finite rank matrix factorisation of $U - W$.
-\end{lemma}
-\begin{proof}
-Since $V$ is a potential $J_V$ is a finite rank free $k$-module, and it follows that $Y \l X$ is a finite rank free $k[x,z]$-module.
-
-\end{proof}
-%If $\{ e_i \}_{i \in I}$ and $\{ f_j \}_{j \in J}$ are homogeneous bases of $Y, X$ over $k[z,y]$ and $k[y,x]$ respectively, and if $\{ v_k \}_{k \in K}$ is a $k$-basis for $J_V$ (which we give degree zero) then $\{ e_i \otimes v_k \otimes f_j \}_{i,j,k}$ is a $k[x,z]$-basis for $Y \l X$.
-
-\begin{definition} Given morphisms of matrix factorisations $\phi: X \lto X'$ and $\psi: Y \lto Y'$ we define the morphism of matrix factorisations
-\[
-\psi \l \phi: Y \l X \lto Y' \l X'
-\]
-to be induced on the quotient by $\psi \otimes \phi: Y \otimes X \lto Y' \otimes X'$. This is clearly functorial in the sense that for morphisms $\phi': X' \lto X''$ and $\psi': Y' \lto Y''$ we have
-\begin{align}
-( \psi' \l \phi' ) \circ ( \psi \l \phi ) = ( \psi' \psi ) \l ( \phi' \phi )\,,
-\end{align}
-and $1_Y \l 1_X = 1_{Y \l X}$.
-\end{definition}
-
-\begin{remark}
-As an explicit matrix of polynomials in $k[x,y]$ the differential on $Y \l X$ can be obtained from the differentials on $X$ and $Y$ (which involve $k[z,x]$ and $k[y,z]$ respectively) by replacing occurrences of $z$ by a certain square matrix of scalars; see the proof of Theorem \ref{theorem:l_cut_system} for more details.
-\end{remark}
-
-The next step is to equip $Y \l X$ with a Clifford action, which will be defined using the partial derivatives $\partial_{y_i}(d_X)$ and Atiyah classes.
-The Atiyah classes are defined by first taking the technical step of extending scalars
-\begin{equation}\label{eq:completed_tensor_product}
-Y \,\check{\otimes}\, X = Y \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} X
-\end{equation}
-and putting a connection on this module.
-We write $t = (t_1,\ldots,t_m)$ for the quasi-regular sequence of partial derivatives $t_i = \partial_{y_i} V$ and recall that there is by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
-\begin{equation}\label{eq:connection_nabla}
-\nabla: k\llbracket y \rrbracket \lto k\llbracket y \rrbracket \otimes_{k[t]} \Omega^1_{k[t]/k}
-\end{equation}
-the components of which are $k$-linear operators $\partial_{t_i}: k\llbracket y \rrbracket \lto k\llbracket y \rrbracket$.
-A simple example of such a connection is given in Section \ref{example:computing_homs}.
-Using a chosen homogeneous basis $\{ e_i \otimes f_j \}_{i,j}$ for $Y \otimes X$ we may extend the operators $\partial_{t_i}$ extend to $k[x,z]$-linear operators
-\begin{gather*}
-\partial_{t_i}: Y \, \check{\otimes}\, X \lto Y \, \check{\otimes}\, X\\
-e_i \otimes h(y) \otimes f_j \mapsto e_i \otimes \partial_{t_i}( h(y) ) \otimes f_j\,.
-\end{gather*}
-
-\begin{lemma} The operator $[ d_{Y \otimes X}, \partial_{t_i} ]$ is $k[t]$-linear and therefore passes to a $k[x,z]$-linear operator on the quotient $Y \l X = \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
-\end{lemma}
-
-\begin{definition} The $i$th Atiyah class is this odd $k[x,z]$-linear operator
-\[
-\At^{Y,X}_i = [d_{Y \otimes X}, \partial_{t_i}]: Y \l X \lto Y \l X \,.
-\]
-Usually we just write this operator as $\At_i$ where it will not cause confusion.
-\end{definition}
-
-This operator is the $i$th Atiyah class of $Y \,\check{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}.
-A reference for Atiyah classes is \cite{buchweitz_flenner}, but we will prove the necessary properties here for the reader's convenience.
-
-\begin{lemma}\label{lemma:atiyahclosed} The operator $\At_i$ on $Y \l X$ is closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are homotopies
-\be\label{eq:atiyahclosednatural}
-\At^{Y',X'}_i \circ \,( \psi \l \phi ) \simeq ( \psi \l \phi ) \circ \At^{Y,X}_i\,.
-\ee
-That is, the Atiyah classes are \emph{natural}.
-\end{lemma}
-\begin{proof}
-The Atiyah class is closed since
-\[
-[d, \At_i] = [d, [d, \partial_{t_i}]] = 0\,.
-\]
-If $\kappa: Y \otimes X \lto Y' \otimes X'$ is any $k[x,y,z]$-linear even closed operator, 
-\[
-[ \kappa, [ d, \partial_{t_i} ] ] + [ \partial_{t_i}, [\kappa, d]] + [ d, [ \partial_{t_i}, \kappa] ] = 0
-\]
-from which we deduce that $[\partial_{t_i}, \kappa]$ is a homotopy establishing \eqref{eq:atiyahclosednatural}.
-\end{proof}
-
-The other ingredient in defining the Clifford action are the partial derivatives $\partial_{y_i}(d_X)$, as discussed in Section \ref{section:partial}.
-On $Y \otimes X$ we have the odd operator $\partial_{y_i}(d_X) = 1 \otimes \partial_{y_i}(d_X)$ which is a homotopy for the action of $\partial_{y_i}(V - W) = \partial_{y_i}(V)$.
-Hence when we pass to the quotient, $\partial_{y_i}(d_X)$ is a closed odd operator on $Y \l X$.
-
-\begin{definition}\label{defn:cliffordaction_cut} On $Y \l X$ we define odd $k[x,z]$-linear closed operators
-\begin{equation}\label{eq:intro_clifford_act1}
-\gamma_i^\dagger = \At_i\,, \qquad \gamma_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
-\end{equation}
-\end{definition}
-
-\begin{theorem} Given matrix factorisations $Y,X$ as above, the data
-\be
-Y \l X = \left( Y \otimes_{k[y]} J_V \otimes_{k[y]} X, \{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m \right)
-\ee
-defines a representation of $C_m$ in the homotopy category of matrix factorisations, that is, the $\gamma_i, \gamma_i^\dagger$ satisfy the Clifford relations \eqref{eq:clifford_relations}
-up to homotopy.
-\end{theorem}
-\begin{proof}
-This will follow from the considerations of Section \ref{??} but we feel it is worthwhile to give a direct proof, both to demonstrate how straightforward it is and in order to have written down explicit homotopies for the various relations.
-
-By the graded Jacobi identity
-\begin{align*}
-[\At_i, \At_j] &= [\At_i, [d, \partial_{t_j}]]\\
-&= - [\partial_{t_j}, [\At_i, d]] - [d, [\partial_{t_j}, \At_i]]\\
-&= [d, -[\partial_{t_j}, \At_i]]\,.
-\end{align*}
-Hence $[\gamma_i^\dagger, \gamma_j^\dagger] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
-\begin{align*}
-[\partial_{y_i}(d_X), \At_j] &= [\partial_{y_i}(d_X), [d, \partial_{t_j}]]\\
-&= -[\partial_{t_j}, [\partial_{y_i}(d_X), d]] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
-&= -[\partial_{t_j}, t_i] + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\\
-&= -\delta_{ij} + [d, [\partial_{t_j}, \partial_{y_i}(d_X)]]\,.
-\end{align*}
-Again we set $g_{ij} = [\partial_{t_j}, \partial_{y_i}(d_X)]$ for later use. We compute that
-\begin{align*}
-[ \gamma_i, \gamma^\dagger_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
-&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [ \At_q, \At_j]\\
-&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [d, h_{qj}]\\
-&= \delta_{ij} + \big[d, -g_{ij} - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) h_{qj}\big]\,.
-\end{align*}
-Finally, using Lemma \ref{lemma:commutator_of_lambdas}
-\begin{align*}
-[ \gamma_i, \gamma_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
-&= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
-&\quad + \frac{1}{2}\sum_q \partial_{y_q y_i}(V) \big[ \At_q, \partial_{y_j}(d_X) \big]\\
-&\quad + \frac{1}{4}\sum_{p,q} \partial_{y_py_i}(V) \partial_{y_qy_j}(V) \big[ \At_p, \At_q \big]\\
-&= \partial_{y_iy_j}(V) + [d, - \partial_{y_jy_i}(d_X)]\\
-&\qquad + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \left( -\delta_{iq} + [d, [ \partial_{t_q}, \partial_{y_i}(d_X)]] \right)\\
-&\qquad + \frac{1}{2} \sum_q \partial_{y_qy_i}(V) \left( -\delta_{jq} + [d, [\partial_{t_q}, \partial_{y_j}(d_X)]] \right)\\
-&\qquad + \frac{1}{4}\sum_{p,q} \partial_{y_py_i}(V) \partial_{y_qy_j}(V) [d, -[\partial_{t_q}, \At_p]]\\
-&= [d, c_{ij}]
-\end{align*}
-where
-\begin{align*}
-c_{ij} &= - \partial_{y_jy_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_qy_j}(V)  [\partial_{t_q}, \partial_{y_i}(d_X)]\\
-&\qquad + \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [\partial_{t_q}, \partial_{y_j}(d_X)]\\
-&\qquad - \frac{1}{4} \sum_{p,q}  \partial_{y_py_i}(V) \partial_{y_qy_j}(V)  [\partial_{t_q}, \At_p]\,.
-\end{align*}
-\end{proof}
-
-\begin{lemma}\label{prop:morphismsarecliffordreps} Given morphisms $\phi: X \lto X', \psi: Y \lto Y'$, the morphism of matrix factorisations $\psi \l \phi$ is a morphism of $C_m$-representations in the homotopy category.
-\end{lemma}
-\begin{proof}
-This follows easily from the fact that Atiyah classes are natural (Lemma \ref{lemma:atiyahclosed}) and the homotopies $\partial_{y_i}(d_X)$ are central (Lemma \ref{lemma:naturalityoflambda}).
-\end{proof}
-
-\begin{proposition}\label{prop:cutisafunctor} The cut operation defines a functor
-\be\label{eq:cutisafunctor}
-\cat{L}(V,U) \otimes_k \cat{L}(W,V) \lto \cat{L}(W, U)
-\ee
-\end{proposition}
-\begin{proof}
-What we have done so far in this section defines a functor
-\[
-\hmf( k[y,z], U - V ) \otimes \hmf( k[x,y], V - W ) \lto \hmf( k[x,z], U - W )^{\omega \bullet}
-\]
-and since the latter category is idempotent complete, this lifts to a functor
-\[
-\hmf( k[y,z], U - V )^{\omega} \otimes \hmf( k[x,y], V - W )^{\omega} \lto \hmf( k[x,z], U - W )^{\omega \bullet}\,.
-\]
-Explicitly, this functor is given for $(Y,e_Y) \in \cat{L}(V,U)$ and $(X,e_X) \in \cat{L}(W,V)$ by
-\[
-(Y, e_Y) \l (X, e_X) = (Y \l X, e_Y \l e_X)\,.
-\]
-Now suppose we have representations $( Y, \{ \rho_j, \rho_j^\dagger \}_{j=1}^r )$ of $C_r$ in $\cat{L}(V,U)$ and $( X, \{ \tau_l, \tau^\dagger_l \}_{l=1}^s )$ of $C_s$ in $\cat{L}(W,V)$.
-Here $Y,X$ may come equipped with idempotents but these are easily handled so we ignore them in what follows.
-Since the cut operation is functorial, we have representations of $C_r$ and $C_s$ on $Y \l X$ given by
-\[
-\big\{ \rho_j \l 1_X, \rho_j^\dagger \l 1_X \big\}_{j=1}^r\,, \qquad \big\{ 1_Y \l \tau_l, 1_Y \l \tau_l^\dagger \big\}_{l=1}^s\,.
-\]
-The operators from the action of $C_r$ anticommute with the operators from the action of $C_s$ because they act on different components of a tensor product.
-Moreover, both actions anticommute with the new $C_m$ action $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ coming from the cut, by Lemma \ref{prop:morphismsarecliffordreps}.
-Thus $Y \l X$ is equipped with the structure of a $C_r \otimes C_m \otimes C_s \cong C_{r+m+s}$-representation.
-\end{proof}
-
-In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.
-
-\begin{definition} A \textsl{(super)bicategory without units} has all the data and satisfies all the conditions of a (super)bicategory, with the exception of the existence of unit $1$-morphisms, unitors, and their coherence diagram.
-\end{definition}
-
-\begin{definition} The superbicategory without units $\cat{L}$ has
-\begin{itemize}
-\item \textbf{Objects:} same as $\LG$, that is, potentials $(k[x], W)$.
-\item \textbf{$1$- and $2$-morphisms:} defined by \eqref{eq:defnluv}.
-\item \textbf{Composition:} defined by the cut operation \eqref{eq:cutisafunctor}.
-\item \textbf{Associators:} given a triple of composable $1$-morphisms
-\begin{equation}\label{eq:composable_triple}
-\xymatrix@C+2pc{
-(q, Q) & (y, U) \ar[l]_-{Z} & (z,V) \ar[l]_-{Y} & (x,W) \ar[l]_-{X}
-}\,.
-\end{equation}
-with $V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ the isomorphism
-\begin{gather*}
-\alpha: Z \l (Y \l X) \lto (Z \l Y) \l X,\\
-z \otimes (y \otimes x) \mapsto (z \otimes y) \otimes x
-\end{gather*}
-is $C_m \otimes C_p$-linear (see Lemma \ref{lemma:associator} below) and is the associator for $\cat{L}$.
-\end{itemize}
-\end{definition}
-
-\begin{lemma}\label{lemma:associator} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $C_m \otimes C_p$-linear.
-\end{lemma}
-\begin{proof}
-We prove the $C_p$-linearity of $\alpha$, the proof for $C_m$ is similar.
-The algebra $C_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$.
-The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of
-\[
-M = Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
-\]
-relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
-Specifically, the generator $C_i^{\dagger}$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
-But this operator can be identified with an Atiyah class of the linear factorisation
-\begin{equation}\label{eq:assoc_proof_M}
-Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X \big)
-\end{equation}
-relative to the ring morphism
-\begin{equation}\label{eq:assoc_proof_M2}
-k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
-\end{equation}
-By the same argument the action of $C_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} Y \big) \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}.
-It is therefore clear that the associator $\alpha$ identifies these two actions.
-\end{proof}
-
-\begin{theorem} Thus defined $\cat{L}$ is a superbicategory without units.
-\end{theorem}
-\begin{proof}
-The only thing to check is the coherence of the associator, which is trivial.
-\end{proof}
-
-\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}.
-To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$.
-The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is
-\[
-e_m' = a_1 \cdots a_m a_m^\dagger \cdots a_1^\dagger\,.
-\]
-Using \eqref{eq:intro_clifford_act1} and \eqref{eq:intro_clifford_act2} we can write down the explicit form of this idempotent acting on $Y \l X$.
-On this object each of the $a_i$'s acts simply as $- \lambda_i$ because all of the $a_j^\dagger$'s appear to the right.
-Hence on $Y \l X$
-\begin{align*}
-e_m' &= (-1)^{\binom{m}{2}} a_1 \cdots a_m a_1^\dagger \cdots a_m^\dagger \\
-&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
-\end{align*}
-which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.
-
-In \emph{ibid.} we constructed finite models of convolutions $Y \circ X$ one pair $(Y,X)$ at time.
-To make this assignment of finite models coherently for all $1$-morphisms in $\LG$ simultaneously it is natural to identify the Clifford actions which underlie the idempotents, as we do here.
-\end{remark}
-
-\begin{remark} There is a question of whether or not the $A_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
-But Atiyah classes are independent, up to homotopy, of the choice of connection, and it is easy to see that the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis.
-Hence the action is indeed canonical.
-\end{remark}
-
-\begin{remark}\label{remark:inflation} Let $V \in k[z_1,\ldots,z_m]$ be a potential and choose a $k$-basis for $J_V$.
-Then multiplication by $z_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[z_i]$ over $k$.
-
-Given $X$ and $Y$ the cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $z_i$ by the scalar matrix $[z_i]$.
-This ``inflation'' produces a matrix of polynomials over $k[x,y]$.
-\end{remark}
-
-\section{The equivalence of $\cat{L}$ and $\LG$}
-
-We prove that the cut functor defined in Section \ref{section:lg_cut_system} models composition in $\LG$ by providing an equivalence of this bicategory with $\cat{L}$.
-This is done by presenting the cut $Y \l X$ with its Clifford action as the solution of the problem of finding a finite model for the matrix factorisation $Y \otimes X$ over $k[x,z]$.
-
-As was mentioned in Section \ref{section:superbicatLG}, $Y \otimes X$ is a matrix factorisation of infinite rank over $k[x,z]$.
-The obvious notion of a ``finite model'' would be a finite rank matrix factorisation to which $Y \otimes X$ is homotopy equivalent, but providing such a finite model generically seems impossible.
-We propose a different notion of finite model based on Clifford representations, and solve the problem in this setting.
-The solution we give here builds on earlier progress on this problem with Dyckerhoff \cite{dm1102.2957}.
-
-\begin{setup}\label{setupforfusion} The situation is as follows:
-\begin{itemize}
-\item $(x,W), (y, V), (z,U)$ are objects of $\LG$ with $k[y] = k[y_1,\ldots,y_m]$.
-\item $Y$ is a finite rank matrix factorisation of $U - V$ over $k[y,z]$.
-\item $X$ is a finite rank matrix factorisation of $V - W$ over $k[x,y]$.
-\end{itemize}
-\end{setup}
-
-The strategy is to consider the direct sum of (shifted) copies
-\begin{equation}\label{eq:larger_object}
-V \otimes_k ( Y \otimes X ) = (Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
-\end{equation}
-where $V$ is the exterior algebra
-\[
-V = \bigwedge( k[1]^{\oplus m} )\,.
-\]
-We find a finite model of this larger object, and in addition record a method of extracting the subobject $Y \otimes X$.
-Some necessary background is presented in Section \ref{section:homolog_fix} and Section \ref{section:cliffordactkos}, and finally the full construction is presented in Section \ref{section:theequivalence}.
-The overall strategy is:
-
-\begin{strat}\label{strategy} We show there is a differential $d_K$ ($K$ stands for Koszul) such that
-\begin{itemize}
-\item[1)] The complex $( V \otimes_k ( Y \otimes X ), d_K )$ has a finite model: there is a homotopy equivalence
-\be
-(Y \l X, 0) \cong \big( V \otimes_k ( Y \otimes X ), d_K \big)
-\ee
- over $k[x,z]$ where $Y \l X$ is the graded module from Section \ref{section:lg_cut_system}.
-\item[2)] The perturbation lemma (Section \ref{section:homolog_fix}) promotes this to a homotopy equivalence
-\be\label{eq:woofeif}
-(Y \l X, d_{Y \otimes X}) \cong \big( V \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big)
-\ee
-by mixing in the differential $d_{Y \otimes X}$ on both sides.
-\item[3)] Using Section \ref{section:cliffordactkos} we show there is a homotopy equivalence
-\be\label{eq:woofeif2}
-\big( V \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big) \cong \big( V \otimes_k ( Y \otimes X ), d_{Y \otimes X}\big)\,.
-\ee
-\item[4)] Combining \eqref{eq:woofeif} and \eqref{eq:woofeif2} we have the desired finite model
-\be\label{eq:iso_of_clifford_modelfinite}
-(Y \l X, d_{Y \otimes X}) \cong ( V \otimes_k ( Y \otimes X ), d_{Y \otimes X})\,.
-\ee
-There is a canonical action of the Clifford algebra $C_m$ on $V$ and thus on the right hand side, which ``remembers'' how to extract $Y \otimes X$ from this larger object.
-Transferring this action yields the operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ on $Y \l X$ from Section \ref{section:lg_cut_system}.
-\end{itemize}
-\end{strat}
-
-In conclusion, there is an isomorphism of Clifford representations \eqref{eq:iso_of_clifford_modelfinite} in the homotopy category of finite rank matrix factorisations of $U - W$ over $k[x,z]$, and this is our solution to the problem of finding a finite model of $Y \otimes X$.
-Once we have established all of this, proving that $\cat{L}$ and $\LG$ are equivalent bicategories will be immediate.
-
-\subsection{Homological perturbation and fixed points}\label{section:homolog_fix}
-
-A fundamental role in this paper is played by the homological perturbation lemma.
-While this result is usually stated for complexes the standard results generalise immediately to linear factorisations, and in this section we collect these standard results.
-But we begin by recalling the motivating problem for which the perturbation lemma is the solution.
-
-Let $Q$ be a complex of infinite rank free abelian groups.
-Suppose that the cohomology is finitely generated, so that $Q$ contains in some sense only a ``finite'' amount of information.
-One can ask for a description which makes this finiteness manifest: the obvious answer is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.
-
-A \emph{deformation retract} of complexes is a pair of morphisms
-\begin{equation}\label{eq:example_defo_retract}
-\xymatrix@C+2pc{
-C \ar@<-1ex>[r]_\nabla & Q, \ar@<-1ex>[l]_f
-} \quad \phi
-\end{equation}
-and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $f \nabla = 1_C, \nabla f = 1_Q - [d_Q, \phi]$ so that $f, \nabla$ are mutually inverse homotopy equivalences.
-A deformation retract is \emph{strong} if it satisfies some additional conditions, listed below.
-The point is that if $C$ is finitely generated, then \eqref{eq:example_defo_retract} gives the desired finite representative in the homotopy equivalence class of $Q$.
-
-\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-modules
-\[
-\xymatrix@C+2pc@R+1pc{
-0 \ar[d] \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar[d]^-{x}\\
-k \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar@/_3pc/@{.>}[u]_-{\phi}
-}
-\]
-in which the first column is the complex $C$ which has $k$ concentrated in degree zero, and the second column $Q$ is the Koszul complex on $x$.
-The map $f: k[x] \lto k$ sends every polynomial to its constant term, while $\nabla: k \lto k[x]$ is the inclusion of the constants.
-The operator $\phi$ is defined by $\phi( x^n ) = x^{n-1}$ and $\phi(1) = 0$.
-Together these maps are a deformation retract giving $k$ as the ``finite model'' of $Q$.
-\end{example}
-
-Suppose now that a deformation retract computing a finite representative for $Q$ cannot be found immediately, but that we know how to decompose the differential as $d_Q = d + \tau$ in such a way that there is a finite representative for the complex $(Q,d)$.
-The perturbation lemma allows us, with some conditions, to ``mix in'' the operator $\tau$ to obtain a finite model for the original complex $Q$.
-\\
-
-Let $R$ be a commutative ring and $W \in R$.
-Everything we say applies, in the case where $W = 0$, to both $\mathbb{Z}_2$-graded and $\mathbb{Z}$-graded complexes.
-For our purposes the reformulation of the perturbation lemma in terms of fixed points by Barnes and Lambe is more natural, so we emphasise the ``splitting homotopies'' of \cite{barneslambe}.
-
-\begin{definition} A \emph{splitting homotopy} on a linear factorisation $(A,d)$ of $W$ is a degree $-1$ operator $\phi$ on $A$ satisfying
-\begin{itemize}
-\item[(i)] $\phi^2 = 0$,
-\item[(ii)] $\phi d \phi = \phi$.
-\end{itemize}
-A \emph{morphism} $(A,d, \phi) \lto (A,d',\phi')$ of splitting homotopies is a morphism $\alpha: A \lto A'$ of linear factorisations satisfying $\phi' \alpha = \alpha \phi$.
-\end{definition}
-
-The condition (ii) says that $\phi$ is a \emph{fixed point} of the operator $F(x) = x d x$.
-
-\begin{definition} A \emph{strong deformation retract} of linear factorisations of $W$ is a pair of morphisms of linear factorisations
-\begin{equation}\label{eq:defn_sdr}
-\xymatrix@C+2pc{
-(M,d) \ar@<-1ex>[r]_\nabla & (A,d), \ar@<-1ex>[l]_f
-} \quad \phi
-\end{equation}
-together with a degree $-1$ operator $\phi: A \lto A$ satisfying
-\begin{itemize}
-\item[(i)] $f \nabla = 1_M$,
-\item[(ii)] $\nabla f = 1_A - [d, \phi]$,
-\item[(iii)] $\phi^2 = 0$,
-\item[(iv)] $\phi \nabla = 0$,
-\item[(v)] $f \phi = 0$.
-\end{itemize}
-A \emph{morphism} of strong deformation retracts is a commutative diagram
-\[
-\xymatrix@C+2pc{
-(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\nabla & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_f\\
-(M',d') \ar@<-1ex>[r]_{\nabla'} & (A',d') \ar@<-1ex>[l]_{f'}
-}
-\]
-that is, a pair of morphisms $\alpha, \beta$ such that $\beta \nabla = \nabla' \alpha$, $\alpha f = f' \beta$ and $\phi' \beta = \beta \phi$.
-\end{definition}
-
-We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}.
-Namely, a strong deformation retract in the above sense is the same as a special deformation retract in the sense of \emph{ibid.} with $h = - \phi$.
-
-\begin{lemma}\label{lemma:equivocate} There is an equivalence between the category of splitting homotopies $\cat{C}_1$ and the category of  strong deformation retracts $\cat{C}_2$.
-\end{lemma}
-\begin{proof}
-We briefly recall the construction from \cite[p.883]{barneslambe}, which is not stated in terms of categories but is obviously functorial.
-Given a strong deformation retract \eqref{eq:defn_sdr} the data $(A, \phi)$ is a splitting homotopy.
-In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $\pi = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(\phi)$ with the associated projection $f$ and inclusion $\nabla$.
-Then this is a strong deformation retract, together with the original $\phi$.
-\end{proof}
-
-%Taking splitting homotopies as the primary object has the advantage of hiding some of the incidental complexity in the perturbation lemma.
-Here is the problem that the formalism is designed to solve: suppose $(A,d)$ is a linear factorisation of $W$ and that $\tau$ is a degree $+1$ operator on $A$ such that $(A, d + \tau)$ is a linear factorisation of $V$ (possibly different to $W$).
-This $\tau$ is called the \emph{perturbation}.
-
-\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(\pi) \cong \im(\pi')$ as graded $R$-modules, where $\pi = 1_A - [d, \phi]$ and $\pi' = 1_A - [d + \tau, \phi']$.
-\end{definition}
-
-That is, with $\xi = d + \tau$ the problem is to find a fixed point of the operator
-\[
-F(x) = x \xi x
-\]
-among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(\pi)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
-\[
-\phi_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \phi = \phi - \phi \tau \phi + \phi \tau \phi \tau \phi - \cdots
-\]
-is a solution of this fixed point problem:
-
-\begin{theorem}[Perturbation lemma]\label{theorem:pertlemma} Suppose $\phi \tau$ has finite order.
-Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi)$ and satisfies the isomorphism condition in the transference problem.
-\end{theorem}
-\begin{proof}
-The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations (see comments in blah).
-\end{proof}
-
-The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}.
-The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
-\begin{equation}\label{eq:perturbedsdr}
-\xymatrix@C+2pc{
-(M,d_\infty) \ar@<-1ex>[r]_{\nabla_\infty} & (A, \xi), \ar@<-1ex>[l]_{f_\infty}
-} \quad \phi_\infty
-\end{equation}
-where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
-\begin{align*}
-\nabla_\infty &= \nabla - \phi A \nabla,\\
-f_\infty &= f - f A \phi,\\
-d_\infty &= d + f A \nabla\,.
-\end{align*}
-As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
-\[
-\im(1 - [\xi, \phi_\infty]) \cong \im(\pi) = M
-\]
-be identified with $M$, and the induced maps are the $\nabla_\infty, f_\infty, d_\infty$ given above.
-It is also possible to give a direct proof as in \cite{crainic}.
-To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one just studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.
-
-\subsection{Clifford actions and Koszul complexes}\label{section:cliffordactkos}
-% spkos series
-
-Let $(X,d)$ be a complex of $R$-modules on which $t_1,\ldots,t_n \in R$ act null-homotopically.
-Tensoring $X$ with the Koszul complex $K(t_i)$ yields the same complex as taking the cone of $t_i \cdot 1_X = 0: X \lto X$, and therefore we have a homotopy equivalence
-\be
-K(t_i) \otimes_R X \cong \operatorname{cone}( t_i \cdot 1_X ) \cong X \oplus X[1] \cong ( k \oplus k[1] ) \otimes_k X\,.
-\ee
-Iterating this operation we obtain a homotopy equivalence with $K = K(t_1,\ldots,t_n)$,
-\be\label{eq:cliffordactkos_1}
-K \otimes_R X \cong \bigwedge( k[1]^{\oplus n} ) \otimes_k X
-\ee
-where the left hand side is a complex with differential $d_K + d$ and the right hand side has only the differential $d$. On the right hand side we have an obvious action of
-\be
-C_n = \End_k\left( \bigwedge( k[1]^{\oplus n} ) \right)
-\ee
-and the purpose of this section is to compute the corresponding action of $C_n$ via closed odd endomorphisms of the complex $K \otimes_R X$. In fact we will do this more generally:
-
-\begin{setup} Let $R$ be a $k$-algebra and write $\otimes$ for $\otimes_R$.
-Let $(X,d)$ be a linear factorisation of $W \in R$ and $t_1,\ldots,t_n$ a sequence of elements of $R$ acting null-homotopically on $X$.
-We choose odd $R$-linear operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$ for $1 \le i \le n$.
-\end{setup}
-
-\begin{remark} All equalities in this section mean equalities of linear maps. If we mean homotopy, we will explicitly write $\simeq$.
-\end{remark}
-
-We introduce formal variables $\theta_1,\ldots,\theta_n$ of odd degree and set
-\[
-V = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
-\]
-On this $\nZ$-graded $k$-module there are canonical odd $k$-linear operators $\theta_i, \theta_i^*$ defined as in Definition \ref{defn:contraction}.
-The Koszul complex $K$ of the sequence $t_1,\ldots,t_n$ is defined by
-\begin{equation}\label{defn:koszul}
-K = V \otimes_k R, \qquad d_K = \sum_{i=1}^n t_i \theta_i^*\,.
-\end{equation} 
-The tensor products $K \otimes X = (K \otimes X, d + d_K)$ and $V \otimes_k X = ( V \otimes_k X, d )$ are both linear factorisation of $W$ with isomorphic underlying graded modules.
-On this underlying graded module $K \otimes X \cong V \otimes_k X$ we have the odd $R$-linear operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$ and we introduce the following even $R$-linear operators
-\begin{align*}
-\delta &= \sum_{i=1}^n \lambda_i \theta_i^*,\\
-\exp(-\delta) &= \sum_{m \ge 0} (-1)^m \frac{1}{m!} \delta^m\,.
-\end{align*}
-Observe that $\delta$ is nilpotent so the exponential makes sense.
-
-\begin{proposition}\label{prop:equivalencekoszul} There are mutually inverse isomorphisms of linear factorisations
-\be\label{eq:equivalencekoszul}
-\xymatrix@C+5pc{ K \otimes X\; \ar@<1ex>[r]^-{ \exp(\delta) } & \;V \otimes_k X \ar@<1ex>[l]^-{ \exp(-\delta) } }
-\ee
-where the left hand side has differential $d + d_K$ and the right hand side has $d$.
-\end{proposition}
-
-We break the proof into a series of lemmas:
-
-\begin{lemma}\label{lemma:pert1} $[d, \delta^m] = m \delta^{m-1} d_K$ for $m \ge 1$.
-\end{lemma}
-\begin{proof}
-The case of $m = 1$ is clear
-\[
-[d, \delta] = \sum_i [d, \lambda_i] \theta_i^* = d_K\,.
-\]
-For $m > 1$ we use the case $m = 1$ to show that
-\[
-[ d, \delta^m ] = \sum_{i=0}^{m-1} \delta^i [d, \delta] \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i d_K \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i \delta^{m-i-1} d_K = m \delta^{m-1} d_K\,.
-\]
-\end{proof}
-
-\begin{lemma}\label{lemma:pert2} $[ d, \exp(-\delta) ] = - \exp(-\delta) d_K$ and $[ d, \exp(\delta) ] = \exp(\delta) d_K$.
-\end{lemma}
-\begin{proof}
-We prove the first identity using Lemma \ref{lemma:pert1}, the second is the same:
-\begin{align*}
-[d, \exp(-\delta)] &= \sum_{m \ge 1} \frac{(-1)^m}{m!} [ d, \delta^m ]\\
-&= \sum_{m \ge 1} \frac{(-1)^m}{m!} m \delta^{m-1} d_K\\
-&= - \sum_{m \ge 0} \frac{(-1)^m}{m!} \delta^m d_K\\
-&= - \exp(-\delta) d_K
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop:equivalencekoszul}]
-It suffices to show $\exp(-\delta)$ is a morphism of linear factorisations. But using Lemma \ref{lemma:pert2}
-\[
-(d + d_K) \exp(-\delta) - \exp(-\delta) d = [d, \exp(-\delta)] + d_K \exp(-\delta) = 0
-\]
-and similarly for the other equation.
-\end{proof}
-
-\begin{definition}\label{defn:transfer_contract} Let $\gamma$ be a homogeneous $R$-linear operator on $V \otimes_k X$.
-We define the \textsl{transfer} $\cat{T}(\gamma)$ to be the homogeneous $R$-linear operator on $K \otimes X$ induced by $\gamma$ using the equivalence \eqref{eq:equivalencekoszul}, that is,
-\be
-\cat{T}(\gamma) = \exp(-\delta) \gamma \exp(\delta)\,.
-\ee
-\end{definition}
-
-\begin{remark} We do not necessarily require that $\gamma$ be closed, but since
-\be
-[\cat{T}(\gamma), d_K + d] = \cat{T}( [\gamma, d] )
-\ee
-if $\gamma$ is a closed operator then so is $\cat{T}(\gamma)$. 
-\end{remark}
-
-Of particular interest are the transfers of the generators $\theta_i, \theta_i^*$ of the Clifford action. The transfer of the contraction operator $\theta_i^*$ is easy:
-
-\begin{lemma} $\cat{T}(\theta_i^*) = \theta_i^*$.
-\end{lemma}
-\begin{proof}
-Since $\theta_i^*$ commutes with $\delta$.
-\end{proof}
-
-However the calculation of $\cat{T}(\theta_i)$ is much more involved.
-To compute $\cat{T}(\gamma)$ the strategy is to try and commute $\gamma$ past $\exp(-\delta)$ and see what happens.
-To this end we must first compute $[\gamma, \delta^m]$.
-We begin the calculations with some general statements about graded commutators.
-
-To this end let $A$ be a $\nZ$-graded $\nQ$-algebra and $a,b,c$ homogeneous elements.
-
-\begin{lemma} We have
-\begin{align}
-[ab,c] &= a[b,c] + (-1)^{|b||c|} [a,c]b\,,\\
-[a,bc] &= [a,b]c + (-1)^{|a||b|} b[a,c]\,. \label{eq:commutator_with_product}
-\end{align}
-\end{lemma}
-
-We adopt the following notation for iterated commutators
-
-\begin{definition} The iterated commutator $[a,b]^{(m)}$ is defined by $[a,b]^{(0)} = b$ and
-\[
-[a,b]^{(m+1)} = [a, [a,b]^{(m)}]\,.
-\]
-Observe that $[a,b]^{(m)}$ is a linear function of $b$, but not $a$.
-\end{definition}
-
-\begin{lemma}\label{lemma:woop3} For $m \ge 1$ we have
-\[
-[a,b^m] = \sum_{i=0}^{m-1} (-1)^{i|a||b|} b^i [a,b] b^{m-i-1}\,.
-\]
-\end{lemma}
-\begin{proof}
-Easy proof by induction using \eqref{eq:commutator_with_product}.
-\end{proof}
-
-\begin{lemma}\label{lemma:woop4} For $m \ge 1$ we have
-\be
-a^m [a, b] = \sum_{\substack{0 \le i,j \le m \\ i+j=m}} \binom{m}{i} [a,b]^{(i+1)} a^j\,.
-\ee
-\end{lemma}
-\begin{proof}
-By induction, with the case $m = 1$ being clear. Using the inductive hypothesis
-\[
-a^{m+1} [a, b] = \sum_{i+j=m} \binom{m}{i} a [a,b]^{(i+1)} a^j = \sum_{i+j=m} \binom{m}{i} \Big[ [a,b]^{(i+2)} a^j + [a,b]^{(i+1)} a^{j+1} \Big]\,.
-\]
-The powers of $a$ range from $0$ to $m+1$ and the coefficient of $a^j$ for $1 \le j \le m$ is
-\[
-\binom{m}{m-j} [a,b]^{(m-j+2)} + \binom{m}{m-j+1} [a,b]^{(m-j+2)} = \binom{m+1}{m+1-j} [a,b]^{(m-j+2)}\,.
-\]
-The coefficient of $a^0$ is $[a,b]^{(m+2)}$ and the coefficient of $a^{m+1}$ is $[a,b]^{(1)}$, so we are done.
-\end{proof}
-
-\begin{lemma}\label{lemma_iteratedcomm} Let odd elements $a_i, b_i \in A$ be given for $1 \le i \le n$ such that $[a_i, b_j] = 0$ for all $1 \le i,j \le n$ and define
-\[
-D = \sum_{i=1}^n a_i b_i\,.
-\]
-Suppose $[b_i,c] = 0$ for $1 \le i \le n$. Then for $m \ge 0$
-\be\label{eq:lemma_iteratedcomm}
-[D, c]^{(m)} = (-1)^{m|c|} \sum_{1 \le q_1,\ldots,q_m \le n} [a_{q_m}, [a_{q_{m-1}}, \ldots, [ a_{q_1}, c] \cdots ]] b_{q_1} \cdots b_{q_m}\,.
-\ee
-\end{lemma}
-\begin{proof}
-For convenience we introduce, for any tuple of indices $\bold{q} = (q_1,\ldots,q_m)$ of integers $1 \le q_i \le n$, the notation
-\begin{gather}
-\tau_{\bold{q}} = [ a_{q_m}, [ a_{q_{m-1}}, \ldots [ a_{q_1}, c ] \cdots ] \label{defn:tau}\\
-b_{\bold{q}} = b_{q_1} \cdots b_{q_m} \label{defn:bq}\,.
-\end{gather}
-For $m = 0$ the right hand side of \eqref{eq:lemma_iteratedcomm} is $c$ by convention, so the statement is trivial. We compute using the inductive hypothesis that
-\begin{align*}
-[D, c]^{(m+1)} &= [ D, [D, c]^{(m)} ]\\
-&= \big[D, (-1)^{m|c|} \sum_{\bold{q}} \tau_{\bold{q}} b_{\bold{q}}\big]\\
-&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i [ a_i b_i , \tau_{\bold{q}} b_{\bold{q}}]\\
-&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i \left( a_i b_i \tau_{\bold{q}} b_{\bold{q}} - \tau_{\bold{q}} b_{\bold{q}} a_i b_i \right)\\
-&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i \left( (-1)^{|c|} a_i \tau_{\bold{q}} b_{\bold{q}} b_i - (-1)^m \tau_{\bold{q}} a_i b_{\bold{q}} b_i \right)\\
-&= (-1)^{(m+1)|c|} \sum_{\bold{q}, i} [ a_i, \tau_{\bold{q}} ] b_{\bold{q}} b_i
-\end{align*}
-which completes the proof.
-\end{proof}
-
-Eventually we are going to substitute $a_i = \lambda_i, b_i = \theta_i^*$ so that $D = \delta$, and we will take further $c = \gamma$.
-In this notation, the aim of all of this is to compute the commutators $[c, D^m]$ and then $[c, \exp(-D)]$.
-Since most of the calculation can be done in $A$, so we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.
-
-\begin{lemma}\label{lemma:commutator_wha} For $m \ge 1$
-\[
-[ c, D^m ] = \sum_{i=0}^{m-1} (-1)^{(i+1)|c| + 1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}\,.
-\]
-\end{lemma}
-\begin{proof} 
-By Lemma \ref{lemma:woop3} we have
-\begin{equation}\label{eq:catfish}
-[ c, D^m ] = \sum_{p=0}^{m-1} D^p [ c, D ] D^{m-p-1} = -\sum_{p=0}^{m-1} D^p [ c, D ] D^{m-p-1}\,.
-\end{equation}
-Then using Lemma \ref{lemma:woop4} this becomes
-\be
--\sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} [D, c]^{(i+1)} D^{m-p-1+j}
-\ee
-which by Lemma \ref{lemma_iteratedcomm} equals
-\be
-\sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} (-1)^{(i+1)|c| + 1} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}
-\ee
-which is what we needed to show.
-\end{proof}
-
-Putting this all together:
-
-\begin{proposition}\label{prop:ccommutesexpD} Let $A$ be a $\nZ_2$-graded $\nQ$-algebra and
-\begin{itemize}
-\item Let $a_i, b_i \in A$ be odd elements with $[a_i,b_j] = 0$ for $1 \le i,j \le n$.
-\item Assume that $D = \sum_{i=1}^n a_i b_i$ has finite order, that is, $D^r = 0$ for some $r > 0$.
-\item Let $c \in A$ be an odd element, with $[b_i, c] = 0$ for $1 \le i \le n$.
-\end{itemize}
-Then
-\be\label{eq:ccommutesexpD}
-[c, \exp(-D)] = - \sum_{m \ge 1} \frac{1}{m!} \sum_{q_1,\ldots,q_m} [ a_{q_m}, [ a_{q_{m-1}}, \ldots [ a_{q_1}, c ] \cdots ] b_{q_1} \cdots b_{q_m} \exp(-D)\,.
-\ee
-\end{proposition}
-\begin{proof}
-Using Lemma \ref{lemma:commutator_wha}
-\begin{align*}
-[c, \exp(-D)] &= \sum_{m \ge 0} \frac{(-1)^m}{m!} [c, D^m]\\
-&= \sum_{m \ge 0} \frac{(-1)^{m+i}}{m!} \sum_{i=0}^{m-1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}\,.
-\end{align*}
-Rewriting this sum in terms of the variable $t = m - i - 1$ yields
-\[
-- \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^{t}}{(t+i+1)!} \sum_{i \le p \le t+i}  \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{t}\,.
-\]
-Using Lemma \ref{lemma:combin} below this may be rewritten as
-\[
-- \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{t!} \frac{1}{(i+1)!} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{t}
-\]
-which clearly agrees with \eqref{eq:ccommutesexpD}.
-\end{proof}
-
-\begin{lemma}\label{lemma:combin} For integers $a, b \ge 0$
-\begin{equation}\label{eq:combin}
-\frac{b!}{(a+b+1)!} \sum_{a \le m \le a + b} \binom{m}{a} = \frac{1}{(a+1)!}
-\end{equation}
-\end{lemma}
-\begin{proof}
-Denoting the left hand side of \eqref{eq:combin} by $\Omega_{a,b}$ the proof is an induction on $b$, i.e. by computing $\Omega_{a,b+1}$ in terms of $\Omega_{a,b}$.
-\end{proof}
-
-Now let us return to the original problem, of calculating the transfer $\cat{T}(\gamma)$ from Definition \ref{defn:transfer_contract}. We will only need this in the following special case:
-
-\begin{corollary}\label{corollary_transfergamma} Let $\gamma$ be an odd $R$-linear operator on $X$. Then
-\be\label{eq:transfer_gamma}
-\cat{T}(\gamma) = \gamma + \sum_{m \ge 1} \sum_{q_1,\ldots,q_m}  \frac{1}{m!} [\lambda_{q_m}, [\lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \gamma] \cdots ]] \theta^*_{q_1} \ldots \theta^*_{q_m}
-\ee
-is the tranferred operator on $K \otimes X$, where the $q_j$'s range over $1, \ldots, n$.
-\end{corollary}
-\begin{proof}
-This is immediate from Proposition \ref{prop:ccommutesexpD}, substituting $a_i = \lambda_i, b_i = \theta_i^*,c = \gamma$, since
-\[
-\exp(-D) c \exp(D) = c - [c, \exp(-D)] \exp(D)\,.
-\]
-\end{proof}
-
-%\cat{T}(\gamma) = \gamma + \sum_{m \ge 1} \sum_{\bold{q} = (q_1,\ldots,q_m)}  \sum_{\sigma \in \mf{S}_m} \frac{(-1)^{|\sigma|}}{(m!)^2} \tau_{\bold{q}}(\gamma) \At_{\sigma(\bold{q})}
-%\ee
-%where for $\bold{q} = (q_1,\ldots,q_m)$
-%\begin{align*}
-%\tau_{\bold{q}}(\gamma) &= [\lambda_{q_m}, [\lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \gamma] \cdots ]]\,,\\
-%\At_{\sigma(\bold{q})} &= \At_{q_{\sigma(1)}} \cdots \At_{q_{\sigma(m)}}\,.
-
-\begin{remark} Observe that since the $\theta_i^*$ square to zero, only sequences of distinct indices $q_1,\ldots,q_m$ contribute in the sum \eqref{eq:transfer_gamma}. The low order terms are
-\be
-\cat{T}(\gamma) = \gamma + \sum_q [\lambda_q, \gamma] \theta^*_q + \frac{1}{2} \sum_{p,q} [\lambda_p, [\lambda_q, \gamma]] \theta_q^*\theta_p^* + \cdots
-\ee
-\end{remark}
-
-Finally, we compute the transfer of the operator $\theta_i$ on $\bigwedge( \oplus_j k \theta_j ) \otimes_k X$:
-
-\begin{theorem}\label{theorem:psik} We have
-\begin{equation}\label{eq:psik}
-\cat{T}(\theta_i) = \theta_i - \sum_{m \ge 0} \sum_{q_1,\ldots,q_m} \frac{1}{(m+1)!} [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
-\end{equation}
-\end{theorem}
-\begin{proof}
-Observe that Corollary \ref{corollary_transfergamma} and the preceeding developments do not apply directly to $\theta_i$, because $[ \theta_j^*, \theta_i ] = \delta_{ij}$ whereas we have required the commutator $[b_j,c] = 0$ to vanish in the above.
-However, we do have
-\[
-[ \delta, \theta_i ] = \sum_j [ \lambda_j \theta_j^*, \theta_i ] = \sum_j \lambda_j \delta_{ij} = \lambda_i\,.
-\]
-And we can adjust the calculations above as follows. Firstly, using Lemma \ref{lemma:woop4} we obtain
-\[
-\delta^p [\delta, \theta_i] = \sum_{i+j=p} \binom{p}{i} [\delta, \theta_i]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [\delta, \lambda_i]^{(i)} \delta^j
-\]
-Tracking this through the rest of the calculation, as above, yields \eqref{eq:psik}.
-\end{proof}
-
-\begin{remark} The low order terms of \eqref{eq:psik} are
-\be
-\cat{T}(\theta_i) = \theta_i - \lambda_i - \frac{1}{2} \sum_q [\lambda_q, \lambda_i] \theta^*_q + \cdots
-\ee
-\end{remark}
-
-It is immediate that
-
-\begin{theorem} The closed odd operators $\cat{T}(\theta_i)$ and $\cat{T}(\theta_i^*) = \theta_i^*$ on the linear factorisation $(K \otimes X, d_K + d)$ form a representation of the Clifford algebra $C_n$.
-\end{theorem}
-
-By construction, Proposition \ref{prop:equivalencekoszul} is now promoted to an isomorphism of representations of $C_n$, with $\cat{T}(\theta_i), \cat{T}(\theta_i^*)$ acting on $K \otimes X$ and the $\theta_i, \theta_i^*$ acting on $\bigwedge( \oplus_i k\theta_i ) \otimes_k X$.
-
-\begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_n$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_n$.
-An explicit isomorphism can be written down using the techniques developed in this Section, see Appendix \ref{section:variation_of_homotopy}.
-\end{remark}
-
-\begin{remark}\label{remark:cancellations_transfer} Suppose for each pair $1 \le i,j \le n$ that up to homotopy
-\be
-[\lambda_i, \lambda_j] \simeq f_{ij} \cdot 1_X
-\ee
-for elements $f_{ij} \in R$.
-Then the formula for $\cat{T}(\theta_i)$ simplifies substantially: for any indices $i,j,k$ we have $[\lambda_i, [\lambda_j, \lambda_k]] \simeq [\lambda_i, f_{jk}] = 0$ so that \eqref{eq:psik} becomes
-\be
-\cat{T}(\theta_i) \simeq \theta_i - \lambda_i - \frac{1}{2} \sum_q f_{qi} \theta^*_q\,.
-\ee
-%The simplification for a general odd operator $\gamma$ is more modest. By the Jacobi identity
-%\[
-%[\lambda_i, [\lambda_j,\gamma]] + [\gamma, [\lambda_i, \lambda_j]] + [\lambda_j, [\gamma, \lambda_i]] = 0\,.
-%\]
-%Since $[\gamma, [\lambda_i, \lambda_j]] = [\gamma, f_{ij}] = 0$, this yields
-%\[
-%[\lambda_i, [\lambda_j, \gamma]] = -[\lambda_j, [\lambda_i, \gamma]]\,.
-%\]
-%Thus
-%\begin{align*}
-%\sum_{i,j} [\lambda_i, [\lambda_j, \gamma]] \theta_j^* \theta_i^* &= \sum_{i < j}\left( [\lambda_i, [\lambda_j, \gamma]] \theta_j^* \theta_i^* + [\lambda_j, [\lambda_i, \gamma]] \theta_i^*\theta_j^* \right)\\
-%&= \sum_{i < j} 2 [\lambda_i, [\lambda_j, \gamma]] \theta_j^*\theta_i^*\,.
-%\end{align*}
-%In this way any truly interesting cancellations are prevented by the operators $\theta_i^*$.
-\end{remark}
-
-\subsection{The finite model}\label{section:theequivalence}
-
-% As long as the $t_i$ belong to the maximal ideal
-We proceed to rediscover $Y \l X$ with its Clifford action as a finite model of $Y \otimes X$.
-Using this we prove in the next section that $\cat{L}$ and $\LG$ are equivalent bicategories.
-The notation is as in Setup \ref{setupforfusion}.
-We introduce formal variables $\theta_i$ of odd degree and set
-\[
-V = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
-\]
-The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ (where $t_i = \partial_{y_i} V$) is defined by
-\begin{equation}\label{defn:koszul}
-K = V \otimes_k k[y], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
-\end{equation}
-According to Strategy \ref{strategy} the first step is to find a finite model of
-\[
-( K \otimes_{k[y]} ( Y \otimes X ), d_K ) = ( V \otimes_k ( Y \otimes X ), d_K )\,.
-\]
-\textbf{First step.} A finite model for $(K, d_K)$ is obtained using connections.
-The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $k\llbracket y \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra.
-By identifying $d t_i$ with $\theta_i$ we may make the identification
-\[
-\check{K} := K \otimes_{k[y]} k\llbracket y \rrbracket \cong k\llbracket y \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}
-\]
-so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $\check{K}$.
-It is straightforward to check that $[d_K, \nabla]$ is invertible on the graded submodule $\check{K}_{\le -1}$ of nonzero degree terms, and we define
-\[
-H = [d_K, \nabla]^{-1} \nabla\,.
-\]
-
-\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $(\check{K},d_K)$.
-\end{proposition}
-\begin{proof}
-See \cite[Section 8.1]{dm1102.2957}.
-\end{proof}
-
-The associated strong deformation retract of $\mathbb{Z}$-graded $k$-complexes is
-\begin{equation}\label{eq:originalHdef}
-\xymatrix@C+2pc{
-(J_V,0) \ar@<-1ex>[r]_{\sigma} & (\check{K}, d_K), \ar@<-1ex>[l]_{\pi}
-} \quad H
-\end{equation}
-where $J_V$ is the Jacobi algebra from \eqref{eq:defnjacobian}, $\pi: \check{K} \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $k\llbracket y \rrbracket \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $k\llbracket y \rrbracket$ uniquely determined by $\nabla$.
-The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of the Koszul complex $\check{K}$.
-
-Recall that the tensor product $Y \,\check{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,z]\llbracket y \rrbracket$.
-The connection $\nabla$ extends to a standard $k[x,z]$-linear flat connection on $R$.
-A choice of homogeneous basis for $X$ and $Y$ allows us to write $Y \otimes X \cong k[x,y,z] \otimes_k Q$ for some $\mathbb{Z}_2$-graded free $k$-module $Q$, so
-\begin{equation}\label{eq:lambdaiso2}
-\check{K} \otimes_{k\llbracket y \rrbracket}( Y \,\check{\otimes}\, X ) \cong \check{K} \otimes_{k\llbracket y \rrbracket} (R \otimes_k Q) \cong \check{K} \otimes_k k[x,z] \otimes_k Q
-\end{equation}
-In this way the $k$-linear splitting homotopy $H$ on $\check{K}$ induces an $k[x,z]$-linear operator $H \otimes 1$ on $\check{K} \otimes_{k\llbracket y \rrbracket}( Y \,\check{\otimes}\, X)$, which we again denote by $H$.
-It is immediate that
-
-\begin{lemma} $H$ is a $k[x,z]$-linear splitting homotopy on $(\check{K} \otimes_{k\llbracket y \rrbracket} ( Y \,\check{\otimes}\, X ), d_K)$.
-\end{lemma}
-
-The associated strong deformation retract is
-\[
-\xymatrix@C+2pc{
-(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
-} \quad H
-\]
-The map $\pi$ is $R$-linear induced by the map $\pi: \check{K} \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.
-This is the desired finite model of $K \otimes Y \otimes X$ equipped with only the differential $d_K$.
-
-\vspace{0.3cm}
-
-\textbf{Second step.} We now view $d_{Y \otimes X}$ as a perturbation.
-The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
-Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
-\[
-\phi_\infty = \sum_{m \ge 0} (-1)^m (H d_{Y \otimes X})^m H
-\]
-is $k[x,z]$-linear splitting homotopy achieving the desired aim.
-
-Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $k[x,z]$-linear splitting homotopy on $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ and the associated $k[x,z]$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
-\begin{equation}\label{eq:finite_model_defo}
-\xymatrix@C+4pc{
-\big( Y \l X, d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{\sigma_\infty} & \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X, d_K + d_{Y \otimes X} \big)\,, \ar@<-1ex>[l]_-{\pi}
-} \quad \phi_\infty\,.
-\end{equation}
-%$A = d_{Y \otimes X}( 1 + H d_{Y \otimes X} )^{-1}$ and $\sigma_\infty = \sigma - H A \sigma$.
-We need only justify why in \eqref{eq:perturbedsdr} we have $d_\infty = d_{Y \otimes X}$ and $f_\infty = \pi$.
-But this follows from $H \sigma = 0$ and $\pi H = 0$.
-%\begin{equation}
-%\xymatrix@C+4pc{
-%Y \l X \ar@<-1ex>[r]_-{\exp(-\delta) \sigma_\infty} & S_m \otimes_k ( Y \,\check{\otimes}\, X )\ar@<-1ex>[l]_-{\pi \exp(\delta)}
-%}\,.
-%\end{equation}
-%of linear factorisations of $U - W$ over $k[x,y]$.
-
-\textbf{Third step.} Since each $t_i$ acts null-homotopically on $Y \otimes X$ there is by Section \ref{section:cliffordactkos} an isomorphism of linear factorisations
-\begin{equation}\label{eq:iso_larger_object}
-\xymatrix@C+3pc{ \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \otimes X, d_K + d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{ \exp(\delta) } & \big( V \otimes_k Y \,\check{\otimes}\, X, d_{Y \otimes X} \big)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
-\end{equation}
-where $\delta = \sum_i \lambda_i \theta_i^*$ for a choice $\lambda_i$ of null-homotopy for the action of $t_i$.
-From the identity $d^2_X = V - W$ we deduce that $\partial_{y_i}(d_X) d_X + d_X \partial_{y_i}(d_X) = \partial_{y_i} V = t_i$ so that we may, and do, choose $\lambda_i = \partial_{y_i}(d_X)$, see Section \ref{section:partial}.
-
-\vspace{0.3cm}
-
-\textbf{Fourth step.} Combining \eqref{eq:finite_model_defo} and \eqref{eq:iso_larger_object} we have a homotopy equivalence of matrix factorisations over $k[x,z]$
-\begin{equation}\label{eq:final_finite_model2}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & V \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
-}\,.
-\end{equation}
-By \cite[Remark 7.7]{dm1102.2957} the canonical map $\epsilon: Y \otimes X \lto Y \,\check{\otimes}\, X$ is a homotopy equivalence over $k[x,z]$ so finally we have
-
-\begin{theorem}\label{theorem:htpy_equivalence_main} There is a homotopy equivalence of matrix factorisations over $k[x,z]$
-\begin{equation}\label{eq:final_finite_model}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & V \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
-}
-\end{equation}
-where $\Phi = \pi \exp(-\delta) \epsilon$ and $\Phi^{-1} = \epsilon^{-1} \exp(\delta) \sigma_\infty$.
-\end{theorem}
-
-The canonical action of $C_m$ on the spinor representation $V$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $V \otimes_k ( Y \otimes X )$.
-In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$, and it remains to show that these two actions are compatible.
-
-\begin{proposition}\label{prop:clifford_action} The map $\Phi$ is an isomorphism of $C_m$- representations in the homotopy category. That is, there are homotopies
-\[
-\gamma_i \Phi \simeq \Phi \theta_i \,, \qquad \gamma_i^\dagger \Phi \simeq \Phi \theta_i^*\,.
-\]
-\end{proposition}
-\begin{proof}
-We prove that $\gamma_i \simeq \Phi \theta_i \Phi^{-1}$ and $\gamma_i^\dagger \simeq \Phi \theta_i^* \Phi^{-1}$.
-With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $V \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
-\[
-\cat{T}(\theta_i) = \exp(-\delta) \theta_i \exp(\delta)\,, \qquad \cat{T}(\theta_i^*) = \exp(-\delta) \theta_i^* \exp(\delta)\,.
-\]
-Then we use Lemma \ref{lemma:commutator_of_lambdas}, according to which there are homotopies
-\[
-[ \lambda_j, \lambda_k ] = [ \partial_{y_j}(d_X), \partial_{y_k}(d_X) ] \simeq \partial_{y_jy_k}(V)\,.
-\]
-Therefore by Theorem \ref{theorem:psik} and Remark \ref{remark:cancellations_transfer} we have $\cat{T}(\theta_i^*) = \theta_i^*$ and a homotopy
-\be\label{eq:comp338h}
-\cat{T}(\theta_i) \simeq \theta_i - \lambda_i - \frac{1}{2}\sum_q \partial_{y_q y_i}(V) \theta_q^*\,.
-\ee
-It remains to compute the further transfer of these operators to $Y \l X$. The key point is proven in Lemma \ref{lemma:transfercreations} below, where we show that there is a homotopy
-\be\label{eq:transfercr}
-\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty \simeq \At_{q_1} \cdots \At_{q_l}
-\ee
-for any indices $q_1,\ldots,q_l$. Hence
-\[
-\Phi \theta_i^* \Phi^{-1} \simeq \pi \cat{T}(\theta_i^*) \sigma_\infty = \pi \theta_i^* \sigma_\infty \simeq \At_i = \gamma_i^\dagger\,.
-\]
-Since $\pi$ projects onto $\theta$-degree zero,
-\begin{align*}
-\Phi \theta_i \Phi^{-1} &\simeq \pi \cat{T}(\theta_i) \sigma_\infty\\
-&\simeq - \pi \lambda_i \sigma_\infty - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) \pi \theta_q^* \sigma_\infty\\
-&\simeq - \lambda_i - \frac{1}{2}\sum_q \partial_{y_qy_i}(V) \At_q\\
-&= \gamma_i
-\end{align*}
-which completes the proof.
-\end{proof}
-
-\begin{lemma}\label{lemma:transfercreations} In the context of the diagram \eqref{eq:final_finite_model2} there is a $k[x,z]$-linear homotopy
-\[
-\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty \simeq \At_{q_1} \cdots \At_{q_l}
-\]
-for any sequence of indices $1 \le q_1,\ldots,q_l \le m$.
-\end{lemma}
-\begin{proof}
-Recall that, with $t_i = \partial_{z_i} V$, we have by \cite[Section 10]{dm1102.2957}
-\begin{equation}\label{eq:atiyah_formula_sigma}
-\sigma_\infty = \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2}} \frac{1}{s!} [ d_{Y \otimes X}, \partial_{t_{p_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{p_s}}] \theta_{p_1} \cdots \theta_{p_s} + (t \text{ terms})\,.
-\end{equation}
-That is, $\sigma_\infty$ is given modulo the submodule $(t_1,\ldots,t_m) K \otimes Y \otimes X$ by the formula above. Since $\pi$ vanishes on this submodule,
-\begin{align*}
-\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty &= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2}} \frac{1}{s!} [ d_{Y \otimes X}, \partial_{t_{p_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{p_s}}] \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}\\
-&= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s}{2}} \frac{1}{s!} \At_{p_1} \cdots \At_{p_s} \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}
-\end{align*}
-since $[ d_{Y \otimes X}, \partial_{t_{p_i}}] = - \At_{p_i}$.
-Now $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $s = l$ and to $\bold{p}$ a permutation of $\bold{q}$.
-Since
-\[
-\theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{q_{\sigma(1)}} \cdots \theta_{q_{\sigma(l)}} = (-1)^{|\sigma|} (-1)^{\binom{l}{2}}
-\]
-we have, using the fact that the Atiyah classes anti-commute,
-\begin{align*}
-\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty &= \sum_{\sigma \in \mathfrak{S}_l} (-1)^{|\sigma|} \frac{1}{l!} \At_{q_{\sigma(1)}} \cdots \At_{q_{\sigma(l)}}\\
-&\simeq \At_{q_1} \cdots \At_{q_l}
-\end{align*}
-which completes the proof.
-\end{proof}
-
-Finally, we will need naturality of Theorem \ref{theorem:htpy_equivalence_main}.
-
-\begin{proposition}\label{prop:naturality_main_thm} If $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations the diagram
-\begin{equation}\label{eq:final_finite_naturality}
-\xymatrix@C+4pc@R+1pc{
-Y \l X \ar[d]_-{\psi \l \phi} & V \otimes_k ( Y \otimes X )\ar[l]_-{\Phi} \ar[d]^-{\psi \otimes \phi}\\
-Y' \l X' & V \otimes_k ( Y' \otimes X' )\ar[l]^-{\Phi}
-}
-\end{equation}
-commutes up to $k[x,z]$-linear homotopy.
-\end{proposition}
-\begin{proof}
-Given the formula $\Phi = \pi \exp(-\delta) \epsilon$ it is clearly enough to show that $\psi \l \phi$ commutes up to homotopy with $\delta$, and for this it is enough to show that there is a homotopy
-\[
-\partial_{y_i}(d_{X'}) \phi \simeq \phi \partial_{y_i}(d_X)
-\]
-for each $i$. But this is the content of Lemma \ref{lemma:naturalityoflambda}.
-\end{proof}
-
-This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $V \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object.
-It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $V \otimes_k( Y \otimes X )$.
-
-\begin{remark} The isomorphism of $C_m$-representations in the homotopy category
-\[
-\Phi: V \otimes_k (Y \otimes X) \lto Y \l X
-\]
-is straightforward to compute.
-Firstly, since $\Phi = \pi \exp(-\delta) \varepsilon$ and the operator $\delta = \sum_i \lambda_i \theta_i^*$ annihilates the identity of the exterior algebra $1 \in V$, the composite
-\be
-\xymatrix@C+2pc{
-( k \cdot 1 ) \otimes_k ( Y \otimes X ) \ar[r]^-{\operatorname{inc}} & V \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
-}
-\ee
-is just the quotient map $Y \otimes X \lto Y \l X$, which we write as $\nu \mapsto \bar{\nu}$. Using
-\[
-\exp(-\delta) = 1 - \sum_i \lambda_i \theta_i^* - \frac{1}{2}\sum_{i,j} \lambda_i \lambda_j \theta_i^* \theta_j^* + \cdots
-\]
-we have for example
-\begin{align*}
-\Phi( \theta_1 \theta_2 \otimes \nu ) &= - \frac{1}{2} \sum_{i,j} \pi \lambda_i \lambda_j  \theta_i^* \theta_j^*( \theta_1 \theta_2 \otimes \nu )\\
-&= \frac{1}{2}\left( \lambda_1 \lambda_2 -\lambda_2 \lambda_1 \right)( \bar{\nu} )\,.
-\end{align*}
-\end{remark}
-
-\subsection{The equivalence of $\cat{L}$ and $\LG$}\label{section:equivalenceforreal}
-
-The bicategories $\LG$ and $\cat{L}$ have the same objects. Their morphism categories are 
-\begin{align*}
-\cat{L}(W,V) &= \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,\\
-\LG(W,V) &= \hmf( k[x,y], V - W )^{\oplus}
-\end{align*}
-with the notation from Section \ref{section:superbicatLG}. These are equivalent supercategories, via the following chain of equivalences
-\be
-\xymatrix@C-1pc{
-& \ar[dl]_-{\iota}\hmf( k[x,y], V - W )^{\omega}\ar[dr]^-{F}\\
-\Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet} &  & \hmf( k[x,y], V - W )^{\oplus}\ar@{.>}[ll]^-{\cat{Z}_{W,V}}
-}
-\ee
-where $\iota$ is the equivalence of a supercategory with its Clifford thickening, $F$ is the functor given earlier in \eqref{eq:omegavsoplus} and we define $\cat{Z}_{W,V} = \iota \circ F^{-1}$ to make the diagram commute.
-
-The latter functor $F$ is defined by choosing\footnote{One can avoid invoking the axiom of choice here by defining the splitting using homotopy colimits, see \cite{??}}, for each object $(X,e)$ a (possibly infinite rank) matrix factorisation $F(X,e)$ which splits the idempotent $e$.
-That is, such that there are morphisms in the homotopy category
-\[
-\xymatrix@C+2pc{
-X \ar@<1ex>[r]^-{f} & F(X,e) \ar@<1ex>[l]^-{g}
-}
-\]
-with $f g = 1$ and $gf = e$.
-The inverse is defined by choosing, for each infinite rank matrix factorisation $T$ which is a summand in the homotopy category of something finite rank, an actual finite rank $X$ and morphisms $f,g$ with $fg = 1_T$, and defining
-\[
-F^{-1}(T) = (X,gf)\,.
-\]
-We may arrange these choices so that if $T$ is \emph{already} finite rank then $F^{-1}(T) = (T, 1_T)$.
-
-\begin{theorem} $\cat{Z}: \LG \lto \cat{L}$ is an equivalence of superbicategories without units.
-\end{theorem}
-\begin{proof}
-The only real content here is to produce a $2$-isomorphism
-\be\label{eq:superfuncvarphi}
-\varphi_{Y,X}: \cat{Z}_{V,U}(Y) \l \cat{Z}_{W,V}(X) \lto \cat{Z}_{W,U}( Y \otimes X )
-\ee
-in the usual situation of Setup \ref{setupforfusion}, which is natural in both $Y$ and $X$. Once we have done this the rest follows by functoriality.
-
-Since $Y,X$ in this case are already finite rank $\cat{Z}(Y) = Y$ and $\cat{Z}(X) = X$.
-The calculation of $\cat{Z}( Y \otimes X )$ is more interesting, because $Y \otimes X$ is infinite rank over $k[x,z]$.
-However we know from Proposition \ref{prop:clifford_action} that there is an isomorphism in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $k[x,z]$
-\begin{equation}\label{eq:final_finite_modelagain}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & V \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
-}
-\end{equation}
-where $Y \l X$ is finite rank. Recall from Definition \ref{defn:idempotent_e} that the idempotent
-\[
-e_m = \gamma_1^\dagger \cdots \gamma_m^\dagger \gamma_m \cdots \gamma_1 \in C_m
-\]
-represents projection onto $k \cdot 1$ in $V$.
-Since \eqref{eq:final_finite_modelagain} is an isomorphism of $C_m$-representations the idempotent $e_m$ acting on $Y \l X$ must split to the same thing as the idempotent $e_m$ acting on the right hand side, which obviously splits to $Y \otimes X$.
-Put differently, there is a diagram in the homotopy category
-\[
-\xymatrix@C+2pc{
-Y \l X \ar@<1ex>[r]^-{f} & Y \otimes X \ar@<1ex>[l]^-{g}
-}
-\]
-where $g$ is the quotient map, and $f g = 1_{Y \otimes X}$ while $g f = e_m$.\footnote{$f$ is $\Phi^{-1}$ followed by projection onto $\theta$-degree zero.
-Not a very friendly map.} Then we may take as our definition
-\[
-\cat{Z}( Y \otimes X ) = (Y \l X, e_m)\,.
-\]
-So the problem is to define a $2$-isomorphism \eqref{eq:superfuncvarphi}, that is,
-\[
-\varphi_{Y,X}: (Y \l X, 1, \{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m) \lto (Y \l X, e_m)
-\]
-in the Clifford thickening of the idempotent completion of $\hmf(k[x,z],U - W)$, where the left hand side is equipped with the idempotent $1$ and the action $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ of $C_m$ while the right hand side has no Clifford action and idempotent $e_m$.
-
-But by Lemma \ref{lemma:whackamole} the identity map $\varphi_{Y,X} = 1_{Y \l X}$ is such an isomorphism, because the object $(Y \l X, e_m)$ of the idempotent completion by definition splits the idempotent $e_m$ on $Y \l X$.
-Naturality of \eqref{eq:superfuncvarphi} in $Y,X$ is a consequence of the naturality of \eqref{eq:final_finite_modelagain}, see Proposition \ref{prop:naturality_main_thm}.
-\end{proof}
-
-\subsection{Example: the Hom complex}\label{example:computing_homs}
-
-Using the cut model $\cat{L}$ we can study the complex $\Hom_R(X,Y)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[z_1,\ldots,z_m]$.
-In particular, we will explain how the homotopy relation on morphisms of matrix factorisations is effectively computable.
-
-The pair $(k,0)$ is an object in $\LG$ and we may view $Y$ and the dual matrix factorisation $X^{\vee}$ of $-V$ as a pair of $1$-morphisms
-\begin{equation}\label{eq:compute_hom_composition}
-\xymatrix@C+2pc{
-0 \ar[r]^-{Y} & V \ar[r]^-{X^{\vee}} & 0
-}\,.
-\end{equation}
-The composite is a $1$-morphism $0 \lto 0$, that is, $\mathbb{Z}_2$-graded complex of $k$-modules. This is the Hom complex of $R$-linear homogeneous maps $X \lto Y$,
-\[
-X^{\vee} \otimes_R Y \cong \Hom_R(X, Y)
-\]
-with the differential $\phi \mapsto d_Y \circ \phi - (-1)^{|\phi|} \phi \circ d_X$.
-The cut model provides a two-step process to compute the result of the composition in \eqref{eq:compute_hom_composition}.
-First form the cut
-\[
-X^{\vee} \l Y = X^{\vee} \otimes_R J_V \otimes_R Y = \Hom_{J_V}( \bar{X}, \bar{Y} )
-\]
-where $\bar{X} = X \otimes_R J_V, \bar{Y} = Y \otimes_R J_V$. This is a complex of finite-rank $\mathbb{Z}_2$-graded free $k$-modules, and there is an $A_m$-linear homotopy equivalence
-\[
-\Phi: S_m \otimes_k \Hom_R(X,Y) \lto \Hom_{J_V}( \bar{X}, \bar{Y} )\,.
-\]
-Set $H = \Hom_{J_V}( \bar{X}, \bar{Y} )$ and define
-\[
-B = \im( d^1_H: H^1 \lto H^0 )\,.
-\]
-As a matrix of scalars $d^1_H$ may be computed from the differentials $d_X, d_Y$ by inflation, as described in Remark \ref{remark:inflation}.
-Let $\psi: X \lto Y$ be a morphism of matrix factorisations.
-Then $\psi$ is null-homotopic if and only if $\psi' = \Phi(\psi) \in \Hom_{J_V}( \bar{X}, \bar{Y} )$ is a coboundary.
-As a matrix, $\psi'$ is obtained from $\psi$ by inflation.
-This reduces the problem of determing whether or not $\psi$ is null-homotopic to the subspace membership problem for the pair $(B, \psi')$.
-If $k$ is a field this may be computed by a row-reduction, and otherwise using Gr\"obner bases.
-
-\begin{example} Suppose $V = z^N$ in $k[z]$ for $N \ge 2$. Take matrix factorisations $X,Y$ with the same underlying free $R = k[z]$-module $X = Y = R \oplus R \theta$ and differentials
-\[
-d_X = z^i \theta + z^{N-i} \theta^* = \begin{pmatrix} 0 & z^{N-i} \\ z^i & 0 \end{pmatrix}, \qquad d_Y = z^j \theta + z^{N-j} \theta^* = \begin{pmatrix} 0 & z^{N-j}\\ z^j & 0 \end{pmatrix}
-\]
-where $1 \le i,j \le N/2$. Using the basis $\Hom_R(X,Y) = R \theta \theta^* \oplus R \theta^* \theta \oplus R\theta \oplus R \theta^*$,
-\begin{equation}\label{eq:differential_hom}
-d_{\Hom} = \begin{pmatrix} 0 & 0 & z^{N-i} & z^j \\ 
-0 & 0 & z^{N-j} & z^i \\
--z^i & z^j & 0 & 0 \\
-z^{N-j} & -z^{N-i} & 0 & 0 \end{pmatrix}\,.
-\end{equation}
-Let us now compute the cut $X^{\vee} \l Y$ with its Clifford action. With
-\[
-J_V = k[z]/z^{N-1} = k \cdot 1 \oplus k \cdot z \oplus \cdots k \cdot z^{N-2}
-\]
-the matrix of multiplication by $z$ on $J_V$ is $[z] = \begin{pmatrix} 0 & 0\\ I_{N-2} & 0 \end{pmatrix}$. The differential on
-\[
-X^{\vee} \l Y = \Hom_{J_V}( \bar{X}, \bar{Y} ) = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
-\]
-is then obtained from \eqref{eq:differential_hom} by replacing every $z$ by the matrix $[z]$.
-
-The Clifford algebra $A_1$ acts by two generators $a, a^\dagger$.
-To determine their matrices, note that with $t = z^{N-1}$, $k[z]$ is a free $k[t]$-module with basis $1, \ldots, z^{N-2}$.
-Given a polynomial $f(z)$ we may uniquely write it as $f(z) = \sum_{l = 0}^{N-2} f_l \cdot z^l$ with $f_l \in k[t]$.
-There is a connection $\nabla: k[z] \lto k[z] \otimes_{k[t]} \Omega^1_{k[t]/k}$ whose associated $k$-linear operator $\partial_t$ is
-\[
-\partial_t: k[z] \lto k[z], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) z^l \,.
-\]
-Notice that for $0 \le q \le N - 1$, $\partial_t(z^q) = \delta_{q (N-1)} \cdot 1$.
-
-The Atiyah class is the $k[t]$-linear operator $\At = [d_{\Hom}, \partial_t]$ on $\Hom_R(X,Y)$. We may compute it for example on generators by
-\[
-\At( \theta \theta^* ) = \partial_t d_{\Hom}( \theta \theta^* ) = - \partial_t( z^i ) \theta + \partial_t( z^{N-j} ) \theta^* = - \delta_{i (N-1)} \theta + \delta_{(N-j)(N-1)} \theta^*\,.
-\]
-The Atiyah class passes to a $k$-linear operator $a^\dagger$ on $X^{\vee} \l Y$ with matrix ($I$ denotes $I_{N-1}$)
-\begin{equation}\label{eq:aityah_class_hom_example}
-a^\dagger = \begin{pmatrix} 0 & 0 & \delta_{i1} \cdot I & \delta_{j(N-1)} \cdot I \\ 
-0 & 0 & \delta_{j1} \cdot I & \delta_{i(N-1)} \cdot I \\
-- \delta_{i(N-1)} \cdot I & \delta_{j(N-1)} \cdot I & 0 & 0 \\
-\delta_{j1} \cdot I & - \delta_{i1} \cdot I & 0 & 0 \end{pmatrix}\,.
-\end{equation}
-Similarly one can determine that the matrix of $\lambda$ on $X^{\vee} \l Y$ is
-\[
-\lambda = \begin{pmatrix} 0 & 0 & 0 & \frac{j}{N} [z^{j-1}] \\
-0 & 0 & \frac{N-j}{N} [z^{N-j-1}] & 0\\
-0 & \frac{j}{N} [z^{j-1}] & 0 & 0\\
-\frac{N-j}{N} [z^{N-j-1}] & 0 & 0 & 0\end{pmatrix}\,.
-\]
-By definition $a = - \lambda - \lambda^2 a^\dagger$ so this completes the description of the cut $( X^{\vee} \l Y, \{ a, a^\dagger \} )$.
-Splittng the idempotent $a^\dagger a$ on the $\mathbb{Z}_2$-graded complex $X^{\vee} \l Y$ of finite rank free $k$-modules yields a finite model for $\Hom_R(X,Y)$.
-\end{example}
-
-TODO: remark on difference between $\partial(d_Y)$ and $\partial(d_X)$
-
-\appendix
-
-\section{Tensor products in supercategories}\label{section:tensorproduct_supcat}
-
-Let $\cat{C}$ be an idempotent complete supercategory.
-
-\begin{definition} Let $V$ be a $\mathbb{Z}_2$-graded $k$-module and $X$ an object of $\cat{C}$.
-An object of $\cat{C}$ representing the functor $\Hom^0_k( V, \cat{C}^*(X, -))$ is denoted $V \otimes_k X$ if it exists.
-That is to say, the tensor product consists of an object $V \otimes_k X$ and a natural isomorphism
-\[
-\rho_Y: \cat{C}( V \otimes_k X, Y ) \lto \Hom^0_k( V, \cat{C}^*(X,Y) )\,.
-\]
-Such a pair is unique up to unique isomorphism, if it exists.
-\end{definition}
-
-\begin{remark} 
-From $\rho$ we also obtain an isomorphism of $\mathbb{Z}_2$-graded $k$-modules
-\[
-\cat{C}^*( V \otimes_k X, Y ) \cong \Hom_k^*( V, \cat{C}^*(X,Y) )\,.
-\]
-The tensor product $V \otimes_k X$ is made functorial in $V$ and $X$ in such a way that $\rho$ is natural in all its variables.
-\end{remark}
-
-\begin{example} If $V = k^{\oplus n} \oplus k[1]^{\oplus m}$ is finite and free then
-\[
-V \otimes_k X = X^{\oplus n} \oplus \Psi X ^{\oplus m}
-\]
-is a representing object, with the obvious isomorphism $\rho$.
-\end{example}
-
-\begin{lemma} If $\cat{C}$ is idempotent complete and $V$ is a finitely generated projective $\mathbb{Z}_2$-graded $k$-module, then $V \otimes_k X$ exists for any object $X$.
-\end{lemma}
-\begin{proof}
-Let $V'$ be a finite free $k$-module with $f: V' \lto V, g: V \lto V'$ satisfying $fg = 1$.
-This determines an idempotent $1 \otimes e$ on $V' \otimes_k X$, which splits by hypothesis in $\cat{C}$.
-The object splitting this idempotent has the right property to be $V \otimes_k X$.
-\end{proof}
-% via morphisms $F,G$ with
-%\[
-%\xymatrix@C+1pc{
-%Q \ar@<0.8ex>[r]^-{G} & V' \otimes_k X \ar@<0.8ex>[l]^-{F} 
-%} \qquad FG = 1, GF = 1 \otimes e
-%\]
-%for some object $Q$. We have
-%\begin{align*}
-%\cat{C}( Q, Y ) &\cong \{ f: V' \otimes_k X \lto Y \l f(1 \otimes e) = 1 \otimes e \}\\
-%&\cong \{ \hat{f} \in \Hom_k( V', \cat{C}^*(X,Y)) \l \hat{f} e = e \}\\
-%&\cong \Hom_k( V, \cat{C}^*(X,Y))\,.
-%\end{align*}
-%and hence $V \otimes_k X = Q$ exists.
-%\end{proof}
-
-More generally, let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra.
-
-\begin{definition} Given a right $\mathbb{Z}_2$-graded $A$-module $V$ and an object $X$ of $\cat{C}$, we denote by $V \otimes_A X$ the object representing the functor $\Hom^0_A( V, \cat{C}^*(X,-))$ if it exists.
-That is, the tensor product is an object $V \otimes_A X$ together with a natural isomorphism
-\begin{equation}\label{eq:isodefatensor}
-\rho_Y: \cat{C}(V \otimes_A X, Y) \lto \Hom^0_A( V, \cat{C}^*(X,Y))\,.
-\end{equation}
-As before, the tensor product is functorial in both $V$ and $X$.
-\end{definition}
-
-Henceforth we concentrate our attention on $\mathbb{Z}_2$-graded $k$-algebras $A$ which are \emph{Morita trivial} in the sense that they are isomorphic to an algebra of the form $\End_k(P)$ for a finite rank free $\mathbb{Z}_2$-graded $k$-module $P$.
-
-\begin{lemma} If $A \cong \End_k(P)$ then for any $A$-module $X$ in $\cat{C}$ there is an object $\widetilde{X}$ and an isomorphism of $A$-modules $X \cong P \otimes_k \widetilde{X}$.
-\end{lemma}
-\begin{proof}
-The natural idempotents in $A$ act as idempotents on $X$, which split.
-\end{proof}
-
-\begin{lemma} If $A \cong \End_k(P)$ and $V$ is a $\mathbb{Z}_2$-graded right $A$-module which is finitely generated and projective as a $k$-module, then $V \otimes_A X$ exists for any $A$-module $X$.
-\end{lemma}
-\begin{proof}
-Write $P^* = \Hom_k(P,k)$ so that $V \cong \widetilde{V} \otimes_k P^*$ as right $A$-modules for some $\mathbb{Z}_2$-graded $k$-module $\widetilde{V}$.
-Since $V$ is finitely generated projective over $k$, so is $\widetilde{V}$.
-By the previous lemma, $X \cong P \otimes_k \widetilde{X}$ for some object $\widetilde{X}$, so we might expect that
-\[
-V \otimes_A X \cong (\widetilde{V} \otimes_k P^*) \otimes_A (P \otimes_k \widetilde{X}) \cong \widetilde{V} \otimes_k \widetilde{X}
-\]
-Working backwards: $\widetilde{V} \otimes_k \widetilde{X}$ exists and has the right universal property since
-\begin{align*}
-\cat{C}(\widetilde{V} \otimes_k \widetilde{X}, Y) &\cong \Hom_k( V \otimes_A P, \cat{C}^*(\widetilde{X}, Y))\\
-&\cong \Hom_A( V, P^* \otimes_k \cat{C}^*(\widetilde{X}, Y))\\
-&\cong \Hom_A( V, \cat{C}^*( X, Y ) )
-\end{align*}
-as claimed.
-\end{proof}
-
-From now on $A,B,C$ are Morita trivial $k$-algebras. Recall $\cat{C}_A$ denotes the category of left $A$-modules in $\cat{C}$.
-
-\begin{definition}\label{defn:psimodule} Given a left $A$-module $X$ in $\cat{C}$, the object $\Psi X$ is a left $A$-module, where $a \in A_0$ acts by $\Psi(a)$ and $a \in A_1$ acts by
-\[
-\xymatrix{
-\Psi (X) \ar[r]^-{\Psi(a)} & \Psi \Psi (X) \ar[r]^-{-1} & \Psi \Psi (X)
-}\,.
-\]
-This determines a functor $\Psi: \cat{C}_A \lto \cat{C}_A$.
-\end{definition}
-
-\begin{lemma} $(\cat{C}_A, \Psi)$ is a supercategory.
-\end{lemma}
-\begin{proof}
-The natural isomorphism $\xi_X: \Psi \Psi (X) \lto X$ is given by the identity in $\cat{C}$.
-\end{proof}
-
-Let $V$ be a $B$-$A$-bimodule which is finitely generated and projective over $k$.
-If $X$ is a left $A$-module in $\cat{C}$ then $V \otimes_A X$ is made into a left $B$-module in $\cat{C}$ uniquely such that \eqref{eq:isodefatensor} is a natural isomorphism of $B$-modules.
-Hence the tensor product gives a functor
-\[
-\Phi_V = V \otimes_A (-): \cat{C}_A \lto \cat{C}_B\,.
-\]
-Given a $B$-$A$-bimodule $V$ and an object $X$ for which $V \otimes_A X$ exists, there are natural isomorphisms of $B$-modules
-\[
-\Psi V \otimes_A X \cong \Psi(V \otimes_A X) \cong V \otimes_A \Psi X
-\]
-induced from the isomorphisms
-\[
-\Hom_A( \Psi V, \cat{C}^*(X, -)) \cong \Hom_A( V, \Psi \cat{C}^*(X, -) ) \cong \Hom_A( V, \cat{C}^*(\Psi X, -))\,.
-\]
-It follows that $\Phi_V$ is a superfunctor.
-
-\begin{lemma}\label{lemma:assoctensor} Let $W$ be a $C$-$B$-bimodule and $V$ a $B$-$A$-bimodule. Then there is a natural isomorphism of $C$-modules
-\[
-(W \otimes_B V) \otimes_A X \cong W \otimes_B ( V \otimes_A X )
-\]
-\end{lemma}
-\begin{proof}
-This follows from the isomorphism
-\begin{align*}
-\Hom_A(W, \cat{C}^*(V \otimes_A X, -)) &\cong \Hom_A( W, \Hom_A^*(V, \cat{C}^*(X, -)))\\
-&\cong \Hom_A(W \otimes_A V, \cat{C}^*(X, -))\,.
-\end{align*}
-\end{proof}
-
-Now we specialise to the Clifford algebras $C_n$ and their modules.
-
-\begin{lemma}\label{lemma:simplehom} Let $X$ be a $\mathbb{Z}_2$-graded left $C_n$-module. There is a $k$-linear isomorphism
-\[
-\Hom_{C_n}^0( S_n, X ) \cong \big\{ x \in X^0 \l \gamma_i^\dagger \cdot x = 0 \text{ for all } 1 \le i \le n \big\}
-\]
-defined by $f \mapsto f(1)$. If $X$ is a right $C_n$-module there is a $k$-linear isomorphism
-\[
-\Hom^0_{C_n}( (S_n)^*, X ) \cong \big\{ x \in X^0 \l x \cdot \gamma_i = 0 \text{ for all } 1 \le i \le n \big\}
-\]
-defined by $f \mapsto f(1^*)$.
-\end{lemma}
-
-\begin{lemma}\label{lemma:morphism_out_1} For an $C_n$-module $Y$ there is a $k$-linear isomorphism
-\[
-\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta: X \lto Y \l \gamma_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
-\]
-defined by sending $\alpha: S_n \otimes_k X \lto Y$ to the composite
-\[
-\xymatrix@C+2pc{
-X \cong k \otimes_k X \ar[r]^-{\iota \otimes 1} & S_n \otimes_k X \ar[r]^-{\alpha} & Y
-}
-\]
-where $\iota: k \lto S_n$ is defined by $\iota(1) = 1$.
-\end{lemma}
-\begin{proof}
-This follows from Lemma \ref{lemma:simplehom} and the isomorphism
-\[
-\cat{C}_{C_n}(S_n \otimes_k X, Y ) \cong \Hom_{C_n}( S_n, \cat{C}^*(X,Y) )\,.
-\]
-\end{proof}
-
-More generally
-
-\begin{lemma}\label{lemma:morphisms_two_forms} Let $X \in C_{C_p}$ and $Y \in \cat{C}_{C_q}$. There is a $k$-linear isomorphism
-\begin{align*}
-\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ \gamma_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ \gamma_i^\dagger \circ \delta &= 0 \text{ for } 1 \le i \le q \}
-\end{align*}
-defined by sending $\alpha: S_{q,p} \otimes_{C_p} X \lto Y$ to the composite
-\[
-\xymatrix@C+2pc{
-X \cong C_p \otimes_{C_p} X \ar[r]^-{\iota \otimes 1} & S_{q,p} \otimes_{C_p} X \ar[r]^-{\alpha} & Y
-}
-\]
-where $\iota: C_p \lto S_{q,p}$ is defined by $\iota(1) = 1 \otimes 1^*$.
-\end{lemma}
-\begin{proof}
-Using the previous lemma and Lemma \ref{lemma:simplehom},
-\begin{align*}
-\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) &\cong \Hom^0_{C_p-C_q-\operatorname{bimod}}( S_{q} \otimes_k S_p^* , \cat{C}^*(X,Y))\\
-&\cong \Hom^0_{C_q}( S_q, \Hom^*_{C_p}( S_p^*, \cat{C}^*(X,Y) ))\\
-&\cong \{ \delta \in \Hom^0_{C_q}( S_p^*, \cat{C}^*(X,Y) ) \l \gamma_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
-&\cong \{ \delta: X \lto Y \l \delta \circ \gamma_i = 0 \text{ for } 1 \le i \le p \text{ and } \gamma_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}
-\end{align*}
-as claimed.
-\end{proof}
-
-\section{Constructing superbicategories}\label{section:constructing_superbicategories}
-
-This appendix collects the data needed for constructing a superbicategory $\cat{B}$ from a collection of supercategories $\cat{B}(a,b)$.
-Given a bicategory $\cat{B}$ and for each pair of objects $a,b$ the structure of a supercategory on $\cat{B}(a,b)$, we denote composition by
-\[
-T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
-\]
-We assume this is a superfunctor, i.e.
-that \eqref{eq:psicomp1}-\eqref{eq:psicomp3} commute.
-Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$.
-We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.
-
-Suppose that for all objects $a,b,c$ we are given natural isomorphisms
-\begin{align*}
-T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T, \qquad T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
-\end{align*}
-both of which will be denoted $\tau$.
-We define for an object $a$ the $1$-morphism $\Psi_a = \Psi( \Delta_a )$ and the $2$-isomorphism $\xi_a$ to be the following composite (using the structure maps of $\cat{B}$ and isomorphisms $\tau$)
-\[
-\xi_a: \Psi_a \l \Psi_a = \Psi( \Delta_a ) \l \Psi( \Delta_a ) \cong \Psi( \Delta_a \l \Psi(\Delta_a ) ) \cong \Psi^2( \Delta_a \l \Delta_a ) \cong \Delta_a \l \Delta_a \cong \Delta_a\,.
-\]
-Similarly given a $1$-morphism $X: a \lto b$ we have a $2$-isomorphism $\gamma_X$
-\[
-\gamma_X: X \l \Psi_a = X \l \Psi( \Delta_a ) \cong \Psi( X \l \Delta_a ) \cong \Psi(X) \cong \Psi( \Delta_b \l X ) \cong \Psi( \Lambda_b ) \l X = \Psi_b \l X\,.
-\]
-Given a $1$-morphism $X: a \lto b$ in $\cat{B}$ there are diagrams
-\begin{gather}
-\xymatrix@R+1pc@C+1pc{
-\Delta_b \l \Psi (X) \ar[dr]_-{\lambda_{\Psi a}} \ar[rr]^-{\tau} & & \Psi( \Delta_b \l X ) \ar[dl]^-{\Psi( \lambda )}\\
-& \Psi(X)
-} \label{eq:psiunitor1}\\
-\xymatrix@R+1pc@C+1pc{
-\Psi(X) \l \Delta_a \ar[rr]^-{\tau}\ar[dr]_-{\rho} & & \Psi( X \l \Delta_a ) \ar[dl]^-{\Psi(\rho)}\\
-& \Psi(X)
-} \label{eq:psiunitor2}
-\end{gather}
-whose commutativity expresses compatibility of the functors $\Psi$ with the units, while for a composable triple $X,Y,Z$ the commutativity of the diagrams
-\begin{gather}
-\xymatrix{
-(Z \l Y) \l \Psi(X) \ar[dd]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( Y \l \Psi(X)) \ar[d]^-{\tau}\\
- & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
-\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
-} \label{eq:psithirdlastdia}\\
-\xymatrix{
-(Z \l \Psi(Y)) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( \Psi(Y) \l X) \ar[d]^-{\tau}\\
-\Psi( Z \l Y ) \l X \ar[d]_-{\tau} & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
-\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
-} \label{eq:psimiddledia}\\
-\xymatrix{
-(\Psi(Z) \l Y) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & \Psi(Z) \l ( Y \l X ) \ar[dd]^-{\tau}\\
-\Psi(Z \l Y) \l X \ar[d]_-{\tau} & & \\
-\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
-}\label{eq:psilastdia}
-\end{gather}
-expresses compatibility of $\Psi$ with the associator of $\cat{B}$.
-
-\begin{lemma}\label{lemma:constructingsuper}
-Given a bicategory $\cat{B}$ with the structure of a supercategory on $\cat{B}(a,b)$ for all pairs $a,b$, and natural isomorphisms $\tau$, suppose that \eqref{eq:psiunitor1}-\eqref{eq:psilastdia} commute.
-Then with $\Psi, \xi$ and $\gamma$ defined as above, $\cat{B}$ is a superbicategory.
-\end{lemma}
-\begin{proof}
-The proof is an easy but somewhat lengthy exercise, which we omit.
-\end{proof}
 
@@
 
-% reference for \lambda-calculus
-% reference for cut
-% geometry of interaction
-
 \bibitem{barneslambe}
@@
 
-\bibitem{bor94}
-F.~Borceux, \textsl{Handbook of categorical algebra $1$}, volume $50$ of \textsl{Encyclopedia of Mathematics and its Applications}, Cambridge University Press, Cambridge, 1994.
-
-\bibitem{buchweitz_flenner}
-R.-O.~Buchweitz and H.~Flenner, \textsl{A semiregularity map for modules and applications to deformations}, Compositio Math. \textbf{137} (2003), 135--210.
-
-\bibitem{ct1007.2679}
-A.~{C\u ald\u araru} and S.~Willerton, \textsl{The Mukai pairing, I: a categorical approach},
-New York Journal of Mathematics \textbf{16} (2010), 61--98, 
-  \href{http://arxiv.org/abs/0707.2052}{[arXiv:0707.2052]}.
-
-\bibitem{khovhompaper}
-N.~Carqueville and D.~Murfet, \textsl{Computing {K}hovanov-{R}ozansky homology and defect fusion}, Algebraic \& Geometric Topology \textbf{14} (2014), 489--537, \href{http://arxiv.org/abs/1108.1081}{[arXiv:1108.1081]}.
-
-\bibitem{lgdual}
-N.~Carqueville and D.~Murfet, \textsl{Adjunctions and defects in {L}andau-{G}inzburg models}, \href{http://arxiv.org/abs/1208.1481}{[arXiv:1208.1481]}.
-
-\bibitem{lgdual_survey}
-N.~Carqueville and D.~Murfet, \textsl{A toolkit for defect computations in Landau-Ginzburg models}, \href{http://arxiv.org/abs/1303.1389}{[arXiv:1303.1389]}, contribution to the String-Math 2012 proceedings.
-
-\bibitem{ade}
-N.~Carqueville, A.~Ros Camacho and I.~Runkel, \textsl{Orbifold equivalent potentials}, \href{http://arxiv.org/abs/1311.3354}{[arXiv:1311.3354]}.
-
-\bibitem{cr0909.4381}
-N.~Carqueville and I.~Runkel, \textsl{On the monoidal structure of matrix bi-factorisations}, J. Phys.
-  A: Math. Theor. \textbf{43} (2010), 275401,
-  \href{http://arxiv.org/abs/0909.4381}{[arXiv:0909.4381]}.
-
-\bibitem{crainic}
-M.~Crainic, \emph{On the perturbation lemma, and deformations}, \href{http://arxiv.org/abs/math/0403266}{[arXiv:0403266]}
-
-\bibitem{d0904.4713}
-T.~Dyckerhoff, \textsl{Compact generators in categories of matrix factorizations},
-  Duke Math. J. \textbf{159} (2011), 223--274,
-  \href{http://arxiv.org/abs/0904.4713}{[arXiv:0904.4713]}.
-
-\bibitem{dm1102.2957}
-T.~Dyckerhoff and D.~Murfet, \textsl{Pushing forward matrix factorisations}, Duke Math. J. \textbf{162} (2013), 1249--1311, \href{http://arxiv.org/abs/1102.2957}{[arXiv:1102.2957]}.
-
-\bibitem{ellis_lauda}
-A.~Ellis and A.~Lauda, \textsl{An odd categorification of $U_q(\mathfrak{sl}_2)$}, \href{http://arxiv.org/abs/1307.7816}{[arXiv:1307.7816]}.
-
-\bibitem{friedrich}
-T.~Friedrich, \textsl{{D}irac operations in {R}iemannian geometry}, Graduate studies in mathematics \textbf{25}, AMS (1997).
-
-\bibitem{girard_llogic}
-J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
-
-\bibitem{greuel}
-G.-M.~Greuel, C.~Lossen and E.~Shustin, \textsl{Introduction to singularities and deformations}, Springer (2007).
-
-\bibitem{kang}
-S.-J.~Kang, M.~Kashiwara and S.-J.~Oh, \textsl{Supercategorification of quantum Kac-Moody algebras}, Adv. Math \textbf{242} (2013) 116--162, \href{http://arxiv.org/abs/1206.5933}{[arXiv:1206.5933]}.
-
-\bibitem{kang2}
-S.-J.~Kang, M.~Kashiwara and S.-J.~Oh, \textsl{Supercategorification of quantum Kac-Moody algebras II}, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.
-
-\bibitem{McNameethesis}
-D.~McNamee, \textsl{On the mathematical structure of topological defects in
-  {L}andau-{G}inzburg models}, MSc Thesis, Trinity College Dublin, 2009.
-
-\bibitem{cutsystems2}
-D.~Murfet, \textsl{Computing with cut systems II: linear logic}, in progress.
-
-\bibitem{selinger}
-P.~Selinger, \textsl{Lecture notes on the {L}ambda calculus}, \href{http://arxiv.org/abs/0804.3434}{[arXiv:0804.3434]}.
-
-\bibitem{vistoli}
-A.~Vistoli, \textsl{Notes on {G}rothendieck topologies, fibered categories and descent theory}, \href{http://arxiv.org/abs/math/0412512}{[arXiv:0412512]}.
-
-\bibitem{yoshino98}
-Y.~Yoshino, \textsl{Tensor products of matrix factorizations}, Nagoya Math. J.
-  \textbf{152} (1998), 39--56.
+\bibitem[Cra04]{crainic}
+M.~Crainic, \emph{On the perturbation lemma, and deformations}, arXiv:0403266
+  [math.AT].
 

### 2015-08-29 cutsystems_cuts.tex
New version of cut systems paper.

@@
 
+\section{Defining Cut systems}
+
+To complete the construction of the cut system we need to finish defining the associator and unitors (a task begun at the outset of the section) and to prove that the coherence conditions hold.
+
+Earlier the unitors were described by explicit formulas.
+Here we begin more abstractly: let $X \in \cat{L}(W,V)$ be a matrix factorisation with $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$.
+Since $\Delta_V$ is the unit in $\LG$ there is a homotopy equivalence $\lambda: \Delta_V \otimes_{k[z]} X \lto X$ and so by Proposition \ref{prop:final_homotopy_equiv_cut} there are homotopy equivalences
+\begin{equation}
+\xymatrix@C+3pc{
+\Delta_V \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( \Delta_V \otimes X )\ar@<-1ex>[l]_-{\Phi} \ar@<-1ex>[r]_-{1 \otimes \lambda} & S_m \otimes_k X \ar@<-1ex>[l]_-{1 \otimes \lambda^{-1}} 
+}\,.
+\end{equation}
+By construction these isomorphisms are $A_m$-linear, and the map from right to left is an isomorphism $\mu: X \lto \Delta_V \l X$ in $\cat{L}(W,V)^\bullet$ corresponding under Lemma \ref{lemma:morphism_out_1} to
+\[
+\mu_0 = \xymatrix@C+1pc{
+X \ar[r]^-{\lambda^{-1}} & \Delta_V \otimes_{k[z]} X \ar[r]^-{\varrho} & \Delta_V \l X
+}\,.
+\]
+where $\varrho$ is the quotient map.
+Given the explicit formula for $\lambda^{-1}$ from \cite[Section 4.1]{lgdual}, this map $\mu_0$ has the explicit formula given earlier in \eqref{eq:explicit_mu0}.
+Since $\mu_0$ is natural in $X$, this also proves that $\mu$ is a natural isomorphism.
+The details for $\eta$ are similar, so the unitors are now defined.
+
+The remaining components of the cut system $\cat{L}$ are the units $\Delta_W \in \cat{L}(W,W)$, which are the same as those for $\LG$ given in Section \ref{section:superbicatLG}, and the associators and unitors.
+
+The unitors can also be described by explicit formulas.
+Given $X \in \cat{L}(W,V)$ as above with homogeneous basis $e_i$ as a $\mathbb{Z}_2$-graded $k[x,z]$-module, we define morphisms of matrix factorisations
+\begin{gather}
+\mu_0: X \lto \Delta_V \l X \,, \\
+\mu_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j \Theta_{i_1} \ldots \Theta_{i_l} \left\{ \partial^{z,z'}_{[i_l]}(d_X) \cdots \partial^{z,z'}_{[i_1]}(d_X) \right\}_{ji} \otimes e_j\label{eq:explicit_mu0}
+\end{gather}
+and
+\begin{gather}
+\eta_0: X \lto X \l \Delta_W \,,\\
+\eta_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j (-1)^{\binom{l}{2} + l|e_i|} e_j \otimes \left\{ \partial^{x,x'}_{[i_1]}(d_X) \cdots \partial^{x,x'}_{[i_l]}(d_X) \right\}_{ji} \Theta_{i_1} \ldots \Theta_{i_l}
+\end{gather}
+To make sense of these formulas, note that $\Delta_V$ is a matrix factorisation of $V(z) - V(z')$ over $k[z,z']$ and $\Delta_W$ is a matrix factorisation of $W(x) - W(x')$ over $k[x,x']$, while the divided difference operators are defined by
+\[
+{}^{t_i}(-): k[x,x'] \lto k[x,x']\,, \qquad f \mapsto f|_{x_i \mapsto x'_i}
+\]
+and
+\[
+\partial^{x,x'}_{[i]}: k[x,x'] \lto k[x,x']\,, \qquad f \mapsto \frac{{}^{t_1 \ldots t_{i-1}} f - {}^{t_1 \ldots t_i} f}{x_i - x'_i}
+\]
+and in the same way for $z,z'$.
+For a concrete example of these formulas see \cite{lgdual_survey}.
+The actual unitors are the morphisms $X \lto \Delta_V \l X$ and $X \lto X \l \Delta_W$ in $\cat{L}(W,V)^\bullet$ corresponding to $\mu_0$ and $\eta_0$ under the bijection of Lemma \ref{lemma:morphism_out_1}.
+It is not meant to be clear \emph{a priori} that these formulas even define morphisms, let alone that they satisfy the axioms for unitors; all these checks will be performed below.
+
+\section{Convolution as a morphism of schemes}
+
+We either fix a basis for Jacobians or assume $k$ a field so we can use Grobner.
+
+\begin{itemize}
+\item Restate hmf as matrices
+\item Do idempotent completion as matrices with chosen homotopies
+\item Do Clifford thickening as matrices with chosen homotopies
+\item Write down the morphism of schemes
+\end{itemize}
+
+% This is the definition from cutsys10
+\begin{definition} A \emph{cut system} $\cat{A}$ is determined by the following data:
+\begin{itemize}
+\item A class $|\cat{A}|$ of objects and for each object $a$ an integer $\pi(a) \ge 0$.
+\item For each pair $a,b$ of objects a small idempotent complete supercategory $\cat{A}(a,b)$. 
+\item For each triple $a,b,c$ of objects a cut functor of degree $\pi(b)$
+\[
+T: \cat{A}(a,b) \otimes_k \cat{A}(b,c) \lto \cat{A}(a,c)^{\bullet}\,.
+\]
+The image of a pair $X \otimes Y$ under the canonical extension
+\[
+\widetilde{T}: \cat{A}(a,b)^\bullet \otimes_k \cat{A}(b,c)^\bullet \lto \cat{A}(a,c)^\bullet
+\]
+is denoted $Y \l X$ and is called the \emph{cut of $Y$ and $X$ along $b$}.
+\item For each object $a$, an object $\Delta_a \in \cat{A}(a,a)$.
+\item For objects $a,b,c,d$ a natural isomorphism $\alpha$ as shown below:
+\[
+\xymatrix@C+2pc{
+\cat{A}(a,b) \times \cat{A}(b,c) \times \cat{A}(c,d) \ar[d]_-{T \times 1} \ar[r]^-{1 \times T} & \cat{A}(a,b) \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\alpha}\\
+\cat{A}(a,c)^\bullet \times \cat{A}(c,d) \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
+}
+\]
+That is, for $X \in \cat{A}(a,b), Y \in \cat{A}(b,c), Z \in \cat{A}(c,d)$ an isomorphism
+\[
+\alpha_{Z,Y,X}: ( Z \l Y ) \l X \lto Z \l ( Y \l X )
+\]
+of $A_{\pi(b)} \otimes_k A_{\pi(c)}$-modules in $\cat{A}(a,d)$, natural in all three variables.
+\item For objects $a,b$ natural isomorphisms $\mu, \eta$ as shown below:
+\[
+\xymatrix@C+2pc{
+1 \times \cat{A}(a,b) \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b) \ar@{=>}@<4ex>[l]_-{\eta} \ar@{=>}@<-4ex>[r]^-{\mu} \ar[d]^-{\iota} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b) \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
+\cat{A}(a,a) \times \cat{A}(a,b) \ar[r]_-{T} & \cat{A}(A,B)^\bullet & \cat{A}(a,b) \times \cat{A}(b,b) \ar[l]^-{T}
+}
+\]
+where $1$ is the category with one object and one morphism and $\iota_{\Delta}$ is the functor sending this object to $\Delta$. That is, for each $X \in \cat{A}(a,b)$ a pair of isomorphisms
+\begin{equation}\label{eq:defn_cutsys_lambda}
+\mu: X \lto \Delta_b \l X, \quad \eta: X \lto X \l \Delta_a
+\end{equation}
+in $\cat{A}(a,b)^\bullet$ natural in $X$.
+\end{itemize}
+This data is subject to the following coherence conditions:
+\begin{itemize}
+\item[(1)] For objects $a,b,c,d,e$ and $X \in \cat{A}(a,b),Y \in \cat{A}(b,c),Z \in \cat{A}(c,d),Q \in \cat{A}(d,e)$, commutativity of the diagram
+\begin{equation}
+\xymatrix@C+2pc{
+((Q \l Z) \l Y ) \l X \ar[d]_-{\alpha_{Q \l Z, Y, X}}\ar[r]^-{\alpha_{Q,Z,Y} \l 1} & (Q \l (Z \l Y)) \l X \ar[r]^-{\alpha_{Q, Z \l Y, X}} & Q \l ( ( Z \l Y ) \l X ) \ar[d]^-{1 \l \alpha_{Z,Y,X}}\\
+(Q \l Z) \l (Y \l X) \ar[rr]_-{\alpha_{Q, Z, Y \l X}} & & Q \l ( Z \l ( Y \l X ) )
+}
+\end{equation}
+Note that when we write $\alpha_{Q, Z \l Y, X}$ we refer only the underlying object of $Z \l Y$.
+\item[(2)] For objects $a,b$ and $X \in \cat{A}(a,b), Y \in \cat{A}(b,c)$ commutativity of the diagram
+\begin{equation}\label{eq:unitor_constraint_cut}
+\xymatrix{
+(Y \l \Delta_b ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
+& Y \l X \ar[ul]^-{\eta \l 1_X} \ar[ur]_-{1_Y \l \mu}
+}
+\end{equation}
+\item[(3)] commutativity of \eqref{eq:psiunitor1},\eqref{eq:psiunitor2} for every $X$ and \eqref{eq:psithirdlastdia}, \eqref{eq:psimiddledia}, \eqref{eq:psilastdia} for every composable triple $X,Y,Z$.
+\end{itemize}
+%Finally, the data is subject to three computability conditions:
+%\begin{itemize}
+%\item[(1)] For each pair of objects $a,b$ the category $\cat{A}(a,b)$ is effectively computable, in the sense that the morphisms and objects are described by finite data and the composition rule is computable.
+%\item[(2)] For each triple $a,b,c$ of objects the associated cut functor is effectively computable.
+In particular, for $1$-morphisms $Y$ and $X$ the object $Y \l X$ and its Clifford action are effectively computable from $X$ and $Y$.
+%\item[(3)] The associators and unitors are effectively computable from their arguments.
+%\end{itemize}
+\end{definition}
+
+Let $\cat{A}$ be a cut system.
+There is a superbicategory $\cat{A}^\bullet$ with objects the class of objects of $\cat{A}$ and with $1$- and $2$-morphisms defined by $\cat{A}^\bullet(a,b) = \cat{A}(a,b)^\bullet$.
+The units of $\cat{A}^\bullet$ are the objects $\Delta_a$ in the cut system, and the composition in the bicategory is given by the canonical extensions $\widetilde{T}$.
+To complete the definition of a superbicategory it only remains to give the associators and unitors, and the super-structure.
+
+\begin{lemma} Given objects $a,b,c,d$ the natural isomorphism $\alpha$ canonically extends to a natural isomorphism $\widetilde{\alpha}$ as in the diagram
+\[
+\xymatrix@C+2pc{
+\cat{A}(a,b)^\bullet \times \cat{A}(b,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[d]_-{\widetilde{T} \times 1} \ar[r]^-{1 \times \widetilde{T}} & \cat{A}(a,b)^\bullet \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\widetilde{\alpha}}\\
+\cat{A}(a,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
+}
+\]
+\end{lemma}
+\begin{proof}
+Suppose $(X,n) \in \cat{A}(a,b)^\bullet, (Y,m) \in \cat{A}(b,c)^\bullet$ and $(Z,t) \in \cat{A}(c,d)^\bullet$ are given.
+The underlying object of $((Z,t) \l (Y, m)) \l (X,n)$ is $(Z \l Y) \l X$, and it is clear that $\alpha_{Z,Y,X}$ is $A_t \otimes A_m \otimes A_n$-linear and therefore defines an isomorphism in $\cat{A}(a,d)^\bullet$
+\[
+\alpha_{Z,Y,X}: ((Z,t) \l (Y, m)) \l (X,n) \lto (Z,t) \l ((Y, m) \l (X,n))\,.
+\]
+Naturality is straightforward.
+\end{proof}
+
+\begin{lemma} Given objects $a,b$ the natural isomorphisms $\eta, \mu$ canonically extend to natural isomorphisms $\widetilde{\eta}, \widetilde{\mu}$ as in the diagram
+\[
+\xymatrix@C+2pc{
+1 \times \cat{A}(a,b)^\bullet \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b)^\bullet \ar@{=>}@<4ex>[l]_-{\widetilde{\eta}} \ar@{=>}@<-4ex>[r]^-{\widetilde{\mu}} \ar[d]^-{1} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b)^\bullet \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
+\cat{A}(a,a)^\bullet \times \cat{A}(a,b)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(A,B)^\bullet & \cat{A}(a,b)^\bullet \times \cat{A}(b,b)^\bullet \ar[l]^-{\widetilde{T}}
+}
+\]
+ \end{lemma}
+\begin{proof}
+Let $(X,n) \in \cat{A}(a,b)^\bullet$.
+Forgetting the $A_n$-action on $X$, we have isomorphisms $\eta$ and $\mu$ as in \eqref{eq:unitor_tilde_pre}, which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.
+Since these isomorphisms are natural, they are automatically $A_n$-linear.
+Verifying that these isomorphisms are natural with respect to the larger class of morphisms in $\cat{A}(a,b)^\bullet$ is straightforward.
+\end{proof}
+
+The supercategory structure is given as part of the cut system, so we have:
+
+% The above definition of a cut system is from cutsys10. This is by p.11 there something which gives rise to a cut system in the sense of cutsys6, which is proved there to define a superbicategory.
+\begin{proposition} Given a cut system $\cat{A}$, $\cat{A}^\bullet$ is a superbicategory.
+\end{proposition}
+\begin{proof}
+This follows from Lemma \ref{lemma:constructingsuper}, with associator $\widetilde{\alpha}$ and unitors $\lambda =\widetilde{\mu}^{-1}, \rho = \widetilde{\eta}^{-1}$.
+The coherence follows from the coherence axioms of the cut system.
+\end{proof}
+
+We often confuse a cut system $\cat{A}$ with the associated superbicategory.
+For example, we refer to objects $X$ of $\cat{A}(a,b)^\bullet$ as a $1$-morphisms.
+To distinguish objects of the original category $\cat{A}(a,b)$ we refer to these objects as \emph{normal} or \emph{cut-free} $1$-morphisms.
+We keep the notation $Y \l X$ for the composition rule in $\cat{A}^\bullet$.
+
+The following lemma is useful in verifying the unitor constraint.
+
+\begin{lemma}\label{lemma:unitor_check_help} The commutativity of \eqref{eq:unitor_constraint_cut} is equivalent to commutativity of
+\begin{equation}\label{eq:unitor_check_help1}
+\xymatrix@C+1pc{
+(Y \l \Delta_b) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
+Y \l X \ar[u]^-{\eta_0 \l 1} & Y \l X \ar[l]^-{e_{\pi(b)}} \ar[r]_-{e_{\pi(b)}} & Y \l X \ar[u]_-{1 \l \mu_0}
+}
+\end{equation}
+where $e_{\pi(b)}$ is the idempotent of Definition \ref{defn:idempotent_e}.
+\end{lemma}
+\begin{proof}
+Let $m = \pi(b)$.
+Then $(Y \l \Delta_b) \l X$ has two $A_m$ actions, one from $Y \l \Delta_b$ which we denote by $A_{m_1}$, and the other from the cut with $X$ which we denote by $A_{m_2}$.
+By definition of the canonical extension $\widetilde{T}$ in Appendix \ref{app:proof_cut_extension}, $\eta \l 1$ is the $A_{m_1+m_2}$-linear morphism
+\[
+\eta: S_{m_1 + m_2, m_2} \otimes_{A_{m_2}} ( Y \l X ) \lto (Y \l \Delta_b ) \l X
+\]
+which corresponds under Lemma \ref{lemma:morphisms_two_forms} to
+\[
+\xymatrix@C+1pc{
+Y \l X \ar[r]^-{e_m} & Y \l X \ar[r]^-{\eta_0 \l 1} & (Y \l \Delta_b) \l X
+}\,.
+\]
+Applying the same logic to $\mu$ completes the proof.
+\end{proof}
+
+In a cut system the unitors $\mu, \eta$ go in the opposite direction to what one would expect from the conventions of bicategories.
+This is because it is more natural to describe morphisms out of a cut-free $1$-morphism and into a $1$-morphism carrying a nontrivial Clifford representation, than in the other direction.
+
+\begin{proof}[Proof of Theorem \ref{theorem:l_cut_system}] We first check the coherence axioms.
+The first and third are trivial.
+To prove (2) we need by Lemma \ref{lemma:unitor_check_help} only check commutativity of \eqref{eq:unitor_check_help1} in the usual situation of $X: W \lto V$ and $Y: V \lto U$.
+
+This amounts to checking commutativity of
+\begin{equation}\label{eq:coherence3_1}
+\xymatrix{
+(Y \l \Delta_V ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_V \l X )\\
+(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
+Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes J_V \otimes X \ar[l]^-{e_m} \ar[r]_-{e_m} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
+}\,.
+\end{equation}
+By definition $e_m$ factors as
+\[
+\xymatrix{
+Y \l X \ar[r]^-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X ) \ar[r] & Y \otimes X \ar[r] & S_m \otimes_k (Y \otimes X) \ar[r]^-{\Phi} & Y \l X
+}
+\]
+so commutativity of \eqref{eq:coherence3_1} follows from commutativity of
+\[
+\xymatrix@C-0.5pc{
+(Y \l \Delta_V ) \l X \ar[rrr]^-{\alpha} & & & Y \l ( \Delta_V \l X )\\
+(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & (Y \otimes \Delta_V ) \otimes X \ar[l]_-{\varrho} \ar[r]^-{\alpha} & Y \otimes (\Delta_V \otimes X) \ar[r]^-{\varrho} & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
+Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes X \ar[u]^-{\rho^{-1} \otimes 1} \ar@{=}[r] \ar[l]^-{\varrho} & Y \otimes X \ar[u]_-{1 \otimes \lambda^{-1}} \ar[r]_-{\varrho} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
+}\,.
+\]
+The innermost square of this diagram is the coherence constraint for the unitors in $\LG$.
+
+%Finally, we check the computability conditions.
+The associator and unitors are derived explicitly from $d_X$ and $d_Y$, so (3) is clear, and (2) is addressed by Remark \ref{remark:inflation} and the explicit formulas for the Clifford action.
+For (1), the objects and morphisms of $\cat{L}(W,V)$ are described by finite matrices of polynomials, and the composition rule is given by multiplication of matrices.
+There is one subtlety: morphisms are matrices of polynomials \emph{identified up to homotopy}.
+
+%To argue that $\cat{L}(W,V)$ is effectively computable we need to show that it is possible to determine algorithmically whether two morphisms are homotopic.
+This is important even at the level of objects: an object is a pair $(X,e)$ where $e^2 = e$ holds up to homotopy.
+Without an effective homotopy relation, there would be no algorithmic way to even distinguish between objects and non-objects.
+The necessary check is in Section \ref{example:computing_homs}.
+\end{proof}
+
+We will use \emph{effectively computable} as a synonym for the precise notion of a \emph{computable} function \cite{enderton}, since ``computable'' often has a more colloquial meaning in our context.
+
+\begin{remark} To give natural isomorphisms \eqref{eq:defn_cutsys_lambda} in $\cat{A}(a,b)^\bullet$ is equivalent to giving natural isomorphisms in $\cat{A}(a,b)$
+\begin{equation}\label{eq:unitor_tilde_pre}
+\mu: S_{\pi(b)} \otimes_k X \lto \Delta_b \l X, \quad \eta: S_{\pi(a)} \otimes_k X \lto X \l \Delta_a
+\end{equation}
+which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.
+
+By Lemma \ref{lemma:morphism_out_1} such morphisms correspond bijectively to morphisms in $\cat{A}(a,b)$
+\begin{equation}\label{eq:unitor_tilde}
+\mu_0: X \lto \Delta_b \l X, \quad \eta_0: X \lto X \l \Delta_a
+\end{equation}
+satisfying respectively $a_i^\dagger \circ \mu_0 = 0$ for $1 \le i \le m$ and $a_i^\dagger \circ \eta_0 = 0$ for $1 \le i \le n$.
+The reason to introduce these maps is that commutativity of \eqref{eq:unitor_constraint_cut} can be more conveniently expressed in terms of the maps in \eqref{eq:unitor_tilde}, see Lemma \ref{lemma:unitor_check_help} below.
+\end{remark}
+
+\subsection{Cut models}\label{section:cut_models}
+
+\begin{definition} A \emph{cut model} for a superbicategory $\cat{B}$ is a cut system $\cat{A}$ with the same underlying class of objects as $\cat{B}$ and a strong superfunctor $I: \cat{B} \lto \cat{A}^\bullet$ with the property that for every pair of objects $a,b$ the functor
+\[
+I_{a,b}: \cat{B}(a,b) \lto \cat{A}(a,b)^\bullet
+\]
+factors as
+\[
+\xymatrix{
+\cat{B}(a,b) \ar[rr]^-{I_{a,b}} \ar[dr]_-{J_{a,b}} & & \cat{A}(a,b)^\bullet\\
+& \cat{A}(a,b) \ar[ur]_-{\iota}
+}
+\]
+where $J_{a,b}$ is an equivalence of supercategories. We often identify $X$ with $I(X)$.
+\end{definition}
+
+A cut model is an effectively computable model for composition of $1$-morphisms in~$\cat{B}$.
+Given $X: a \lto b$ and $Y: b \lto c$, let us suppose that the composition $Y \circ X$ in $\cat{B}$ is not defined algorithmically: perhaps this object is only identified up to unique isomorphism by a universal property.
+In contrast, the cut $Y \l X$ is computable from $X$ and $Y$, and the strong superfunctor $I$ provides an isomorphism in $\cat{A}(a,c)^\bullet$
+\begin{equation}
+Y \l X \cong Y \circ X\,.
+\end{equation}
+Here $Y \circ X$ is embedded into $\cat{A}^\bullet$ as a cut-free $1$-morphism and the cut $Y \l X$ by definition comes with an $A_{\pi(b)}$-module structure.
+That is, there is an isomorphism of $A_{\pi(b)}$-modules
+\begin{equation}\label{eq:cutvsoriginal}
+Y \l X \cong S_{\pi(b)} \otimes_k (Y \circ X )
+\end{equation}
+or what is the same, an isomorphism of objects in $\cat{A}(a,b)$
+\begin{equation}\label{eq:cutvsoriginal2}
+S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X ) \cong Y \circ X \,.
+\end{equation}
+The general philosophy is that a cut model decomposes composition in $\cat{B}$ into two stages: 
+\begin{itemize}
+\item first form the cut $Y \l X$, and then
+\item tensor $Y \l X$ with $S^*_{\pi(b)}$ to compute $Y \circ X$. 
+\end{itemize}
+The idea is that the desired composition $Y \circ X$ lies inside $Y \l X$ in a way that is ``known'' in the sense that it is encoded by the Clifford action, but which is only \emph{realised} or \emph{constructed} after a computation is done.
+Forming the tensor product $S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ starting with the concretely known object $Y \l X$ can be further decomposed into a $\pi(b)$-step process of ``atomic'' computations, using the diagram of Remark \ref{remark:tensor_and_idempotent}
+\begin{equation}\label{eq:computation_fiber_diagram}
+\xymatrix@C+1pc@R+1pc{
+Z_0 \cong Y \circ X \ar@{.}[d] & Z_1 \ar@{.}[d] & & Z_{\pi(b)-1} \ar@{.}[d] & Z_{\pi(b)} = Y \l X \ar@{.}[d]\\
+0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b)-1  \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b) \ar@{.>}@<0.8ex>[l]
+}\,.
+\end{equation}
+% remark:tensor_in_steps.
+The intermediate objects are $Z_i = S_{i, \pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ for $i < \pi(b)$.
+Each of these objects $Z_i$ is obtained from $Z_{i+1}$ by splitting an idempotent of the form $a^\dagger a$.
+
+Suppose we are in the situation where $Y \circ X$ is identified by a universal property but an explicit object realising this universal property is not given as part of $\cat{B}$.
+Then the result of the $\pi(b)$-step computation depicted above is an explicit object $Z_0$ of $\cat{A}(a,c) \cong \cat{B}(a,c)$ with this universal property.
+Thus the cut system gives a process for constructing representing objects for the uniquely defined isomorphism class $Y \circ X$ of $\cat{B}(a,c)$.
+
+Conceptually, the number of steps in \eqref{eq:computation_fiber_diagram} represents the computational cost of a cut across the object $b$.
+For any cut across this object, $\pi(b)$-steps are necessary to convert the ``uncertainty'' represented by $Y \l X$ with its $A_{\pi(b)}$-action to the certainty of an object of $\cat{A}(a,c)$ (in the sense of Remark \ref{remark:tensor_and_idempotent}).
+In the example of the next section, the cost $\pi(W)$ of cutting across a hypersurface singularity $W$ is determined by its dimension.
+
+\section{Cut systems}\label{section:cut_systems}
+
+We begin with the definition of cut functors.
+
+\begin{definition} Given supercategories $\cat{C}_1,\cat{C}_2,\cat{C}_3$ a \emph{superfunctor} $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3$ is a functor together with natural isomorphisms
+\begin{align*}
+\tau &: T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T,\\
+\tau &: T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
+\end{align*}
+making the following diagrams commute:
+\begin{equation}\label{eq:psicomp1}
+\xymatrix@R+1pc@C+1pc{
+T( 1 \otimes \Psi^2 ) \ar[r]^-{\tau}\ar[d]_-{T(1 \otimes \xi)} & \Psi T( 1 \otimes \Psi ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
+T \ar[rr]_-{1_T} & & T
+}
+\end{equation}
+\begin{equation}\label{eq:psicomp2}
+\xymatrix@R+1pc@C+1pc{
+T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\psi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
+T \ar[rr]_-{1_T} & & T
+}
+\end{equation}
+\begin{equation}\label{eq:psicomp3}
+\xymatrix@R+1pc@C+1pc{
+T( \Psi \otimes \Psi ) \ar[r]^-{\tau}\ar[d]_-{-\tau} & \Psi T( 1 \otimes \Psi ) \ar[d]^-{\tau}\\
+\Psi T( \Psi \otimes 1 ) \ar[r]_-{\tau} & \Psi^2 T
+}
+\end{equation}
+
+\end{definition}
+
+\begin{definition}\label{defn:cutfunctor1} A \emph{cut functor of degree $t$} on a triple $\cat{C}_1, \cat{C}_2,\cat{C}_3$ of idempotent complete small supercategories is a superfunctor $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3^\bullet$ such that
+\[
+\xymatrix{
+\cat{C}_1 \times \cat{C}_2 \ar[r]^-{T} & \cat{C}_3^\bullet \ar[r]^-{p} & \mathbb{N}
+}
+\]
+sends every object to the integer $t \in \mathbb{N}$.
+\end{definition}
+
+With the above notation:
+
+\begin{proposition}\label{prop:extend_cut_functor} Given a cut functor $T$ of degree $t$ on $\cat{C}_1, \cat{C}_2,\cat{C}_3$ there is a canonical superfunctor $\widetilde{T}: \cat{C}_1^\bullet \otimes_k \cat{C}_2^\bullet \lto \cat{C}_3^\bullet$ with the property that the diagram
+\[
+\xymatrix{
+\cat{C}_1 \times \cat{C}_2 \ar[dr]_-{\iota \times \iota} \ar[rr]^-{T} & & \cat{C}_3^\bullet\\
+& \cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[ur]_-{\widetilde{T}}
+}
+\]
+commutes, and for every pair of objects $X \in \cat{C}_1^\bullet$ and $Y \in \cat{C}_2^\bullet$
+\[
+p \widetilde{T}( X, Y ) = p( X ) + p( Y ) + t\,.
+\]
+We refer to $\widetilde{T}$ as the \emph{extension} of $T$.
+%and
+%\[
+%\xymatrix@C+2pc{
+%\cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[d]_-{p \times p}\ar[rr]^-{\widetilde{T}} & & \cat{C}_3^\bullet \ar[dd]^-{p}\\
+%\mathbb{N} \times \mathbb{N} \ar[d]_-{\cong}\\
+%\mathbb{N} \times \{ * \} \times \mathbb{N} \ar[r]_-{1 \times t \times 1} & \mathbb{N} \times \mathbb{N} \times \mathbb{N} \ar[r]_-{\otimes} & \mathbb{N}
+%}
+%\]
+%commute. 
+\end{proposition}
+\begin{proof}
+The proof is given in Appendix \ref{app:proof_cut_extension}.
+\end{proof}
+
+\section{Extending cut functors}\label{app:proof_cut_extension}
+
+The purpose of this appendix is to give the proof of Proposition \ref{prop:extend_cut_functor}. First, note that
+
+\begin{lemma}\label{lemma:altcomppersp} Let $\cat{C}$ be a small idempotent complete supercategory and take morphisms
+\[
+\xymatrix{
+(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
+}\\
+\]
+in $\cat{C}^\bullet$. Under \eqref{eq:isodefatensor} these correspond to bimodule maps
+\[
+\widetilde{\alpha}: S_{m,n} \lto \cat{C}^*(X,Y)\,, \qquad \widetilde{\beta}: S_{l,m} \lto \cat{C}^*(Y,Z)\,.
+\]
+The composite $\beta \circ \alpha: S_{l,n} \otimes_{A_n} X \lto Z$ in $\cat{C}^\bullet$ corresponds to the composite
+\[
+\xymatrix{
+S_{l,n} \cong S_{l,m} \otimes_{A_m} S_{m,n} \ar[r]^-{\widetilde{\beta} \otimes \widetilde{\alpha}} & \cat{C}^*(Y,Z) \otimes_{A_m} \cat{C}^*(X,Y) \ar[r]^-{\circ} & \cat{C}^*(X,Z)
+}\,.
+\]
+\end{lemma}
+\begin{proof}
+Follows by evaluation on $1 \otimes 1^* \in S_{l,n}$.
+\end{proof}
+
+\begin{proof}[Proof of Proposition \ref{prop:extend_cut_functor}]
+Given $(X,n) \in \cat{C}_1^\bullet$ and $(Y,m) \in \cat{C}_2^\bullet$ we have $T(X,Y) = (Z,t)$ for some object $Z$ of $\cat{C}_3$.
+Given $a \in A_n$, say of odd degree, there is a morphism of $A_t$-modules $Z \lto \Psi Z$ given by
+\[
+\xymatrix@C+2pc{
+T(X,Y) \ar[r]^-{T(a \otimes 1)} & T(\Psi X, Y ) \ar[r]^-{\tau} & \Psi T(X,Y)
+}
+\]
+and this defines an algebra morphism $A_n \lto \cat{C}_3^*(Z,Z)$.
+Doing the same for $A_m$ defines a morphism $A_{m+t+n} \cong A_m \otimes A_t \otimes A_n \lto \cat{C}_3^*(Z,Z)$ and an object $(Z, m + t +n) \in \cat{C}_3^\bullet$.
+We define $\widetilde{T}$ on objects by
+\begin{equation}\label{eq:ttilde}
+\widetilde{T}( (X,n), (Y,m) ) = (Z, m + t + n)\,.
+\end{equation}
+Next we define $\widetilde{T}$ on morphisms. Given $\alpha: (X_1,n_1) \lto (X_2,n_2)$ in $\cat{C}_1^\bullet$ and $T(X_i,Y) = (Z_i,t)$ for $i = 1,2$ we must construct a morphism
+\[
+\widetilde{T}(\alpha,1): (Z_1, m+t+n_1) \lto (Z_2, m+t+n_2)\,.
+\]
+Since $\alpha$ corresponds to an $A_{n_1}$-linear map $\widetilde{\alpha}: V \lto \cat{C}_1^*(X_1,X_2)$ we can compose with $T$ to get an $A_{n_2}$-$A_{n_1}$-bilinear map $\eta := T(1,Y) \circ \widetilde{\alpha}: V \lto \cat{C}_3^*(Z_1,Z_2)$.
+This extends to a morphism of $A_{n_2+c}$-$A_{n_1+c}$-bimodules
+\[
+V \otimes_k A_c \lto \cat{C}_3^*(Z_1,Z_2), \qquad v \otimes a \mapsto \eta(v) a\,.
+\]
+There is a canonical isomorphism of $A_{n+2+c}$-$A_{n_1+c}$-bimodules
+\begin{align*}
+S_{n_2+c,n_1+c} \cong S_{n_2+c} \otimes_k S_{n_1+c}^* \cong (S_{n_2} \otimes_k S_c) \otimes_k (S_c^* \otimes_k S_{n_1}^*) \cong V \otimes_k (S_c \otimes_k S_c^*) \cong V \otimes_k A_c
+\end{align*}
+so we have constructed $S_{n_2+c,n_1+c} \lto \cat{C}_3^*(Z_1,Z_2)$ which corresponds to a morphism of $A_{n_2+c}$-modules $S_{n_2+c, n_1+c} \otimes_{A_{n_1+c}} Z_1 \lto Z_2$ which we define to be $\widetilde{T}(\alpha,1)$.
+Functoriality of this construction follows from Lemma \ref{lemma:altcomppersp}.
+The functoriality in the other variable follows similarly.
+By construction $\widetilde{T}$ makes both of the required diagrams commute.
+\end{proof}
+
+\subsection{The cut model of $\LG$}
+
+Let $\cat{L}$ be the cut system described above, and let $\cat{L}^\bullet$ denote the associated superbicategory.
+With $\LG$ the superbicategory of Section \ref{section:superbicatLG} we construct a cut model $I: \LG \lto \cat{L}^\bullet$.
+On objects $I$ is the identity.
+For potentials $V,W$ we need to define a functor
+\begin{equation}\label{eq:cut_model_equiv}
+I_{V,W}: \LG(W,V) \lto \cat{L}^\bullet(W,V)\,.
+\end{equation}
+Recall that with $\cat{C} = \hmf(k[x,z], V - W)$,
+\[
+\cat{L}^\bullet(W,V) = \cat{C}^{\omega \bullet}\,, \quad \LG(W,V) = \cat{C}^{\oplus}\,.
+\]
+An object of $\cat{C}^{\omega \bullet}$ is a tuple $((X,e), n)$ consisting of an integer $n \ge 0$ and an $A_n$-module $(X,e)$ in $\cat{C}^\omega$, while an object of $\cat{C}^{\oplus}$ is a (possibly infinite) matrix factorisation of $V - W$ which is a direct summand of a finite rank one.
+
+On the full subcategory of finite rank matrix factorisation of $V - W$, $I_{V,W}$ is the identity and this functor extends uniquely (up to natural equivalence) to $\LG(W,V)$.
+To be more explicit about it: for each $X \in \LG(W,V)$ we \emph{choose} a finite rank matrix factorisation $\bar{X}$ together with an idempotent $e$ and morphisms $f_X, g_X$ as in the diagram
+\[
+\xymatrix@C+2pc{
+\bar{X} \ar@(ul,dl)_-{e} \ar@<1ex>[r]^-{f_X} & X \ar@<1ex>[l]^-{g_X}
+}
+\]
+satisfying $g_X f_X = e$ and $f_X g_X = 1_X$. Then the full definition of $I$ is given by
+\[
+I( X ) = ((\bar{X}, e), 0)\,, \qquad I( \phi ) = g_Y \phi f_X\,.
+\]
+To complete the definition of a strong functor $I$ it remains to give a natural $2$-isomorphism
+\begin{equation}\label{eq:strong_functor_varphi}
+\varphi: I(Y \otimes X) \lto I(Y) \l I(X)
+\end{equation}
+for every pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ in $\LG$.
+
+We give the definition of $\varphi$ where $X,Y$ are finite rank matrix factorisations; the general case follows. Recall the $A_m$-linear isomorphism of Proposition \ref{prop:final_homotopy_equiv_cut}
+\begin{equation}\label{eq:cutmodelequiv}
+\xymatrix@C+4pc{
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
+}\,.
+\end{equation}
+% TODO issue with completion
+This is essentially the desired natural isomorphism $\varphi$, and it is only necessary to package it a little more carefully.
+Let $e = e_m \in A_m$ denote the idempotent from Definition \ref{defn:idempotent_e}.
+If we define $\nu: S_m \lto k$ to be the projection onto $k \cdot 1$ then there is a diagram
+\[
+\xymatrix@C+4pc{
+Y \l X \ar@<1ex>[r]^-{\nu \Phi^{-1}} & Y \otimes X \ar@<1ex>[l]^-{\varrho}
+}
+\]
+expressing $Y \otimes X$ as the splitting of the idempotent $e$ on $Y \l X$.
+Here $\varrho: Y \otimes X \lto Y \l X$ is the quotient map.
+The usphot is that as objects of $\cat{L}(W,V)^{\omega \bullet}$
+\[
+I(Y \otimes X) = ((Y\l X, e), 0), \qquad I(Y) \l I(X) = ( (Y \l X, 1), m )\,.
+\]
+Morphisms $\varphi$ as in \eqref{eq:strong_functor_varphi} are in bijection with morphisms
+\[
+\varphi_0: (Y \l X, e) \lto (Y\l X, 1)
+\]
+in $\hmf(k[x,z], U - W)^{\omega}$ satisfying $\theta_i^* \circ \varphi_0 = 0$ for $1 \le i \le m$.
+The endomorphism $\varphi_0 = e_m$ of $Y \l X$ fits the bill.
+In the category of infinite rank matrix factorisations, $\varphi_0$ is just the morphism $\varrho$.
+It follows that $\varphi$ is a natural isomorphism, since it corresponds to $\Phi$.
+
+\begin{theorem} The data $(I, \varphi)$ defines a cut model $\LG \lto \cat{L}^\bullet$.
+\end{theorem}
+\begin{proof}
+Once we have shown that $(I, \varphi)$ is a strong functor it is clearly ``super'', and by construction it defines a cut model.
+There are two coherence conditions: the first is commutativity of the following diagram, in the context of a composable triple as in \eqref{eq:composable_triple}:
+\begin{equation}\label{eq:dia_coherence1}
+\xymatrix@C+2pc{
+(I(Z) \l I(Y) ) \l I(X) \ar[r]^-{\alpha} \ar[d]_-{\varphi \l 1} & I(Z) \l ( I(Y) \l I(X) ) \ar[d]^-{1 \l \varphi} \\
+I(Z \otimes Y) \l I(X) \ar[d]_-{\varphi} &  I(Z) \l I(Y \otimes X)\ar[d]^-{\varphi}\\
+I( (Z \otimes Y) \otimes X ) \ar[r]_-{I(\alpha)} & I(Z \otimes (Y \otimes X))
+}
+\end{equation}
+The key to checking this lies in understanding what $I( Z \otimes (Y \otimes X) )$ is.
+But as we have argued above, $Y \otimes X$ is a summand of $Y \l X$ with idempotent $e_m$ while $Z \otimes ( Y \l X )$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p$.
+This implies that $Z \otimes (Y \otimes X)$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p e_m = e_m e_p = e_{m+p}$, so
+\[
+I( (Z \otimes Y) \otimes X ) = ( Z \l (Y \l X), e_{m+p} ), \quad I( Z \otimes (Y \otimes X) ) = ( (Z \l Y) \l X, e_{m+p} )\,.
+\]
+Then commutativity of \eqref{eq:dia_coherence1} reduces to commutativity in $\hmf(Q - W)^{\omega}$ of
+\[
+\xymatrix@C+2pc{
+( (Z \l Y ) \l X, 1 ) \ar[r]^-{\alpha} & ( Z \l (Y \l X ), 1)\\
+( (Z \l Y) \l X, e_p \l 1) \ar[u]^-{e_p \l 1} & ( Z \l (Y \l X), 1 \l e_m) \ar[u]_-{e_m}\\
+( (Z \l Y) \l X, e_{m+p} ) \ar[u]^-{e_{m+p}} \ar[r]_-{e_{m+p}} & ( Z \l (Y \l X), e_{m+p} ) \ar[u]_-{e_{m+p}}
+}
+\]
+which is clear.
+\end{proof}
+
+\section{Constructing superbicategories}\label{section:constructing_superbicategories}
+
+This appendix collects the data needed for constructing a superbicategory $\cat{B}$ from a collection of supercategories $\cat{B}(a,b)$.
+Given a bicategory $\cat{B}$ and for each pair of objects $a,b$ the structure of a supercategory on $\cat{B}(a,b)$, we denote composition by
+\[
+T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
+\]
+We assume this is a superfunctor, i.e.
+that \eqref{eq:psicomp1}-\eqref{eq:psicomp3} commute.
+Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$.
+We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.
+
+Suppose that for all objects $a,b,c$ we are given natural isomorphisms
+\begin{align*}
+T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T, \qquad T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
+\end{align*}
+both of which will be denoted $\tau$.
+We define for an object $a$ the $1$-morphism $\Psi_a = \Psi( \Delta_a )$ and the $2$-isomorphism $\xi_a$ to be the following composite (using the structure maps of $\cat{B}$ and isomorphisms $\tau$)
+\[
+\xi_a: \Psi_a \l \Psi_a = \Psi( \Delta_a ) \l \Psi( \Delta_a ) \cong \Psi( \Delta_a \l \Psi(\Delta_a ) ) \cong \Psi^2( \Delta_a \l \Delta_a ) \cong \Delta_a \l \Delta_a \cong \Delta_a\,.
+\]
+Similarly given a $1$-morphism $X: a \lto b$ we have a $2$-isomorphism $\gamma_X$
+\[
+\gamma_X: X \l \Psi_a = X \l \Psi( \Delta_a ) \cong \Psi( X \l \Delta_a ) \cong \Psi(X) \cong \Psi( \Delta_b \l X ) \cong \Psi( \Lambda_b ) \l X = \Psi_b \l X\,.
+\]
+Given a $1$-morphism $X: a \lto b$ in $\cat{B}$ there are diagrams
+\begin{gather}
+\xymatrix@R+1pc@C+1pc{
+\Delta_b \l \Psi (X) \ar[dr]_-{\lambda_{\Psi a}} \ar[rr]^-{\tau} & & \Psi( \Delta_b \l X ) \ar[dl]^-{\Psi( \lambda )}\\
+& \Psi(X)
+} \label{eq:psiunitor1}\\
+\xymatrix@R+1pc@C+1pc{
+\Psi(X) \l \Delta_a \ar[rr]^-{\tau}\ar[dr]_-{\rho} & & \Psi( X \l \Delta_a ) \ar[dl]^-{\Psi(\rho)}\\
+& \Psi(X)
+} \label{eq:psiunitor2}
+\end{gather}
+whose commutativity expresses compatibility of the functors $\Psi$ with the units, while for a composable triple $X,Y,Z$ the commutativity of the diagrams
+\begin{gather}
+\xymatrix{
+(Z \l Y) \l \Psi(X) \ar[dd]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( Y \l \Psi(X)) \ar[d]^-{\tau}\\
+ & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
+\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
+} \label{eq:psithirdlastdia}\\
+\xymatrix{
+(Z \l \Psi(Y)) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( \Psi(Y) \l X) \ar[d]^-{\tau}\\
+\Psi( Z \l Y ) \l X \ar[d]_-{\tau} & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
+\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
+} \label{eq:psimiddledia}\\
+\xymatrix{
+(\Psi(Z) \l Y) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & \Psi(Z) \l ( Y \l X ) \ar[dd]^-{\tau}\\
+\Psi(Z \l Y) \l X \ar[d]_-{\tau} & & \\
+\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
+}\label{eq:psilastdia}
+\end{gather}
+expresses compatibility of $\Psi$ with the associator of $\cat{B}$.
+
+\begin{lemma}\label{lemma:constructingsuper}
+Given a bicategory $\cat{B}$ with the structure of a supercategory on $\cat{B}(a,b)$ for all pairs $a,b$, and natural isomorphisms $\tau$, suppose that \eqref{eq:psiunitor1}-\eqref{eq:psilastdia} commute.
+Then with $\Psi, \xi$ and $\gamma$ defined as above, $\cat{B}$ is a superbicategory.
+\end{lemma}
+\begin{proof}
+The proof is an easy but somewhat lengthy exercise, which we omit.
+\end{proof}
+
+\subsection{Supercategories}
+
+A superbicategory has for every $1$-morphism $F$ an associated $1$-morphism $\Psi F$ with $\Psi^2 \cong 1$, and in this sense the categories of $1$-morphisms are $\mathbb{Z}_2$-graded.
+The bicategory of Landau-Ginzburg models is an example of a superbicategory.
+Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role in the definition of cut systems, superbicategories are the natural language.
+Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.
+
+\begin{definition} A \emph{supercategory} is a category $\cat{C}$ together with a functor $\Psi: \cat{C} \lto \cat{C}$ and a natural isomorphism $\xi: \Psi^2 \lto 1_{\cat{C}}$ satisfying the condition
+\[
+\xi * 1_{\Psi} = 1_{\Psi} * \xi
+\]
+as natural transformations $\Psi^3 \lto \Psi$.
+A \emph{superfunctor} $(F, \gamma)$ from a supercategory $(\cat{C}, \Psi_{\cat{C}})$ to a supercategory $(\cat{D}, \Psi_{\cat{D}})$ is a functor $F: \cat{C} \lto \cat{D}$ together with a natural isomorphism $\gamma: F \Psi_{\cat{C}} \lto \Psi_{\cat{D}} F$ satisfying
+\[
+1_F * \xi = (\xi * 1_F ) ( 1_{\Psi} * \gamma ) ( \gamma * 1_{\Psi} )\,.
+\]
+A \emph{supernatural transformation} $\varphi: F \lto G$ between superfunctors $(F,\gamma_F), (G,\gamma_G)$ is a natural transformation making the following diagram commute:
+\[
+\xymatrix{
+F \Psi \ar[r]^-{\varphi \Psi}\ar[d]_-{\gamma_F} & G \Psi \ar[d]^-{\gamma_G}\\
+\Psi F \ar[r]_-{\Psi \varphi} & \Psi G
+}\,.
+\] 
+\end{definition}
+
+\begin{example}\label{example:Aassup} If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra there is a supercategory $\cat{A}$ with set of objects $|\cat{A}| = \mathbb{Z}_2$ and morphisms $\cat{A}(0,0) = \cat{A}(1,1) = A_0, \cat{A}(0,1) = \cat{A}(1,0) = A_1$ with the obvious composition and addition rules.
+The functor $\Psi$ is defined on objects by $\Psi(i) = i+1$ and on morphisms by the identity, while $\xi = 1$.
+\end{example}
+
+Let $\cat{C}$ be a supercategory. For objects $X,Y \in \cat{C}$ we define the $\mathbb{Z}_2$-graded $k$-module
+\[
+\cat{C}^*(X,Y) = \prod_{i \in \mathbb{Z}_2} \cat{C}(X, \Psi^i Y)\,.
+\]
+There is for any triple $X,Y,Z$ of objects a morphism of graded modules
+\[
+\cat{C}^*(Y,Z) \otimes_k \cat{C}^*(X, Y) \lto \cat{C}^*(X,Z)
+\]
+given for instance by $\varphi \otimes \psi \mapsto \xi \Psi( \varphi ) \psi$ when $\varphi, \psi$ are both of degree one.
+This makes $\cat{C}$ into a category enriched over the monoidal category of $\mathbb{Z}_2$-graded $k$-modules.
+
+There are isomorphisms of graded modules $\cat{C}^*(X, \Psi Y) \cong \Psi \cat{C}^*(X, Y) \cong \cat{C}^*(\Psi X, Y)$ where $\Psi V = V [1]$ denotes the grading shift on a $\mathbb{Z}_2$-graded $k$-module.
+For $\mathbb{Z}_2$-graded $k$-modules $V,W$ we write $\Hom^0_k(V, W)$ for the module of degree zero maps and $\Hom_k^*(V, W)$ for the $\mathbb{Z}_2$-graded module of homogeneous maps.
+If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $A^{\operatorname{op}}$ denotes the same underlying graded module with multiplication $f * g = (-1)^{|f||g|} gf$.
+
+\begin{definition} Let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra and $\cat{C}$ a supercategory.
+A \emph{left $A$-module in $\cat{C}$} is an object $X \in \cat{C}$ together with a morphism of $\mathbb{Z}_2$-graded algebras $A \lto \cat{C}^*(X,X)$.
+A \emph{morphism} of left $A$-modules is a morphism in $\cat{C}$ which commutes with the $A$-action in the obvious sense.
+The category of left $A$-modules in $\cat{C}$ is denoted $\cat{C}_A$.
+Right modules are defined similarly, using $A^{\operatorname{op}}$.
+\end{definition}
+
+\begin{remark}\label{remark:supercat_idempcomp} Viewing $A$ as a supercategory $\cat{A}$ as in Example \ref{example:Aassup}, there is an equivalence between the category of $A$-modules in $\cat{C}$ and the category of superfunctors $\cat{A} \lto \cat{C}$ and supernatural transformations.
+\end{remark}
+
+\begin{remark}\label{remark:idempotent_completion} The \emph{idempotent completion} $\cat{C}^\omega$ of a category $\cat{C}$ has as objects pairs $(X,e)$ consisting of an object $X \in \cat{C}$ and an idempotent endomorphism $e: X \lto X$.
+In $\cat{C}^\omega$ a morphism $\phi: (X,e) \lto (Y,e)$ is a morphism $\phi: X \lto Y$ satisfying $\phi e = \phi$ and $e \phi = \phi$.
+The identity on $(X,e)$ is $e$.
+There is a fully faithful functor $\iota: \cat{C} \lto \cat{C}^{\omega}, \iota(X) = (X,1_X)$ which is an equivalence if $\cat{C}$ is idempotent complete (i.e.
+all idempotents split in $\cat{C}$).
+
+If $\cat{C}$ is a supercategory then there is a functor $\Psi^\omega: \cat{C}^\omega \lto \cat{C}^\omega$ defined on objects by $\Psi(X,e) = (\Psi X, \Psi e)$ and a natural isomorphism $\xi: \Psi^\omega \circ \Psi^\omega \lto 1_{\cat{C}^\omega}$ defined by $\xi_{(X,e)} = e \xi_X$.
+The tuple $(\cat{C}^\omega, \Psi^\omega, \xi^\omega)$ is a supercategory.
+\end{remark}
+
+For background on bicategories see \cite{bor94} and the references in \cite{lgdual}.
+We follow the notation of \cite{lgdual}, so that lower case letters $a,b, \ldots$ denote objects of a bicategory, while upper case letters $X,Y, \ldots$ and greek letters $\alpha, \beta, \ldots$ respectively denote $1$-morphisms and $2$-morphisms.
+Units are denoted $\Delta$, associators are $\alpha$, and unitors are $\lambda, \rho$.
+The composition of $Y,X$ is denoted $YX$ or $Y \circ X$.
+
+\begin{definition} A \emph{superbicategory} is a bicategory $\cat{B}$ together with the data:
+\begin{itemize}
+\item For each object $a$ a $1$-morphism $\Psi_a: a \lto a$ and a $2$-isomorphism $\xi_a: \Psi^2_a \lto \Delta_a$.
+\item For each $1$-morphism $X: a \lto b$ a natural $2$-isomorphism $\gamma_X: X \Psi_a \lto \Psi_b X$.
+\end{itemize}
+This data is required to satisfy the following axioms:
+\begin{itemize}
+\item For each composable pair $X,Y$ of $1$-morphisms the diagram
+\[
+\xymatrix@C+2pc@R+1pc{
+(YX) \Psi \ar[rrr]^-{\gamma_{YX}} \ar[d]_-{\alpha} & & & \Psi ( YX )\\
+Y ( X \Psi ) \ar[r]_-{1_Y * \gamma_X} & Y( \Psi X ) \ar[r]_-{\alpha^{-1}} & ( Y \Psi ) X \ar[r]_-{\gamma_Y * 1_X} & (\Psi Y ) X \ar[u]_-{\alpha}
+}
+\]
+commutes.
+\item For every object $a$, $\xi_a * 1_\Psi = 1_\Psi * \xi_a$.
+\item For every $1$-morphism $X : a \lto b$, $1_X * \xi_a = ( \xi_b * 1_X ) ( 1_\Psi * \gamma_X ) (\gamma_X * 1_\Psi )$.
+\end{itemize}
+\end{definition}
+
+\begin{example} Supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
+\end{example}
+
+A superbicategory can be constructed out of a bicategory $\cat{B}$ in which the categories $\cat{B}(a,b)$ are all equipped with the structure of supercategories; see Appendix \ref{section:constructing_superbicategories}.
+
+\begin{example}\label{example:bicategory_m} There is a bicategory of $\mathbb{Z}_2$-graded $k$-algebras where $1$-morphisms are $\mathbb{Z}_2$-graded bimodules and $2$-morphisms are degree zero bimodule maps.
+Given a $B$-$A$-module $M$ the shift $M[1]$ has the grading $M[1]_i = M_{i+1}$ and the left and right action given by
+\[
+b \cdot m = (-1)^{|b|} bm, \qquad m \cdot a = (-1)^{|a|} m a\,.
+\]
+This is a functor $\Psi = (-)[1]$ on the category of $B$-$A$-bimodules and with $\xi = 1$ this defines the structure of a supercategory on this category of bimodules.
+The usual isomorphisms of bimodules $\tau$
+\begin{align}
+N[1] \otimes M &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto n \otimes m \label{eq:shift_iso_a}\\
+N \otimes M[1] &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto (-1)^{|n|} n \otimes m\label{eq:shift_iso_b}
+\end{align}
+satisfy the conditions in Appendix \ref{section:constructing_superbicategories} and therefore give the bicategory of $\mathbb{Z}_2$-graded algebras and bimodules the structure of a superbicategory.
+\end{example}
+
+\begin{definition} Given two superbicategories $\cat{B}, \cat{C}$ a \emph{lax superfunctor} $\Phi: \cat{B} \lto \cat{C}$ is a lax functor together with, for each object $a$ in $\cat{B}$, a $2$-morphism
+\[
+\kappa_a: \Psi_{\Phi a} \lto \Phi( \Psi_a )
+\]
+satisfying two coherence conditions:
+\begin{itemize}
+\item[(a)] for all $a$, commutativity of
+\[
+\xymatrix@C+2pc{
+\Psi_{\Phi a} \Psi_{\Phi a} \ar[dd]_-{\xi}\ar[r]^-{\kappa * \kappa} & \Phi( \Psi_a ) \Phi( \Psi_a ) \ar[d]\\
+& \Phi( \Psi_a \Psi_a ) \ar[d]^-{\Phi(\xi)}\\
+\Delta_{\Phi a} \ar[r] & \Phi( \Delta_a )
+}
+\]
+\item[(b)] for each $1$-morphism $X: a \lto b$ in $\cat{B}$, commutativity of
+\[
+\xymatrix@C+2pc{
+\Phi(X) \Psi_{\Phi a} \ar[d]_-{\gamma} \ar[r]^-{1 * \kappa} & \Phi(X) \Phi(\Psi_a) \ar[r] & \Phi( X \Psi_a ) \ar[d]^-{\Phi(\gamma)}\\
+\Psi_{\Phi b} \Phi(X) \ar[r]_-{\kappa * 1} & \Phi(\Psi_b) \Phi(X) \ar[r] & \Phi( \Psi_b X)
+}
+\]
+\end{itemize}
+A \emph{strong superfunctor} is a lax superfunctor with $\kappa_a$ an isomorphism for every object $a$.
+\end{definition}
 \subsection{Splitting homotopies from connections}

### 2015-10-14 cutsystems-new.tex
Revisions.

@@
 \begin{abstract}
-A cut system has objects, $1$-morphisms and $2$-morphisms, similar to a bicategory.
-In contrast to the composition of $1$-morphisms in a bicategory, the cut operation on $1$-morphims in a cut system produces representations of Clifford algebras in supercategories rather than bare objects.
-The motivating example of a cut system refines the bicategory of Landau-Ginzburg models, in which the objects are hypersurface singularities and the $1$-morphisms are matrix factorisations.
+In the bicategory of Landau-Ginzburg models $\LG$ the objects are certain polynomials called potentials, and the $1$-morphisms are matrix factorisations.
+The composition of these $1$-morphisms is defined by a form of convolution, and is not easy to compute.
+In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms is given explicitly.
+This construction will be applied in a sequel to define an enrichment of $\LG$ over affine schemes.
 \end{abstract}
@@
 
-The bicategory of Landau-Ginzburg models $\LG$ has polynomials $W(x)$ called \textsl{potentials} as its objects, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
-This bicategory has been studied extensively in connection with topological field theory \cite{??} and knot invariants \cite{??}.
-The most important and nontrivial structure in this bicategory is the functor
-\be\label{eq:intro_functor_comp}
-\LG(V,U) \otimes_{\nC} \LG(W, V) \lto \LG(W,U)
-\ee
-which composes $1$-morphisms for potentials $W(x),V(y),U(z)$.
-Continuing the approach developed with Dyckerhoff in \cite{??}, the aim of this paper is to explicitly describe this functor.
-Any increase in our understanding of the operation of composition in $\LG$ has implications for the subjects where this bicategory makes an appearance, but our primary application is to the semantics of linear logic constructed in \cite{??}.
-
-\begin{itemize}
-\item We define another bicategory without units $\cat{L}$
-\item We prove $\cat{L}$ is equivalent to $\LG$
-\item We show how to model $\cat{L}$ in schemes (next paper)
-\end{itemize}
-
-First of all, let us be more precise about the kind of explicit description we are looking for.
-Observe that once we have chosen a homogeneous basis, a matrix factorisation of $W(x) - V(y)$ is just a matrix of polynomials
-\[
-D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (W(x) - V(y)) \cdot I_{2r}\,.
-\]
-If we fix the rank $r$ and bound the degrees of the monomials appearing in $D$ by some integer $k$, it is easy to parametrise such matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$.
-Then the set of objects of $\LG(W,V)$ can be described as a disjoint union of inductive limits of these schemes
-\[
-\operatorname{ob} \LG(W,V) = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)\,.
-\]
-The kind of explicit description we are looking for is a lifting of the function \eqref{eq:intro_functor_comp} on the level of objects to a morphism of schemes
-\be\label{eq:composition_as_schememap}
-\mathscr{M}_{r',k'}(V,U) \times \mathscr{M}_{r,k}(W,V) \lto \mathscr{M}_{f(r,r'),g(k,k')}(W, U)\,.
-\ee
-Unfortunately this appears difficult, if not impossible, as stated.
-In this article we explain how the replacement of $\LG(W,U)$ by an equivalent category $\cat{L}(W,U)$, called the \textsl{Clifford thickening}, allows for such a lifting of \eqref{eq:intro_functor_comp} to a morphism of schemes.
-
-% One consequence is that $\LG$ is equivalent to the bicategory $\cat{L}^\bullet$, which is \emph{computable} in the sense that its operations may be embodied in software.
-To some extent this software already exists: a component of what we are here calling the cut system $\cat{L}$ (developed earlier in joint work with Dyckerhoff \cite{dm1102.2957}\footnote{For a more detailed discussion of the relation of this work with the present paper, see Remark \ref{remark:relation_to_toby_paper}.}) has already been implemented in the computer algebra package Singular in joint work with Carqueville \cite{khovhompaper}, and used to compute tables of Khovanov-Rozansky knot homologies.
-The code was also used in the discovery of the generalised orbifolding relations among ADE singularities by Carqueville, Ros Camacho and Runkel \cite{ade}.
-\medskip
+The bicategory of Landau-Ginzburg models $\LG$ has polynomials $W(x)$ called \textsl{potentials} as its objects (typically, the defining equation of an isolated singularity) and the $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
+This bicategory plays an important role in topological field theory \cite{McNameethesis,lgdual,genorb} and the study of homological knot invariants \cite{kr0401268}.
+In \cite{lgdual} it was shown that $\LG$ is a pivotal bicategory with adjoints, and closed formulas were given for the units and counits of adjunction.
+In this paper and its sequel we study an enrichment of $\LG$ which we refer to as a \emph{cut system}.
+
+A finite rank matrix factorisation of $V(y) - W(x)$ is a matrix of polynomials
+\[
+D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
+\]
+where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices.
+The set of finite rank matrix factorisations is denoted $\LG(W,V)_{fin}$.
+For technical reasons the category of $1$-morphisms $\LG(W,V)$ contains, in addition to the finite rank matrix factorisations, those infinite rank matrix factorisations which are homotopy equivalent to finite rank ones; this means in particular that the inclusion
+\[
+\LG(W,V)_{fin} \lto \LG(W,V)
+\]
+is an equivalence of categories.
+
+If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise the possible matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$ whose coordinates are the coefficients of the various monomials in each row and column of $D$.
+Hence as sets we have
+\begin{equation}\label{eq:param_frmf}
+\LG(W,V)_{fin} = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)_{\nC}\,.
+\end{equation}
+For various applications, two of which we sketch below, we would like to know that the basic operations of the bicategory $\LG$ respect this additional scheme structure; that is, that these operations are continuous in the coordinates which parametrise the $1$-morphisms.
+The most important and nontrivial such structure is the composition functor
+\begin{gather*}
+\LG(V,U)_{fin} \times \LG(W, V)_{fin} \lto \LG(W,U)\,,\\
+(Y,X) \mapsto Y \otimes X\,.
+\end{gather*}
+We would like therefore to produce a morphism of schemes (omitting indices)
+\[
+c: \mathscr{M}(V,U) \times \mathscr{M}(W,V) \lto \mathscr{M}(W,U)
+\]
+with the property that $c([Y], [X]) = [Y \otimes X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.
+
+The problem is that this doesn't make any sense, because $Y \otimes X$ contains monomials $x^i y^j z^k$ with $y$'s in them (we say $Y \otimes X$ is \emph{infinite rank} over $k[x,z]$) and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$.
+However one can prove that $Y \otimes X$ is a summand in the homotopy category of a finite rank matrix factorisation (involving only $x$'s and $z$'s) and even describe this object and the corresponding idempotent explicitly \cite{dm1102.2957}.
+This is a finite amount of data which can be used to encode $Y \otimes X$, so we just need to replace $\mathscr{M}(W,U)$ by some scheme which knows how to store such data.
+
+\vspace{0.5cm}
+
+After some refinements\footnote{See Remark \ref{remark:relation_to_toby_paper} for a discussion of why we end up encoding the finite model by Clifford actions rather than the idempotents of \cite{dm1102.2957}.} this amounts to replacing $\LG$ by an equivalent bicategory $\cat{L}$ with the same objects and (almost) the same $1$-morphisms, but whose composition operation is easily encoded as a morphism of schemes.
+We say \emph{almost} the same $1$-morphisms because in $\cat{L}$ the $1$-morphisms are still finite rank matrix factorisations, but now they may additionally equipped with the action of a Clifford algebra.
+It remains straightforward to parametrise these $1$-morphisms by the closed points of an affine scheme, but in contrast to $\LG$ the composition functor in $\cat{L}$ (which we refer to as the \emph{cut operation})
+\begin{gather}
+\cat{L}(V,U) \times \cat{L}(W,V) \lto \cat{L}(W,U)\,,\\
+(Y,X) \mapsto Y \l X
+\end{gather}
+does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal.
+The schemes parametrising $1$-morphisms in $\cat{L}$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}.
+However the present paper is concerned only with defining the bicategory $\cat{L}$ and proving that it is equivalent to $\LG$.
 
@@
 
+\subsection{Applications}
+
+\subsubsection{Topological field theory}
+
+The bicategory $\LG$ arises in topological field theory (TFT) as the data necessary to define a two-dimensional topological field theory with defects \cite{k1004.2307,dkr1107.0495}.
+It is expected that such a TFT should be associated to any suitably nice bicategory $\cat{B}$.
+In the formalisation of \cite[\S 3.1]{dkr1107.0495} the associated TFT is a symmetric monoidal functor
+\[
+\mathcal{Z}: \operatorname{Bord}_{2,1} \lto \operatorname{Vect}_\nC
+\]
+where the objects of $\operatorname{Bord}_{2,1}$ are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.
+
+\begin{figure}[bt]
+$$
+  \raisebox{-75pt}{\begin{picture}(300,130)
+  \put(0,0){\scalebox{0.6}{\includegraphics{pic02.eps}}}
+  \put(0,0){
+     \setlength{\unitlength}{.55pt}\put(-22,-8){
+%     \put(136,224)   {$ \phi_\text{in} $}
+%     \put(140, 22)   {$ \phi_\text{in} $}
+%     \put(433,142)   {$ \phi_\text{out} $}
+	 \put(295,85)   {$ Y $}
+	 \put(240,190)   {$ X $}
+     \put(510,180)   {$ O_{3} $}
+     \put( 10,230)   {$ O_{1} $}
+     \put( 10,110)   {$ O_{2} $}
+     }\setlength{\unitlength}{1pt}}
+  \end{picture}}
+$$
+\caption{A world-sheet $M$ with defect lines from $\,(O_1,O_2)\,$ to
+$\,(O_{3})$.\ The two-dimensional regions of the world-sheet are all labelled with the same potential $W(x)$, while $X,Y$ are matrix factorisations of $W(x) - W(x')$.
+The labels on the other defect lines are omitted.}
+\label{fig:wsh-defect}
+\end{figure}
+
+Consider the example shown in Figure \ref{fig:wsh-defect}, where $\cat{B} = \LG$, the two-dimensional regions are all labelled with a single potential $W(x)$ and $X,Y: W \lto W$ are $1$-morphisms.
+The value of $\mathcal{Z}$ on $M$ is a $\nC$-linear map
+\be\label{eq:value_of_bordism}
+\mathcal{Z}(M): \mathcal{Z}(O_1) \otimes \mathcal{Z}(O_2) \lto \mathcal{Z}(O_3)\,.
+\ee
+We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$.
+Namely, it is a consequence of the way the defect conditions $X,Y$ enter the partition function \cite[(3.16)]{laz} that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining $Y,X$.
+To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme $\mathscr{M}_Y \times \mathscr{M}_X$ parametrising possible labels and $\mathcal{Z}(M)$ as a morphism of these vector bundles.
+But there are some obstacles.
+% \cite[(2.9)]{dkr1107.0495}
+
+Consider the incoming circle $O_2$ with its labels $Y,X$. The construction gives
+\be\label{eq:zo2orig}
+\mathcal{Z}(O_2) := H^0 \Hom_{\nC[x,x']}( Y, X )
+\ee
+which is the vector space of $2$-morphisms $Y \lto X$ in $\LG(W,W)$. Now suppose that the defect conditions are made to depend on parameters 
+\[
+Y = Y(t_1,\ldots,t_r)\,, \qquad X = X(u_1,\ldots,u_s)
+\]
+which satisfy their own equations and cut out a parametrising scheme $\mathscr{M}_Y \times \mathscr{M}_X \subseteq \mathbb{A}^{r+s}$.
+The question is: what kind of global object $\mathcal{Z}(O_2)$ on $\mathscr{M}_Y \times \mathscr{M}_X$ is formed by the finite-dimensional vector spaces
+\[
+\mathcal{Z}(O_2)_{P,Q} := H^0 \Hom_{\nC[x,x']}( Y(P), X(Q) )
+\]
+as $P$ varies over $\mathscr{M}_Y$ and $Q$ over $\mathscr{M}_X$? The problem is that \emph{a priori} we have
+\be\label{eq:cohom_sucks}
+\big\{ H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \big\}_{P,Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
+\ee
+%This is a particular case of a general phenomenon: any complex of $\nC$-vector spaces $C$ is isomorphic in the derived category $\mathbb{D}(\nC)$ to $\bigoplus_n H^n(C)[n]$, but over a general ring, for instance the coordinate ring of $\mathscr{M}_Y \times \mathscr{M}_X$, this is not the case.
+The solution is to work instead with the full complex, which suggests the definition\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
+\be\label{eq:wuhe20}
+\mathcal{Z}(O_2) := \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \in \mathbb{D}( \operatorname{qcoh} \mathscr{M}_Y \times \mathscr{M}_X )\,.
+\ee
+An alternative (and we believe simpler) approach is to take $\cat{L}$ rather than $\LG$ as the input to the definition of the TFT.
+Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define $\mathcal{Z}(O_2)$ to be the following composite in $\LG$:
+\be\label{eq:composite_intro_o2}
+\xymatrix@C+2pc{
+0 \ar[r]^-X & W(x) - W(x') \ar[r]^-{Y^{\vee}} & 0
+}\,.
+\ee
+Now let $\mathcal{Z}'$ be the TFT defined using the bicategory $\cat{L}$ as input.
+Then $\mathcal{Z}'(O_2)$ may likewise be computed by the composite \eqref{eq:composite_intro_o2} in $\cat{L}$, which is a $\nZ_2$-graded complex of vector spaces $Y^{\vee} \l X$ equipped with the action of a Clifford algebra.
+If $Y(t), X(u)$ are allowed to depend on parameters, the cut becomes a vector bundle
+\be\label{eq:orynx}
+\mathcal{Z}'(O_2) := Y^{\vee}(t) \l X(u)
+\ee
+over $\mathscr{M}_Y \times \mathscr{M}_X$ equipped with a differential and compatible Clifford action, such that
+\be
+\{ Y^{\vee}(t) \l X(u) \}_{P,Q} \cong Y^{\vee}(P) \l X(Q)
+\ee
+for every point $(P,Q)$.
+
+Since $\cat{L}$ and $\LG$ are equivalent, the two ways \eqref{eq:wuhe20},\eqref{eq:orynx} of reading the composite \eqref{eq:composite_intro_o2} must contain the same information.
+However, the fact that $\eqref{eq:orynx}$ is a finite rank vector bundle over $\mathscr{M}_Y \times \mathscr{M}_X$ while \eqref{eq:wuhe20} is a complex of (non-finitely generated) quasi-coherent sheaves explains why $\cat{L}$ is better suited to this kind of problem.
+
+%We leave the details to the aforementioned sequel \cite{??}, but here is a simple example which already shows the nontriviality of viewing correlators as functionals of the moduli of the labels on defects.
+Consider the following bordism which is a morphism from the empty manifold $\emptyset$ to $O$, where $X$ denotes a matrix factorisation of $V(y) - W(x)$.
+The value of this diagram is an element
+%\[
+%\mathcal{Z}(M) \in \mathcal{Z}(O) \cong Jac(V)
+%\]
+%By virtue of the above discussion, we may think of $\mathcal{Z}(M)$ as a \emph{section} of the trivial vector bundle with fiber $Jac(V)$ over the scheme $\mathscr{M}(W,V)$ which parametrises $1$-morphisms from $W$ to $V$ in $\LG$.
+If this section is not identically zero, then $V$ is called a \emph{generalised orbifold} of $W$ \cite{??} and it is of great interest to know when this is the case.
+From what we have said, it is clear that this is essentially a question of the geometry of $\mathscr{M}(W,V)$.
+
+\subsubsection{Semantics of logic}
+
+In forthcoming work we use the results of this paper to define a novel semantics of linear logic, in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
+Proofs in the logic are interpreted by certain correspondences between these pairs.
+To explain briefly why we are forced to use $\cat{L}$ rather than $\LG$, it is enough to describe the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
+
+Let $x$ be a variable of the logic and suppose it has denotation $\llbracket x \rrbracket = (\Spec(\nC), \nC[x], W)$ in the semantics.
+Let $\mathscr{M} = \mathscr{M}(W,W)$ be the affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\cat{L}$, as discussed above.
+Then
+\begin{gather*}
+\llbracket x \multimap x \rrbracket = \big(\Spec(\nC), \nC[x,x'], W(x) - W(x') \big)\,,\\
+\llbracket {!}( x \multimap x ) \rrbracket = \big( \mathscr{M}, \nC, 0 \big)\,.
+\end{gather*}
+The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ is roughly speaking a bundle $\llbracket \underline{2} \rrbracket$ over the scheme $\mathscr{M}$ whose fiber over a loop $X$ is the square $X \l X$.
+More precisely, the denotation is the vector bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over a point $(X, a)$ is
+\be\label{eq:bundledifferentialcliffordproof}
+\llbracket \underline{2} \rrbracket_{X,a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)\,.
+\ee
+For these definitions to work, it is necessary to be able to compute the coefficients of $X \l X$ as a function of the coefficients of $X$, so we must use $\cat{L}$ in place of $\LG$.
+
 \medskip
 
-\emph{Acknowledgements.} Thanks to Nils Carqueville and Ingo Runkel for helpful comments on the draft.
-Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.
+\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft, and to Ingo Runkel and Rafal Suszek for kindly providing Figure \ref{fig:wsh-defect}.
+%Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.
 
@@
 Let us fix a homogeneous basis for $X$ so that we may identify $d_X$ with a matrix, and differentiate this matrix entry-wise to obtain the matrix $\lambda_i = \partial_{x_i}(d_X)$.
-
-\begin{lemma} The odd $R$-linear operator $\lambda_i$ on $X$ is independent, up to homotopy, of the choice of basis.
+It is easy to check that
+
+\begin{lemma}\label{lemma:homotopy_indept} The odd $R$-linear operator $\lambda_i$ on $X$ is independent, up to homotopy, of the choice of basis.
 \end{lemma}
@@
 \begin{lemma}\label{lemma:naturalityoflambda} Let $\phi: X \lto X'$ be a morphism of matrix factorisations and write $\lambda_i = \partial_{x_i}(d_X)$ and $\lambda'_i = \partial_{x_i}(d_{X'})$.
-Then there is a homotopy $\phi \lambda_i \simeq \lambda'_i \phi$.
+There is a homotopy $\phi \lambda_i \simeq \lambda'_i \phi$.
 \end{lemma}
@@
 
-In a cut system the composition rule produces objects which are representations of Clifford algebras.
+The cut operation in $\cat{L}$ produces objects which are representations of Clifford algebras.
 We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}.
@@
 \begin{equation}
-S_{m,n} = S_m \otimes_k S_n^* = \Hom_k(S_n,S_m)
+S_{m,n} = S_m \otimes_k S_n^* \cong \Hom_k(S_n,S_m)
 \end{equation}
@@
 \begin{equation}\label{eq:isosbimodule}
-S_{l,m} \otimes_{A_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{C_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
+S_{l,m} \otimes_{C_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{C_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
 \end{equation}
@@
 
-\section{The Clifford thickening}
+\section{The Clifford thickening}\label{section:cliff_thick}
 
@@
 S_{l, n} \otimes_{C_n} X \ar[r]^-{\cong} & (S_{l,m} \otimes_{C_m} S_{m,n}) \otimes_{C_n} X \ar[d]^-{\cong}\\
-& S_{l,m} \otimes_{A_m} ( S_{m,n} \otimes_{C_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{C_m} Y \ar[r]^-{\beta} & Z\,.
+& S_{l,m} \otimes_{C_m} ( S_{m,n} \otimes_{C_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{C_m} Y \ar[r]^-{\beta} & Z\,.
 }
@@
 
-In this section we define a bicategory without units which we call the \textsl{cut system} model of $\LG$.
-Later in Section \ref{??} we will prove that this bicategory is equivalent to $\LG$, although this will not be apparent at first.
-Given objects $(x,W)$ and $(y,V)$ of $\LG$ we define
+In this section we define a superbicategory without units $\cat{L}$.
+Later we will prove that this bicategory is equivalent to $\LG$, although this will not be apparent at first.
+The objects of $\cat{L}$ are the same as $\LG$, namely potentials $(x,W)$.
+
+\begin{definition} Given potentials $(x,W)$ and $(y,V)$ we define
 \be\label{eq:defnluv}
@@
 \ee
-where $(-)^\omega$ denotes the idempotent completion and $(-)^{\bullet}$ the Clifford thickening. The first aim of this section is to define, for any object $(z,U)$ of $\LG$, a functor
+where $(-)^\omega$ denotes the idempotent completion (see Remark \ref{remark:idempotent_completion}) and $(-)^{\bullet}$ is the Clifford thickening (see Section \ref{section:cliff_thick}).
+\end{definition}
+
+Thus a $1$-morphism $W \lto V$ in $\cat{L}$ is a finite rank matrix factorisation $X$ of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\gamma_i, \gamma_i^\dagger$ for $1 \le i \le a$ satisfying Clifford relations and the equations (all up to homotopy)
+\begin{gather*}
+\gamma_i e = \gamma_i = e \gamma_i\,, \\
+\gamma_i^\dagger e = \gamma_i^\dagger = e \gamma_i^\dagger\,.
+\end{gather*}
+Most of the time we only care about $1$-morphisms where $e = 1$, and let us only describe $2$-morphisms in this case.
+For matrix factorisations $X,Y$ of $V(y) - W(x)$ with respective Clifford actions $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^a$ and $\{ \rho_j, \rho_j^\dagger \}_{j=1}^b$ the $2$-morphisms $\phi: (X,a) \lto (Y,b)$ in $\cat{L}$ are by Lemma \ref{lemma:equivcliffordthick} in bijection with morphisms of matrix factorisations $\phi: X \lto Y$ satisfying
+\[
+\phi \gamma_i = 0\,, \qquad \rho_j^\dagger \phi = 0\,, \qquad \forall 1 \le i \le a, 1 \le j \le b\,.
+\]
+Observe that the homotopy category $\LG(W,V)_{fin}$ of finite rank matrix factorisations sits fully faithfully inside $\cat{L}(W,V)$ as the subcategory where all idempotents are identities and there are no Clifford actions, and by Lemma \ref{lemma:embedcliffordthick} the inclusion of this subcategory into $\cat{L}(W,V)$ is an idempotent completion.
+
+ The first aim of this section is to define, for any object $(z,U)$ of $\LG$, a functor
 \begin{gather*}
@@
 
+\begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$.
+
+The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$.
+This ``inflation'' produces a matrix of polynomials over $k[x,z]$.
+\end{remark}
+
 \begin{definition} Given morphisms of matrix factorisations $\phi: X \lto X'$ and $\psi: Y \lto Y'$ we define the morphism of matrix factorisations
@@
 \end{definition}
-
-\begin{remark}
-As an explicit matrix of polynomials in $k[x,y]$ the differential on $Y \l X$ can be obtained from the differentials on $X$ and $Y$ (which involve $k[z,x]$ and $k[y,z]$ respectively) by replacing occurrences of $z$ by a certain square matrix of scalars; see the proof of Theorem \ref{theorem:l_cut_system} for more details.
-\end{remark}
 
@@
 
-\begin{lemma} The operator $[ d_{Y \otimes X}, \partial_{t_i} ]$ is $k[t]$-linear and therefore passes to a $k[x,z]$-linear operator on the quotient $Y \l X = \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
+\begin{lemma} The operator $[ d_{Y \otimes X}, \partial_{t_i} ]$ on $Y \, \check{\otimes}\, X$ is $k[t]$-linear and therefore passes to a $k[x,z]$-linear operator on the quotient $Y \l X = \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
 \end{lemma}
@@
 \]
-Usually we just write this operator as $\At_i$ where it will not cause confusion.
+Usually we just write $\At_i$ where it will not cause confusion.
 \end{definition}
@@
 
-\begin{lemma}\label{lemma:atiyahclosed} The operator $\At_i$ on $Y \l X$ is closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are homotopies
+\begin{lemma}\label{lemma:atiyahclosed} The operator $\At_i$ on $Y \l X$ is closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are $k[x,z]$-linear homotopies
 \be\label{eq:atiyahclosednatural}
@@
 
+For a concrete example, see Section \ref{example:computing_homs}.
+
 \begin{theorem} Given matrix factorisations $Y,X$ as above, the data
@@
 \begin{proof}
-This will follow from the considerations of Section \ref{??} but we feel it is worthwhile to give a direct proof, both to demonstrate how straightforward it is and in order to have written down explicit homotopies for the various relations.
+This will follow from the considerations of Section \ref{section:theequivalence} but we feel it is worthwhile to give a direct proof, both to demonstrate how straightforward it is and in order to have written down explicit homotopies for the various relations.
 
@@
 \begin{itemize}
-\item \textbf{Objects:} same as $\LG$, that is, potentials $(k[x], W)$.
+\item \textbf{Objects:} same as $\LG$, that is, potentials $(x, W)$.
 \item \textbf{$1$- and $2$-morphisms:} defined by \eqref{eq:defnluv}.
@@
 
-\begin{theorem} Thus defined $\cat{L}$ is a superbicategory without units.
-\end{theorem}
+\begin{proposition} Thus defined $\cat{L}$ is a superbicategory without units.
+\end{proposition}
 \begin{proof}
@@
 \[
-e_m' = a_1 \cdots a_m a_m^\dagger \cdots a_1^\dagger\,.
-\]
-Using \eqref{eq:intro_clifford_act1} and \eqref{eq:intro_clifford_act2} we can write down the explicit form of this idempotent acting on $Y \l X$.
-On this object each of the $a_i$'s acts simply as $- \lambda_i$ because all of the $a_j^\dagger$'s appear to the right.
-Hence on $Y \l X$
+e_m' = \gamma_1 \cdots \gamma_m \gamma_m^\dagger \cdots \gamma_1^\dagger\,.
+\]
+Observe that each of the $\gamma_i$'s acts as $- \lambda_i$ because all of the $\gamma_j^\dagger$'s to the right. Hence
 \begin{align*}
-e_m' &= (-1)^{\binom{m}{2}} a_1 \cdots a_m a_1^\dagger \cdots a_m^\dagger \\
+e_m' &= (-1)^{\binom{m}{2}} \gamma_1 \cdots \gamma_m \gamma_1^\dagger \cdots \gamma_m^\dagger \\
 &= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
@@
 
-\begin{remark} There is a question of whether or not the $A_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
-But Atiyah classes are independent, up to homotopy, of the choice of connection, and it is easy to see that the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis.
-Hence the action is indeed canonical.
+\begin{remark} There is a question of whether or not the $C_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
+But Atiyah classes are independent, up to homotopy, of the choice of connection, and the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis (Lemma \ref{lemma:homotopy_indept}).
 \end{remark}
 
-\begin{remark}\label{remark:inflation} Let $V \in k[z_1,\ldots,z_m]$ be a potential and choose a $k$-basis for $J_V$.
-Then multiplication by $z_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[z_i]$ over $k$.
-
-Given $X$ and $Y$ the cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $z_i$ by the scalar matrix $[z_i]$.
-This ``inflation'' produces a matrix of polynomials over $k[x,y]$.
-\end{remark}
-
-\section{The equivalence of $\cat{L}$ and $\LG$}
+\section{The equivalence of $\cat{L}$ and $\LG$}\label{section:equivllg}
 
@@
 \end{equation}
-where $V$ is the exterior algebra
+where $V$ is the exterior algebra viewed as a $\nZ_2$-graded $k$-module
 \[
@@
 In conclusion, there is an isomorphism of Clifford representations \eqref{eq:iso_of_clifford_modelfinite} in the homotopy category of finite rank matrix factorisations of $U - W$ over $k[x,z]$, and this is our solution to the problem of finding a finite model of $Y \otimes X$.
-Once we have established all of this, proving that $\cat{L}$ and $\LG$ are equivalent bicategories will be immediate.
+Once we have established all of this, proving that $\cat{L}$ and $\LG$ are equivalent bicategories will be straightforward.
 
@@
 
-Let $(X,d)$ be a complex of $R$-modules on which $t_1,\ldots,t_n \in R$ act null-homotopically.
+Let $R$ be a $k$-algebra and $(X,d)$ a complex of $R$-modules on which $t_1,\ldots,t_n \in R$ act null-homotopically.
 Tensoring $X$ with the Koszul complex $K(t_i)$ yields the same complex as taking the cone of $t_i \cdot 1_X = 0: X \lto X$, and therefore we have a homotopy equivalence
@@
 \begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_n$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_n$.
-An explicit isomorphism can be written down using the techniques developed in this Section, see Appendix \ref{section:variation_of_homotopy}.
+An explicit isomorphism can be written down using the techniques developed in this Section.
 \end{remark}
@@
 
-\begin{proposition}\label{prop:clifford_action} The map $\Phi$ is an isomorphism of $C_m$- representations in the homotopy category. That is, there are homotopies
+\begin{proposition}\label{prop:clifford_action} The map $\Phi$ is an isomorphism of $C_m$- representations in the homotopy category. That is, there are homotopies for $1 \le i \le m$
 \[
@@
 \begin{align*}
-\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty &= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2}} \frac{1}{s!} [ d_{Y \otimes X}, \partial_{t_{p_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{p_s}}] \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}\\
-&= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s}{2}} \frac{1}{s!} \At_{p_1} \cdots \At_{p_s} \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}
+\pi \theta_{q_1}^* \cdots \theta_{q_l}^* \sigma_\infty &= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2}} \frac{1}{s!} \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \At_{p_1} \cdots \At_{p_s} \theta_{p_1} \cdots \theta_{p_s}\\
+&= \sum_{s \ge 0} \sum_{p_1,\ldots,p_s} (-1)^{\binom{s+1}{2} + sl} \frac{1}{s!} \At_{p_1} \cdots \At_{p_s} \pi \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{p_1} \cdots \theta_{p_s}\,.
 \end{align*}
-since $[ d_{Y \otimes X}, \partial_{t_{p_i}}] = - \At_{p_i}$.
-Now $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $s = l$ and to $\bold{p}$ a permutation of $\bold{q}$.
-Since
+Now $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $s = l$ and to $\bold{p}$ a permutation of $\bold{q}$. Since
 \[
@@
 
-The latter functor $F$ is defined by choosing\footnote{One can avoid invoking the axiom of choice here by defining the splitting using homotopy colimits, see \cite{??}}, for each object $(X,e)$ a (possibly infinite rank) matrix factorisation $F(X,e)$ which splits the idempotent $e$.
+The functor $F$ is defined by choosing\footnote{One can avoid invoking the axiom of choice here by defining the splitting using homotopy colimits, see \cite{??}}, for each object $(X,e)$ a (possibly infinite rank) matrix factorisation $F(X,e)$ which splits the idempotent $e$.
 That is, such that there are morphisms in the homotopy category
@@
 
-Using the cut model $\cat{L}$ we can study the complex $\Hom_R(X,Y)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[z_1,\ldots,z_m]$.
+Using the bicategory $\cat{L}$ we can study the complex $\Hom_R(Y,X)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[y_1,\ldots,y_m]$.
 In particular, we will explain how the homotopy relation on morphisms of matrix factorisations is effectively computable.
 
-The pair $(k,0)$ is an object in $\LG$ and we may view $Y$ and the dual matrix factorisation $X^{\vee}$ of $-V$ as a pair of $1$-morphisms
+The pair $(k,0)$ is an object in $\LG$ and we may view $X$ and the dual matrix factorisation $Y^{\vee}$ of $-V$ as a pair of $1$-morphisms
 \begin{equation}\label{eq:compute_hom_composition}
 \xymatrix@C+2pc{
-0 \ar[r]^-{Y} & V \ar[r]^-{X^{\vee}} & 0
+0 \ar[r]^-{X} & V \ar[r]^-{Y^{\vee}} & 0
 }\,.
 \end{equation}
-The composite is a $1$-morphism $0 \lto 0$, that is, $\mathbb{Z}_2$-graded complex of $k$-modules. This is the Hom complex of $R$-linear homogeneous maps $X \lto Y$,
-\[
-X^{\vee} \otimes_R Y \cong \Hom_R(X, Y)
-\]
-with the differential $\phi \mapsto d_Y \circ \phi - (-1)^{|\phi|} \phi \circ d_X$.
-The cut model provides a two-step process to compute the result of the composition in \eqref{eq:compute_hom_composition}.
-First form the cut
-\[
-X^{\vee} \l Y = X^{\vee} \otimes_R J_V \otimes_R Y = \Hom_{J_V}( \bar{X}, \bar{Y} )
-\]
-where $\bar{X} = X \otimes_R J_V, \bar{Y} = Y \otimes_R J_V$. This is a complex of finite-rank $\mathbb{Z}_2$-graded free $k$-modules, and there is an $A_m$-linear homotopy equivalence
-\[
-\Phi: S_m \otimes_k \Hom_R(X,Y) \lto \Hom_{J_V}( \bar{X}, \bar{Y} )\,.
-\]
-Set $H = \Hom_{J_V}( \bar{X}, \bar{Y} )$ and define
+The composite is a $1$-morphism $0 \lto 0$, that is, $\mathbb{Z}_2$-graded complex of $k$-modules. This is the Hom complex of $R$-linear homogeneous maps $Y \lto X$,
+\[
+Y^{\vee} \otimes_R X \cong \Hom_R(Y, X)
+\]
+with the differential $\phi \mapsto d_X \circ \phi - (-1)^{|\phi|} \phi \circ d_Y$. The cut is
+\[
+Y^{\vee} \l X = Y^{\vee} \otimes_R J_V \otimes_R X \cong \Hom_{J_V}( \bar{Y}, \bar{X} )
+\]
+where $\bar{X} = X \otimes_R J_V, \bar{Y} = Y \otimes_R J_V$.
+This is a complex of finite-rank $\mathbb{Z}_2$-graded free $k$-modules, and there is an $C_m$-linear homotopy equivalence (Theorem \ref{theorem:htpy_equivalence_main})
+\[
+\Phi: S_m \otimes_k \Hom_R(Y,X) \lto \Hom_{J_V}( \bar{Y}, \bar{X} )\,.
+\]
+Set $H = \Hom_{J_V}( \bar{Y}, \bar{X} )$ and define
 \[
@@
 As a matrix of scalars $d^1_H$ may be computed from the differentials $d_X, d_Y$ by inflation, as described in Remark \ref{remark:inflation}.
-Let $\psi: X \lto Y$ be a morphism of matrix factorisations.
-Then $\psi$ is null-homotopic if and only if $\psi' = \Phi(\psi) \in \Hom_{J_V}( \bar{X}, \bar{Y} )$ is a coboundary.
+Let $\psi: Y \lto X$ be a morphism of matrix factorisations.
+Then $\psi$ is null-homotopic if and only if $\psi' = \Phi(\psi) \in \Hom_{J_V}( \bar{Y}, \bar{X} )$ is a coboundary.
 As a matrix, $\psi'$ is obtained from $\psi$ by inflation.
 This reduces the problem of determing whether or not $\psi$ is null-homotopic to the subspace membership problem for the pair $(B, \psi')$.
-If $k$ is a field this may be computed by a row-reduction, and otherwise using Gr\"obner bases.
-
-\begin{example} Suppose $V = z^N$ in $k[z]$ for $N \ge 2$. Take matrix factorisations $X,Y$ with the same underlying free $R = k[z]$-module $X = Y = R \oplus R \theta$ and differentials
-\[
-d_X = z^i \theta + z^{N-i} \theta^* = \begin{pmatrix} 0 & z^{N-i} \\ z^i & 0 \end{pmatrix}, \qquad d_Y = z^j \theta + z^{N-j} \theta^* = \begin{pmatrix} 0 & z^{N-j}\\ z^j & 0 \end{pmatrix}
-\]
-where $1 \le i,j \le N/2$. Using the basis $\Hom_R(X,Y) = R \theta \theta^* \oplus R \theta^* \theta \oplus R\theta \oplus R \theta^*$,
+If $k$ is a field this may be computed by a row-reduction, or if $k$ is a polynomial ring over a field using Gr\"obner bases.
+
+\begin{example} Suppose $V = y^N$ in $k[y]$ for $N \ge 2$. Take matrix factorisations $X,Y$ with the same underlying free $R = k[y]$-module $X = Y = R \oplus R \theta$ and differentials
+\[
+d_Y = y^i \theta + y^{N-i} \theta^* = \begin{pmatrix} 0 & y^{N-i} \\ y^i & 0 \end{pmatrix}, \qquad d_X = y^j \theta + y^{N-j} \theta^* = \begin{pmatrix} 0 & y^{N-j}\\ y^j & 0 \end{pmatrix}
+\]
+where $1 \le i,j \le N/2$. Using the basis $\Hom_R(Y,X) = R \theta \theta^* \oplus R \theta^* \theta \oplus R\theta \oplus R \theta^*$,
 \begin{equation}\label{eq:differential_hom}
-d_{\Hom} = \begin{pmatrix} 0 & 0 & z^{N-i} & z^j \\ 
-0 & 0 & z^{N-j} & z^i \\
--z^i & z^j & 0 & 0 \\
-z^{N-j} & -z^{N-i} & 0 & 0 \end{pmatrix}\,.
-\end{equation}
-Let us now compute the cut $X^{\vee} \l Y$ with its Clifford action. With
-\[
-J_V = k[z]/z^{N-1} = k \cdot 1 \oplus k \cdot z \oplus \cdots k \cdot z^{N-2}
-\]
-the matrix of multiplication by $z$ on $J_V$ is $[z] = \begin{pmatrix} 0 & 0\\ I_{N-2} & 0 \end{pmatrix}$. The differential on
-\[
-X^{\vee} \l Y = \Hom_{J_V}( \bar{X}, \bar{Y} ) = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
-\]
-is then obtained from \eqref{eq:differential_hom} by replacing every $z$ by the matrix $[z]$.
-
-The Clifford algebra $A_1$ acts by two generators $a, a^\dagger$.
-To determine their matrices, note that with $t = z^{N-1}$, $k[z]$ is a free $k[t]$-module with basis $1, \ldots, z^{N-2}$.
-Given a polynomial $f(z)$ we may uniquely write it as $f(z) = \sum_{l = 0}^{N-2} f_l \cdot z^l$ with $f_l \in k[t]$.
-There is a connection $\nabla: k[z] \lto k[z] \otimes_{k[t]} \Omega^1_{k[t]/k}$ whose associated $k$-linear operator $\partial_t$ is
-\[
-\partial_t: k[z] \lto k[z], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) z^l \,.
-\]
-Notice that for $0 \le q \le N - 1$, $\partial_t(z^q) = \delta_{q (N-1)} \cdot 1$.
-
-The Atiyah class is the $k[t]$-linear operator $\At = [d_{\Hom}, \partial_t]$ on $\Hom_R(X,Y)$. We may compute it for example on generators by
-\[
-\At( \theta \theta^* ) = \partial_t d_{\Hom}( \theta \theta^* ) = - \partial_t( z^i ) \theta + \partial_t( z^{N-j} ) \theta^* = - \delta_{i (N-1)} \theta + \delta_{(N-j)(N-1)} \theta^*\,.
-\]
-The Atiyah class passes to a $k$-linear operator $a^\dagger$ on $X^{\vee} \l Y$ with matrix ($I$ denotes $I_{N-1}$)
+d_{\Hom} = \begin{pmatrix} 0 & 0 & y^{N-i} & y^j \\ 
+0 & 0 & y^{N-j} & y^i \\
+-y^i & y^j & 0 & 0 \\
+y^{N-j} & -y^{N-i} & 0 & 0 \end{pmatrix}\,.
+\end{equation}
+Let us now compute the cut $Y^{\vee} \l X$, according to Definition \ref{defn:cliffordaction_cut}. With
+\[
+J_V = k[y]/y^{N-1} = k \cdot 1 \oplus k \cdot y \oplus \cdots k \cdot y^{N-2}
+\]
+the matrix of multiplication by $y$ on $J_V$ is $[y] = \begin{pmatrix} 0 & 0\\ I_{N-2} & 0 \end{pmatrix}$. The differential on
+\[
+Y^{\vee} \l X = \Hom_{J_V}( \bar{Y}, \bar{X} ) = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
+\]
+is then obtained from \eqref{eq:differential_hom} by replacing every $y$ by the matrix $[y]$.
+
+The Clifford algebra $C_1$ acts by generators $\gamma, \gamma^\dagger$.
+To determine their matrices, note that with $t = \partial_y(V) = N y^{N-1}$, $k[y]$ is a free $k[t]$-module with basis $1, \ldots, y^{N-2}$.
+Given a polynomial $f(y)$ we may uniquely write it as $f(y) = \sum_{l = 0}^{N-2} f_l \cdot y^l$ with $f_l \in k[t]$.
+There is a connection $\nabla: k[y] \lto k[y] \otimes_{k[t]} \Omega^1_{k[t]/k}$ whose associated $k$-linear operator $\partial_t$ is
+\[
+\partial_t: k[y] \lto k[y], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) y^l \,.
+\]
+Notice that for $0 \le q \le N - 1$, $\partial_t(y^q) = \frac{1}{N} \delta_{q (N-1)} \cdot 1$.
+
+The Atiyah class is the $k[t]$-linear operator $\At = [d_{\Hom}, \partial_t]$ on $\Hom_R(Y,X)$. We may compute it for example on generators by
+\[
+\At( \theta \theta^* ) = \partial_t d_{\Hom}( \theta \theta^* ) = - \partial_t( y^i ) \theta + \partial_t( y^{N-j} ) \theta^* = - \frac{1}{N}\delta_{i (N-1)} \theta + \frac{1}{N}\delta_{(N-j)(N-1)} \theta^*\,.
+\]
+The Atiyah class passes to a $k$-linear operator $\gamma^\dagger$ on $Y^{\vee} \l X$ with matrix ($I$ denotes $I_{N-1}$)
 \begin{equation}\label{eq:aityah_class_hom_example}
-a^\dagger = \begin{pmatrix} 0 & 0 & \delta_{i1} \cdot I & \delta_{j(N-1)} \cdot I \\ 
+\gamma^\dagger = \frac{1}{N} \begin{pmatrix} 0 & 0 & \delta_{i1} \cdot I & \delta_{j(N-1)} \cdot I \\ 
 0 & 0 & \delta_{j1} \cdot I & \delta_{i(N-1)} \cdot I \\
@@
 \end{equation}
-Similarly one can determine that the matrix of $\lambda$ on $X^{\vee} \l Y$ is
-\[
-\lambda = \begin{pmatrix} 0 & 0 & 0 & \frac{j}{N} [z^{j-1}] \\
-0 & 0 & \frac{N-j}{N} [z^{N-j-1}] & 0\\
-0 & \frac{j}{N} [z^{j-1}] & 0 & 0\\
-\frac{N-j}{N} [z^{N-j-1}] & 0 & 0 & 0\end{pmatrix}\,.
-\]
-By definition $a = - \lambda - \lambda^2 a^\dagger$ so this completes the description of the cut $( X^{\vee} \l Y, \{ a, a^\dagger \} )$.
-Splittng the idempotent $a^\dagger a$ on the $\mathbb{Z}_2$-graded complex $X^{\vee} \l Y$ of finite rank free $k$-modules yields a finite model for $\Hom_R(X,Y)$.
+Similarly the matrix of $\partial_{y}(d_X) = j y^{j-1} \theta + (N-j) y^{N-j-1} \theta^*$ on $Y^{\vee} \l X$ is
+\[
+\partial_y(d_X) = \begin{pmatrix} 0 & 0 & 0 & j [y^{j-1}] \\
+0 & 0 & (N-j) [y^{N-j-1}] & 0\\
+0 & j [y^{j-1}] & 0 & 0\\
+(N-j) [y^{N-j-1}] & 0 & 0 & 0\end{pmatrix}\,.
+\]
+By definition
+\[
+\gamma = - \partial_y(d_X) - \frac{1}{2} N (N-1) y^{N-2} \gamma^\dagger
+\]
+which completes the description of the cut $( Y^{\vee} \l X, \{ \gamma, \gamma^\dagger \} )$.
+Splittng the idempotent $\gamma^\dagger \gamma$ on $Y^{\vee} \l X$ yields a finite model for $\Hom_R(Y,X)$.
 \end{example}
 
-TODO: remark on difference between $\partial(d_Y)$ and $\partial(d_X)$
+%TODO: remark on difference between $\partial(d_Y)$ and $\partial(d_X)$
 
@@
 
-\begin{lemma} If $A \cong \End_k(P)$ then for any $A$-module $X$ in $\cat{C}$ there is an object $\widetilde{X}$ and an isomorphism of $A$-modules $X \cong P \otimes_k \widetilde{X}$.
+\begin{lemma} If $P$ is a finite rank free $\nZ_2$-graded $k$-module and $A \cong \End_k(P)$, then for any $A$-module $X$ in $\cat{C}$ there is an object $\widetilde{X}$ and an isomorphism of $A$-modules $X \cong P \otimes_k \widetilde{X}$.
 \end{lemma}
@@
 
-\begin{lemma} If $A \cong \End_k(P)$ and $V$ is a $\mathbb{Z}_2$-graded right $A$-module which is finitely generated and projective as a $k$-module, then $V \otimes_A X$ exists for any $A$-module $X$.
-\end{lemma}
-\begin{proof}
-Write $P^* = \Hom_k(P,k)$ so that $V \cong \widetilde{V} \otimes_k P^*$ as right $A$-modules for some $\mathbb{Z}_2$-graded $k$-module $\widetilde{V}$.
+\begin{lemma} If $A$ is Morita trivial and $V$ is a $\mathbb{Z}_2$-graded right $A$-module which is finitely generated and projective as a $k$-module, then $V \otimes_A X$ exists for any $A$-module $X$.
+\end{lemma}
+\begin{proof}
+Write $A \cong \End_k(P)$ and $P^* = \Hom_k(P,k)$ so that $V \cong \widetilde{V} \otimes_k P^*$ as right $A$-modules for some $\mathbb{Z}_2$-graded $k$-module $\widetilde{V}$.
 Since $V$ is finitely generated projective over $k$, so is $\widetilde{V}$.
@@
 
-\begin{lemma}\label{lemma:assoctensor} Let $W$ be a $C$-$B$-bimodule and $V$ a $B$-$A$-bimodule. Then there is a natural isomorphism of $C$-modules
-\[
-(W \otimes_B V) \otimes_A X \cong W \otimes_B ( V \otimes_A X )
+\begin{lemma}\label{lemma:assoctensor} Let $W$ be a $C$-$B$-bimodule and $V$ a $B$-$A$-bimodule in $\cat{C}$.
+Then for any left $A$-module $X$ in $\cat{C}$ there is a natural isomorphism of $C$-modules
+\[
+(W \otimes_B V) \otimes_A X \cong W \otimes_B ( V \otimes_A X )\,.
 \]
@@
 
-\begin{lemma}\label{lemma:simplehom} Let $X$ be a $\mathbb{Z}_2$-graded left $C_n$-module. There is a $k$-linear isomorphism
+\begin{lemma}\label{lemma:simplehom} Let $X$ be a left $C_n$-module in $\cat{C}$. There is a $k$-linear isomorphism
 \[
@@
 \[
-\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta: X \lto Y \l \gamma_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
+\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta \in \cat{C}(X,Y) \l \gamma_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
 \]
@@
 
+\bibitem{genorb}
+\bysame, \textsl{Orbifold completion of defect bicategories}, 
+\href{http://arxiv.org/abs/1210.6363}{[arXiv:1210.6363]}.
+
 \bibitem{crainic}
 M.~Crainic, \emph{On the perturbation lemma, and deformations}, \href{http://arxiv.org/abs/math/0403266}{[arXiv:0403266]}
+
+\bibitem{dkr1107.0495}
+A.~Davydov, L.~Kong, and I.~Runkel, \textsl{Field theories with defects and the
+  centre functor}, Mathematical Foundations of Quantum Field Theory and Perturbative String Theory, 
+  Proceedings of Symposia in Pure Mathematics, AMS, 2011, \href{http://arxiv.org/abs/1107.0495}{[arXiv:1107.0495]}.
 
@@
 
-\bibitem{girard_llogic}
-J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
-
-\bibitem{greuel}
-G.-M.~Greuel, C.~Lossen and E.~Shustin, \textsl{Introduction to singularities and deformations}, Springer (2007).
+%\bibitem{girard_llogic}
+%J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
 
@@
 \bibitem{kang2}
-S.-J.~Kang, M.~Kashiwara and S.-J.~Oh, \textsl{Supercategorification of quantum Kac-Moody algebras II}, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.
+\bysame, \textsl{Supercategorification of quantum Kac-Moody algebras II}, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.
+
+\bibitem{k1004.2307}
+A.~Kapustin, \textsl{Topological {F}ield {T}heory, {H}igher {C}ategories, and
+  {T}heir {A}pplications},
+  \href{http://arxiv.org/abs/1004.2307}{[arXiv:1004.2307]}.
+
+\bibitem{kr0401268}
+M.~Khovanov and L.~Rozansky, \textsl{Matrix factorizations and link homology}, Fund. Math.
+  \textbf{199} (2008), 1--91,
+  \href{http://arxiv.org/abs/math/0401268}{[math/0401268]}.
+
+\bibitem{laz}
+C.~I.~Lazaroiu, \textsl{On the boundary coupling of topological {L}andau-{G}inzburg models}, JHEP 0505 (2005), no. 037 [hep-th/0312286].
 
@@
 \bibitem{cutsystems2}
-D.~Murfet, \textsl{Computing with cut systems II: linear logic}, in progress.
-
-\bibitem{selinger}
-P.~Selinger, \textsl{Lecture notes on the {L}ambda calculus}, \href{http://arxiv.org/abs/0804.3434}{[arXiv:0804.3434]}.
+D.~Murfet, \textsl{Computing with cut systems II}, in progress.
+
+\bibitem{murfet_ll}
+\bysame, \textsl{Logic and linear algebra: an introduction}, \href{http://arxiv.org/abs/1407.2650}{[arXiv:1407.2650]}.
+
+%\bibitem{selinger}
+%P.~Selinger, \textsl{Lecture notes on the {L}ambda calculus}, \href{http://arxiv.org/abs/0804.3434}{[arXiv:0804.3434]}.
 

### 2015-10-14 cutsystems-scheme.tex
Revisions.

--- 2015-03-02 cutsystems.tex
@@
 
-\section{Introduction}
+\tableofcontents
 
-In this paper we develop a new semantics of composition using a bicategorical formalism that we call \emph{cut systems}, inspired by Gentzen's cut-elimination \cite{gentzen} and Girard's geometry of interaction \cite{girard_towards}.
-The formalism is used to ``make computable'' a bicategory of isolated hypersurface singularities and matrix factorisations that has been studied in the context of topological field theory \cite{McNameethesis, cr0909.4381}.
-This means that the operations making up the data of the bicategory are given algorithmically, and can be implemented on a computer.
-One of the main applications, to be given in a sequel \cite{cutsystems2}, is to construct a model of a fragment of Girard's linear logic \cite{girard_llogic}.
-Roughly speaking, this provides mathematical semantics for a programming language in which data types are interpreted as hypersurface singularities, and programs are interpreted as homotopy equivalence classes of matrix factorisations.
+\section{Composition as a morphism of schemes}
 
-What is a semantics of composition? Consider that in a category or bicategory $\cat{A}$, for every triple of objects $a,b,c$ and morphisms
+We have now shown that $\LG$ is equivalent to $\cat{L}$, and in this section we explain how to model the composition of $1$-morphisms in this latter bicategory as a morphism of schemes.
+Throughout $k$ is a $\nQ$-algebra and $R$ any $k$-algebra.
+
+\begin{definition}\label{defn:hmfomegac} Given $W \in R$ the category $\cat{K}(R,W)$ has for its objects tuples
+\be\label{eq:hmfomegacd}
+\left( D, E, l, m, \{ \gamma_i, \gamma_i^{\dagger} \}_{i=1}^m, \{ s_{ij}, s^{\dagger}_{ij}, t_{ij} \}_{i,j=1}^m, \{ z_{ai}, z^\dagger_{ai} \}_{0 \le a \le 1, 1 \le i \le m} \right)
+\ee
+where $m \ge 0$ is an integer and
+\begin{itemize}
+\item A matrix $D \in M_{2r}(R)$ with $D^2 = W \cdot I_{2r}$.
+\item A morphism $E: D \lto D$
+\item An odd matrix $l$ with
+\be\label{eq:defnhmfomega2}
+EE - E = Dl + lD\,.
+\ee
+\item $\gamma_i, \gamma_i^{\dagger} \in M_{2r}(R)$ are closed odd matrices, i.e. morphisms $D \lto D[1]$ for $1 \le i \le m$.
+\item The $s_{ij}, s^\dagger_{ij}, t_{ij} \in M_{2r}(R)$ are odd matrices satisfying, for $1 \le i,j \le m$,
+\begin{align}
+\gamma_i \gamma_j + \gamma_j \gamma_i &= D s_{ij} + s_{ij} D \,,\label{eq:hmfomegac3}\\
+\gamma^\dagger_i \gamma^\dagger_j + \gamma^\dagger_j \gamma^\dagger_i &= D s^\dagger_{ij} + s^\dagger_{ij} D\,,\label{eq:hmfomegac4}\\
+\gamma_i \gamma_j^\dagger + \gamma_j^\dagger \gamma_i &= \delta_{ij} \cdot I_{2r} + D t_{ij} + t_{ij} D\,.\label{eq:hmfomegac5}
+\end{align}
+These homotopies establish that the $\gamma_i, \gamma^\dagger_i$ satisfy Clifford relations.
+\item The $z_{ai}, z^\dagger_{ai} \in M_{2r}(R)$ are odd matrices satisfying, for $1 \le i \le m$,
+\begin{align}
+\gamma_i E - \gamma_i &= D z_{0i} + z_{0i} D\,\label{eq:hmfomegac6}\\
+E \gamma_i - \gamma_i &= D z_{1i} + z_{1i} D\,\label{eq:hmfomegac7}\\
+\gamma^\dagger E - \gamma^\dagger_i &= Dz^\dagger_{0i} + z^\dagger_{0i} D\,\label{eq:hmfomegac8}\\
+E \gamma^\dagger - \gamma^\dagger_i &= Dz^\dagger_{1i} + z^\dagger_{1i} D\,.\label{eq:hmfomegac9}
+\end{align}
+These homotopies establish that the $\gamma_i, \gamma^\dagger_i$ are morphisms in $\hmf(R,W)^\omega$.
+\end{itemize}
+A \emph{morphism} of such tuples
 \[
-\xymatrix@C+2pc{
-a \ar[r]^-{\Phi} & b \ar[r]^-{\Psi} & c
-}
+\phi: \left( D,E,l, \{ \gamma_i, \gamma_i^{\dagger} \}_{i=1}^m, \ldots \right) \lto \left( D',E',l', \{ \rho_i, \rho_i^{\dagger} \}_{i=1}^m, \ldots \right)
 \]
-there is an assignment to $(\Psi, \Phi)$ of a composition $\Psi \circ \Phi$.
-A \emph{semantics of composition} for $\cat{A}$ is a mathematical construct providing some kind of inner structure for this ``assignment'' which is coherent as $a,b,c,\Phi,\Psi$ vary.
-The main examples of this kind of semantics are in computer science and mathematical logic.
-
-For example, suppose that $\cat{A}$ is the category of sets and that we have functions
-\[
-\xymatrix@C+2pc{
-\mathbb{N} \ar[r]^-{\Phi} & \mathbb{N} \ar[r]^-{\Psi} & \mathbb{N}
-}
-\]
-where $\Phi$ and $\Psi$ are ``finitely described'' in the sense that they are computed by algorithms $X$ and $Y$, respectively.
-To be explicit, let us take $X,Y$ to be terms in the $\lambda$-calculus \cite{selinger}.
-If $[-]$ denotes assignment to an algorithm of the function it describes, then $\Phi = [X], \Psi = [Y]$ and $\Psi \circ \Phi = [Y \l X]$ where $Y \l X$ is the result of feeding the output of the algorithm $X$ as an input to the algorithm $Y$.
-In the logic literature this concatenation is known as a \emph{cut}.\footnote{We note that the notation $Y \l X$ for the cut is not standard, so don't blame the logicians for it.} To encounter the desired semantics we need the additional observation that the cut $Y \l X$ is not in normal form (whatever this means) but it may be reduced to normal form by a rewriting process on terms in the $\lambda$-calculus called $\beta$-reduction.
-This does not change the associated function: the normal form of $Y \l X$ also computes $\Psi \circ \Phi$.
-
-A semantics of composition for the category of computable functions is then given by the process which begins with the pair $(Y,X)$ of finite descriptions of $\Psi,\Phi$, forms the cut $Y \l X$, and then computes a normal form giving a finite description of $\Psi \circ \Phi$.
-
-\medskip
-
-This seems very far from geometry, but we can informally recast a problem of algebraic geometry in a similar light.
-Suppose $A,B,C$ are smooth projective algebraic varieties and that we are given triangulated functors between derived categories of coherent sheaves
-\[
-\xymatrix{
-\mathbf{D}^b(A) \ar[r]^-{\Phi} & \mathbf{D}^b(B) \ar[r]^-{\Psi} & \mathbf{D}^b(C)
-}\,.
-\]
-Suppose that $\Phi,\Psi$ are finitely described, in the sense that they are both integral functors associated to kernels: $\Phi$ is convolution with a complex of coherent sheaves $X$ on $A \times B$, and $\Psi$ is convolution with a complex $Y$ on $B \times C$.
-If for example $A,B,C$ are the $\operatorname{Proj}$ of graded algebras, $X$ and $Y$ can be described by lists of matrices of homogeneous polynomials.
-An obvious question is: what is the finite description of the functor $\Psi \circ \Phi$?
-
-It is easy to see that $\Psi \circ \Phi$ is convolution with the kernel $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$, which is a complex of quasi-coherent sheaves on $A \times C$ with coherent cohomology, but this is not described by a finite amount of data.
-Finding a finite description of $\Psi \circ \Phi$ is precisely the problem of determing the complex of coherent sheaves which is isomorphic, in $\mathbf{D}^b(A \times C)$, to $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$.
-We refer to such a complex of coherent sheaves as a \emph{finite model} of $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$.
-
-Consider the case where $A = C = \operatorname{Spec}(\mathbb{C})$, so $X,Y$ are complexes of coherent sheaves on $B$ and $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X \cong \mathbb{R}\!
-\operatorname{Hom}_{\cat{O}_B}(Y^{\vee}, X)$ is a complex of infinite-dimensional vector spaces with finite-dimensional cohomology.
-An example of a finite model is an isomorphism in the derived category of all $\mathbb{C}$-vector spaces of this complex with its cohomology
-\begin{equation}\label{eq:computing_hom_derived}
-Y \otimes^{\mathbb{L}}_{\cat{O}_B} X \cong \bigoplus_{n \in \mathbb{Z}} \Ext^n(Y^{\vee},X)[-n]\,.
-\end{equation}
-One finite description of $Y \otimes^{\mathbb{L}}_{\cat{O}_B} X$, and transitively of $\Psi \circ \Phi$, is therefore a list of numbers: the dimensions of the vector spaces on the right hand side of \eqref{eq:computing_hom_derived}.
-Determining these numbers is difficult, to put it mildly: a fundamental problem in algebraic geometry is to understand how these numbers depend on the input data $X$ and $Y$.
-
-By a (perhaps naive) analogy with computable functions, one might wonder if in the general case there exists an object $Y \l X$ in some triangulated category together with a reduction process that would help find a finite description for $\Psi \circ \Phi$.
-This is the question of whether or not there is a semantics of composition in the bicategory of smooth projective varieties and Fourier-Mukai kernels \cite{ct1007.2679}.
-Unfortunately, we do not know such a theory!
-
-However, it turns out that there \emph{is} a satisfactory semantics of this kind when instead of smooth projective varieties we consider isolated hypersurface singularities $W,V,U$ and triangulated functors between homotopy categories of matrix factorisations \cite{yoshino98}
-\begin{equation}\label{eq:pair_functors_hmf}
-\xymatrix{
-\hmf(W) \ar[r]^-{\Phi} & \hmf(V) \ar[r]^-{\Psi} & \hmf(U)
-}\,.
-\end{equation}
-To explain further, we need to introduce the language of cut systems.
-
-\medskip
-
-A \emph{cut system} $\cat{A}$ over a $\mathbb{Q}$-algebra $k$ has a class of objects and for each pair $a,b$ of objects a $k$-linear supercategory $\cat{A}(a,b)$.
-Informally, one should think of this as a category of finite models.
-There is an operation on $\cat{A}$, the \emph{cut}, which assigns to $X \in \cat{A}(a,b)$ and $Y \in \cat{A}(b,c)$ a representation $Y \l X$ in $\cat{A}(a,c)$ of a Clifford algebra which depends on the intermediate object $b$.
-The object $Y \l X$ and the endomorphisms giving the Clifford action are required to be effectively computable, say by explicit formulas, from the input data $X,Y$.
-In the example of a cut system developed in this paper, Clifford algebras arise as endomorphism algebras of exterior algebras, which in turn arise as the underlying graded modules of Koszul complexes.
-Associated to the cut system $\cat{A}$ is a bicategory $\cat{A}^\bullet$ in which the composition is derived from the cut operation, and so is also effectively computable.
-
-A \emph{cut model} of a bicategory $\cat{B}$ is a cut system $\cat{A}$ with the same objects as $\cat{B}$, together with an equivalence $I: \cat{B} \lto \cat{A}^\bullet$.
-There are fully faithful functors $I: \cat{B}(a,b) \lto \cat{A}(a,b)$ which we think of as assigning finite models to the $1$-morphisms of $\cat{B}$, and an isomorphism of Clifford representations for every composable pair of $1$-morphisms $X,Y$ in $\cat{B}$, where $S$ denotes the spinor representation:
-\begin{equation}\label{eq:intro_cut_semantics}
-I(Y) \l I(X) \cong S \otimes_k I( Y \circ X )\,.
-\end{equation}
-The cut model provides $\cat{B}$ with a semantics of composition: given finite models $I(X), I(Y)$ of $X,Y$ there is a process beginning with the cut $I(Y) \l I(X)$ which extracts the subobject $I(Y \circ X)$ using the Clifford action.
-The result $I( Y \circ X )$ of this computation is the desired finite model of the composition $Y \circ X$ in $\cat{B}$.
-\medskip
-
-The formalism is adapted to, and motivated by, an example: the bicategory of Landau-Ginzburg models $\LG$.
-Let us return to the diagram \eqref{eq:pair_functors_hmf} as our starting point.
-There is an analogue of integral functors in this setting, so that it makes sense to talk about $\Phi$ and $\Psi$ as being respectively given by convolution with kernels $X,Y$.
-If $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$ define isolated hypersurface singularities then $X$ is a finite rank matrix factorisation of $V - W$ over $k[x,z]$, and similarly for $Y$.
-
-Again, the question is: what is the finite description of $\Psi \circ \Phi$?
-It is naturally given by convolution with a matrix factorisation $Y \otimes X$ which is not finitely generated: finding a finite description of $\Psi \circ \Phi$ therefore amounts to finding a finite model for $Y \otimes X$.
-To fit this into the formalism of cut systems, we use the  bicategory $\LG$ in which the objects are isolated hypersurface singularities\footnote{Roughly speaking.
-See Section \ref{section:superbicatLG}.} and $1$-morphisms $W \lto V$ are matrix factorisations of $V - W$.
-In this bicategory, the finite descriptions of the functors in \eqref{eq:pair_functors_hmf} give rise to a composable pair of $1$-morphisms
-\begin{equation}\label{eq:cut_lg}
-\xymatrix@C+2pc{
-W \ar[r]^-{X} & V \ar[r]^-{Y} & U
-}\,.
-\end{equation}
-whose composition in $\LG$ is the tensor product $Y \otimes X$.
-
-The main results of this paper are the construction of a cut sytem $\cat{L}$ and cut model $I: \LG \lto \cat{L}^\bullet$.
-In the situation of \eqref{eq:cut_lg} $X$ and $Y$ are their own finite model (so $I(X) = X$ and $I(Y) = Y$) and a finite model of the composite $Y \otimes X$ in $\cat{B}$ may be computed from the cut $Y \l X$ in $\cat{L}$, which is an explicitly given finite rank matrix factorisation of $U - W$ together with a Clifford action described in terms of derivatives of the differentials of $X,Y$ and certain invariants called Atiyah classes.
-
-One consequence is that $\LG$ is equivalent to the bicategory $\cat{L}^\bullet$, which is \emph{computable} in the sense that its operations may be embodied in software.
-To some extent this software already exists: a component of what we are here calling the cut system $\cat{L}$ (developed earlier in joint work with Dyckerhoff \cite{dm1102.2957}\footnote{For a more detailed discussion of the relation of this work with the present paper, see Remark \ref{remark:relation_to_toby_paper}.}) has already been implemented in the computer algebra package Singular in joint work with Carqueville \cite{khovhompaper}, and used to compute tables of Khovanov-Rozansky knot homologies.
-The code was also used in the discovery of the generalised orbifolding relations among ADE singularities by Carqueville, Ros Camacho and Runkel \cite{ade}.
-
-\medskip
-In conclusion, the purpose of this paper is to develop the theory of cut systems as a mathematical foundation for the application to be given in \cite{cutsystems2}.
-Let us briefly summarise the contents of that work: one can show that the superbicategory $\cat{L}^\bullet$ is monoidal, has adjoints and is pivotal.
-This makes it a natural target for models of Girard's linear logic, which is a generalisation of the $\lambda$-calculus in which the terms may be viewed as algorithms that have a refined syntax of resource usage compared to the $\lambda$-calculus.
-The model of linear logic to be given in \cite{cutsystems2} interprets algorithms $x,y$ as $1$-morphisms $[x],[y]$ in $\cat{L}^\bullet$.
-
-This interpretation has two novelties: first of all, the target $\cat{L}^\bullet$ has a semantics of composition that may be compared to cut-elimination in linear logic (the analogue of $\beta$-reduction in the $\lambda$-calculus) as in Girard's geometry of interaction \cite{girard_towards}.
-This connection is what motivates the terminology of ``cut systems'' in the present paper.
-The second novelty is that, compared to the usual mathematical semantics of programming languages where algorithms are interpreted as functions between sets, our interpretation is bicategorical: in particular, equations $[x] \circ [y] \cong [y] \circ [x]$ or $[x]^2 \cong [x]$ on programs are represented by data that is part of the semantics.
-
-%.
-For a precise definition see Section \ref{??}}.
-To such a $W$ we associate a category of algebraic objects called matrix factorisations.
-A matrix factorisation of $W(x)$ is a matrix of polynomials $D$ satisfying $D^2 = W \cdot I_n$, where $I_n$ is the identity matrix.
-
-%For $W = x y^2 + y^3$ an example is
-%\[
-%D_1 = \begin{pmatrix} 0 & x - i y \\ x + iy & 0 \end{pmatrix} %, \qquad D_2 = \begin{pmatrix} 0 & y - x \\ (y - e^{2 \pi i /3} x)(y - e^{4 \pi i /3} x ) & 0 \end{pmatrix}
-%\]
-%A \emph{morphism} of matrix factorisations $\Phi: D_1 \lto D_2$ is a matrix of polynomials $\Phi$ satisfying the relation $\Phi D_1 = D_2 \Phi$.
-Together the matrix factorisations of $W$ and the morphisms between them form the category of matrix factorisations of $W$.
-
-%In the second part of the paper we explain how the multiplicative fragment of linear logic can be interpreted in the bicategory of Landau-Ginzburg models, with formulas mapped to isolated hypersurface singularities and proofs mapped to matrix factorisations.
-The multiplicative fragment is not very expressive, so our focus in the present paper is not on embedding sophisticated programs into $\cat{LG}$.
-Rather, we explain how cut systems give a dynamic model of cut-elimination following Girard's geometry of interaction.
-The basic construction of a cut system involves homological perturbation, and by interpreting this as a fixed point construction we will show that the result of normalization can be expressed in a power series expansion similar to Girard's famous execution formula.
-
-\medskip
-
-The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
-In Section \ref{section:cut_systems} we define cut systems and the superbicategory associated to a cut system, then we construct the cut model of $\LG$ in Section \ref{section:lg_cut_system}.
-
-\medskip
-
-\emph{Acknowledgements.} Thanks to Nils Carqueville and Ingo Runkel for helpful comments on the draft.
-Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.
-
-\section{Background}\label{section:background}
-
-Throughout $k$ is a commutative $\mathbb{Q}$-algebra. By default categories and functors are $k$-linear.
-
-\subsection{Supercategories}
-
-A superbicategory has for every $1$-morphism $F$ an associated $1$-morphism $\Psi F$ with $\Psi^2 \cong 1$, and in this sense the categories of $1$-morphisms are $\mathbb{Z}_2$-graded.
-The bicategory of Landau-Ginzburg models is an example of a superbicategory.
-Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role in the definition of cut systems, superbicategories are the natural language.
-Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.
-
-\begin{definition} A \emph{supercategory} is a category $\cat{C}$ together with a functor $\Psi: \cat{C} \lto \cat{C}$ and a natural isomorphism $\xi: \Psi^2 \lto 1_{\cat{C}}$ satisfying the condition
-\[
-\xi * 1_{\Psi} = 1_{\Psi} * \xi
-\]
-as natural transformations $\Psi^3 \lto \Psi$.
-A \emph{superfunctor} $(F, \gamma)$ from a supercategory $(\cat{C}, \Psi_{\cat{C}})$ to a supercategory $(\cat{D}, \Psi_{\cat{D}})$ is a functor $F: \cat{C} \lto \cat{D}$ together with a natural isomorphism $\gamma: F \Psi_{\cat{C}} \lto \Psi_{\cat{D}} F$ satisfying
-\[
-1_F * \xi = (\xi * 1_F ) ( 1_{\Psi} * \gamma ) ( \gamma * 1_{\Psi} )\,.
-\]
-A \emph{supernatural transformation} $\varphi: F \lto G$ between superfunctors $(F,\gamma_F), (G,\gamma_G)$ is a natural transformation making the following diagram commute:
-\[
-\xymatrix{
-F \Psi \ar[r]^-{\varphi \Psi}\ar[d]_-{\gamma_F} & G \Psi \ar[d]^-{\gamma_G}\\
-\Psi F \ar[r]_-{\Psi \varphi} & \Psi G
-}\,.
-\] 
+is a morphism $\phi: D \lto D'$ of matrix factorisations with the additional property that $E' \phi \simeq \phi$ and $\phi E \simeq E$ and there are homotopies
+\be
+\phi \gamma_i \simeq 0\,, \qquad \rho_i^\dagger \phi \simeq 0
+\ee
+These morphisms are composed by matrix multiplication.
 \end{definition}
 
-\begin{example}\label{example:Aassup} If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra there is a supercategory $\cat{A}$ with set of objects $|\cat{A}| = \mathbb{Z}_2$ and morphisms $\cat{A}(0,0) = \cat{A}(1,1) = A_0, \cat{A}(0,1) = \cat{A}(1,0) = A_1$ with the obvious composition and addition rules.
-The functor $\Psi$ is defined on objects by $\Psi(i) = i+1$ and on morphisms by the identity, while $\xi = 1$.
-\end{example}
+\begin{proposition} For potentials $(x,W),(y,V)$ there is an equivalence of categories
+\be\label{eq:equivalence_psi_final}
+\Psi: \cat{K}( k[x,y], V - W ) \lto \cat{L}( W, V )\,.
+\ee
+\end{proposition}
 
-Let $\cat{C}$ be a supercategory. For objects $X,Y \in \cat{C}$ we define the $\mathbb{Z}_2$-graded $k$-module
+\begin{definition} Given a $k$-algebra $R$ and integers $r \ge 1,m \ge 0, d \ge 0$ let
 \[
-\cat{C}^*(X,Y) = \prod_{i \in \mathbb{Z}_2} \cat{C}(X, \Psi^i Y)\,.
+\mathfrak{D}(R, k[x_1,\ldots,x_n],W)_{r,m,d}
 \]
-There is for any triple $X,Y,Z$ of objects a morphism of graded modules
-\[
-\cat{C}^*(Y,Z) \otimes_k \cat{C}^*(X, Y) \lto \cat{C}^*(X,Z)
-\]
-given for instance by $\varphi \otimes \psi \mapsto \xi \Psi( \varphi ) \psi$ when $\varphi, \psi$ are both of degree one.
-This makes $\cat{C}$ into a category enriched over the monoidal category of $\mathbb{Z}_2$-graded $k$-modules.
-
-There are isomorphisms of graded modules $\cat{C}^*(X, \Psi Y) \cong \Psi \cat{C}^*(X, Y) \cong \cat{C}^*(\Psi X, Y)$ where $\Psi V = V [1]$ denotes the grading shift on a $\mathbb{Z}_2$-graded $k$-module.
-For $\mathbb{Z}_2$-graded $k$-modules $V,W$ we write $\Hom^0_k(V, W)$ for the module of degree zero maps and $\Hom_k^*(V, W)$ for the $\mathbb{Z}_2$-graded module of homogeneous maps.
-If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $A^{\operatorname{op}}$ denotes the same underlying graded module with multiplication $f * g = (-1)^{|f||g|} gf$.
-
-\begin{definition} Let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra and $\cat{C}$ a supercategory.
-A \emph{left $A$-module in $\cat{C}$} is an object $X \in \cat{C}$ together with a morphism of $\mathbb{Z}_2$-graded algebras $A \lto \cat{C}^*(X,X)$.
-A \emph{morphism} of left $A$-modules is a morphism in $\cat{C}$ which commutes with the $A$-action in the obvious sense.
-The category of left $A$-modules in $\cat{C}$ is denoted $\cat{C}_A$.
-Right modules are defined similarly, using $A^{\operatorname{op}}$.
+denote the set of tuples \eqref{eq:hmfomegacd} over the ring $R[x]$ with all matrices of fixed size $2r$ and such that every matrix in the tuple has entries which are polynomials in $R[x]$ which involve only monomials $x^\alpha$ with $|\alpha| \le d$.
+Here $m$ is the number of Clifford actions.
 \end{definition}
 
-\begin{remark}\label{remark:supercat_idempcomp} Viewing $A$ as a supercategory $\cat{A}$ as in Example \ref{example:Aassup}, there is an equivalence between the category of $A$-modules in $\cat{C}$ and the category of superfunctors $\cat{A} \lto \cat{C}$ and supernatural transformations.
-\end{remark}
+\begin{lemma} Given $W \in k[x_1,\ldots,x_n]$ and integers $r \ge 1, m \ge 0, k \ge 0$ there is a finitely generated $k$-algebra $M(k[x],W)_{r,m,d}$ together with a natural bijection for any $k$-algebra $R$
+\[
+\Hom_{k}( M(k[x],W)_{r,m,d}, R ) \cong \mathfrak{D}( R, k[x], W )_{r,m,d}\,.
+\]
+\end{lemma}
 
-\begin{remark}\label{remark:idempotent_completion} The \emph{idempotent completion} $\cat{C}^\omega$ of a category $\cat{C}$ has as objects pairs $(X,e)$ consisting of an object $X \in \cat{C}$ and an idempotent endomorphism $e: X \lto X$.
-In $\cat{C}^\omega$ a morphism $\phi: (X,e) \lto (Y,e)$ is a morphism $\phi: X \lto Y$ satisfying $\phi e = \phi$ and $e \phi = \phi$.
-The identity on $(X,e)$ is $e$.
-There is a fully faithful functor $\iota: \cat{C} \lto \cat{C}^{\omega}, \iota(X) = (X,1_X)$ which is an equivalence if $\cat{C}$ is idempotent complete (i.e.
-all idempotents split in $\cat{C}$).
+\begin{definition} Given $W \in k[x_1,\ldots,x_n]$ and $r \ge 1,m \ge 0, d \ge 0$ we define the affine $k$-scheme
+\[
+\cat{M}( k[x], W )_{r,m,d} = \Spec\big( M(k[x],W)_{r,m, d} \big)\,.
+\]
+By definition there is an identification of the $k$-points of this scheme with a subset of the objects of the category $\cat{K}( k[x], W )$ since
+\begin{align*}
+\Big( \cat{M}( k[x], W )_{r,m,d} \Big)_k &\cong \Hom_k( M(k[x],W)_{r,m,d}, k )\\
+&\cong \mathfrak{D}( k, k[x], W )_{r,m,d}\\
+&\subseteq \cat{K}( k[x], W )\,.
+\end{align*}
+\end{definition}
 
-If $\cat{C}$ is a supercategory then there is a functor $\Psi^\omega: \cat{C}^\omega \lto \cat{C}^\omega$ defined on objects by $\Psi(X,e) = (\Psi X, \Psi e)$ and a natural isomorphism $\xi: \Psi^\omega \circ \Psi^\omega \lto 1_{\cat{C}^\omega}$ defined by $\xi_{(X,e)} = e \xi_X$.
-The tuple $(\cat{C}^\omega, \Psi^\omega, \xi^\omega)$ is a supercategory.
-\end{remark}
-
-For background on bicategories see \cite{bor94} and the references in \cite{lgdual}.
-We follow the notation of \cite{lgdual}, so that lower case letters $a,b, \ldots$ denote objects of a bicategory, while upper case letters $X,Y, \ldots$ and greek letters $\alpha, \beta, \ldots$ respectively denote $1$-morphisms and $2$-morphisms.
-Units are denoted $\Delta$, associators are $\alpha$, and unitors are $\lambda, \rho$.
-The composition of $Y,X$ is denoted $YX$ or $Y \circ X$.
-
-\begin{definition} A \emph{superbicategory} is a bicategory $\cat{B}$ together with the data:
-\begin{itemize}
-\item For each object $a$ a $1$-morphism $\Psi_a: a \lto a$ and a $2$-isomorphism $\xi_a: \Psi^2_a \lto \Delta_a$.
-\item For each $1$-morphism $X: a \lto b$ a natural $2$-isomorphism $\gamma_X: X \Psi_a \lto \Psi_b X$.
-\end{itemize}
-This data is required to satisfy the following axioms:
-\begin{itemize}
-\item For each composable pair $X,Y$ of $1$-morphisms the diagram
+\begin{theorem} Given potentials $(x,W), (y,V), (z,U)$ and $r,r' \ge 1$ and $m,m',d,d' \ge 0$ set
+\begin{align*}
+\cat{M}^{W,V}_{r,m,d} &= \cat{M}( k[x,y], V - W )_{r,m,d}\,,\\
+\cat{M}^{V,U}_{r',m',d'} &= \cat{M}( k[y,z], U - V )_{r',m',d'}\,,\\
+\cat{M}^{U,W}_{a, b,c} &= \cat{M}( k[x,z], U - W )_{a,b,c}\,.
+\end{align*}
+There are functions $f,g,h: \mathbb{N}^2 \lto \mathbb{N}$ and morphisms of affine schemes
 \[
-\xymatrix@C+2pc@R+1pc{
-(YX) \Psi \ar[rrr]^-{\gamma_{YX}} \ar[d]_-{\alpha} & & & \Psi ( YX )\\
-Y ( X \Psi ) \ar[r]_-{1_Y * \gamma_X} & Y( \Psi X ) \ar[r]_-{\alpha^{-1}} & ( Y \Psi ) X \ar[r]_-{\gamma_Y * 1_X} & (\Psi Y ) X \ar[u]_-{\alpha}
+C_{r,r',m,m',d,d'}: \cat{M}^{V,U}_{r,d} \times \cat{M}_{r',d'}^{W,V} \lto \cat{M}_{f(r,r'), g(m,m'),h(d,d')}^{U, W}
+\]
+such that the diagram of sets
+\[
+\xymatrix@C+1pc{
+\big( \cat{M}^{V,U}_{r,m,d} \big)_k \times \big( \cat{M}_{r',m',d'}^{W,V} \big)_k \ar[d] \ar[r]^{C_{r,r',m,m',d,d'}} & \big( \cat{M}_{f(r,r'), g(m,m'),h(d,d')}^{U, W} \big)_k \ar[d]\\
+\cat{K}( k[y,z], U - V ) \times \cat{K}( k[x,y], V - W ) \ar[d]_-{\Psi \times \Psi} & \cat{K}( k[x,z], U - W )\ar[d]^-{\Psi} \\
+\cat{L}( V, U ) \times \cat{L}( W, V ) \ar[r]_-{-\l-} & \cat{L}(W,U)
 }
@@
 commutes.
-\item For every object $a$, $\xi_a * 1_\Psi = 1_\Psi * \xi_a$.
-\item For every $1$-morphism $X : a \lto b$, $1_X * \xi_a = ( \xi_b * 1_X ) ( 1_\Psi * \gamma_X ) (\gamma_X * 1_\Psi )$.
+\end{theorem}
+
+\begin{itemize}
+\item The morphisms of schemes $C$ satisfy associativity on the nose. 
+\item Given $(x,W)$ there are integers $r,d$ depending on $(x,W)$ and a morphism of schemes
+\[
+\Spec(k) \lto \cat{M}^{W,W}_{r,d}
+\]
+which embeds the unit $1$-morphism, but we don't know any reasonable way to impose a condition involving this.
 \end{itemize}
-\end{definition}
 
-\begin{example} Supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
-\end{example}
-
-A superbicategory can be constructed out of a bicategory $\cat{B}$ in which the categories $\cat{B}(a,b)$ are all equipped with the structure of supercategories; see Appendix \ref{section:constructing_superbicategories}.
-
-\begin{example}\label{example:bicategory_m} There is a bicategory of $\mathbb{Z}_2$-graded $k$-algebras where $1$-morphisms are $\mathbb{Z}_2$-graded bimodules and $2$-morphisms are degree zero bimodule maps.
-Given a $B$-$A$-module $M$ the shift $M[1]$ has the grading $M[1]_i = M_{i+1}$ and the left and right action given by
+Set $\cat{M} = \cat{M}^{W,V}$ and let $\mathscr{H}\!om$ denote the Clifford bundle on $\cat{M} \times \cat{M}$ whose fiber over $( [X], [X'] )$ is $X^{\vee} \l X'$. Consider
 \[
-b \cdot m = (-1)^{|b|} bm, \qquad m \cdot a = (-1)^{|a|} m a\,.
-\]
-This is a functor $\Psi = (-)[1]$ on the category of $B$-$A$-bimodules and with $\xi = 1$ this defines the structure of a supercategory on this category of bimodules.
-The usual isomorphisms of bimodules $\tau$
-\begin{align}
-N[1] \otimes M &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto n \otimes m \label{eq:shift_iso_a}\\
-N \otimes M[1] &\lto (N \otimes M)[1], \qquad n \otimes m \mapsto (-1)^{|n|} n \otimes m\label{eq:shift_iso_b}
-\end{align}
-satisfy the conditions in Appendix \ref{section:constructing_superbicategories} and therefore give the bicategory of $\mathbb{Z}_2$-graded algebras and bimodules the structure of a superbicategory.
-\end{example}
-
-\begin{definition} Given two superbicategories $\cat{B}, \cat{C}$ a \emph{lax superfunctor} $\Phi: \cat{B} \lto \cat{C}$ is a lax functor together with, for each object $a$ in $\cat{B}$, a $2$-morphism
-\[
-\kappa_a: \Psi_{\Phi a} \lto \Phi( \Psi_a )
-\]
-satisfying two coherence conditions:
-\begin{itemize}
-\item[(a)] for all $a$, commutativity of
-\[
-\xymatrix@C+2pc{
-\Psi_{\Phi a} \Psi_{\Phi a} \ar[dd]_-{\xi}\ar[r]^-{\kappa * \kappa} & \Phi( \Psi_a ) \Phi( \Psi_a ) \ar[d]\\
-& \Phi( \Psi_a \Psi_a ) \ar[d]^-{\Phi(\xi)}\\
-\Delta_{\Phi a} \ar[r] & \Phi( \Delta_a )
+\xymatrix@C+3pc{
+\cat{M} \times \cat{M} \times \cat{M} \ar[r]^-{1 \times \Delta \times 1} & \cat{M} \times \cat{M} \times \cat{M} \times \cat{M}
 }
 \]
-\item[(b)] for each $1$-morphism $X: a \lto b$ in $\cat{B}$, commutativity of
+on the right hand side we have the vector bundle $\mathscr{H}\!om \boxtimes \mathscr{H}\!om$ which has an action of the bundle of Clifford algebras $C_m \boxtimes C_m$.
+Set $\varphi = 1 \times \Delta \times 1$ and consider the morphism of bundles of Clifford algebras given by the product
+\be\label{eq:morphism_of_clifford}
+\varphi^*( C_m \boxtimes C_m ) \lto C_m
+\ee
+Let $\mathscr{H}\!om$ be the bundle on $\cat{M}^3$ whose fiber over $([X_1], [X_2], [X_3])$ is $X_1^{\vee} \l X_3$. There is a morphism of vector bundles on $\cat{M}^3$
 \[
-\xymatrix@C+2pc{
-\Phi(X) \Psi_{\Phi a} \ar[d]_-{\gamma} \ar[r]^-{1 * \kappa} & \Phi(X) \Phi(\Psi_a) \ar[r] & \Phi( X \Psi_a ) \ar[d]^-{\Phi(\gamma)}\\
-\Psi_{\Phi b} \Phi(X) \ar[r]_-{\kappa * 1} & \Phi(\Psi_b) \Phi(X) \ar[r] & \Phi( \Psi_b X)
-}
+\varphi^*\big( \mathscr{H}\!om \boxtimes \mathscr{H}\!om \big) \lto \mathscr{H}\!om
 \]
-\end{itemize}
-A \emph{strong superfunctor} is a lax superfunctor with $\kappa_a$ an isomorphism for every object $a$.
-\end{definition}
+compatible with \eqref{eq:morphism_of_clifford} whose fiber is a finite model of composition.
 
-\subsection{The superbicategory of Landau-Ginzburg models}\label{section:superbicatLG}
-
-A polynomial $W \in k[x_1,\ldots,x_n]$ is a \emph{potential} if it satisfies the three conditions set out in \cite[Section 2.2]{lgdual}, the two most important being that the partial derivatives $\partial_{x_1} W, \ldots, \partial_{x_n} W$ form a quasi-regular sequence in $k[x]$ and that the quotient $J_W = k[x]/(\partial_{x_1} W, \ldots, \partial_{x_n} W)$ is a finitely generated free $k$-module.
-Typical examples are the ADE singularities \cite[I \S 2.4]{greuel} of which the simplest are the $A_N$-singularities $W_{A_N} = x_1^{N+1} + x_2^2 + \cdots + x_n^2$ .
-
-A \emph{matrix factorisation} of $W$ over $k[x]$ is a $\mathbb{Z}_2$-graded free $k[x]$-module $X = X^0 \oplus X^1$ together with an odd operator (the differential) $d_X: X \lto X$ satisfying $d_X^2 = W \cdot 1_X$.
-A matrix factorisation $(X,d_X)$ is \emph{finite rank} if the underlying free module is finitely generated.
-In this case we may, after choosing a homogeneous basis, write
-\[
-d_X = \begin{pmatrix} 0 & d_X^1 \\ d_X^0 & 0 \end{pmatrix}
-\]
-for matrices of polynomials $d_X^0, d_X^1$.
-Morphisms of matrix factorisations are degree zero $k[x]$-linear maps which commute with the differentials.
-There is a homotopy relation on morphisms, and the \emph{homotopy category} $\HMF(k[x],W)$ of matrix factorisations has as objects matrix factorisations and as morphisms the equivalence classes of morphisms of matrix factorisations up to homotopy.
-By $\hmf(k[x],W)$ we denote the full subcategory of finite rank matrix factorisations.
-For background we refer to \cite{yoshino98}.
-
-By $\hmf(k[x],W)^{\oplus}$ we denote the full subcategory of $\HMF(k[x],W)$ consisting of matrix factorisations which are direct summands (in the homotopy category) of finite rank matrix factorisations.
-Since $\HMF(k[x],W)$ is idempotent complete, there is an equivalence (see Remark \ref{remark:idempotent_completion} for the notation)
-\[
-\hmf(k[x],W)^\omega \lto \hmf(k[x],W)^{\oplus}
-\]
-sending a pair $(X,e)$ to an infinite rank matrix factorisation splitting the idempotent $e$.
-
-If $(X,d_X)$ is a matrix factorisation then so is $(X[1], -d_X)$, and this defines a functor $\Psi = (-)[1]$ on the homotopy category of matrix factorisations.
-Together with the identity $\xi: \Psi^2 \lto 1$ this makes $\HMF(k[x],W)$ and $\hmf(k[x],W)$ into supercategories.
-
-The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$.
-Given potentials $W \in k[x]$ and $V \in k[z]$ the supercategory $\cat{LG}(W,V)$ is
-\[
-\cat{LG}(W,V) = \hmf(k[x,z], V - W)^{\oplus}\,.
-\]
-Given a third potential $U \in k[y]$ the composition law is a functor
-\[
-\LG(W,V) \otimes_k \LG(V, U) \lto \LG(W, U)
-\]
-which sends a pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ to the tensor product
-\begin{equation}\label{eq:tensor_comp}
-Y \otimes X = ( Y \otimes_{k[z]} X, d_{Y \otimes X} = d_Y \otimes 1 + 1 \otimes d_X )\,.
-\end{equation}
-This statement requires some care: $k[x,y,z]$ is an infinite rank free module over $k[x,z]$ and so $Y \otimes X$ is an infinite rank matrix factorisation of $U - W$ over $k[x,z]$.
-However one can prove that $Y \otimes X$ is a direct summand of a finite rank matrix factorisation \cite{dm1102.2957} and therefore a valid object in $\LG(W,U)$.
-
-Let $W \in k[x_1,\ldots,x_n]$ be a potential and $W(x')$ the same polynomial but in a second set of variables $x_1',\ldots,x_n'$.
-Using formal symbols $\Theta_i$ of odd degree, we define the $k[x,x']$-module
-\[
-\Delta_W = \bigwedge \big( \bigoplus_{i=1}^n k[x,x'] \cdot \Theta_i \big)\,.
-\]
-Equipped with a certain differential (see \cite{lgdual}) this is a matrix factorisation of $W(x) - W(x')$ and defines the unit in $\cat{LG}(W,W)$ for composition of $1$-morphisms.
-For the associator and unitor maps $\rho: X \otimes \Delta_W \lto X$ and $\lambda: \Delta_V \otimes X \lto X$ we also refer to \emph{ibid.}
-
-\begin{lemma} $\LG$ is a superbicategory.
-\end{lemma}
-\begin{proof}
-The categories $\LG(W,V)$ are all naturally supercategories, and the same isomorphisms as in \eqref{eq:shift_iso_a}, \eqref{eq:shift_iso_b} define the necessary natural isomorphisms $\tau$ to equip $\LG$ with the structure of a superbicategory with $\Psi_W = \Delta_W[1]$, using Appendix \ref{section:constructing_superbicategories}.
-\end{proof}
-
-The superbicategory structure on $\LG$ is used implicitly in \cite[Section 7]{lgdual}.
-
-\subsection{Clifford algebras}\label{section:clifford_algs}
-
-In a cut system the composition rule produces objects which are representations of Clifford algebras.
-We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}.
-For $n \ge 0$ the Clifford algebra $A_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $a_1,\ldots,a_n$ and $a_1^\dagger, \ldots, a_n^\dagger$ subject to the following relations
-\[
-[a_i, a_j] = 0, \qquad [a_i^\dagger, a_j^\dagger] = 0, \qquad [a_i, a_j^\dagger] = \delta_{ij}\,.
-\]
-for all $1 \le i, j \le n$.
-In this paper all our commutators are graded, $[a,b] = ab - (-1)^{|a||b|} ba$.
-We set $A_0 = k$.
-The algebras $A_n$ are Morita trivial in the sense that they are isomorphic to the endomorphism algebras of finite rank free $\mathbb{Z}_2$-graded $k$-modules.
-
-Indeed, if $F_n = k \theta_1 \oplus \cdots \oplus k \theta_n$ with $|\theta_i| = 1$ for all $i$, then
-
-\begin{lemma} With $S_n = \bigwedge F_n$ the map $A_n \lto \End_k(S_n)$ defined by
-\[
-a_i \mapsto \theta_i \wedge (-), \qquad a_i^\dagger \mapsto \theta_i^*\, \lrcorner\, (-)
-\]
-is an isomorphism of $\mathbb{Z}_2$-graded $k$-algebras, where $\lrcorner$ denotes contraction.
-\end{lemma}
-
-In particular this means that every $\mathbb{Z}_2$-graded $A_n$-module is isomorphic to $S_n \otimes_k V$ for some $\mathbb{Z}_2$-graded $k$-module $V$. From the isomorphism of $k$-modules
-\[
-S_m \otimes_k S_n = \bigwedge F_m \otimes_k \bigwedge F_n \cong \bigwedge F_{m+n} = S_{m+n}
-\]
-we deduce an isomorphism of algebras
-\begin{equation}\label{eq:algebra_A_additive}
-A_m \otimes_k A_n \cong A_{m+n}\,.
-\end{equation}
-Given $m, n \ge 0$ we introduce notation for the $A_m$-$A_n$-bimodule
-\begin{equation}
-S_{m,n} = S_m \otimes_k S_n^*
-\end{equation}
-where $S_n^* = \Hom_k(S_n, k)$. There is an isomorphism of $A_l$-$A_n$-bimodules
-\begin{equation}\label{eq:isosbimodule}
-S_{l,m} \otimes_{A_m} S_{m,n} = S_l \otimes_k S_m^* \otimes_{A_m} S_m \otimes_k S_n^* \cong S_{l,n}\,.
-\end{equation}
-In the case $k = \mathbb{C}$, $S_n$ is often referred to as the \emph{spinor representation} \cite[p.14]{friedrich}.
-
-\begin{remark} Recall that given a finite rank free $k$-module $V$ and a symmetric bilinear form $B: V \otimes_k V \lto k$ the associated Clifford algebra $\operatorname{Cl}(V, B)$ is the associative $k$-algebra generated by the elements of $V$ subject to the relations
-\[
-vw + wv = B(v,w) \cdot 1\,.
-\]
-This is a $\mathbb{Z}_2$-graded $k$-algebra when we assign $|v| = 1$ for all $v \in V$ and $|1| = 0$.
-If we take $V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then $A_n$ is the Clifford algebra of the pair $(V,B)$.
-\end{remark}
-
-\subsection{The Clifford thickening}
-
-Let $\cat{C}$ be a small idempotent complete supercategory.
-We construct a new supercategory $\cat{C}^\bullet$ called the \emph{Clifford thickening} in which the objects are pairs $(X,n)$ of an integer $n \ge 0$ and a left $A_n$-module $X$ in $\cat{C}$.
-
-We will need the operation of tensoring objects of $\cat{C}$ with $k$-modules.
-This is standard material, which is recalled in Appendix \ref{section:tensorproduct_supcat}.
-The upshot is that if $A$ is a Morita trivial $\mathbb{Z}_2$-graded $k$-algebra and if $X \in \cat{C}$ is a left $A$-module, while $V$ is a $\mathbb{Z}_2$-graded right $A$-module (in the usual sense, i.e.
-in the category of $k$-modules) then there is an object $V \otimes_A X$ in $\cat{C}$ which is functorial in both $V$ and $X$.
-Morever if $V$ is a $B$-$A$-bimodule then $V \otimes_A X$ is naturally a left $B$-module, and so on.
-If $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{C}_A$ denotes the supercategory of $A$-modules in $\cat{C}$ with $A$-linear maps.
-
-Similarly to Example \ref{example:bicategory_m} there is a superbicategory $\cat{M}$ of Morita trivial $\mathbb{Z}_2$-graded $k$-algebras: $1$-morphisms are $\mathbb{Z}_2$-graded bimodules which are finitely generated and projective over $k$ and $2$-morphisms are degree zero bimodule maps.
-
-\begin{proposition} The assignment of the supercategory $\cat{C}_A$ to an algebra $A$ and of the superfunctor $\Phi_V = V \otimes_A (-)$ to a $B$-$A$-bimodule $V$ determines a strong superfunctor
-\[
-\Phi^{\cat{C}}: \cat{M} \lto \Cat^{\operatorname{sup}}_k
-\]
-to the superbicategory of small supercategories and superfunctors.
-\end{proposition}
-\begin{proof}
-The isomorphism $\Phi_W \circ \Phi_V \cong \Phi_{W \otimes V}$ is given by Lemma \ref{lemma:assoctensor}, and apart from that the only checking that needs to be done are straightforward coherence diagrams.
-\end{proof}
-
-Next we construct a strong functor into $\cat{M}$ which picks out the Clifford algebras.
-
-\begin{definition}
-Let $\mathbb{N}$ denote the category of integers $n \ge 0$ with a unique morphism $\phi_{m,n}: n \lto m$ for each pair $m,n$. %This category is monoidal with $m \otimes n = m + n$.
-\end{definition}
-
-We view $\mathbb{N}$ as a bicategory with only identity $2$-morphisms.
-
-\begin{lemma} There is a strong functor $\mathbb{N} \lto \cat{M}$ defined by
-\begin{gather*}
-n \mapsto A_n = \End_k( S_n ),\\
-\phi_{m,n} \mapsto S_{m,n} = S_m \otimes_k S_n^*\,.
-\end{gather*}
-\end{lemma}
-
-The composite of these strong functors is a strong functor
-\begin{equation}\label{eq:strongfunctorgroth}
-\xymatrix@C+1pc{
-\mathbb{N} \ar[r] & \cat{M} \ar[r]^-{\Phi^{\cat{C}}} & \Cat^{\operatorname{sup}}_k
-}
-\end{equation}
-sending $n$ to the category of left $A_n$-modules in $\cat{C}$ and $\phi_{m,n}$ to the functor $S_{m,n} \otimes_{A_n} -$.
-There is a close connection between strong functors into the bicategory of small categories, and what are called cofibered categories, given by the Grothendieck construction \cite{vistoli}.
-
-\begin{definition} The \emph{Clifford thickening} $\cat{C}^\bullet$ of the supercategory $\cat{C}$ is the category which results from the Grothendieck construction applied to the strong functor \eqref{eq:strongfunctorgroth}.
-\end{definition}
-
-More concretely $\cat{C}^\bullet$ is the category with objects all pairs $(X,n)$ of an integer $n \ge 0$ and an object $X \in \cat{C}$ with a left $A_n$-action.
-A morphism $\alpha: (X,n) \lto (Y,m)$ is a morphism of $A_m$-modules $\alpha: S_{m,n} \otimes_{A_n} X \lto Y$.
-Composition of a pair of morphisms
-\begin{equation}\label{eq:comp_chain0}
-\xymatrix{
-(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
-}
-\end{equation}
-is given by the morphism of $A_l$-modules
-\begin{equation}\label{eq:comp_chain1}
-\xymatrix@C+1pc{
-S_{l, n} \otimes_{A_n} X \ar[r]^-{\cong} & (S_{l,m} \otimes_{A_m} S_{m,n}) \otimes_{A_n} X \ar[d]^-{\cong}\\
-& S_{l,m} \otimes_{A_m} ( S_{m,n} \otimes_{A_n} X ) \ar[r]^-{ 1 \otimes \alpha } & S_{l,m} \otimes_{A_m} Y \ar[r]^-{\beta} & Z\,.
-}
-\end{equation}
-There is a canonical functor $p: \cat{C}^\bullet \lto \mathbb{N}$ defined by $p(X,n) = n$, which defines a cofibered category over $\mathbb{N}$ by the definition of the Grothendieck construction.
-
-\begin{lemma} $\cat{C}^\bullet$ is a supercategory and the functor $\iota: \cat{C} \lto \cat{C}^\bullet$ defined by $\iota(X) = (X,0)$ is an equivalence of supercategories.
-\end{lemma}
-\begin{proof}
-The supercategory structure is given by the functor $\Psi: \cat{C}^\bullet \lto \cat{C}^\bullet$ where $\Psi(X,n) = ( \Psi X, n )$ and $\Psi X$ has the $A_n$-action given by Definition \ref{defn:psimodule}.
-
-The functor $\iota$ is fully faithful.
-To see that it is essentially surjective, let $(X,n) \in \cat{C}^\bullet$ be given.
-We show that $(X,n)$ is isomorphic to $(\widetilde{X},0)$ where $\widetilde{X} = S_n^* \otimes_{A_n} X$.
-This follows from the fact that the isomorphism
-\[
-S_n \otimes_k \widetilde{X} = S_n \otimes_k S_n^* \otimes_{A_n} X \cong X
-\]
-defines an isomorphism $(\widetilde{X}, 0) \lto (X,n)$ in $\cat{C}^\bullet$.
-\end{proof}
-
-\begin{definition}\label{defn:idempotent_e} For $n \ge 0$ let $e_n \in A_n$ denote the element
-\[
-e_n = a_1^\dagger \cdots a_n^\dagger a_n \cdots a_1\,.
-\]
-This is the idempotent corresponding to the summand $k \cdot 1$ of $S_n$.
-\end{definition}
-
-\begin{remark}\label{remark:tensor_and_idempotent} It may seem odd to labour to construct a category $\cat{C}^\bullet$ equivalent to $\cat{C}$.
-The point is that while $(X,n)$ and $(\widetilde{X}, 0)$ are isomorphic in $\cat{C}^\bullet$, they still represent quantitatively different states of knowledge.
-If $\widetilde{X}$ is known then $X$ may be easily constructed by taking direct sums, but if $X$ is known then forming the tensor product $\widetilde{X}$ is equivalent to splitting the idempotent $e_n: X \lto X$ and this requires work.
-% If $X$ is an $A_n$-module in $\cat{C}$, then the defining property of $\widetilde{X} = S_n^* \otimes_{A_n} X$ is that there is a morphism $\eta: X \lto \widetilde{X}$ satisfying $\eta \circ a_i = 0$ for all $1 \le i \le n$ and which is universal with this property.
-That is, given any morphism $\delta:X  \lto Y$ with this property there is a unique morphism $\kappa: \widetilde{X} \lto Y$ such that $\kappa \circ \eta = \delta$.
-A morphism $\delta: X \lto Y$ satisfies $\delta \circ a_i = 0$ for $1 \le i \le n$ if and only if $\delta \circ ( 1 - e_n ) = 0$.
-
-For each $n$ the fiber of the functor $p: \cat{C}^\bullet \lto \mathbb{N}$ over $n$ is $\cat{C}_{A_n}$. We may depict the cofibered category $p$ as follows:
-\begin{equation}\label{eq:cofibered_diagram}
-\xymatrix@C+3pc@R+1pc{
-\cat{C} \ar@{.}[d] \ar@<1ex>[rrr]^-{E} & & & \cat{C}_{A_n} \ar@{.}[d] \ar@<1ex>[lll]^-{F}\\
-0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & n \ar@{.>}@<0.8ex>[l]
-}\,.
-\end{equation}
-The transport between the fibers is given by the equivalences
-\[
-E(-) = S_{n} \otimes_k (-), \qquad F(-) = S^*_{n} \otimes_{A_n} (-)\,.
-\]
-While these functors are adjoint, and therefore uniquely determine one another, we have explained that there is a fundamental asymmetry between them from the point of view of computation: knowledge of an object of $\cat{C}^\bullet$ over $n$ represents a state of higher uncertainty than knowledge of an object over $m < n$, given that in the end both objects ``only'' contain the information of the corresponding object $\widetilde{X}$ over zero, but more work is necessary to extract this information from an object of $\cat{C}_{A_n}$ than from an object of $\cat{C}_{A_m}$.
-\end{remark}
-
-\begin{remark}\label{remark:tensor_in_steps} Given $(X,n) \in \cat{C}^\bullet$, one way to compute the tensor product
-\[
-S_{n+1,n} \otimes_{A_n} X = (S_{n+1} \otimes_k S_n^*) \otimes_{A_n} X \cong S_{n+1} \otimes_k ( S_n^* \otimes_{A_n} X )
-\]
-is to compute $S_n^* \otimes_{A_n} X$ and then take direct sums. Alternatively,
-\begin{align*}
-S_{n+1,n} \otimes_{A_n} X &= S_{n+1} \otimes_k S_n^* \otimes_{A_n} X\\
-&\cong S_1 \otimes_k S_n \otimes_k S_n^* \otimes_{A_n} X \\
-&\cong S_1 \otimes_k A_n \otimes_{A_n} X \\
-&\cong S_1 \otimes_k X\,.
-\end{align*}
-That is, if we equip $S_1 \otimes_k X = X \oplus \Psi X$ with an $A_{n+1} \cong A_1 \otimes A_n$ action by making $A_n$ act on $X$ and $A_1$ act on $S_1$, this computes the tensor product.
-In a similar way, $S_{n-1,n} \otimes_{A_n} X$ is computed by splitting the idempotent $a_1^\dagger a_1$ on $X$, so that the functor $F$ of \eqref{eq:cofibered_diagram} may be computed in $n$ steps by splitting $a_1^\dagger a_1$, then $a_2^\dagger a_2$, and so on.
-\end{remark}
-%TODO note: $S_{m,n} \otimes_{A_n}$ is an equivalence so all fibers are isomorphic to $\cat{C}$.
-
-\begin{remark} An alternative description of morphisms in $\cat{C}^\bullet$ follows from Lemma \ref{lemma:morphisms_two_forms}.
-This result tells us that given an $A_n$-module $X$ and $A_m$-module $Y$ in $\cat{C}$ there is a bijection between morphisms of $A_m$-modules $\alpha: S_{m,n} \otimes_{A_n} X \lto Y$ and morphisms
-\[
-\alpha_0: X \lto Y \text{ satisfying } \alpha_0 \circ a_i = 0 \text{ for } 1 \le i \le n \text{ and } a_i^\dagger \circ \alpha_0 = 0 \text{ for } 1 \le i \le m\,.
-\]
-The bijection is defined by sending $\alpha$ to the composite ($\iota$ is defined by $\iota(1) = 1 \otimes 1^*$)
-\[
-\xymatrix@C+2pc{
-X \cong A_n \otimes_{A_n} X \ar[r]^-{\iota \otimes 1} & S_{m,n} \otimes_{A_n} X \ar[r]^-{\alpha} & Y
-}\,
-\]
-Given a chain of composable morphisms as in \eqref{eq:comp_chain0} there are corresponding morphisms $\alpha_0: X \lto Y$ and $\beta_0: Y \lto Z$ and it can be checked that the morphism corresponding under the bijection of Lemma \ref{lemma:morphisms_two_forms} to the composite $\beta \circ \alpha$ given in \eqref{eq:comp_chain1} is
-\[
-(\beta \circ \alpha)_0 = \beta_0 \circ \alpha_0\,.
-\]
-\end{remark}
-
-\section{Cut systems}\label{section:cut_systems}
-
-We begin with the definition of cut functors.
-
-\begin{definition} Given supercategories $\cat{C}_1,\cat{C}_2,\cat{C}_3$ a \emph{superfunctor} $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3$ is a functor together with natural isomorphisms
-\begin{align*}
-\tau &: T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T,\\
-\tau &: T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
-\end{align*}
-making the following diagrams commute:
-\begin{equation}\label{eq:psicomp1}
-\xymatrix@R+1pc@C+1pc{
-T( 1 \otimes \Psi^2 ) \ar[r]^-{\tau}\ar[d]_-{T(1 \otimes \xi)} & \Psi T( 1 \otimes \Psi ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
-T \ar[rr]_-{1_T} & & T
-}
-\end{equation}
-\begin{equation}\label{eq:psicomp2}
-\xymatrix@R+1pc@C+1pc{
-T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\psi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
-T \ar[rr]_-{1_T} & & T
-}
-\end{equation}
-\begin{equation}\label{eq:psicomp3}
-\xymatrix@R+1pc@C+1pc{
-T( \Psi \otimes \Psi ) \ar[r]^-{\tau}\ar[d]_-{-\tau} & \Psi T( 1 \otimes \Psi ) \ar[d]^-{\tau}\\
-\Psi T( \Psi \otimes 1 ) \ar[r]_-{\tau} & \Psi^2 T
-}
-\end{equation}
-
-\end{definition}
-
-\begin{definition}\label{defn:cutfunctor1} A \emph{cut functor of degree $t$} on a triple $\cat{C}_1, \cat{C}_2,\cat{C}_3$ of idempotent complete small supercategories is a superfunctor $T: \cat{C}_1 \otimes_k \cat{C}_2 \lto \cat{C}_3^\bullet$ such that
-\[
-\xymatrix{
-\cat{C}_1 \times \cat{C}_2 \ar[r]^-{T} & \cat{C}_3^\bullet \ar[r]^-{p} & \mathbb{N}
-}
-\]
-sends every object to the integer $t \in \mathbb{N}$.
-\end{definition}
-
-With the above notation:
-
-\begin{proposition}\label{prop:extend_cut_functor} Given a cut functor $T$ of degree $t$ on $\cat{C}_1, \cat{C}_2,\cat{C}_3$ there is a canonical superfunctor $\widetilde{T}: \cat{C}_1^\bullet \otimes_k \cat{C}_2^\bullet \lto \cat{C}_3^\bullet$ with the property that the diagram
-\[
-\xymatrix{
-\cat{C}_1 \times \cat{C}_2 \ar[dr]_-{\iota \times \iota} \ar[rr]^-{T} & & \cat{C}_3^\bullet\\
-& \cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[ur]_-{\widetilde{T}}
-}
-\]
-commutes, and for every pair of objects $X \in \cat{C}_1^\bullet$ and $Y \in \cat{C}_2^\bullet$
-\[
-p \widetilde{T}( X, Y ) = p( X ) + p( Y ) + t\,.
-\]
-We refer to $\widetilde{T}$ as the \emph{extension} of $T$.
-%and
-%\[
-%\xymatrix@C+2pc{
-%\cat{C}_1^\bullet \times \cat{C}_2^\bullet \ar[d]_-{p \times p}\ar[rr]^-{\widetilde{T}} & & \cat{C}_3^\bullet \ar[dd]^-{p}\\
-%\mathbb{N} \times \mathbb{N} \ar[d]_-{\cong}\\
-%\mathbb{N} \times \{ * \} \times \mathbb{N} \ar[r]_-{1 \times t \times 1} & \mathbb{N} \times \mathbb{N} \times \mathbb{N} \ar[r]_-{\otimes} & \mathbb{N}
-%}
-%\]
-%commute. 
-\end{proposition}
-\begin{proof}
-The proof is given in Appendix \ref{app:proof_cut_extension}.
-\end{proof}
-
-We will use \emph{effectively computable} as a synonym for the precise notion of a \emph{computable} function \cite{enderton}, since ``computable'' often has a more colloquial meaning in our context.
-
-% This is the definition from cutsys10
-\begin{definition} A \emph{cut system} $\cat{A}$ is determined by the following data:
-\begin{itemize}
-\item A class $|\cat{A}|$ of objects and for each object $a$ an integer $\pi(a) \ge 0$.
-\item For each pair $a,b$ of objects a small idempotent complete supercategory $\cat{A}(a,b)$. 
-\item For each triple $a,b,c$ of objects a cut functor of degree $\pi(b)$
-\[
-T: \cat{A}(a,b) \otimes_k \cat{A}(b,c) \lto \cat{A}(a,c)^{\bullet}\,.
-\]
-The image of a pair $X \otimes Y$ under the canonical extension
-\[
-\widetilde{T}: \cat{A}(a,b)^\bullet \otimes_k \cat{A}(b,c)^\bullet \lto \cat{A}(a,c)^\bullet
-\]
-is denoted $Y \l X$ and is called the \emph{cut of $Y$ and $X$ along $b$}.
-\item For each object $a$, an object $\Delta_a \in \cat{A}(a,a)$.
-\item For objects $a,b,c,d$ a natural isomorphism $\alpha$ as shown below:
-\[
-\xymatrix@C+2pc{
-\cat{A}(a,b) \times \cat{A}(b,c) \times \cat{A}(c,d) \ar[d]_-{T \times 1} \ar[r]^-{1 \times T} & \cat{A}(a,b) \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\alpha}\\
-\cat{A}(a,c)^\bullet \times \cat{A}(c,d) \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
-}
-\]
-That is, for $X \in \cat{A}(a,b), Y \in \cat{A}(b,c), Z \in \cat{A}(c,d)$ an isomorphism
-\[
-\alpha_{Z,Y,X}: ( Z \l Y ) \l X \lto Z \l ( Y \l X )
-\]
-of $A_{\pi(b)} \otimes_k A_{\pi(c)}$-modules in $\cat{A}(a,d)$, natural in all three variables.
-\item For objects $a,b$ natural isomorphisms $\mu, \eta$ as shown below:
-\[
-\xymatrix@C+2pc{
-1 \times \cat{A}(a,b) \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b) \ar@{=>}@<4ex>[l]_-{\eta} \ar@{=>}@<-4ex>[r]^-{\mu} \ar[d]^-{\iota} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b) \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
-\cat{A}(a,a) \times \cat{A}(a,b) \ar[r]_-{T} & \cat{A}(A,B)^\bullet & \cat{A}(a,b) \times \cat{A}(b,b) \ar[l]^-{T}
-}
-\]
-where $1$ is the category with one object and one morphism and $\iota_{\Delta}$ is the functor sending this object to $\Delta$. That is, for each $X \in \cat{A}(a,b)$ a pair of isomorphisms
-\begin{equation}\label{eq:defn_cutsys_lambda}
-\mu: X \lto \Delta_b \l X, \quad \eta: X \lto X \l \Delta_a
-\end{equation}
-in $\cat{A}(a,b)^\bullet$ natural in $X$.
-\end{itemize}
-This data is subject to the following coherence conditions:
-\begin{itemize}
-\item[(1)] For objects $a,b,c,d,e$ and $X \in \cat{A}(a,b),Y \in \cat{A}(b,c),Z \in \cat{A}(c,d),Q \in \cat{A}(d,e)$, commutativity of the diagram
-\begin{equation}
-\xymatrix@C+2pc{
-((Q \l Z) \l Y ) \l X \ar[d]_-{\alpha_{Q \l Z, Y, X}}\ar[r]^-{\alpha_{Q,Z,Y} \l 1} & (Q \l (Z \l Y)) \l X \ar[r]^-{\alpha_{Q, Z \l Y, X}} & Q \l ( ( Z \l Y ) \l X ) \ar[d]^-{1 \l \alpha_{Z,Y,X}}\\
-(Q \l Z) \l (Y \l X) \ar[rr]_-{\alpha_{Q, Z, Y \l X}} & & Q \l ( Z \l ( Y \l X ) )
-}
-\end{equation}
-Note that when we write $\alpha_{Q, Z \l Y, X}$ we refer only the underlying object of $Z \l Y$.
-\item[(2)] For objects $a,b$ and $X \in \cat{A}(a,b), Y \in \cat{A}(b,c)$ commutativity of the diagram
-\begin{equation}\label{eq:unitor_constraint_cut}
-\xymatrix{
-(Y \l \Delta_b ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
-& Y \l X \ar[ul]^-{\eta \l 1_X} \ar[ur]_-{1_Y \l \mu}
-}
-\end{equation}
-\item[(3)] commutativity of \eqref{eq:psiunitor1},\eqref{eq:psiunitor2} for every $X$ and \eqref{eq:psithirdlastdia}, \eqref{eq:psimiddledia}, \eqref{eq:psilastdia} for every composable triple $X,Y,Z$.
-\end{itemize}
-Finally, the data is subject to three computability conditions:
-\begin{itemize}
-\item[(1)] For each pair of objects $a,b$ the category $\cat{A}(a,b)$ is effectively computable, in the sense that the morphisms and objects are described by finite data and the composition rule is computable.
-\item[(2)] For each triple $a,b,c$ of objects the associated cut functor is effectively computable.
-In particular, for $1$-morphisms $Y$ and $X$ the object $Y \l X$ and its Clifford action are effectively computable from $X$ and $Y$.
-\item[(3)] The associators and unitors are effectively computable from their arguments.
-\end{itemize}
-\end{definition}
-
-\begin{remark} To give natural isomorphisms \eqref{eq:defn_cutsys_lambda} in $\cat{A}(a,b)^\bullet$ is equivalent to giving natural isomorphisms in $\cat{A}(a,b)$
-\begin{equation}\label{eq:unitor_tilde_pre}
-\mu: S_{\pi(b)} \otimes_k X \lto \Delta_b \l X, \quad \eta: S_{\pi(a)} \otimes_k X \lto X \l \Delta_a
-\end{equation}
-which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.
-
-By Lemma \ref{lemma:morphism_out_1} such morphisms correspond bijectively to morphisms in $\cat{A}(a,b)$
-\begin{equation}\label{eq:unitor_tilde}
-\mu_0: X \lto \Delta_b \l X, \quad \eta_0: X \lto X \l \Delta_a
-\end{equation}
-satisfying respectively $a_i^\dagger \circ \mu_0 = 0$ for $1 \le i \le m$ and $a_i^\dagger \circ \eta_0 = 0$ for $1 \le i \le n$.
-The reason to introduce these maps is that commutativity of \eqref{eq:unitor_constraint_cut} can be more conveniently expressed in terms of the maps in \eqref{eq:unitor_tilde}, see Lemma \ref{lemma:unitor_check_help} below.
-\end{remark}
-
-Let $\cat{A}$ be a cut system.
-There is a superbicategory $\cat{A}^\bullet$ with objects the class of objects of $\cat{A}$ and with $1$- and $2$-morphisms defined by $\cat{A}^\bullet(a,b) = \cat{A}(a,b)^\bullet$.
-The units of $\cat{A}^\bullet$ are the objects $\Delta_a$ in the cut system, and the composition in the bicategory is given by the canonical extensions $\widetilde{T}$.
-To complete the definition of a superbicategory it only remains to give the associators and unitors, and the super-structure.
-
-\begin{lemma} Given objects $a,b,c,d$ the natural isomorphism $\alpha$ canonically extends to a natural isomorphism $\widetilde{\alpha}$ as in the diagram
-\[
-\xymatrix@C+2pc{
-\cat{A}(a,b)^\bullet \times \cat{A}(b,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[d]_-{\widetilde{T} \times 1} \ar[r]^-{1 \times \widetilde{T}} & \cat{A}(a,b)^\bullet \times \cat{A}(b,d)^\bullet \ar[d]^{\widetilde{T}} \ar@{=>}[dl]^-{\widetilde{\alpha}}\\
-\cat{A}(a,c)^\bullet \times \cat{A}(c,d)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(a,d)^\bullet
-}
-\]
-\end{lemma}
-\begin{proof}
-Suppose $(X,n) \in \cat{A}(a,b)^\bullet, (Y,m) \in \cat{A}(b,c)^\bullet$ and $(Z,t) \in \cat{A}(c,d)^\bullet$ are given.
-The underlying object of $((Z,t) \l (Y, m)) \l (X,n)$ is $(Z \l Y) \l X$, and it is clear that $\alpha_{Z,Y,X}$ is $A_t \otimes A_m \otimes A_n$-linear and therefore defines an isomorphism in $\cat{A}(a,d)^\bullet$
-\[
-\alpha_{Z,Y,X}: ((Z,t) \l (Y, m)) \l (X,n) \lto (Z,t) \l ((Y, m) \l (X,n))\,.
-\]
-Naturality is straightforward.
-\end{proof}
-
-\begin{lemma} Given objects $a,b$ the natural isomorphisms $\eta, \mu$ canonically extend to natural isomorphisms $\widetilde{\eta}, \widetilde{\mu}$ as in the diagram
-\[
-\xymatrix@C+2pc{
-1 \times \cat{A}(a,b)^\bullet \ar[d]_-{\iota_{\Delta} \times 1} & \cat{A}(a,b)^\bullet \ar@{=>}@<4ex>[l]_-{\widetilde{\eta}} \ar@{=>}@<-4ex>[r]^-{\widetilde{\mu}} \ar[d]^-{1} \ar[l]_-{\cong} \ar[r]^-{\cong} & \cat{A}(a,b)^\bullet \times 1 \ar[d]^-{1 \times \iota_{\Delta}}\\
-\cat{A}(a,a)^\bullet \times \cat{A}(a,b)^\bullet \ar[r]_-{\widetilde{T}} & \cat{A}(A,B)^\bullet & \cat{A}(a,b)^\bullet \times \cat{A}(b,b)^\bullet \ar[l]^-{\widetilde{T}}
-}
-\]
- \end{lemma}
-\begin{proof}
-Let $(X,n) \in \cat{A}(a,b)^\bullet$.
-Forgetting the $A_n$-action on $X$, we have isomorphisms $\eta$ and $\mu$ as in \eqref{eq:unitor_tilde_pre}, which are respectively $A_{\pi(b)}$ and $A_{\pi(a)}$-linear.
-Since these isomorphisms are natural, they are automatically $A_n$-linear.
-Verifying that these isomorphisms are natural with respect to the larger class of morphisms in $\cat{A}(a,b)^\bullet$ is straightforward.
-\end{proof}
-
-The supercategory structure is given as part of the cut system, so we have:
-
-% The above definition of a cut system is from cutsys10. This is by p.11 there something which gives rise to a cut system in the sense of cutsys6, which is proved there to define a superbicategory.
-\begin{proposition} Given a cut system $\cat{A}$, $\cat{A}^\bullet$ is a superbicategory.
-\end{proposition}
-\begin{proof}
-This follows from Lemma \ref{lemma:constructingsuper}, with associator $\widetilde{\alpha}$ and unitors $\lambda =\widetilde{\mu}^{-1}, \rho = \widetilde{\eta}^{-1}$.
-The coherence follows from the coherence axioms of the cut system.
-\end{proof}
-
-We often confuse a cut system $\cat{A}$ with the associated superbicategory.
-For example, we refer to objects $X$ of $\cat{A}(a,b)^\bullet$ as a $1$-morphisms.
-To distinguish objects of the original category $\cat{A}(a,b)$ we refer to these objects as \emph{normal} or \emph{cut-free} $1$-morphisms.
-We keep the notation $Y \l X$ for the composition rule in $\cat{A}^\bullet$.
-
-The following lemma is useful in verifying the unitor constraint.
-
-\begin{lemma}\label{lemma:unitor_check_help} The commutativity of \eqref{eq:unitor_constraint_cut} is equivalent to commutativity of
-\begin{equation}\label{eq:unitor_check_help1}
-\xymatrix@C+1pc{
-(Y \l \Delta_b) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_b \l X )\\
-Y \l X \ar[u]^-{\eta_0 \l 1} & Y \l X \ar[l]^-{e_{\pi(b)}} \ar[r]_-{e_{\pi(b)}} & Y \l X \ar[u]_-{1 \l \mu_0}
-}
-\end{equation}
-where $e_{\pi(b)}$ is the idempotent of Definition \ref{defn:idempotent_e}.
-\end{lemma}
-\begin{proof}
-Let $m = \pi(b)$.
-Then $(Y \l \Delta_b) \l X$ has two $A_m$ actions, one from $Y \l \Delta_b$ which we denote by $A_{m_1}$, and the other from the cut with $X$ which we denote by $A_{m_2}$.
-By definition of the canonical extension $\widetilde{T}$ in Appendix \ref{app:proof_cut_extension}, $\eta \l 1$ is the $A_{m_1+m_2}$-linear morphism
-\[
-\eta: S_{m_1 + m_2, m_2} \otimes_{A_{m_2}} ( Y \l X ) \lto (Y \l \Delta_b ) \l X
-\]
-which corresponds under Lemma \ref{lemma:morphisms_two_forms} to
-\[
-\xymatrix@C+1pc{
-Y \l X \ar[r]^-{e_m} & Y \l X \ar[r]^-{\eta_0 \l 1} & (Y \l \Delta_b) \l X
-}\,.
-\]
-Applying the same logic to $\mu$ completes the proof.
-\end{proof}
-
-In a cut system the unitors $\mu, \eta$ go in the opposite direction to what one would expect from the conventions of bicategories.
-This is because it is more natural to describe morphisms out of a cut-free $1$-morphism and into a $1$-morphism carrying a nontrivial Clifford representation, than in the other direction.
-
-\subsection{Cut models}\label{section:cut_models}
-
-\begin{definition} A \emph{cut model} for a superbicategory $\cat{B}$ is a cut system $\cat{A}$ with the same underlying class of objects as $\cat{B}$ and a strong superfunctor $I: \cat{B} \lto \cat{A}^\bullet$ with the property that for every pair of objects $a,b$ the functor
-\[
-I_{a,b}: \cat{B}(a,b) \lto \cat{A}(a,b)^\bullet
-\]
-factors as
-\[
-\xymatrix{
-\cat{B}(a,b) \ar[rr]^-{I_{a,b}} \ar[dr]_-{J_{a,b}} & & \cat{A}(a,b)^\bullet\\
-& \cat{A}(a,b) \ar[ur]_-{\iota}
-}
-\]
-where $J_{a,b}$ is an equivalence of supercategories. We often identify $X$ with $I(X)$.
-\end{definition}
-
-A cut model is an effectively computable model for composition of $1$-morphisms in~$\cat{B}$.
-Given $X: a \lto b$ and $Y: b \lto c$, let us suppose that the composition $Y \circ X$ in $\cat{B}$ is not defined algorithmically: perhaps this object is only identified up to unique isomorphism by a universal property.
-In contrast, the cut $Y \l X$ is computable from $X$ and $Y$, and the strong superfunctor $I$ provides an isomorphism in $\cat{A}(a,c)^\bullet$
-\begin{equation}
-Y \l X \cong Y \circ X\,.
-\end{equation}
-Here $Y \circ X$ is embedded into $\cat{A}^\bullet$ as a cut-free $1$-morphism and the cut $Y \l X$ by definition comes with an $A_{\pi(b)}$-module structure.
-That is, there is an isomorphism of $A_{\pi(b)}$-modules
-\begin{equation}\label{eq:cutvsoriginal}
-Y \l X \cong S_{\pi(b)} \otimes_k (Y \circ X )
-\end{equation}
-or what is the same, an isomorphism of objects in $\cat{A}(a,b)$
-\begin{equation}\label{eq:cutvsoriginal2}
-S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X ) \cong Y \circ X \,.
-\end{equation}
-The general philosophy is that a cut model decomposes composition in $\cat{B}$ into two stages: 
-\begin{itemize}
-\item first form the cut $Y \l X$, and then
-\item tensor $Y \l X$ with $S^*_{\pi(b)}$ to compute $Y \circ X$. 
-\end{itemize}
-The idea is that the desired composition $Y \circ X$ lies inside $Y \l X$ in a way that is ``known'' in the sense that it is encoded by the Clifford action, but which is only \emph{realised} or \emph{constructed} after a computation is done.
-Forming the tensor product $S^*_{\pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ starting with the concretely known object $Y \l X$ can be further decomposed into a $\pi(b)$-step process of ``atomic'' computations, using the diagram of Remark \ref{remark:tensor_and_idempotent}
-\begin{equation}\label{eq:computation_fiber_diagram}
-\xymatrix@C+1pc@R+1pc{
-Z_0 \cong Y \circ X \ar@{.}[d] & Z_1 \ar@{.}[d] & & Z_{\pi(b)-1} \ar@{.}[d] & Z_{\pi(b)} = Y \l X \ar@{.}[d]\\
-0 \ar@{.>}@<0.8ex>[r] & 1 \ar@{.>}@<0.8ex>[r]\ar@{.>}@<0.8ex>[l] & \cdots \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b)-1  \ar@{.>}@<0.8ex>[l]\ar@{.>}@<0.8ex>[r] & \pi(b) \ar@{.>}@<0.8ex>[l]
-}\,.
-\end{equation}
-% remark:tensor_in_steps.
-The intermediate objects are $Z_i = S_{i, \pi(b)} \otimes_{A_{\pi(b)}} ( Y \l X )$ for $i < \pi(b)$.
-Each of these objects $Z_i$ is obtained from $Z_{i+1}$ by splitting an idempotent of the form $a^\dagger a$.
-
-Suppose we are in the situation where $Y \circ X$ is identified by a universal property but an explicit object realising this universal property is not given as part of $\cat{B}$.
-Then the result of the $\pi(b)$-step computation depicted above is an explicit object $Z_0$ of $\cat{A}(a,c) \cong \cat{B}(a,c)$ with this universal property.
-Thus the cut system gives a process for constructing representing objects for the uniquely defined isomorphism class $Y \circ X$ of $\cat{B}(a,c)$.
-
-Conceptually, the number of steps in \eqref{eq:computation_fiber_diagram} represents the computational cost of a cut across the object $b$.
-For any cut across this object, $\pi(b)$-steps are necessary to convert the ``uncertainty'' represented by $Y \l X$ with its $A_{\pi(b)}$-action to the certainty of an object of $\cat{A}(a,c)$ (in the sense of Remark \ref{remark:tensor_and_idempotent}).
-In the example of the next section, the cost $\pi(W)$ of cutting across a hypersurface singularity $W$ is determined by its dimension.
-
-\section{The Landau-Ginzburg cut system}\label{section:lg_cut_system}
-
-In this section we introduce the cut system $\cat{L}$, beginning with a sketch of the major pieces and then proceeding to the technical details.
-The objects of the cut system are the same as the objects of the bicategory $\LG$, that is, pairs $(x, W)$ consisting of a set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x]$.
-Such an object is often written as $W$ or $W(x)$.
-The integer $\pi(x,W) = n$ is the number of variables.
-
-Given objects $(x,W)$ and $(z,V)$ the supercategory $\cat{L}(W, V)$ is
-\[
-\cat{L}(W,V) = \hmf( k[x,z], V - W )^{\omega}\,,
-\]
-where $(-)^\omega$ denotes the idempotent completion; see Remark \ref{remark:idempotent_completion}.
-The objects of $\cat{L}(W,V)$ are therefore pairs $(X,e)$ consisting of a matrix factorisation $X$ of $V - W$ and an idempotent $e: X \lto X$.
-
-Next we sketch the definition of the cut functors for $\cat{L}$. Let $W \in k[x_1,\ldots,x_n], V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ be potentials. The cut functor
-\begin{gather*}
-\cat{L}(W, V) \otimes_k \cat{L}(V, U) \lto \cat{L}(W, U)^\bullet\,\\
-X \otimes Y \mapsto Y \l X
-\end{gather*}
-of degree $m$ is defined on matrix factorisations $X$ of $V - W$ and $Y$ of $U - V$ as follows.
-The object $Y \l X$ is a finite rank matrix factorisation of $W - U$ equipped with an action of the Clifford algebra $A_m$.
-The underlying matrix factorisation is
-\[
-Y \l X = Y \otimes_{k[z]} J_V \otimes_{k[z]} X
-\]
-where
-\[
-J_V = k[z] / ( \partial_{z_1} V, \ldots, \partial_{z_m} V )\,.
-\]
-With the differential $d_Y \otimes 1 + 1 \otimes d_X$, $Y \l X$ is a finite rank matrix factorisation of $U - W$ over $k[x,y]$ by virtue of the fact that $J_V$ is a finite rank free $k$-module.
-As an explicit matrix of polynomials in $k[x,y]$ the differential on $Y \l X$ can be obtained from the differentials on $X$ and $Y$ (which involve $k[z,x]$ and $k[y,z]$ respectively) by replacing occurrences of $z$ by a certain square matrix of scalars; see the proof of Theorem \ref{theorem:l_cut_system} for more details.
-
-It remains to define the action of the generators $a_i$ and $a_i^\dagger$ of $A_m$ on $Y \l X$.
-We give the formulas below; later we will prove that these operators satisfy Clifford relations and that, with this action, $X \otimes Y \mapsto Y \l X$ is a cut functor.
-
-The key ingredients of the Clifford action are the Atiyah classes of $Y \otimes X$, which are defined by first taking the technical step of extending scalars
-\begin{equation}\label{eq:completed_tensor_product}
-Y \,\check{\otimes}\, X = Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X
-\end{equation}
-and putting a connection on this module.
-We write $t = (t_1,\ldots,t_m)$ for the quasi-regular sequence of partial derivatives $t_i = \partial_{z_i} V$ and recall that there is by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
-\begin{equation}\label{eq:connection_nabla}
-\nabla: k\llbracket z \rrbracket \lto k\llbracket z \rrbracket \otimes_{k[t]} \Omega^1_{k[t]/k}
-\end{equation}
-the components of which are $k$-linear operators denoted $\partial_{t_i}: k\llbracket z \rrbracket \lto k\llbracket z \rrbracket$.
-A simple example of such a connection is given in Section \ref{example:computing_homs}.
-The operators $\partial_{t_i}$ extend to $k[x,y]$-linear operators on the free module $Y \, \check{\otimes}\, X$ and the $i$th Atiyah class is the operator
-\[
-\At_i = [d_{Y \otimes X}, \partial_{t_i}]\,.
-\]
-on $Y \,\check{\otimes}\, X$.
-This operator is the $i$th Atiyah class of $Y \,\check{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}.
-A reference for Atiyah classes is \cite{buchweitz_flenner}.
-
-The Atiyah class is $k[t]$-linear and passes to a $k$-linear operator on the quotient $Y \l X$ of $Y \,\check{\otimes}\, X$. We need another operator on this matrix factorisation, for $1 \le j \le m$
-\begin{equation}\label{eq:lambda_defn}
-\lambda_j = 1 \otimes \partial_{z_j}(d_X)\,.
-\end{equation}
-With this notation, the action of the generators $a_i, a_i^\dagger$ of $A_m$ on $Y \l X$ is defined by
-\begin{equation}\label{eq:intro_clifford_act1}
-a_i^\dagger = \At_i
-\end{equation}
-and
-\begin{equation}\label{eq:intro_clifford_act2}
-a_i = - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \At_{q_1} \cdots \At_{q_l}
-\end{equation}
-where $1 \le q_i \le m$ for $1 \le i \le l$. For explicit examples of these operators, see Section \ref{example:computing_homs}.
-
-The remaining components of the cut system $\cat{L}$ are the units $\Delta_W \in \cat{L}(W,W)$, which are the same as those for $\LG$ given in Section \ref{section:superbicatLG}, and the associators and unitors.
-To define the associator, let $W, V, U, Q$ be potentials with $V \in k[z_1,\ldots,z_m]$ and $U \in k[y_1,\ldots,y_p]$ and suppose we are given a triple of composable $1$-morphisms
-\begin{equation}\label{eq:composable_triple}
-\xymatrix{
-(q, Q) & (y, U) \ar[l]_-{Z} & (z,V) \ar[l]_-{Y} & (x,W) \ar[l]_-{X}
-}\,.
-\end{equation}
-The isomorphism of matrix factorisations
-\begin{gather*}
-\alpha: Z \l (Y \l X) = Z \otimes J_U \otimes ( Y \otimes J_V \otimes X ) \lto (Z \otimes J_U \otimes Y) \otimes J_V \otimes X = (Z \l Y) \l X,\\
-z \otimes (y \otimes x) \mapsto (z \otimes y) \otimes x
-\end{gather*}
-turns out to be $A_m \otimes A_p$-linear, and defines the associator for $\cat{L}$.
-
-The unitors can also be described by explicit formulas.
-Given $X \in \cat{L}(W,V)$ as above with homogeneous basis $e_i$ as a $\mathbb{Z}_2$-graded $k[x,z]$-module, we define morphisms of matrix factorisations
-\begin{gather}
-\mu_0: X \lto \Delta_V \l X \,, \\
-\mu_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j \Theta_{i_1} \ldots \Theta_{i_l} \left\{ \partial^{z,z'}_{[i_l]}(d_X) \cdots \partial^{z,z'}_{[i_1]}(d_X) \right\}_{ji} \otimes e_j\label{eq:explicit_mu0}
-\end{gather}
-and
-\begin{gather}
-\eta_0: X \lto X \l \Delta_W \,,\\
-\eta_0(e_i) = \sum_{l \ge 0} \sum_{i_1 < \cdots < i_l} \sum_j (-1)^{\binom{l}{2} + l|e_i|} e_j \otimes \left\{ \partial^{x,x'}_{[i_1]}(d_X) \cdots \partial^{x,x'}_{[i_l]}(d_X) \right\}_{ji} \Theta_{i_1} \ldots \Theta_{i_l}
-\end{gather}
-To make sense of these formulas, note that $\Delta_V$ is a matrix factorisation of $V(z) - V(z')$ over $k[z,z']$ and $\Delta_W$ is a matrix factorisation of $W(x) - W(x')$ over $k[x,x']$, while the divided difference operators are defined by
-\[
-{}^{t_i}(-): k[x,x'] \lto k[x,x']\,, \qquad f \mapsto f|_{x_i \mapsto x'_i}
-\]
-and
-\[
-\partial^{x,x'}_{[i]}: k[x,x'] \lto k[x,x']\,, \qquad f \mapsto \frac{{}^{t_1 \ldots t_{i-1}} f - {}^{t_1 \ldots t_i} f}{x_i - x'_i}
-\]
-and in the same way for $z,z'$.
-For a concrete example of these formulas see \cite{lgdual_survey}.
-The actual unitors are the morphisms $X \lto \Delta_V \l X$ and $X \lto X \l \Delta_W$ in $\cat{L}(W,V)^\bullet$ corresponding to $\mu_0$ and $\eta_0$ under the bijection of Lemma \ref{lemma:morphism_out_1}.
-It is not meant to be clear \emph{a priori} that these formulas even define morphisms, let alone that they satisfy the axioms for unitors; all these checks will be performed below.
-\\
-
-The major theorem, to be proved over the course of this section:
-
-\begin{theorem}\label{theorem:l_cut_system} $\cat{L}$ is a cut system.
-\end{theorem}
-
-\subsection{The details}
-
-We present the cut $Y \l X$ with its Clifford action as arising from the following problem: how do we find a finite model of the matrix factorisation $Y \otimes X$ over $k[x,y]$?
-This problem was addressed in joint work with Dyckerhoff \cite{dm1102.2957} and we rely heavily on these results; the main new ingredient here is the construction of Appendix \ref{section:cliffordactkos}.
-
-The solution is given in the language of homological perturbation, which is recalled in Appendix \ref{section:homolog_fix}, with a reformulation in terms of splitting homotopies due to Barnes and Lambe \cite{barneslambe}.
-From the point of view of perturbation it is natural to look for a decomposition $d_{Y \otimes X} = d + \delta$ where a finite representative of $(Y \otimes X, d)$.
-Then the perturbation lemma can be used to parlay this into a finite model for the object of interest $(Y \otimes X, d + \delta)$.
-
-There seems to be no obvious way to do this, but there is a simple way out: we replace $Y \otimes X$ by a sum of copies
-\begin{equation}\label{eq:larger_object}
-(Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
-\end{equation}
-in such a way that this larger object \emph{does} fit into the pattern of the perturbation lemma.
-More precisely, \eqref{eq:larger_object} will be the tensor product of $Y \otimes X$ with a $\mathbb{Z}_2$-graded $k$-module and we find in \eqref{eq:iso_larger_object} an isomorphic object for which a finite model may be found by perturbing a finite model for one ``piece'' of the differential.
-Then we need only remember the data of how to extract $Y \otimes X$ from inside this larger object: this data is the Clifford action.
-\medskip
-
-% As long as the $t_i$ belong to the maximal ideal
-Let us now proceed to the details.
-We keep the above notation, so $k[z] = k[z_1,\ldots,z_m]$.
-The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ (where $t_i = \partial_{z_i} V$) has as its underlying graded module the exterior algebra on the $\theta_i$ of degree $-1$.
-If $F = k\theta_1 \oplus \cdots \oplus k\theta_m$ then
-\begin{equation}\label{defn:koszul}
-K = \bigwedge F \otimes_k k[z], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
-\end{equation}
-As explained in Appendix \ref{section:cliffordactkos} since each $t_i$ acts null-homotopically on $Y \otimes X$ there is an isomorphism of linear factorisations (writing $S_m = \bigwedge F$ as per our usual convention)
-\begin{equation}\label{eq:iso_larger_object}
-\xymatrix@C+3pc{ K \otimes Y \otimes X \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k (Y \otimes X)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
-\end{equation}
-where the differential on the left is $d_{Y \otimes X} + d_K$, on the right the differential is $d_{Y \otimes X}$, and $\delta = \sum_i \lambda_i \theta_i^*$ where $\lambda_i$ is a choice of null-homotopy for the action of $t_i$.
-
-From the identity $d^2_Y = V - W$ we deduce that
-\[
-\partial_{z_i}(d_Y) d_Y + d_Y \partial_{z_i}(d_Y) = \partial_{z_i} V
-\]
-so that we may choose $\lambda_j$ to be the operator \eqref{eq:lambda_defn}.
-Note that the right hand side of \eqref{eq:iso_larger_object} is a direct sum of (shifted) copies of $Y \otimes X$; this is the object we intended in \eqref{eq:larger_object}.
-The Clifford algebra $A_m$ naturally acts on this matrix factorisation via closed linear operators.
-
-The next step is to find a finite model of $K \otimes Y \otimes X$ using the perturbation lemma, by writing the differential as $d_K + d_{Y \otimes X}$ and finding a finite model of $(K \otimes Y \otimes X, d_K)$.
-We begin by giving a finite model for the Koszul complex $(K, d_K)$ using connections.
-\medskip
-
-The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $k\llbracket z \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra.
-By identifying $d t_i$ with $\theta_i$ we may identify this tensor product with $K$ itself, so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $K$.
-It is straightforward to check that $[d_K, \nabla]$ is invertible on the graded submodule $K_{\le -1}$ of nonzero degree terms, and we define
-\[
-H = [d_K, \nabla]^{-1} \nabla\,.
-\]
-
-\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $K$.
-\end{proposition}
-\begin{proof}
-See \cite[Section 8.1]{dm1102.2957}.
-\end{proof}
-
-The associated strong deformation retract of $\mathbb{Z}$-graded $k$-complexes is
-\begin{equation}\label{eq:originalHdef}
-\xymatrix@C+2pc{
-(J_V,0) \ar@<-1ex>[r]_{\sigma} & (K, d_K), \ar@<-1ex>[l]_{\pi}
-} \quad H
-\end{equation}
-where $\pi: K \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $k\llbracket z \rrbracket \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $k\llbracket z \rrbracket$ uniquely determined by $\nabla$.
-The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of the Koszul complex $K$.
-
-Recall that the tensor product $Y \,\check{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,y]\llbracket z \rrbracket$.
-Let us write $\ell = k[x,y]$ so that the connection $\nabla$ extends to a standard $\ell$-linear flat connection on $R$.
-A choice of homogeneous basis for $X$ and $Y$ allows us to write $Y \otimes X \cong k[x,y,z] \otimes_k V$ for some $\mathbb{Z}_2$-graded free $k$-module $V$, so
-\begin{equation}\label{eq:lambdaiso2}
-K \otimes_{k\llbracket z \rrbracket}( Y \,\check{\otimes}\, X ) \cong K \otimes_{k\llbracket z \rrbracket} (R \otimes_k V) \cong K \otimes_k k[x,y] \otimes_k V
-\end{equation}
-In this way the $k$-linear splitting homotopy $H$ on $K$ induces an $\ell$-linear operator $H \otimes 1$ on $K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X$, which we again denote by $H$.
-
-\begin{lemma} $H$ is an $\ell$-linear splitting homotopy on the complex $(K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, d_K)$.
-\end{lemma}
-
-The associated strong deformation retract is
-\[
-\xymatrix@C+2pc{
-(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
-} \quad H
-\]
-The map $\pi$ is $R$-linear induced by the map $\pi: K \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.
-This is the desired finite model of $K \otimes Y \otimes X$ equipped with only the differential $d_K$.
-
-We now view $d_{Y \otimes X}$ as a perturbation.
-The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
-Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
-\[
-\phi_\infty = \sum_{m \ge 0} (-1)^m (H d_{Y \otimes X})^m H
-\]
-is an $\ell$-linear splitting homotopy achieving the desired aim.
-
-Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $\ell$-linear splitting homotopy on $K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X$ and the associated $\ell$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
-\begin{equation}\label{eq:finite_model_defo}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & K \otimes_{k\llbracket z \rrbracket} Y \,\check{\otimes}\, X, \ar@<-1ex>[l]_-{\pi}
-} \quad \phi_\infty
-\end{equation}
-where the differential on the left is $d_{Y \otimes X}$ and on the right it is $d_K + d_{Y \otimes X}$. 
-%$A = d_{Y \otimes X}( 1 + H d_{Y \otimes X} )^{-1}$ and $\sigma_\infty = \sigma - H A \sigma$.
-We need only justify why in \eqref{eq:perturbedsdr} we have $d_\infty = d_{Y \otimes X}$ and $f_\infty = \pi$.
-But this follows from $H \sigma = 0$ and $\pi H = 0$.
-%\begin{equation}
-%\xymatrix@C+4pc{
-%Y \l X \ar@<-1ex>[r]_-{\exp(-\delta) \sigma_\infty} & S_m \otimes_k ( Y \,\check{\otimes}\, X )\ar@<-1ex>[l]_-{\pi \exp(\delta)}
-%}\,.
-%\end{equation}
-%of linear factorisations of $U - W$ over $k[x,y]$.
-
-\begin{proposition}\label{prop:final_homotopy_equiv_cut} There is a homotopy equivalence of matrix factorisations over $k[x,y]$
-\begin{equation}\label{eq:final_finite_model}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
-}
-\end{equation}
-where $\Phi = \pi \exp(-\delta) \epsilon$ and $\Phi^{-1} = \epsilon^{-1} \exp(\delta) \sigma_\infty$ and $\epsilon: Y \otimes X \lto Y \,\check{\otimes}\, X$ is canonical.
-\end{proposition}
-\begin{proof}
-Together \eqref{eq:iso_larger_object} and \eqref{eq:finite_model_defo} give a homotopy equivalence
-\begin{equation}\label{eq:final_finite_model2}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & K \otimes Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
-}\,.
-\end{equation}
-By \cite[Remark 7.7]{dm1102.2957} $\epsilon$ is a homotopy equivalence over $k[x,y]$, completing the proof.
-\end{proof}
-
-This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $S_m \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object.
-It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $S_m \otimes_k( Y \otimes X )$.
-
-This equivalence induces an $A_m$ action on $Y \l X$ via the action on $S_m$.
-
-\begin{definition} We introduce closed odd $k[x,y]$-linear operators on $Y \l X$ by
-\begin{equation}\label{eq:new_operators}
-(a_i^\dagger)_{Y,X} = \Phi \circ a_i^\dagger \circ \Phi^{-1}, \qquad (a_i)_{Y,X} = \Phi \circ a_i \circ \Phi^{-1}\,.
-\end{equation}
-\end{definition}
-
-\begin{proposition}\label{prop:clifford_action} The operators $(a_i)_{Y,X}, (a_i^{\dagger})_{Y,X}$ of \eqref{eq:new_operators} agree with those in \eqref{eq:intro_clifford_act1}, \eqref{eq:intro_clifford_act2}.
-\end{proposition}
-\begin{proof}
-Let us define intermediate operators on $K \otimes Y \otimes X$
-\[
-\psi_i^\dagger = \exp(-\delta) a_i^\dagger \exp(\delta), \qquad \psi_i = \exp(-\delta) a_i \exp(\delta).
-\]
-By Appendix \ref{section:cliffordactkos}, $\psi_i^\dagger = \theta^*_i$ and
-\[
-\psi_i = \theta_i - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_l}^*\,.
-\]
-Next we recall that, with $t_i = \partial_{z_i} V$, we have by \cite[Section 10]{dm1102.2957}
-\begin{equation}\label{eq:atiyah_formula_sigma}
-\sigma_\infty = \sum_{l \ge 0} \sum_{q_1,\ldots,q_l} (-1)^{\binom{l+1}{2}} \frac{1}{l!} [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}] \theta_{q_1} \cdots \theta_{q_l} + (t \text{ terms})\,.
-\end{equation}
-That is, $\sigma_\infty$ is given modulo the submodule $(t_1,\ldots,t_m) K \otimes Y \otimes X$ by the formula above. Hence we compute
-\begin{align*}
-(a_i^\dagger)_{Y,X} &= \pi \psi_i^\dagger \sigma_\infty = \pi \theta_i^* \sigma_\infty\\
-&= \sum_{l \ge 0} \sum_{q_1,\ldots,q_l} (-1)^{\binom{l+1}{2}} \frac{1}{l!} [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}] \pi \theta_i^* \theta_{q_1} \cdots \theta_{q_l}\\
-&= \sum_q [d_{Y \otimes X}, \partial_{t_q}] \pi \theta_i^* \theta_q\\
-&= [d_{Y \otimes X}, \partial_{t_i}] = \At_i\,.
-\end{align*}
-To simplify the notation in the following, we define ($i$ is fixed) for a tuple $\bold{q} = (q_1,\ldots,q_l)$
-\begin{gather*}
-\tau_{\bold{q}} = [ \lambda_{q_l}, [ \lambda_{q_{l-1}}, \ldots [ \lambda_{q_1}, \lambda_i ] \cdots ]\,,\\
-\At_{\bold{q}} = [ d_{Y \otimes X}, \partial_{t_{q_1}}] \cdots [ d_{Y \otimes X}, \partial_{t_{q_l}}]\,.
-\end{gather*}
-With this notation we compute
-\begin{align*}
-(a_i)_{Y,X} &= \pi \psi_i \sigma_\infty\\
-&= - \lambda_i - \pi \sum_{l \ge 1, k \ge 0} \sum_{q_1,\ldots,q_l} \sum_{w_1,\ldots,w_k} \frac{1}{(l+1)!
-k!} (-1)^{kl+\binom{k+1}{2}} \tau_{\bold{q}}  \At_{\bold{w}} \theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{w_1} \cdots \theta_{w_k}\,.
-\end{align*}
-But $\pi$ is non-vanishing only on terms of $\theta$-degree zero, so the sum restricts to $l = k$ and to $\bold{q}$ a permutation of $\bold{w}$. Since
-\[
-\theta_{q_1}^* \cdots \theta_{q_l}^* \theta_{q_{\sigma(1)}} \cdots \theta_{q_{\sigma(l)}} = (-1)^{|\sigma|} (-1)^{\binom{l}{2}}
-\]
-we have, using the fact that the Atiyah classes anti-commute,
-\begin{align*}
-(a_i)_{Y,X} &= - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \sum_{\sigma \in S_l} (-1)^{|\sigma|} \frac{1}{l! (l+1)!} \tau_{\bold{q}} \At_{\sigma(\bold{q})}\\
-&= - \lambda_i - \sum_{l \ge 1} \sum_{q_1,\ldots,q_l} \frac{1}{(l+1)!} \tau_{\bold{q}} \At_{\bold{q}}
-\end{align*}
-which completes the proof.
-\end{proof}
-
-%The upshot is that if we equip $Y \l X$ with the Clifford action $\{ a_i, a_i^\dagger \}_i$ defined at the beginning of this section then the homotopy equivalence of Proposition \ref{prop:final_homotopy_equiv_cut} is $A_m$-linear.
-
-\begin{remark} There is a question of whether or not the $A_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
-But Atiyah classes are independent, up to homotopy, of the choice of connection, and it is easy to see that the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis.
-Hence the action is indeed canonical.
-\end{remark}
-
-\begin{proposition} The above construction defines a cut functor of degree $m$
-\begin{gather*}
-\cat{L}(W, V) \otimes_k \cat{L}(V,U) \lto \cat{L}(W, U)^\bullet\\
-X \otimes Y \mapsto (Y \l X, \{ a_i, a_i^\dagger \}_i )
-\end{gather*}
-sending a morphism $\phi \otimes \psi$ to $\psi \l \phi = \psi \otimes 1 \otimes \phi$.
-\end{proposition}
-\begin{proof}
-We check that the construction is functorial, the compatibility with the supercategory structure is straightforward and we omit it.
-We only check functoriality in $X$, as the check for $Y$ is the same.
-So let $\phi: X \lto X'$ be a morphism of matrix factorisations.
-Let $a_i, a_i^\dagger$ denote the actions on both $X$ and $X'$, so that we need to check
-\[
-(1\l\phi) a_i = a_i (1 \l \phi), \qquad (1\l\phi) a_i^\dagger = a_i^\dagger (1 \l \phi)\,.
-\]
-It is enough to prove that $(1 \l \phi) \At_i = \At_i (1 \l \phi)$ and $(1 \l \phi) \lambda_i = \lambda_i (1 \l \phi)$ up to homotopy.
-The former follows from naturality of the Atiyah class (the arguments in either \cite[Lemma 3.3]{buchweitz_flenner} or \cite[Lemma 3.6]{dm1102.2957} also apply in the current context to show the desired naturality).
-For the latter we use Lemma \ref{lemma:naturalityoflambda} below.
-\end{proof}
-
-\begin{remark}\label{remark:iso_quotient_map} If $\iota: k \lto S_m$ denotes the map $\iota(1) = 1$ then by Lemma \ref{lemma:morphism_out_1} the composite
-\[
-\xymatrix@C+2pc{
-Y \otimes X \cong k \otimes_k ( Y \otimes X ) \ar[r]^-{\iota \otimes 1} & S_m \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
-}
-\]
-is simply the quotient map $\varrho: Y \otimes X \lto Y \l X$.
-\end{remark}
-
-\begin{lemma}\label{lemma:naturalityoflambda} Let $R$ be a $k$-algebra, $W \in R$.
-Let $\partial$ be a $k$-linear derivation on $R$ and $\phi: X \lto X'$ a morphism of finite rank matrix factorisations over $R$ with chosen homogeneous bases.
-Then the diagram
-\[
-\xymatrix{
-X \ar[d]_{\partial(d_X)} \ar[r]^\phi & X' \ar[d]^{\partial(d_{X'})}\\
-X \ar[r]_{\phi} & X'
-}
-\]
-commutes up to homotopy.
-\end{lemma}
-\begin{proof}
-From $d_{X'} \phi = \phi d_X$ we deduce
-\[
-\partial( d_{X'} ) \phi + d_{X'} \partial( \phi ) = \partial( \phi ) d_X + \phi \partial( d_X )
-\]
-and hence
-\[
-\partial( d_{X'} ) \phi - \phi \partial( d_X ) = \partial(\phi) d_X - d_{X'} \partial(\phi)
-\]
-as claimed.
-\end{proof}
-
-To complete the construction of the cut system we need to finish defining the associator and unitors (a task begun at the outset of the section) and to prove that the coherence conditions hold.
-Regarding the associator, we only need to check that $\alpha$ commutes with the Clifford actions.
-In the context of \eqref{eq:composable_triple},
-
-\begin{lemma} The morphism $\alpha: (Z \l Y) \l X \lto Z \l (Y \l X)$ is $A_m \otimes A_p$-linear.
-\end{lemma}
-\begin{proof}
-We prove the $A_p$-linearity of $\alpha$, the proof for $A_m$ is similar.
-The algebra $A_p$ acts on the cut between $Z$ and $Y$ involving the variables $y_1,\ldots,y_p$.
-The action on $Z \l ( Y \l X ) = Z \otimes J_U \otimes (Y \otimes J_V \otimes X)$ is via $1 \otimes (\partial_{y_i}(d_Y) \otimes 1)$ and the Atiyah classes of
-\[
-M = Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
-\]
-relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
-Specifically, the generator $a_i^{\dagger}$ of $A_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
-But this operator can be identified with an Atiyah class of the linear factorisation
-\begin{equation}\label{eq:assoc_proof_M}
-Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X \big)
-\end{equation}
-relative to the ring morphism
-\begin{equation}\label{eq:assoc_proof_M2}
-k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U, \partial_{z_1} V, \ldots, \partial_{z_m} V ]\,.
-\end{equation}
-By the same argument the action of $A_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} Y \big) \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}.
-It is therefore clear that the associator $\alpha$ identifies these two actions.
-\end{proof}
-
-Earlier the unitors were described by explicit formulas.
-Here we begin more abstractly: let $X \in \cat{L}(W,V)$ be a matrix factorisation with $W \in k[x_1,\ldots,x_n]$ and $V \in k[z_1,\ldots,z_m]$.
-Since $\Delta_V$ is the unit in $\LG$ there is a homotopy equivalence $\lambda: \Delta_V \otimes_{k[z]} X \lto X$ and so by Proposition \ref{prop:final_homotopy_equiv_cut} there are homotopy equivalences
-\begin{equation}
-\xymatrix@C+3pc{
-\Delta_V \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( \Delta_V \otimes X )\ar@<-1ex>[l]_-{\Phi} \ar@<-1ex>[r]_-{1 \otimes \lambda} & S_m \otimes_k X \ar@<-1ex>[l]_-{1 \otimes \lambda^{-1}} 
-}\,.
-\end{equation}
-By construction these isomorphisms are $A_m$-linear, and the map from right to left is an isomorphism $\mu: X \lto \Delta_V \l X$ in $\cat{L}(W,V)^\bullet$ corresponding under Lemma \ref{lemma:morphism_out_1} to
-\[
-\mu_0 = \xymatrix@C+1pc{
-X \ar[r]^-{\lambda^{-1}} & \Delta_V \otimes_{k[z]} X \ar[r]^-{\varrho} & \Delta_V \l X
-}\,.
-\]
-where $\varrho$ is the quotient map.
-Given the explicit formula for $\lambda^{-1}$ from \cite[Section 4.1]{lgdual}, this map $\mu_0$ has the explicit formula given earlier in \eqref{eq:explicit_mu0}.
-Since $\mu_0$ is natural in $X$, this also proves that $\mu$ is a natural isomorphism.
-The details for $\eta$ are similar, so the unitors are now defined.
-
-\begin{remark}\label{remark:inflation} Let $V \in k[z_1,\ldots,z_m]$ be a potential and choose a $k$-basis for $J_V$.
-Then multiplication by $z_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[z_i]$ over $k$.
-
-Given $X$ and $Y$ the cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $z_i$ by the scalar matrix $[z_i]$.
-This ``inflation'' produces a matrix of polynomials over $k[x,y]$.
-\end{remark}
-
-\begin{proof}[Proof of Theorem \ref{theorem:l_cut_system}] We first check the coherence axioms.
-The first and third are trivial.
-To prove (2) we need by Lemma \ref{lemma:unitor_check_help} only check commutativity of \eqref{eq:unitor_check_help1} in the usual situation of $X: W \lto V$ and $Y: V \lto U$.
-
-This amounts to checking commutativity of
-\begin{equation}\label{eq:coherence3_1}
-\xymatrix{
-(Y \l \Delta_V ) \l X \ar[rr]^-{\alpha} & & Y \l ( \Delta_V \l X )\\
-(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
-Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes J_V \otimes X \ar[l]^-{e_m} \ar[r]_-{e_m} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
-}\,.
-\end{equation}
-By definition $e_m$ factors as
-\[
-\xymatrix{
-Y \l X \ar[r]^-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X ) \ar[r] & Y \otimes X \ar[r] & S_m \otimes_k (Y \otimes X) \ar[r]^-{\Phi} & Y \l X
-}
-\]
-so commutativity of \eqref{eq:coherence3_1} follows from commutativity of
-\[
-\xymatrix@C-0.5pc{
-(Y \l \Delta_V ) \l X \ar[rrr]^-{\alpha} & & & Y \l ( \Delta_V \l X )\\
-(Y \otimes \Delta_V) \otimes J_V \otimes X \ar[u]^-{\varrho \otimes 1} & (Y \otimes \Delta_V ) \otimes X \ar[l]_-{\varrho} \ar[r]^-{\alpha} & Y \otimes (\Delta_V \otimes X) \ar[r]^-{\varrho} & Y \otimes J_V \otimes ( \Delta_V \otimes X) \ar[u]_-{1 \otimes \varrho}\\
-Y \otimes J_V \otimes X \ar[u]^-{ \rho^{-1} \otimes 1} & Y \otimes X \ar[u]^-{\rho^{-1} \otimes 1} \ar@{=}[r] \ar[l]^-{\varrho} & Y \otimes X \ar[u]_-{1 \otimes \lambda^{-1}} \ar[r]_-{\varrho} & Y \otimes J_V \otimes X \ar[u]_-{1 \otimes \lambda^{-1}}
-}\,.
-\]
-The innermost square of this diagram is the coherence constraint for the unitors in $\LG$.
-
-Finally, we check the computability conditions.
-The associator and unitors are derived explicitly from $d_X$ and $d_Y$, so (3) is clear, and (2) is addressed by Remark \ref{remark:inflation} and the explicit formulas for the Clifford action.
-For (1), the objects and morphisms of $\cat{L}(W,V)$ are described by finite matrices of polynomials, and the composition rule is given by multiplication of matrices.
-There is one subtlety: morphisms are matrices of polynomials \emph{identified up to homotopy}.
-
-To argue that $\cat{L}(W,V)$ is effectively computable we need to show that it is possible to determine algorithmically whether two morphisms are homotopic.
-This is important even at the level of objects: an object is a pair $(X,e)$ where $e^2 = e$ holds up to homotopy.
-Without an effective homotopy relation, there would be no algorithmic way to even distinguish between objects and non-objects.
-The necessary check is in Section \ref{example:computing_homs}.
-\end{proof}
-
-\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}.
-To see the connection, recall the idempotent $e_m \in A_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$.
-The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is
-\[
-e_m' = a_1 \cdots a_m a_m^\dagger \cdots a_1^\dagger\,.
-\]
-Using \eqref{eq:intro_clifford_act1} and \eqref{eq:intro_clifford_act2} we can write down the explicit form of this idempotent acting on $Y \l X$.
-On this object each of the $a_i$'s acts simply as $- \lambda_i$ because all of the $a_j^\dagger$'s appear to the right.
-Hence on $Y \l X$
-\begin{align*}
-e_m' &= (-1)^{\binom{m}{2}} a_1 \cdots a_m a_1^\dagger \cdots a_m^\dagger \\
-&= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
-\end{align*}
-which is precisely the idempotent which appears in \cite[Corollary 10.4]{dm1102.2957}.
-
-In \emph{ibid.} we constructed finite models of convolutions $Y \circ X$ one pair $(Y,X)$ at time.
-To make this assignment of finite models coherently for all $1$-morphisms in $\LG$ simultaneously it is natural to identify the Clifford actions which underlie the idempotents, as we do here.
-\end{remark}
-
-\subsection{The cut model of $\LG$}
-
-Let $\cat{L}$ be the cut system described above, and let $\cat{L}^\bullet$ denote the associated superbicategory.
-With $\LG$ the superbicategory of Section \ref{section:superbicatLG} we construct a cut model $I: \LG \lto \cat{L}^\bullet$.
-On objects $I$ is the identity.
-For potentials $V,W$ we need to define a functor
-\begin{equation}\label{eq:cut_model_equiv}
-I_{V,W}: \LG(W,V) \lto \cat{L}^\bullet(W,V)\,.
-\end{equation}
-Recall that with $\cat{C} = \hmf(k[x,z], V - W)$,
-\[
-\cat{L}^\bullet(W,V) = \cat{C}^{\omega \bullet}\,, \quad \LG(W,V) = \cat{C}^{\oplus}\,.
-\]
-An object of $\cat{C}^{\omega \bullet}$ is a tuple $((X,e), n)$ consisting of an integer $n \ge 0$ and an $A_n$-module $(X,e)$ in $\cat{C}^\omega$, while an object of $\cat{C}^{\oplus}$ is a (possibly infinite) matrix factorisation of $V - W$ which is a direct summand of a finite rank one.
-
-On the full subcategory of finite rank matrix factorisation of $V - W$, $I_{V,W}$ is the identity and this functor extends uniquely (up to natural equivalence) to $\LG(W,V)$.
-To be more explicit about it: for each $X \in \LG(W,V)$ we \emph{choose} a finite rank matrix factorisation $\bar{X}$ together with an idempotent $e$ and morphisms $f_X, g_X$ as in the diagram
-\[
-\xymatrix@C+2pc{
-\bar{X} \ar@(ul,dl)_-{e} \ar@<1ex>[r]^-{f_X} & X \ar@<1ex>[l]^-{g_X}
-}
-\]
-satisfying $g_X f_X = e$ and $f_X g_X = 1_X$. Then the full definition of $I$ is given by
-\[
-I( X ) = ((\bar{X}, e), 0)\,, \qquad I( \phi ) = g_Y \phi f_X\,.
-\]
-To complete the definition of a strong functor $I$ it remains to give a natural $2$-isomorphism
-\begin{equation}\label{eq:strong_functor_varphi}
-\varphi: I(Y \otimes X) \lto I(Y) \l I(X)
-\end{equation}
-for every pair of $1$-morphisms $X: W \lto V$ and $Y: V \lto U$ in $\LG$.
-
-We give the definition of $\varphi$ where $X,Y$ are finite rank matrix factorisations; the general case follows. Recall the $A_m$-linear isomorphism of Proposition \ref{prop:final_homotopy_equiv_cut}
-\begin{equation}\label{eq:cutmodelequiv}
-\xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
-}\,.
-\end{equation}
-% TODO issue with completion
-This is essentially the desired natural isomorphism $\varphi$, and it is only necessary to package it a little more carefully.
-Let $e = e_m \in A_m$ denote the idempotent from Definition \ref{defn:idempotent_e}.
-If we define $\nu: S_m \lto k$ to be the projection onto $k \cdot 1$ then there is a diagram
-\[
-\xymatrix@C+4pc{
-Y \l X \ar@<1ex>[r]^-{\nu \Phi^{-1}} & Y \otimes X \ar@<1ex>[l]^-{\varrho}
-}
-\]
-expressing $Y \otimes X$ as the splitting of the idempotent $e$ on $Y \l X$.
-Here $\varrho: Y \otimes X \lto Y \l X$ is the quotient map.
-The usphot is that as objects of $\cat{L}(W,V)^{\omega \bullet}$
-\[
-I(Y \otimes X) = ((Y\l X, e), 0), \qquad I(Y) \l I(X) = ( (Y \l X, 1), m )\,.
-\]
-Morphisms $\varphi$ as in \eqref{eq:strong_functor_varphi} are in bijection with morphisms
-\[
-\varphi_0: (Y \l X, e) \lto (Y\l X, 1)
-\]
-in $\hmf(k[x,z], U - W)^{\omega}$ satisfying $\theta_i^* \circ \varphi_0 = 0$ for $1 \le i \le m$.
-The endomorphism $\varphi_0 = e_m$ of $Y \l X$ fits the bill.
-In the category of infinite rank matrix factorisations, $\varphi_0$ is just the morphism $\varrho$.
-It follows that $\varphi$ is a natural isomorphism, since it corresponds to $\Phi$.
-
-\begin{theorem} The data $(I, \varphi)$ defines a cut model $\LG \lto \cat{L}^\bullet$.
-\end{theorem}
-\begin{proof}
-Once we have shown that $(I, \varphi)$ is a strong functor it is clearly ``super'', and by construction it defines a cut model.
-There are two coherence conditions: the first is commutativity of the following diagram, in the context of a composable triple as in \eqref{eq:composable_triple}:
-\begin{equation}\label{eq:dia_coherence1}
-\xymatrix@C+2pc{
-(I(Z) \l I(Y) ) \l I(X) \ar[r]^-{\alpha} \ar[d]_-{\varphi \l 1} & I(Z) \l ( I(Y) \l I(X) ) \ar[d]^-{1 \l \varphi} \\
-I(Z \otimes Y) \l I(X) \ar[d]_-{\varphi} &  I(Z) \l I(Y \otimes X)\ar[d]^-{\varphi}\\
-I( (Z \otimes Y) \otimes X ) \ar[r]_-{I(\alpha)} & I(Z \otimes (Y \otimes X))
-}
-\end{equation}
-The key to checking this lies in understanding what $I( Z \otimes (Y \otimes X) )$ is.
-But as we have argued above, $Y \otimes X$ is a summand of $Y \l X$ with idempotent $e_m$ while $Z \otimes ( Y \l X )$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p$.
-This implies that $Z \otimes (Y \otimes X)$ is a summand of $Z \l (Y \l X)$ with idempotent $e_p e_m = e_m e_p = e_{m+p}$, so
-\[
-I( (Z \otimes Y) \otimes X ) = ( Z \l (Y \l X), e_{m+p} ), \quad I( Z \otimes (Y \otimes X) ) = ( (Z \l Y) \l X, e_{m+p} )\,.
-\]
-Then commutativity of \eqref{eq:dia_coherence1} reduces to commutativity in $\hmf(Q - W)^{\omega}$ of
-\[
-\xymatrix@C+2pc{
-( (Z \l Y ) \l X, 1 ) \ar[r]^-{\alpha} & ( Z \l (Y \l X ), 1)\\
-( (Z \l Y) \l X, e_p \l 1) \ar[u]^-{e_p \l 1} & ( Z \l (Y \l X), 1 \l e_m) \ar[u]_-{e_m}\\
-( (Z \l Y) \l X, e_{m+p} ) \ar[u]^-{e_{m+p}} \ar[r]_-{e_{m+p}} & ( Z \l (Y \l X), e_{m+p} ) \ar[u]_-{e_{m+p}}
-}
-\]
-which is clear.
-
-The remaining coherence conditions are commutativity, for $X: W \lto V$, of
-\begin{equation}\label{eq:dia_coherence2}
-\xymatrix{
-I(X) \ar[dr]_-{\eta} & & I( X \otimes \Delta_W ) \ar[ll]_-{I(\rho)} \\
-& I(X) \l \Delta_W \ar[ur]_-{\varphi}
-}
-\end{equation}
-and a similar diagram for $\lambda$. By definition $I(\rho)$ is the inverse of
-\[
-\xymatrix{
-X \ar[r]^-{\eta^{-1}} & X \otimes \Delta_W \ar[r]^{\varrho} & X \l \Delta_W
-}
-\]
-so checking commutativity of \eqref{eq:dia_coherence2} can be done using Lemma \ref{lemma:morphism_out_1}, and similarly for the diagram involving $\mu$.
-\end{proof}
-
-\subsection{Example: the Hom complex}\label{example:computing_homs}
-
-Using the cut model $\cat{L}$ we can study the complex $\Hom_R(X,Y)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[z_1,\ldots,z_m]$.
-In particular, we will explain how the homotopy relation on morphisms of matrix factorisations is effectively computable.
-
-The pair $(k,0)$ is an object in $\LG$ and we may view $Y$ and the dual matrix factorisation $X^{\vee}$ of $-V$ as a pair of $1$-morphisms
-\begin{equation}\label{eq:compute_hom_composition}
-\xymatrix@C+2pc{
-0 \ar[r]^-{Y} & V \ar[r]^-{X^{\vee}} & 0
-}\,.
-\end{equation}
-The composite is a $1$-morphism $0 \lto 0$, that is, $\mathbb{Z}_2$-graded complex of $k$-modules. This is the Hom complex of $R$-linear homogeneous maps $X \lto Y$,
-\[
-X^{\vee} \otimes_R Y \cong \Hom_R(X, Y)
-\]
-with the differential $\phi \mapsto d_Y \circ \phi - (-1)^{|\phi|} \phi \circ d_X$.
-The cut model provides a two-step process to compute the result of the composition in \eqref{eq:compute_hom_composition}.
-First form the cut
-\[
-X^{\vee} \l Y = X^{\vee} \otimes_R J_V \otimes_R Y = \Hom_{J_V}( \bar{X}, \bar{Y} )
-\]
-where $\bar{X} = X \otimes_R J_V, \bar{Y} = Y \otimes_R J_V$. This is a complex of finite-rank $\mathbb{Z}_2$-graded free $k$-modules, and there is an $A_m$-linear homotopy equivalence
-\[
-\Phi: S_m \otimes_k \Hom_R(X,Y) \lto \Hom_{J_V}( \bar{X}, \bar{Y} )\,.
-\]
-Set $H = \Hom_{J_V}( \bar{X}, \bar{Y} )$ and define
-\[
-B = \im( d^1_H: H^1 \lto H^0 )\,.
-\]
-As a matrix of scalars $d^1_H$ may be computed from the differentials $d_X, d_Y$ by inflation, as described in Remark \ref{remark:inflation}.
-Let $\psi: X \lto Y$ be a morphism of matrix factorisations.
-Then $\psi$ is null-homotopic if and only if $\psi' = \Phi(\psi) \in \Hom_{J_V}( \bar{X}, \bar{Y} )$ is a coboundary.
-As a matrix, $\psi'$ is obtained from $\psi$ by inflation.
-This reduces the problem of determing whether or not $\psi$ is null-homotopic to the subspace membership problem for the pair $(B, \psi')$.
-If $k$ is a field this may be computed by a row-reduction, and otherwise using Gr\"obner bases.
-
-\begin{example} Suppose $V = z^N$ in $k[z]$ for $N \ge 2$. Take matrix factorisations $X,Y$ with the same underlying free $R = k[z]$-module $X = Y = R \oplus R \theta$ and differentials
-\[
-d_X = z^i \theta + z^{N-i} \theta^* = \begin{pmatrix} 0 & z^{N-i} \\ z^i & 0 \end{pmatrix}, \qquad d_Y = z^j \theta + z^{N-j} \theta^* = \begin{pmatrix} 0 & z^{N-j}\\ z^j & 0 \end{pmatrix}
-\]
-where $1 \le i,j \le N/2$. Using the basis $\Hom_R(X,Y) = R \theta \theta^* \oplus R \theta^* \theta \oplus R\theta \oplus R \theta^*$,
-\begin{equation}\label{eq:differential_hom}
-d_{\Hom} = \begin{pmatrix} 0 & 0 & z^{N-i} & z^j \\ 
-0 & 0 & z^{N-j} & z^i \\
--z^i & z^j & 0 & 0 \\
-z^{N-j} & -z^{N-i} & 0 & 0 \end{pmatrix}\,.
-\end{equation}
-Let us now compute the cut $X^{\vee} \l Y$ with its Clifford action. With
-\[
-J_V = k[z]/z^{N-1} = k \cdot 1 \oplus k \cdot z \oplus \cdots k \cdot z^{N-2}
-\]
-the matrix of multiplication by $z$ on $J_V$ is $[z] = \begin{pmatrix} 0 & 0\\ I_{N-2} & 0 \end{pmatrix}$. The differential on
-\[
-X^{\vee} \l Y = \Hom_{J_V}( \bar{X}, \bar{Y} ) = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
-\]
-is then obtained from \eqref{eq:differential_hom} by replacing every $z$ by the matrix $[z]$.
-
-The Clifford algebra $A_1$ acts by two generators $a, a^\dagger$.
-To determine their matrices, note that with $t = z^{N-1}$, $k[z]$ is a free $k[t]$-module with basis $1, \ldots, z^{N-2}$.
-Given a polynomial $f(z)$ we may uniquely write it as $f(z) = \sum_{l = 0}^{N-2} f_l \cdot z^l$ with $f_l \in k[t]$.
-There is a connection $\nabla: k[z] \lto k[z] \otimes_{k[t]} \Omega^1_{k[t]/k}$ whose associated $k$-linear operator $\partial_t$ is
-\[
-\partial_t: k[z] \lto k[z], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) z^l \,.
-\]
-Notice that for $0 \le q \le N - 1$, $\partial_t(z^q) = \delta_{q (N-1)} \cdot 1$.
-
-The Atiyah class is the $k[t]$-linear operator $\At = [d_{\Hom}, \partial_t]$ on $\Hom_R(X,Y)$. We may compute it for example on generators by
-\[
-\At( \theta \theta^* ) = \partial_t d_{\Hom}( \theta \theta^* ) = - \partial_t( z^i ) \theta + \partial_t( z^{N-j} ) \theta^* = - \delta_{i (N-1)} \theta + \delta_{(N-j)(N-1)} \theta^*\,.
-\]
-The Atiyah class passes to a $k$-linear operator $a^\dagger$ on $X^{\vee} \l Y$ with matrix ($I$ denotes $I_{N-1}$)
-\begin{equation}\label{eq:aityah_class_hom_example}
-a^\dagger = \begin{pmatrix} 0 & 0 & \delta_{i1} \cdot I & \delta_{j(N-1)} \cdot I \\ 
-0 & 0 & \delta_{j1} \cdot I & \delta_{i(N-1)} \cdot I \\
-- \delta_{i(N-1)} \cdot I & \delta_{j(N-1)} \cdot I & 0 & 0 \\
-\delta_{j1} \cdot I & - \delta_{i1} \cdot I & 0 & 0 \end{pmatrix}\,.
-\end{equation}
-Similarly one can determine that the matrix of $\lambda$ on $X^{\vee} \l Y$ is
-\[
-\lambda = \begin{pmatrix} 0 & 0 & 0 & \frac{j}{N} [z^{j-1}] \\
-0 & 0 & \frac{N-j}{N} [z^{N-j-1}] & 0\\
-0 & \frac{j}{N} [z^{j-1}] & 0 & 0\\
-\frac{N-j}{N} [z^{N-j-1}] & 0 & 0 & 0\end{pmatrix}\,.
-\]
-By definition $a = - \lambda - \lambda^2 a^\dagger$ so this completes the description of the cut $( X^{\vee} \l Y, \{ a, a^\dagger \} )$.
-Splittng the idempotent $a^\dagger a$ on the $\mathbb{Z}_2$-graded complex $X^{\vee} \l Y$ of finite rank free $k$-modules yields a finite model for $\Hom_R(X,Y)$.
-\end{example}
-
-\appendix
-
-\section{Homological perturbation and fixed points}\label{section:homolog_fix}
-
-A fundamental role in this paper is played by the homological perturbation lemma.
-While this result is usually stated for complexes the standard results generalise immediately to linear factorisations, and in this section we collect these standard results.
-But we begin by recalling the motivating problem for which the perturbation lemma is the solution.
-
-Let $Q$ be a complex of infinite rank free abelian groups.
-Suppose that the cohomology is finitely generated, so that $Q$ contains in some sense only a ``finite'' amount of information.
-One can ask for a description which makes this finiteness manifest: the obvious answer is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.
-
-A \emph{deformation retract} of complexes is a pair of morphisms
-\begin{equation}\label{eq:example_defo_retract}
-\xymatrix@C+2pc{
-C \ar@<-1ex>[r]_\nabla & Q, \ar@<-1ex>[l]_f
-} \quad \phi
-\end{equation}
-and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $f \nabla = 1_C, \nabla f = 1_Q - [d_Q, \phi]$ so that $f, \nabla$ are mutually inverse homotopy equivalences.
-A deformation retract is \emph{strong} if it satisfies some additional conditions, listed below.
-The point is that if $C$ is finitely generated, then \eqref{eq:example_defo_retract} gives the desired finite representative in the homotopy equivalence class of $Q$.
-
-\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-modules
-\[
-\xymatrix@C+2pc@R+1pc{
-0 \ar[d] \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar[d]^-{x}\\
-k \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar@/_3pc/@{.>}[u]_-{\phi}
-}
-\]
-in which the first column is the complex $C$ which has $k$ concentrated in degree zero, and the second column $Q$ is the Koszul complex on $x$.
-The map $f: k[x] \lto k$ sends every polynomial to its constant term, while $\nabla: k \lto k[x]$ is the inclusion of the constants.
-The operator $\phi$ is defined by $\phi( x^n ) = x^{n-1}$ and $\phi(1) = 0$.
-Together these maps are a deformation retract giving $k$ as the ``finite model'' of $Q$.
-\end{example}
-
-Suppose now that a deformation retract computing a finite representative for $Q$ cannot be found immediately, but that we know how to decompose the differential as $d_Q = d + \tau$ in such a way that there is a finite representative for the complex $(Q,d)$.
-The perturbation lemma allows us, with some conditions, to ``mix in'' the operator $\tau$ to obtain a finite model for the original complex $Q$.
-\\
-
-Let $R$ be a commutative ring and $W \in R$.
-Everything we say applies, in the case where $W = 0$, to both $\mathbb{Z}_2$-graded and $\mathbb{Z}$-graded complexes.
-For our purposes the reformulation of the perturbation lemma in terms of fixed points by Barnes and Lambe is more natural, so we emphasise the ``splitting homotopies'' of \cite{barneslambe}.
-
-\begin{definition} A \emph{splitting homotopy} on a linear factorisation $(A,d)$ of $W$ is a degree $-1$ operator $\phi$ on $A$ satisfying
-\begin{itemize}
-\item[(i)] $\phi^2 = 0$,
-\item[(ii)] $\phi d \phi = \phi$.
-\end{itemize}
-A \emph{morphism} $(A,d, \phi) \lto (A,d',\phi')$ of splitting homotopies is a morphism $\alpha: A \lto A'$ of linear factorisations satisfying $\phi' \alpha = \alpha \phi$.
-\end{definition}
-
-The condition (ii) says that $\phi$ is a \emph{fixed point} of the operator $F(x) = x d x$.
-
-\begin{definition} A \emph{strong deformation retract} of linear factorisations of $W$ is a pair of morphisms of linear factorisations
-\begin{equation}\label{eq:defn_sdr}
-\xymatrix@C+2pc{
-(M,d) \ar@<-1ex>[r]_\nabla & (A,d), \ar@<-1ex>[l]_f
-} \quad \phi
-\end{equation}
-together with a degree $-1$ operator $\phi: A \lto A$ satisfying
-\begin{itemize}
-\item[(i)] $f \nabla = 1_M$,
-\item[(ii)] $\nabla f = 1_A - [d, \phi]$,
-\item[(iii)] $\phi^2 = 0$,
-\item[(iv)] $\phi \nabla = 0$,
-\item[(v)] $f \phi = 0$.
-\end{itemize}
-A \emph{morphism} of strong deformation retracts is a commutative diagram
-\[
-\xymatrix@C+2pc{
-(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\nabla & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_f\\
-(M',d') \ar@<-1ex>[r]_{\nabla'} & (A',d') \ar@<-1ex>[l]_{f'}
-}
-\]
-that is, a pair of morphisms $\alpha, \beta$ such that $\beta \nabla = \nabla' \alpha$, $\alpha f = f' \beta$ and $\phi' \beta = \beta \phi$.
-\end{definition}
-
-We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}.
-Namely, a strong deformation retract in the above sense is the same as a special deformation retract in the sense of \emph{ibid.} with $h = - \phi$.
-
-\begin{lemma}\label{lemma:equivocate} There is an equivalence between the category of splitting homotopies $\cat{C}_1$ and the category of  strong deformation retracts $\cat{C}_2$.
-\end{lemma}
-\begin{proof}
-We briefly recall the construction from \cite[p.883]{barneslambe}, which is not stated in terms of categories but is obviously functorial.
-Given a strong deformation retract \eqref{eq:defn_sdr} the data $(A, \phi)$ is a splitting homotopy.
-In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $\pi = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(\phi)$ with the associated projection $f$ and inclusion $\nabla$.
-Then this is a strong deformation retract, together with the original $\phi$.
-\end{proof}
-
-%Taking splitting homotopies as the primary object has the advantage of hiding some of the incidental complexity in the perturbation lemma.
-Here is the problem that the formalism is designed to solve: suppose $(A,d)$ is a linear factorisation of $W$ and that $\tau$ is a degree $+1$ operator on $A$ such that $(A, d + \tau)$ is a linear factorisation of $V$ (possibly different to $W$).
-This $\tau$ is called the \emph{perturbation}.
-
-\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(\pi) \cong \im(\pi')$ as graded $R$-modules, where $\pi = 1_A - [d, \phi]$ and $\pi' = 1_A - [d + \tau, \phi']$.
-\end{definition}
-
-That is, with $\xi = d + \tau$ the problem is to find a fixed point of the operator
-\[
-F(x) = x \xi x
-\]
-among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(\pi)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
-\[
-\phi_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \phi = \phi - \phi \tau \phi + \phi \tau \phi \tau \phi - \cdots
-\]
-is a solution of this fixed point problem:
-
-\begin{theorem}[Perturbation lemma]\label{theorem:pertlemma} Suppose $\phi \tau$ has finite order.
-Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi)$ and satisfies the isomorphism condition in the transference problem.
-\end{theorem}
-\begin{proof}
-The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations.
-\end{proof}
-
-The more common statement of the basic perturbation lemma involves the deformation retract corresponding to the splitting homotopy $\phi_\infty$ under the equivalence of Lemma \ref{lemma:equivocate}.
-The statement is that given a splitting homotopy $\phi$ as above with associated deformation retract \eqref{eq:defn_sdr} there is a strong deformation retract
-\begin{equation}\label{eq:perturbedsdr}
-\xymatrix@C+2pc{
-(M,d_\infty) \ar@<-1ex>[r]_{\nabla_\infty} & (A, \xi), \ar@<-1ex>[l]_{f_\infty}
-} \quad \phi_\infty
-\end{equation}
-where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
-\begin{align*}
-\nabla_\infty &= \nabla - \phi A \nabla,\\
-f_\infty &= f - f A \phi,\\
-d_\infty &= d + f A \nabla\,.
-\end{align*}
-As explained in \cite{barneslambe}, to derive these formulas one has only to notice that the sub-complex in the deformation retract associated to $\phi_\infty$ can, by the isomorphism
-\[
-\im(1 - [\xi, \phi_\infty]) \cong \im(\pi) = M
-\]
-be identified with $M$, and the induced maps are the $\nabla_\infty, f_\infty, d_\infty$ given above.
-It is also possible to give a direct proof as in \cite{crainic}.
-To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one just studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation.
-The standard way of generating fixed points, say by iterating $F$ infinitely many times on $\phi$, produces the same answer provided one takes the limit of the coefficients in $\mathbb{Q}$ with respect to the $2$-adic valuation; see \cite[p.885]{barneslambe}.
-
-\section{Tensor products in supercategories}\label{section:tensorproduct_supcat}
-
-Let $\cat{C}$ be an idempotent complete supercategory.
-
-\begin{definition} Let $V$ be a $\mathbb{Z}_2$-graded $k$-module and $X$ an object of $\cat{C}$.
-An object of $\cat{C}$ representing the functor $\Hom^0_k( V, \cat{C}^*(X, -))$ is denoted $V \otimes_k X$ if it exists.
-That is to say, the tensor product consists of an object $V \otimes_k X$ and a natural isomorphism
-\[
-\rho_Y: \cat{C}( V \otimes_k X, Y ) \lto \Hom^0_k( V, \cat{C}^*(X,Y) )\,.
-\]
-Such a pair is unique up to unique isomorphism, if it exists.
-\end{definition}
-
-\begin{remark} 
-From $\rho$ we also obtain an isomorphism of $\mathbb{Z}_2$-graded $k$-modules
-\[
-\cat{C}^*( V \otimes_k X, Y ) \cong \Hom_k^*( V, \cat{C}^*(X,Y) )\,.
-\]
-The tensor product $V \otimes_k X$ is made functorial in $V$ and $X$ in such a way that $\rho$ is natural in all its variables.
-\end{remark}
-
-\begin{example} If $V = k^{\oplus n} \oplus k[1]^{\oplus m}$ is finite and free then
-\[
-V \otimes_k X = X^{\oplus n} \oplus \Psi X ^{\oplus m}
-\]
-is a representing object, with the obvious isomorphism $\rho$.
-\end{example}
-
-\begin{lemma} If $\cat{C}$ is idempotent complete and $V$ is a finitely generated projective $\mathbb{Z}_2$-graded $k$-module, then $V \otimes_k X$ exists for any object $X$.
-\end{lemma}
-\begin{proof}
-Let $V'$ be a finite free $k$-module with $f: V' \lto V, g: V \lto V'$ satisfying $fg = 1$.
-This determines an idempotent $1 \otimes e$ on $V' \otimes_k X$, which splits by hypothesis in $\cat{C}$.
-The object splitting this idempotent has the right property to be $V \otimes_k X$.
-\end{proof}
-% via morphisms $F,G$ with
-%\[
-%\xymatrix@C+1pc{
-%Q \ar@<0.8ex>[r]^-{G} & V' \otimes_k X \ar@<0.8ex>[l]^-{F} 
-%} \qquad FG = 1, GF = 1 \otimes e
-%\]
-%for some object $Q$. We have
-%\begin{align*}
-%\cat{C}( Q, Y ) &\cong \{ f: V' \otimes_k X \lto Y \l f(1 \otimes e) = 1 \otimes e \}\\
-%&\cong \{ \hat{f} \in \Hom_k( V', \cat{C}^*(X,Y)) \l \hat{f} e = e \}\\
-%&\cong \Hom_k( V, \cat{C}^*(X,Y))\,.
-%\end{align*}
-%and hence $V \otimes_k X = Q$ exists.
-%\end{proof}
-
-More generally, let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra.
-
-\begin{definition} Given a right $\mathbb{Z}_2$-graded $A$-module $V$ and an object $X$ of $\cat{C}$, we denote by $V \otimes_A X$ the object representing the functor $\Hom^0_A( V, \cat{C}^*(X,-))$ if it exists.
-That is, the tensor product is an object $V \otimes_A X$ together with a natural isomorphism
-\begin{equation}\label{eq:isodefatensor}
-\rho_Y: \cat{C}(V \otimes_A X, Y) \lto \Hom^0_A( V, \cat{C}^*(X,Y))\,.
-\end{equation}
-As before, the tensor product is functorial in both $V$ and $X$.
-\end{definition}
-
-Henceforth we concentrate our attention on $\mathbb{Z}_2$-graded $k$-algebras $A$ which are \emph{Morita trivial} in the sense that they are isomorphic to an algebra of the form $\End_k(P)$ for a finite rank free $\mathbb{Z}_2$-graded $k$-module $P$.
-
-\begin{lemma} If $A \cong \End_k(P)$ then for any $A$-module $X$ in $\cat{C}$ there is an object $\widetilde{X}$ and an isomorphism of $A$-modules $X \cong P \otimes_k \widetilde{X}$.
-\end{lemma}
-\begin{proof}
-The natural idempotents in $A$ act as idempotents on $X$, which split.
-\end{proof}
-
-\begin{lemma} If $A \cong \End_k(P)$ and $V$ is a $\mathbb{Z}_2$-graded right $A$-module which is finitely generated and projective as a $k$-module, then $V \otimes_A X$ exists for any $A$-module $X$.
-\end{lemma}
-\begin{proof}
-Write $P^* = \Hom_k(P,k)$ so that $V \cong \widetilde{V} \otimes_k P^*$ as right $A$-modules for some $\mathbb{Z}_2$-graded $k$-module $\widetilde{V}$.
-Since $V$ is finitely generated projective over $k$, so is $\widetilde{V}$.
-By the previous lemma, $X \cong P \otimes_k \widetilde{X}$ for some object $\widetilde{X}$, so we might expect that
-\[
-V \otimes_A X \cong (\widetilde{V} \otimes_k P^*) \otimes_A (P \otimes_k \widetilde{X}) \cong \widetilde{V} \otimes_k \widetilde{X}
-\]
-Working backwards: $\widetilde{V} \otimes_k \widetilde{X}$ exists and has the right universal property since
-\begin{align*}
-\cat{C}(\widetilde{V} \otimes_k \widetilde{X}, Y) &\cong \Hom_k( V \otimes_A P, \cat{C}^*(\widetilde{X}, Y))\\
-&\cong \Hom_A( V, P^* \otimes_k \cat{C}^*(\widetilde{X}, Y))\\
-&\cong \Hom_A( V, \cat{C}^*( X, Y ) )
-\end{align*}
-as claimed.
-\end{proof}
-
-From now on $A,B,C$ are Morita trivial $k$-algebras. Recall $\cat{C}_A$ denotes the category of left $A$-modules in $\cat{C}$.
-
-\begin{definition}\label{defn:psimodule} Given a left $A$-module $X$ in $\cat{C}$, the object $\Psi X$ is a left $A$-module, where $a \in A_0$ acts by $\Psi(a)$ and $a \in A_1$ acts by
-\[
-\xymatrix{
-\Psi (X) \ar[r]^-{\Psi(a)} & \Psi \Psi (X) \ar[r]^-{-1} & \Psi \Psi (X)
-}\,.
-\]
-This determines a functor $\Psi: \cat{C}_A \lto \cat{C}_A$.
-\end{definition}
-
-\begin{lemma} $(\cat{C}_A, \Psi)$ is a supercategory.
-\end{lemma}
-\begin{proof}
-The natural isomorphism $\xi_X: \Psi \Psi (X) \lto X$ is given by the identity in $\cat{C}$.
-\end{proof}
-
-Let $V$ be a $B$-$A$-bimodule which is finitely generated and projective over $k$.
-If $X$ is a left $A$-module in $\cat{C}$ then $V \otimes_A X$ is made into a left $B$-module in $\cat{C}$ uniquely such that \eqref{eq:isodefatensor} is a natural isomorphism of $B$-modules.
-Hence the tensor product gives a functor
-\[
-\Phi_V = V \otimes_A (-): \cat{C}_A \lto \cat{C}_B\,.
-\]
-Given a $B$-$A$-bimodule $V$ and an object $X$ for which $V \otimes_A X$ exists, there are natural isomorphisms of $B$-modules
-\[
-\Psi V \otimes_A X \cong \Psi(V \otimes_A X) \cong V \otimes_A \Psi X
-\]
-induced from the isomorphisms
-\[
-\Hom_A( \Psi V, \cat{C}^*(X, -)) \cong \Hom_A( V, \Psi \cat{C}^*(X, -) ) \cong \Hom_A( V, \cat{C}^*(\Psi X, -))\,.
-\]
-It follows that $\Phi_V$ is a superfunctor.
-
-\begin{lemma}\label{lemma:assoctensor} Let $W$ be a $C$-$B$-bimodule and $V$ a $B$-$A$-bimodule. Then there is a natural isomorphism of $C$-modules
-\[
-(W \otimes_B V) \otimes_A X \cong W \otimes_B ( V \otimes_A X )
-\]
-\end{lemma}
-\begin{proof}
-This follows from the isomorphism
-\begin{align*}
-\Hom_A(W, \cat{C}^*(V \otimes_A X, -)) &\cong \Hom_A( W, \Hom_A^*(V, \cat{C}^*(X, -)))\\
-&\cong \Hom_A(W \otimes_A V, \cat{C}^*(X, -))\,.
-\end{align*}
-\end{proof}
-
-Now we specialise to the Clifford algebras $A_n$ and their modules.
-
-\begin{lemma}\label{lemma:simplehom} Let $X$ be a $\mathbb{Z}_2$-graded left $A_n$-module. There is a $k$-linear isomorphism
-\[
-\Hom_{A_n}^0( S_n, X ) \cong \{ x \in X^0 \l a_i^\dagger \cdot x = 0 \text{ for all } 1 \le i \le n \}
-\]
-defined by $f \mapsto f(1)$. If $X$ is a right $A_n$-module there is a $k$-linear isomorphism
-\[
-\Hom^0_{A_n}( (S_n)^*, X ) \cong \{ x \in X^0 \l x \cdot a_i = 0 \text{ for all } 1 \le i \le n \}
-\]
-defined by $f \mapsto f(1^*)$.
-\end{lemma}
-
-\begin{lemma}\label{lemma:morphism_out_1} For an $A_n$-module $Y$ there is a $k$-linear isomorphism
-\[
-\cat{C}_{A_n}( S_n \otimes_k X, Y ) \cong \{ \delta: X \lto Y \l a_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
-\]
-defined by sending $\alpha: S_n \otimes_k X \lto Y$ to the composite
-\[
-\xymatrix@C+2pc{
-X \cong k \otimes_k X \ar[r]^-{\iota \otimes 1} & S_n \otimes_k X \ar[r]^-{\alpha} & Y
-}
-\]
-where $\iota: k \lto S_n$ is defined by $\iota(1) = 1$.
-\end{lemma}
-\begin{proof}
-This follows from Lemma \ref{lemma:simplehom} and the isomorphism
-\[
-\cat{C}_{A_n}(S_n \otimes_k X, Y ) \cong \Hom_{A_n}( S_n, \cat{C}^*(X,Y) )\,.
-\]
-\end{proof}
-
-More generally
-
-\begin{lemma}\label{lemma:morphisms_two_forms} Let $X \in C_{A_p}$ and $Y \in \cat{C}_{A_q}$. There is a $k$-linear isomorphism
-\begin{align*}
-\cat{C}_{A_q}( S_{q,p} \otimes_{A_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ a_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ a_i^\dagger \circ \delta &= 0 \text{ for } 1 \le i \le q \}
-\end{align*}
-defined by sending $\alpha: S_{q,p} \otimes_{A_p} X \lto Y$ to the composite
-\[
-\xymatrix@C+2pc{
-X \cong A_p \otimes_{A_p} X \ar[r]^-{\iota \otimes 1} & S_{q,p} \otimes_{A_p} X \ar[r]^-{\alpha} & Y
-}
-\]
-where $\iota: A_p \lto S_{q,p}$ is defined by $\iota(1) = 1 \otimes 1^*$.
-\end{lemma}
-\begin{proof}
-Using the previous lemma and Lemma \ref{lemma:simplehom},
-\begin{align*}
-\cat{C}_{A_q}( S_{q,p} \otimes_{A_p} X, Y ) &\cong \Hom^0_{A_p-A_q}( S_{q} \otimes_k S_p^* , \cat{C}^*(X,Y))\\
-&\cong \Hom^0_{A_q}( S_q, \Hom^*_{A_p}( S_p^*, \cat{C}^*(X,Y) ))\\
-&\cong \{ \delta \in \Hom^0_{A_q}( S_p^*, \cat{C}^*(X,Y) ) \l a_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
-&\cong \{ \delta: X \lto Y \l \delta \circ a_i = 0 \text{ for } 1 \le i \le p \text{ and } a_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}
-\end{align*}
-as claimed.
-\end{proof}
-
-\section{Extending cut functors}\label{app:proof_cut_extension}
-
-The purpose of this appendix is to give the proof of Proposition \ref{prop:extend_cut_functor}. First, note that
-
-\begin{lemma}\label{lemma:altcomppersp} Let $\cat{C}$ be a small idempotent complete supercategory and take morphisms
-\[
-\xymatrix{
-(X,n) \ar[r]^-{\alpha} & (Y,m) \ar[r]^-{\beta} & (Z,l)
-}\\
-\]
-in $\cat{C}^\bullet$. Under \eqref{eq:isodefatensor} these correspond to bimodule maps
-\[
-\widetilde{\alpha}: S_{m,n} \lto \cat{C}^*(X,Y)\,, \qquad \widetilde{\beta}: S_{l,m} \lto \cat{C}^*(Y,Z)\,.
-\]
-The composite $\beta \circ \alpha: S_{l,n} \otimes_{A_n} X \lto Z$ in $\cat{C}^\bullet$ corresponds to the composite
-\[
-\xymatrix{
-S_{l,n} \cong S_{l,m} \otimes_{A_m} S_{m,n} \ar[r]^-{\widetilde{\beta} \otimes \widetilde{\alpha}} & \cat{C}^*(Y,Z) \otimes_{A_m} \cat{C}^*(X,Y) \ar[r]^-{\circ} & \cat{C}^*(X,Z)
-}\,.
-\]
-\end{lemma}
-\begin{proof}
-Follows by evaluation on $1 \otimes 1^* \in S_{l,n}$.
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop:extend_cut_functor}]
-Given $(X,n) \in \cat{C}_1^\bullet$ and $(Y,m) \in \cat{C}_2^\bullet$ we have $T(X,Y) = (Z,t)$ for some object $Z$ of $\cat{C}_3$.
-Given $a \in A_n$, say of odd degree, there is a morphism of $A_t$-modules $Z \lto \Psi Z$ given by
-\[
-\xymatrix@C+2pc{
-T(X,Y) \ar[r]^-{T(a \otimes 1)} & T(\Psi X, Y ) \ar[r]^-{\tau} & \Psi T(X,Y)
-}
-\]
-and this defines an algebra morphism $A_n \lto \cat{C}_3^*(Z,Z)$.
-Doing the same for $A_m$ defines a morphism $A_{m+t+n} \cong A_m \otimes A_t \otimes A_n \lto \cat{C}_3^*(Z,Z)$ and an object $(Z, m + t +n) \in \cat{C}_3^\bullet$.
-We define $\widetilde{T}$ on objects by
-\begin{equation}\label{eq:ttilde}
-\widetilde{T}( (X,n), (Y,m) ) = (Z, m + t + n)\,.
-\end{equation}
-Next we define $\widetilde{T}$ on morphisms. Given $\alpha: (X_1,n_1) \lto (X_2,n_2)$ in $\cat{C}_1^\bullet$ and $T(X_i,Y) = (Z_i,t)$ for $i = 1,2$ we must construct a morphism
-\[
-\widetilde{T}(\alpha,1): (Z_1, m+t+n_1) \lto (Z_2, m+t+n_2)\,.
-\]
-Since $\alpha$ corresponds to an $A_{n_1}$-linear map $\widetilde{\alpha}: V \lto \cat{C}_1^*(X_1,X_2)$ we can compose with $T$ to get an $A_{n_2}$-$A_{n_1}$-bilinear map $\eta := T(1,Y) \circ \widetilde{\alpha}: V \lto \cat{C}_3^*(Z_1,Z_2)$.
-This extends to a morphism of $A_{n_2+c}$-$A_{n_1+c}$-bimodules
-\[
-V \otimes_k A_c \lto \cat{C}_3^*(Z_1,Z_2), \qquad v \otimes a \mapsto \eta(v) a\,.
-\]
-There is a canonical isomorphism of $A_{n+2+c}$-$A_{n_1+c}$-bimodules
-\begin{align*}
-S_{n_2+c,n_1+c} \cong S_{n_2+c} \otimes_k S_{n_1+c}^* \cong (S_{n_2} \otimes_k S_c) \otimes_k (S_c^* \otimes_k S_{n_1}^*) \cong V \otimes_k (S_c \otimes_k S_c^*) \cong V \otimes_k A_c
-\end{align*}
-so we have constructed $S_{n_2+c,n_1+c} \lto \cat{C}_3^*(Z_1,Z_2)$ which corresponds to a morphism of $A_{n_2+c}$-modules $S_{n_2+c, n_1+c} \otimes_{A_{n_1+c}} Z_1 \lto Z_2$ which we define to be $\widetilde{T}(\alpha,1)$.
-Functoriality of this construction follows from Lemma \ref{lemma:altcomppersp}.
-The functoriality in the other variable follows similarly.
-By construction $\widetilde{T}$ makes both of the required diagrams commute.
-\end{proof}
-
-\section{Constructing superbicategories}\label{section:constructing_superbicategories}
-
-This appendix collects the data needed for constructing a superbicategory $\cat{B}$ from a collection of supercategories $\cat{B}(a,b)$.
-Given a bicategory $\cat{B}$ and for each pair of objects $a,b$ the structure of a supercategory on $\cat{B}(a,b)$, we denote composition by
-\[
-T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
-\]
-We assume this is a superfunctor, i.e.
-that \eqref{eq:psicomp1}-\eqref{eq:psicomp3} commute.
-Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$.
-We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.
-
-Suppose that for all objects $a,b,c$ we are given natural isomorphisms
-\begin{align*}
-T \circ ( \Psi \otimes 1 ) \lto \Psi \circ T, \qquad T \circ ( 1 \otimes \Psi ) \lto \Psi \circ T
-\end{align*}
-both of which will be denoted $\tau$.
-We define for an object $a$ the $1$-morphism $\Psi_a = \Psi( \Delta_a )$ and the $2$-isomorphism $\xi_a$ to be the following composite (using the structure maps of $\cat{B}$ and isomorphisms $\tau$)
-\[
-\xi_a: \Psi_a \l \Psi_a = \Psi( \Delta_a ) \l \Psi( \Delta_a ) \cong \Psi( \Delta_a \l \Psi(\Delta_a ) ) \cong \Psi^2( \Delta_a \l \Delta_a ) \cong \Delta_a \l \Delta_a \cong \Delta_a\,.
-\]
-Similarly given a $1$-morphism $X: a \lto b$ we have a $2$-isomorphism $\gamma_X$
-\[
-\gamma_X: X \l \Psi_a = X \l \Psi( \Delta_a ) \cong \Psi( X \l \Delta_a ) \cong \Psi(X) \cong \Psi( \Delta_b \l X ) \cong \Psi( \Lambda_b ) \l X = \Psi_b \l X\,.
-\]
-Given a $1$-morphism $X: a \lto b$ in $\cat{B}$ there are diagrams
-\begin{gather}
-\xymatrix@R+1pc@C+1pc{
-\Delta_b \l \Psi (X) \ar[dr]_-{\lambda_{\Psi a}} \ar[rr]^-{\tau} & & \Psi( \Delta_b \l X ) \ar[dl]^-{\Psi( \lambda )}\\
-& \Psi(X)
-} \label{eq:psiunitor1}\\
-\xymatrix@R+1pc@C+1pc{
-\Psi(X) \l \Delta_a \ar[rr]^-{\tau}\ar[dr]_-{\rho} & & \Psi( X \l \Delta_a ) \ar[dl]^-{\Psi(\rho)}\\
-& \Psi(X)
-} \label{eq:psiunitor2}
-\end{gather}
-whose commutativity expresses compatibility of the functors $\Psi$ with the units, while for a composable triple $X,Y,Z$ the commutativity of the diagrams
-\begin{gather}
-\xymatrix{
-(Z \l Y) \l \Psi(X) \ar[dd]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( Y \l \Psi(X)) \ar[d]^-{\tau}\\
- & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
-\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
-} \label{eq:psithirdlastdia}\\
-\xymatrix{
-(Z \l \Psi(Y)) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & Z \l ( \Psi(Y) \l X) \ar[d]^-{\tau}\\
-\Psi( Z \l Y ) \l X \ar[d]_-{\tau} & & Z \l \Psi( Y \l X ) \ar[d]^-{\tau}\\
-\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
-} \label{eq:psimiddledia}\\
-\xymatrix{
-(\Psi(Z) \l Y) \l X \ar[d]_-{\tau} \ar[rr]^-{\alpha} & & \Psi(Z) \l ( Y \l X ) \ar[dd]^-{\tau}\\
-\Psi(Z \l Y) \l X \ar[d]_-{\tau} & & \\
-\Psi( (Z \l Y) \l X ) \ar[rr]_-{\alpha} & & \Psi( Z \l ( Y \l X ) )
-}\label{eq:psilastdia}
-\end{gather}
-expresses compatibility of $\Psi$ with the associator of $\cat{B}$.
+Somehow in this language we encode the fact that the cut is linear in any extra degrees of freedom you add in.
+This can also be seen in the nature of what happens when you interact the $\mathscr{H}\!om$ bundle with the universal property defining $\cat{M}$.
 
@@
 The proof is an easy but somewhat lengthy exercise, which we omit.
-\end{proof}
-
-\section{Clifford actions and Koszul complexes}\label{section:cliffordactkos}
-% spkos series
-
-Let $R$ be a $\mathbb{Q}$-algebra and $(X,d)$ a linear factorisation of some $W \in R$.
-Let $t_1,\ldots,t_n$ be a sequence of elements of $R$ acting null-homotopically on $X$ and choose degree $-1$ operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$.
-
-Letting $\theta_i$ be a formal variable of degree $-1$, we define the Koszul complex $(K,d_K)$ with underlying graded module the exterior algebra $K$ on the $\theta_i$, as in \eqref{defn:koszul}.
-The tensor product $K \otimes X = (K \otimes X, d + d_K)$ is another linear factorisation of $W$ and on the underlying graded module $K \otimes X$ we have operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$.
-We can define additional operators in terms of these by $\psi_k^* = \theta_k^*$ and
-\begin{equation}
-\psi_k = \theta_k - \sum_{m \ge 0} \sum_{q_1,\ldots,q_m} \frac{1}{(m+1)!} [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_k ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
-\end{equation}
-The appendix is taken up with the proof of:
-
-\begin{theorem}\label{theorem:psik} The operators $\psi_k, \psi_k^*$ on $K \otimes X$ are closed and satisfy the Clifford relations
-\begin{equation}\label{eq:clifford_reln_psi}
-[ \psi_i, \psi_j ] = 0, \quad [ \psi_i^{*}, \psi_j^{*} ] = 0, \quad [ \psi_i, \psi_j^{*} ] = \delta_{ij}\,.
-\end{equation}
-\end{theorem}
-
-We introduce the notation
-\begin{align*}
-\delta &= \sum_{i=1}^n \lambda_i \theta_i^*,\\
-\exp(-\delta) &= \sum_{m \ge 0} (-1)^m \frac{1}{m!} \delta^m\,.
-\end{align*}
-
-\begin{proposition}\label{prop:equivalencekoszul} There are mutually inverse isomorphisms of linear factorisations
-\[
-\xymatrix@C+3pc{ (K \otimes X, d + d_K) \ar@<1ex>[r]^-{ \exp(\delta) } & (K \otimes X, d) \ar@<1ex>[l]^-{ \exp(-\delta) } }\,.
-\]
-\end{proposition}
-
-Before we give the proof, we need the key observation that $[d, \delta] = \sum_i [d, \lambda_i] \theta_i^* = d_K$. More generally
-
-\begin{lemma}\label{lemma:pert1} $[d, \delta^m] = m \delta^{m-1} d_K$ for $m \ge 1$.
-\end{lemma}
-\begin{proof}
-\[
-[ d, \delta^m ] = \sum_{i=0}^{m-1} \delta^i [d, \delta] \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i d_K \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i \delta^{m-i-1} d_K = m \delta^{m-1} d_K
-\]
-\end{proof}
-
-\begin{lemma}\label{lemma:pert2} $[ d, \exp(-\delta) ] = - \exp(-\delta) d_K$ and $[ d, \exp(\delta) ] = \exp(\delta) d_K$.
-\end{lemma}
-\begin{proof}
-We prove the first identity using Lemma \ref{lemma:pert1}, the second is the same:
-\begin{align*}
-[d, \exp(-\delta)] &= \sum_{m \ge 1} \frac{(-1)^m}{m!} [ d, \delta^m ]\\
-&= \sum_{m \ge 1} \frac{(-1)^m}{m!} m \delta^{m-1} d_K\\
-&= - \sum_{m \ge 0} \frac{(-1)^m}{m!} \delta^m d_K\\
-&= - \exp(-\delta) d_K
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Proposition \ref{prop:equivalencekoszul}]
-It suffices to show $\exp(-\delta)$ is a morphism of linear factorisations. But using Lemma \ref{lemma:pert2}
-\[
-(d + d_K) \exp(-\delta) - \exp(-\delta) d = [d, \exp(-\delta)] + d_K \exp(-\delta) = 0
-\]
-and similarly for the other equation.
-\end{proof}
-
-The operators $\theta_i, \theta_i^*$ generate a Clifford action on the exterior algebra $K$ and therefore act via closed operators on $K \otimes X$.
-The $\psi_k, \psi_k^*$ are defined to be the translation of this Clifford structure to the $K \otimes X$ using the Proposition, i.e.
-\begin{align}
-\psi_k &= \exp(-\delta) \theta_k \exp(\delta), \label{eq:defn_psik1}\\
-\psi_k^{*} &= \exp(-\delta) \theta_k^* \exp(\delta)\,. \label{eq:defn_psik2}
-\end{align}
-
-It remains to show that these operators have the form described prior to the statement of the theorem.
-
-\begin{lemma} $\psi_k^{*} = \theta_k^*$ for $1 \le k \le n$.
-\end{lemma}
-\begin{proof}
-Since $\delta$ commutes with $\theta_k^*$, $\exp(-\delta) \theta_k^* = \theta_k^* \exp(-\delta)$.
-\end{proof}
-
-However the operator $\theta_k$ is not closed, indeed $[ \theta_i, d + d_K ] = t_i$, and so giving a closed formula for $\psi_k^*$ is more involved.
-In the development below we fix an index $k$.
-To compute $\psi_k$ the strategy is to commute $\theta_k$ past $\exp(-\delta)$.
-To this end we must first compute $[\theta_k, \delta^m]$ and then $[\theta_k, \exp(-\delta)]$.
-The calculation begins
-\begin{equation}\label{eq:catfish}
-[ \theta_k, \delta^m ] = \sum_{p=0}^{m-1} \delta^p [ \theta_k, \delta ] \delta^{m-p-1} = - \sum_{p=0}^{m-1} \delta^p [ \delta, \theta_k ] \delta^{m-p-1}\,.
-\end{equation}
-We need to understand how to commute $\delta^p$ past the $[ \delta, \theta_k ]$. The following notation will be used for any elements of $a,b$ of a graded ring and $m \ge 1$
-\[
-[b, a]^{(m)} = [b, [b, [b, \cdots [b, a] \dots ]
-\]
-where there are $m$ occurrences of $b$. By convention $[b,a]^{(0)} = a$.
-
-\begin{lemma} $b^m [b, a] = \sum_{i+j=m} \binom{m}{i} [b,a]^{(i+1)} b^j$ for $m \ge 1$.
-\end{lemma}
-\begin{proof}
-By induction, with the case $m = 1$ being clear. Using the inductive hypothesis
-\[
-b^{m+1} [b, a] = \sum_{i+j=m} \binom{m}{i} b [b,a]^{(i+1)} b^j = \sum_{i+j=m} \binom{m}{i} \Big[ [b,a]^{(i+2)} b^j + [b,a]^{(i+1)} b^{j+1} \Big]\,.
-\]
-The powers of $b$ range from $0$ to $m+1$ and the coefficient of $b^j$ for $1 \le j \le m$ is
-\[
-\binom{m}{m-j} [b,a]^{(m-j+2)} + \binom{m}{m-j+1} [b,a]^{(m-j+2)} = \binom{m+1}{m+1-j} [b,a]^{(m-j+2)}\,.
-\]
-The coefficient of $b^0$ is $[b,a]^{(m+2)}$ and the coefficient of $b^{m+1}$ is $[b,a]^{(1)}$, so we are done.
-\end{proof}
-
-From the previous lemma we deduce that
-\begin{equation}\label{eq:calc1}
-\delta^p [ \delta, \theta_k ] = \sum_{i+j=p} \binom{p}{i} [ \delta, \theta_k ]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [ \delta, \lambda_k ]^{(i)} \delta^j\,.
-\end{equation}
-The next thing to compute is $[ \delta, \lambda_k ]^{(i)}$ for any $i$. For a tuple $\bold{q} = (q_1,\ldots,q_m)$ of integers between $1$ and $n$ we write (remembering that $k$ is fixed)
-\begin{gather*}
-\tau_{\bold{q}} = [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \lambda_k ] \cdots ]\\
-\theta_{\bold{q}}^* = \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
-\end{gather*}
-
-\begin{lemma} For $m \ge 0$
-\[
-[ \delta, \lambda_k ]^{(m)} = (-1)^m \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m}\,.
-\]
-\end{lemma}
-\begin{proof}
-By the inductive hypothesis
-\begin{align*}
-[\delta, \lambda_k]^{(m+1)} &= [ \delta, [ \delta, \lambda_k ]^{(m)} ]\\
-&= (-1)^m \sum_{\bold{q}} [ \delta, \tau_{\bold{q}} \theta_{\bold{q}}^* ]\\
-&= (-1)^m \sum_{\bold{q}, q_{m+1}} [ \lambda_{q_{m+1}} \theta_{q_{m+1}}^*, \tau_{\bold{q}} \theta_{\bold{q}}^* ]\\
-&= (-1)^m \sum_{\bold{q}, q_{m+1}} \big( \lambda_{q_{m+1}} \theta_{q_{m+1}}^* \tau_{\bold{q}} \theta_{\bold{q}}^* + \tau_{\bold{q}} \theta_{\bold{q}}^* \lambda_{q_{m+1}} \theta_{q_{m+1}}^* \big)\\
-&= (-1)^m \sum_{\bold{q}, q_{m+1}} \big( -\lambda_{q_{m+1}} \tau_{\bold{q}}  \theta_{\bold{q}}^* \theta_{q_{m+1}}^* + (-1)^m \tau_{\bold{q}} \lambda_{q_{m+1}} \theta_{\bold{q}}^* \theta_{q_{m+1}}^* \big)\\
-&= (-1)^{m+1} \sum_{\bold{q}, q_{m+1}} [ \lambda_{q_{m+1}}, \tau_{\bold{q}} ] \theta_{\bold{q}}^* \theta_{q_{m+1}}^*
-\end{align*}
-as claimed.
-\end{proof}
-
-Continuing the computation of \eqref{eq:calc1} we have
-\begin{equation}
-\label{eq:calc2}
-\delta^p [\delta, \theta_k ] = \sum_{i+j=p} \binom{p}{i} (-1)^i \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^j\,.
-\end{equation}
-
-\begin{lemma}\label{lemma:commutator_wha} For $m \ge 1$
-\[
-[ \theta_k, \delta^m ] = \sum_{i=0}^{m-1} (-1)^{i+1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^{m-i-1}
-\]
-\end{lemma}
-\begin{proof} 
-Beginning from \eqref{eq:catfish}
-\begin{align*}
-[ \theta_k, \delta^m ] &= - \sum_{p=0}^{m-1} \delta^p [ \delta, \theta_k ] \delta^{m-p-1}\\
-&= - \sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} (-1)^i \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^j \delta^{m-p-1}
-\end{align*}
-\end{proof}
-
-\begin{lemma}\label{lemma:combin} For integers $a, b \ge 0$
-\begin{equation}\label{eq:combin}
-\frac{b!}{(a+b+1)!} \sum_{a \le m \le a + b} \binom{m}{a} = \frac{1}{(a+1)!}
-\end{equation}
-\end{lemma}
-\begin{proof}
-Denoting the left hand side of \eqref{eq:combin} by $\Omega_{a,b}$ the proof is an induction on $b$, i.e. by computing $\Omega_{a,b+1}$ in terms of $\Omega_{a,b}$.
-\end{proof}
-
-\begin{lemma}
-\[
-[\theta_k, \exp(-\delta)] = \sum_{m \ge 0} \frac{1}{(m+1)!} \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m} \exp(-\delta)\,.
-\]
-\end{lemma}
-\begin{proof}
-Using Lemma \ref{lemma:combin} and Lemma \ref{lemma:commutator_wha}
-\begin{align*}
-[\theta_k, \exp(-\delta)] &= \sum_{m \ge 0} \frac{(-1)^m}{m!} [\theta_k, \delta^m]\\
-&= \sum_{m \ge 0} \sum_{i=0}^{m-1} (-1)^{i+m+1} \frac{1}{m!} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^{m-i-1}\\
-&= \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{(t+1+i)!} \sum_{i \le p \le t + i} \binom{p}{i} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta_{q_1,\ldots,q_i}^* \delta^t\\
-&= \sum_{t \ge 0} \sum_{i \ge 0} \frac{(-1)^t}{t!} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \delta^t\\
-&= \sum_{m \ge 0} \frac{1}{(m+1)!} \sum_{q_1,\ldots,q_m} \tau_{q_1,\ldots,q_m} \theta^*_{q_1,\ldots,q_m} \exp(-\delta)\,.
-\end{align*}
-\end{proof}
-
-\begin{proof}[Proof of Theorem \ref{theorem:psik}] 
-\begin{align*}
-\psi_k &= \exp(-\delta) \theta_k \exp(\delta)\\
-&= \theta_k \exp(-\delta) \exp(\delta) + [ \exp(-\delta), \theta_k ] \exp(\delta)\\
-&= \theta_k - [ \theta_k, \exp(-\delta) ] \exp(\delta)\\
-&= \theta_k - \sum_{i \ge 0} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} \exp(-\delta) \exp(\delta)\\
-&= \theta_k - \sum_{i \ge 0} \frac{1}{(i+1)!} \sum_{q_1,\ldots,q_i} \tau_{q_1,\ldots,q_i} \theta^*_{q_1,\ldots,q_i} 
-\end{align*}
-which completes the proof.
 \end{proof}
@@
 
-\bibitem{gentzen}
-G.~Gentzen, \textsl{The Collected Papers of Gerhard Gentzen}, (Ed. M. E. Szabo), Amsterdam, Netherlands: North-Holland, 1969.
-
 \bibitem{girard_llogic}
 J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
-
-\bibitem{girard_towards}
-J.-Y.~Girard, \textsl{Towards a geometry of interaction}, In J.~W.~Gray and A.~Scedrov, editors, Categories in Computer Science and Logic, volume 92 of Contemporary Mathematics, 69--108, AMS (1989).
 

### 2015-10-18 cutsystems-new.tex
Edits.

@@
 \newcommand{\md}[1]{\mathscr{#1}}
+\def\sus{\l}
 \def\l{\,|\,}
@@
 \begin{abstract}
-In the bicategory of Landau-Ginzburg models $\LG$ the objects are certain polynomials called potentials, and the $1$-morphisms are matrix factorisations.
-The composition of these $1$-morphisms is defined by a form of convolution, and is not easy to compute.
-In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms is given explicitly.
-This construction will be applied in a sequel to define an enrichment of $\LG$ over affine schemes.
+The bicategory $\LG$ of Landau-Ginzburg models has polynomials as objects and matrix factorisations as $1$-morphisms.
+The composition of $1$-morphisms in this bicategory naturally produces infinite rank matrix factorisations, which is a nuisance.
+In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
 \end{abstract}
@@
 \LG(V,U)_{fin} \times \LG(W, V)_{fin} \lto \LG(W,U)\,,\\
-(Y,X) \mapsto Y \otimes X\,.
+(Y,X) \mapsto Y \circ X\,.
 \end{gather*}
@@
 \]
-with the property that $c([Y], [X]) = [Y \otimes X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.
-
-The problem is that this doesn't make any sense, because $Y \otimes X$ contains monomials $x^i y^j z^k$ with $y$'s in them (we say $Y \otimes X$ is \emph{infinite rank} over $k[x,z]$) and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$.
-However one can prove that $Y \otimes X$ is a summand in the homotopy category of a finite rank matrix factorisation (involving only $x$'s and $z$'s) and even describe this object and the corresponding idempotent explicitly \cite{dm1102.2957}.
-This is a finite amount of data which can be used to encode $Y \otimes X$, so we just need to replace $\mathscr{M}(W,U)$ by some scheme which knows how to store such data.
+with the property that $c([Y], [X]) = [Y \circ X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.
+
+The problem is that this doesn't make sense, because the matrix of polynomials defining the composite $Y \circ X$ contains monomials $x^i y^j z^k$ with $y$'s in them and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$.
+However one can prove that $Y \circ X$ is a summand in the homotopy category of a finite rank matrix factorisation (involving only $x$'s and $z$'s) and even describe this object and the corresponding idempotent explicitly \cite{dm1102.2957}.
+This is a finite amount of data which can be used to encode $Y \circ X$, so we just need to replace $\mathscr{M}(W,U)$ by some scheme which knows how to store such data.
 
@@
 The schemes parametrising $1$-morphisms in $\cat{L}$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}.
-However the present paper is concerned only with defining the bicategory $\cat{L}$ and proving that it is equivalent to $\LG$.
+However the present paper is concerned only with defining the superbicategory $\cat{L}$ and proving that it is equivalent to $\LG$.
 
 The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
-In Section \ref{section:cut_systems} we define cut systems and the superbicategory associated to a cut system, then we construct the cut model of $\LG$ in Section \ref{section:lg_cut_system}.
+In Section \ref{section:lg_cut_system} we define $\cat{L}$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$.
 
@@
 \]
-where the objects of $\operatorname{Bord}_{2,1}$ are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.
+where the symmetric monoidal category $\operatorname{Bord}_{2,1}$ is defined roughly as follows: the objects are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.
 
@@
 %     \put(433,142)   {$ \phi_\text{out} $}
-	 \put(295,85)   {$ Y $}
-	 \put(240,190)   {$ X $}
+	 \put(295,190)   {$ {\scriptstyle Y} $}
+	 \put(240,190)   {$ {\scriptstyle X} $}
+	 \put(335,85)   {$ {\scriptstyle Z} $}
+	 \put(390,105)   {$ {\scriptstyle Q} $}
      \put(510,180)   {$ O_{3} $}
@@
 \caption{A world-sheet $M$ with defect lines from $\,(O_1,O_2)\,$ to
-$\,(O_{3})$.\ The two-dimensional regions of the world-sheet are all labelled with the same potential $W(x)$, while $X,Y$ are matrix factorisations of $W(x) - W(x')$.
-The labels on the other defect lines are omitted.}
+$\,(O_{3})$.}
 \label{fig:wsh-defect}
@@
 
-Consider the example shown in Figure \ref{fig:wsh-defect}, where $\cat{B} = \LG$, the two-dimensional regions are all labelled with a single potential $W(x)$ and $X,Y: W \lto W$ are $1$-morphisms.
+With $\cat{B} = \LG$ an example of a morphism is given in Figure \ref{fig:wsh-defect}.
+The two-dimensional regions of $M$ are labelled with potentials and the defect lines are labelled with $1$-morphisms in $\LG$, that is, matrix factorisations.
+In the special case where we use a single label $W(x)$ for all regions, the labels $X,Y,Z,Q$ for the defect lines are all chosen from the set of $1$-morphisms $W \lto W$.
 The value of $\mathcal{Z}$ on $M$ is a $\nC$-linear map
@@
 We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$.
-Namely, it is a consequence of the way the defect conditions $X,Y$ enter the partition function \cite[(3.16)]{laz} that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining $Y,X$.
-To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme $\mathscr{M}_Y \times \mathscr{M}_X$ parametrising possible labels and $\mathcal{Z}(M)$ as a morphism of these vector bundles.
+Namely, it is a consequence of the way the defect conditions $X,Y,Z,Q$ enter the partition function (see for example \cite[(3.16)]{laz}) that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining the defect conditions.
+To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme parametrising possible defect conditions and $\mathcal{Z}(M)$ as a morphism of these vector bundles.
 But there are some obstacles.
@@
 
-Consider the incoming circle $O_2$ with its labels $Y,X$. The construction gives
+Consider the incoming circle $O_2$ with two points marked $X,Y$. The construction gives
 \be\label{eq:zo2orig}
-\mathcal{Z}(O_2) := H^0 \Hom_{\nC[x,x']}( Y, X )
+\mathcal{Z}(O_2) := \Hom_{\LG(W,W)}( \Delta_W, Y^{\vee} \otimes X) \cong H^0 \Hom_{\nC[x,x']}( Y, X )
 \ee
@@
 \be\label{eq:cohom_sucks}
-\big\{ H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \big\}_{P,Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
+H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \Big\vert_{t=P, u=Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
 \ee
 %This is a particular case of a general phenomenon: any complex of $\nC$-vector spaces $C$ is isomorphic in the derived category $\mathbb{D}(\nC)$ to $\bigoplus_n H^n(C)[n]$, but over a general ring, for instance the coordinate ring of $\mathscr{M}_Y \times \mathscr{M}_X$, this is not the case.
-The solution is to work instead with the full complex, which suggests the definition\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
+This discrepancy suggests that we should take as our global object $\mathcal{Z}(O_2)$ the Hom complex itself, as an object in the derived category\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
 \be\label{eq:wuhe20}
@@
 An alternative (and we believe simpler) approach is to take $\cat{L}$ rather than $\LG$ as the input to the definition of the TFT.
-Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define $\mathcal{Z}(O_2)$ to be the following composite in $\LG$:
+Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define the vector space $\mathcal{Z}(O_2)$ from \eqref{eq:zo2orig} via the following composite in $\LG$:
 \be\label{eq:composite_intro_o2}
@@
 \be
-\{ Y^{\vee}(t) \l X(u) \}_{P,Q} \cong Y^{\vee}(P) \l X(Q)
+Y^{\vee}(t) \l X(u) \Big\vert_{t=P,u=Q} \cong Y^{\vee}(P) \l X(Q)
 \ee
@@
 
-In forthcoming work we use the results of this paper to define a novel semantics of linear logic, in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
+In forthcoming work we will use the results of this paper to define a novel semantics of linear logic, in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
 Proofs in the logic are interpreted by certain correspondences between these pairs.
-To explain briefly why we are forced to use $\cat{L}$ rather than $\LG$, it is enough to describe the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
+To explain briefly why we are forced to use $\cat{L}$ rather than $\LG$, we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
 
 Let $x$ be a variable of the logic and suppose it has denotation $\llbracket x \rrbracket = (\Spec(\nC), \nC[x], W)$ in the semantics.
-Let $\mathscr{M} = \mathscr{M}(W,W)$ be the affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\cat{L}$, as discussed above.
-Then
+Let $\mathscr{M} = \mathscr{M}(W,W)$ be the (indexed) affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\cat{L}$, as discussed above.
+Then the semantics works as follows:
 \begin{gather*}
@@
 \end{gather*}
-The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ is roughly speaking a bundle $\llbracket \underline{2} \rrbracket$ over the scheme $\mathscr{M}$ whose fiber over a loop $X$ is the square $X \l X$.
-More precisely, the denotation is the vector bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over a point $(X, a)$ is
+The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which concretely means that $\llbracket \underline{2} \rrbracket$ is a bundle over the scheme $\mathscr{M}$ whose fiber over a loop $X$, viewed as a point $[X] \in \mathscr{M}$, is the square $X \l X$.
+More precisely, $\llbracket \underline{2} \rrbracket$ is the bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over $([X], a)$ is
 \be\label{eq:bundledifferentialcliffordproof}
-\llbracket \underline{2} \rrbracket_{X,a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)\,.
-\ee
-For these definitions to work, it is necessary to be able to compute the coefficients of $X \l X$ as a function of the coefficients of $X$, so we must use $\cat{L}$ in place of $\LG$.
+\llbracket \underline{2} \rrbracket_{[X],a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)\,.
+\ee
+For these definitions to work, the coefficients of the monomials in the matrix factorisation $X \l X$ need to be given explicitly as polynomial functions of the coefficients in $X$.
+This means we have to use $\cat{L}$ rather than $\LG$.
 
@@
 
-\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft, and to Ingo Runkel and Rafal Suszek for kindly providing Figure \ref{fig:wsh-defect}.
+\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft, and to Ingo Runkel and Rafal Suszek for kindly allowing the use of Figure \ref{fig:wsh-defect} from \cite{runkel}.
 %Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.
@@
 \end{equation}
+Thus $Y \circ X := Y \otimes X$.
 This statement requires some care: $k[x,y,z]$ is an infinite rank free module over $k[x,z]$ and so $Y \otimes X$ is an infinite rank matrix factorisation of $U - W$ over $k[x,z]$.
@@
 We set $C_0 = k$.
-These Clifford algebras have essentially only one nontrivial representation, sometimes called the \emph{spinor representation} \cite[p.14]{friedrich}.
-To define this representation we use the $\nZ_2$-graded $k$-module
-\[
+These Clifford algebras have essentially only one nontrivial representation, sometimes called the \emph{spinor representation} \cite[p.14]{friedrich}, defined as follows:
+
+\begin{definition} We use the $\nZ_2$-graded $k$-module
+\be
 F_n = k \theta_1 \oplus \cdots \oplus k \theta_n
-\]
+\ee
 where the $\theta_i$ are formal variables of odd degree, and set
@@
 \ee
+\end{definition}
 
@@
 
-\section{The Clifford thickening}\label{section:cliff_thick}
+\subsection{The Clifford thickening}\label{section:cliff_thick}
 
@@
 
-Thus a $1$-morphism $W \lto V$ in $\cat{L}$ is a finite rank matrix factorisation $X$ of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\gamma_i, \gamma_i^\dagger$ for $1 \le i \le a$ satisfying Clifford relations and the equations (all up to homotopy)
+Thus a $1$-morphism $W \lto V$ in $\cat{L}$ is a finite rank matrix factorisation $X$ of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\gamma_i, \gamma_i^\dagger$ satisfying Clifford relations and the equations (all up to homotopy)
 \begin{gather*}
@@
 \[
-\phi \gamma_i = 0\,, \qquad \rho_j^\dagger \phi = 0\,, \qquad \forall 1 \le i \le a, 1 \le j \le b\,.
+\phi \gamma_i = 0\,, \qquad \rho_j^\dagger \phi = 0\,, \qquad 1 \le i \le a, \quad 1 \le j \le b\,.
 \]
@@
 \begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$.
-
 The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$.
@@
 A simple example of such a connection is given in Section \ref{example:computing_homs}.
-Using a chosen homogeneous basis $\{ e_i \otimes f_j \}_{i,j}$ for $Y \otimes X$ we may extend the operators $\partial_{t_i}$ extend to $k[x,z]$-linear operators
+Using a chosen homogeneous basis $\{ e_a \otimes f_b \}_{a,b}$ for $Y \otimes X$ we may extend the operators $\partial_{t_i}$ extend to $k[x,z]$-linear operators
 \begin{gather*}
 \partial_{t_i}: Y \, \check{\otimes}\, X \lto Y \, \check{\otimes}\, X\\
-e_i \otimes h(y) \otimes f_j \mapsto e_i \otimes \partial_{t_i}( h(y) ) \otimes f_j\,.
+e_a \otimes h(y) \otimes f_b \mapsto e_a \otimes \partial_{t_i}( h(y) ) \otimes f_b\,.
 \end{gather*}
 
-\begin{lemma} The operator $[ d_{Y \otimes X}, \partial_{t_i} ]$ on $Y \, \check{\otimes}\, X$ is $k[t]$-linear and therefore passes to a $k[x,z]$-linear operator on the quotient $Y \l X = \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
-\end{lemma}
+\begin{lemma} For $1 \le i \le m$ the operator
+\be
+[ d_{Y \otimes X}, \partial_{t_i} ] = d_{Y \otimes X} \partial_{t_i} - \partial_{t_i} d_{Y \otimes X}: Y \, \check{\otimes}\, X \lto Y \, \check{\otimes}\, X
+\ee
+is $k[t]$-linear and passes to a $k[x,z]$-linear operator on $Y \l X \cong \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
+\end{lemma}
+\begin{proof}
+The fact that $\nabla$ is a connection over $k[t]$ means that the operators $\partial_{t_i}$ obey the Leibniz rule, that is
+\[
+\partial_{t_i}( t_j h ) = \partial_{t_i}( t_j ) h + t_j \partial_{t_i} h = \delta_{ij} h + t_j \partial_{t_i} h
+\]
+so $[ \partial_{t_i}, t_j ] = \delta_{ij}$. We calculate
+\[
+[[d_{Y \otimes X}, \partial_{t_i}], t_j] = - [[t_j, d_{Y \otimes X}], \partial_{t_i}] - [[\partial_{t_i}, t_j], d_{Y \otimes X}] = - [ \delta_{ij}, d_{Y \otimes X}] = 0
+\]
+which shows that $[d_{Y \otimes X}, \partial_{t_i}]$ is $k[t]$-linear.
+\end{proof}
 
@@
 
-In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.
+% In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.
 
@@
 relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
-Specifically, the generator $C_i^{\dagger}$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
+Specifically, the generator $\gamma_i^{\dagger}$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
 But this operator can be identified with an Atiyah class of the linear factorisation
@@
 
-\begin{remark} There is a question of whether or not the $C_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$ (for example, when we write $\partial_{z_j}(d_X)$ we implicitly choose a basis so as to represent $d_X$ as a matrix and differentiate its entries).
-But Atiyah classes are independent, up to homotopy, of the choice of connection, and the operator $\partial_{z_j}(d_X)$ is similarly independent of the choice of basis (Lemma \ref{lemma:homotopy_indept}).
+\begin{remark} There is a question of whether or not the $C_m$-action on $Y \l X$ is canonical, since it depends on the choice of connection $\nabla$ and on a choice of homogeneous basis for $X$ and $Y$.
+But Atiyah classes are independent, up to homotopy, of the choice of connection.
 \end{remark}
@@
 \begin{equation}\label{eq:larger_object}
-V \otimes_k ( Y \otimes X ) = (Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
-\end{equation}
-where $V$ is the exterior algebra viewed as a $\nZ_2$-graded $k$-module
-\[
-V = \bigwedge( k[1]^{\oplus m} )\,.
+S_m \otimes_k ( Y \otimes X ) = (Y \otimes X) \oplus (Y \otimes X)[1] \oplus (Y \otimes X) \oplus \cdots
+\end{equation}
+where $S_m$ is the exterior algebra viewed as a $\nZ_2$-graded $k$-module
+\[
+S_m = \bigwedge( k[1]^{\oplus m} )\,.
 \]
@@
 \begin{itemize}
-\item[1)] The complex $( V \otimes_k ( Y \otimes X ), d_K )$ has a finite model: there is a homotopy equivalence
+\item[1)] The complex $( S_m \otimes_k ( Y \otimes X ), d_K )$ has a finite model: there is a homotopy equivalence
 \be
-(Y \l X, 0) \cong \big( V \otimes_k ( Y \otimes X ), d_K \big)
+(Y \l X, 0) \cong \big( S_m \otimes_k ( Y \otimes X ), d_K \big)
 \ee
@@
 \be\label{eq:woofeif}
-(Y \l X, d_{Y \otimes X}) \cong \big( V \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big)
+(Y \l X, d_{Y \otimes X}) \cong \big( S_m \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big)
 \ee
@@
 \be\label{eq:woofeif2}
-\big( V \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big) \cong \big( V \otimes_k ( Y \otimes X ), d_{Y \otimes X}\big)\,.
+\big( S_m \otimes_k ( Y \otimes X ), d_K + d_{Y \otimes X}\big) \cong \big( S_m \otimes_k ( Y \otimes X ), d_{Y \otimes X}\big)\,.
 \ee
@@
 \be\label{eq:iso_of_clifford_modelfinite}
-(Y \l X, d_{Y \otimes X}) \cong ( V \otimes_k ( Y \otimes X ), d_{Y \otimes X})\,.
-\ee
-There is a canonical action of the Clifford algebra $C_m$ on $V$ and thus on the right hand side, which ``remembers'' how to extract $Y \otimes X$ from this larger object.
+(Y \l X, d_{Y \otimes X}) \cong ( S_m \otimes_k ( Y \otimes X ), d_{Y \otimes X})\,.
+\ee
+There is a canonical action of the Clifford algebra $C_m$ on $S_m$ and thus on the right hand side, which ``remembers'' how to extract $Y \otimes X$ from this larger object.
 Transferring this action yields the operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ on $Y \l X$ from Section \ref{section:lg_cut_system}.
@@
 
-Let $R$ be a $k$-algebra and $(X,d)$ a complex of $R$-modules on which $t_1,\ldots,t_n \in R$ act null-homotopically.
+Let $R$ be a $k$-algebra and $(X,d)$ a complex of $R$-modules on which $t_1,\ldots,t_m \in R$ act null-homotopically.
 Tensoring $X$ with the Koszul complex $K(t_i)$ yields the same complex as taking the cone of $t_i \cdot 1_X = 0: X \lto X$, and therefore we have a homotopy equivalence
@@
 \ee
-Iterating this operation we obtain a homotopy equivalence with $K = K(t_1,\ldots,t_n)$,
+Iterating this operation we obtain a homotopy equivalence with $K = K(t_1,\ldots,t_m)$,
 \be\label{eq:cliffordactkos_1}
-K \otimes_R X \cong \bigwedge( k[1]^{\oplus n} ) \otimes_k X
+K \otimes_R X \cong \bigwedge( k[1]^{\oplus m} ) \otimes_k X
 \ee
@@
 \be
-C_n = \End_k\left( \bigwedge( k[1]^{\oplus n} ) \right)
-\ee
-and the purpose of this section is to compute the corresponding action of $C_n$ via closed odd endomorphisms of the complex $K \otimes_R X$. In fact we will do this more generally:
+C_m = \End_k\left( \bigwedge( k[1]^{\oplus m} ) \right)
+\ee
+and the purpose of this section is to compute the corresponding action of $C_m$ via closed odd endomorphisms of the complex $K \otimes_R X$. In fact we will do this more generally:
 
 \begin{setup} Let $R$ be a $k$-algebra and write $\otimes$ for $\otimes_R$.
-Let $(X,d)$ be a linear factorisation of $W \in R$ and $t_1,\ldots,t_n$ a sequence of elements of $R$ acting null-homotopically on $X$.
-We choose odd $R$-linear operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$ for $1 \le i \le n$.
+Let $(X,d)$ be a linear factorisation of $W \in R$ and $t_1,\ldots,t_m$ a sequence of elements of $R$ acting null-homotopically on $X$.
+We choose odd $R$-linear operators $\lambda_i$ on $X$ with $[\lambda_i, d] = t_i \cdot 1_X$ for $1 \le i \le m$.
 \end{setup}
@@
 
-We introduce formal variables $\theta_1,\ldots,\theta_n$ of odd degree and set
-\[
-V = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
+We introduce formal variables $\theta_1,\ldots,\theta_m$ of odd degree and set
+\[
+S_m = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
 \]
 On this $\nZ$-graded $k$-module there are canonical odd $k$-linear operators $\theta_i, \theta_i^*$ defined as in Definition \ref{defn:contraction}.
-The Koszul complex $K$ of the sequence $t_1,\ldots,t_n$ is defined by
+The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ is defined by
 \begin{equation}\label{defn:koszul}
-K = V \otimes_k R, \qquad d_K = \sum_{i=1}^n t_i \theta_i^*\,.
-\end{equation} 
-The tensor products $K \otimes X = (K \otimes X, d + d_K)$ and $V \otimes_k X = ( V \otimes_k X, d )$ are both linear factorisation of $W$ with isomorphic underlying graded modules.
-On this underlying graded module $K \otimes X \cong V \otimes_k X$ we have the odd $R$-linear operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$ and we introduce the following even $R$-linear operators
+K = S_m \otimes_k R, \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
+\end{equation} 
+The tensor products $K \otimes X = (K \otimes X, d + d_K)$ and $S_m \otimes_k X = ( S_m \otimes_k X, d )$ are both linear factorisation of $W$ with isomorphic underlying graded modules.
+On this underlying graded module $K \otimes X \cong S_m \otimes_k X$ we have the odd $R$-linear operators $\theta_k^* = \theta_k^* \otimes 1$ and $\theta_k = \theta_k \otimes 1$ and we introduce the following even $R$-linear operators
 \begin{align*}
-\delta &= \sum_{i=1}^n \lambda_i \theta_i^*,\\
-\exp(-\delta) &= \sum_{m \ge 0} (-1)^m \frac{1}{m!} \delta^m\,.
+\delta &= \sum_{i=1}^m \lambda_i \theta_i^*,\\
+\exp(-\delta) &= \sum_{n \ge 0} (-1)^n \frac{1}{n!} \delta^n\,.
 \end{align*}
@@
 \be\label{eq:equivalencekoszul}
-\xymatrix@C+5pc{ K \otimes X\; \ar@<1ex>[r]^-{ \exp(\delta) } & \;V \otimes_k X \ar@<1ex>[l]^-{ \exp(-\delta) } }
+\xymatrix@C+5pc{ K \otimes X\; \ar@<1ex>[r]^-{ \exp(\delta) } & \;S_m \otimes_k X \ar@<1ex>[l]^-{ \exp(-\delta) } }
 \ee
@@
 
-\begin{lemma}\label{lemma:pert1} $[d, \delta^m] = m \delta^{m-1} d_K$ for $m \ge 1$.
-\end{lemma}
-\begin{proof}
-The case of $m = 1$ is clear
+\begin{lemma}\label{lemma:pert1} $[d, \delta^n] = n \delta^{n-1} d_K$ for $n \ge 1$.
+\end{lemma}
+\begin{proof}
+The case of $n = 1$ is clear
 \[
@@
 \]
-For $m > 1$ we use the case $m = 1$ to show that
-\[
-[ d, \delta^m ] = \sum_{i=0}^{m-1} \delta^i [d, \delta] \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i d_K \delta^{m-i-1} = \sum_{i=0}^{m-1} \delta^i \delta^{m-i-1} d_K = m \delta^{m-1} d_K\,.
+For $n > 1$ we use the case $n = 1$ to show that
+\[
+[ d, \delta^n ] = \sum_{i=0}^{n-1} \delta^i [d, \delta] \delta^{n-i-1} = \sum_{i=0}^{n-1} \delta^i d_K \delta^{n-i-1} = \sum_{i=0}^{n-1} \delta^i \delta^{n-i-1} d_K = n \delta^{n-1} d_K\,.
 \]
@@
 \begin{align*}
-[d, \exp(-\delta)] &= \sum_{m \ge 1} \frac{(-1)^m}{m!} [ d, \delta^m ]\\
-&= \sum_{m \ge 1} \frac{(-1)^m}{m!} m \delta^{m-1} d_K\\
-&= - \sum_{m \ge 0} \frac{(-1)^m}{m!} \delta^m d_K\\
+[d, \exp(-\delta)] &= \sum_{n \ge 1} \frac{(-1)^n}{n!} [ d, \delta^n ]\\
+&= \sum_{n \ge 1} \frac{(-1)^n}{n!} n \delta^{n-1} d_K\\
+&= - \sum_{n \ge 0} \frac{(-1)^n}{n!} \delta^n d_K\\
 &= - \exp(-\delta) d_K
@@
 
-\begin{definition}\label{defn:transfer_contract} Let $\gamma$ be a homogeneous $R$-linear operator on $V \otimes_k X$.
+\begin{definition}\label{defn:transfer_contract} Let $\gamma$ be a homogeneous $R$-linear operator on $S_m \otimes_k X$.
 We define the \textsl{transfer} $\cat{T}(\gamma)$ to be the homogeneous $R$-linear operator on $K \otimes X$ induced by $\gamma$ using the equivalence \eqref{eq:equivalencekoszul}, that is,
@@
 
-\begin{definition} The iterated commutator $[a,b]^{(m)}$ is defined by $[a,b]^{(0)} = b$ and
-\[
-[a,b]^{(m+1)} = [a, [a,b]^{(m)}]\,.
-\]
-Observe that $[a,b]^{(m)}$ is a linear function of $b$, but not $a$.
+\begin{definition} The iterated commutator $[a,b]^{(n)}$ is defined by $[a,b]^{(0)} = b$ and
+\[
+[a,b]^{(n+1)} = [a, [a,b]^{(n)}]\,.
+\]
+Observe that $[a,b]^{(n)}$ is a linear function of $b$, but not $a$.
 \end{definition}
 
-\begin{lemma}\label{lemma:woop3} For $m \ge 1$ we have
-\[
-[a,b^m] = \sum_{i=0}^{m-1} (-1)^{i|a||b|} b^i [a,b] b^{m-i-1}\,.
+\begin{lemma}\label{lemma:woop3} For $n \ge 1$ we have
+\[
+[a,b^n] = \sum_{i=0}^{n-1} (-1)^{i|a||b|} b^i [a,b] b^{n-i-1}\,.
 \]
@@
 
-\begin{lemma}\label{lemma:woop4} For $m \ge 1$ we have
+\begin{lemma}\label{lemma:woop4} For $n \ge 1$ we have
 \be
-a^m [a, b] = \sum_{\substack{0 \le i,j \le m \\ i+j=m}} \binom{m}{i} [a,b]^{(i+1)} a^j\,.
-\ee
-\end{lemma}
-\begin{proof}
-By induction, with the case $m = 1$ being clear. Using the inductive hypothesis
-\[
-a^{m+1} [a, b] = \sum_{i+j=m} \binom{m}{i} a [a,b]^{(i+1)} a^j = \sum_{i+j=m} \binom{m}{i} \Big[ [a,b]^{(i+2)} a^j + [a,b]^{(i+1)} a^{j+1} \Big]\,.
-\]
-The powers of $a$ range from $0$ to $m+1$ and the coefficient of $a^j$ for $1 \le j \le m$ is
-\[
-\binom{m}{m-j} [a,b]^{(m-j+2)} + \binom{m}{m-j+1} [a,b]^{(m-j+2)} = \binom{m+1}{m+1-j} [a,b]^{(m-j+2)}\,.
-\]
-The coefficient of $a^0$ is $[a,b]^{(m+2)}$ and the coefficient of $a^{m+1}$ is $[a,b]^{(1)}$, so we are done.
-\end{proof}
-
-\begin{lemma}\label{lemma_iteratedcomm} Let odd elements $a_i, b_i \in A$ be given for $1 \le i \le n$ such that $[a_i, b_j] = 0$ for all $1 \le i,j \le n$ and define
-\[
-D = \sum_{i=1}^n a_i b_i\,.
-\]
-Suppose $[b_i,c] = 0$ for $1 \le i \le n$. Then for $m \ge 0$
+a^n [a, b] = \sum_{\substack{0 \le i,j \le n \\ i+j=n}} \binom{n}{i} [a,b]^{(i+1)} a^j\,.
+\ee
+\end{lemma}
+\begin{proof}
+By induction, with the case $n = 1$ being clear. Using the inductive hypothesis
+\[
+a^{n+1} [a, b] = \sum_{i+j=n} \binom{n}{i} a [a,b]^{(i+1)} a^j = \sum_{i+j=n} \binom{n}{i} \Big[ [a,b]^{(i+2)} a^j + [a,b]^{(i+1)} a^{j+1} \Big]\,.
+\]
+The powers of $a$ range from $0$ to $n+1$ and the coefficient of $a^j$ for $1 \le j \le n$ is
+\[
+\binom{n}{n-j} [a,b]^{(n-j+2)} + \binom{n}{n-j+1} [a,b]^{(n-j+2)} = \binom{n+1}{n+1-j} [a,b]^{(n-j+2)}\,.
+\]
+The coefficient of $a^0$ is $[a,b]^{(n+2)}$ and the coefficient of $a^{n+1}$ is $[a,b]^{(1)}$, so we are done.
+\end{proof}
+
+\begin{lemma}\label{lemma_iteratedcomm} Let odd elements $a_i, b_i \in A$ be given for $1 \le i \le m$ such that $[a_i, b_j] = 0$ for all $1 \le i,j \le m$ and define
+\[
+D = \sum_{i=1}^m a_i b_i\,.
+\]
+Suppose $[b_i,c] = 0$ for $1 \le i \le m$. Then for $n \ge 0$
 \be\label{eq:lemma_iteratedcomm}
-[D, c]^{(m)} = (-1)^{m|c|} \sum_{1 \le q_1,\ldots,q_m \le n} [a_{q_m}, [a_{q_{m-1}}, \ldots, [ a_{q_1}, c] \cdots ]] b_{q_1} \cdots b_{q_m}\,.
-\ee
-\end{lemma}
-\begin{proof}
-For convenience we introduce, for any tuple of indices $\bold{q} = (q_1,\ldots,q_m)$ of integers $1 \le q_i \le n$, the notation
+[D, c]^{(n)} = (-1)^{n|c|} \sum_{1 \le q_1,\ldots,q_n \le m} [a_{q_n}, [a_{q_{n-1}}, \ldots, [ a_{q_1}, c] \cdots ]] b_{q_1} \cdots b_{q_n}\,.
+\ee
+\end{lemma}
+\begin{proof}
+For convenience we introduce, for any tuple of indices $\bold{q} = (q_1,\ldots,q_n)$ of integers $1 \le q_i \le m$, the notation
 \begin{gather}
-\tau_{\bold{q}} = [ a_{q_m}, [ a_{q_{m-1}}, \ldots [ a_{q_1}, c ] \cdots ] \label{defn:tau}\\
-b_{\bold{q}} = b_{q_1} \cdots b_{q_m} \label{defn:bq}\,.
+\tau_{\bold{q}} = [ a_{q_n}, [ a_{q_{n-1}}, \ldots [ a_{q_1}, c ] \cdots ] \label{defn:tau}\\
+b_{\bold{q}} = b_{q_1} \cdots b_{q_n} \label{defn:bq}\,.
 \end{gather}
-For $m = 0$ the right hand side of \eqref{eq:lemma_iteratedcomm} is $c$ by convention, so the statement is trivial. We compute using the inductive hypothesis that
+For $n = 0$ the right hand side of \eqref{eq:lemma_iteratedcomm} is $c$ by convention, so the statement is trivial. We compute using the inductive hypothesis that
 \begin{align*}
-[D, c]^{(m+1)} &= [ D, [D, c]^{(m)} ]\\
-&= \big[D, (-1)^{m|c|} \sum_{\bold{q}} \tau_{\bold{q}} b_{\bold{q}}\big]\\
-&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i [ a_i b_i , \tau_{\bold{q}} b_{\bold{q}}]\\
-&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i \left( a_i b_i \tau_{\bold{q}} b_{\bold{q}} - \tau_{\bold{q}} b_{\bold{q}} a_i b_i \right)\\
-&= (-1)^{m|c|} \sum_{\bold{q}} \sum_i \left( (-1)^{|c|} a_i \tau_{\bold{q}} b_{\bold{q}} b_i - (-1)^m \tau_{\bold{q}} a_i b_{\bold{q}} b_i \right)\\
-&= (-1)^{(m+1)|c|} \sum_{\bold{q}, i} [ a_i, \tau_{\bold{q}} ] b_{\bold{q}} b_i
+[D, c]^{(n+1)} &= [ D, [D, c]^{(n)} ]\\
+&= \big[D, (-1)^{n|c|} \sum_{\bold{q}} \tau_{\bold{q}} b_{\bold{q}}\big]\\
+&= (-1)^{n|c|} \sum_{\bold{q}} \sum_i [ a_i b_i , \tau_{\bold{q}} b_{\bold{q}}]\\
+&= (-1)^{n|c|} \sum_{\bold{q}} \sum_i \left( a_i b_i \tau_{\bold{q}} b_{\bold{q}} - \tau_{\bold{q}} b_{\bold{q}} a_i b_i \right)\\
+&= (-1)^{n|c|} \sum_{\bold{q}} \sum_i \left( (-1)^{|c|} a_i \tau_{\bold{q}} b_{\bold{q}} b_i - (-1)^n \tau_{\bold{q}} a_i b_{\bold{q}} b_i \right)\\
+&= (-1)^{(n+1)|c|} \sum_{\bold{q}, i} [ a_i, \tau_{\bold{q}} ] b_{\bold{q}} b_i
 \end{align*}
@@
 Eventually we are going to substitute $a_i = \lambda_i, b_i = \theta_i^*$ so that $D = \delta$, and we will take further $c = \gamma$.
-In this notation, the aim of all of this is to compute the commutators $[c, D^m]$ and then $[c, \exp(-D)]$.
+In this notation, the aim of all of this is to compute the commutators $[c, D^n]$ and then $[c, \exp(-D)]$.
 Since most of the calculation can be done in $A$, so we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.
 
-\begin{lemma}\label{lemma:commutator_wha} For $m \ge 1$
-\[
-[ c, D^m ] = \sum_{i=0}^{m-1} (-1)^{(i+1)|c| + 1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}\,.
+\begin{lemma}\label{lemma:commutator_wha} For $n \ge 1$
+\[
+[ c, D^n ] = \sum_{i=0}^{n-1} (-1)^{(i+1)|c| + 1} \sum_{i \le p \le n-1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{n-i-1}\,.
 \]
@@
 \begin{equation}\label{eq:catfish}
-[ c, D^m ] = \sum_{p=0}^{m-1} D^p [ c, D ] D^{m-p-1} = -\sum_{p=0}^{m-1} D^p [ c, D ] D^{m-p-1}\,.
+[ c, D^n ] = \sum_{p=0}^{n-1} D^p [ c, D ] D^{n-p-1} = -\sum_{p=0}^{n-1} D^p [ c, D ] D^{n-p-1}\,.
 \end{equation}
@@
 \be
--\sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} [D, c]^{(i+1)} D^{m-p-1+j}
+-\sum_{p=0}^{n-1} \sum_{i+j=p} \binom{p}{i} [D, c]^{(i+1)} D^{n-p-1+j}
 \ee
@@
 \be
-\sum_{p=0}^{m-1} \sum_{i+j=p} \binom{p}{i} (-1)^{(i+1)|c| + 1} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}
+\sum_{p=0}^{n-1} \sum_{i+j=p} \binom{p}{i} (-1)^{(i+1)|c| + 1} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{n-i-1}
 \ee
@@
 \begin{itemize}
-\item Let $a_i, b_i \in A$ be odd elements with $[a_i,b_j] = 0$ for $1 \le i,j \le n$.
-\item Assume that $D = \sum_{i=1}^n a_i b_i$ has finite order, that is, $D^r = 0$ for some $r > 0$.
-\item Let $c \in A$ be an odd element, with $[b_i, c] = 0$ for $1 \le i \le n$.
+\item Let $a_i, b_i \in A$ be odd elements with $[a_i,b_j] = 0$ for $1 \le i,j \le m$.
+\item Assume that $D = \sum_{i=1}^m a_i b_i$ has finite order, that is, $D^r = 0$ for some $r > 0$.
+\item Let $c \in A$ be an odd element, with $[b_i, c] = 0$ for $1 \le i \le m$.
 \end{itemize}
@@
 \be\label{eq:ccommutesexpD}
-[c, \exp(-D)] = - \sum_{m \ge 1} \frac{1}{m!} \sum_{q_1,\ldots,q_m} [ a_{q_m}, [ a_{q_{m-1}}, \ldots [ a_{q_1}, c ] \cdots ] b_{q_1} \cdots b_{q_m} \exp(-D)\,.
+[c, \exp(-D)] = - \sum_{n \ge 1} \frac{1}{n!} \sum_{q_1,\ldots,q_n} [ a_{q_n}, [ a_{q_{n-1}}, \ldots [ a_{q_1}, c ] \cdots ] b_{q_1} \cdots b_{q_n} \exp(-D)\,.
 \ee
@@
 \begin{align*}
-[c, \exp(-D)] &= \sum_{m \ge 0} \frac{(-1)^m}{m!} [c, D^m]\\
-&= \sum_{m \ge 0} \frac{(-1)^{m+i}}{m!} \sum_{i=0}^{m-1} \sum_{i \le p \le m -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{m-i-1}\,.
+[c, \exp(-D)] &= \sum_{n \ge 0} \frac{(-1)^n}{n!} [c, D^n]\\
+&= \sum_{n \ge 0} \frac{(-1)^{n+i}}{n!} \sum_{i=0}^{n-1} \sum_{i \le p \le n -1} \binom{p}{i} \sum_{\bold{q} = (q_1,\ldots,q_{i+1})} \tau_{\bold{q}} b_{\bold{q}} D^{n-i-1}\,.
 \end{align*}
-Rewriting this sum in terms of the variable $t = m - i - 1$ yields
+Rewriting this sum in terms of the variable $t = n - i - 1$ yields
 \[
@@
 \begin{equation}\label{eq:combin}
-\frac{b!}{(a+b+1)!} \sum_{a \le m \le a + b} \binom{m}{a} = \frac{1}{(a+1)!}
+\frac{b!}{(a+b+1)!} \sum_{a \le n \le a + b} \binom{n}{a} = \frac{1}{(a+1)!}
 \end{equation}
@@
 \be\label{eq:transfer_gamma}
-\cat{T}(\gamma) = \gamma + \sum_{m \ge 1} \sum_{q_1,\ldots,q_m}  \frac{1}{m!} [\lambda_{q_m}, [\lambda_{q_{m-1}}, \ldots [ \lambda_{q_1}, \gamma] \cdots ]] \theta^*_{q_1} \ldots \theta^*_{q_m}
-\ee
-is the tranferred operator on $K \otimes X$, where the $q_j$'s range over $1, \ldots, n$.
+\cat{T}(\gamma) = \gamma + \sum_{n \ge 1} \sum_{q_1,\ldots,q_n}  \frac{1}{n!} [\lambda_{q_n}, [\lambda_{q_{n-1}}, \ldots [ \lambda_{q_1}, \gamma] \cdots ]] \theta^*_{q_1} \ldots \theta^*_{q_n}
+\ee
+is the tranferred operator on $K \otimes X$, where the $q_j$'s range over $1, \ldots, m$.
 \end{corollary}
@@
 
-\begin{remark} Observe that since the $\theta_i^*$ square to zero, only sequences of distinct indices $q_1,\ldots,q_m$ contribute in the sum \eqref{eq:transfer_gamma}. The low order terms are
+\begin{remark} Observe that since the $\theta_i^*$ square to zero, only sequences of distinct indices $q_1,\ldots,q_n$ contribute in the sum \eqref{eq:transfer_gamma}. The low order terms are
 \be
@@
 
-Finally, we compute the transfer of the operator $\theta_i$ on $\bigwedge( \oplus_j k \theta_j ) \otimes_k X$:
+Finally, we compute the transfer of the operator $\theta_i$ on $S_m \otimes_k X$:
 
@@
 \begin{equation}\label{eq:psik}
-\cat{T}(\theta_i) = \theta_i - \sum_{m \ge 0} \sum_{q_1,\ldots,q_m} \frac{1}{(m+1)!} [ \lambda_{q_m}, [ \lambda_{q_{m-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_m}^*\,.
+\cat{T}(\theta_i) = \theta_i - \sum_{n \ge 0} \sum_{q_1,\ldots,q_n} \frac{1}{(n+1)!} [ \lambda_{q_n}, [ \lambda_{q_{n-1}}, [ \cdots \big[ \lambda_{q_1}, \lambda_i ] \cdots ] \theta_{q_1}^* \cdots \theta_{q_n}^*\,.
 \end{equation}
@@
 
-\begin{theorem} The closed odd operators $\cat{T}(\theta_i)$ and $\cat{T}(\theta_i^*) = \theta_i^*$ on the linear factorisation $(K \otimes X, d_K + d)$ form a representation of the Clifford algebra $C_n$.
+\begin{theorem} The closed odd operators $\cat{T}(\theta_i)$ and $\cat{T}(\theta_i^*) = \theta_i^*$ on the linear factorisation $(K \otimes X, d_K + d)$ form a representation of the Clifford algebra $C_m$.
 \end{theorem}
 
-By construction, Proposition \ref{prop:equivalencekoszul} is now promoted to an isomorphism of representations of $C_n$, with $\cat{T}(\theta_i), \cat{T}(\theta_i^*)$ acting on $K \otimes X$ and the $\theta_i, \theta_i^*$ acting on $\bigwedge( \oplus_i k\theta_i ) \otimes_k X$.
-
-\begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_n$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_n$.
+By construction, Proposition \ref{prop:equivalencekoszul} is now promoted to an isomorphism of representations of $C_m$, with $\cat{T}(\theta_i), \cat{T}(\theta_i^*)$ acting on $K \otimes X$ and the $\theta_i, \theta_i^*$ acting on $S_m \otimes_k X$.
+
+\begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_m$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_m$.
 An explicit isomorphism can be written down using the techniques developed in this Section.
@@
 
-\begin{remark}\label{remark:cancellations_transfer} Suppose for each pair $1 \le i,j \le n$ that up to homotopy
+\begin{remark}\label{remark:cancellations_transfer} Suppose for each pair $1 \le i,j \le m$ that up to homotopy
 \be
@@
 \[
-V = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
+S_m = \bigwedge\left( k \theta_1 \oplus \cdots \oplus k \theta_m \right)\,.
 \]
@@
 \begin{equation}\label{defn:koszul}
-K = V \otimes_k k[y], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
+K = S_m \otimes_k k[y], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
 \end{equation}
@@
 \[
-( K \otimes_{k[y]} ( Y \otimes X ), d_K ) = ( V \otimes_k ( Y \otimes X ), d_K )\,.
+( K \otimes_{k[y]} ( Y \otimes X ), d_K ) = ( S_m \otimes_k ( Y \otimes X ), d_K )\,.
 \]
@@
 \begin{equation}\label{eq:iso_larger_object}
-\xymatrix@C+3pc{ \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \otimes X, d_K + d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{ \exp(\delta) } & \big( V \otimes_k Y \,\check{\otimes}\, X, d_{Y \otimes X} \big)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
+\xymatrix@C+3pc{ \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \otimes X, d_K + d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{ \exp(\delta) } & \big( S_m \otimes_k Y \,\check{\otimes}\, X, d_{Y \otimes X} \big)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
 \end{equation}
@@
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & V \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
+Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
 }\,.
@@
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & V \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
 }
@@
 
-The canonical action of $C_m$ on the spinor representation $V$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $V \otimes_k ( Y \otimes X )$.
+The canonical action of $C_m$ on the spinor representation $S_m$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $S_m \otimes_k ( Y \otimes X )$.
 In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$, and it remains to show that these two actions are compatible.
@@
 We prove that $\gamma_i \simeq \Phi \theta_i \Phi^{-1}$ and $\gamma_i^\dagger \simeq \Phi \theta_i^* \Phi^{-1}$.
-With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $V \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
+With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $S_m \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
 \[
@@
 \xymatrix@C+4pc@R+1pc{
-Y \l X \ar[d]_-{\psi \l \phi} & V \otimes_k ( Y \otimes X )\ar[l]_-{\Phi} \ar[d]^-{\psi \otimes \phi}\\
-Y' \l X' & V \otimes_k ( Y' \otimes X' )\ar[l]^-{\Phi}
+Y \l X \ar[d]_-{\psi \l \phi} & S_m \otimes_k ( Y \otimes X )\ar[l]_-{\Phi} \ar[d]^-{\psi \otimes \phi}\\
+Y' \l X' & S_m \otimes_k ( Y' \otimes X' )\ar[l]^-{\Phi}
 }
@@
 
-This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $V \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object.
-It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $V \otimes_k( Y \otimes X )$.
+This achieves our aim: we took direct sums of copies of $Y \otimes X$ to form $S_m \otimes_k( Y \otimes X )$ and then used perturbation to find a finite model of this latter object.
+It is worth noting that, in the language of splitting homotopies, the cut $Y \l X$ is the solution of a fixed point problem formulated in terms of linear operators on the initial data $S_m \otimes_k( Y \otimes X )$.
 
@@
 \[
-\Phi: V \otimes_k (Y \otimes X) \lto Y \l X
+\Phi: S_m \otimes_k (Y \otimes X) \lto Y \l X
 \]
 is straightforward to compute.
-Firstly, since $\Phi = \pi \exp(-\delta) \varepsilon$ and the operator $\delta = \sum_i \lambda_i \theta_i^*$ annihilates the identity of the exterior algebra $1 \in V$, the composite
+Firstly, since $\Phi = \pi \exp(-\delta) \varepsilon$ and the operator $\delta = \sum_i \lambda_i \theta_i^*$ annihilates the identity of the exterior algebra $1 \in S_m$, the composite
 \be
 \xymatrix@C+2pc{
-( k \cdot 1 ) \otimes_k ( Y \otimes X ) \ar[r]^-{\operatorname{inc}} & V \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
+( k \cdot 1 ) \otimes_k ( Y \otimes X ) \ar[r]^-{\operatorname{inc}} & S_m \otimes_k ( Y \otimes X ) \ar[r]^-{\Phi} & Y \l X
 }
@@
 
-The functor $F$ is defined by choosing\footnote{One can avoid invoking the axiom of choice here by defining the splitting using homotopy colimits, see \cite{??}}, for each object $(X,e)$ a (possibly infinite rank) matrix factorisation $F(X,e)$ which splits the idempotent $e$.
+The functor $F$ is defined by choosing for each object $(X,e)$ a (possibly infinite rank) matrix factorisation $F(X,e)$ which splits the idempotent $e$.
 That is, such that there are morphisms in the homotopy category
@@
 \]
-represents projection onto $k \cdot 1$ in $V$.
+represents projection onto $k \cdot 1$ in $S_m$.
 Since \eqref{eq:final_finite_modelagain} is an isomorphism of $C_m$-representations the idempotent $e_m$ acting on $Y \l X$ must split to the same thing as the idempotent $e_m$ acting on the right hand side, which obviously splits to $Y \otimes X$.
@@
 where $\bar{X} = X \otimes_R J_V, \bar{Y} = Y \otimes_R J_V$.
-This is a complex of finite-rank $\mathbb{Z}_2$-graded free $k$-modules, and there is an $C_m$-linear homotopy equivalence (Theorem \ref{theorem:htpy_equivalence_main})
-\[
-\Phi: S_m \otimes_k \Hom_R(Y,X) \lto \Hom_{J_V}( \bar{Y}, \bar{X} )\,.
-\]
-Set $H = \Hom_{J_V}( \bar{Y}, \bar{X} )$ and define
-\[
-B = \im( d^1_H: H^1 \lto H^0 )\,.
-\]
-As a matrix of scalars $d^1_H$ may be computed from the differentials $d_X, d_Y$ by inflation, as described in Remark \ref{remark:inflation}.
+There is by Theorem \ref{theorem:htpy_equivalence_main} a $C_m$-linear isomorphism in the homotopy category of $\mathbb{Z}_2$-graded complexes of free $k$-modules
+\be
+\Phi: S_m \otimes_k \Hom_R(Y,X) \lto Y^{\vee} \l X\,.
+\ee
+%Set $H = \Hom_{J_V}( \bar{Y}, \bar{X} )$ and define
+%\[
+%B = \im( d^1_H: H^1 \lto H^0 )\,.
+%\]
+%As a matrix of scalars $d^1_H$ may be computed from the differentials $d_X, d_Y$ by inflation, as described in Remark \ref{remark:inflation}.
 Let $\psi: Y \lto X$ be a morphism of matrix factorisations.
@@
 Let us now compute the cut $Y^{\vee} \l X$, according to Definition \ref{defn:cliffordaction_cut}. With
-\[
+\be\label{eq:examplecut_basis2}
 J_V = k[y]/y^{N-1} = k \cdot 1 \oplus k \cdot y \oplus \cdots k \cdot y^{N-2}
-\]
+\ee
 the matrix of multiplication by $y$ on $J_V$ is $[y] = \begin{pmatrix} 0 & 0\\ I_{N-2} & 0 \end{pmatrix}$. The differential on
-\[
-Y^{\vee} \l X = \Hom_{J_V}( \bar{Y}, \bar{X} ) = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
-\]
+\be\label{eq:examplecut_basis}
+Y^{\vee} \l X = J_V \theta \theta^* \oplus J_V \theta^* \theta \oplus J_V\theta \oplus J_V \theta^*
+\ee
 is then obtained from \eqref{eq:differential_hom} by replacing every $y$ by the matrix $[y]$.
 
-The Clifford algebra $C_1$ acts by generators $\gamma, \gamma^\dagger$.
-To determine their matrices, note that with $t = \partial_y(V) = N y^{N-1}$, $k[y]$ is a free $k[t]$-module with basis $1, \ldots, y^{N-2}$.
+The Clifford algebra $C_1$ acts on $Y^{\vee} \l X$ by generators $\gamma, \gamma^\dagger$.
+To determine their matrices in the basis determined by \eqref{eq:examplecut_basis2} and \eqref{eq:examplecut_basis}, note that with $t = \partial_y(V) = N y^{N-1}$, $k[y]$ is a free $k[t]$-module with basis $1, \ldots, y^{N-2}$.
 Given a polynomial $f(y)$ we may uniquely write it as $f(y) = \sum_{l = 0}^{N-2} f_l \cdot y^l$ with $f_l \in k[t]$.
@@
 \[
-\partial_t: k[y] \lto k[y], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) y^l \,.
-\]
-Notice that for $0 \le q \le N - 1$, $\partial_t(y^q) = \frac{1}{N} \delta_{q (N-1)} \cdot 1$.
-
-The Atiyah class is the $k[t]$-linear operator $\At = [d_{\Hom}, \partial_t]$ on $\Hom_R(Y,X)$. We may compute it for example on generators by
-\[
-\At( \theta \theta^* ) = \partial_t d_{\Hom}( \theta \theta^* ) = - \partial_t( y^i ) \theta + \partial_t( y^{N-j} ) \theta^* = - \frac{1}{N}\delta_{i (N-1)} \theta + \frac{1}{N}\delta_{(N-j)(N-1)} \theta^*\,.
-\]
-The Atiyah class passes to a $k$-linear operator $\gamma^\dagger$ on $Y^{\vee} \l X$ with matrix ($I$ denotes $I_{N-1}$)
+\partial_t: k[y] \lto k[y], \qquad \partial_t(f) = \sum_{l = 0}^{N-2} \frac{\partial}{\partial t}( f_l ) y^l
+\]
+where $\frac{\partial}{\partial t}$ is the usual operator on $k[t]$. For $q < N - 1$ we have $\partial_t(y^q) = 0$ and $\partial_t(y^{N-1+q}) = \frac{1}{N} y^q$, so the $k$-linear operator
+\[
+R_a: J_V \lto J_V \,, \qquad y^q \mapsto \partial_t( y^{a+q} )
+\]
+has the following block form for $0 \le a \le N - 2$
+\[
+[R_a] = \frac{1}{N} \begin{pmatrix} 0 & I_{a} \\ 0 & 0 \end{pmatrix}\,.
+\]
+The Atiyah class is the operator $\At = [d_{\Hom}, \partial_t] = d_{\Hom} \partial_t - \partial_t d_{\Hom}$. For example,
+\begin{align*}
+\At( y^q \theta \theta^* ) &= - \partial_t d_{\Hom}( y^q \theta \theta^* ) = \partial_t( y^{i+q} ) \theta - \partial_t( y^{N-j+q} ) \theta^*\,.
+\end{align*}
+The matrix of the Atiyah class as an operator $\gamma^\dagger$ on $Y^{\vee} \l X$ is therefore
 \begin{equation}\label{eq:aityah_class_hom_example}
-\gamma^\dagger = \frac{1}{N} \begin{pmatrix} 0 & 0 & \delta_{i1} \cdot I & \delta_{j(N-1)} \cdot I \\ 
-0 & 0 & \delta_{j1} \cdot I & \delta_{i(N-1)} \cdot I \\
-- \delta_{i(N-1)} \cdot I & \delta_{j(N-1)} \cdot I & 0 & 0 \\
-\delta_{j1} \cdot I & - \delta_{i1} \cdot I & 0 & 0 \end{pmatrix}\,.
-\end{equation}
-Similarly the matrix of $\partial_{y}(d_X) = j y^{j-1} \theta + (N-j) y^{N-j-1} \theta^*$ on $Y^{\vee} \l X$ is
+\gamma^\dagger = \begin{pmatrix} 0 & 0 & -[R_{N-i}] & -[R_{j}] \\ 
+0 & 0 & -[R_{N-j}] & -[R_{i}] \\
+[R_i] & -[R_j] & 0 & 0 \\
+-[R_{N-j}] & [R_{N-i}] & 0 & 0 \end{pmatrix}\,.
+\end{equation}
+Whereas the matrix of $\partial_{y}(d_X) = j y^{j-1} \theta + (N-j) y^{N-j-1} \theta^*$ on $Y^{\vee} \l X$ is
 \[
@@
 which completes the description of the cut $( Y^{\vee} \l X, \{ \gamma, \gamma^\dagger \} )$.
-Splittng the idempotent $\gamma^\dagger \gamma$ on $Y^{\vee} \l X$ yields a finite model for $\Hom_R(Y,X)$.
+%Splittng the idempotent $\gamma^\dagger \gamma$ on $Y^{\vee} \l X$ yields a finite model for $\Hom_R(Y,X)$.
 \end{example}
@@
 
+\bibitem{runkel}
+I.~Runkel and R.~Suszek, \textsl{Gerbe-holonomy for surfaces with defect networks} Advances in Theoretical and Mathematical Physics 13.4 (2009): 1137--1219, \href{http://arxiv.org/abs/0808.1419}{[arXiv:0808.1419]}.
+
 \bibitem{vistoli}

### 2015-11-04 cutsystems-new.tex
Various.

@@
 
-\title{Computing with cut systems +}
+\title{Computing with cut systems}
 \author{Daniel Murfet}
@@
 The bicategory $\LG$ of Landau-Ginzburg models has polynomials as objects and matrix factorisations as $1$-morphisms.
-The composition of $1$-morphisms in this bicategory naturally produces infinite rank matrix factorisations, which is a nuisance.
+The composition of $1$-morphisms naturally produces infinite rank matrix factorisations, which is a nuisance.
 In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
@@
 The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
-In Section \ref{section:lg_cut_system} we define $\cat{L}$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$.
+In Section \ref{section:lg_cut_system} we define $\cat{L}$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$ as a superbicategory without units.
+We do not consider unit $1$-morphisms here because $\cat{L}$ does not make working with units any simpler.
 
@@
 We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$.
-Namely, it is a consequence of the way the defect conditions $X,Y,Z,Q$ enter the partition function (see for example \cite[(3.16)]{laz}) that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining the defect conditions.
+Namely, it is a consequence of the way the defect conditions $X,Y,Z,Q$ enter the partition function (see for example \cite[(3.16)]{laz}) that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining the defect conditions (TODO of course not).
+
 To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme parametrising possible defect conditions and $\mathcal{Z}(M)$ as a morphism of these vector bundles.
@@
 From what we have said, it is clear that this is essentially a question of the geometry of $\mathscr{M}(W,V)$.
+
+TODO: discuss $A_\infty$ algebras.
+If we want to understand how minimal models vary with the coefficients, and where the jumps occur, we need an intermediate finite object over blah since minimal models only work well over a field.
 
@@
 
-For background on bicategories see \cite{bor94} and the references in \cite{lgdual}.
+For background on bicategories see \cite{bor94, benabou, gray, kellystreet, lack}.
 We follow the notation of \cite{lgdual}, so that lower case letters $a,b, \ldots$ denote objects of a bicategory, while upper case letters $X,Y, \ldots$ and greek letters $\alpha, \beta, \ldots$ respectively denote $1$-morphisms and $2$-morphisms.
@@
 
-\begin{definition} Given two superbicategories $\cat{B}, \cat{C}$ a \emph{lax superfunctor} $\Phi: \cat{B} \lto \cat{C}$ is a lax functor together with, for each object $a$ in $\cat{B}$, a $2$-morphism
+\begin{definition}\label{defn:laxsuperfunctor} Given two superbicategories $\cat{B}, \cat{C}$ a \emph{lax superfunctor} $\Phi: \cat{B} \lto \cat{C}$ is a lax functor together with, for each object $a$ in $\cat{B}$, a $2$-morphism
 \[
@@
 
-We prove that the cut functor defined in Section \ref{section:lg_cut_system} models composition in $\LG$ by providing an equivalence of this bicategory with $\cat{L}$.
+We prove that the cut functor defined in Section \ref{section:lg_cut_system} models composition in $\LG$ by providing an equivalence of this superbicategory with $\cat{L}$.
 This is done by presenting the cut $Y \l X$ with its Clifford action as the solution of the problem of finding a finite model for the matrix factorisation $Y \otimes X$ over $k[x,z]$.
@@
 \xymatrix@C+2pc{
-C \ar@<-1ex>[r]_\nabla & Q, \ar@<-1ex>[l]_f
+C \ar@<-1ex>[r]_\sigma & Q, \ar@<-1ex>[l]_\pi
 } \quad \phi
 \end{equation}
-and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $f \nabla = 1_C, \nabla f = 1_Q - [d_Q, \phi]$ so that $f, \nabla$ are mutually inverse homotopy equivalences.
+and a degree $-1$ operator $\phi: Q \lto Q$ satisfying $\pi \sigma = 1_C, \sigma \pi = 1_Q - [d_Q, \phi]$ so that $\pi, \sigma$ are mutually inverse homotopy equivalences.
 A deformation retract is \emph{strong} if it satisfies some additional conditions, listed below.
@@
 \xymatrix@C+2pc@R+1pc{
-0 \ar[d] \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar[d]^-{x}\\
-k \ar@<-1ex>[r]_-{\nabla} & k[x] \ar@<-1ex>[l]_-{f} \ar@/_3pc/@{.>}[u]_-{\phi}
+0 \ar[d] \ar@<-1ex>[r] & k[x] \ar@<-1ex>[l] \ar[d]^-{x}\\
+k \ar@<-1ex>[r]_-{\sigma} & k[x] \ar@<-1ex>[l]_-{\pi} \ar@/_3pc/@{.>}[u]_-{\phi}
 }
@@
 in which the first column is the complex $C$ which has $k$ concentrated in degree zero, and the second column $Q$ is the Koszul complex on $x$.
-The map $f: k[x] \lto k$ sends every polynomial to its constant term, while $\nabla: k \lto k[x]$ is the inclusion of the constants.
+The map $\pi: k[x] \lto k$ sends every polynomial to its constant term, while $\sigma: k \lto k[x]$ is the inclusion of the constants.
 The operator $\phi$ is defined by $\phi( x^n ) = x^{n-1}$ and $\phi(1) = 0$.
@@
 \xymatrix@C+2pc{
-(M,d) \ar@<-1ex>[r]_\nabla & (A,d), \ar@<-1ex>[l]_f
+(M,d) \ar@<-1ex>[r]_\sigma & (A,d), \ar@<-1ex>[l]_\pi
 } \quad \phi
@@
 \begin{itemize}
-\item[(i)] $f \nabla = 1_M$,
-\item[(ii)] $\nabla f = 1_A - [d, \phi]$,
+\item[(i)] $\pi \sigma = 1_M$,
+\item[(ii)] $\sigma \pi = 1_A - [d, \phi]$,
 \item[(iii)] $\phi^2 = 0$,
-\item[(iv)] $\phi \nabla = 0$,
-\item[(v)] $f \phi = 0$.
+\item[(iv)] $\phi \sigma = 0$,
+\item[(v)] $\pi \phi = 0$.
 \end{itemize}
@@
 \xymatrix@C+2pc{
-(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\nabla & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_f\\
-(M',d') \ar@<-1ex>[r]_{\nabla'} & (A',d') \ar@<-1ex>[l]_{f'}
+(M,d) \ar[d]_{\alpha} \ar@<-1ex>[r]_\sigma & (A,d)\ar[d]^\beta \ar@<-1ex>[l]_\pi\\
+(M',d') \ar@<-1ex>[r]_{\sigma'} & (A',d') \ar@<-1ex>[l]_{\pi'}
 }
 \]
-that is, a pair of morphisms $\alpha, \beta$ such that $\beta \nabla = \nabla' \alpha$, $\alpha f = f' \beta$ and $\phi' \beta = \beta \phi$.
+that is, a pair of morphisms $\alpha, \beta$ such that $\beta \sigma = \sigma' \alpha$, $\alpha \pi = \pi' \beta$ and $\phi' \beta = \beta \phi$.
 \end{definition}
@@
 Given a strong deformation retract \eqref{eq:defn_sdr} the data $(A, \phi)$ is a splitting homotopy.
-In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $\pi = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(\phi)$ with the associated projection $f$ and inclusion $\nabla$.
+In the reverse direction, if $(A, \phi)$ is a splitting homotopy then $e = 1_A - [d, \phi]$ is idempotent and we define the linear factorisation $M = \operatorname{im}(e)$ with the associated projection $\pi$ and inclusion $\sigma$.
 Then this is a strong deformation retract, together with the original $\phi$.
@@
 
-\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(\pi) \cong \im(\pi')$ as graded $R$-modules, where $\pi = 1_A - [d, \phi]$ and $\pi' = 1_A - [d + \tau, \phi']$.
+\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(e) \cong \im(e')$ as graded $R$-modules, where $e = 1_A - [d, \phi]$ and $e' = 1_A - [d + \tau, \phi']$.
 \end{definition}
@@
 \]
-among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(\pi)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
+among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(e)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
 \[
@@
 \begin{proof}
-The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations (see comments in blah).
+The proof for complexes \cite[p.886]{barneslambe} goes through unchanged for linear factorisations, with some minor modifications that are elaborated in \cite[\S 2.5]{lgdual}.
 \end{proof}
@@
 \xymatrix@C+2pc{
-(M,d_\infty) \ar@<-1ex>[r]_{\nabla_\infty} & (A, \xi), \ar@<-1ex>[l]_{f_\infty}
+(M,d_\infty) \ar@<-1ex>[r]_{\sigma_\infty} & (A, \xi), \ar@<-1ex>[l]_{\pi_\infty}
 } \quad \phi_\infty
@@
 \begin{align*}
-\nabla_\infty &= \nabla - \phi A \nabla,\\
-f_\infty &= f - f A \phi,\\
-d_\infty &= d + f A \nabla\,.
+\sigma_\infty &= \sigma - \phi A \sigma,\\
+\pi_\infty &= \pi - \pi A \phi,\\
+d_\infty &= d + \pi A \sigma\,.
 \end{align*}
@@
 \[
-\im(1 - [\xi, \phi_\infty]) \cong \im(\pi) = M
-\]
-be identified with $M$, and the induced maps are the $\nabla_\infty, f_\infty, d_\infty$ given above.
+\im(1 - [\xi, \phi_\infty]) \cong \im(e) = M
+\]
+be identified with $M$, and the induced maps are the $\sigma_\infty, \pi_\infty, d_\infty$ given above.
 It is also possible to give a direct proof as in \cite{crainic}.
-To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one just studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.
+%To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.
 
@@
 \[
-\check{K} := K \otimes_{k[y]} k\llbracket y \rrbracket \cong k\llbracket y \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}
+\check{K} := K \otimes_{k[y]} k\llbracket y \rrbracket \cong \Omega^*_{k[t]/k} \otimes_{k[t]} k\llbracket y \rrbracket 
 \]
 so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $\check{K}$.
-It is straightforward to check that $[d_K, \nabla]$ is invertible on the graded submodule $\check{K}_{\le -1}$ of nonzero degree terms, and we define
+It is straightforward to check (see \cite[Lemma 8.7]{dm1102.2957}) that $[d_K, \nabla]$ is invertible on the graded submodule $\check{K}_{\le -1}$ of negative degree terms (in the usual $\nZ$-grading on the Koszul complex) and we define
 \[
@@
 \begin{proof}
-Recall that, with $t_i = \partial_{z_i} V$, we have by \cite[Section 10]{dm1102.2957}
+This is implicit in \cite[Section 10]{dm1102.2957}.
+The formula $\sigma_\infty = \sum_{m \ge 0} (-1)^m(H d_{Y \otimes X})^m \sigma$ is given there, and with $t_i = \partial_{z_i} V$ the calculation that takes place in \cite[(10.3)]{dm1102.2957} yields
 \begin{equation}\label{eq:atiyah_formula_sigma}
@@
 
-\begin{theorem} $\cat{Z}: \LG \lto \cat{L}$ is an equivalence of superbicategories without units.
+\begin{definition} A \emph{strong superfunctor} $F: \cat{C} \lto \cat{D}$ between superbicategories without units is a strong superfunctor in the sense of Definition \ref{defn:laxsuperfunctor}, but without the data related to units.
+We say further that $F$ is an \emph{equivalence} if
+\begin{itemize}
+\item for all $a,b \in \cat{C}$, $F_{a,b}: \cat{C}(a,b) \lto \cat{D}(Fa, Fb)$ is an equivalence of categories, and
+\item for all $d \in \cat{D}$ there exists $a \in \cat{C}$ with $Fa \cong c$ in the sense that there are $1$-morphisms $f: Fa \lto c$ and $g: c \lto Fa$ with $fg \cong 1$ and $gf \cong 1$.
+\end{itemize}
+\end{definition}
+
+\begin{theorem} There is an equivalence $\cat{Z}: \LG \lto \cat{L}$ of superbicategories without units.
 \end{theorem}
 \begin{proof}
-The only real content here is to produce a $2$-isomorphism
+We define $\mathcal{Z}$ to be the identity on objects and $\mathcal{Z}_{W,V}$ on $1$- and $2$-morphisms. The only remaining content is to produce a $2$-isomorphism
 \be\label{eq:superfuncvarphi}
@@
 \end{proof}
+
+\begin{remark} Obviously the $1$-morphisms $\Delta_W: W \lto W$ which are the units in $\LG$ are, by virtue of the equivalence $\mathcal{Z}$, also units in $\cat{L}$, so that this is an honest bicategory and $\mathcal{Z}$ an equivalence of bicategories.
+The reason we do not begin with units in $\cat{L}$ is that the unitors are no simpler in $\cat{L}$ than $\LG$, so there is no real point to introducing them.
+\end{remark}
 
@@
 
+\bibitem{benabou}
+J.~B\'{e}nabou, \textsl{Introduction to bicategories}, Reports of the Midwest Category Seminar, Springer, 1967.
+
 \bibitem{bor94}
@@
 
+\bibitem{gray}
+J.~W.~Gray, \textsl{Formal category theory: adjointness for 2-categories}, Springer, Berlin, 1974.
+
 %\bibitem{girard_llogic}
@@
 
+\bibitem{kellystreet}
+G.~M.~Kelly and R.~Street, \textsl{Review of the elements of 2-categories}, In Category Seminar (Proc.
+Sem., Sydney, 1972/1973), pages 75--103, Lecture Notes in Math., Vol.
+420, Springer, Berlin, 1974.
+
 \bibitem{kr0401268}
@@
 
+\bibitem{lack}
+S.~Lack, \textsl{A $2$-categories companion}, 
+Towards Higher Categories, 
+The IMA Volumes in Mathematics and its Applications \textbf{152} (2010), 105--191, 
+\href{http://arxiv.org/abs/math/0702535}{[math/0702535]}.
+
 \bibitem{laz}

### 2015-12-14 cutsystems-new.tex
Prior to changing Atiyahs to annihilation.

@@
 \def\nC{\mathds{C}}
+\def\L{\mathcal{C}}
+\def\ferm{\gamma}
+\def\fermc{\gamma^\dagger}
 \DeclareMathOperator{\Ext}{Ext}
@@
 The composition of $1$-morphisms naturally produces infinite rank matrix factorisations, which is a nuisance.
-In this paper we define a bicategory $\cat{L}$ which is equivalent to $\LG$ but for which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
+In this paper we define a bicategory $\L$ which is equivalent to $\LG$ but for which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
 \end{abstract}
@@
 \section{Introduction}
-
-The bicategory of Landau-Ginzburg models $\LG$ has polynomials $W(x)$ called \textsl{potentials} as its objects (typically, the defining equation of an isolated singularity) and the $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
-This bicategory plays an important role in topological field theory \cite{McNameethesis,lgdual,genorb} and the study of homological knot invariants \cite{kr0401268}.
-In \cite{lgdual} it was shown that $\LG$ is a pivotal bicategory with adjoints, and closed formulas were given for the units and counits of adjunction.
-In this paper and its sequel we study an enrichment of $\LG$ which we refer to as a \emph{cut system}.
+% In the functorial approach to two-dimensional topological field theory with defects \cite{??,??} the data of the field theory is encoded as a bicategory with additional structure, including adjoints for all its $1$-morphisms.
+In the example of topological sigma models the associated bicategory has smooth projective varieties as objects and Fourier-Mukai kernels as $1$-morphisms \cite{??} while for topological Landau-Ginzburg models the associated bicategory $\LG$ has
+
+The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, as can be seen by its important role in topological field theory \cite{McNameethesis,lgdual,genorb} homological knot invariants \cite{kr0401268} and $2$-representations of quantum groups \cite{??}, but the definition is still relatively elementary.
+This makes $\LG$ an attractive algebraic object of study, but for one major wrinkle: the composition operation for $1$-morphisms is infinitary.
+
+The objects of $\LG$ are potentials $W(x)$, while $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
+Such a matrix factorisation is a $\nZ_2$-graded free $\nC[x,y]$-module $X = X^0 \oplus X^1$ together with an odd operator $d_X$ satisfying $d_X^2 = (V(y) - W(x)) \cdot 1_X$.
+For a third potential $U(z)$, the composition of $1$-morphisms is a functor
+\begin{gather*}
+\LG(V,U) \times \LG(W,V) \lto \LG(W,U)\,,\\
+(Y , X) \mapsto Y \circ X
+\end{gather*}
+% In this paper and its sequel we study an enrichment of $\LG$ which we refer to as a \emph{cut system}.
+defined for matrix factorisations $Y$ of $V - U$ and $X$ of $W - V$ by
+\be
+Y \circ X = \big( Y \otimes_{\nC[y]} X, d_Y \otimes 1 + 1 \otimes d_X \big)\,.
+\ee
+This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$ which is only homotopy equivalent (that is, isomorphic in the homotopy category) to a finite rank matrix factorisation.
+While this finite model can be proven abstractly to exist, there is no obvious way to describe it as a function of the input data $Y,X$ viewed as matrices of polynomials.
+This need to deal throughout with infinite rank matrix factorisations introduces a certain minimal level of complexity into the theory, which for many applications is undesirable.
+
+Together with Dyckerhoff we initiated in \cite{dm1102.2957} the study of these finite models in terms of homological perturbation and Atiyah classes, and in the present paper this program reaches its logical conclusion.
+We introduce a bicategory $\L$ in which the objects are again potentials and where the $1$-morphisms are finite rank matrix factorisations equipped with the structure of a representation of a Clifford algebra.
+We will prove that this bicategory is equivalent to $\LG$, but is much simpler - in particular, it has a composition operation which is described by a finite number of polynomial functions of the input data.
+
+More precisely: the composition of $1$-morphisms in $\L$ is a functor
+\begin{gather}
+\L(V,U) \times \L(W,V) \lto \L(W,U)\,,\\
+(Y,X) \mapsto Y \l X
+\end{gather}
+which we call the \emph{cut operation}.
+The definition of the cut is very simple.
+With $J_V = \nC[y]/(\partial V)$ the Jacobi algebra of $\nC$ (which is a finite-dimensional $\nC$-vector space by the assumption that $V(y)$ is a potential) the cut of $Y$ and $X$ is a finite rank matrix factorisation
+\be
+Y \l X = Y \otimes_{\nC[y]} J_V \otimes_{\nC[y]} X = ( Y \otimes_{\nC[y]} X ) / (\partial V) (Y \otimes_{\nC[y]} X )
+\ee
+over $\nC[x,z]$
+
+equipped with odd operators $\ferm_i, \fermc_i$ satisfying Clifford relations
+\begin{gather*}
+\ferm_i e = \ferm_i = e \ferm_i\,, \\
+\fermc_i e = \fermc_i = e \fermc_i\,.
+\end{gather*}
+up to homotopy (see Theorem \ref{theorem:cut_is_rep}).
+The differential on $Y \l X$ is induced from the differential on $Y \otimes X$ and can be written explicitly as a matrix over $\nC[x,z]$ in terms of the polynomial entries of $d_Y, d_X$.
+The Clifford action and the matrices which define the Clifford actions on $Y,X$.
+In particular, infinite rank matrix factorisations are never involved.
+In the remainder of the introduction we sketch how the cut operation arises from homological perturbation, why Clifford algebras are involved, where the equivalence $\L \cong \LG$ comes from, and our motivations for pursuing this ``finite model'' $\L$ of $\LG$.
+%In this sense the bicategory $\L$, which we prove is equivalent to $\LG$, provides a ``finite model'' of $\LG$.
+This has various applications, which we will describe later in the introduction.
+
+The main theorem (Theorem \ref{theorem:htpy_equivalence_main}) says
+\begin{equation}\label{eq:final_finite_model}
+\xymatrix@C+4pc{
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
+}
+\end{equation}
+The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
+In Section \ref{section:lg_cut_system} we define $\L$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$ as a superbicategory without units.
+We do not consider unit $1$-morphisms here because $\L$ does not make working with units any simpler.
+
+\subsection{$A_\infty$-algebras and minimal models}
+
+The relationship between $\LG$ and $\L$ is similar to the relationship between a DG-algebra and its $A_\infty$-minimal model.
+Given a DG algebra $A$ over a field $k$, which is infinite-dimensional but has finite-dimensional cohomology, the $A_\infty$-minimal model is an $A_\infty$-structure on the cohomology $H^*(A)$ which is $A_\infty$-quasi-isomorphic to $A$.
+The tradeoff being made is that $A$ is infinite-dimensional but with a simple structure (i.e.
+one multiplication map $m_2$) while $H^*(A)$ is finite-dimensional but with possibly an infinite family of higher multiplications.
+In $\LG$ the composition operation is not described by a finite amount of data, and the price that one pays by going to $\L$ where this is the case, is that the composition has additional structure (a Clifford action).
+There is a more precise link to $A_\infty$-minimal models.
+A special case of the equivalence between $\L$ and $\LG$ gives, for a matrix factorisation $X$ of the potential $W(x_1,\ldots,x_m)$ viewed, a strong deformation retract
+\be
+\Phi: S_m \otimes_k \Hom_R(X,X) \lto X^{\vee} \l X\,.
+\ee
+where $S_m = \bigwedge( k \theta_1 \oplus \cdots \oplus k \theta_m )$ is an exterior algbera, $\Hom_R(X,X)$ is the Hom complex.
+This deformation retract can be used as the input data for the usual construction of an $A_\infty$-minimal on the left hand side, viewed as a DG-algebra.
+
+\subsection{A geometric enrichment of $\LG$}
 
@@
 is an equivalence of categories.
-
 If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise the possible matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$ whose coordinates are the coefficients of the various monomials in each row and column of $D$.
@@
 \end{equation}
-For various applications, two of which we sketch below, we would like to know that the basic operations of the bicategory $\LG$ respect this additional scheme structure; that is, that these operations are continuous in the coordinates which parametrise the $1$-morphisms.
+
+does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal.
+The schemes parametrising $1$-morphisms in $\L$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}.
+However the present paper is concerned only with defining the superbicategory $\L$ and proving that it is equivalent to $\LG$.
+TODO: A cut system is a bicategory enriched in a certain sense in the category of (indexed families of) affine schemes.
+
+%For various applications, two of which we sketch below, we would like to know that the basic operations of the bicategory $\LG$ respect this additional scheme structure; that is, that these operations are continuous in the coordinates which parametrise the $1$-morphisms.
 The most important and nontrivial such structure is the composition functor
-\begin{gather*}
-\LG(V,U)_{fin} \times \LG(W, V)_{fin} \lto \LG(W,U)\,,\\
-(Y,X) \mapsto Y \circ X\,.
-\end{gather*}
-We would like therefore to produce a morphism of schemes (omitting indices)
-\[
-c: \mathscr{M}(V,U) \times \mathscr{M}(W,V) \lto \mathscr{M}(W,U)
-\]
-with the property that $c([Y], [X]) = [Y \circ X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.
-
-The problem is that this doesn't make sense, because the matrix of polynomials defining the composite $Y \circ X$ contains monomials $x^i y^j z^k$ with $y$'s in them and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$.
+%\begin{gather*}
+%\LG(V,U)_{fin} \times \LG(W, V)_{fin} \lto \LG(W,U)\,,\\
+%(Y,X) \mapsto Y \circ X\,.
+%%\end{gather*}
+%(finite model) We would like therefore to produce a morphism of schemes (omitting indices)
+%\[
+%c: \mathscr{M}(V,U) \times \mathscr{M}(W,V) \lto \mathscr{M}(W,U)
+%\]
+%with the property that $c([Y], [X]) = [Y \circ X]$, where $[-]$ denotes the point of the parameter space corresponding to a given matrix factorisation.
+
+% The problem is that this doesn't make sense, because the matrix of polynomials defining the composite $Y \circ X$ contains monomials $x^i y^j z^k$ with $y$'s in them and we have no way to store the coefficients of such monomials in the space $\mathscr{M}(W,U)$.
 However one can prove that $Y \circ X$ is a summand in the homotopy category of a finite rank matrix factorisation (involving only $x$'s and $z$'s) and even describe this object and the corresponding idempotent explicitly \cite{dm1102.2957}.
@@
 
-\vspace{0.5cm}
-
-After some refinements\footnote{See Remark \ref{remark:relation_to_toby_paper} for a discussion of why we end up encoding the finite model by Clifford actions rather than the idempotents of \cite{dm1102.2957}.} this amounts to replacing $\LG$ by an equivalent bicategory $\cat{L}$ with the same objects and (almost) the same $1$-morphisms, but whose composition operation is easily encoded as a morphism of schemes.
-We say \emph{almost} the same $1$-morphisms because in $\cat{L}$ the $1$-morphisms are still finite rank matrix factorisations, but now they may additionally equipped with the action of a Clifford algebra.
-It remains straightforward to parametrise these $1$-morphisms by the closed points of an affine scheme, but in contrast to $\LG$ the composition functor in $\cat{L}$ (which we refer to as the \emph{cut operation})
-\begin{gather}
-\cat{L}(V,U) \times \cat{L}(W,V) \lto \cat{L}(W,U)\,,\\
-(Y,X) \mapsto Y \l X
-\end{gather}
-does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal.
-The schemes parametrising $1$-morphisms in $\cat{L}$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}.
-However the present paper is concerned only with defining the superbicategory $\cat{L}$ and proving that it is equivalent to $\LG$.
-
-The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
-In Section \ref{section:lg_cut_system} we define $\cat{L}$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$ as a superbicategory without units.
-We do not consider unit $1$-morphisms here because $\cat{L}$ does not make working with units any simpler.
-
-\subsection{Applications}
-
-\subsubsection{Topological field theory}
-
-The bicategory $\LG$ arises in topological field theory (TFT) as the data necessary to define a two-dimensional topological field theory with defects \cite{k1004.2307,dkr1107.0495}.
-It is expected that such a TFT should be associated to any suitably nice bicategory $\cat{B}$.
-In the formalisation of \cite[\S 3.1]{dkr1107.0495} the associated TFT is a symmetric monoidal functor
-\[
-\mathcal{Z}: \operatorname{Bord}_{2,1} \lto \operatorname{Vect}_\nC
-\]
-where the symmetric monoidal category $\operatorname{Bord}_{2,1}$ is defined roughly as follows: the objects are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.
-
-\begin{figure}[bt]
-$$
-  \raisebox{-75pt}{\begin{picture}(300,130)
-  \put(0,0){\scalebox{0.6}{\includegraphics{pic02.eps}}}
-  \put(0,0){
-     \setlength{\unitlength}{.55pt}\put(-22,-8){
-%     \put(136,224)   {$ \phi_\text{in} $}
-%     \put(140, 22)   {$ \phi_\text{in} $}
-%     \put(433,142)   {$ \phi_\text{out} $}
-	 \put(295,190)   {$ {\scriptstyle Y} $}
-	 \put(240,190)   {$ {\scriptstyle X} $}
-	 \put(335,85)   {$ {\scriptstyle Z} $}
-	 \put(390,105)   {$ {\scriptstyle Q} $}
-     \put(510,180)   {$ O_{3} $}
-     \put( 10,230)   {$ O_{1} $}
-     \put( 10,110)   {$ O_{2} $}
-     }\setlength{\unitlength}{1pt}}
-  \end{picture}}
-$$
-\caption{A world-sheet $M$ with defect lines from $\,(O_1,O_2)\,$ to
-$\,(O_{3})$.}
-\label{fig:wsh-defect}
-\end{figure}
-
-With $\cat{B} = \LG$ an example of a morphism is given in Figure \ref{fig:wsh-defect}.
-The two-dimensional regions of $M$ are labelled with potentials and the defect lines are labelled with $1$-morphisms in $\LG$, that is, matrix factorisations.
-In the special case where we use a single label $W(x)$ for all regions, the labels $X,Y,Z,Q$ for the defect lines are all chosen from the set of $1$-morphisms $W \lto W$.
-The value of $\mathcal{Z}$ on $M$ is a $\nC$-linear map
-\be\label{eq:value_of_bordism}
-\mathcal{Z}(M): \mathcal{Z}(O_1) \otimes \mathcal{Z}(O_2) \lto \mathcal{Z}(O_3)\,.
-\ee
-We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$.
-Namely, it is a consequence of the way the defect conditions $X,Y,Z,Q$ enter the partition function (see for example \cite[(3.16)]{laz}) that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining the defect conditions (TODO of course not).
-
-To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme parametrising possible defect conditions and $\mathcal{Z}(M)$ as a morphism of these vector bundles.
-But there are some obstacles.
-% \cite[(2.9)]{dkr1107.0495}
-
-Consider the incoming circle $O_2$ with two points marked $X,Y$. The construction gives
-\be\label{eq:zo2orig}
-\mathcal{Z}(O_2) := \Hom_{\LG(W,W)}( \Delta_W, Y^{\vee} \otimes X) \cong H^0 \Hom_{\nC[x,x']}( Y, X )
-\ee
-which is the vector space of $2$-morphisms $Y \lto X$ in $\LG(W,W)$. Now suppose that the defect conditions are made to depend on parameters 
-\[
-Y = Y(t_1,\ldots,t_r)\,, \qquad X = X(u_1,\ldots,u_s)
-\]
-which satisfy their own equations and cut out a parametrising scheme $\mathscr{M}_Y \times \mathscr{M}_X \subseteq \mathbb{A}^{r+s}$.
-The question is: what kind of global object $\mathcal{Z}(O_2)$ on $\mathscr{M}_Y \times \mathscr{M}_X$ is formed by the finite-dimensional vector spaces
-\[
-\mathcal{Z}(O_2)_{P,Q} := H^0 \Hom_{\nC[x,x']}( Y(P), X(Q) )
-\]
-as $P$ varies over $\mathscr{M}_Y$ and $Q$ over $\mathscr{M}_X$? The problem is that \emph{a priori} we have
-\be\label{eq:cohom_sucks}
-H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \Big\vert_{t=P, u=Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
-\ee
-%This is a particular case of a general phenomenon: any complex of $\nC$-vector spaces $C$ is isomorphic in the derived category $\mathbb{D}(\nC)$ to $\bigoplus_n H^n(C)[n]$, but over a general ring, for instance the coordinate ring of $\mathscr{M}_Y \times \mathscr{M}_X$, this is not the case.
-This discrepancy suggests that we should take as our global object $\mathcal{Z}(O_2)$ the Hom complex itself, as an object in the derived category\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
-\be\label{eq:wuhe20}
-\mathcal{Z}(O_2) := \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \in \mathbb{D}( \operatorname{qcoh} \mathscr{M}_Y \times \mathscr{M}_X )\,.
-\ee
-An alternative (and we believe simpler) approach is to take $\cat{L}$ rather than $\LG$ as the input to the definition of the TFT.
-Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define the vector space $\mathcal{Z}(O_2)$ from \eqref{eq:zo2orig} via the following composite in $\LG$:
-\be\label{eq:composite_intro_o2}
-\xymatrix@C+2pc{
-0 \ar[r]^-X & W(x) - W(x') \ar[r]^-{Y^{\vee}} & 0
-}\,.
-\ee
-Now let $\mathcal{Z}'$ be the TFT defined using the bicategory $\cat{L}$ as input.
-Then $\mathcal{Z}'(O_2)$ may likewise be computed by the composite \eqref{eq:composite_intro_o2} in $\cat{L}$, which is a $\nZ_2$-graded complex of vector spaces $Y^{\vee} \l X$ equipped with the action of a Clifford algebra.
-If $Y(t), X(u)$ are allowed to depend on parameters, the cut becomes a vector bundle
-\be\label{eq:orynx}
-\mathcal{Z}'(O_2) := Y^{\vee}(t) \l X(u)
-\ee
-over $\mathscr{M}_Y \times \mathscr{M}_X$ equipped with a differential and compatible Clifford action, such that
-\be
-Y^{\vee}(t) \l X(u) \Big\vert_{t=P,u=Q} \cong Y^{\vee}(P) \l X(Q)
-\ee
-for every point $(P,Q)$.
-
-Since $\cat{L}$ and $\LG$ are equivalent, the two ways \eqref{eq:wuhe20},\eqref{eq:orynx} of reading the composite \eqref{eq:composite_intro_o2} must contain the same information.
-However, the fact that $\eqref{eq:orynx}$ is a finite rank vector bundle over $\mathscr{M}_Y \times \mathscr{M}_X$ while \eqref{eq:wuhe20} is a complex of (non-finitely generated) quasi-coherent sheaves explains why $\cat{L}$ is better suited to this kind of problem.
-
-%We leave the details to the aforementioned sequel \cite{??}, but here is a simple example which already shows the nontriviality of viewing correlators as functionals of the moduli of the labels on defects.
-Consider the following bordism which is a morphism from the empty manifold $\emptyset$ to $O$, where $X$ denotes a matrix factorisation of $V(y) - W(x)$.
-The value of this diagram is an element
-%\[
-%\mathcal{Z}(M) \in \mathcal{Z}(O) \cong Jac(V)
-%\]
-%By virtue of the above discussion, we may think of $\mathcal{Z}(M)$ as a \emph{section} of the trivial vector bundle with fiber $Jac(V)$ over the scheme $\mathscr{M}(W,V)$ which parametrises $1$-morphisms from $W$ to $V$ in $\LG$.
-If this section is not identically zero, then $V$ is called a \emph{generalised orbifold} of $W$ \cite{??} and it is of great interest to know when this is the case.
-From what we have said, it is clear that this is essentially a question of the geometry of $\mathscr{M}(W,V)$.
-
-TODO: discuss $A_\infty$ algebras.
-If we want to understand how minimal models vary with the coefficients, and where the jumps occur, we need an intermediate finite object over blah since minimal models only work well over a field.
-
-\subsubsection{Semantics of logic}
+\subsection{Semantics of linear logic}
 
@@
 Proofs in the logic are interpreted by certain correspondences between these pairs.
-To explain briefly why we are forced to use $\cat{L}$ rather than $\LG$, we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
+To explain briefly why we are forced to use $\L$ rather than $\LG$, we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
 
 Let $x$ be a variable of the logic and suppose it has denotation $\llbracket x \rrbracket = (\Spec(\nC), \nC[x], W)$ in the semantics.
-Let $\mathscr{M} = \mathscr{M}(W,W)$ be the (indexed) affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\cat{L}$, as discussed above.
+Let $\mathscr{M} = \mathscr{M}(W,W)$ be the (indexed) affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\L$, as discussed above.
 Then the semantics works as follows:
@@
 For these definitions to work, the coefficients of the monomials in the matrix factorisation $X \l X$ need to be given explicitly as polynomial functions of the coefficients in $X$.
-This means we have to use $\cat{L}$ rather than $\LG$.
+This means we have to use $\L$ rather than $\LG$.
 
@@
 
-The cut operation in $\cat{L}$ produces objects which are representations of Clifford algebras.
+The cut operation in $\L$ produces objects which are representations of Clifford algebras.
 We briefly recall the basic theory of these algebras and their modules; for a full discussion see \cite{friedrich}.
-For $n \ge 0$ the Clifford algebra $C_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $\gamma_1,\ldots,\gamma_n$ and $\gamma_1^\dagger, \ldots, \gamma_n^\dagger$ subject to the following relations
+For $n \ge 0$ the Clifford algebra $C_n$ is the associative $\mathbb{Z}_2$-graded $k$-algebra generated by odd elements $\ferm_1,\ldots,\ferm_n$ and $\fermc_1, \ldots, \fermc_n$ subject to the following relations
 \be\label{eq:clifford_relations}
-[\gamma_i, \gamma_j] = 0, \qquad [\gamma_i^\dagger, \gamma_j^\dagger] = 0, \qquad [\gamma_i, \gamma_j^\dagger] = \delta_{ij}\,.
+[\ferm_i, \ferm_j] = 0, \qquad [\fermc_i, \fermc_j] = 0, \qquad [\ferm_i, \fermc_j] = \delta_{ij}\,.
 \ee
@@
 \[
-\gamma_i \mapsto \theta_i \wedge (-), \qquad \gamma_i^\dagger \mapsto \theta_i^*\, \lrcorner\, (-)
+\ferm_i \mapsto \theta_i \wedge (-), \qquad \fermc_i \mapsto \theta_i^*\, \lrcorner\, (-)
 \]
@@
 \[
-e_n = \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1\,.
+e_n = \fermc_1 \cdots \fermc_n \ferm_n \cdots \ferm_1\,.
 \]
@@
 \begin{align*}
-\cat{T}^{\star}( (X,n), (Y,m) ) &= \Big\{ \alpha \in \cat{T}(X,Y) \l \alpha \gamma_i = 0 \text{ for } 1 \le i \le n \text{ and }\\
-&\qquad \qquad\qquad \qquad \;\; \gamma_i^\dagger \alpha = 0 \text{ for } 1 \le i \le m \Big\}\,.
+\cat{T}^{\star}( (X,n), (Y,m) ) &= \Big\{ \alpha \in \cat{T}(X,Y) \l \alpha \ferm_i = 0 \text{ for } 1 \le i \le n \text{ and }\\
+&\qquad \qquad\qquad \qquad \;\; \fermc_i \alpha = 0 \text{ for } 1 \le i \le m \Big\}\,.
 \end{align*}
@@
 \begin{align*}
-\alpha e_n &= \alpha \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1\\
-&= \alpha \left( \gamma_1^\dagger \cdots \gamma_{n-1}^\dagger \gamma_{n-1} \cdots \gamma_1 - \gamma_1^\dagger \cdots \gamma_n \gamma_n^\dagger \cdots \gamma_1 \right)\\
-&= \alpha \gamma_1^\dagger \cdots \gamma_{n-1}^\dagger \gamma_{n-1} \cdots \gamma_1
+\alpha e_n &= \alpha \fermc_1 \cdots \fermc_n \ferm_n \cdots \ferm_1\\
+&= \alpha \left( \fermc_1 \cdots \fermc_{n-1} \ferm_{n-1} \cdots \ferm_1 - \fermc_1 \cdots \ferm_n \fermc_n \cdots \ferm_1 \right)\\
+&= \alpha \fermc_1 \cdots \fermc_{n-1} \ferm_{n-1} \cdots \ferm_1
 \end{align*}
-since in the second summand within the brackets, there is nothing to stop $\gamma_n$ from commuting to the left and annihilating with $\alpha$.
+since in the second summand within the brackets, there is nothing to stop $\ferm_n$ from commuting to the left and annihilating with $\alpha$.
 Proceeding inductively, we see that $\alpha e_n = \alpha$.
@@
 \[
-f_0 \gamma_i = f_0 e_n \gamma_i = f_0 \gamma_1^\dagger \cdots \gamma_n^\dagger \gamma_n \cdots \gamma_1 \gamma_i = 0\,.
+f_0 \ferm_i = f_0 e_n \ferm_i = f_0 \fermc_1 \cdots \fermc_n \ferm_n \cdots \ferm_1 \ferm_i = 0\,.
 \]
@@
 
-\section{The superbicategory $\cat{L}$}\label{section:lg_cut_system}
-
-%In this section we introduce the cut system $\cat{L}$, beginning with a sketch of the major pieces and then proceeding to the technical details.
+\section{The superbicategory $\L$}\label{section:lg_cut_system}
+
+%In this section we introduce the cut system $\L$, beginning with a sketch of the major pieces and then proceeding to the technical details.
 The objects of the cut system are the same as the objects of the bicategory $\LG$, that is, pairs $(x, W)$ consisting of a set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x]$.
@@
 
-In this section we define a superbicategory without units $\cat{L}$.
+In this section we define a superbicategory without units $\L$.
 Later we will prove that this bicategory is equivalent to $\LG$, although this will not be apparent at first.
-The objects of $\cat{L}$ are the same as $\LG$, namely potentials $(x,W)$.
+The objects of $\L$ are the same as $\LG$, namely potentials $(x,W)$.
 
@@
 \be\label{eq:defnluv}
-\cat{L}(W,V) = \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,
+\L(W,V) = \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,
 \ee
@@
 
-Thus a $1$-morphism $W \lto V$ in $\cat{L}$ is a finite rank matrix factorisation $X$ of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\gamma_i, \gamma_i^\dagger$ satisfying Clifford relations and the equations (all up to homotopy)
+Thus a $1$-morphism $W \lto V$ in $\L$ is a finite rank matrix factorisation $X$ of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\ferm_i, \fermc_i$ satisfying Clifford relations and the equations (all up to homotopy)
 \begin{gather*}
-\gamma_i e = \gamma_i = e \gamma_i\,, \\
-\gamma_i^\dagger e = \gamma_i^\dagger = e \gamma_i^\dagger\,.
+\ferm_i e = \ferm_i = e \ferm_i\,, \\
+\fermc_i e = \fermc_i = e \fermc_i\,.
 \end{gather*}
 Most of the time we only care about $1$-morphisms where $e = 1$, and let us only describe $2$-morphisms in this case.
-For matrix factorisations $X,Y$ of $V(y) - W(x)$ with respective Clifford actions $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^a$ and $\{ \rho_j, \rho_j^\dagger \}_{j=1}^b$ the $2$-morphisms $\phi: (X,a) \lto (Y,b)$ in $\cat{L}$ are by Lemma \ref{lemma:equivcliffordthick} in bijection with morphisms of matrix factorisations $\phi: X \lto Y$ satisfying
-\[
-\phi \gamma_i = 0\,, \qquad \rho_j^\dagger \phi = 0\,, \qquad 1 \le i \le a, \quad 1 \le j \le b\,.
-\]
-Observe that the homotopy category $\LG(W,V)_{fin}$ of finite rank matrix factorisations sits fully faithfully inside $\cat{L}(W,V)$ as the subcategory where all idempotents are identities and there are no Clifford actions, and by Lemma \ref{lemma:embedcliffordthick} the inclusion of this subcategory into $\cat{L}(W,V)$ is an idempotent completion.
+For matrix factorisations $X,Y$ of $V(y) - W(x)$ with respective Clifford actions $\{ \ferm_i, \fermc_i \}_{i=1}^a$ and $\{ \rho_j, \rho_j^\dagger \}_{j=1}^b$ the $2$-morphisms $\phi: (X,a) \lto (Y,b)$ in $\L$ are by Lemma \ref{lemma:equivcliffordthick} in bijection with morphisms of matrix factorisations $\phi: X \lto Y$ satisfying
+\[
+\phi \ferm_i = 0\,, \qquad \rho_j^\dagger \phi = 0\,, \qquad 1 \le i \le a, \quad 1 \le j \le b\,.
+\]
+Observe that the homotopy category $\LG(W,V)_{fin}$ of finite rank matrix factorisations sits fully faithfully inside $\L(W,V)$ as the subcategory where all idempotents are identities and there are no Clifford actions, and by Lemma \ref{lemma:embedcliffordthick} the inclusion of this subcategory into $\L(W,V)$ is an idempotent completion.
 
@@
 \begin{gather*}
-\cat{L}(V,U) \otimes_k \cat{L}(W,V) \lto \cat{L}(W, U)\,\\
+\L(V,U) \otimes_k \L(W,V) \lto \L(W, U)\,\\
 (Y,X) \mapsto Y \l X
@@
 \begin{equation}\label{eq:intro_clifford_act1}
-\gamma_i^\dagger = \At_i\,, \qquad \gamma_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
+\fermc_i = \At_i\,, \qquad \ferm_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
 \end{equation}
@@
 
-\begin{theorem} Given matrix factorisations $Y,X$ as above, the data
+\begin{theorem}\label{theorem:cut_is_rep} Given matrix factorisations $Y,X$ as above, the data
 \be
-Y \l X = \left( Y \otimes_{k[y]} J_V \otimes_{k[y]} X, \{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m \right)
-\ee
-defines a representation of $C_m$ in the homotopy category of matrix factorisations, that is, the $\gamma_i, \gamma_i^\dagger$ satisfy the Clifford relations \eqref{eq:clifford_relations}
+Y \l X = \left( Y \otimes_{k[y]} J_V \otimes_{k[y]} X, \{ \ferm_i, \fermc_i \}_{i=1}^m \right)
+\ee
+defines a representation of $C_m$ in the homotopy category of matrix factorisations, that is, the $\ferm_i, \fermc_i$ satisfy the Clifford relations \eqref{eq:clifford_relations}
 up to homotopy.
@@
 \end{align*}
-Hence $[\gamma_i^\dagger, \gamma_j^\dagger] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
+Hence $[\fermc_i, \fermc_j] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
 \begin{align*}
@@
 \begin{align*}
-[ \gamma_i, \gamma^\dagger_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
+[ \ferm_i, \fermc_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
 &= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [ \At_q, \At_j]\\
@@
 \begin{align*}
-[ \gamma_i, \gamma_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
+[ \ferm_i, \ferm_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
 &= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
@@
 \be\label{eq:cutisafunctor}
-\cat{L}(V,U) \otimes_k \cat{L}(W,V) \lto \cat{L}(W, U)
+\L(V,U) \otimes_k \L(W,V) \lto \L(W, U)
 \ee
@@
 \]
-Explicitly, this functor is given for $(Y,e_Y) \in \cat{L}(V,U)$ and $(X,e_X) \in \cat{L}(W,V)$ by
+Explicitly, this functor is given for $(Y,e_Y) \in \L(V,U)$ and $(X,e_X) \in \L(W,V)$ by
 \[
@@
 \]
-Now suppose we have representations $( Y, \{ \rho_j, \rho_j^\dagger \}_{j=1}^r )$ of $C_r$ in $\cat{L}(V,U)$ and $( X, \{ \tau_l, \tau^\dagger_l \}_{l=1}^s )$ of $C_s$ in $\cat{L}(W,V)$.
+Now suppose we have representations $( Y, \{ \rho_j, \rho_j^\dagger \}_{j=1}^r )$ of $C_r$ in $\L(V,U)$ and $( X, \{ \tau_l, \tau^\dagger_l \}_{l=1}^s )$ of $C_s$ in $\L(W,V)$.
 Here $Y,X$ may come equipped with idempotents but these are easily handled so we ignore them in what follows.
@@
 The operators from the action of $C_r$ anticommute with the operators from the action of $C_s$ because they act on different components of a tensor product.
-Moreover, both actions anticommute with the new $C_m$ action $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ coming from the cut, by Lemma \ref{prop:morphismsarecliffordreps}.
+Moreover, both actions anticommute with the new $C_m$ action $\{ \ferm_i, \fermc_i \}_{i=1}^m$ coming from the cut, by Lemma \ref{prop:morphismsarecliffordreps}.
 Thus $Y \l X$ is equipped with the structure of a $C_r \otimes C_m \otimes C_s \cong C_{r+m+s}$-representation.
@@
 
-% In the remainder of this section we define a bicategory without units $\cat{L}$ with these functors as its composition of $1$-morphisms.
+% In the remainder of this section we define a bicategory without units $\L$ with these functors as its composition of $1$-morphisms.
 
@@
 
-\begin{definition} The superbicategory without units $\cat{L}$ has
+\begin{definition} The superbicategory without units $\L$ has
 \begin{itemize}
@@
 \end{gather*}
-is $C_m \otimes C_p$-linear (see Lemma \ref{lemma:associator} below) and is the associator for $\cat{L}$.
+is $C_m \otimes C_p$-linear (see Lemma \ref{lemma:associator} below) and is the associator for $\L$.
 \end{itemize}
@@
 relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
-Specifically, the generator $\gamma_i^{\dagger}$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
+Specifically, the generator $\fermc_i$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
 But this operator can be identified with an Atiyah class of the linear factorisation
@@
 
-\begin{proposition} Thus defined $\cat{L}$ is a superbicategory without units.
+\begin{proposition} Thus defined $\L$ is a superbicategory without units.
 \end{proposition}
@@
 \[
-e_m' = \gamma_1 \cdots \gamma_m \gamma_m^\dagger \cdots \gamma_1^\dagger\,.
-\]
-Observe that each of the $\gamma_i$'s acts as $- \lambda_i$ because all of the $\gamma_j^\dagger$'s to the right. Hence
+e_m' = \ferm_1 \cdots \ferm_m \fermc_m \cdots \fermc_1\,.
+\]
+Observe that each of the $\ferm_i$'s acts as $- \lambda_i$ because all of the $\fermc_j$'s to the right. Hence
 \begin{align*}
-e_m' &= (-1)^{\binom{m}{2}} \gamma_1 \cdots \gamma_m \gamma_1^\dagger \cdots \gamma_m^\dagger \\
+e_m' &= (-1)^{\binom{m}{2}} \ferm_1 \cdots \ferm_m \fermc_1 \cdots \fermc_m \\
 &= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
@@
 
-\section{The equivalence of $\cat{L}$ and $\LG$}\label{section:equivllg}
-
-We prove that the cut functor defined in Section \ref{section:lg_cut_system} models composition in $\LG$ by providing an equivalence of this superbicategory with $\cat{L}$.
+\section{The equivalence of $\L$ and $\LG$}\label{section:equivllg}
+
+We prove that the cut functor defined in Section \ref{section:lg_cut_system} models composition in $\LG$ by providing an equivalence of this superbicategory with $\L$.
 This is done by presenting the cut $Y \l X$ with its Clifford action as the solution of the problem of finding a finite model for the matrix factorisation $Y \otimes X$ over $k[x,z]$.
@@
 There is a canonical action of the Clifford algebra $C_m$ on $S_m$ and thus on the right hand side, which ``remembers'' how to extract $Y \otimes X$ from this larger object.
-Transferring this action yields the operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ on $Y \l X$ from Section \ref{section:lg_cut_system}.
+Transferring this action yields the operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$ on $Y \l X$ from Section \ref{section:lg_cut_system}.
 \end{itemize}
@@
 In conclusion, there is an isomorphism of Clifford representations \eqref{eq:iso_of_clifford_modelfinite} in the homotopy category of finite rank matrix factorisations of $U - W$ over $k[x,z]$, and this is our solution to the problem of finding a finite model of $Y \otimes X$.
-Once we have established all of this, proving that $\cat{L}$ and $\LG$ are equivalent bicategories will be straightforward.
+Once we have established all of this, proving that $\L$ and $\LG$ are equivalent bicategories will be straightforward.
 
@@
 
-Let $Q$ be a complex of infinite rank free abelian groups.
-Suppose that the cohomology is finitely generated, so that $Q$ contains in some sense only a ``finite'' amount of information.
-One can ask for a description which makes this finiteness manifest: the obvious answer is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.
+Let $Q$ be a complex of vector spaces (possibly infinite dimensional) with finite dimensional cohomology, so that $Q$ contains in some sense only a ``finite'' amount of information.
+One way of making this finiteness manifest is to simply list the cohomology groups of $Q$, but a more flexible and categorical solution is to find a finite representative in the homotopy equivalence class of $Q$.
 
@@
 
-\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-modules
+\begin{example}\label{example:koszulsplit} Consider the following diagram of complexes of $k$-vector spaces
 \[
@@
 We proceed to rediscover $Y \l X$ with its Clifford action as a finite model of $Y \otimes X$.
-Using this we prove in the next section that $\cat{L}$ and $\LG$ are equivalent bicategories.
+Using this we prove in the next section that $\L$ and $\LG$ are equivalent bicategories.
 The notation is as in Setup \ref{setupforfusion}.
@@
 The canonical action of $C_m$ on the spinor representation $S_m$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $S_m \otimes_k ( Y \otimes X )$.
-In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$, and it remains to show that these two actions are compatible.
+In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible.
 
@@
 \[
-\gamma_i \Phi \simeq \Phi \theta_i \,, \qquad \gamma_i^\dagger \Phi \simeq \Phi \theta_i^*\,.
+\ferm_i \Phi \simeq \Phi \theta_i \,, \qquad \fermc_i \Phi \simeq \Phi \theta_i^*\,.
 \]
@@
 \begin{proof}
-We prove that $\gamma_i \simeq \Phi \theta_i \Phi^{-1}$ and $\gamma_i^\dagger \simeq \Phi \theta_i^* \Phi^{-1}$.
+We prove that $\ferm_i \simeq \Phi \theta_i \Phi^{-1}$ and $\fermc_i \simeq \Phi \theta_i^* \Phi^{-1}$.
 With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $S_m \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
@@
 \[
-\Phi \theta_i^* \Phi^{-1} \simeq \pi \cat{T}(\theta_i^*) \sigma_\infty = \pi \theta_i^* \sigma_\infty \simeq \At_i = \gamma_i^\dagger\,.
+\Phi \theta_i^* \Phi^{-1} \simeq \pi \cat{T}(\theta_i^*) \sigma_\infty = \pi \theta_i^* \sigma_\infty \simeq \At_i = \fermc_i\,.
 \]
@@
 &\simeq - \lambda_i - \frac{1}{2}\sum_q \partial_{y_qy_i}(V) \At_q\\
-&= \gamma_i
+&= \ferm_i
 \end{align*}
@@
 
-\subsection{The equivalence of $\cat{L}$ and $\LG$}\label{section:equivalenceforreal}
-
-The bicategories $\LG$ and $\cat{L}$ have the same objects. Their morphism categories are 
+\subsection{The equivalence of $\L$ and $\LG$}\label{section:equivalenceforreal}
+
+The bicategories $\LG$ and $\L$ have the same objects. Their morphism categories are 
 \begin{align*}
-\cat{L}(W,V) &= \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,\\
+\L(W,V) &= \Big( \hmf( k[x,y], V - W )^{\omega} \Big)^{\bullet}\,,\\
 \LG(W,V) &= \hmf( k[x,y], V - W )^{\oplus}
@@
 
-\begin{theorem} There is an equivalence $\cat{Z}: \LG \lto \cat{L}$ of superbicategories without units.
+\begin{theorem} There is an equivalence $\cat{Z}: \LG \lto \L$ of superbicategories without units.
 \end{theorem}
@@
 \[
-e_m = \gamma_1^\dagger \cdots \gamma_m^\dagger \gamma_m \cdots \gamma_1 \in C_m
+e_m = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1 \in C_m
 \]
@@
 \[
-\varphi_{Y,X}: (Y \l X, 1, \{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m) \lto (Y \l X, e_m)
-\]
-in the Clifford thickening of the idempotent completion of $\hmf(k[x,z],U - W)$, where the left hand side is equipped with the idempotent $1$ and the action $\{ \gamma_i, \gamma_i^\dagger \}_{i=1}^m$ of $C_m$ while the right hand side has no Clifford action and idempotent $e_m$.
+\varphi_{Y,X}: (Y \l X, 1, \{ \ferm_i, \fermc_i \}_{i=1}^m) \lto (Y \l X, e_m)
+\]
+in the Clifford thickening of the idempotent completion of $\hmf(k[x,z],U - W)$, where the left hand side is equipped with the idempotent $1$ and the action $\{ \ferm_i, \fermc_i \}_{i=1}^m$ of $C_m$ while the right hand side has no Clifford action and idempotent $e_m$.
 
@@
 
-\begin{remark} Obviously the $1$-morphisms $\Delta_W: W \lto W$ which are the units in $\LG$ are, by virtue of the equivalence $\mathcal{Z}$, also units in $\cat{L}$, so that this is an honest bicategory and $\mathcal{Z}$ an equivalence of bicategories.
-The reason we do not begin with units in $\cat{L}$ is that the unitors are no simpler in $\cat{L}$ than $\LG$, so there is no real point to introducing them.
+\begin{remark} Obviously the $1$-morphisms $\Delta_W: W \lto W$ which are the units in $\LG$ are, by virtue of the equivalence $\mathcal{Z}$, also units in $\L$, so that this is an honest bicategory and $\mathcal{Z}$ an equivalence of bicategories.
+The reason we do not begin with units in $\L$ is that the unitors are no simpler in $\L$ than $\LG$, so there is no real point to introducing them.
 \end{remark}
@@
 
-Using the bicategory $\cat{L}$ we can study the complex $\Hom_R(Y,X)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[y_1,\ldots,y_m]$.
+Using the bicategory $\L$ we can study the complex $\Hom_R(Y,X)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[y_1,\ldots,y_m]$.
 In particular, we will explain how the homotopy relation on morphisms of matrix factorisations is effectively computable.
@@
 
-The Clifford algebra $C_1$ acts on $Y^{\vee} \l X$ by generators $\gamma, \gamma^\dagger$.
+The Clifford algebra $C_1$ acts on $Y^{\vee} \l X$ by generators $\ferm, \fermc$.
 To determine their matrices in the basis determined by \eqref{eq:examplecut_basis2} and \eqref{eq:examplecut_basis}, note that with $t = \partial_y(V) = N y^{N-1}$, $k[y]$ is a free $k[t]$-module with basis $1, \ldots, y^{N-2}$.
@@
 \end{align*}
-The matrix of the Atiyah class as an operator $\gamma^\dagger$ on $Y^{\vee} \l X$ is therefore
+The matrix of the Atiyah class as an operator $\fermc$ on $Y^{\vee} \l X$ is therefore
 \begin{equation}\label{eq:aityah_class_hom_example}
-\gamma^\dagger = \begin{pmatrix} 0 & 0 & -[R_{N-i}] & -[R_{j}] \\ 
+\fermc = \begin{pmatrix} 0 & 0 & -[R_{N-i}] & -[R_{j}] \\ 
 0 & 0 & -[R_{N-j}] & -[R_{i}] \\
@@
 \[
-\gamma = - \partial_y(d_X) - \frac{1}{2} N (N-1) y^{N-2} \gamma^\dagger
-\]
-which completes the description of the cut $( Y^{\vee} \l X, \{ \gamma, \gamma^\dagger \} )$.
-%Splittng the idempotent $\gamma^\dagger \gamma$ on $Y^{\vee} \l X$ yields a finite model for $\Hom_R(Y,X)$.
+\ferm = - \partial_y(d_X) - \frac{1}{2} N (N-1) y^{N-2} \fermc
+\]
+which completes the description of the cut $( Y^{\vee} \l X, \{ \ferm, \fermc \} )$. %Splittng the idempotent $\gamma^\dagger \gamma$ on $Y^{\vee} \l X$ yields a finite model for $\Hom_R(Y,X)$.
 \end{example}
@@
 \[
-\Hom_{C_n}^0( S_n, X ) \cong \big\{ x \in X^0 \l \gamma_i^\dagger \cdot x = 0 \text{ for all } 1 \le i \le n \big\}
+\Hom_{C_n}^0( S_n, X ) \cong \big\{ x \in X^0 \l \fermc_i \cdot x = 0 \text{ for all } 1 \le i \le n \big\}
 \]
@@
 \[
-\Hom^0_{C_n}( (S_n)^*, X ) \cong \big\{ x \in X^0 \l x \cdot \gamma_i = 0 \text{ for all } 1 \le i \le n \big\}
+\Hom^0_{C_n}( (S_n)^*, X ) \cong \big\{ x \in X^0 \l x \cdot \ferm_i = 0 \text{ for all } 1 \le i \le n \big\}
 \]
@@
 \[
-\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta \in \cat{C}(X,Y) \l \gamma_i^\dagger \circ \delta = 0 \text{ for all } 1 \le i \le n \}
+\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta \in \cat{C}(X,Y) \l \fermc_i \circ \delta = 0 \text{ for all } 1 \le i \le n \}
 \]
@@
 \begin{align*}
-\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ \gamma_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ \gamma_i^\dagger \circ \delta &= 0 \text{ for } 1 \le i \le q \}
+\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ \ferm_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ \fermc_i \circ \delta &= 0 \text{ for } 1 \le i \le q \}
 \end{align*}
@@
 &\cong \Hom^0_{C_q}( S_q, \Hom^*_{C_p}( S_p^*, \cat{C}^*(X,Y) ))\\
-&\cong \{ \delta \in \Hom^0_{C_q}( S_p^*, \cat{C}^*(X,Y) ) \l \gamma_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
-&\cong \{ \delta: X \lto Y \l \delta \circ \gamma_i = 0 \text{ for } 1 \le i \le p \text{ and } \gamma_i^\dagger \circ \delta = 0 \text{ for } 1 \le i \le q \}
+&\cong \{ \delta \in \Hom^0_{C_q}( S_p^*, \cat{C}^*(X,Y) ) \l \fermc_i \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
+&\cong \{ \delta: X \lto Y \l \delta \circ \ferm_i = 0 \text{ for } 1 \le i \le p \text{ and } \fermc_i \circ \delta = 0 \text{ for } 1 \le i \le q \}
 \end{align*}

### 2015-12-14 cutsystems_cuts.tex
Prior to changing Atiyahs to annihilation.

@@
 \end{proof}
+
+\subsubsection{Topological field theory}
+
+The bicategory $\LG$ arises in topological field theory (TFT) as the data necessary to define a two-dimensional topological field theory with defects \cite{k1004.2307,dkr1107.0495}.
+It is expected that such a TFT should be associated to any suitably nice bicategory $\cat{B}$.
+In the formalisation of \cite[\S 3.1]{dkr1107.0495} the associated TFT is a symmetric monoidal functor
+\[
+\mathcal{Z}: \operatorname{Bord}_{2,1} \lto \operatorname{Vect}_\nC
+\]
+where the symmetric monoidal category $\operatorname{Bord}_{2,1}$ is defined roughly as follows: the objects are disjoint unions of (collared) circles labelled with objects and $1$-morphisms of $\cat{B}$, and the morphisms are diffeomorphism equivalence classes of two-dimensional manifolds with boundary and a labelled network of ``defects''.
+
+\begin{figure}[bt]
+$$
+  \raisebox{-75pt}{\begin{picture}(300,130)
+  \put(0,0){\scalebox{0.6}{\includegraphics{pic02.eps}}}
+  \put(0,0){
+     \setlength{\unitlength}{.55pt}\put(-22,-8){
+%     \put(136,224)   {$ \phi_\text{in} $}
+%     \put(140, 22)   {$ \phi_\text{in} $}
+%     \put(433,142)   {$ \phi_\text{out} $}
+	 \put(295,190)   {$ {\scriptstyle Y} $}
+	 \put(240,190)   {$ {\scriptstyle X} $}
+	 \put(335,85)   {$ {\scriptstyle Z} $}
+	 \put(390,105)   {$ {\scriptstyle Q} $}
+     \put(510,180)   {$ O_{3} $}
+     \put( 10,230)   {$ O_{1} $}
+     \put( 10,110)   {$ O_{2} $}
+     }\setlength{\unitlength}{1pt}}
+  \end{picture}}
+$$
+\caption{A world-sheet $M$ with defect lines from $\,(O_1,O_2)\,$ to
+$\,(O_{3})$.}
+\label{fig:wsh-defect}
+\end{figure}
+
+With $\cat{B} = \LG$ an example of a morphism is given in Figure \ref{fig:wsh-defect}.
+The two-dimensional regions of $M$ are labelled with potentials and the defect lines are labelled with $1$-morphisms in $\LG$, that is, matrix factorisations.
+In the special case where we use a single label $W(x)$ for all regions, the labels $X,Y,Z,Q$ for the defect lines are all chosen from the set of $1$-morphisms $W \lto W$.
+The value of $\mathcal{Z}$ on $M$ is a $\nC$-linear map
+\be\label{eq:value_of_bordism}
+\mathcal{Z}(M): \mathcal{Z}(O_1) \otimes \mathcal{Z}(O_2) \lto \mathcal{Z}(O_3)\,.
+\ee
+We would like to discuss an additional property of the physicist's Landau-Ginzburg model which is not encoded into the data of the functor $\mathcal{Z}$.
+Namely, it is a consequence of the way the defect conditions $X,Y,Z,Q$ enter the partition function (see for example \cite[(3.16)]{laz}) that the vector spaces $\mathcal{Z}(O_i)$ and linear map $\mathcal{Z}(M)$ should depend continuously on the coefficients defining the defect conditions (TODO of course not).
+
+To represent this mathematically we might try to present $\mathcal{Z}(O_i)$ as a vector bundle over a scheme parametrising possible defect conditions and $\mathcal{Z}(M)$ as a morphism of these vector bundles.
+But there are some obstacles.
+% \cite[(2.9)]{dkr1107.0495}
+
+Consider the incoming circle $O_2$ with two points marked $X,Y$. The construction gives
+\be\label{eq:zo2orig}
+\mathcal{Z}(O_2) := \Hom_{\LG(W,W)}( \Delta_W, Y^{\vee} \otimes X) \cong H^0 \Hom_{\nC[x,x']}( Y, X )
+\ee
+which is the vector space of $2$-morphisms $Y \lto X$ in $\LG(W,W)$. Now suppose that the defect conditions are made to depend on parameters 
+\[
+Y = Y(t_1,\ldots,t_r)\,, \qquad X = X(u_1,\ldots,u_s)
+\]
+which satisfy their own equations and cut out a parametrising scheme $\mathscr{M}_Y \times \mathscr{M}_X \subseteq \mathbb{A}^{r+s}$.
+The question is: what kind of global object $\mathcal{Z}(O_2)$ on $\mathscr{M}_Y \times \mathscr{M}_X$ is formed by the finite-dimensional vector spaces
+\[
+\mathcal{Z}(O_2)_{P,Q} := H^0 \Hom_{\nC[x,x']}( Y(P), X(Q) )
+\]
+as $P$ varies over $\mathscr{M}_Y$ and $Q$ over $\mathscr{M}_X$? The problem is that \emph{a priori} we have
+\be\label{eq:cohom_sucks}
+H^* \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \Big\vert_{t=P, u=Q} \neq H^* \Hom_{\nC[x,x']}( Y(P), X(Q) )\,.
+\ee
+%This is a particular case of a general phenomenon: any complex of $\nC$-vector spaces $C$ is isomorphic in the derived category $\mathbb{D}(\nC)$ to $\bigoplus_n H^n(C)[n]$, but over a general ring, for instance the coordinate ring of $\mathscr{M}_Y \times \mathscr{M}_X$, this is not the case.
+This discrepancy suggests that we should take as our global object $\mathcal{Z}(O_2)$ the Hom complex itself, as an object in the derived category\footnote{Note that it is not enough to take the derived category of coherent sheaves, because the Hom complex is made up of non-finitely-generated modules over $\mathscr{M}_Y \times \mathscr{M}_X$.}
+\be\label{eq:wuhe20}
+\mathcal{Z}(O_2) := \Hom_{\nC[x,x',t,u]}( Y(t), X(u) ) \in \mathbb{D}( \operatorname{qcoh} \mathscr{M}_Y \times \mathscr{M}_X )\,.
+\ee
+An alternative (and we believe simpler) approach is to take $\cat{L}$ rather than $\LG$ as the input to the definition of the TFT.
+Before doing so, let us observe that in the situation where $X,Y$ do not depend on parameters, we may equivalently\footnote{This definition is not quite equivalent, because the displayed composite produces a complex of vector spaces quasi-isomorphic to $H^* \Hom(Y,X)$ rather than $H^0 \Hom(Y,X)$, but this is not important here.} define the vector space $\mathcal{Z}(O_2)$ from \eqref{eq:zo2orig} via the following composite in $\LG$:
+\be\label{eq:composite_intro_o2}
+\xymatrix@C+2pc{
+0 \ar[r]^-X & W(x) - W(x') \ar[r]^-{Y^{\vee}} & 0
+}\,.
+\ee
+Now let $\mathcal{Z}'$ be the TFT defined using the bicategory $\cat{L}$ as input.
+Then $\mathcal{Z}'(O_2)$ may likewise be computed by the composite \eqref{eq:composite_intro_o2} in $\cat{L}$, which is a $\nZ_2$-graded complex of vector spaces $Y^{\vee} \l X$ equipped with the action of a Clifford algebra.
+If $Y(t), X(u)$ are allowed to depend on parameters, the cut becomes a vector bundle
+\be\label{eq:orynx}
+\mathcal{Z}'(O_2) := Y^{\vee}(t) \l X(u)
+\ee
+over $\mathscr{M}_Y \times \mathscr{M}_X$ equipped with a differential and compatible Clifford action, such that
+\be
+Y^{\vee}(t) \l X(u) \Big\vert_{t=P,u=Q} \cong Y^{\vee}(P) \l X(Q)
+\ee
+for every point $(P,Q)$.
+
+Since $\cat{L}$ and $\LG$ are equivalent, the two ways \eqref{eq:wuhe20},\eqref{eq:orynx} of reading the composite \eqref{eq:composite_intro_o2} must contain the same information.
+However, the fact that $\eqref{eq:orynx}$ is a finite rank vector bundle over $\mathscr{M}_Y \times \mathscr{M}_X$ while \eqref{eq:wuhe20} is a complex of (non-finitely generated) quasi-coherent sheaves explains why $\cat{L}$ is better suited to this kind of problem.
+
+%We leave the details to the aforementioned sequel \cite{??}, but here is a simple example which already shows the nontriviality of viewing correlators as functionals of the moduli of the labels on defects.
+Consider the following bordism which is a morphism from the empty manifold $\emptyset$ to $O$, where $X$ denotes a matrix factorisation of $V(y) - W(x)$.
+The value of this diagram is an element
+%\[
+%\mathcal{Z}(M) \in \mathcal{Z}(O) \cong Jac(V)
+%\]
+%By virtue of the above discussion, we may think of $\mathcal{Z}(M)$ as a \emph{section} of the trivial vector bundle with fiber $Jac(V)$ over the scheme $\mathscr{M}(W,V)$ which parametrises $1$-morphisms from $W$ to $V$ in $\LG$.
+If this section is not identically zero, then $V$ is called a \emph{generalised orbifold} of $W$ \cite{??} and it is of great interest to know when this is the case.
+From what we have said, it is clear that this is essentially a question of the geometry of $\mathscr{M}(W,V)$.
+
+TODO: discuss $A_\infty$ algebras.
+If we want to understand how minimal models vary with the coefficients, and where the jumps occur, we need an intermediate finite object over blah since minimal models only work well over a field.

### 2015-12-15 cutsystems-new.tex
Candidate final draft.

@@
 The bicategory $\LG$ of Landau-Ginzburg models has polynomials as objects and matrix factorisations as $1$-morphisms.
-The composition of $1$-morphisms naturally produces infinite rank matrix factorisations, which is a nuisance.
-In this paper we define a bicategory $\L$ which is equivalent to $\LG$ but for which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
+The composition of these $1$-morphisms produces infinite rank matrix factorisations, which is a nuisance.
+In this paper we define a bicategory $\L$ which is equivalent to $\LG$ in which composition of $1$-morphisms produces finite rank matrix factorisations equipped with the action of a Clifford algebra.
+This amounts to a finite model of composition in $\LG$.
 \end{abstract}
@@
 
-The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, as can be seen by its important role in topological field theory \cite{McNameethesis,lgdual,genorb} homological knot invariants \cite{kr0401268} and $2$-representations of quantum groups \cite{??}, but the definition is still relatively elementary.
-This makes $\LG$ an attractive algebraic object of study, but for one major wrinkle: the composition operation for $1$-morphisms is infinitary.
+The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, attested to by the existence of adjoints and pivotality \cite{lgdual}, its role in recent important results in topological field theory \cite{genorb,ade} and the theory of homological knot invariants \cite{kr0401268}.
+This is remarkable in light of the fact that $1$-morphisms are very simple objects, namely, matrices of polynomials which satisfy an equation.
+This makes $\LG$ an attractive object of study, but for one major wrinkle: the composition operation for $1$-morphisms is infinitary.
 
@@
 Such a matrix factorisation is a $\nZ_2$-graded free $\nC[x,y]$-module $X = X^0 \oplus X^1$ together with an odd operator $d_X$ satisfying $d_X^2 = (V(y) - W(x)) \cdot 1_X$.
-For a third potential $U(z)$, the composition of $1$-morphisms is a functor
+For a third potential $U(z)$, composition is a functor
 \begin{gather*}
@@
 \ee
-This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$ which is only homotopy equivalent (that is, isomorphic in the homotopy category) to a finite rank matrix factorisation.
-While this finite model can be proven abstractly to exist, there is no obvious way to describe it as a function of the input data $Y,X$ viewed as matrices of polynomials.
-This need to deal throughout with infinite rank matrix factorisations introduces a certain minimal level of complexity into the theory, which for many applications is undesirable.
+This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$, which is only homotopy equivalent to a finite rank matrix factorisation.
+While this finite model can be proven abstractly to exist, there is no obvious way to describe it as a function of the input data $Y,X$.
+This means that we are stuck with infinite rank matrix factorisations in the theory.
 
 Together with Dyckerhoff we initiated in \cite{dm1102.2957} the study of these finite models in terms of homological perturbation and Atiyah classes, and in the present paper this program reaches its logical conclusion.
-We introduce a bicategory $\L$ in which the objects are again potentials and where the $1$-morphisms are finite rank matrix factorisations equipped with the structure of a representation of a Clifford algebra.
-We will prove that this bicategory is equivalent to $\LG$, but is much simpler - in particular, it has a composition operation which is described by a finite number of polynomial functions of the input data.
-
-More precisely: the composition of $1$-morphisms in $\L$ is a functor
+We introduce a bicategory $\L$ in which the objects are again potentials and the $1$-morphisms $W \lto V$ are finite rank matrix factorisations of $V - W$ additionally equipped with the structure of a representation of a Clifford algebra.
+We will prove that this bicategory is equivalent to $\LG$, but it is much simpler: the composition operation is described by a finite number of polynomial functions of the input data.
+
+More precisely, the composition of $1$-morphisms in $\L$ is a functor
 \begin{gather}
-\L(V,U) \times \L(W,V) \lto \L(W,U)\,,\\
+\L(V,U) \times \L(W,V) \lto \L(W,U)\,,\label{eq:cut_functor_intro}\\
 (Y,X) \mapsto Y \l X
@@
 which we call the \emph{cut operation}.
-The definition of the cut is very simple.
-With $J_V = \nC[y]/(\partial V)$ the Jacobi algebra of $\nC$ (which is a finite-dimensional $\nC$-vector space by the assumption that $V(y)$ is a potential) the cut of $Y$ and $X$ is a finite rank matrix factorisation
+Let us describe the cut in the most important case, where $Y, X$ are matrix factorisations as above, not equipped with any additional structure as representations of a Clifford algebra.
+The Jacobi algebra $J_V = \nC[y_1,\ldots,y_m]/(\partial_{y_1} V, \ldots, \partial_{y_m} V)$ is a finite-dimensional $\nC$-vector space by the assumption that $V(y)$ is a potential, and the cut is defined to be the following finite rank matrix factorisation over $\nC[x,z]$
 \be
@@
 \ee
-over $\nC[x,z]$
-
-equipped with odd operators $\ferm_i, \fermc_i$ satisfying Clifford relations
-\begin{gather*}
-\ferm_i e = \ferm_i = e \ferm_i\,, \\
-\fermc_i e = \fermc_i = e \fermc_i\,.
-\end{gather*}
+equipped with a family of odd closed operators $\{\ferm_i, \fermc_i\}_{i=1}^m$ defined by
+\begin{equation}\label{eq:intro_clifford_act1_intro}
+\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}
+\end{equation}
+where the $\At_q$ are Atiyah classes. These operators satisfy Clifford relations
+\be\label{eq:clifford_relations_intro}
+\ferm_i \ferm_j + \ferm_j \ferm_i = 0, \qquad \fermc_i \fermc_j + \fermc_j \fermc_i = 0, \qquad \ferm_i \fermc_j + \fermc_j \ferm_i = \delta_{ij}
+\ee
 up to homotopy (see Theorem \ref{theorem:cut_is_rep}).
-The differential on $Y \l X$ is induced from the differential on $Y \otimes X$ and can be written explicitly as a matrix over $\nC[x,z]$ in terms of the polynomial entries of $d_Y, d_X$.
-The Clifford action and the matrices which define the Clifford actions on $Y,X$.
-In particular, infinite rank matrix factorisations are never involved.
-In the remainder of the introduction we sketch how the cut operation arises from homological perturbation, why Clifford algebras are involved, where the equivalence $\L \cong \LG$ comes from, and our motivations for pursuing this ``finite model'' $\L$ of $\LG$.
-%In this sense the bicategory $\L$, which we prove is equivalent to $\LG$, provides a ``finite model'' of $\LG$.
-This has various applications, which we will describe later in the introduction.
-
-The main theorem (Theorem \ref{theorem:htpy_equivalence_main}) says
-\begin{equation}\label{eq:final_finite_model}
+The differential on $Y \l X$ and the Clifford operators can be written explicitly as matrices over $\nC[x,z]$, where the coefficients of the monomials in each row and column are polynomials in the monomial coefficients of $d_Y, d_X$ and $V$.
+Thus, the cut operation is a polynomial function of its inputs and, in particular, infinite rank matrix factorisations are banished.
+
+Let us sketch where the cut operation comes from, why Clifford algebras are involved, and why there is an equivalence $\L \cong \LG$.
+In Section \ref{section:intro_appli} we describe various applications.
+The main theorem (Theorem \ref{theorem:htpy_equivalence_main}) uses homological perturbation to produce a strong deformation retract, and in particular an isomorphism, in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $\nC[x,z]$ of the form
+\begin{equation}\label{eq:final_finite_model_intro}
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{\nC} ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
 }
 \end{equation}
+where $S_m = \bigwedge ( \nC^{\oplus m}[1] )$ denotes the exterior algebra.
+The algebra $C_m = \End_{\nC}(S_m)$ is a Clifford algebra, and \eqref{eq:final_finite_model_intro} identifies the natural action of $C_m$ on the right hand side with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.
+
+There is a category called the \emph{Clifford thickening} of the homotopy category of matrix factorisations of $U - W$, in which objects are matrix factorisations equipped with a $C_k$-action for some $k$ (i.e.
+$k$ is allowed to be different for different objects).
+In this category $S_m \otimes_{\nC} ( Y \otimes X )$ with its $C_m$-action is isomorphic to $Y \otimes X$ with no Clifford action, and so \eqref{eq:final_finite_model_intro} can be read as a natural isomorphism $Y \l X \cong Y \otimes X$.
+We prove this is suitably functorial in $Y,X$ and therefore defines an equivalence $\L \cong \LG$.
+
+\vspace{0.5cm}
+
 The paper is structured as follows: in Section \ref{section:background} we recall the definition of superbicategories and Clifford algebras, and introduce the Clifford thickening of a supercategory.
+The reason we need the formalism of supercategories is that we make extensive use of Clifford actions on objects of linear categories, and for this to make sense the categories themselves must be $\nZ_2$-graded (that is, supercategories).
 In Section \ref{section:lg_cut_system} we define $\L$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$ as a superbicategory without units.
-We do not consider unit $1$-morphisms here because $\L$ does not make working with units any simpler.
-
-\subsection{$A_\infty$-algebras and minimal models}
-
-The relationship between $\LG$ and $\L$ is similar to the relationship between a DG-algebra and its $A_\infty$-minimal model.
-Given a DG algebra $A$ over a field $k$, which is infinite-dimensional but has finite-dimensional cohomology, the $A_\infty$-minimal model is an $A_\infty$-structure on the cohomology $H^*(A)$ which is $A_\infty$-quasi-isomorphic to $A$.
-The tradeoff being made is that $A$ is infinite-dimensional but with a simple structure (i.e.
-one multiplication map $m_2$) while $H^*(A)$ is finite-dimensional but with possibly an infinite family of higher multiplications.
-In $\LG$ the composition operation is not described by a finite amount of data, and the price that one pays by going to $\L$ where this is the case, is that the composition has additional structure (a Clifford action).
-There is a more precise link to $A_\infty$-minimal models.
-A special case of the equivalence between $\L$ and $\LG$ gives, for a matrix factorisation $X$ of the potential $W(x_1,\ldots,x_m)$ viewed, a strong deformation retract
-\be
-\Phi: S_m \otimes_k \Hom_R(X,X) \lto X^{\vee} \l X\,.
-\ee
-where $S_m = \bigwedge( k \theta_1 \oplus \cdots \oplus k \theta_m )$ is an exterior algbera, $\Hom_R(X,X)$ is the Hom complex.
-This deformation retract can be used as the input data for the usual construction of an $A_\infty$-minimal on the left hand side, viewed as a DG-algebra.
-
-\subsection{A geometric enrichment of $\LG$}
-
-A finite rank matrix factorisation of $V(y) - W(x)$ is a matrix of polynomials
-\[
+
+\subsection{Applications}\label{section:intro_appli}
+
+\subsubsection{$A_\infty$-algebras and minimal models}
+
+As a special case of the deformation retract \eqref{eq:final_finite_model_intro} we obtain in Section \ref{example:computing_homs} for any potential $V(y)$ and matrix factorisations $X,X'$ of $V$ a deformation retract of $\nZ_2$-graded complexes of vector spaces
+\begin{equation}\label{eq:final_finite_model_hom}
+\xymatrix@C+4pc{
+(X')^{\vee} \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k \Hom_{\nC[y]}(X', X) \ar@<-1ex>[l]_-{\Phi}
+}
+\end{equation}
+where $\Hom_{\nC[y]}(X',X)$ denotes the Hom-complex. Observe that this is infinite-dimensional (with finite-dimensional cohomology) while $(X')^{\vee} \l X$ is finite-dimensional.
+
+In the case $X = X'$ the right hand side is a DG-algebra and the deformation retract may be taken as the input to the standard algorithms for producing an $A_\infty$-minimal model of $\End_{\nC[y]}(X)$.
+It turns out that this input is well-suited for actually doing computations, which we hope to return to elsewhere.
+
+\subsubsection{Cut systems: a geometric enrichment of $\LG$}
+
+The \emph{cut systems} of the title are bicategories enriched over affine schemes.
+Our primary motivation for introducing $\cat{C}$ is that it can be enriched in this way (whereas $\LG$ cannot, because the composition is infinitary).
+For context we sketch the definition of a cut system here; the full definition will appear in a sequel to the present paper.
+
+Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
+\be\label{eq:intro_capitalD}
 D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
-\]
+\ee
 where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices.
-The set of finite rank matrix factorisations is denoted $\LG(W,V)_{fin}$.
-For technical reasons the category of $1$-morphisms $\LG(W,V)$ contains, in addition to the finite rank matrix factorisations, those infinite rank matrix factorisations which are homotopy equivalent to finite rank ones; this means in particular that the inclusion
-\[
-\LG(W,V)_{fin} \lto \LG(W,V)
-\]
-is an equivalence of categories.
-If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise the possible matrix factorisations by the closed points of an affine scheme $\mathscr{M}_{r,k}(W,V)$ whose coordinates are the coefficients of the various monomials in each row and column of $D$.
-Hence as sets we have
+If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the closed points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.
+
+We may add further coordinates and equations to encode closed odd operators satisfying Clifford relations \eqref{eq:clifford_relations_intro} and, in this way, for a choice of parameters $\lambda = (r, k, \ldots)$ define a scheme $\mathscr{M}_{\lambda}(W,V)$ such that as sets
 \begin{equation}\label{eq:param_frmf}
-\LG(W,V)_{fin} = \bigsqcup_{r \ge 1} \bigcup_{k \ge 0} \mathscr{M}_{r,k}(W,V)_{\nC}\,.
-\end{equation}
-
-does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal.
+\cat{C}(W,V) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{\nC}
+\end{equation}
+where $Z_{\nC}$ denotes the $\nC$-points of a scheme $Z$. The cut operation is a polynomial function of its inputs, so there is an indexed family of morphisms of schemes
+\be\label{eq:enrichment_morphisms_intro}
+\mathscr{M}_\mu(V,U) \times \mathscr{M}_\lambda(W,V) \lto \mathscr{M}_{f(\lambda, \mu)}(W, U)
+\ee
+lifting the functor \eqref{eq:cut_functor_intro} on the level of objects for some function $f(\lambda, \mu)$ of indices.
+Finally, using the approach of Section \ref{example:computing_homs}, we can define a bundle of Clifford representations
+\be\label{eq:enrichment_intro_bundles}
+\xymatrix{
+\mathscr{H}\! om_{W,V} \ar[d]\\
+\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)
+}
+\ee
+which for two finite-rank matrix factorisations $X,X'$ of $V - W$ has for its fiber over the point $(X',X)$ the finite-dimensional Clifford representation $(X')^{\vee} \l X$ as in \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{\nC[x,y]}(X',X)$ tensored with a suitable spinor representation.
+The cut system which enriches $\cat{C}$ consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.
+
+% The set of finite rank matrix factorisations is denoted $\LG(W,V)_{fin}$. 
+%For technical reasons the category of $1$-morphisms $\LG(W,V)$ contains, in addition to the finite rank matrix factorisations, those infinite rank matrix factorisations which are homotopy equivalent to finite rank ones; this means in particular that the inclusion
+%\[
+%\LG(W,V)_{fin} \lto \LG(W,V)
+%\]
+%is an equivalence of categories.
+
+% does indeed lift to a morphism of the parametrising schemes - fulfilling the original goal.
 The schemes parametrising $1$-morphisms in $\L$ together with the morphisms of schemes lifting composition, and vector bundles encoding the $2$-morphisms, is what we refer to as a \emph{cut system} in the sequel \cite{cutsystems2}.
-However the present paper is concerned only with defining the superbicategory $\L$ and proving that it is equivalent to $\LG$.
-TODO: A cut system is a bicategory enriched in a certain sense in the category of (indexed families of) affine schemes.
 
@@
 
-\subsection{Semantics of linear logic}
-
-In forthcoming work we will use the results of this paper to define a novel semantics of linear logic, in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
+\subsubsection{Semantics of linear logic}
+
+In forthcoming work we use the cut system enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
 Proofs in the logic are interpreted by certain correspondences between these pairs.
-To explain briefly why we are forced to use $\L$ rather than $\LG$, we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
+Let us briefly explain the general point which leads us to use $\L$ rather than $\LG$, for which we will use the denotation of the Church numeral $\underline{2}$ (see \cite{murfet_ll}).
 
@@
 \end{gather*}
-The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which concretely means that $\llbracket \underline{2} \rrbracket$ is a bundle over the scheme $\mathscr{M}$ whose fiber over a loop $X$, viewed as a point $[X] \in \mathscr{M}$, is the square $X \l X$.
-More precisely, $\llbracket \underline{2} \rrbracket$ is the bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over $([X], a)$ is
+The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which concretely means that $\llbracket \underline{2} \rrbracket$ is a vector bundle over the scheme $\mathscr{M} \cong \mathscr{M} \times \Spec(\nC)$ whose fiber over a loop $X$, viewed as a point of $\mathscr{M}$, is the square $X \l X$.
+More precisely, $\llbracket \underline{2} \rrbracket$ is the bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over $(X, a)$ is the finite-dimensional Clifford representation
 \be\label{eq:bundledifferentialcliffordproof}
-\llbracket \underline{2} \rrbracket_{[X],a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)\,.
-\ee
+\llbracket \underline{2} \rrbracket_{X,a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)
+\ee
+where applying $- \otimes_{\nC[x,x']} \nC(a)$ means that if $a = (a_1,a_2) \in \Spec(\nC[x,x'])$ we substitute the scalar values $x = a_1$ and $x' = a_2$ into the polynomials defining $X \l X$.
+
 For these definitions to work, the coefficients of the monomials in the matrix factorisation $X \l X$ need to be given explicitly as polynomial functions of the coefficients in $X$.
@@
 
-\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft, and to Ingo Runkel and Rafal Suszek for kindly allowing the use of Figure \ref{fig:wsh-defect} from \cite{runkel}.
+\emph{Acknowledgements.} Thanks to Nils Carqueville for helpful comments on the draft.%, and to Ingo Runkel and Rafal Suszek for kindly allowing the use of Figure \ref{fig:wsh-defect} from \cite{runkel}.
 %Although the sequel on linear logic is the proper place to fully acknowledge the debt, we cannot neglect to mention the important role that the beautiful ideas in Girard's geometry of interaction program \cite{girard_towards} had in shaping the present work.
@@
 \[
-\ferm_i \mapsto \theta_i \wedge (-), \qquad \fermc_i \mapsto \theta_i^*\, \lrcorner\, (-)
+\fermc_i \mapsto \theta_i \wedge (-), \qquad \ferm_i \mapsto \theta_i^*\, \lrcorner\, (-)
 \]
@@
 \[
-e_n = \fermc_1 \cdots \fermc_n \ferm_n \cdots \ferm_1\,.
+e_n = \ferm_1 \cdots \ferm_n \fermc_n \cdots \fermc_1\,.
 \]
@@
 \begin{align*}
-\cat{T}^{\star}( (X,n), (Y,m) ) &= \Big\{ \alpha \in \cat{T}(X,Y) \l \alpha \ferm_i = 0 \text{ for } 1 \le i \le n \text{ and }\\
-&\qquad \qquad\qquad \qquad \;\; \fermc_i \alpha = 0 \text{ for } 1 \le i \le m \Big\}\,.
+\cat{T}^{\star}( (X,n), (Y,m) ) &= \Big\{ \alpha \in \cat{T}(X,Y) \l \alpha \fermc_i = 0 \text{ for } 1 \le i \le n \text{ and }\\
+&\qquad \qquad\qquad \qquad \;\; \ferm_i \alpha = 0 \text{ for } 1 \le i \le m \Big\}\,.
 \end{align*}
@@
 \begin{align*}
-\alpha e_n &= \alpha \fermc_1 \cdots \fermc_n \ferm_n \cdots \ferm_1\\
-&= \alpha \left( \fermc_1 \cdots \fermc_{n-1} \ferm_{n-1} \cdots \ferm_1 - \fermc_1 \cdots \ferm_n \fermc_n \cdots \ferm_1 \right)\\
-&= \alpha \fermc_1 \cdots \fermc_{n-1} \ferm_{n-1} \cdots \ferm_1
+\alpha e_n &= \alpha \ferm_1 \cdots \ferm_n \fermc_n \cdots \fermc_1\\
+&= \alpha \left( \ferm_1 \cdots \ferm_{n-1} \fermc_{n-1} \cdots \fermc_1 - \ferm_1 \cdots \fermc_n \ferm_n \cdots \fermc_1 \right)\\
+&= \alpha \ferm_1 \cdots \ferm_{n-1} \fermc_{n-1} \cdots \fermc_1
 \end{align*}
-since in the second summand within the brackets, there is nothing to stop $\ferm_n$ from commuting to the left and annihilating with $\alpha$.
+since in the second summand within the brackets, there is nothing to stop $\fermc_n$ from commuting to the left and annihilating with $\alpha$.
 Proceeding inductively, we see that $\alpha e_n = \alpha$.
@@
 \[
-f_0 \ferm_i = f_0 e_n \ferm_i = f_0 \fermc_1 \cdots \fermc_n \ferm_n \cdots \ferm_1 \ferm_i = 0\,.
+f_0 \fermc_i = f_0 e_n \fermc_i = f_0 \ferm_1 \cdots \ferm_n \fermc_n \cdots \fermc_1 \fermc_i = 0\,.
 \]
@@
 
-Thus a $1$-morphism $W \lto V$ in $\L$ is a finite rank matrix factorisation $X$ of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\ferm_i, \fermc_i$ satisfying Clifford relations and the equations (all up to homotopy)
+Thus a $1$-morphism $W \lto V$ in $\L$ is a finite rank matrix factorisation of $V(y) - W(x)$ together with an idempotent endomorphism $e$ and a family of odd operators $\ferm_i, \fermc_i$ satisfying Clifford relations and the equations (all up to homotopy)
 \begin{gather*}
-\ferm_i e = \ferm_i = e \ferm_i\,, \\
-\fermc_i e = \fermc_i = e \fermc_i\,.
+\ferm_i e = \ferm_i = e \ferm_i\,, \qquad \fermc_i e = \fermc_i = e \fermc_i\,.
 \end{gather*}
-Most of the time we only care about $1$-morphisms where $e = 1$, and let us only describe $2$-morphisms in this case.
 For matrix factorisations $X,Y$ of $V(y) - W(x)$ with respective Clifford actions $\{ \ferm_i, \fermc_i \}_{i=1}^a$ and $\{ \rho_j, \rho_j^\dagger \}_{j=1}^b$ the $2$-morphisms $\phi: (X,a) \lto (Y,b)$ in $\L$ are by Lemma \ref{lemma:equivcliffordthick} in bijection with morphisms of matrix factorisations $\phi: X \lto Y$ satisfying
 \[
-\phi \ferm_i = 0\,, \qquad \rho_j^\dagger \phi = 0\,, \qquad 1 \le i \le a, \quad 1 \le j \le b\,.
+\phi \fermc_i = 0\,, \qquad \rho_j \phi = 0\,, \qquad 1 \le i \le a, \quad 1 \le j \le b\,.
 \]
@@
 \begin{equation}\label{eq:intro_clifford_act1}
-\fermc_i = \At_i\,, \qquad \ferm_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
+\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
 \end{equation}
@@
 \end{align*}
-Hence $[\fermc_i, \fermc_j] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
+Hence $[\ferm_i, \ferm_j] = [d, h_{ij}]$ where $h_{ij} = - [ \partial_{t_j}, \At_i ]$. Next we compute
 \begin{align*}
@@
 \begin{align*}
-[ \ferm_i, \fermc_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
+[ \fermc_i, \ferm_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
 &= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [ \At_q, \At_j]\\
@@
 \begin{align*}
-[ \ferm_i, \ferm_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
+[ \fermc_i, \fermc_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
 &= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
@@
 relative to the ring morphism $k[q,x] \lto k[q,x] [ \partial_{y_1} U, \ldots, \partial_{y_p} U ]$.
-Specifically, the generator $\fermc_i$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
+Specifically, the generator $\ferm_i$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
 But this operator can be identified with an Atiyah class of the linear factorisation
@@
 \[
-e_m' = \ferm_1 \cdots \ferm_m \fermc_m \cdots \fermc_1\,.
-\]
-Observe that each of the $\ferm_i$'s acts as $- \lambda_i$ because all of the $\fermc_j$'s to the right. Hence
+e_m' = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1\,.
+\]
+Observe that each of the $\fermc_i$'s acts as $- \partial_{y_i}(d_X)$ because all of the $\ferm_j$'s to the right. Hence
 \begin{align*}
-e_m' &= (-1)^{\binom{m}{2}} \ferm_1 \cdots \ferm_m \fermc_1 \cdots \fermc_m \\
+e_m' &= (-1)^{\binom{m}{2}} \fermc_1 \cdots \fermc_m \ferm_1 \cdots \ferm_m \\
 &= (-1)^{\binom{m+1}{2}} \lambda_1 \cdots \lambda_m \At_1 \cdots \At_m\,.
@@
 \[
-\ferm_i \Phi \simeq \Phi \theta_i \,, \qquad \fermc_i \Phi \simeq \Phi \theta_i^*\,.
+\fermc_i \Phi \simeq \Phi \theta_i \,, \qquad \ferm_i \Phi \simeq \Phi \theta_i^*\,.
 \]
@@
 \begin{proof}
-We prove that $\ferm_i \simeq \Phi \theta_i \Phi^{-1}$ and $\fermc_i \simeq \Phi \theta_i^* \Phi^{-1}$.
+We prove that $\fermc_i \simeq \Phi \theta_i \Phi^{-1}$ and $\ferm_i \simeq \Phi \theta_i^* \Phi^{-1}$.
 With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $S_m \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
@@
 \[
-\Phi \theta_i^* \Phi^{-1} \simeq \pi \cat{T}(\theta_i^*) \sigma_\infty = \pi \theta_i^* \sigma_\infty \simeq \At_i = \fermc_i\,.
+\Phi \theta_i^* \Phi^{-1} \simeq \pi \cat{T}(\theta_i^*) \sigma_\infty = \pi \theta_i^* \sigma_\infty \simeq \At_i = \ferm_i\,.
 \]
@@
 &\simeq - \lambda_i - \frac{1}{2}\sum_q \partial_{y_qy_i}(V) \At_q\\
-&= \ferm_i
+&= \fermc_i
 \end{align*}
@@
 \[
-e_m = \fermc_1 \cdots \fermc_m \ferm_m \cdots \ferm_1 \in C_m
+e_m = \ferm_1 \cdots \ferm_m \fermc_m \cdots \fermc_1 \in C_m
 \]
@@
 \]
-where $g$ is the quotient map, and $f g = 1_{Y \otimes X}$ while $g f = e_m$.\footnote{$f$ is $\Phi^{-1}$ followed by projection onto $\theta$-degree zero.
-Not a very friendly map.} Then we may take as our definition
+where $g$ is the quotient map, and $f g = 1_{Y \otimes X}$ while $g f = e_m$.\footnote{$f$ is $\Phi^{-1}$ followed by projection onto $\theta$-degree zero.} Then we may take as our definition
 \[
@@
 Using the bicategory $\L$ we can study the complex $\Hom_R(Y,X)$ for two finite rank matrix factorisations $X,Y$ of a potential $V \in R = k[y_1,\ldots,y_m]$.
-In particular, we will explain how the homotopy relation on morphisms of matrix factorisations is effectively computable.
-
 The pair $(k,0)$ is an object in $\LG$ and we may view $X$ and the dual matrix factorisation $Y^{\vee}$ of $-V$ as a pair of $1$-morphisms
@@
 \be\label{eq:examplecut_basis2}
-J_V = k[y]/y^{N-1} = k \cdot 1 \oplus k \cdot y \oplus \cdots k \cdot y^{N-2}
+J_V = k[y]/y^{N-1} = k \cdot 1 \oplus k \cdot y \oplus \cdots \oplus k \cdot y^{N-2}
 \ee
@@
 \end{align*}
-The matrix of the Atiyah class as an operator $\fermc$ on $Y^{\vee} \l X$ is therefore
+The matrix of the Atiyah class as an operator $\ferm$ on $Y^{\vee} \l X$ is therefore
 \begin{equation}\label{eq:aityah_class_hom_example}
-\fermc = \begin{pmatrix} 0 & 0 & -[R_{N-i}] & -[R_{j}] \\ 
+\ferm = \begin{pmatrix} 0 & 0 & -[R_{N-i}] & -[R_{j}] \\ 
 0 & 0 & -[R_{N-j}] & -[R_{i}] \\
@@
 \[
-\ferm = - \partial_y(d_X) - \frac{1}{2} N (N-1) y^{N-2} \fermc
+\fermc = - \partial_y(d_X) - \frac{1}{2} N (N-1) y^{N-2} \ferm
 \]
@@
 \[
-\Hom_{C_n}^0( S_n, X ) \cong \big\{ x \in X^0 \l \fermc_i \cdot x = 0 \text{ for all } 1 \le i \le n \big\}
+\Hom_{C_n}^0( S_n, X ) \cong \big\{ x \in X^0 \l \ferm_i \cdot x = 0 \text{ for all } 1 \le i \le n \big\}
 \]
@@
 \[
-\Hom^0_{C_n}( (S_n)^*, X ) \cong \big\{ x \in X^0 \l x \cdot \ferm_i = 0 \text{ for all } 1 \le i \le n \big\}
+\Hom^0_{C_n}( (S_n)^*, X ) \cong \big\{ x \in X^0 \l x \cdot \fermc_i = 0 \text{ for all } 1 \le i \le n \big\}
 \]
@@
 \[
-\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta \in \cat{C}(X,Y) \l \fermc_i \circ \delta = 0 \text{ for all } 1 \le i \le n \}
+\cat{C}_{C_n}( S_n \otimes_k X, Y ) \cong \{ \delta \in \cat{C}(X,Y) \l \ferm_i \circ \delta = 0 \text{ for all } 1 \le i \le n \}
 \]
@@
 \begin{align*}
-\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ \ferm_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ \fermc_i \circ \delta &= 0 \text{ for } 1 \le i \le q \}
+\cat{C}_{C_q}( S_{q,p} \otimes_{C_p} X, Y ) \cong \{ \delta: X \lto Y \l \delta \circ \fermc_i &= 0 \text{ for } 1 \le i \le p \text{ and }\\ \ferm_i \circ \delta &= 0 \text{ for } 1 \le i \le q \}
 \end{align*}
@@
 &\cong \Hom^0_{C_q}( S_q, \Hom^*_{C_p}( S_p^*, \cat{C}^*(X,Y) ))\\
-&\cong \{ \delta \in \Hom^0_{C_q}( S_p^*, \cat{C}^*(X,Y) ) \l \fermc_i \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
-&\cong \{ \delta: X \lto Y \l \delta \circ \ferm_i = 0 \text{ for } 1 \le i \le p \text{ and } \fermc_i \circ \delta = 0 \text{ for } 1 \le i \le q \}
+&\cong \{ \delta \in \Hom^0_{C_q}( S_p^*, \cat{C}^*(X,Y) ) \l \ferm_i \circ \delta = 0 \text{ for } 1 \le i \le q \}\\
+&\cong \{ \delta: X \lto Y \l \delta \circ \fermc_i = 0 \text{ for } 1 \le i \le p \text{ and } \ferm_i \circ \delta = 0 \text{ for } 1 \le i \le q \}
 \end{align*}
@@
 \bibitem{lgdual}
-N.~Carqueville and D.~Murfet, \textsl{Adjunctions and defects in {L}andau-{G}inzburg models}, \href{http://arxiv.org/abs/1208.1481}{[arXiv:1208.1481]}.
+N.~Carqueville and D.~Murfet, \textsl{Adjunctions and defects in {L}andau-{G}inzburg models}, Adv. Math. \textbf{289} (2016), 480--566, \href{http://arxiv.org/abs/1208.1481}{[arXiv:1208.1481]}.
 
@@
 
-%\bibitem{girard_llogic}
-%J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
+\bibitem{girard_llogic}
+J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
 

### 2015-12-16 cutsystems-new.tex
Second arXiv version.

@@
 
-The objects of $\LG$ are potentials $W(x)$, while $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
+The objects of $\LG$ are a class of polynomials $W(x)$ called potentials, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
 Such a matrix factorisation is a $\nZ_2$-graded free $\nC[x,y]$-module $X = X^0 \oplus X^1$ together with an odd operator $d_X$ satisfying $d_X^2 = (V(y) - W(x)) \cdot 1_X$.
+These $1$-morphisms form a category denoted $\LG(W,V)$.
 For a third potential $U(z)$, composition is a functor
@@
 We introduce a bicategory $\L$ in which the objects are again potentials and the $1$-morphisms $W \lto V$ are finite rank matrix factorisations of $V - W$ additionally equipped with the structure of a representation of a Clifford algebra.
-We will prove that this bicategory is equivalent to $\LG$, but it is much simpler: the composition operation is described by a finite number of polynomial functions of the input data.
-
+This bicategory is equivalent to $\LG$, but it is simpler: the composition operation is described by a finite number of polynomial functions of the input data.
 More precisely, the composition of $1$-morphisms in $\L$ is a functor
@@
 \xymatrix@C+4pc{
-(X')^{\vee} \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_k \Hom_{\nC[y]}(X', X) \ar@<-1ex>[l]_-{\Phi}
+(X')^{\vee} \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{\nC} \Hom_{\nC[y]}(X', X) \ar@<-1ex>[l]_-{\Phi}
 }
@@
 where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices.
-If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the closed points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.
+If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $\nC$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.
 
@@
 lifting the functor \eqref{eq:cut_functor_intro} on the level of objects for some function $f(\lambda, \mu)$ of indices.
-Finally, using the approach of Section \ref{example:computing_homs}, we can define a bundle of Clifford representations
+Finally, using the approach of Section \ref{example:computing_homs}, we can define for each pair of potentials $W,V$ and tuple of parameters $\lambda$ a bundle of Clifford representations
 \be\label{eq:enrichment_intro_bundles}
 \xymatrix{
-\mathscr{H}\! om_{W,V} \ar[d]\\
-\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)
-}
-\ee
-which for two finite-rank matrix factorisations $X,X'$ of $V - W$ has for its fiber over the point $(X',X)$ the finite-dimensional Clifford representation $(X')^{\vee} \l X$ as in \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{\nC[x,y]}(X',X)$ tensored with a suitable spinor representation.
+\mathscr{H}\! om_{W,V,\lambda} \ar[d]\\
+\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)\,.
+}
+\ee
+Given two finite-rank matrix factorisations $X,X'$ of $V - W$ the fiber of this vector bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{\nC[x,y]}(X',X)$ tensored with a suitable spinor representation.
 The cut system which enriches $\cat{C}$ consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.
@@
 \end{gather*}
-The proof $\underline{2}$ of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which concretely means that $\llbracket \underline{2} \rrbracket$ is a vector bundle over the scheme $\mathscr{M} \cong \mathscr{M} \times \Spec(\nC)$ whose fiber over a loop $X$, viewed as a point of $\mathscr{M}$, is the square $X \l X$.
-More precisely, $\llbracket \underline{2} \rrbracket$ is the bundle over $\mathscr{M} \times \Spec(\nC[x,x'])$ whose fiber over $(X, a)$ is the finite-dimensional Clifford representation
-\be\label{eq:bundledifferentialcliffordproof}
-\llbracket \underline{2} \rrbracket_{X,a} = \left( X \l X \right) \otimes_{\nC[x,x']} \nC(a)
-\ee
-where applying $- \otimes_{\nC[x,x']} \nC(a)$ means that if $a = (a_1,a_2) \in \Spec(\nC[x,x'])$ we substitute the scalar values $x = a_1$ and $x' = a_2$ into the polynomials defining $X \l X$.
-
+A proof of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which is a matrix factorisation of $W(x) - W(x')$ over the scheme $\mathscr{M} \times \Spec(\nC[x,x'])$.
+For example, the Church numeral $\underline{2}$ has for its denotation the matrix factorisation whose fiber over a loop $X: W \lto W$, viewed as a point of $\mathscr{M}$, is the square $X \l X$ as a matrix factorisation of $W(x) - W(x')$ over $\Spec(\nC[x,x'])$.
 For these definitions to work, the coefficients of the monomials in the matrix factorisation $X \l X$ need to be given explicitly as polynomial functions of the coefficients in $X$.
@@
 The Koszul complex $K$ of the sequence $t_1,\ldots,t_m$ (where $t_i = \partial_{y_i} V$) is defined by
-\begin{equation}\label{defn:koszul}
+\begin{equation}\label{defn:koszul2}
 K = S_m \otimes_k k[y], \qquad d_K = \sum_{i=1}^m t_i \theta_i^*\,.
@@
 \]
-We assume this is a superfunctor, i.e.
-that \eqref{eq:psicomp1}-\eqref{eq:psicomp3} commute.
 Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$.
@@
 \end{gather}
-expresses compatibility of $\Psi$ with the associator of $\cat{B}$.
+expresses compatibility of $\Psi$ with the associator of $\cat{B}$. Finally, commutativity of
+\begin{equation}\label{eq:psicomp1}
+\xymatrix@R+1pc@C+1pc{
+T( 1 \otimes \Psi^2 ) \ar[r]^-{\tau}\ar[d]_-{T(1 \otimes \xi)} & \Psi T( 1 \otimes \Psi ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
+T \ar[rr]_-{1_T} & & T
+}
+\end{equation}
+\begin{equation}\label{eq:psicomp2}
+\xymatrix@R+1pc@C+1pc{
+T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\psi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
+T \ar[rr]_-{1_T} & & T
+}
+\end{equation}
+\begin{equation}\label{eq:psicomp3}
+\xymatrix@R+1pc@C+1pc{
+T( \Psi \otimes \Psi ) \ar[r]^-{\tau}\ar[d]_-{-\tau} & \Psi T( 1 \otimes \Psi ) \ar[d]^-{\tau}\\
+\Psi T( \Psi \otimes 1 ) \ar[r]_-{\tau} & \Psi^2 T
+}
+\end{equation}
+expresses that $T$ is a superfunctor.
 
 \begin{lemma}\label{lemma:constructingsuper}
-Given a bicategory $\cat{B}$ with the structure of a supercategory on $\cat{B}(a,b)$ for all pairs $a,b$, and natural isomorphisms $\tau$, suppose that \eqref{eq:psiunitor1}-\eqref{eq:psilastdia} commute.
+Given a bicategory $\cat{B}$ with the structure of a supercategory on $\cat{B}(a,b)$ for all pairs $a,b$, and natural isomorphisms $\tau$, suppose that \eqref{eq:psiunitor1}-\eqref{eq:psicomp3} commute.
 Then with $\Psi, \xi$ and $\gamma$ defined as above, $\cat{B}$ is a superbicategory.
@@
 
+\bibitem{girard_llogic}
+J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
+
 \bibitem{gray}
@@
 
-\bibitem{girard_llogic}
-J.-Y.~Girard, \textsl{Linear Logic}, Theoretical Computer Science 50 (1) (1987), 1--102.
+\bibitem{greuel}
+G.-M.~Greuel, C.~Lossen and E.~Shustin, \textsl{Introduction to singularities and deformations}, Springer (2007).
 
@@
 
-\bibitem{cutsystems2}
-D.~Murfet, \textsl{Computing with cut systems II}, in progress.
+%\bibitem{cutsystems2}
+%D.~Murfet, \textsl{Computing with cut systems II}, in progress.
 
 \bibitem{murfet_ll}
-\bysame, \textsl{Logic and linear algebra: an introduction}, \href{http://arxiv.org/abs/1407.2650}{[arXiv:1407.2650]}.
+D.~Murfet, \textsl{Logic and linear algebra: an introduction}, \href{http://arxiv.org/abs/1407.2650}{[arXiv:1407.2650]}.
 

### 2016-11-02 cutsystems-new.tex
Real second arXiv submission, with updated title.
Updates

@@
 
-\title{Computing with cut systems}
+\title{Cut systems and matrix factorisations I}
 \author{Daniel Murfet}
+
+% \classification{18D05, 18E30, 13C14}
+%18D05  	Double categories, $2$-categories, bicategories and generalizations
+%57R56  	Topological quantum field theories
+%13C14		Cohen-Macaulay modules
+%18E30		Derived and triangulated categories
 
@@
 The canonical action of $C_m$ on the spinor representation $S_m$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $S_m \otimes_k ( Y \otimes X )$.
-In Section \ref{section:superbicatLG} we defined an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible.
+In Definition \ref{defn:cliffordaction_cut} we gave an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible.
 

### 2016-11-02 cutsystems-new.tex
Typos

@@
 
-\title{Cut systems and matrix factorisations I}
+\title{The cut operation on matrix factorisations}
 \author{Daniel Murfet}
@@
 The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, attested to by the existence of adjoints and pivotality \cite{lgdual}, its role in recent important results in topological field theory \cite{genorb,ade} and the theory of homological knot invariants \cite{kr0401268}.
-This is remarkable in light of the fact that $1$-morphisms are very simple objects, namely, matrices of polynomials which satisfy an equation.
-This makes $\LG$ an attractive object of study, but for one major wrinkle: the composition operation for $1$-morphisms is infinitary.
+While the objects and $1$-morphisms of $\LG$ are very simple, the composition operation for $1$-morphisms has an ``infinitary'' character.
+This paper continues the study of this operation begun in \cite{dm1102.2957}.
 
@@
 This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$, which is only homotopy equivalent to a finite rank matrix factorisation.
-While this finite model can be proven abstractly to exist, there is no obvious way to describe it as a function of the input data $Y,X$.
+While this finite model can be proven abstractly to exist \cite{dm1102.2957} there is no obvious way to describe it as an explicit function of the input data $Y,X$.
 This means that we are stuck with infinite rank matrix factorisations in the theory.
@@
 \begin{equation}\label{eq:intro_clifford_act1_intro}
-\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}
-\end{equation}
-where the $\At_q$ are Atiyah classes. These operators satisfy Clifford relations
+\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}
+\end{equation}
+where the $\At_q$ are Atiyah classes and $\partial_{y_i} = \frac{\partial}{\partial y_i}$. These operators satisfy Clifford relations
 \be\label{eq:clifford_relations_intro}
@@
 The differential on $Y \l X$ and the Clifford operators can be written explicitly as matrices over $\nC[x,z]$, where the coefficients of the monomials in each row and column are polynomials in the monomial coefficients of $d_Y, d_X$ and $V$.
-Thus, the cut operation is a polynomial function of its inputs and, in particular, infinite rank matrix factorisations are banished.
+Thus, the cut operation is a polynomial function of its inputs and, in particular, infinite rank matrix factorisations do not appear in the definition of $\L$.
 
@@
 In Section \ref{section:intro_appli} we describe various applications.
-The main theorem (Theorem \ref{theorem:htpy_equivalence_main}) uses homological perturbation to produce a strong deformation retract, and in particular an isomorphism, in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $\nC[x,z]$ of the form
+By the results of \cite{dm1102.2957} there is an isomorphism in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $\nC[x,z]$ of the form
 \begin{equation}\label{eq:final_finite_model_intro}
@@
 \end{equation}
-where $S_m = \bigwedge ( \nC^{\oplus m}[1] )$ denotes the exterior algebra.
-The algebra $C_m = \End_{\nC}(S_m)$ is a Clifford algebra, and \eqref{eq:final_finite_model_intro} identifies the natural action of $C_m$ on the right hand side with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.
-
-There is a category called the \emph{Clifford thickening} of the homotopy category of matrix factorisations of $U - W$, in which objects are matrix factorisations equipped with a $C_k$-action for some $k$ (i.e.
-$k$ is allowed to be different for different objects).
+where $S_m = \bigwedge ( \nC^{\oplus m}[1] )$ denotes the exterior algebra on a $\nZ_2$-graded vector space.
+The algebra $C_m = \End_{\nC}(S_m)$ is a Clifford algebra.
+The main theorem of the present paper (Theorem \ref{theorem:htpy_equivalence_main}) identifies the natural action of $C_m$ on the right hand side of \eqref{eq:final_finite_model_intro} with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.
+
+There is a category called the \emph{Clifford thickening} of the homotopy category of matrix factorisations of $U - W$, in which objects are matrix factorisations equipped with a $C_l$-action for some $l$ (i.e.
+$l$ is allowed to be different for different objects).
 In this category $S_m \otimes_{\nC} ( Y \otimes X )$ with its $C_m$-action is isomorphic to $Y \otimes X$ with no Clifford action, and so \eqref{eq:final_finite_model_intro} can be read as a natural isomorphism $Y \l X \cong Y \otimes X$.
@@
 
-\subsubsection{Cut systems: a geometric enrichment of $\LG$}
-
-The \emph{cut systems} of the title are bicategories enriched over affine schemes.
-Our primary motivation for introducing $\cat{C}$ is that it can be enriched in this way (whereas $\LG$ cannot, because the composition is infinitary).
-For context we sketch the definition of a cut system here; the full definition will appear in a sequel to the present paper.
-
+\subsubsection{A geometric enrichment of $\LG$}
+
+Our primary motivation for introducing $\cat{C}$ is that it can be enriched over affine schemes; this is not true directly of $\LG$, because the composition is infinitary.
+For context we include a sketch.
 Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
@@
 
-In forthcoming work we use the cut system enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
+In forthcoming work we use the above enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
 Proofs in the logic are interpreted by certain correspondences between these pairs.
@@
 The bicategory of Landau-Ginzburg models is an example of a superbicategory.
-Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role in the definition of cut systems, superbicategories are the natural language.
+Since Clifford algebras (which are $\mathbb{Z}_2$-graded) play a fundamental role, superbicategories are the natural language.
 Our main references for the foundations are \cite{ellis_lauda,kang,kang2}, but we give the full definitions below as these references work only with strict bicategories.
@@
 
-\begin{remark}\label{remark:relation_to_toby_paper} The cut system presented here refines earlier work in \cite{dm1102.2957}.
+\begin{remark}\label{remark:relation_to_toby_paper} The cut operation presented here refines earlier work in \cite{dm1102.2957}.
 To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$.
@@
 \end{equation}
-where $A = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
+where $C = \tau( 1 + \phi \tau )^{-1} = \sum_{m \ge 0} (-1)^m \tau (\phi \tau)^m$ and
 \begin{align*}
-\sigma_\infty &= \sigma - \phi A \sigma,\\
-\pi_\infty &= \pi - \pi A \phi,\\
-d_\infty &= d + \pi A \sigma\,.
+\sigma_\infty &= \sigma - \phi C \sigma,\\
+\pi_\infty &= \pi - \pi C \phi,\\
+d_\infty &= d + \pi C \sigma\,.
 \end{align*}
@@
 In this notation, the aim of all of this is to compute the commutators $[c, D^n]$ and then $[c, \exp(-D)]$.
-Since most of the calculation can be done in $A$, so we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.
+Since most of the calculation can be done in $A$, we stick to the general setting as long as possible, and maintain the notation $a_i, b_i, c, D$ and \eqref{defn:tau}, \eqref{defn:bq} of the previous lemma.
 
@@
 \]
-Since our main example is constructing the superbicategory associated to a cut system, we write $T(X,Y)$ as $Y \l X$.
+Since our main example is constructing the superbicategory associated to the cut operation, we write $T(X,Y)$ as $Y \l X$.
 We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.

### 2017-07-22 referee-reply.tex
Updates

\documentclass[english,letter paper,12pt,leqno]{article}
\usepackage{stmaryrd}
\usepackage{amsmath, amscd, amssymb, mathrsfs, accents, amsfonts,amsthm}
\usepackage[all]{xy}
\usepackage{dsfont}
\usepackage{tikz}
\def\nicedashedcolourscheme{\shadedraw[top color=blue!22, bottom color=blue!22, draw=gray, dashed]}
\def\nicecolourscheme{\shadedraw[top color=blue!22, bottom color=blue!22, draw=white]}
\def\nicepalecolourscheme{\shadedraw[top color=blue!12, bottom color=blue!12, draw=white]}
\def\nicenocolourscheme{\shadedraw[top color=gray!2, bottom color=gray!25, draw=white]}
\def\nicereallynocolourscheme{\shadedraw[top color=white!2, bottom color=white!25, draw=white]}
\definecolor{Myblue}{rgb}{0,0,0.6}
\usepackage[a4paper,colorlinks,citecolor=Myblue,linkcolor=Myblue,urlcolor=Myblue,pdfpagemode=None]{hyperref}

\SelectTips{cm}{}

\setlength{\evensidemargin}{0.1in}
\setlength{\oddsidemargin}{0.1in}
\setlength{\textwidth}{6.3in}
\setlength{\topmargin}{0.0in}
\setlength{\textheight}{8.5in}
\setlength{\headheight}{0in}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{setup}[theorem]{Setup}

\newtheoremstyle{example}{\topsep}{\topsep}
	{}
	{}
	{\bfseries}
	{.}
	{2pt}
	{\thmname{#1}\thmnumber{ #2}\thmnote{ #3}}

	\theoremstyle{example}
	\newtheorem{definition}[theorem]{Definition}
	\newtheorem{example}[theorem]{Example}
	\newtheorem{remark}[theorem]{Remark}
	\newtheorem{strat}[theorem]{Strategy}

\numberwithin{equation}{section}

% Operators
\def\eval{\operatorname{ev}}
\def\res{\operatorname{Res}}
\def\Coker{\operatorname{Coker}}
\def\Ker{\operatorname{Ker}}
\def\im{\operatorname{Im}}
\def\can{\operatorname{can}}
\def\K{\mathbf{K}}
\def\D{\mathbf{D}}
\def\N{\mathbf{N}}
\def\LG{\mathcal{LG}}
\def\Ab{\operatorname{Ab}}
\def\Hom{\operatorname{Hom}}
\def\modd{\operatorname{mod}}
\def\Modd{\operatorname{Mod}}
\def\be{\begin{equation}}
\def\ee{\end{equation}}
\def\nN{\mathds{N}}
\def\nZ{\mathds{Z}}
\def\nQ{\mathds{Q}}
\def\nR{\mathds{R}}
\def\nC{\mathds{C}}
\def\L{\mathcal{C}}
\def\ferm{\gamma}
\def\fermc{\gamma^\dagger}
\DeclareMathOperator{\Ext}{Ext}
\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\tot}{Tot}
\DeclareMathOperator{\ch}{ch}
\DeclareMathOperator{\str}{str}
\DeclareMathOperator{\hmf}{hmf}
\DeclareMathOperator{\HMF}{HMF}
\DeclareMathOperator{\hf}{HF}
\DeclareMathOperator{\At}{At}
\DeclareMathOperator{\Cat}{Cat}
\DeclareMathOperator{\Spec}{Spec}

\begin{document}

% Commands
\def\Res{\res\!}
\newcommand{\ud}{\mathrm{d}}
\newcommand{\Ress}[1]{\res_{#1}\!}
\newcommand{\cat}[1]{\mathcal{#1}}
\newcommand{\lto}{\longrightarrow}
\newcommand{\xlto}[1]{\stackrel{#1}\lto}
\newcommand{\mf}[1]{\mathfrak{#1}}
\newcommand{\md}[1]{\mathscr{#1}}
\def\sus{\l}
\def\l{\,|\,}
\def\sgn{\textup{sgn}}

\title{Reply to referee report}

I thank the referee for their useful comments, and make the following remarks in reply:

\begin{enumerate}
\item The referee is right to observe that while the term ``cut system'' appears prominently in the title and elsewhere in the paper, it is never really defined. After some consideration it seems to me better to remove the term from the paper altogether, and leave the development to sequels where it belongs. To this end I have removed all occurrences of ``cut system'' and referred instead to the ``cut operation'' which (I hope) is clearly defined in the text. Other occurrences of ``cut system'' (for instance in the discussion of linear logic) have been replaced by ``enrichment'' which is a more useful descriptor.

\item p.3 added reference for Atiyah classes.

\item p.5 the logical variable has been renamed to $\alpha$ for clarity.

\item p.8 the $\Psi_a$ are not given a form of $2$-functoriality in $a$, so no.

\item p.10 added a more precise reference

\item p.11 the nonstandard notation has been fixed.

\item p.13 Added $F = k^n$.

\end{enumerate}

In addition I have made some minor typographical corrections.

\end{document}

### 2017-07-22 cutsystems-new.tex
Updates

@@
 
-The bicategory $\LG$ of Landau-Ginzburg models has a rich structure, attested to by the existence of adjoints and pivotality \cite{lgdual}, its role in recent important results in topological field theory \cite{genorb,ade} and the theory of homological knot invariants \cite{kr0401268}.
-While the objects and $1$-morphisms of $\LG$ are very simple, the composition operation for $1$-morphisms has an ``infinitary'' character.
-This paper continues the study of this operation begun in \cite{dm1102.2957}.
-
-The objects of $\LG$ are a class of polynomials $W(x)$ called potentials, and $1$-morphisms $W(x) \lto V(y)$ are matrix factorisations of the difference $V(y) - W(x)$ over $\nC[x,y]$.
-Such a matrix factorisation is a $\nZ_2$-graded free $\nC[x,y]$-module $X = X^0 \oplus X^1$ together with an odd operator $d_X$ satisfying $d_X^2 = (V(y) - W(x)) \cdot 1_X$.
-These $1$-morphisms form a category denoted $\LG(W,V)$.
-For a third potential $U(z)$, composition is a functor
+The bicategory $\LG_k$ of Landau-Ginzburg models \cite{lgdual} over a noetherian $\mathbb{Q}$-algebra $k$ is a pivotal bicategory defined in terms of the geometry of isolated hypersurface singularities.
+This bicategory has various applications \cite{genorb,ade, kr0401268} but an obstacle to further development of the theory is that, while the objects, $1$-morphisms and $2$-morphisms of $\LG_k$ are simply described, the composition operation for $1$-morphisms has an ``infinitary'' character which makes it hard to work with.
+The current paper aims to resolve this problem.
+% This paper continues the study of this operation begun in \cite{dm1102.2957}.
+
+The objects of $\LG_k$ are a class of polynomials $W(x)$ called potentials, and $1$-morphisms $W(x) \lto V(y)$ are finite-rank matrix factorisations \cite{eisenbud} of the difference $V(y) - W(x)$ over $k[x,y]$.
+The idempotent completion of the homotopy category of such matrix factorisations is denoted $\LG_k(W,V)$.
+For a third potential $U(z)$, composition in $\LG_k$ is a functor
 \begin{gather*}
-\LG(V,U) \times \LG(W,V) \lto \LG(W,U)\,,\\
-(Y , X) \mapsto Y \circ X
+\LG_k(V,U) \times \LG_k(W,V) \lto \LG_k(W,U)\,,\\
+(Y , X) \longmapsto Y \circ X
 \end{gather*}
-% In this paper and its sequel we study an enrichment of $\LG$ which we refer to as a \emph{cut system}.
+% In this paper and its sequel we study an enrichment of $\LG_k$ which we refer to as a \emph{cut system}.
 defined for matrix factorisations $Y$ of $V - U$ and $X$ of $W - V$ by
 \be
-Y \circ X = \big( Y \otimes_{\nC[y]} X, d_Y \otimes 1 + 1 \otimes d_X \big)\,.
-\ee
-This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $\nC[x,z]$, which is only homotopy equivalent to a finite rank matrix factorisation.
-While this finite model can be proven abstractly to exist \cite{dm1102.2957} there is no obvious way to describe it as an explicit function of the input data $Y,X$.
-This means that we are stuck with infinite rank matrix factorisations in the theory.
-
-Together with Dyckerhoff we initiated in \cite{dm1102.2957} the study of these finite models in terms of homological perturbation and Atiyah classes, and in the present paper this program reaches its logical conclusion.
-We introduce a bicategory $\L$ in which the objects are again potentials and the $1$-morphisms $W \lto V$ are finite rank matrix factorisations of $V - W$ additionally equipped with the structure of a representation of a Clifford algebra.
-This bicategory is equivalent to $\LG$, but it is simpler: the composition operation is described by a finite number of polynomial functions of the input data.
+Y \circ X = \big( Y \otimes_{k[y]} X, d_Y \otimes 1 + 1 \otimes d_X \big)\,.
+\ee
+This is the analogue of convolution of Fourier-Mukai kernels in the matrix factorisation setting and suffers from the same defect, namely, the resulting matrix factorisation $Y \circ X$ is a free module of \emph{infinite rank} over $k[x,z]$.
+The problem of describing this \emph{a priori} infinite object in some finite way was studied in \cite{dm1102.2957} and the partial solution provided there was to explicitly describe a finite rank matrix factorisation together with an idempotent, splitting in the homotopy category of matrix factorisations to $Y \circ X$.
+However this solution is not sufficiently functorial to extent to a coherent description of the entire bicategory $\LG_k$.
+
+The current paper refines \cite{dm1102.2957} by presenting the idempotents developed there as arising from representations of Clifford algebras (see Remark \ref{remark:relation_to_toby_paper}).
+This leads us to define a new bicategory $\L$ in which the objects are again potentials and the $1$-morphisms $W \lto V$ are finite rank matrix factorisations of $V - W$ additionally equipped with the structure of a representation of a Clifford algebra.
+This bicategory is equivalent to $\LG_k$, but it is simpler: the composition operation is described by a finite number of polynomial functions of the input data.
 More precisely, the composition of $1$-morphisms in $\L$ is a functor
@@
 \L(V,U) \times \L(W,V) \lto \L(W,U)\,,\label{eq:cut_functor_intro}\\
-(Y,X) \mapsto Y \l X
+(Y,X) \longmapsto Y \l X
 \end{gather}
-which we call the \emph{cut operation}.
+which we call the \emph{cut operation}, and this operation is polynomial in the sense that the coefficients in the polynomials making up the matrix factorisation $Y \l X$ and its Clifford action are themselves polynomial functions of the coefficients defining $X,Y$.
+
  Let us describe the cut in the most important case, where $Y, X$ are matrix factorisations as above, not equipped with any additional structure as representations of a Clifford algebra.
-The Jacobi algebra $J_V = \nC[y_1,\ldots,y_m]/(\partial_{y_1} V, \ldots, \partial_{y_m} V)$ is a finite-dimensional $\nC$-vector space by the assumption that $V(y)$ is a potential, and the cut is defined to be the following finite rank matrix factorisation over $\nC[x,z]$
+The Jacobi algebra $J_V = k[y_1,\ldots,y_m]/(\partial_{y_1} V, \ldots, \partial_{y_m} V)$ is a finitely generated free $k$-module by the assumption that $V(y)$ is a potential, and the cut is defined to be the following finite rank matrix factorisation over $k[x,z]$
 \be
-Y \l X = Y \otimes_{\nC[y]} J_V \otimes_{\nC[y]} X = ( Y \otimes_{\nC[y]} X ) / (\partial V) (Y \otimes_{\nC[y]} X )
-\ee
-equipped with a family of odd closed operators $\{\ferm_i, \fermc_i\}_{i=1}^m$ defined by
+Y \l X = Y \otimes_{k[y]} J_V \otimes_{k[y]} X
+\ee
+equipped with a family of odd closed $k[x,z]$-linear operators $\{\ferm_i, \fermc_i\}_{i=1}^m$ defined by
 \begin{equation}\label{eq:intro_clifford_act1_intro}
@@
 \end{equation}
-where the $\At_q$ are Atiyah classes and $\partial_{y_i} = \frac{\partial}{\partial y_i}$. These operators satisfy Clifford relations
+where the $\At_q$ are Atiyah classes (Definition \ref{defn:atiyah}). These operators satisfy Clifford relations
 \be\label{eq:clifford_relations_intro}
@@
 up to homotopy (see Theorem \ref{theorem:cut_is_rep}).
-The differential on $Y \l X$ and the Clifford operators can be written explicitly as matrices over $\nC[x,z]$, where the coefficients of the monomials in each row and column are polynomials in the monomial coefficients of $d_Y, d_X$ and $V$.
+The differential on $Y \l X$ and the Clifford operators can be written explicitly as matrices over $k[x,z]$, where the coefficients of the monomials in each row and column are polynomials in the monomial coefficients of $d_Y, d_X$ and $V$.
 Thus, the cut operation is a polynomial function of its inputs and, in particular, infinite rank matrix factorisations do not appear in the definition of $\L$.
 
-Let us sketch where the cut operation comes from, why Clifford algebras are involved, and why there is an equivalence $\L \cong \LG$.
+Let us sketch where the cut operation comes from, why Clifford algebras are involved, and why there is an equivalence $\L \cong \LG_k$.
 In Section \ref{section:intro_appli} we describe various applications.
-By the results of \cite{dm1102.2957} there is an isomorphism in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $\nC[x,z]$ of the form
+By the results of \cite{dm1102.2957} there is an isomorphism in the homotopy category of (infinite rank) matrix factorisations of $U - W$ over $k[x,z]$ of the form
 \begin{equation}\label{eq:final_finite_model_intro}
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{\nC} ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
-}
-\end{equation}
-where $S_m = \bigwedge ( \nC^{\oplus m}[1] )$ denotes the exterior algebra on a $\nZ_2$-graded vector space.
-The algebra $C_m = \End_{\nC}(S_m)$ is a Clifford algebra.
-The main theorem of the present paper (Theorem \ref{theorem:htpy_equivalence_main}) identifies the natural action of $C_m$ on the right hand side of \eqref{eq:final_finite_model_intro} with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.
+Y \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{k} ( Y \otimes X )\ar@<-1ex>[l]_-{\Phi}
+}
+\end{equation}
+where $S_m = \bigwedge ( k^{\oplus m}[1] )$ denotes the exterior algebra as a $\nZ_2$-graded module, on the space $k^{\oplus m}$ placed in degree one.
+The main theorem (Theorem \ref{theorem:htpy_equivalence_main}) identifies the natural action of the Clifford algebra $C_m = \End_{k}(S_m)$ on the right hand side of \eqref{eq:final_finite_model_intro} with the action of $C_m$ via the aforementioned operators $\ferm_i, \fermc_i$ on the left hand side.
 
@@
 $l$ is allowed to be different for different objects).
-In this category $S_m \otimes_{\nC} ( Y \otimes X )$ with its $C_m$-action is isomorphic to $Y \otimes X$ with no Clifford action, and so \eqref{eq:final_finite_model_intro} can be read as a natural isomorphism $Y \l X \cong Y \otimes X$.
-We prove this is suitably functorial in $Y,X$ and therefore defines an equivalence $\L \cong \LG$.
+In this category $S_m \otimes_{k} ( Y \otimes X )$ with its $C_m$-action is isomorphic to $Y \otimes X$ with no Clifford action, and so \eqref{eq:final_finite_model_intro} can be read as a natural isomorphism $Y \l X \cong Y \otimes X$.
+We prove this is suitably functorial in $Y,X$ and therefore defines an equivalence $\L \cong \LG_k$.
 
@@
 The reason we need the formalism of supercategories is that we make extensive use of Clifford actions on objects of linear categories, and for this to make sense the categories themselves must be $\nZ_2$-graded (that is, supercategories).
-In Section \ref{section:lg_cut_system} we define $\L$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG$ as a superbicategory without units.
+In Section \ref{section:lg_cut_system} we define $\L$ and in Section \ref{section:equivllg} we prove it is equivalent to $\LG_k$ as a superbicategory without units.
 
@@
 
-As a special case of the deformation retract \eqref{eq:final_finite_model_intro} we obtain in Section \ref{example:computing_homs} for any potential $V(y)$ and matrix factorisations $X,X'$ of $V$ a deformation retract of $\nZ_2$-graded complexes of vector spaces
+As a special case of the deformation retract \eqref{eq:final_finite_model_intro} we obtain in Section \ref{example:computing_homs} for any potential $V(y)$ and matrix factorisations $X,X'$ of $V$ a deformation retract of $\nZ_2$-graded complexes of $k$-modules
 \begin{equation}\label{eq:final_finite_model_hom}
 \xymatrix@C+4pc{
-(X')^{\vee} \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{\nC} \Hom_{\nC[y]}(X', X) \ar@<-1ex>[l]_-{\Phi}
-}
-\end{equation}
-where $\Hom_{\nC[y]}(X',X)$ denotes the Hom-complex. Observe that this is infinite-dimensional (with finite-dimensional cohomology) while $(X')^{\vee} \l X$ is finite-dimensional.
-
-In the case $X = X'$ the right hand side is a DG-algebra and the deformation retract may be taken as the input to the standard algorithms for producing an $A_\infty$-minimal model of $\End_{\nC[y]}(X)$.
+(X')^{\vee} \l X \ar@<-1ex>[r]_-{\Phi^{-1}} & S_m \otimes_{k} \Hom_{k[y]}(X', X) \ar@<-1ex>[l]_-{\Phi}
+}
+\end{equation}
+where $\Hom_{k[y]}(X',X)$ denotes the Hom-complex. Observe that if $k$ is a field this is infinite-dimensional (with finite-dimensional cohomology) while $(X')^{\vee} \l X$ is finite-dimensional.
+
+In the case $X = X'$ the right hand side is a DG-algebra and the deformation retract may be taken as the input to the standard algorithms for producing an $A_\infty$-minimal model of $\End_{k[y]}(X)$.
 It turns out that this input is well-suited for actually doing computations, which we hope to return to elsewhere.
 
-\subsubsection{A geometric enrichment of $\LG$}
-
-Our primary motivation for introducing $\cat{C}$ is that it can be enriched over affine schemes; this is not true directly of $\LG$, because the composition is infinitary.
-For context we include a sketch.
+\subsubsection{A geometric enrichment of $\LG_k$}
+
+Our primary motivation for introducing $\cat{C}$ is that it can be enriched over affine schemes; this is not true directly of $\LG_k$, because the composition is infinitary.
+For context we include a sketch, assuming $k$ is an algebraically closed field of characteristic zero.
 Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
 \be\label{eq:intro_capitalD}
-D \in M_{2r}( \nC[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
+D \in M_{2r}( k[x,y] ) \qquad \text{ satisfying } \qquad D^2 = (V(y) - W(x)) \cdot I_{2r}
 \ee
 where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices.
-If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $\nC$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.
+If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $k$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.
 
@@
 \begin{equation}\label{eq:param_frmf}
-\cat{C}(W,V) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{\nC}
-\end{equation}
-where $Z_{\nC}$ denotes the $\nC$-points of a scheme $Z$. The cut operation is a polynomial function of its inputs, so there is an indexed family of morphisms of schemes
+\cat{C}(W,V) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{k}
+\end{equation}
+where $Z_{k}$ denotes the $k$-points of a scheme $Z$. The cut operation is a polynomial function of its inputs, so there is an indexed family of morphisms of schemes
 \be\label{eq:enrichment_morphisms_intro}
@@
 \ee
-Given two finite-rank matrix factorisations $X,X'$ of $V - W$ the fiber of this vector bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{\nC[x,y]}(X',X)$ tensored with a suitable spinor representation.
-The cut system which enriches $\cat{C}$ consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.
+Given two finite-rank matrix factorisations $X,X'$ of $V - W$ the fiber of this vector bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{k[x,y]}(X',X)$ tensored with a suitable spinor representation.
+The enrichment of $\cat{C}$ consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.
 
@@
 
-In forthcoming work we use the above enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, \nC[x], W)$ where $\md{X}$ is a scheme and $W \in \nC[x]$ is a potential.
+In forthcoming work we use the above enrichment of $\L$ to define a semantics of linear logic \cite{girard_llogic} in which formulas are interpreted by tuples $(\md{X}, k[x], W)$ where $\md{X}$ is a scheme and $W \in k[x]$ is a potential.
 Proofs in the logic are interpreted by certain correspondences between these pairs.
@@
 
-Let $x$ be a variable of the logic and suppose it has denotation $\llbracket x \rrbracket = (\Spec(\nC), \nC[x], W)$ in the semantics.
+Let $\alpha$ be a variable of the logic and suppose it has denotation $\llbracket \alpha \rrbracket = (\Spec(k), k[x], W)$ in the semantics.
 Let $\mathscr{M} = \mathscr{M}(W,W)$ be the (indexed) affine scheme parametrising $1$-morphisms $X: W \lto W$ in $\L$, as discussed above.
@@
 \begin{gather*}
-\llbracket x \multimap x \rrbracket = \big(\Spec(\nC), \nC[x,x'], W(x) - W(x') \big)\,,\\
-\llbracket {!}( x \multimap x ) \rrbracket = \big( \mathscr{M}, \nC, 0 \big)\,.
+\llbracket \alpha \multimap \alpha \rrbracket = \big(\Spec(k), k[x,x'], W(x) - W(x') \big)\,,\\
+\llbracket {!}( \alpha \multimap \alpha ) \rrbracket = \big( \mathscr{M}, k, 0 \big)\,.
 \end{gather*}
-A proof of the sequent ${!}(x \multimap x) \vdash x \multimap x$ has for its denotation a correspondence between $\llbracket {!}( x \multimap x ) \rrbracket$ and $\llbracket x \multimap x \rrbracket$, which is a matrix factorisation of $W(x) - W(x')$ over the scheme $\mathscr{M} \times \Spec(\nC[x,x'])$.
-For example, the Church numeral $\underline{2}$ has for its denotation the matrix factorisation whose fiber over a loop $X: W \lto W$, viewed as a point of $\mathscr{M}$, is the square $X \l X$ as a matrix factorisation of $W(x) - W(x')$ over $\Spec(\nC[x,x'])$.
+A proof of the sequent ${!}(\alpha \multimap \alpha) \vdash \alpha \multimap \alpha$ has for its denotation a correspondence between $\llbracket {!}( \alpha \multimap \alpha ) \rrbracket$ and $\llbracket \alpha \multimap \alpha \rrbracket$, which is a matrix factorisation of $W(x) - W(x')$ over the scheme $\mathscr{M} \times \Spec(k[x,x'])$.
+For example, the Church numeral $\underline{2}$ has for its denotation the matrix factorisation whose fiber over a loop $X: W \lto W$, viewed as a point of $\mathscr{M}$, is the square $X \l X$ as a matrix factorisation of $W(x) - W(x')$ over $\Spec(k[x,x'])$.
 For these definitions to work, the coefficients of the monomials in the matrix factorisation $X \l X$ need to be given explicitly as polynomial functions of the coefficients in $X$.
-This means we have to use $\L$ rather than $\LG$.
+This means we have to use $\L$ rather than $\LG_k$.
 
@@
 
-Throughout $k$ is a commutative $\mathbb{Q}$-algebra. By default categories and functors are $k$-linear.
+Throughout $k$ is a noetherian $\mathbb{Q}$-algebra.\footnote{The noetherian hypothesis is only needed in Section \ref{section:superbicatLG} when we pass from a ring to its adic completion with respect to the Jacobi ideal, and we wish to know the morphism from the ring to its completion is flat.
+This completion is only done to ensure the existence of a suitable connection - if a connection can be provided by other means (e.g.
+a grading) then the noetherian hypothesis could be dropped.} By default categories and functors are $k$-linear.
+We write $\partial_x$ for the differential operator $\frac{\partial}{\partial x}$.
 
@@
 
-\begin{definition} Let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra and $\cat{C}$ a supercategory.
+\begin{definition}\label{defn:algebra_modules} Let $A$ be a $\mathbb{Z}_2$-graded $k$-algebra and $\cat{C}$ a supercategory.
 A \emph{left $A$-module in $\cat{C}$} is an object $X \in \cat{C}$ together with a morphism of $\mathbb{Z}_2$-graded algebras $A \lto \cat{C}^*(X,X)$.
@@
 
-The bicategory of Landau-Ginzburg models $\LG$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$.
+The bicategory of Landau-Ginzburg models $\LG = \LG_k$ has for its objects pairs $(x,W)$ consisting of an ordered set of variables $x = (x_1,\ldots,x_n)$ and a potential $W \in k[x] = k[x_1,\ldots,x_n]$.
 Given potentials $W \in k[x]$ and $V \in k[y]$ the supercategory $\cat{LG}(W,V)$ is
@@
 \]
-Equipped with a certain differential (see \cite{lgdual}) this is a matrix factorisation of $W(x) - W(x')$ and defines the unit in $\cat{LG}(W,W)$ for composition of $1$-morphisms.
+Equipped with a certain differential (see \cite[(2.15)]{lgdual}) this is a matrix factorisation of $W(x) - W(x')$ and defines the unit in $\cat{LG}(W,W)$ for composition of $1$-morphisms.
 For the associator and unitor maps $\rho: X \otimes \Delta_W \lto X$ and $\lambda: \Delta_V \otimes X \lto X$ we also refer to \emph{ibid.}
@@
 
-\begin{lemma}\label{lemma:commutator_of_lambdas} There is a homotopy $[ \lambda_i, \lambda_j ] \simeq \partial_{x_i x_j}(W) \cdot 1_X$.
+\begin{lemma}\label{lemma:commutator_of_lambdas} There is a homotopy $[ \lambda_i, \lambda_j ] \simeq \partial_{x_i} \partial_{x_j}(W) \cdot 1_X$.
 \end{lemma}
@@
 \[
-\partial_{x_j}(d_X) \partial_{x_i}(d_X) + d_X \partial_{x_jx_i}(d_X) + \partial_{x_jx_i}(d_X) d_X + \partial_{x_i}(d_X) \partial_{x_j}(d_X) = \partial_{x_ix_j}W
+\partial_{x_j}(d_X) \partial_{x_i}(d_X) + d_X \partial_{x_j} \partial_{x_i}(d_X) + \partial_{x_j} \partial_{x_i}(d_X) d_X + \partial_{x_i}(d_X) \partial_{x_j}(d_X) = \partial_{x_i} \partial_{x_j}W
 \]
@@
 \[
-\lambda_i \lambda_j + \lambda_j \lambda_i = \partial_{x_ix_j}W + [d, -\partial_{x_jx_i}(d_X)]\,.
+\lambda_i \lambda_j + \lambda_j \lambda_i = \partial_{x_i} \partial_{x_j}W + [d, -\partial_{x_j} \partial_{x_i}(d_X)]\,.
 \]
@@
 \be\label{eq:clifford_relations}
-[\ferm_i, \ferm_j] = 0, \qquad [\fermc_i, \fermc_j] = 0, \qquad [\ferm_i, \fermc_j] = \delta_{ij}\,.
+[\ferm_i, \ferm_j] = 0, \qquad [\fermc_i, \fermc_j] = 0, \qquad [\ferm_i, \fermc_j] = \delta_{ij}
 \ee
@@
 This is a $\mathbb{Z}_2$-graded $k$-algebra when we assign $|v| = 1$ for all $v \in V$ and $|1| = 0$.
-If we take $V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then $C_n$ is the Clifford algebra of the pair $(V,B)$.
+If we take $F = k^n, V = F \oplus F^*$ with the bilinear form $B$ under which $B(F,F) = 0, B(F^*, F^*) = 0$ and for $x \in F$ and $\nu \in F^*$, $B(x, \nu) = \frac{1}{2} \nu(x)$, then the algebra $C_n$ defined above is the Clifford algebra of the pair $(V,B)$.
 \end{remark}
@@
 We construct a new supercategory $\cat{T}^\bullet$ called the \emph{Clifford thickening} in which the objects are pairs $(X,n)$ of an integer $n \ge 0$ and a left $C_n$-module $X$ in $\cat{T}$.
-Recall that if $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{T}_A$ denotes the supercategory of $A$-modules in $\cat{T}$ with $A$-linear maps.
+Recall that if $A$ is a $\mathbb{Z}_2$-graded $k$-algebra then $\cat{T}_A$ denotes the supercategory of $A$-modules in $\cat{T}$ with $A$-linear maps (see Definition \ref{defn:algebra_modules}).
 
@@
 
-Similarly to Example \ref{example:bicategory_m} there is a superbicategory $\cat{M}$ of Morita trivial $\mathbb{Z}_2$-graded $k$-algebras: $1$-morphisms are $\mathbb{Z}_2$-graded bimodules which are finitely generated and projective over $k$ and $2$-morphisms are degree zero bimodule maps.
-We will need the operation of tensoring objects of $\cat{T}$ with $k$-modules, which is recalled in Appendix \ref{section:tensorproduct_supcat}.
+\begin{definition} Let $\cat{M}$ denote the superbicategory of Morita trivial $\mathbb{Z}_2$-graded $k$-algebras.
+The $1$-morphisms are $\mathbb{Z}_2$-graded bimodules which are finitely generated and projective over $k$ and the $2$-morphisms are degree zero bimodule maps (see Example \ref{example:bicategory_m}).
+\end{definition}
+
+We will need to tensor objects of $\cat{T}$ with $k$-modules, which is recalled in Appendix \ref{section:tensorproduct_supcat}.
 
@@
 We relegate the proof that this functor gives a bijection on morphism sets to Lemma \ref{lemma:morphisms_two_forms}.
-Functoriality is easily checked, and $\Theta(1_X) = e_n$ since by definition $\iota_{n,n} = e_n$.
+Functoriality is easily checked, and $\Theta(1_X) = 1^*_{(X,n)}$ since by definition $\iota_{n,n} = e_n$.
 \end{proof}
@@
 
-The next step is to equip $Y \l X$ with a Clifford action, which will be defined using the partial derivatives $\partial_{y_i}(d_X)$ and Atiyah classes.
-The Atiyah classes are defined by first taking the technical step of extending scalars
+The next step is to equip $Y \l X$ with a Clifford action. To do this we need to take the technical step of passing to a completion of the ring $k[y]$.
+
+\begin{definition} For $1 \le i \le m$ set $t_i = \partial_{y_i} V$ and let $I = (t_1,\ldots,t_m) \subseteq k[y]$. Then
+\[
+\widehat{k[y]} = \varprojlim_r k[y]/I^r
+\]
+denotes the completion of $k[y]$ at the ideal $I$, that is, along the critical locus of $V$.
+
+We also define the completed tensor product of $Y, X$ to be
 \begin{equation}\label{eq:completed_tensor_product}
-Y \,\check{\otimes}\, X = Y \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} X
-\end{equation}
-and putting a connection on this module.
-We write $t = (t_1,\ldots,t_m)$ for the quasi-regular sequence of partial derivatives $t_i = \partial_{y_i} V$ and recall that there is by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
+Y \,\widehat{\otimes}\, X = Y \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} X
+\end{equation}
+\end{definition}
+
+\begin{remark}\label{remark:flatness} By hypothesis $k$ is noetherian, hence so is $k[y]$ and therefore the canonical ring morphism $k[y] \lto \widehat{k[y]}$ is flat. 
+\end{remark}
+
+By \cite[Appendix B]{dm1102.2957} there exists a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
 \begin{equation}\label{eq:connection_nabla}
-\nabla: k\llbracket y \rrbracket \lto k\llbracket y \rrbracket \otimes_{k[t]} \Omega^1_{k[t]/k}
-\end{equation}
-the components of which are $k$-linear operators $\partial_{t_i}: k\llbracket y \rrbracket \lto k\llbracket y \rrbracket$.
+\nabla: \widehat{k[y]} \lto \widehat{k[y]} \otimes_{k[t]} \Omega^1_{k[t]/k}
+\end{equation}
+the components of which are $k$-linear operators $\partial_{t_i}: \widehat{k[y]} \lto \widehat{k[y]}$.
 A simple example of such a connection is given in Section \ref{example:computing_homs}.
@@
 \begin{gather*}
-\partial_{t_i}: Y \, \check{\otimes}\, X \lto Y \, \check{\otimes}\, X\\
+\partial_{t_i}: Y \, \widehat{\otimes}\, X \lto Y \, \widehat{\otimes}\, X\\
 e_a \otimes h(y) \otimes f_b \mapsto e_a \otimes \partial_{t_i}( h(y) ) \otimes f_b\,.
@@
 \be
-[ d_{Y \otimes X}, \partial_{t_i} ] = d_{Y \otimes X} \partial_{t_i} - \partial_{t_i} d_{Y \otimes X}: Y \, \check{\otimes}\, X \lto Y \, \check{\otimes}\, X
-\ee
-is $k[t]$-linear and passes to a $k[x,z]$-linear operator on $Y \l X \cong \left( Y \, \check{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
+[ d_{Y \otimes X}, \partial_{t_i} ] = d_{Y \otimes X} \partial_{t_i} - \partial_{t_i} d_{Y \otimes X}: Y \, \widehat{\otimes}\, X \lto Y \, \widehat{\otimes}\, X
+\ee
+is $k[t]$-linear and passes to a $k[x,z]$-linear operator on $Y \l X \cong \left( Y \, \widehat{\otimes}\, X \right) \otimes_{k[t]} k[t]/(t)$.
 \end{lemma}
@@
 
-\begin{definition} The $i$th Atiyah class is this odd $k[x,z]$-linear operator
+\begin{definition}\label{defn:atiyah} The $i$th Atiyah class is this odd $k[x,z]$-linear operator
 \[
@@
 
-This operator is the $i$th Atiyah class of $Y \,\check{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}.
+This operator is the $i$th Atiyah class of $Y \,\widehat{\otimes}\, X$ relative to the ring morphism $k[x,y] \lto k[x,y,t]$ as defined in \cite[Section 9]{dm1102.2957}.
 A reference for Atiyah classes is \cite{buchweitz_flenner}, but we will prove the necessary properties here for the reader's convenience.
@@
 \begin{equation}\label{eq:intro_clifford_act1}
-\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\,.
+\ferm_i = \At_i\,, \qquad \fermc_i = - \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}\,.
 \end{equation}
@@
 \begin{align*}
-[ \fermc_i, \ferm_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}, \At_j \big]\\
-&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [ \At_q, \At_j]\\
-&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [d, h_{qj}]\\
-&= \delta_{ij} + \big[d, -g_{ij} - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) h_{qj}\big]\,.
+[ \fermc_i, \ferm_j] &= \big[- \partial_{y_i}(d_X) - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}, \At_j \big]\\
+&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [ \At_q, \At_j]\\
+&= \delta_{ij} - [d, g_{ij}] - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [d, h_{qj}]\\
+&= \delta_{ij} + \big[d, -g_{ij} - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) h_{qj}\big]\,.
 \end{align*}
@@
 \begin{align*}
-[ \fermc_i, \fermc_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q y_j}(V) \At_{q} \Big]\\
-&= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
-&\quad + \frac{1}{2}\sum_q \partial_{y_q y_i}(V) \big[ \At_q, \partial_{y_j}(d_X) \big]\\
-&\quad + \frac{1}{4}\sum_{p,q} \partial_{y_py_i}(V) \partial_{y_qy_j}(V) \big[ \At_p, \At_q \big]\\
-&= \partial_{y_iy_j}(V) + [d, - \partial_{y_jy_i}(d_X)]\\
-&\qquad + \frac{1}{2}\sum_q \partial_{y_qy_j}(V) \left( -\delta_{iq} + [d, [ \partial_{t_q}, \partial_{y_i}(d_X)]] \right)\\
-&\qquad + \frac{1}{2} \sum_q \partial_{y_qy_i}(V) \left( -\delta_{jq} + [d, [\partial_{t_q}, \partial_{y_j}(d_X)]] \right)\\
-&\qquad + \frac{1}{4}\sum_{p,q} \partial_{y_py_i}(V) \partial_{y_qy_j}(V) [d, -[\partial_{t_q}, \At_p]]\\
+[ \fermc_i, \fermc_j ] &= \Big[ \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \At_{q}\; , \; \partial_{y_j}(d_X) + \frac{1}{2} \sum_q \partial_{y_q}\partial_{y_j}(V) \At_{q} \Big]\\
+&= [ \partial_{y_i}(d_X), \partial_{y_j}(d_X) ] + \frac{1}{2}\sum_q \partial_{y_q}\partial_{y_j}(V) \big[ \partial_{y_i}(d_X), \At_q \big]\\
+&\quad + \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_i}(V) \big[ \At_q, \partial_{y_j}(d_X) \big]\\
+&\quad + \frac{1}{4}\sum_{p,q} \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V) \big[ \At_p, \At_q \big]\\
+&= \partial_{y_iy_j}(V) + [d, - \partial_{y_j} \partial_{y_i}(d_X)]\\
+&\qquad + \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_j}(V) \left( -\delta_{iq} + [d, [ \partial_{t_q}, \partial_{y_i}(d_X)]] \right)\\
+&\qquad + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \left( -\delta_{jq} + [d, [\partial_{t_q}, \partial_{y_j}(d_X)]] \right)\\
+&\qquad + \frac{1}{4}\sum_{p,q} \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V) [d, -[\partial_{t_q}, \At_p]]\\
 &= [d, c_{ij}]
@@
 \begin{align*}
-c_{ij} &= - \partial_{y_jy_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_qy_j}(V)  [\partial_{t_q}, \partial_{y_i}(d_X)]\\
-&\qquad + \frac{1}{2} \sum_q \partial_{y_qy_i}(V) [\partial_{t_q}, \partial_{y_j}(d_X)]\\
-&\qquad - \frac{1}{4} \sum_{p,q}  \partial_{y_py_i}(V) \partial_{y_qy_j}(V)  [\partial_{t_q}, \At_p]\,.
+c_{ij} &= - \partial_{y_j} \partial_{y_i}(d_X) + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_j}(V)  [\partial_{t_q}, \partial_{y_i}(d_X)]\\
+&\qquad + \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) [\partial_{t_q}, \partial_{y_j}(d_X)]\\
+&\qquad - \frac{1}{4} \sum_{p,q}  \partial_{y_p} \partial_{y_i}(V) \partial_{y_q} \partial_{y_j}(V)  [\partial_{t_q}, \At_p]\,.
 \end{align*}
@@
 \[
-M = Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
+M = Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} \big( Y \otimes_{k[z]} J_V \otimes_{k[z]} X \big)
 \]
@@
 \begin{equation}\label{eq:assoc_proof_M}
-Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} \big( Y \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X \big)
+Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} \big( Y \otimes_{k[z]} \widehat{k[z]} \otimes_{k[z]} X \big)
 \end{equation}
@@
 \end{equation}
-By the same argument the action of $C_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} k\llbracket y \rrbracket \otimes_{k[y]} Y \big) \otimes_{k[z]} k\llbracket z \rrbracket \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}.
+By the same argument the action of $C_p$ on $(Z \l Y ) \l X$ is via $(1 \otimes \partial_{y_i}(d_Y)) \otimes 1$ and the Atiyah classes of $\big( Z \otimes_{k[y]} \widehat{k[y]} \otimes_{k[y]} Y \big) \otimes_{k[z]} \widehat{k[z]} \otimes_{k[z]} X$ relative to the same ring morphism \eqref{eq:assoc_proof_M2}.
 It is therefore clear that the associator $\alpha$ identifies these two actions.
@@
 
-We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}.
+\begin{remark}\label{remark:strongdefosigns} We follow the conventions of \cite{barneslambe} in defining strong deformation retracts; up to a sign this the same as the special deformation retracts of \cite{crainic} and \cite{dm1102.2957}.
 Namely, a strong deformation retract in the above sense is the same as a special deformation retract in the sense of \emph{ibid.} with $h = - \phi$.
+\end{remark}
 
@@
 
-\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(e) \cong \im(e')$ as graded $R$-modules, where $e = 1_A - [d, \phi]$ and $e' = 1_A - [d + \tau, \phi']$.
+\begin{definition} Given a splitting homotopy $\phi$ on $(A,d)$ and a perturbation $\tau$ in the above sense, the \emph{transference problem} is to find a splitting homotopy $\phi'$ on $(A, d + \tau)$ such that $\im(e) \cong \im(e')$ as graded $R$-modules, where $e = 1_A - [d, \phi]$ and $e' = 1_A - [d + \tau, \phi']$.
 \end{definition}
@@
 among operators with $x^2 = 0$ satisfying the boundary condition $\im(1_A - [d,x]) \cong \im(e)$. If $\phi \tau$ has finite order, i.e. $(\phi \tau)^m = 0$ for some $m$, then
-\[
+\begin{equation}\label{eq:formula_phi_infty}
 \phi_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \phi = \phi - \phi \tau \phi + \phi \tau \phi \tau \phi - \cdots
-\]
+\end{equation}
 is a solution of this fixed point problem:
@@
 \begin{theorem}[Perturbation lemma]\label{theorem:pertlemma} Suppose $\phi \tau$ has finite order.
-Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi)$ and satisfies the isomorphism condition in the transference problem.
+Then $\phi_\infty$ is a splitting homotopy on the linear factorisation $(A, \xi = d + \tau)$ and satisfies the isomorphism condition in the transference problem.
 \end{theorem}
@@
 \xymatrix@C+2pc{
-(M,d_\infty) \ar@<-1ex>[r]_{\sigma_\infty} & (A, \xi), \ar@<-1ex>[l]_{\pi_\infty}
+(M,d_\infty) \ar@<-1ex>[r]_{\sigma_\infty} & (A, \xi = d + \tau), \ar@<-1ex>[l]_{\pi_\infty}
 } \quad \phi_\infty
@@
 It is also possible to give a direct proof as in \cite{crainic}.
-%To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.
+In applications the most important output of the construction are the formulas \eqref{eq:formula_phi_infty} for $\phi_\infty$ and%To see that $\phi_\infty = (1 + \phi \tau)^{-1} \phi$ is the universal solution in the input data $\phi, d$ and $\tau$, one studies the fixed point equation $F(x) = x \xi x$ and develops a recurrence relation \cite[p.885]{barneslambe}.
+\be
+\sigma_\infty = \sum_{m \ge 0} (-1)^m (\phi \tau)^m \sigma\,,
+\ee
+which follows easily from the above.
 
@@
 \textbf{First step.} A finite model for $(K, d_K)$ is obtained using connections.
-The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $k\llbracket y \rrbracket \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra.
+The connection $\nabla$ of \eqref{eq:connection_nabla} extends canonically to an operator on $\widehat{k[y]} \otimes_{k[t]} \Omega^*_{k[t]/k}$ where $\Omega^* = \bigwedge \Omega^1$ is the exterior algebra.
 By identifying $d t_i$ with $\theta_i$ we may make the identification
 \[
-\check{K} := K \otimes_{k[y]} k\llbracket y \rrbracket \cong \Omega^*_{k[t]/k} \otimes_{k[t]} k\llbracket y \rrbracket 
-\]
-so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $\check{K}$.
-It is straightforward to check (see \cite[Lemma 8.7]{dm1102.2957}) that $[d_K, \nabla]$ is invertible on the graded submodule $\check{K}_{\le -1}$ of negative degree terms (in the usual $\nZ$-grading on the Koszul complex) and we define
+\widehat{K} := K \otimes_{k[y]} \widehat{k[y]} \cong \Omega^*_{k[t]/k} \otimes_{k[t]} \widehat{k[y]}
+\]
+so that $\nabla$ becomes identified with a degree $-1$ $k$-linear operator on $\widehat{K}$.
+It is straightforward to check (see \cite[Lemma 8.7]{dm1102.2957}) that $[d_K, \nabla]$ is invertible on the graded submodule $\widehat{K}_{\le -1}$ of negative degree terms (in the usual $\nZ$-grading on the Koszul complex) and we define
 \[
@@
 
-\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $(\check{K},d_K)$.
+\begin{proposition} $H$ is a $k$-linear splitting homotopy on the complex $(\widehat{K},d_K)$.
 \end{proposition}
@@
 \xymatrix@C+2pc{
-(J_V,0) \ar@<-1ex>[r]_{\sigma} & (\check{K}, d_K), \ar@<-1ex>[l]_{\pi}
+(J_V,0) \ar@<-1ex>[r]_{\sigma} & (\widehat{K}, d_K), \ar@<-1ex>[l]_{\pi}
 } \quad H
 \end{equation}
-where $J_V$ is the Jacobi algebra from \eqref{eq:defnjacobian}, $\pi: \check{K} \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $k\llbracket y \rrbracket \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $k\llbracket y \rrbracket$ uniquely determined by $\nabla$.
-The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of the Koszul complex $\check{K}$.
-
-Recall that the tensor product $Y \,\check{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,z]\llbracket y \rrbracket$.
+where $J_V$ is the Jacobi algebra from \eqref{eq:defnjacobian}, $\pi: \widehat{K} \lto J_V$ is the canonical quasi-isomorphism which vanishes on $K_{\le -1}$ and is in degree zero the quotient map $\widehat{k[y]} \lto J_V$, and $\sigma$ is a $k$-linear embedding of $J_V$ into $\widehat{k[y]}$ uniquely determined by $\nabla$.
+The splitting homotopy $H$, or equivalently the deformation retract \eqref{eq:originalHdef}, is the desired finite model of $\widehat{K}$.
+Note that \eqref{eq:originalHdef} is \cite[(10.1)]{dm1102.2957}, modulo the sign difference referred to in Remark \ref{remark:strongdefosigns}.
+
+Recall that the tensor product $Y \,\widehat{\otimes}\, X$ of \eqref{eq:completed_tensor_product} is a finite rank matrix factorisation of $U - W$ over $R = k[x,z] \otimes_k \widehat{k[y]}$.
 The connection $\nabla$ extends to a standard $k[x,z]$-linear flat connection on $R$.
@@
 \begin{equation}\label{eq:lambdaiso2}
-\check{K} \otimes_{k\llbracket y \rrbracket}( Y \,\check{\otimes}\, X ) \cong \check{K} \otimes_{k\llbracket y \rrbracket} (R \otimes_k Q) \cong \check{K} \otimes_k k[x,z] \otimes_k Q
-\end{equation}
-In this way the $k$-linear splitting homotopy $H$ on $\check{K}$ induces an $k[x,z]$-linear operator $H \otimes 1$ on $\check{K} \otimes_{k\llbracket y \rrbracket}( Y \,\check{\otimes}\, X)$, which we again denote by $H$.
+\widehat{K} \otimes_{\widehat{k[y]}}( Y \,\widehat{\otimes}\, X ) \cong \widehat{K} \otimes_{\widehat{k[y]}} (R \otimes_k Q) \cong \widehat{K} \otimes_k k[x,z] \otimes_k Q
+\end{equation}
+In this way the $k$-linear splitting homotopy $H$ on $\widehat{K}$ induces an $k[x,z]$-linear operator $H \otimes 1$ on $\widehat{K} \otimes_{\widehat{k[y]}}( Y \,\widehat{\otimes}\, X)$, which we again denote by $H$.
 It is immediate that
 
-\begin{lemma} $H$ is a $k[x,z]$-linear splitting homotopy on $(\check{K} \otimes_{k\llbracket y \rrbracket} ( Y \,\check{\otimes}\, X ), d_K)$.
+\begin{lemma} $H$ is a $k[x,z]$-linear splitting homotopy on $(\widehat{K} \otimes_{\widehat{k[y]}} ( Y \,\widehat{\otimes}\, X ), d_K)$.
 \end{lemma}
@@
 \xymatrix@C+2pc{
-(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
+(Y \l X,0) \ar@<-1ex>[r]_-{\sigma} & (\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X, d_K), \ar@<-1ex>[l]_-{\pi}
 } \quad H
 \]
-The map $\pi$ is $R$-linear induced by the map $\pi: \check{K} \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.
+The map $\pi$ is $R$-linear induced by the map $\pi: \widehat{K} \lto J_V$, and $\sigma = 1 \otimes \sigma$ is defined using map $\sigma$ of \eqref{eq:originalHdef} and the isomorphism \eqref{eq:lambdaiso2}.
 This is the desired finite model of $K \otimes Y \otimes X$ equipped with only the differential $d_K$.
@@
 \textbf{Second step.} We now view $d_{Y \otimes X}$ as a perturbation.
-The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
+The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
 Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
@@
 
-Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $k[x,z]$-linear splitting homotopy on $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ and the associated $k[x,z]$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
+Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $k[x,z]$-linear splitting homotopy on $\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X$ and the associated $k[x,z]$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
 \begin{equation}\label{eq:finite_model_defo}
 \xymatrix@C+4pc{
-\big( Y \l X, d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{\sigma_\infty} & \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X, d_K + d_{Y \otimes X} \big)\,, \ar@<-1ex>[l]_-{\pi}
+\big( Y \l X, d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{\sigma_\infty} & \big( \widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X, d_K + d_{Y \otimes X} \big)\,, \ar@<-1ex>[l]_-{\pi}
 } \quad \phi_\infty\,.
@@
 %\xymatrix@C+4pc{
-%Y \l X \ar@<-1ex>[r]_-{\exp(-\delta) \sigma_\infty} & S_m \otimes_k ( Y \,\check{\otimes}\, X )\ar@<-1ex>[l]_-{\pi \exp(\delta)}
+%Y \l X \ar@<-1ex>[r]_-{\exp(-\delta) \sigma_\infty} & S_m \otimes_k ( Y \,\widehat{\otimes}\, X )\ar@<-1ex>[l]_-{\pi \exp(\delta)}
 %}\,.
@@
 \begin{equation}\label{eq:iso_larger_object}
-\xymatrix@C+3pc{ \big( \check{K} \otimes_{k\llbracket y \rrbracket} Y \otimes X, d_K + d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{ \exp(\delta) } & \big( S_m \otimes_k Y \,\check{\otimes}\, X, d_{Y \otimes X} \big)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
+\xymatrix@C+3pc{ \big( \widehat{K} \otimes_{\widehat{k[y]}} Y \otimes X, d_K + d_{Y \otimes X} \big) \ar@<-1ex>[r]_-{ \exp(\delta) } & \big( S_m \otimes_k Y \,\widehat{\otimes}\, X, d_{Y \otimes X} \big)\ar@<-1ex>[l]_-{ \exp(-\delta) } }
 \end{equation}
@@
 \xymatrix@C+4pc{
-Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & \check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k ( Y \,\check{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
+Y \l X \ar@<-1ex>[r]_-{\sigma_\infty} & \widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X \ar@<-1ex>[l]_-{\pi} \ar@<-1ex>[r]_-{ \exp(\delta) } & S_m \otimes_k ( Y \,\widehat{\otimes}\, X ) \ar@<-1ex>[l]_-{ \exp(-\delta) }
 }\,.
 \end{equation}
-By \cite[Remark 7.7]{dm1102.2957} the canonical map $\epsilon: Y \otimes X \lto Y \,\check{\otimes}\, X$ is a homotopy equivalence over $k[x,z]$ so finally we have
+By \cite[Remark 7.7]{dm1102.2957} the canonical map $\epsilon: Y \otimes X \lto Y \,\widehat{\otimes}\, X$ is a homotopy equivalence over $k[x,z]$ (here we use that $k[y] \lto \widehat{k[y]}$ is flat, see Remark \ref{remark:flatness}) so finally we have
 
@@
 The canonical action of $C_m$ on the spinor representation $S_m$ by wedge product and contraction $\{ \theta_i, \theta_i^* \}_{i=1}^m$ (see Lemma \ref{defn:spinorrep}) induces an action  of $C_m$ on $S_m \otimes_k ( Y \otimes X )$.
-In Definition \ref{defn:cliffordaction_cut} we gave an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible.
+In Definition \ref{defn:cliffordaction_cut} we gave an action of $C_m$ on the cut $Y \l X$ by operators $\{ \ferm_i, \fermc_i \}_{i=1}^m$, and it remains to show that these two actions are compatible under \eqref{eq:final_finite_model}.
 
@@
 We prove that $\fermc_i \simeq \Phi \theta_i \Phi^{-1}$ and $\ferm_i \simeq \Phi \theta_i^* \Phi^{-1}$.
-With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $S_m \otimes_k ( Y \,\check{\otimes}\, X )$ to operators on the intermediate object $\check{K} \otimes_{k\llbracket y \rrbracket} Y \,\check{\otimes}\, X$ by
+With the diagram \eqref{eq:final_finite_model2} in mind, and following the terminology of Section \ref{section:cliffordactkos}, we define the transfers of $\theta_i, \theta_i^*$ from closed operators on $S_m \otimes_k ( Y \,\widehat{\otimes}\, X )$ to operators on the intermediate object $\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X$ by
 \[
@@
 \be\label{eq:comp338h}
-\cat{T}(\theta_i) \simeq \theta_i - \lambda_i - \frac{1}{2}\sum_q \partial_{y_q y_i}(V) \theta_q^*\,.
+\cat{T}(\theta_i) \simeq \theta_i - \lambda_i - \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_i}(V) \theta_q^*\,.
 \ee
@@
 \Phi \theta_i \Phi^{-1} &\simeq \pi \cat{T}(\theta_i) \sigma_\infty\\
-&\simeq - \pi \lambda_i \sigma_\infty - \frac{1}{2} \sum_q \partial_{y_qy_i}(V) \pi \theta_q^* \sigma_\infty\\
-&\simeq - \lambda_i - \frac{1}{2}\sum_q \partial_{y_qy_i}(V) \At_q\\
+&\simeq - \pi \lambda_i \sigma_\infty - \frac{1}{2} \sum_q \partial_{y_q} \partial_{y_i}(V) \pi \theta_q^* \sigma_\infty\\
+&\simeq - \lambda_i - \frac{1}{2}\sum_q \partial_{y_q} \partial_{y_i}(V) \At_q\\
 &= \fermc_i
@@
 
+\bibitem{eisenbud}
+D.~Eisenbud, \textsl{Homological algebra on a complete intersection, with an application to group representations}, Trans. Amer. Math. Soc. \textbf{260} (1980), 35--64.
+
 \bibitem{ellis_lauda}

### 2017-07-23 referee-reply.tex
Re-submission version

@@
 
+\item p.14 added a definition for $\cat{M}$.
+
+\item Typos in the penultimate sentence of the proof of Lemma 2.27 (now Lemma 2.28) corrected.
+
+\item Extra line in the proof of Lemma 3.2 fixed.
+
+\item Clarified the matrix assigned to $1 \in k$ in Remark 3.3.
+
+\item In (3.5) explained the notation for K\"ahler differentials
+
+\item Corrected ``this odd''
+
+\item In Lemma 3.9 clarified which differential is being referred to.
+
+\item Removed the reference to linear factorisation (it is not necessary).
+
+\item Fixed the definition of a morphism of strong deformation retracts.
+
+\item Changed one of the two $A$s to a $C$, near (4.9).
+
+\item Fixed equality that should have been $\simeq$ in second sentence of Section $4.2$.
+
+\item Proof of Lemma 4.16, changed ``commute'' to ``anticommute''.
+
+\item Removed Remark 4.30.
+
+\item Fixed typo in Definition 4.39.
+
+\item End of p.44 added reference to definition of $\cat{C}_A$.
+
+\item Fixed the definition of $T$ in Appendix B, and the typo in (B.7).
+
+\item Fixed references.
+
 \end{enumerate}
 
-In addition I have made some minor typographical corrections.
+In addition I have made some minor typographical corrections, and made the following more serious corrections:
+
+\begin{enumerate}
+\item I actually need the base ring $k$ to be noetherian in order for some completions to be flat algebras (see the footnote to the first sentence of the Background section), but this wasn't being assumed in the original version.
+\item In the original I took a completion from $k[y]$ to $k\llbracket y \rrbracket$ in order to ensure the existence of a connection (p.17 of the original).
+However what is actually needed is that this completion is separated and complete for the adic topology determined by the ideal $I$ generated by the partial derivatives $\partial_{y_i} V$, which is not true unless the origin is the only critical point.
+This was therefore a genuine error in the paper.
+However it is easily fixed by changing the completion to the $I$-adic completion everywhere, which has been done (see Definition 3.5).
+\end{enumerate}
 

### 2017-07-23 cutsystems-new.tex
Re-submission version

@@
 
-Our primary motivation for introducing $\cat{C}$ is that it can be enriched over affine schemes; this is not true directly of $\LG_k$, because the composition is infinitary.
-For context we include a sketch, assuming $k$ is an algebraically closed field of characteristic zero.
+One of our motivations for introducing $\cat{C}$ is that it has an enrichment over affine schemes.
+This is not true of $\LG_k$, precisely because the composition is infinitary.
+We hope to return to this elsewhere, but for context we include a sketch assuming $k$ is an algebraically closed field of characteristic zero.
 Given potentials $W(x), V(y)$, a matrix factorisation of $V(y) - W(x)$ is after choosing a homogeneous basis just a matrix
@@
 \ee
-where we require that, dividing $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices.
-If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by some integer $k$, we can parametrise matrix factorisations by the $k$-points of an affine scheme whose coordinates are the coefficients of the various monomials in each row and column of $D$.
-
-We may add further coordinates and equations to encode closed odd operators satisfying Clifford relations \eqref{eq:clifford_relations_intro} and, in this way, for a choice of parameters $\lambda = (r, k, \ldots)$ define a scheme $\mathscr{M}_{\lambda}(W,V)$ such that as sets
+where, dividing the matrix $D$ into $r \times r$ blocks, the upper left and bottom right blocks are zero matrices.
+If we fix the size $r$ of the blocks and bound the degrees of the monomials appearing in $D$ by an integer $s$, then we can easily parametrise matrix factorisations by the $k$-points of an affine scheme.
+
+We may add further coordinates and equations to encode closed odd operators satisfying Clifford relations \eqref{eq:clifford_relations_intro} and, in this way, for a choice of parameters $\lambda = (r, s, \ldots)$ define a scheme $\mathscr{M}_{\lambda}(W,V)$ such that as sets
 \begin{equation}\label{eq:param_frmf}
-\cat{C}(W,V) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{k}
+\operatorname{ob}(\cat{C}(W,V)) = \bigcup_{\lambda} \mathscr{M}_{\lambda}(W,V)_{k}
 \end{equation}
@@
 lifting the functor \eqref{eq:cut_functor_intro} on the level of objects for some function $f(\lambda, \mu)$ of indices.
-Finally, using the approach of Section \ref{example:computing_homs}, we can define for each pair of potentials $W,V$ and tuple of parameters $\lambda$ a bundle of Clifford representations
+Finally, using the approach of Section \ref{example:computing_homs}, we can define for each pair of potentials $W,V$ and tuple of parameters $\lambda$ a vector bundle of Clifford representations
 \be\label{eq:enrichment_intro_bundles}
@@
 \mathscr{H}\! om_{W,V,\lambda} \ar[d]\\
-\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)\,.
-}
-\ee
-Given two finite-rank matrix factorisations $X,X'$ of $V - W$ the fiber of this vector bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{k[x,y]}(X',X)$ tensored with a suitable spinor representation.
-The enrichment of $\cat{C}$ consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.
+\mathscr{M}_\lambda(W,V) \times \mathscr{M}_\lambda(W,V)\,,
+}
+\ee
+such that for matrix factorisations $X,X'$ of $V - W$ the fiber of this bundle over the point $(X',X)$ is the Clifford representation $(X')^{\vee} \l X$ of \eqref{eq:final_finite_model_hom}, which is isomorphic to the Hom-complex $\Hom_{k[x,y]}(X',X)$ tensored with a suitable spinor representation.
+
+The enrichment of $\cat{C}$ then consists of the family of schemes $\mathscr{M}_\lambda(W,V)$, the composition morphisms \eqref{eq:enrichment_morphisms_intro}, the bundles \eqref{eq:enrichment_intro_bundles}, and various other data satisfying natural constraints which encode the structure of the bicategory.
 
@@
 
-\begin{example} Supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
+\begin{example} Small supercategories, superfunctors and supernatural transformations form a superbicategory $\Cat^{\operatorname{sup}}_k$.
 \end{example}
@@
 \xymatrix@C+2pc{
-(X, n) \ar@<1ex>[r]^-{f} & (V,0) \ar@<1ex>[l]^-{g}\,.
+(X, n) \ar@<1ex>[r]^-{f} & (V,0) \ar@<1ex>[l]^-{g}
 }
@@
 \]
-Similarly $g_0$ defines a morphism $(V,0) \lto (X,n)$.
+Similarly $g_0$ is a morphism $(V,0) \lto (X,n)$ in $\cat{T}^{\star}$.
 Let $f,g$ be the morphisms in $\cat{T}^\bullet$ corresponding to $f_0,g_0$ under the equivalence of Lemma \ref{lemma:equivcliffordthick}.
-To prove that $fg = 1_{(X,n)}$ and $gf = 1_{(V,0)}$ in $\cat{T}^{\bullet}$ it suffices to prove that $f_0 g_0 = 1^*_{(X,n)} = e_n$ and $g_0 f_0 = 1^*_{(V,0)}$ in $\cat{T}^{\star}$.
+To prove that $fg = 1_{(X,n)}$ and $gf = 1_{(V,0)}$ in $\cat{T}^{\bullet}$ it suffices to prove that $g_0 f_0 = 1^*_{(X,n)} = e_n$ and $f_0 g_0 = 1^*_{(V,0)} = 1_V$ in $\cat{T}$.
 But this is true by definition.
@@
 Since $V$ is a potential $J_V$ is a finite rank free $k$-module, and it follows that $Y \l X$ is a finite rank free $k[x,z]$-module. 
-
 \end{proof}
@@
 \begin{remark}\label{remark:inflation} If we choose a $k$-basis for $J_V$ then multiplication by $y_i$, as a $k$-linear operator $J_V \lto J_V$, gives a matrix $[y_i]$ over $k$.
-The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$.
+The cut $Y \l X$ has a differential which, as a matrix, can be described by taking the matrix of $d_Y \otimes 1 + 1 \otimes d_X$ over $k[x,y,z]$ and replacing every occurrence of $y_i$ by the scalar matrix $[y_i]$ and $1 \in k$ by the identity matrix.
 This ``inflation'' produces a matrix of polynomials over $k[x,z]$.
@@
 
-By \cite[Appendix B]{dm1102.2957} there exists a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
+With $\Omega^1_{k[t]/k} \cong \bigoplus_{i=1}^m k[t] dt_i$ denoting K\"ahler diferentials, there exists by \cite[Appendix B]{dm1102.2957} a $k$-linear flat connection (which is ``standard'' in the sense of \cite[Definition 8.6]{dm1102.2957})
 \begin{equation}\label{eq:connection_nabla}
@@
 
-\begin{definition}\label{defn:atiyah} The $i$th Atiyah class is this odd $k[x,z]$-linear operator
+\begin{definition}\label{defn:atiyah} The $i$th Atiyah class is the odd $k[x,z]$-linear operator
 \[
@@
 
-\begin{lemma}\label{lemma:atiyahclosed} The operator $\At_i$ on $Y \l X$ is closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are $k[x,z]$-linear homotopies
+\begin{lemma}\label{lemma:atiyahclosed} $\At_i$ is $d_{Y \otimes X}$-closed, and if $\phi: X \lto X'$ and $\psi: Y \lto Y'$ are morphisms of matrix factorisations then there are $k[x,z]$-linear homotopies
 \be\label{eq:atiyahclosednatural}
@@
 \begin{proof}
-The Atiyah class is closed since
+The Atiyah class is closed since (with $d = d_{Y \otimes X}$)
 \[
@@
 
-By the graded Jacobi identity
+With $d = d_{Y \otimes X}$ the differential on $Y \l X$, we have by the graded Jacobi identity
 \begin{align*}
@@
 Specifically, the generator $\ferm_i$ of $C_p$ is the commutator $[d_{M}, \partial_s]$ where $s = \partial_{y_i} U$.
-But this operator can be identified with an Atiyah class of the linear factorisation
+But this operator can be identified with an Atiyah class of
 \begin{equation}\label{eq:assoc_proof_M}
@@
 \begin{remark}\label{remark:relation_to_toby_paper} The cut operation presented here refines earlier work in \cite{dm1102.2957}.
-To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto lowest degree in $S_m$.
+To see the connection, recall the idempotent $e_m \in C_m$ of Definition \ref{defn:idempotent_e} which corresponds to projection onto $k \cdot 1 \subset S_m$.
 The projector onto top degree $k \cdot \theta_1 \cdots \theta_m \subset S_m$ is
@@
 \end{itemize}
-A \emph{morphism} of strong deformation retracts is a commutative diagram
+A \emph{morphism} of strong deformation retracts is a a pair of morphisms of linear factorisations $\alpha: (M,d) \lto (M',d')$ and $\beta: (A,d) \lto (A',d')$ satisfying $\beta \sigma = \sigma' \alpha, \alpha \pi = \pi' \beta$, that is, making the two squares implicit in the diagram
 \[
@@
 \]
-that is, a pair of morphisms $\alpha, \beta$ such that $\beta \sigma = \sigma' \alpha$, $\alpha \pi = \pi' \beta$ and $\phi' \beta = \beta \phi$.
+commute, and in addition satisfying $\phi' \beta = \beta \phi$.
 \end{definition}
@@
 Let $R$ be a $k$-algebra and $(X,d)$ a complex of $R$-modules on which $t_1,\ldots,t_m \in R$ act null-homotopically.
-Tensoring $X$ with the Koszul complex $K(t_i)$ yields the same complex as taking the cone of $t_i \cdot 1_X = 0: X \lto X$, and therefore we have a homotopy equivalence
+Tensoring $X$ with the Koszul complex $K(t_i)$ yields the same complex as taking the cone of $t_i \cdot 1_X \simeq 0: X \lto X$, and therefore we have a homotopy equivalence
 \be
@@
 \begin{proof}
-Since $\theta_i^*$ commutes with $\delta$.
+Since $\theta_i^*$ anticommutes with $\delta$.
 \end{proof}
@@
 \[
-\delta^p [\delta, \theta_i] = \sum_{i+j=p} \binom{p}{i} [\delta, \theta_i]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [\delta, \lambda_i]^{(i)} \delta^j
+\delta^p [\delta, \theta_i] = \sum_{i+j=p} \binom{p}{i} [\delta, \theta_i]^{(i+1)} \delta^j = \sum_{i+j=p} \binom{p}{i} [\delta, \lambda_i]^{(i)} \delta^j\,.
 \]
@@
 
-\begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_m$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_m$.
+%\begin{remark} The construction of the Clifford operators $\psi_i, \psi_i^\dagger$ depends on the choice of homotopies $\lambda_1,\ldots,\lambda_m$, but it is clear from what we have just said that different choices give rise to isomorphic representations of $C_m$.
 An explicit isomorphism can be written down using the techniques developed in this Section.
-\end{remark}
+%\end{remark}
 
@@
 \end{equation}
-In this way the $k$-linear splitting homotopy $H$ on $\widehat{K}$ induces an $k[x,z]$-linear operator $H \otimes 1$ on $\widehat{K} \otimes_{\widehat{k[y]}}( Y \,\widehat{\otimes}\, X)$, which we again denote by $H$.
+In this way the $k$-linear splitting homotopy $H$ on $\widehat{K}$ induces a $k[x,z]$-linear operator $H \otimes 1$ on $\widehat{K} \otimes_{\widehat{k[y]}}( Y \,\widehat{\otimes}\, X)$, which we again denote by $H$.
 It is immediate that
@@
 The transference problem asks how to define a splitting homotopy $\phi_\infty$ on the matrix factorisation $(\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X , d_K + d_{Y \otimes X})$ in such a way that the underlying graded module is $Y \l X$.
-Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) that
+Since $H d_{Y \otimes X}$ has finite order, it follows from the perturbation lemma (Theorem \ref{theorem:pertlemma}) with $\tau = d_{Y \otimes X}, \phi = H$ that
 \[
@@
 is $k[x,z]$-linear splitting homotopy achieving the desired aim.
-
-Specifically, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is an $k[x,z]$-linear splitting homotopy on $\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X$ and the associated $k[x,z]$-linear strong deformation retract of linear factorisations of $U - W$ is of the form
+That is, by \cite[Proposition 7.1]{dm1102.2957} $\phi_\infty$ is a $k[x,z]$-linear splitting homotopy on $\widehat{K} \otimes_{\widehat{k[y]}} Y \,\widehat{\otimes}\, X$ and with
+\[
+\sigma_\infty = \sum_{m \ge 0} (-1)^m (H d_{Y \otimes X})^m \sigma
+\]
+there is a $k[x,z]$-linear strong deformation retract of linear factorisations of $U - W$
 \begin{equation}\label{eq:finite_model_defo}
@@
 \item for all $a,b \in \cat{C}$, $F_{a,b}: \cat{C}(a,b) \lto \cat{D}(Fa, Fb)$ is an equivalence of categories, and
-\item for all $d \in \cat{D}$ there exists $a \in \cat{C}$ with $Fa \cong c$ in the sense that there are $1$-morphisms $f: Fa \lto c$ and $g: c \lto Fa$ with $fg \cong 1$ and $gf \cong 1$.
+\item for all $c \in \cat{D}$ there exists $a \in \cat{C}$ with $Fa \cong c$ in the sense that there are $1$-morphisms $f: Fa \lto c$ and $g: c \lto Fa$ with $fg \cong 1$ and $gf \cong 1$.
 \end{itemize}
@@
 
-From now on $A,B,C$ are Morita trivial $k$-algebras. Recall $\cat{C}_A$ denotes the category of left $A$-modules in $\cat{C}$.
+From now on $A,B,C$ are Morita trivial $k$-algebras. Recall from Definition \ref{defn:algebra_modules} that $\cat{C}_A$ denotes the category of left $A$-modules in $\cat{C}$.
 
@@
 \[
-T: \cat{B}(a, b) \otimes_k \cat{B}(b,c) \lto \cat{B}(a,c)\,.
-\]
-Since our main example is constructing the superbicategory associated to the cut operation, we write $T(X,Y)$ as $Y \l X$.
+T: \cat{B}(b, c) \otimes_k \cat{B}(a,b) \lto \cat{B}(a,c)\,.
+\]
+Since our main example is constructing the superbicategory associated to the cut operation, we write $T(Y,X)$ as $Y \l X$.
 We denote the associator by $\alpha$, the units in $\cat{B}$ by $\Delta_a: a \lto a$, and the unitors for $X: a \lto b$ by $\lambda_X: \Delta_b \l X \lto X$ and $\rho_X: X \l \Delta_a \lto X$.
@@
 \xymatrix@R+1pc@C+1pc{
-T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\psi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
+T( \Psi^2 \otimes 1 ) \ar[r]^-{\tau} \ar[d]_-{T (\xi \otimes 1)}  & \Psi T( \Psi \otimes 1 ) \ar[r]^-{\tau} & \Psi^2 T \ar[d]^-{\xi * 1_T}\\
 T \ar[rr]_-{1_T} & & T
@@
 \bibitem{ade}
-N.~Carqueville, A.~Ros Camacho and I.~Runkel, \textsl{Orbifold equivalent potentials}, \href{http://arxiv.org/abs/1311.3354}{[arXiv:1311.3354]}.
+N.~Carqueville, A.~Ros Camacho and I.~Runkel, \textsl{Orbifold equivalent potentials}, Journal of Pure and Applied Algebra 220.2 (2016), 759--781, \href{http://arxiv.org/abs/1311.3354}{[arXiv:1311.3354]}.
 
@@
 N.~Carqueville and I.~Runkel, \textsl{On the monoidal structure of matrix bi-factorisations}, J. Phys.
-  A: Math. Theor. \textbf{43} (2010), 275401,
+  A: Math. Theor. \textbf{43} (2010), 
   \href{http://arxiv.org/abs/0909.4381}{[arXiv:0909.4381]}.
@@
 \bibitem{genorb}
-\bysame, \textsl{Orbifold completion of defect bicategories}, 
-\href{http://arxiv.org/abs/1210.6363}{[arXiv:1210.6363]}.
+\bysame, \textsl{Orbifold completion of defect bicategories}, Quantum Topology 7 (2016), 203--279, \href{http://arxiv.org/abs/1210.6363}{[arXiv:1210.6363]}.
 
@@
 \bibitem{ellis_lauda}
-A.~Ellis and A.~Lauda, \textsl{An odd categorification of $U_q(\mathfrak{sl}_2)$}, \href{http://arxiv.org/abs/1307.7816}{[arXiv:1307.7816]}.
+A.~Ellis and A.~Lauda, \textsl{An odd categorification of $U_q(\mathfrak{sl}_2)$}, Quantum Topology, Volume 7, Issue 2 (2016), 329--433, \href{http://arxiv.org/abs/1307.7816}{[arXiv:1307.7816]}.
 
@@
 \bibitem{kang2}
-\bysame, \textsl{Supercategorification of quantum Kac-Moody algebras II}, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.
+\bysame, \textsl{Supercategorification of quantum Kac-Moody algebras II},  Adv. Math \textbf{265} (2014) 169--240, \href{http://arxiv.org/abs/1303.1916}{[arXiv:1303.1916]}.
 
@@
 A.~Kapustin, \textsl{Topological {F}ield {T}heory, {H}igher {C}ategories, and
-  {T}heir {A}pplications},
-  \href{http://arxiv.org/abs/1004.2307}{[arXiv:1004.2307]}.
+  {T}heir {A}pplications}, Proceedings of the ICM 2010, \href{http://arxiv.org/abs/1004.2307}{[arXiv:1004.2307]}.
 
